### 2017-09-20 main.tex
Update on Overleaf.

\documentclass[modern]{aastex61}

%% Reintroduced the \received and \accepted commands from AASTeX v5.2
%\received{July 1, 2016}
%\revised{September 27, 2016}
\draft{\today}
%% Command to document which AAS Journal the manuscript was submitted to.
%% Adds "Submitted to " the arguement.
\submitjournal{ApJ}

%% Mark up commands to limit the number of authors on the front page.
%% Note that in AASTeX v6.1 a \collaboration call (see below) counts as
%% an author in this case.
%
%\AuthorCollaborationLimit=3
%

\shorttitle{\aastex\ Astropy Project II}
\shortauthors{Astropy Project et al.}

\begin{document}

\title{Astropy - New software standards for a growing community}

%%
%% The \author command is the same as before except it now takes an optional
%% arguement which is the 16 digit ORCID. The syntax is:
%% \author[xxxx-xxxx-xxxx-xxxx]{Author Name}
%%
%% This will hyperlink the author name to the author's ORCID page. Note that
%% during compilation, LaTeX will do some limited checking of the format of
%% the ID to make sure it is valid.
%%
%%
%% The new \altaffiliation can be used to indicate some secondary information
%% such as fellowships. This command produces a non-numeric footnote that is
%% set away from the numeric \affiliation footnotes.  NOTE that if an
%% \altaffiliation command is used it must come BEFORE the \affiliation call,
%% right after the \author command, in order to place the footnotes in
%% the proper location.
%%
%% Use \email to set provide email addresses. Each \email will appear on its
%% own line so you can put multiple email address in one \email call. A new
%% \correspondingauthor command is available in V6.1 to identify the
%% corresponding author of the manuscript. It is the author's responsibility
%% to make sure this name is also in the author list.
%%
%% While authors can be grouped inside the same \author and \affiliation
%% commands it is better to have a single author for each. This allows for
%% one to exploit all the new benefits and should make book-keeping easier.
%%
%% If done correctly the peer review system will be able to
%% automatically put the author and affiliation information from the manuscript
%% and save the corresponding author the trouble of entering it by hand.

\correspondingauthor{Astropy Coordinating committee or First Author}
\email{coordinators@astropy.org}

\author{Astropy Project}

\begin{abstract}

Astropy is amazing. and even more amazing than before

\end{abstract}

%% Keywords should appear after the \end{abstract} command. 
%% See the online documentation for the full list of available subject
%% keywords and the rules for their use.
\keywords{}

\section{Introduction} \label{sec:intro}

Moritz volunteered to write the intro

Difficulty of reversing design choices
Deciding if a feature should be included
difficulty to decide where general use ends and "handy feature for some" starts, i.e. how to reject PRs or deal with maintenance burden

\section{Major concepts}
\subsection{Astropy development model, astropy ecosystem}
This subsection should include some basic statistics about the contributors, commits, line of code etc. up to the 2.0 release when we know it.
\subsection{Mixin}
\subsection{Accuracy testing across many different implementation}

\section{Key features}

The astropy project aims to provide python-based packages for all tasks that are commonly needed in a large subset of the astronomical community. Two aspects of this (time and coordinate transformations) are already discussed in great detail in section 3. In this section, we highlight other features introduced or substantially improved since version v0.2, which is described in Astropy Collaboration et al. (2013).
(ordered in the order in which they appear in the astropy documentation)

\subsection{Constants}
versioning

\subsection{Coordinates}

start with short description of the astropy approach and features (JPL ephemerids, barycentric correction, proper motions, coordinate frames) then shows the tests. In particular, we had a discussion on problems with the definition of some coordinate system on the mailing list. Getting that discussion in here gives us a refereed paper to point to when we need to push the IAU to fix that.

\subsection{Units and quantities}

incl logarithmic units and magnitudes
speed improvements,
interaction with numpy arrays

\subsection{Data arrays}

\subsubsection{NDDdata}

\subsubsection{Tables}
QTable is new, mixin columns for time and coordinates. Table operations were added in v0.3

\subsection{Convolution}
Astropy implements `normalized convolution' (e.g., Knutsson and Westin 1993; http://ieeexplore.ieee.org/abstract/document/341081/), which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.   In version $<=1.3$, the direct convolution and fft convolution approaches were not consistent, with fft convolution implementing normalized convolution and direct convolution implementing a different approach.  As of v2.0, the two methods are consistent and include a suite of consistency checks.

\begin{figure}
\includegraphics[width=\textwidth]{convolution_example.png}
An example showing different modes of convolution available in the python ecosystem.  The red x's mark pixels that are set to NaN in the original data (a).  If the data are convolved with a Gaussian kernel on a 9x9 grid using scipy's direct convolution (b), any pixel within range of the original NaN pixels is also set to NaN.  Panel (c) shows what happens if the NaNs are set to zero first: the originally NaN regions are depressed relative to their surroundings.  Finally, panel (d) shows astropy's convolution behavior, where the missing pixels are replaced with values interpolated from their surroundings using the convolution kernel.
\end{figure}

\subsection{Modeling}
The whole modeling submodule was missing from the previous paper, so everything really, including compound models, unit support etc.

\subsection{Visualization}
wcsaxis, rgb, histograms comes to mind.Can use more publicity and also makes good images to include in the paper.

\subsection{Statistics}
%Crawford and JV

major additions to be discussed: lomb-scargle, sigma clipping, bayesian blocks, histograms

\section{Infrastructure for affiliated packages}
\subsubsection{Package template}
\subsection{Continuous integration helpers}
bsipocz should write this up
\subsection{sphinx extensions}
probably Tom R should write this up
\section{State of the Ecosystem}

\section{Tutorials, Snippets, Gallery}

\section{Outlook}
dropping python2 support, growths of affiliated packages
Summary

\acknowledgments

Who to thank?

%% Similar to \facility{}, there is the optional \software command to allow 
%% authors a place to specify which programs were used during the creation of 
%% the manusscript. Authors should list each code and include either a
%% citation or url to the code inside ()s when available.

\software{astropy \citep{2013A&A...558A..33A},  
          numpy, 
          scipy, 
          }

%\bibliographystyle{aasjournal}          
%\bibliography{bibliography}

\begin{thebibliography}{}

\end{thebibliography}

\end{document}

### 2017-09-20 main.tex
Update on Overleaf.

@@
 %\revised{September 27, 2016}
-\draft{\today}
+
 %% Command to document which AAS Journal the manuscript was submitted to.
@@
 
-\shorttitle{\aastex\ Astropy Project II}
+\shorttitle{Astropy Project II}
 \shortauthors{Astropy Project et al.}
@@
 \begin{document}
+
+\draft{\today}
 
@@
 
-Difficulty of reversing design choices
-Deciding if a feature should be included
-difficulty to decide where general use ends and "handy feature for some" starts, i.e. how to reject PRs or deal with maintenance burden
-
 \section{Major concepts}
@@
 \subsection{Accuracy testing across many different implementation}
+
+%\subsection{Difficulty of reversing design choices}
+%Deciding if a feature should be included
+%difficulty to decide where general use ends and "handy feature for some" starts, i.e. how to reject PRs or deal with maintenance burden
 
@@
 \subsubsection{Package template}
+bsipocz may write this up tif there is no other takers
 \subsection{Continuous integration helpers}
@@
 
-%\bibliographystyle{aasjournal}          
-%\bibliography{bibliography}
+\bibliographystyle{aasjournal}          
+\bibliography{bibliography}
 

### 2017-09-20 main.tex
Update on Overleaf.
added cite

@@
 \subsection{Convolution}
-Astropy implements `normalized convolution' (e.g., Knutsson and Westin 1993; http://ieeexplore.ieee.org/abstract/document/341081/), which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.
+Astropy implements `normalized convolution' \citep[e.g.][]{Knutsson1993}, which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.
 In version $<=1.3$, the direct convolution and fft convolution approaches were not consistent, with fft convolution implementing normalized convolution and direct convolution implementing a different approach.

### 2017-09-20 main.tex
Update on Overleaf.

@@
 \subsection{Convolution}
-Astropy implements `normalized convolution' \citep[e.g.][]{Knutsson1993}, which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.
+Astropy implements `normalized convolution' \citep[e.g.,][]{Knutsson1993}, which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.
 In version $<=1.3$, the direct convolution and fft convolution approaches were not consistent, with fft convolution implementing normalized convolution and direct convolution implementing a different approach.
@@
 \subsubsection{Package template}
-bsipocz may write this up tif there is no other takers
+bsipocz may write this up if there is no other takers
 \subsection{Continuous integration helpers}

### 2017-09-20 main.tex
Update on Overleaf.
cite

@@
 Two aspects of this (time and coordinate transformations) are already discussed in great detail in section 3.
-In this section, we highlight other features introduced or substantially improved since version v0.2, which is described in Astropy Collaboration et al.
-(2013).
+In this section, we highlight other features introduced or substantially improved since version v0.2, which is described in \citet{2013A&A...558A..33A}.
 (ordered in the order in which they appear in the astropy documentation)

### 2017-09-20 main.tex
Update on Overleaf.
add outline

--- 2017-09-20 main.tex
@@
 %\revised{September 27, 2016}
-
+\draft{\today}
 %% Command to document which AAS Journal the manuscript was submitted to.
@@
 
-\shorttitle{Astropy Project II}
+\shorttitle{\aastex\ Astropy Project II}
 \shortauthors{Astropy Project et al.}
@@
 \begin{document}
-
-\draft{\today}
 
@@
 
+Difficulty of reversing design choices
+Deciding if a feature should be included
+difficulty to decide where general use ends and "handy feature for some" starts, i.e. how to reject PRs or deal with maintenance burden
+
 \section{Major concepts}
@@
 \subsection{Accuracy testing across many different implementation}
-
-%\subsection{Difficulty of reversing design choices}
-%Deciding if a feature should be included
-%difficulty to decide where general use ends and "handy feature for some" starts, i.e. how to reject PRs or deal with maintenance burden
 
@@
 
+The \texttt{astropy.coordinates} subpackage ...
+
+- Three-tiered structure for coordinates: representation, frame, skycoord
+- With differential classes, frames support velocities
+- Celestial coordinates, and local coordinates (via EarthLocation + Time)
+- JPL ephemerids
+
 start with short description of the astropy approach and features (JPL ephemerids, barycentric correction, proper motions, coordinate frames) then shows the tests.
+
 In particular, we had a discussion on problems with the definition of some coordinate system on the mailing list.
@@
 \subsection{Convolution}
-Astropy implements `normalized convolution' \citep[e.g.,][]{Knutsson1993}, which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.
+Astropy implements `normalized convolution' (e.g., Knutsson and Westin 1993; http://ieeexplore.ieee.org/abstract/document/341081/), which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.
 In version $<=1.3$, the direct convolution and fft convolution approaches were not consistent, with fft convolution implementing normalized convolution and direct convolution implementing a different approach.
@@
 \subsubsection{Package template}
-bsipocz may write this up if there is no other takers
 \subsection{Continuous integration helpers}
@@
 
-\bibliographystyle{aasjournal}          
-\bibliography{bibliography}
+%\bibliographystyle{aasjournal}
+%\bibliography{bibliography}
 

### 2017-09-20 main.tex
fix merge conflict issue

--- 2017-09-20 main.tex
@@
 
-\section{Key features}
+\section{Astropy Core Package v2.0}
 
@@
 \subsection{Coordinates}
+% Adrian & Erik
+
+The \texttt{astropy.coordinates} subpackage ...
+
+- Three-tiered structure for coordinates: representation, frame, skycoord
+- With differential classes, frames support velocities
+- Celestial coordinates, and local coordinates (via EarthLocation + Time)
+- JPL ephemerids
 
 start with short description of the astropy approach and features (JPL ephemerids, barycentric correction, proper motions, coordinate frames) then shows the tests.
+
 In particular, we had a discussion on problems with the definition of some coordinate system on the mailing list.
@@
 \subsubsection{NDDdata}
+% Matt C., Michael, or Steve C.
 
 \subsubsection{Tables}
+% Tom A.
 QTable is new, mixin columns for time and coordinates. Table operations were added in v0.3

### 2017-09-20 main.tex
Update on Overleaf.
first stab at abstract

@@
 \begin{abstract}
-
-Astropy is amazing. and even more amazing than before
-
+The Astropy project supports and fosters the development of open-source Python
+packages that provide commonly-needed functionality to the astronomical
+community.
+A key element of the project is the Astropy core package, which serves as the
+foundation for more specialized projects and packages.
+In this article, we provide an overview of the organization of the Astropy
+project and summarize key features in the core package as of the recent major
+release, version 2.0.
+We then describe the project infrastructure designed to facilitate [...]
+We conclude with a future outlook of planned new features and directions for the
+broader Astropy ecosystem.
 \end{abstract}
@@
 
-The \texttt{astropy.coordinates} subpackage ...
+The \texttt{astropy.coordinates} subpackage is designed to support
 
@@
 - With differential classes, frames support velocities
+
+Accuracy and comparison of coordinate system definitions?
+
+\subsubsection{Key features}
+
 - Celestial coordinates, and local coordinates (via EarthLocation + Time)
 - JPL ephemerids
-
-start with short description of the astropy approach and features (JPL ephemerids, barycentric correction, proper motions, coordinate frames) then shows the tests.
-
-In particular, we had a discussion on problems with the definition of some coordinate system on the mailing list.
-Getting that discussion in here gives us a refereed paper to point to when we need to push the IAU to fix that.
 

### 2017-09-20 main.tex
Update on Overleaf.

@@
 
-%% Reintroduced the \received and \accepted commands from AASTeX v5.2
-%\received{July 1, 2016}
-%\revised{September 27, 2016}
-
-%% Command to document which AAS Journal the manuscript was submitted to.
-%% Adds "Submitted to " the arguement.
 \submitjournal{ApJ}
-
-%% Mark up commands to limit the number of authors on the front page.
-%% Note that in AASTeX v6.1 a \collaboration call (see below) counts as
-%% an author in this case.
-%
-%\AuthorCollaborationLimit=3
-%
 
@@
 
-\title{Astropy - New software standards for a growing community}
+\title{The Astropy Project: }
 
-%%
-%% The \author command is the same as before except it now takes an optional
-%% arguement which is the 16 digit ORCID. The syntax is:
-%% \author[xxxx-xxxx-xxxx-xxxx]{Author Name}
-%%
-%% This will hyperlink the author name to the author's ORCID page. Note that
-%% during compilation, LaTeX will do some limited checking of the format of
-%% the ID to make sure it is valid.
-%%
-%%
-%% The new \altaffiliation can be used to indicate some secondary information
-%% such as fellowships. This command produces a non-numeric footnote that is
-%% set away from the numeric \affiliation footnotes.  NOTE that if an
-%% \altaffiliation command is used it must come BEFORE the \affiliation call,
-%% right after the \author command, in order to place the footnotes in
-%% the proper location.
-%%
-%% Use \email to set provide email addresses. Each \email will appear on its
-%% own line so you can put multiple email address in one \email call. A new
-%% \correspondingauthor command is available in V6.1 to identify the
-%% corresponding author of the manuscript. It is the author's responsibility
-%% to make sure this name is also in the author list.
-%%
-%% While authors can be grouped inside the same \author and \affiliation
-%% commands it is better to have a single author for each. This allows for
-%% one to exploit all the new benefits and should make book-keeping easier.
-%%
-%% If done correctly the peer review system will be able to
-%% automatically put the author and affiliation information from the manuscript
-%% and save the corresponding author the trouble of entering it by hand.
-
-\correspondingauthor{Astropy Coordinating committee or First Author}
+\correspondingauthor{Astropy coordination committee}
 \email{coordinators@astropy.org}
 
-\author{Astropy Project}
+\author{Astropy Collaboration}
 
@@
 \subsection{Accuracy testing across many different implementation}
+\subsection{Use of Quantities across package}
 
@@
 
+% \subsection{Analytic Functions}
+
 \subsection{Constants}
+% David S.
 versioning
@@
 
-\subsubsection{Key features}
+\textbf{Key features}
 
-- Celestial coordinates, and local coordinates (via EarthLocation + Time)
-- JPL ephemerids
+\begin{itemize}
+	\item Celestial coordinates, and local coordinates (via EarthLocation + Time)
+	\item JPL ephemerids
+\end{itemize}
 
 \subsection{Units and quantities}
+% Marten, Adrian
 
@@
 \subsection{Convolution}
+% Adam G.
+
 Astropy implements `normalized convolution' \citep[e.g.,][]{Knutsson1993}, which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.
@@
 \subsection{Modeling}
+% Nadia
+
 The whole modeling submodule was missing from the previous paper, so everything really, including compound models, unit support etc.
@@
 
-\section{Tutorials, Snippets, Gallery}
+\section{Learning Astropy}
+% Kelle & Adrian?
 
-\section{Outlook}
+Explain components: Documentation, Example gallery, Tutorials and lessons
+
+\section{The future of the Astropy project}
+
 dropping python2 support, growths of affiliated packages

### 2017-09-20 main.tex
Update on Overleaf.

@@
 \keywords{}
+
+\section{Notes and guidelines (to be removed)}
+
+\begin{itemize}
+	\item Right now, we don't foresee needing to include code in this paper.
+But, if you think you will need to include code in your section, please add it to a separate Python module (.py file) and include it in this repository.
+\end{itemize}
 
@@
 \subsection{Visualization}
+% Larry, Tom R.
+
 wcsaxis, rgb, histograms comes to mind.Can use more publicity and also makes good images to include in the paper.
@@
 \subsection{Statistics}
-%Crawford and JV
+% Steve C. and Jake V.
 

### 2017-09-20 main.tex
Update on Overleaf.

@@
 \documentclass[modern]{aastex61}
+
+\newcommand{\escapecmd}[1]{\texttt{\detokenize{#1}}}
 
@@
 
-\section{Notes and guidelines (to be removed)}
+\section*{Notes and guidelines (\textit{to be removed})}
 
 \begin{itemize}
-	\item Right now, we don't foresee needing to include code in this paper.
-But, if you think you will need to include code in your section, please add it to a separate Python module (.py file) and include it in this repository.
+	\item We don't plan on including code in this paper, but if you think you will need to include code in your section, please add it to a separate Python module (.py file) and include it in this repository.
+    \item Use \escapecmd{\sectionname} not Section, \escapecmd{\figname} not Figure, \escapecmd{\documentname} not Article
 \end{itemize}
@@
 \section{Introduction} \label{sec:intro}
-
-Moritz volunteered to write the intro
+% Moritz (first draft)
 
 \section{Major concepts}
+
 \subsection{Astropy development model, astropy ecosystem}
 This subsection should include some basic statistics about the contributors, commits, line of code etc. up to the 2.0 release when we know it.
+
 \subsection{Mixin}
+
 \subsection{Accuracy testing across many different implementation}
+
 \subsection{Use of Quantities across package}
@@
 
-\textbf{Key features}
-
+\textbf{Key features:}
 \begin{itemize}
@@
 
-incl logarithmic units and magnitudes
-speed improvements,
-interaction with numpy arrays
+\textbf{Key features:}
+\begin{itemize}
+	\item incl logarithmic units and magnitudes
+	\item speed improvements
+    \item interaction with numpy arrays
+\end{itemize}
 

### 2017-09-21 main.tex
Update on Overleaf.

@@
 
-\section*{Notes and guidelines (\textit{to be removed})}
+\section*{\textit{Notes and guidelines (to be removed)}}
 
@@
 	\item We don't plan on including code in this paper, but if you think you will need to include code in your section, please add it to a separate Python module (.py file) and include it in this repository.
-    \item Use \escapecmd{\sectionname} not Section, \escapecmd{\figname} not Figure, \escapecmd{\documentname} not Article
+    \item Use \escapecmd{\sectionname} not ``Section,'' \escapecmd{\figurename} not ``Figure''
 \end{itemize}
@@
 \section{Major concepts}
+% Anyone want to take this??
 
@@
 \subsection{Coordinates}
-% Adrian & Erik
+% Adrian, Erik
 
-The \texttt{astropy.coordinates} subpackage is designed to support
+The \texttt{astropy.coordinates} subpackage is designed to support representing and transforming celestial coordinates and velocities.
 
@@
 \subsection{Statistics}
-% Steve C. and Jake V.
+% Steve C., Jake V.
 
@@
 \section{Learning Astropy}
-% Kelle & Adrian?
+% Kelle, Adrian
 

### 2017-09-21 main.tex
whitespace
Update on Overleaf.

@@
 \begin{itemize}
+   \item The goal is to produce a brief and informative paper that covers major astropy principles not mentioned in the first paper, the core v2.0 package, and infrastructure in astropy project to support development in python.
 	\item We don't plan on including code in this paper, but if you think you will need to include code in your section, please add it to a separate Python module (.py file) and include it in this repository.
     \item Use \escapecmd{\sectionname} not ``Section,'' \escapecmd{\figurename} not ``Figure''
+    \item If your subpackage was included in Paper I, then please just include a note on what the package does, a reference to paper I, and any new major updates to your package
+    \item If your subpackage was not included, then please a further description of the sub-package on level with what was in the first paper, and highlight any major features in it.
+Typically length should be equivalent to one column
+
 \end{itemize}
@@
 \subsection{Use of Quantities across package}
+% Marten and Tom R.
+
+{\bf Very rough first text!}
+
+Historically, it has been unusual to keep units as part of numbers, especially as speed was often deemed essential and quantities used to be slower than regular arrays.
+Hence, programs and functions expected to be fed parameters in particular units, as (hopefully) stated in their documentation.
+In astropy 0.4, therefore, unit and quantity support was still somewhat spotty, but this has changed greatly.
+One of the riskiest classes was ngles, where both degrees and radians were ``obvious'' default units to some.
+As a consequence, quantities are most fully integrated in the coordinates module (Sect.~\ref{sec:coordinates}).
+In astropy 2.0, one can also opt in to use quantities fully in tables, by using the {\tt QTable} class (see Sect.~\ref{sec:table}).
+As a result, units in fits tables are also well-supported.
+For most other modules, quantities are at least accepted, and often assumed by default.
+
+In the process, some standard wrappers have been defined that make defining functions that require quantities as input simpler.
+As an extension of this, we plan to define wrappers for functions that work on numbers that will automatically convert quantities to any required units.
+
+\subsection{Long term support of v2.0}
+% This could also include information about the development cycle
 
@@
 % \subsection{Analytic Functions}
+% moved to models and depreciated -- 
+% just here for completeness at the moment
+
+\subsection{Units and quantities}
+\label{sec:units}
+% Marten, Adrian
+
+\textbf{Key features:}
+\begin{itemize}
+	\item incl logarithmic units and magnitudes
+	\item speed improvements
+    \item interaction with numpy arrays
+\end{itemize}
 
@@
 \subsection{Coordinates}
+\label{sec:coordinates}
 % Adrian, Erik
 
-The \texttt{astropy.coordinates} subpackage is designed to support representing and transforming celestial coordinates and velocities.
+The \texttt{astropy.coordinates} subpackage is designed to support representing
+and transforming celestial coordinates and velocities.
 
@@
 	\item JPL ephemerids
+    \item Proper motions, radial velocities
 \end{itemize}
 
-\subsection{Units and quantities}
-% Marten, Adrian
+Separately, talk about representations as vectors? (MHvK)
 
-\textbf{Key features:}
-\begin{itemize}
-	\item incl logarithmic units and magnitudes
-	\item speed improvements
-    \item interaction with numpy arrays
-\end{itemize}
+\subsection{Time}
+\label{sec:time}
+
+Q: does it make sense to refer forward to fits support, even though it is 3.0?
 
@@
 % Matt C., Michael, or Steve C.
+% Larry (nddata.utils)
+NOTE (Larry), The package is nddata, which includes the NDData object.  Don't forget the nddata.utils functionality (e.g. Cutout2D, block\_reduce, etc.).
 
 \subsubsection{Tables}
+\label{sec:table}
 % Tom A.
 QTable is new, mixin columns for time and coordinates. Table operations were added in v0.3
+
+\subsection{io}
+% Simon
+
+\subsection{Modeling}
+\label{sec:modeling}
+% Nadia
+% Lim blackbody
+% Tom R. -- unit support
+The whole modeling submodule was missing from the previous paper, so everything really, including compound models, unit support etc.
 
@@
 
-\subsection{Modeling}
-% Nadia
-
-The whole modeling submodule was missing from the previous paper, so everything really, including compound models, unit support etc.
-
 \subsection{Visualization}
-% Larry, Tom R.
+% Larry:  Image visualization (stretching, scaling), RGB
+% Tom R.:  WCSAxes
 
@@
 
+%\subsection{Utils}
+% Lim
+
+\subsection{Cosmology}
+
 \subsection{Statistics}
-% Steve C., Jake V.
-
-major additions to be discussed: lomb-scargle, sigma clipping, bayesian blocks, histograms
+% Steve C.
+% Jake V.:  Lomb-scargle, Bayesian blocks
+% Larry:  sigma clipping, biweight stats
+major additions to be discussed: lomb-scargle, sigma clipping, bayesian blocks, histograms, also:  robust (biweight) statistics
 
@@
 probably Tom R should write this up
-\section{State of the Ecosystem}
+
+% \section{State of the Ecosystem}
+% Commenting out unless a clear statement is added
 
@@
 
-Who to thank?
+Who to thank?  numfocus,
 
@@
 
-%\bibliographystyle{aasjournal}
-%\bibliography{bibliography}
+\bibliographystyle{aasjournal}
+\bibliography{bibliography}
 

### 2017-09-22 main.tex
Update on Overleaf.

@@
 
-\correspondingauthor{Astropy coordination committee}
+\correspondingauthor{Astropy Coordination Committee}
 \email{coordinators@astropy.org}
@@
 Typically length should be equivalent to one column
+    \item Please make sure you are logged into Overleaf or pushing a commit with your information to be able to track the contributors to the paper.
 
@@
 
+\subsection{Coordination of Astropy}
+% Kelle
+
 \subsection{Astropy development model, astropy ecosystem}
+% Erik 
 This subsection should include some basic statistics about the contributors, commits, line of code etc. up to the 2.0 release when we know it.
@@
 % Larry (nddata.utils)
-NOTE (Larry), The package is nddata, which includes the NDData object.  Don't forget the nddata.utils functionality (e.g. Cutout2D, block\_reduce, etc.).
+%NOTE (Larry), The package is nddata, which includes the NDData object.  %Don't forget the nddata.utils functionality (e.g. Cutout2D, block\_reduce, %etc.).
 

### 2017-09-23 main.tex
Update on Overleaf.
Adding text about release cycle and versioning

@@
 
-\subsection{Long term support of v2.0}
+\subsection{Release cycle and Long Term Support}
 % This could also include information about the development cycle
+% Brigitta can writes this up if there's no other taker
+%
+% - reference APE2 for versioning and APE10 for dropping python2 support
+% - shall we maybe refer to the release calendar, too?
+% - should we mention that v3.0 is the exception to the version numbering
+%   scheme we use by not being 2.1?
+\par The general scheme for the releases and version numbering that the core
+package has adopted if the following. Astropy has new feature releases every
+6 month, and between feature releases additional bugfix releases that
+contain only bugfixes but no new features. The timing of
+%
+\par Long-term support (LTS) releases continue to receive bugfixes for 2
+years with no changes to the API. They are ideal for pipelines and other
+applications where API stability is essential. The latest LTS release is
+also the last one that supports Python2, and will receive bug fixes until the
+end of 2019.
+%
+\par The version numbering of astropy reflects on the release scheme
+described above. The core package uses the form x.y.z, where x is advances
+on LTS, y is advanced for a non-LTS feature release, and z is advanced on
+bugfix releases.
 
@@
 \subsubsection{Package template}
-bsipocz may write this up if there is no other takers
+% Brigitta may write this up if there is no other takers
 \subsection{Continuous integration helpers}
-bsipocz should write this up
+% Brigitta
 \subsection{sphinx extensions}
-probably Tom R should write this up
+% Tom R
 

### 2017-09-23 main.tex
Adding infrastructure text: ci-helpers and package-template

@@
 \section{Infrastructure for affiliated packages}
+% - should we use links to the appropriate github repo?
+%
+\par In addition to astronomy related packages and libraries, the Astropy
+Project also contains and supports several infrastructure package that are
+very generic. The following sections describes the most widely used
+selection of them.
+%
 \subsubsection{Package template}
 % Brigitta may write this up if there is no other takers
+\par Astropy provides a template package that any Python package is welcome to
+use (many affiliated packages do so). The template contains a ready-to-go
+package layout. It provides infrastructure such as documentation tools,
+testing framework and CI templates and configurations, Cython integration,
+and documentation on how to make it all work.
+%
 \subsection{Continuous integration helpers}
 % Brigitta
+\texttt{ci-helpers} is a collection of scripts that empowers package
+maintainers to control their testing set up and installation process for
+various continuous integration services via a set of environment
+variables. While the current development is mostly driven by the needs of
+the astropy ecosystem, the actual usage of this package is extremely
+widespread. Currently we support setups for TravisCI and AppveyorCI.
+%
 \subsection{sphinx extensions}

### 2017-09-23 main.tex
adding section headings for APEs and concept of affiliated packages

@@
 % Anyone want to take this??
+\subsection{APEs - Astropy Proposals for Enhancement}
+% would be nice to write about the concept of APEs so we can refer to the
+% relevant ones latr in the text
 
@@
 This subsection should include some basic statistics about the contributors, commits, line of code etc. up to the 2.0 release when we know it.
+
+\subsection{Concept of affiliated packages}
+% it may be described in previous subsection, if not the Brigitta can try to
+% write it up
 
@@
 
-Astropy implements `normalized convolution' \citep[e.g.,][]{Knutsson1993}, which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.
+astropy implements `normalized convolution' \citep[e.g.,][]{Knutsson1993}, which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.
 In version $<=1.3$, the direct convolution and fft convolution approaches were not consistent, with fft convolution implementing normalized convolution and direct convolution implementing a different approach.

### 2017-09-23 main.tex
Update on Overleaf.
draft of introduction

@@
     \item Use \escapecmd{\sectionname} not ``Section,'' \escapecmd{\figurename} not ``Figure''
+    % I have never seen the \sectionname command and google is not any cleverer
+    % Also, compilation fails when I use that. What's it good for?
     \item If your subpackage was included in Paper I, then please just include a note on what the package does, a reference to paper I, and any new major updates to your package
@@
 \section{Introduction} \label{sec:intro}
-% Moritz (first draft)
+% first draft by Moritz (hamogu)
+All astronomical research makes use of software in some way and
+astronomy as a field has long supported the development of specialized
+software tools for different astronomical tasks. Some of those
+software packages are (or at least were) supported by large
+institutions, e.g.\ IRAF \citep[developed at NAOA,][]{IRAF}, MIDAS
+\citep[developed at ESO,][]{MIDAS}, or ds9 \citep[developed at
+  SAO,][]{ds9}. These packages tend to address a wide range of users
+and they typically provide some level of documentation and user
+support. Other packages are developed foremost by individual research
+groups and used mostly in work by members of this group. Those
+packages can address more specialized needs, but are not necessarily
+available to the community and even if they are, documentation can in
+some cases be insufficient for new users and the quality of the
+software, i.e. the robustness and the level of testing that has been
+performed to ensure correctness, is not always clear. On the other
+hand, there are also many widely used, well documented, high quality
+software packages which are developed by individuals or small groups.
+
+The implementation of astronomical software, be it for a package meant
+for wide distribution or scripts and programs for a specific research
+project, can be eased by the use of a library that provides core
+functionality that is common to many astronomical tasks. Reading and
+writing fits files is one example where it is time
+consuming to implement the fits standard correctly and
+programming is much faster when using an existing library perform this
+task. Another example of such a common task is dealing with different
+astronomical coordinate systems. The astropy project aims to provide a
+library of core astronomical functionality in the Python programming
+language.
+
+Python\footnote{\url{https://www.python.org/}} is an increasingly
+popular general-purpose scripting language that is available under a
+permissive open source software licence free of charge for all major
+operating systems. Stable and well-developed packages provide support
+for array arithmetic \citep[numpy,][]{numpy}, a wide variety of
+functions for scientific computing \citep[scipy,][]{numpy}, and
+publication-quality plotting \citep[matplotlib,][]{matplotlib}. Tens of
+thousands of other packages are available which can help with tasks
+that are not astronomy specific but might be performed in the course
+of astronomical research, e.g.\ presenting results on websites or
+interfacing with databases.
+
+At the same time, an ecosystem of tools, programms, and webservices
+has become available that makes it easier to collaborate on code development,
+continuously test the code, build and provide documentation, and
+supply downloadable packages. The astropy project aims to develop and
+provide high quality code and documentation according to the best
+practices in software development. The project makes use of these
+tools to do so without central institutional oversight.
+
+The first public release of the astropy package is described in
+\cite{2013A&A...558A..33A}. Since then, the astropy package has been
+used in hundreds of projects, and the scope of the package as grown
+considerably. At the same time, the community of astronomers
+contributing to the project has grown tremendeously and an ecosystem
+of packages supporting or affiliated with the astropy core has
+developed. In this paper, we describe the current status of the
+astropy community, the astropy core package, and the astropy
+ecosystem.
+
+We start by describing the way the astropy project works and is
+organized in section~\ref{sec:concepts}.  The project develops a core
+package called \texttt{astropy} (section~\ref{sec:core}) and several
+separate packages that help setting up the infrastructure for testing,
+documentation etc.\ (section~\ref{sec:infrastructure}). In
+section~\ref{sec:learning} we give an overview of the wealth of
+recources created to teach new users the use of the astropy packages
+and how to contribute to the community. We end with a short vision for
+the future of astropy in section~\ref{sec:future}.
 
 \section{Major concepts}
+\label{sec:concepts}
 % Anyone want to take this??
@@
 \section{Astropy Core Package v2.0}
-
+\label{sec:core}
 The astropy project aims to provide python-based packages for all tasks that are commonly needed in a large subset of the astronomical community.
@@
 \section{Infrastructure for affiliated packages}
+\label{sec:infrastructure}
 % - should we use links to the appropriate github repo?
@@
 \section{Learning Astropy}
+\label{sec:learning}
 % Kelle, Adrian
@@
 \section{The future of the Astropy project}
+\label{sec:future}
 

### 2017-09-28 main.tex
Update on Overleaf.

@@
 software packages are (or at least were) supported by large
-institutions, e.g.\ IRAF \citep[developed at NAOA,][]{IRAF}, MIDAS
+institutions, e.g.\ IRAF \citep[developed at NOAO,][]{IRAF}, MIDAS
 \citep[developed at ESO,][]{MIDAS}, or ds9 \citep[developed at
+% * <bsipocz@gmail.com> 2017-09-28T21:05:00.569Z:
+% 
+% > or ds9 
+% probably starlink is a better example as being a large package of software similarly to IRAF and MIDAS rather than a single tool.
+% 
+% ^.
   SAO,][]{ds9}. These packages tend to address a wide range of users
@@
 
-At the same time, an ecosystem of tools, programms, and webservices
+At the same time, an ecosystem of tools, programs, and webservices
 has become available that makes it easier to collaborate on code development,
@@
 considerably. At the same time, the community of astronomers
-contributing to the project has grown tremendeously and an ecosystem
+contributing to the project has grown tremendously and an ecosystem
 of packages supporting or affiliated with the astropy core has
@@
 section~\ref{sec:learning} we give an overview of the wealth of
-recources created to teach new users the use of the astropy packages
+resources created to teach new users the use of the astropy packages
 and how to contribute to the community. We end with a short vision for
@@
 
+\subsubsection{Unified file read/write interface}
+
+Check when it was added (0.3?). Overview of the supported formats (ascii, fits, votable).
+
+\subsubsection{Enhanced CSV format}
+
+\subsubsection{ASCII, FITS, etc.}
+
+One subsection per format (if enough new features) ?
+
+\begin{itemize}
+\item ascii : fast reader/writer (1.0), HTML tables
+\item fits: lazy loading, command-line scripts (fitsheader, fitsinfo)
+\end{itemize}
+
 \subsection{Modeling}
@@
 \subsection{Statistics}
-% Steve C.
+% Steve C.: overview, circular stats, 
 % Jake V.:  Lomb-scargle, Bayesian blocks
 % Larry:  sigma clipping, biweight stats
+% Ze':  Ripley's K (spatial stats)
 major additions to be discussed: lomb-scargle, sigma clipping, bayesian blocks, histograms, also:  robust (biweight) statistics
+
+\subsection{Robust Statistical Estimators}
+\subsection{Circular Statistics}
+\subsection{Lomb-Scargle Periodograms}
+\subsection{Ripley's K Function Estimators}
+\subsection{Histogram Binning}
 
@@
 % Kelle, Adrian
+% - would astropy learn mature enough to described in the paper, or maybe it should go as a subsection for the next, future of astropy section?
 

### 2017-09-29 main.tex
Update on Overleaf.
coordinates

@@
 The \texttt{astropy.coordinates} subpackage is designed to support representing
-and transforming celestial coordinates and velocities.
+and transforming celestial coordinates and, new in version 2.0, velocities.
+A key concept behind the design of this subpackage is that coordinate
+\textit{representations} and \textit{reference systems / frames} are independent
+of one another.
+For example, a set of coordinates in the International Celestial Reference
+System (ICRS) reference frame could be represented as a spherical (distance,
+right ascension, declination) or Cartesian coordinates.
+They can therefore be re-represented or transformed to other reference frames
+(e.g., the Galactic frame) in an independent way.
 

### 2017-09-29 main.tex
add word new

@@
 
-\textbf{Key features:}
+\textbf{Key new features:}
 \begin{itemize}
@@
 
-- Three-tiered structure for coordinates: representation, frame, skycoord
+The classes that handle coordinate representations (the \texttt{Representation}
+classes) act like three-dimensional vectors and thus support vector arithmetic.
+
 - With differential classes, frames support velocities

### 2017-09-29 main.tex
more about class hierarchy

@@
 classes) act like three-dimensional vectors and thus support vector arithmetic.
+The classes that represent reference systems and frames (the \texttt{Frame}
+classes) internally use \texttt{Representation} objects to store the coordinate
+data---that is, the \texttt{Frame} classes accept coordinate data, either as a
+specified \texttt{Representation} object, or using short-hand keyword arguments
+to specify the components of the coordinates.
+Many of the \texttt{Frame} classes also have attributes specific to the
+corresponding reference system that allow the user to specify the frame.
+For example, the Fifth Fundamental Catalogue (FK5) reference system requires
+specifying an equinox to determine the reference frame.
 

### 2017-09-29 main.tex
component names

@@
 to specify the components of the coordinates.
+These preferred representation and short-hand component names differ between
+various astronomical reference systems.
+For example, in the ICRS frame, longitude and latitude are right ascension
+(\texttt{ra}) and declination ((\texttt{dec})), whereas in the Galactic frame,
+the spherical angles are Galactic longitude (\texttt{l}) and latitude
+(\texttt{b}).
+Each of the \texttt{Frame} classes define their own component names and
+preferred \texttt{Representation} class.
+The frame-specific component names map to corresponding components on the
+underlying \texttt{Representation} object that interally stores the coordinate
+data.
+For most frames the preferred representation is spherical.
+
 Many of the \texttt{Frame} classes also have attributes specific to the
@@
 
-- With differential classes, frames support velocities
+todo: The typical user doesn't have to interact with the frame classes or
+representation classes directly.
+Instead, use the \texttt{SkyCoord} object...
 
@@
 	\item Celestial coordinates, and local coordinates (via EarthLocation + Time)
+    \item differential classes
+    \item Proper motions, radial velocities
     \item JPL ephemerids
-    \item Proper motions, radial velocities
 \end{itemize}

### 2017-09-29 main.tex
re-wrap

--- 2017-09-29 main.tex
@@
 to specify the components of the coordinates.
+These preferred representation and short-hand component names differ between
+various astronomical reference systems.
+For example, in the ICRS frame, longitude and latitude are right ascension
+(\texttt{ra}) and declination (\texttt{dec}), whereas in the Galactic frame, the
+spherical angles are Galactic longitude (\texttt{l}) and latitude (\texttt{b}).
+Each of the \texttt{Frame} classes define their own component names and
+preferred \texttt{Representation} class.
+The frame-specific component names map to corresponding components on the
+underlying \texttt{Representation} object that internally stores the coordinate
+data.
+For most frames the preferred representation is spherical.
+
 Many of the \texttt{Frame} classes also have attributes specific to the
@@
 specifying an equinox to determine the reference frame.
+If required, these additional frame attributes must be specified along with the
+coordinate data when a \texttt{Frame} object is created.
 
-- With differential classes, frames support velocities
+With all of that in mind, the typical user doesn't usually have to interact with
+the \texttt{Frame} or \texttt{Representation} classes directly.
+
+Instead, use the \texttt{SkyCoord} object...
 

### 2017-09-29 main.tex
quantities
skycoord

@@
 and transforming celestial coordinates and, new in version 2.0, velocities.
+The framework heavily relies on the \texttt{astropy.units} subpackage, and most
+inputs to objects in this subpackage are expected to be \texttt{Quantity}
+objects.
 A key concept behind the design of this subpackage is that coordinate
@@
 
-With all of that in mind, the typical user doesn't usually have to interact with
-the \texttt{Frame} or \texttt{Representation} classes directly.
-
-Instead, use the \texttt{SkyCoord} object...
+The typical user doesn't usually have to interact with the \texttt{Frame} or
+\texttt{Representation} classes directly.
+Instead, \texttt{astropy.coordinates} provides a high-level interface to
+representing astronomical coordinates through the \texttt{SkyCoord} class.
+The \texttt{SkyCoord} class was designed to provide a single, go-to class that
+accepts a wide range of possible inputs, and supports coordinate data in any
+reference frame with a corresponding \texttt{Frame} class in any representation
+with a corresponding \texttt{Representation} class.
 

### 2017-09-29 main.tex
accuracy subsection
new features

@@
 
-Accuracy and comparison of coordinate system definitions?
-
 \textbf{Key new features:}
 \begin{itemize}
-	\item Celestial coordinates, and local coordinates (via EarthLocation + Time)
+	\item Celestial coordinates, but now also local coordinates (via EarthLocation + Time)
     \item differential classes
@@
 
-Separately, talk about representations as vectors? (MHvK)
+\subsubsection{Accuracy and comparison of coordinate system definitions?}
+% Erik?
 

### 2017-09-29 main.tex
add todos
expand todos in coordinates

@@
 \begin{itemize}
-	\item Celestial coordinates, but now also local coordinates (via EarthLocation + Time)
-    \item differential classes
-    \item Proper motions, radial velocities
-    \item JPL ephemerids
+    \item TODO: Celestial coordinates, but now also local coordinates (via
+    EarthLocation + Time). Now supports Alt-Az coordinates, observation planning
+    - shoutout to astroplan
+    \item TODO: differential classes. Represent single-derivatives of
+    representations. Used to store velocity information, only really useful
+    attached to a representation object.
+    \item TODO: Frame classes support proper motions, radial velocities. Explain
+    component naming, why SkyCoord doesn't support right now, "experimental" but
+    tested feature.
+    \item TODO: JPL ephemerids % Who can write this? Erik?
 \end{itemize}

### 2017-09-29 main.tex
tweaks
note about abs

@@
 \begin{abstract}
+% I (Adrian) took a first stab at the abstract, but it needs some work. Feel
+% free to modify!
 The Astropy project supports and fosters the development of open-source Python
@@
 One of the riskiest classes was ngles, where both degrees and radians were ``obvious'' default units to some.
-As a consequence, quantities are most fully integrated in the coordinates module (Sect.~\ref{sec:coordinates}).
-In astropy 2.0, one can also opt in to use quantities fully in tables, by using the {\tt QTable} class (see Sect.~\ref{sec:table}).
+As a consequence, quantities are most fully integrated in the coordinates module (\sectionname~\ref{sec:coordinates}).
+In astropy 2.0, one can also opt in to use quantities fully in tables, by using the {\tt QTable} class (see \sectionname~\ref{sec:table}).
 As a result, units in fits tables are also well-supported.
@@
 
-\subsubsection{Accuracy and comparison of coordinate system definitions?}
+\subsubsection{Accuracy and comparison of coordinate system definitions}
 % Erik?
@@
 
-Explain components: Documentation, Example gallery, Tutorials and lessons
+Explain components: Documentation, Tutorials, and lessons
 

### 2017-09-29 main.tex
add makefile to build paper
went a little crazy with commands

@@
 \shortauthors{Astropy Project et al.}
+
+% Packages / projects / programming - for consistency!
+\newcommand{\package}[1]{\texttt{#1}}
+\newcommand{\github}{\package{GitHub}}
+\newcommand{\python}{\package{Python}}
+\newcommand{\astropy}{\package{Astropy}}
+
+% For consistency:
+\newcommand{\sectionname}{Section}
+\renewcommand{\figurename}{Figure}
+\newcommand{\equationname}{Equation}
+\renewcommand{\tablename}{Table}
+
+\include{gitstuff}
 
@@
 % free to modify!
-The Astropy project supports and fosters the development of open-source Python
+The \astropy\ project supports and fosters the development of open-source Python
 packages that provide commonly-needed functionality to the astronomical
 community.
-A key element of the project is the Astropy core package, which serves as the
+A key element of the project is the \astropy\ core package, which serves as the
 foundation for more specialized projects and packages.
-In this article, we provide an overview of the organization of the Astropy
+In this article, we provide an overview of the organization of the \astropy\
 project and summarize key features in the core package as of the recent major
@@
 We conclude with a future outlook of planned new features and directions for the
-broader Astropy ecosystem.
+broader \astropy\ ecosystem.
 \end{abstract}
@@
 \begin{itemize}
-   \item The goal is to produce a brief and informative paper that covers major astropy principles not mentioned in the first paper, the core v2.0 package, and infrastructure in astropy project to support development in python.
+   \item The goal is to produce a brief and informative paper that covers major \astropy\ principles not mentioned in the first paper, the core v2.0 package, and infrastructure in \astropy\ project to support development in \python.
 	\item We don't plan on including code in this paper, but if you think you will need to include code in your section, please add it to a separate Python module (.py file) and include it in this repository.
     \item Use \escapecmd{\sectionname} not ``Section,'' \escapecmd{\figurename} not ``Figure''
-    % I have never seen the \sectionname command and google is not any cleverer
-    % Also, compilation fails when I use that. What's it good for?
+    \item Use \escapecmd{\astropy} not ``astropy'', \escapecmd{\python} not ``Python''
     \item If your subpackage was included in Paper I, then please just include a note on what the package does, a reference to paper I, and any new major updates to your package
@@
 task. Another example of such a common task is dealing with different
-astronomical coordinate systems. The astropy project aims to provide a
+astronomical coordinate systems. The \astropy\ project aims to provide a
 library of core astronomical functionality in the Python programming
@@
 
-Python\footnote{\url{https://www.python.org/}} is an increasingly
+\python\footnote{\url{https://www.python.org/}} is an increasingly
 popular general-purpose scripting language that is available under a
@@
 continuously test the code, build and provide documentation, and
-supply downloadable packages. The astropy project aims to develop and
+supply downloadable packages. The \astropy\ project aims to develop and
 provide high quality code and documentation according to the best
@@
 
-The first public release of the astropy package is described in
-\cite{2013A&A...558A..33A}. Since then, the astropy package has been
+The first public release of the \astropy\ package is described in
+\cite{2013A&A...558A..33A}. Since then, the \astropy\ package has been
 used in hundreds of projects, and the scope of the package as grown
@@
 contributing to the project has grown tremendously and an ecosystem
-of packages supporting or affiliated with the astropy core has
+of packages supporting or affiliated with the \astropy\ core has
 developed. In this paper, we describe the current status of the
-astropy community, the astropy core package, and the astropy
+\astropy\ community, the \astropy\ core package, and the \astropy\
 ecosystem.
 
-We start by describing the way the astropy project works and is
+We start by describing the way the \astropy\ project works and is
 organized in section~\ref{sec:concepts}.  The project develops a core
@@
 section~\ref{sec:learning} we give an overview of the wealth of
-resources created to teach new users the use of the astropy packages
+resources created to teach new users the use of the \astropy\ packages
 and how to contribute to the community. We end with a short vision for
-the future of astropy in section~\ref{sec:future}.
+the future of \astropy\ in section~\ref{sec:future}.
 
@@
 Hence, programs and functions expected to be fed parameters in particular units, as (hopefully) stated in their documentation.
-In astropy 0.4, therefore, unit and quantity support was still somewhat spotty, but this has changed greatly.
+In \astropy\ 0.4, therefore, unit and quantity support was still somewhat spotty, but this has changed greatly.
 One of the riskiest classes was ngles, where both degrees and radians were ``obvious'' default units to some.
 As a consequence, quantities are most fully integrated in the coordinates module (\sectionname~\ref{sec:coordinates}).
-In astropy 2.0, one can also opt in to use quantities fully in tables, by using the {\tt QTable} class (see \sectionname~\ref{sec:table}).
+In \astropy\ 2.0, one can also opt in to use quantities fully in tables, by using the {\tt QTable} class (see \sectionname~\ref{sec:table}).
 As a result, units in fits tables are also well-supported.
@@
 \par The general scheme for the releases and version numbering that the core
-package has adopted if the following. Astropy has new feature releases every
+package has adopted if the following. \astropy\ has new feature releases every
 6 month, and between feature releases additional bugfix releases that
@@
 %
-\par The version numbering of astropy reflects on the release scheme
+\par The version numbering of \astropy\ reflects on the release scheme
 described above. The core package uses the form x.y.z, where x is advances
@@
 \label{sec:core}
-The astropy project aims to provide python-based packages for all tasks that are commonly needed in a large subset of the astronomical community.
+The \astropy\ project aims to provide \python-based packages for all tasks that are commonly needed in a large subset of the astronomical community.
 Two aspects of this (time and coordinate transformations) are already discussed in great detail in section 3.
 In this section, we highlight other features introduced or substantially improved since version v0.2, which is described in \citet{2013A&A...558A..33A}.
-(ordered in the order in which they appear in the astropy documentation)
+(ordered in the order in which they appear in the \astropy\ documentation)
 
@@
 
-astropy implements `normalized convolution' \citep[e.g.,][]{Knutsson1993}, which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.
+\astropy\ implements `normalized convolution' \citep[e.g.,][]{Knutsson1993}, which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.
 In version $<=1.3$, the direct convolution and fft convolution approaches were not consistent, with fft convolution implementing normalized convolution and direct convolution implementing a different approach.
@@
 \includegraphics[width=\textwidth]{convolution_example.png}
-An example showing different modes of convolution available in the python ecosystem.
+An example showing different modes of convolution available in the \python ecosystem.
 The red x's mark pixels that are set to NaN in the original data (a).
@@
 Panel (c) shows what happens if the NaNs are set to zero first: the originally NaN regions are depressed relative to their surroundings.
-Finally, panel (d) shows astropy's convolution behavior, where the missing pixels are replaced with values interpolated from their surroundings using the convolution kernel.
+Finally, panel (d) shows \astropy's convolution behavior, where the missing pixels are replaced with values interpolated from their surroundings using the convolution kernel.
 \end{figure}
@@
 %
-\par In addition to astronomy related packages and libraries, the Astropy
+\par In addition to astronomy related packages and libraries, the \astropy\
 Project also contains and supports several infrastructure package that are
@@
 % Brigitta may write this up if there is no other takers
-\par Astropy provides a template package that any Python package is welcome to
+\par \astropy\ provides a template package that any Python package is welcome to
 use (many affiliated packages do so). The template contains a ready-to-go
@@
 variables. While the current development is mostly driven by the needs of
-the astropy ecosystem, the actual usage of this package is extremely
+the \astropy\ ecosystem, the actual usage of this package is extremely
 widespread. Currently we support setups for TravisCI and AppveyorCI.
@@
 
+% Adrian: this is something I do in my own papers - comment out if you think
+% it's crazy...
+This paper version was generated with the git commit
+\texttt{\githash\,(\gitdate)}.
+
 %% Similar to \facility{}, there is the optional \software command to allow
@@
 
-\software{astropy \citep{2013A&A...558A..33A},
-          numpy,
-          scipy,
+\software{\package{astropy} (\citealt{astropy}),
+          \package{numpy} (\citealt{numpy}),
+          \package{scipy} (\url{https://www.scipy.org/}),
           }

### 2017-09-29 main.tex
Update on Overleaf.
proj vs pkg

@@
 \newcommand{\python}{\package{Python}}
-\newcommand{\astropy}{\package{Astropy}}
+\newcommand{\astropy}{Astropy}
+\newcommand{\astropypkg}{\package{Astropy}}
 
@@
 \renewcommand{\tablename}{Table}
-
-\include{gitstuff}
 
@@
     \item Use \escapecmd{\sectionname} not ``Section,'' \escapecmd{\figurename} not ``Figure''
-    \item Use \escapecmd{\astropy} not ``astropy'', \escapecmd{\python} not ``Python''
+    \item Use \escapecmd{\astropypkg} for the astropy package, \escapecmd{\astropy} for the astropy project, \escapecmd{\python} not ``Python''
     \item If your subpackage was included in Paper I, then please just include a note on what the package does, a reference to paper I, and any new major updates to your package
@@
 organized in section~\ref{sec:concepts}.  The project develops a core
-package called \texttt{astropy} (section~\ref{sec:core}) and several
+package called \astropypkg\ (section~\ref{sec:core}) and several
 separate packages that help setting up the infrastructure for testing,
@@
 Hence, programs and functions expected to be fed parameters in particular units, as (hopefully) stated in their documentation.
-In \astropy\ 0.4, therefore, unit and quantity support was still somewhat spotty, but this has changed greatly.
+In \astropypkg\ 0.4, therefore, unit and quantity support was still somewhat spotty, but this has changed greatly.
 One of the riskiest classes was ngles, where both degrees and radians were ``obvious'' default units to some.
 As a consequence, quantities are most fully integrated in the coordinates module (\sectionname~\ref{sec:coordinates}).
-In \astropy\ 2.0, one can also opt in to use quantities fully in tables, by using the {\tt QTable} class (see \sectionname~\ref{sec:table}).
+In \astropypkg\ 2.0, one can also opt in to use quantities fully in tables, by using the {\tt QTable} class (see \sectionname~\ref{sec:table}).
 As a result, units in fits tables are also well-supported.
@@
 \par The general scheme for the releases and version numbering that the core
-package has adopted if the following. \astropy\ has new feature releases every
-6 month, and between feature releases additional bugfix releases that
+package has adopted if the following. \astropypkg\ has new feature releases every
+6 months, and between feature releases additional bugfix releases that
 contain only bugfixes but no new features. The timing of
@@
 %
-\par The version numbering of \astropy\ reflects on the release scheme
+\par The version numbering of \astropypkg\ reflects on the release scheme
 described above. The core package uses the form x.y.z, where x is advances
@@
 Two aspects of this (time and coordinate transformations) are already discussed in great detail in section 3.
-In this section, we highlight other features introduced or substantially improved since version v0.2, which is described in \citet{2013A&A...558A..33A}.
+In this section, we highlight other features introduced or substantially improved since version v0.2, which is described in \citet{astropy}.
 (ordered in the order in which they appear in the \astropy\ documentation)
@@
 
-\astropy\ implements `normalized convolution' \citep[e.g.,][]{Knutsson1993}, which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.
+\astropypkg\ implements `normalized convolution' \citep[e.g.,][]{Knutsson1993}, which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.
 In version $<=1.3$, the direct convolution and fft convolution approaches were not consistent, with fft convolution implementing normalized convolution and direct convolution implementing a different approach.
@@
 Panel (c) shows what happens if the NaNs are set to zero first: the originally NaN regions are depressed relative to their surroundings.
-Finally, panel (d) shows \astropy's convolution behavior, where the missing pixels are replaced with values interpolated from their surroundings using the convolution kernel.
+Finally, panel (d) shows \astropypkg's convolution behavior, where the missing pixels are replaced with values interpolated from their surroundings using the convolution kernel.
 \end{figure}
@@
 
-% Adrian: this is something I do in my own papers - comment out if you think
-% it's crazy...
-This paper version was generated with the git commit
-\texttt{\githash\,(\gitdate)}.
-
 %% Similar to \facility{}, there is the optional \software command to allow

### 2017-09-29 main.tex
imposing my will

@@
 
-\python\footnote{\url{https://www.python.org/}} is an increasingly
-popular general-purpose scripting language that is available under a
-permissive open source software licence free of charge for all major
-operating systems. Stable and well-developed packages provide support
-for array arithmetic \citep[numpy,][]{numpy}, a wide variety of
-functions for scientific computing \citep[scipy,][]{numpy}, and
-publication-quality plotting \citep[matplotlib,][]{matplotlib}. Tens of
-thousands of other packages are available which can help with tasks
-that are not astronomy specific but might be performed in the course
-of astronomical research, e.g.\ presenting results on websites or
-interfacing with databases.
+\python\footnote{\url{https://www.python.org/}} is an increasingly popular
+general-purpose scripting language that is available under a permissive open
+source software licence free of charge for all major operating systems. Stable
+and well-developed packages provide support for array arithmetic
+\citep[\package{numpy},][]{numpy}, a wide variety of functions for scientific
+computing \citep[\package{scipy},][]{numpy}, and publication-quality plotting
+\citep[\package{matplotlib},][]{matplotlib}. Tens of thousands of other packages
+are available which can help with tasks that are not astronomy specific but
+might be performed in the course of astronomical research, e.g., presenting
+results on websites or interfacing with databases.
 
@@
 The first public release of the \astropy\ package is described in
-\cite{2013A&A...558A..33A}. Since then, the \astropy\ package has been
+\cite{astropy}. Since then, the \astropy\ package has been
 used in hundreds of projects, and the scope of the package as grown
@@
 We start by describing the way the \astropy\ project works and is
-organized in section~\ref{sec:concepts}.  The project develops a core
-package called \astropypkg\ (section~\ref{sec:core}) and several
+organized in \sectionname~\ref{sec:concepts}.  The project develops a core
+package called \astropypkg\ (\sectionname~\ref{sec:core}) and several
 separate packages that help setting up the infrastructure for testing,
-documentation etc.\ (section~\ref{sec:infrastructure}). In
-section~\ref{sec:learning} we give an overview of the wealth of
+documentation etc.\ (\sectionname~\ref{sec:infrastructure}). In
+\sectionname~\ref{sec:learning} we give an overview of the wealth of
 resources created to teach new users the use of the \astropy\ packages
 and how to contribute to the community. We end with a short vision for
-the future of \astropy\ in section~\ref{sec:future}.
+the future of \astropy\ in \sectionname~\ref{sec:future}.
 

### 2017-09-29 main.tex
python

@@
 % free to modify!
-The \astropy\ project supports and fosters the development of open-source Python
-packages that provide commonly-needed functionality to the astronomical
+The \astropy\ project supports and fosters the development of open-source
+\python\ packages that provide commonly-needed functionality to the astronomical
 community.
@@
 astronomical coordinate systems. The \astropy\ project aims to provide a
-library of core astronomical functionality in the Python programming
+library of core astronomical functionality in the \python\ programming
 language.
@@
 applications where API stability is essential. The latest LTS release is
-also the last one that supports Python2, and will receive bug fixes until the
+also the last one that supports \python 2, and will receive bug fixes until the
 end of 2019.
@@
 \includegraphics[width=\textwidth]{convolution_example.png}
-An example showing different modes of convolution available in the \python ecosystem.
+An example showing different modes of convolution available in the \python\ ecosystem.
 The red x's mark pixels that are set to NaN in the original data (a).
@@
 % Brigitta may write this up if there is no other takers
-\par \astropy\ provides a template package that any Python package is welcome to
+\par \astropy\ provides a template package that any \python\ package is welcome to
 use (many affiliated packages do so). The template contains a ready-to-go
@@
 
-dropping python2 support, growths of affiliated packages
+dropping \python 2 support, growths of affiliated packages
 Summary

### 2017-09-29 main.tex
wrapping

@@
 \begin{itemize}
-   \item The goal is to produce a brief and informative paper that covers major \astropy\ principles not mentioned in the first paper, the core v2.0 package, and infrastructure in \astropy\ project to support development in \python.
-	\item We don't plan on including code in this paper, but if you think you will need to include code in your section, please add it to a separate Python module (.py file) and include it in this repository.
-    \item Use \escapecmd{\sectionname} not ``Section,'' \escapecmd{\figurename} not ``Figure''
-    \item Use \escapecmd{\astropypkg} for the astropy package, \escapecmd{\astropy} for the astropy project, \escapecmd{\python} not ``Python''
-    \item If your subpackage was included in Paper I, then please just include a note on what the package does, a reference to paper I, and any new major updates to your package
-    \item If your subpackage was not included, then please a further description of the sub-package on level with what was in the first paper, and highlight any major features in it.
-Typically length should be equivalent to one column
-    \item Please make sure you are logged into Overleaf or pushing a commit with your information to be able to track the contributors to the paper.
+   \item The goal is to produce a brief and informative paper that covers major
+        \astropy\ principles not mentioned in the first paper, the core v2.0
+        package, and infrastructure in \astropy\ project to support development
+        in \python.
+    \item We don't plan on including code in this paper, but if you think you
+        will need to include code in your section, please add it to a separate
+        Python module (.py file) and include it in this repository.
+    \item Use \escapecmd{\sectionname} not ``Section,'' \escapecmd{\figurename}
+        not ``Figure''
+    \item Use \escapecmd{\astropypkg} for the astropy package,
+        \escapecmd{\astropy} for the astropy project, \escapecmd{\python} not
+        ``Python''
+    \item If your subpackage was included in Paper I, then please just include a
+        note on what the package does, a reference to paper I, and any new major
+        updates to your package
+    \item If your subpackage was not included, then please a further description
+        of the sub-package on level with what was in the first paper, and
+        highlight any major features in it. Typical length should be
+        equivalent to one column.
+    \item Please make sure you are logged into Overleaf or pushing a commit with
+        your information to be able to track the contributors to the paper.
 

### 2017-09-29 main.tex
earth coordinates

@@
 \begin{itemize}
-    \item TODO: Celestial coordinates, but now also local coordinates (via
-    EarthLocation + Time). Now supports Alt-Az coordinates, observation planning
-    - shoutout to astroplan
+    \item In addition to representing celestial coordinates, \astropypkg\
+    now supports specifying positions on the Earth in a number of different
+    geocentric systems with the \texttt{EarthLocation} class.
+    With this, \astropypkg\ now supports Earth-location-specific coordinate
+    systems such as the altitude-azimuth (\texttt{AltAz}) or horizontal system.
+    Transformations between \texttt{AltAz} and any Barycentric coordinate frame
+    also requires specifying a time using the \texttt{Time} class from
+    \texttt{astropy.time}.
+    With this new functionality, many of the common tasks associated with
+    observation planning can now be completed with \astropypkg\ or the
+    \astropy-affiliated package \texttt{astroplan} (TODO: cite zenodo entry?).
     \item TODO: differential classes. Represent single-derivatives of

### 2017-09-29 main.tex
use a description list for key new features

@@
 
+\subsubsection{Overview}
 The \texttt{astropy.coordinates} subpackage is designed to support representing
@@
 
-\textbf{Key new features:}
-\begin{itemize}
-    \item In addition to representing celestial coordinates, \astropypkg\
-    now supports specifying positions on the Earth in a number of different
-    geocentric systems with the \texttt{EarthLocation} class.
+\subsubsection{Key new features}
+
+\begin{description}\itemsep0ex
+    \item[Local Earth coordinate frames] In addition to representing celestial
+    coordinates, \astropypkg\ now supports specifying positions on the Earth in
+    a number of different geocentric systems with the \texttt{EarthLocation}
+    class.
     With this, \astropypkg\ now supports Earth-location-specific coordinate
@@
     \astropy-affiliated package \texttt{astroplan} (TODO: cite zenodo entry?).
-    \item TODO: differential classes. Represent single-derivatives of
+
+    \item[Derivatives of coordinate representations]
+    As mentioned above, the \texttt{Representation} classes act like
+    three-dimensional vectors.
+    \texttt{astropy.coordinates} now also supports handling first derivatives of
+    the \texttt{Representation} classes through the new \texttt{Differential}
+    classes.
+    The \texttt{Differential} classes are currently used internal to the
+    \texttt{Frame} classes to store velocity data when attached to a
+    \texttt{Representation} instance.
+
+    TODO: differential classes. Represent single-derivatives of
     representations. Used to store velocity information, only really useful
     attached to a representation object.
-    \item TODO: Frame classes support proper motions, radial velocities. Explain
+
+    \item[Proper motion and velocity transformations]
+    TODO: Frame classes support proper motions, radial velocities. Explain
     component naming, why SkyCoord doesn't support right now, "experimental" but
     tested feature.
-    \item TODO: JPL ephemerids % Who can write this? Erik?
-\end{itemize}
+
+    \item[JPL ephemeris]
+    TODO: JPL ephemerids % Who can write this? Erik?
+\end{description}
 

### 2017-09-29 main.tex
velocities

@@
 
+    \item[Proper motion and velocity transformations]
+    In addition to positional coordinate data, the \texttt{Frame} classes now
+    also support velocity data.
+    As the default representation for most frames is spherical, most of the
+    \texttt{Frame} classes expect proper motion and radial velocity components
+    to specify the velocity information.
+    The names of the proper motion components all start with \texttt{pm_} and
+    adopt the same longitude and latitude names as the positional components.
+    Transforming coordinates with velocity data is also supported, but in some
+    cases the transformed velocity components have limited accuracy because the
+    transformations are done numerically.
+    The visualization of the coordinate frame transform graph highlights which
+    velocity transformations can be done exactly and which transformations are
+    done using a finite-difference scheme.
+    The low-level interface for specifying and transforming velocity data (see
+    the next point) is currently experimental.
+    As such, in v2.0, only the \texttt{Frame} classes (and not the
+    \texttt{SkyCoord} class) support handling velocities.
+
     \item[Derivatives of coordinate representations]
@@
     \texttt{astropy.coordinates} now also supports handling first derivatives of
-    the \texttt{Representation} classes through the new \texttt{Differential}
-    classes.
-    The \texttt{Differential} classes are currently used internal to the
-    \texttt{Frame} classes to store velocity data when attached to a
-    \texttt{Representation} instance.
-
-    TODO: differential classes. Represent single-derivatives of
-    representations. Used to store velocity information, only really useful
-    attached to a representation object.
-
-    \item[Proper motion and velocity transformations]
-    TODO: Frame classes support proper motions, radial velocities. Explain
-    component naming, why SkyCoord doesn't support right now, "experimental" but
-    tested feature.
+    vectors / representations through the new \texttt{Differential} classes.
+    The \texttt{Differential} classes are currently used internally within the
+    \texttt{Frame} classes to store the velocity data.
 
     \item[JPL ephemeris]
-    TODO: JPL ephemerids % Who can write this? Erik?
+    TODO: JPL ephemerids % Erik?
 \end{description}

### 2017-10-01 main.tex
typo
Update on Overleaf.
Adding affiliated concept first super rought draft

@@
 
+% For commenting - can be deleted before submission
+\usepackage[colorinlistoftodos]{todonotes}
+\newcommand{\inlinecomment}[2]{\todo[inline]{#1: #2}}
+\newcommand{\comment}[2]{\todo{#1: #2}}
+
 \begin{document}
@@
 
-\title{The Astropy Project: }
+\title{The Astropy Project}
 
@@
 release, version 2.0.
-We then describe the project infrastructure designed to facilitate [...]
+We then describe the project infrastructure designed to facilitate and support
+development for a broader ecosystem of interoperable packages.
 We conclude with a future outlook of planned new features and directions for the
-broader \astropy\ ecosystem.
+broader \astropy\ project.
 \end{abstract}
@@
         updates to your package
-    \item If your subpackage was not included, then please a further description
-        of the sub-package on level with what was in the first paper, and
-        highlight any major features in it. Typical length should be
-        equivalent to one column.
+    \item If your subpackage was not included, then please describe the
+        sub-package on level with what was in the first paper, and highlight any
+        major features in it. Typical length should be equivalent to one page
+        (single-column).
     \item Please make sure you are logged into Overleaf or pushing a commit with
@@
 % ^.
+% hamogu: Feel free ot swap in Starlink, if you think that's more appropriate.
+I picked ds9 becase (a) it's wider known (e.g.
+in the X-ray sounity) and (b) because it is an example of a widely used tool with institutional support that is NOT a large package.
+TOPCAT would have been another example if we want to expand that list.
   SAO,][]{ds9}. These packages tend to address a wide range of users
@@
 functionality that is common to many astronomical tasks. Reading and
-writing fits files is one example where it is time
-consuming to implement the fits standard correctly and
+writing FITS files is one example where it is time
+consuming to implement the FITS standard correctly and
 programming is much faster when using an existing library perform this
@@
 % Anyone want to take this??
-\subsection{APEs - Astropy Proposals for Enhancement}
-% would be nice to write about the concept of APEs so we can refer to the
-% relevant ones latr in the text
 
@@
 % Kelle
+
+\subsection{APEs - Astropy Proposals for Enhancement}
+%draft by hamogu
+Central to the success of \astropy\ is an open environment where
+anybody can contribute to the code by opening a so-called ``pull
+request'' with a new code contribution on an publically available
+website\footnote{\url{https://github.com/astropy/astropy}}; this
+request is then reviewed by a maintainer responsible for the specific
+sub-package and possibly merged into the main code base. Most bug
+fixes and small features are contributed in this way. However, this
+model leads to ``organic'' growth where different features are
+implemented by different people with different programming styles and
+interfaces. Thus, \astropy\ has a mechanism to more formally propose
+changes to the code management (e.g.\ the release cycle) or to plan
+out major new features. This mechanism is called ``Astropy Proposal
+for Enhancement'' (APE). In an APE one or more authors lay out a
+vision for a new feature, including a rationale why this feature is
+needed, how it should be implemented, and what the interface will
+be. These APEs are discussed and refined before much work is invested
+into a detailed implementation. APEs are again edited and discussed on
+a platform \footnote{\url{https://github.com/astropy/astropy-APEs}}
+open to the public. In previous APEs a community concensus emerged and
+APEs are accepted and become the basis for future work at this
+point. In cases where consensus cannot be reached, the
+\astropy\ coordination committee can decide to close the discussion and
+make an executive decision based on the community input on the APE in
+question. APEs are modeled after the ``Python Enhancement Proposals''
+(PEP) and guide the development of the \python\ programming language.
 
@@
 % write it up
-
+%
+\par A major part of the \astropy project is the concept of “Affiliated
+Packages”. An affiliated package is an astronomy-related Python package that
+is not part of the \astropypkg core package, but has requested to be included as
+part of the astropy project’s community. These packages support the goals
+and vision of \astropy of improving code reuse, interoperability, and
+embracing good coding practices such as testing and thorough
+documentation. \astropypkg currently supports both versions of Python 2.7+ and
+Python 3.x, affiliated packages are strongly encouraged to support at least
+Python 3.x.
+%
+\par Affiliated packages contain functionality that is more specialized, or
+have license incompatibility, or have enough external dependencies (e.g. GUI
+libraries) that limit their integration possibility into the core and thus
+they are more suitable to be separate packages. In general we hope that
+becoming an affiliated package is seen as a good way for new and existing
+packages to gain exposure.
+%
+% TODO: write about the process of becoming affiliated, and project packages
+%
 \subsection{Mixin}
@@
 In \astropypkg\ 0.4, therefore, unit and quantity support was still somewhat spotty, but this has changed greatly.
-One of the riskiest classes was ngles, where both degrees and radians were ``obvious'' default units to some.
+One of the riskiest classes was angles, where both degrees and radians were ``obvious'' default units to some.
 As a consequence, quantities are most fully integrated in the coordinates module (\sectionname~\ref{sec:coordinates}).
 In \astropypkg\ 2.0, one can also opt in to use quantities fully in tables, by using the {\tt QTable} class (see \sectionname~\ref{sec:table}).
-As a result, units in fits tables are also well-supported.
+As a result, units in FITS tables are also well-supported.
 For most other modules, quantities are at least accepted, and often assumed by default.
@@
 % Brigitta can writes this up if there's no other taker
-%
+%\inlinecomment{EJT}{Need to create a Zenodo DOI for ERFA and then cite it here.}
 % - reference APE2 for versioning and APE10 for dropping python2 support
@@
 \label{sec:core}
-The \astropy\ project aims to provide \python-based packages for all tasks that are commonly needed in a large subset of the astronomical community.
-Two aspects of this (time and coordinate transformations) are already discussed in great detail in section 3.
-In this section, we highlight other features introduced or substantially improved since version v0.2, which is described in \citet{astropy}.
-(ordered in the order in which they appear in the \astropy\ documentation)
+
+The \astropy\ project aims to provide \python-based packages for all tasks that
+are commonly needed in a large subset of the astronomical community.
+At the foundation is the \astropypkg\ core package, which provides general
+functionality (e.g., coordinate transformations) or base classes for other
+packages to utilize for a common interface (e.g., \texttt{NDData}).
+In this section, we highlight new features introduced or substantially improved
+since version v0.2 (previously described in \citealt{astropy}).
 
@@
 
-\textbf{Key new features:}
-\begin{itemize}
-	\item incl logarithmic units and magnitudes
-	\item speed improvements
-    \item interaction with numpy arrays
-\end{itemize}
+The \texttt{astropy.units} subpackage provides ...
+
+\subsubsection{Key new features}
+
+\begin{description}
+    \item[Speed improvements] ...
+    \item[Logarithmic units and magnitudes] ...
+    \item[Interaction with \texttt{numpy} arrays] ...
+\end{description}
 
@@
 % Adrian, Erik
+\inlinecomment{APW}{Do we want to put in a PDF of the transform graph?}
+\inlinecomment{EJT}{I think so?  It looks pretty slick...}
 
 \subsubsection{Overview}
-The \texttt{astropy.coordinates} subpackage is designed to support representing
+The \package{astropy.coordinates} subpackage is designed to support representing
 and transforming celestial coordinates and, new in version 2.0, velocities.
-The framework heavily relies on the \texttt{astropy.units} subpackage, and most
+The framework heavily relies on the \package{astropy.units} subpackage, and most
 inputs to objects in this subpackage are expected to be \texttt{Quantity}
 objects.
+Some of the machinery also relies on the Essential Routines of Fundamental
+Astronomy (ERFA) \texttt{C} library for some of the critical underlying
+transformation machinery.
+\inlinecomment{EJT}{Need to create a Zenodo DOI for ERFA and then cite it here.}
 A key concept behind the design of this subpackage is that coordinate
@@
 For example, a set of coordinates in the International Celestial Reference
-System (ICRS) reference frame could be represented as a spherical (distance,
-right ascension, declination) or Cartesian coordinates.
-They can therefore be re-represented or transformed to other reference frames
-(e.g., the Galactic frame) in an independent way.
+System (ICRS) reference frame could be represented as spherical (right
+ascension, declination, and distance from solar system barycenter) or Cartesian
+coordinates ($x$, $y$, $z$ with the origin at ).
+They can therefore change representations independent of being transformed to
+other reference frames (e.g., the Galactic coordinate frame).
 
@@
 data.
-For most frames the preferred representation is spherical.
+For most frames the preferred representation is spherical, although this is
+determined primarily by the common use in the astronomical community.
 
@@
 representing astronomical coordinates through the \texttt{SkyCoord} class.
-The \texttt{SkyCoord} class was designed to provide a single, go-to class that
-accepts a wide range of possible inputs, and supports coordinate data in any
-reference frame with a corresponding \texttt{Frame} class in any representation
-with a corresponding \texttt{Representation} class.
+The \texttt{SkyCoord} class was designed to provide a single class that
+accepts a wide range of possible inputs.
+It supports coordinate data in any coordinate frame in any representation by
+internally using the \texttt{Frame} and \texttt{Representation} classes.
 
@@
 
-\begin{description}\itemsep0ex
+\begin{description}
     \item[Local Earth coordinate frames] In addition to representing celestial
@@
     observation planning can now be completed with \astropypkg\ or the
-    \astropy-affiliated package \texttt{astroplan} (TODO: cite zenodo entry?).
+    \astropy-affiliated package \package{astroplan}. \inlinecomment{APW}{TODO: cite zenodo entry for astroplan?}.
 
@@
     to specify the velocity information.
-    The names of the proper motion components all start with \texttt{pm_} and
+    The names of the proper motion components all start with \texttt{pm} and
     adopt the same longitude and latitude names as the positional components.
@@
 
-    \item[JPL ephemeris]
-    TODO: JPL ephemerids % Erik?
+    \item[Solar System Ephemerides]
+    Also new is support for computing ephemerides of major solar system bodies
+    and outputting the resulting positions as coordinate objects.
+    These ephemerides can be computed either using analytic approximations from
+    ERFA, or from downloaded JPL ephemerides (the latter requires the \package{j
+    plephem}\footnote{\url{https://github.com/brandon-rhodes/python-jplephem}}
+    optional dependency and an internet connection).
+    The \texttt{get\_body} and \texttt{get\_body\_barycentric} functions provide
+    the gateway to this functionality, yielding \texttt{SkyCoord} objects given
+    a specific body and choice of ephemeris source.
+
 \end{description}
@@
 
-Q: does it make sense to refer forward to fits support, even though it is 3.0?
+Q: does it make sense to refer forward to FITS support, even though it is 3.0?
+
+\inlinecomment{EJT}{ERFA is likely to be referenced somewhere here. should cite the DOI as mentioned in the above ERFA refernce once it exists}
 
@@
 
+The \package{astropy.io} subpackage provides support for reading and writing
+various formats: a wide range of ASCII data table formats, FITS, VOTable, etc.
+It also provides a unified interface for reading and writing data with these
+different formats, using the \package{astropy.table} subpackage.
+For many common cases this simplifies the process of file I/O and reduce the
+need to master the separate details of all the I/O packages within Astropy.
+% This functionality is still in active development and the number of supported
+% formats will be increasing.
+
+\inlinecomment{SCO}{Pyfits deprecation in favor of io.fits ?}
+\inlinecomment{SCO}{Table and FITS tables}
+
 \subsubsection{Unified file read/write interface}
 
-Check when it was added (0.3?). Overview of the supported formats (ascii, fits, votable).
+Check when it was added (0.3?). Overview of the supported formats (ASCII,
+FITS, votable, HTML, JSViewer/Datatables).
 
-\subsubsection{Enhanced CSV format}
+\subsubsection{Key new features}
 
-\subsubsection{ASCII, FITS, etc.}
+\inlinecomment{SCO}{One subsection per format (if enough new features) ?}
 
-One subsection per format (if enough new features) ?
+\begin{description}
 
-\begin{itemize}
-\item ascii : fast reader/writer (1.0), HTML tables
-\item fits: lazy loading, command-line scripts (fitsheader, fitsinfo)
-\end{itemize}
+    \item[ASCII: fast reader/writer (v1.0)]
+
+		The \package{astropy.io.ascii} module now includes a significantly faster
+		Cython/C engine for reading and writing ASCII files. This is available
+		for the following formats: basic, commented\_header, csv, no\_header,
+		rdb, and tab.  On average the new engine is about 4 to 5 times faster
+		than the corresponding pure-Python implementation, and is often
+		comparable to the speed of the pandas ASCII file interface. The fast
+		reader has parallel processing option that allows harnessing multiple
+		cores for input parsing to achieve even greater speed gains.
+
+		By default, read() and write() will attempt to use the fast C engine when
+		dealing with compatible formats. Certain features of the full read / write
+		interface are not available in the fast version, in which case the
+		pure-Python version will automatically be used.
+
+    \item[ASCII: HTML tables (v0.4)]
+
+		The \package{astropy.io.ascii} sub-package now provides the capability
+		to read a table within an HTML file or web URL into an astropy
+		\texttt{Table} object. This requires the \package{BeautifulSoup4}
+		package to be installed.  Conversely a \texttt{Table} object can now
+		be written out as an HTML table.
+
+	\item [Enhanced CSV format (v1.0)]
+
+		One of the problems when storing a table in an ASCII format is
+		preserving table meta-data such as comments, keywords and column data
+		types, units, and descriptions. Using the newly defined \emph{Enhanced
+		Character Separated Values} (ECSV) format it is now possible to write
+		a table to an ASCII-format file and read it back with no loss of
+		information. The ECSV format has been designed to be both
+		human-readable and compatible with most simple CSV readers.
+
+	\item [FITS: command-line scripts (\texttt{fitsheader}, \texttt{fitsinfo}, v0.4)]
+
+		The \package{astropy.io.fits} sub-package now provides a command line
+		script for inspecting the header(s) of a FITS file.  Running
+		\texttt{fitsheader file.fits} in a terminal prints the header
+		information to the screen in a human-readable format. Run
+		\texttt{fitsheader --help} to see the full usage documentation.
+
+	\item [FITS: lazy loading (v1.3)]
+
+		The \package{astropy.io.fits} sub-package now supports \emph{lazy
+		loading}, where all HDUs are not loaded until they are requested (or
+		the file is closed). This should provide substantial speedups for
+		situations using the convenience functions (e.g., \texttt{getheader()}
+		or \texttt{getdata()}) to get HDU’s that are near the front of a file
+		with many HDU’s.
+
+	\item [Misc: YAML serialization (v1.3)]
+
+		The new \package{astropy.io.misc.yaml} module allows converting
+		astropy objects into a standard YAML format.
+
+\end{description}
 
@@
 % Larry:  Image visualization (stretching, scaling), RGB
-% Tom R.:  WCSAxes
 
-wcsaxis, rgb, histograms comes to mind.Can use more publicity and also makes good images to include in the paper.
+The \package{visualization} package provides functionality that can be helpful when visualizing data.
+This includes a framework for plotting astronomical images with coordinates with Matplotlib (previously the standalone \package{wcsaxes} package), functionality related to image normaliation (including both scaling and stretching), smart histogram plotting, RGB color image creation from separate images, and custom plotting styles for Matplotlib.
+
+\subsubsection{Image Stretching and Normalization}
+
+The \package{visualization} package provides a framework for transforming values in images (and more generally any arrays), typically for the purpose of visualization.
+Two main types of transformations are normalization and stretching of image values.
+
+Normalization transforms the images values to the [0:1] range using lower and upper limits where $x$ represents the values in the original image:
+
+\begin{equation}
+y = \frac{x - v_{vmin}}{v_{max} − v_{min}}
+\end{equation}
+
+Stretching transforms the image values in the [0:1] range to the [0:1] range using a linear or non-linear function:
+\begin{equation}
+z = f(y)
+\end{equation}
+
+In addition, classes are provided in order to identify lower and upper limits for a dataset based on specific algorithms (such as using percentiles).
+
+Identifying lower and upper limits, as well as re-normalizing, is described in the Intervals and Normalization section, while stretching is described in the Stretching section.
+
+\subsubsection{WCSAxes}
+% Tom R.
+
+\subsubsection{Choosing Histogram Bins}
+
+\subsubsection{Creating color RGB images}
+% include images
 
@@
 \subsection{Statistics}
+
+The \astropypkg\ \package{stats} package provides
+statistical tools that are useful for or specific to
+astronomy and are not found in other \python\
+statistics packages such as \package{scipy}
+\citep{scipy} or \package{statsmodels}
+\citep{seabold2010statsmodels}.   The
+\package{stats} package contains a range of
+different functionality used by many different
+disciplines in astronomy.   It is not a complete set
+of statistic tools, but rather a still growing
+collection of useful features.
+
+The current review process for contributions to the \package{stats} package includes review of the code, documentation, testing, and scientific merit of the inclusion.
+When necessary, scientific reviewers outside of the maintainers will be sought for their input on new pull requests.
+
+In this section, we describe these tools that provide a range of different functionality including robust statistical estimators, circular statistics, periodograms, spatial statistics, and histogram binning.
+
 % Steve C.: overview, circular stats,
@@
 % Ze':  Ripley's K (spatial stats)
-major additions to be discussed: lomb-scargle, sigma clipping, bayesian blocks, histograms, also:  robust (biweight) statistics
 
-\subsection{Robust Statistical Estimators}
-\subsection{Circular Statistics}
-\subsection{Lomb-Scargle Periodograms}
-\subsection{Ripley's K Function Estimators}
-\subsection{Histogram Binning}
+\subsubsection{Robust Statistical Estimators}
+
+Robust statistics provide reliable estimates of basic statistics for complex distributions.
+The \package{stats} package includes several robust statistical functions that are commonly used in astronomy.
+This includes methods for rejecting outliers as well as statistical description of the underlying distributions.
+
+\subsubsection{Sigma Clipping}
+
+Sigma clipping provides a fast method to identify outliers in a distribution.
+For a distribution of points, a center and a standard deviation are calculated.
+Values which are a set number of sigma times the standard deviation away from the center are rejected.
+The process can be iterated to further reject outliers.
+
+\subsubsection{Median Absolute Deviation}
+
+The median abosolute deviation (MAD) is a measure of the spread of a distribution and is defined as median(abs(a - median(a))).
+For a normal distribution, the MAD is related to the standard deviation by a factor of 1.4826, and a convenience function is available to apply the conversion.
+
+\subsubsection{Biweight Estimators}
+
+A set of functions are included in the \package{stats} package that use the biweight formalism.
+These functions have long been used in astronomy, particularly to calculate the velocity dispersion of galaxy clusters [XXX].
+
+\subsubsection{Circular Statistics}
+%steve
+\subsubsection{Lomb-Scargle Periodograms}
+%jake
+\subsubsection{Ripley's K Function Estimators}
+%ze
+\subsubsection{Histogram Binning}
+%jake
 
@@
 % - should we use links to the appropriate github repo?
+% - should we describe astropy-helpers even though it's future is unsure?
 %
@@
 %
-\subsubsection{Package template}
+\subsection{Package template}
 % Brigitta may write this up if there is no other takers
@@
           \package{scipy} (\url{https://www.scipy.org/}),
+          \package{matplotlib} (\url{https://matplotlib.org/}),
           }
@@
 
-\begin{thebibliography}{}
-
-\end{thebibliography}
-
 \end{document}

### 2017-10-02 main.tex
Update on Overleaf.
s/ngles/angles/

--- 2017-09-29 main.tex
@@
 In \astropypkg\ 0.4, therefore, unit and quantity support was still somewhat spotty, but this has changed greatly.
-One of the riskiest classes was ngles, where both degrees and radians were ``obvious'' default units to some.
+One of the riskiest classes was angles, where both degrees and radians were ``obvious'' default units to some.
 As a consequence, quantities are most fully integrated in the coordinates module (\sectionname~\ref{sec:coordinates}).
@@
 % Adrian, Erik
+% TODO: Do we want to put in a PDF of the transform graph?
 

### 2017-10-03 main.tex
units new features
Update on Overleaf.

@@
 \subsection{Robust Statistical Estimators}
+
+Robust statistics provide reliable estimates of basic statistics for complex distributions.
+The \package{stats} package includes several robust statistical functions that are commonly used in astronomy.
+This includes methods for rejecting outliers as well as statistical description of the underlying distributions.
+
+\subsubsection{Sigma Clipping}
+
+Sigma clipping provides a fast method to identify outliers in a distribution.
+For a distribution of points, a center and a standard deviation are calculated.
+Values which are a set number of sigma times the standard deviation away from the center are rejected.
+The process can be iterated to further reject outliers.
+
+\subsubsection{Median Absolute Deviation}
+
+The median abosolute deviation (MAD) is a measure of the spread of a distribution and is defined as median(abs(a - median(a))).
+For a normal distribution, the MAD is related to the standard deviation by a factor of 1.4826, and a convenience function is available to apply the conversion.
+
+\subsubsection{Biweight Estimators}
+
+A set of functions are included in the \package{stats} package that use the biweight formalism.
+These functions have long been used in astronomy, particularly to calculate the velocity dispersion of galaxy clusters [XXX].
+
 \subsection{Circular Statistics}

### 2017-10-03 main.tex
Update on Overleaf.

@@
 \subsection{Statistics}
+
+The \astropypkg\ \package{stats} package provides 
+statistical tools that are useful for or specific to 
+astronomy and are not found in other \python\ 
+statistics packages such as \package{scipy} 
+\citep{scipy} or \package{statsmodels} 
+\citep{seabold2010statsmodels}.   The 
+\package{stats} package contains a range of 
+different functionality used by many different 
+disciplines in astronomy.   It is not a complete set 
+of statistic tools, but rather a still growing 
+collection of useful features.
+
+The current review process for contributions to the \package{stats} package includes review of the code, documentation, testing, and scientific merit of the inclusion.
+When necessary, scientific reviewers outside of the maintainers will be sought for their input on new pull requests.
+
+In this section, we describe these tools that provide a range of different functionality including robust statistical estimators, circular statistics, periodograms, spatial statistics, and histogram binning.
+
 % Steve C.: overview, circular stats,
@@
 % Ze':  Ripley's K (spatial stats)
-major additions to be discussed: lomb-scargle, sigma clipping, bayesian blocks, histograms, also:  robust (biweight) statistics
 
-\subsection{Robust Statistical Estimators}
+\subsubsection{Robust Statistical Estimators}
 
@@
 
-\subsection{Circular Statistics}
-\subsection{Lomb-Scargle Periodograms}
-\subsection{Ripley's K Function Estimators}
-\subsection{Histogram Binning}
+\subsubsection{Circular Statistics}
+%steve
+\subsubsection{Lomb-Scargle Periodograms}
+%jake
+\subsubsection{Ripley's K Function Estimators}
+%ze
+\subsubsection{Histogram Binning}
+%jake
 

### 2017-10-04 main.tex
Update on Overleaf.
Add text for APEs

@@
 % Kelle
+
+\subsection{APEs - Astropy Proposals for Enhancement}
+%draft by hamogu
+Central to the success of \astropy\ is an open environment where
+anybody can contribute to the code by opening a so-called ``pull
+request'' with a new code contribution on an publically available
+website\footnote{\url{https://github.com/astropy/astropy}}; this
+request is then reviewed by a maintainer responsible for the specific
+sub-package and possibly merged into the main code base. Most bug
+fixes and small features are contributed in this way. However, this
+model leads to ``organic'' growth where different features are
+implemented by different people with different programming styles and
+interfaces. Thus, \astropy\ has a mechanism to more formally propose
+changes to the code management (e.g.\ the release cycle) or to plan
+out major new features. This mechanism is called ``Astropy Proposal
+for Enhancement'' (APE). In an APE one or more authors lay out a
+vision for a new feature, including a rationale why this feature is
+needed, how it should be implemented, and what the interface will
+be. These APEs are discussed and refined before much work is invested
+into a detailed implementation. APEs are again edited and discussed on
+a platform \footnote{\url{https://github.com/astropy/astropy-APEs}}
+open to the public. In previous APEs a community concensus emerged and
+APEs are accepted and become the basis for future work at this
+point. In cases where consensus cannot be reached, the
+\astropy\ coordination comitee can decide to close the discussion and
+make an executive decision based on the community input on the APE in
+question. APEs are modeled after the ``Python Enhancement Proposals''
+(PEP) and guide the development of the \python\ programming language.
 

### 2017-10-04 main.tex
Remove colon from title
Update on Overleaf.

@@
 % Adrian, Erik
-% TODO: Do we want to put in a PDF of the transform graph?
+\inlinecomment{APW}{Do we want to put in a PDF of the transform graph?}
+\inlinecomment{EJT}{I think so?  It looks pretty slick...}
 
 \subsubsection{Overview}
-The \texttt{astropy.coordinates} subpackage is designed to support representing
+The \package{astropy.coordinates} subpackage is designed to support representing
 and transforming celestial coordinates and, new in version 2.0, velocities.
-The framework heavily relies on the \texttt{astropy.units} subpackage, and most
+The framework heavily relies on the \package{astropy.units} subpackage, and most
 inputs to objects in this subpackage are expected to be \texttt{Quantity}
-objects.
+objects. Some of the machinery also relies on the Essential Routines of Fundamental Astronomy (ERFA) C library for some of the critical underlying transformation machinery.
+\inlinecomment{EJT}{Need to create a Zenodo DOI for ERFA and then cite it here.}
 A key concept behind the design of this subpackage is that coordinate
@@
 For example, a set of coordinates in the International Celestial Reference
-System (ICRS) reference frame could be represented as a spherical (distance,
-right ascension, declination) or Cartesian coordinates.
-They can therefore be re-represented or transformed to other reference frames
-(e.g., the Galactic frame) in an independent way.
+System (ICRS) reference frame could be represented as spherical (right ascension, declination, and distance from solar system barycenter) or Cartesian coordinates ($x$, $y$, $z$ with the origin at ).
+They can therefore change representations independent of being transformed to other reference frames (e.g., the Galactic coordinate frame).
 
@@
 data.
-For most frames the preferred representation is spherical.
+For most frames the preferred representation is spherical, although this is determined primarily by the common use in the astronomical community.
 
@@
 representing astronomical coordinates through the \texttt{SkyCoord} class.
-The \texttt{SkyCoord} class was designed to provide a single, go-to class that
-accepts a wide range of possible inputs, and supports coordinate data in any
-reference frame with a corresponding \texttt{Frame} class in any representation
-with a corresponding \texttt{Representation} class.
+The \texttt{SkyCoord} class was designed to provide a single class that
+accepts a wide range of possible inputs.  It supports coordinate data in any
+coordinate frame in any representation by internally using the \texttt{Frame} and \texttt{Representation} classes.
 
@@
 
-    \item[JPL ephemeris]
-    TODO: JPL ephemerids % Erik?
+    \item[Solar System Ephemerides]
+    \comment{EJT}{APW, you may want to give this item a quick read-over?  If it looks good just delete this comment}
+    Also new is support for computing ephemeris of major solar system bodies and outputting the resulting positions as coordinate objects. 
+    These ephemerides can be computed either using analytic approximations from ERFA (which requires no data download beyond the source code), or from downloaded JPL ephemerides (which requires the \package{jplephem}\footnote{\url{https://github.com/brandon-rhodes/python-jplephem}} optional dependency).
+    The \texttt{get\_body} and \texttt{get\_body\_barycentric} functions provide the gateway to this functionality, yielding \texttt{SkyCoord} objects given a specific body and choice of ephemeris source.
+
 \end{description}
@@
 Q: does it make sense to refer forward to fits support, even though it is 3.0?
+
+\inlinecomment{EJT}{ERFA is likely to be referenced somewhere here. should cite the DOI as mentioned in the above ERFA refernce once it exists}
 

### 2017-10-04 main.tex
edits to jpl ephemerides bit

@@
 inputs to objects in this subpackage are expected to be \texttt{Quantity}
-objects. Some of the machinery also relies on the Essential Routines of Fundamental Astronomy (ERFA) C library for some of the critical underlying transformation machinery.
+objects.
+Some of the machinery also relies on the Essential Routines of Fundamental
+Astronomy (ERFA) \texttt{C} library for some of the critical underlying
+transformation machinery.
 \inlinecomment{EJT}{Need to create a Zenodo DOI for ERFA and then cite it here.}
@@
 For example, a set of coordinates in the International Celestial Reference
-System (ICRS) reference frame could be represented as spherical (right ascension, declination, and distance from solar system barycenter) or Cartesian coordinates ($x$, $y$, $z$ with the origin at ).
-They can therefore change representations independent of being transformed to other reference frames (e.g., the Galactic coordinate frame).
+System (ICRS) reference frame could be represented as spherical (right
+ascension, declination, and distance from solar system barycenter) or Cartesian
+coordinates ($x$, $y$, $z$ with the origin at ).
+They can therefore change representations independent of being transformed to
+other reference frames (e.g., the Galactic coordinate frame).
 
@@
 data.
-For most frames the preferred representation is spherical, although this is determined primarily by the common use in the astronomical community.
+For most frames the preferred representation is spherical, although this is
+determined primarily by the common use in the astronomical community.
 
@@
 The \texttt{SkyCoord} class was designed to provide a single class that
-accepts a wide range of possible inputs.  It supports coordinate data in any
-coordinate frame in any representation by internally using the \texttt{Frame} and \texttt{Representation} classes.
+accepts a wide range of possible inputs.
+It supports coordinate data in any coordinate frame in any representation by
+internally using the \texttt{Frame} and \texttt{Representation} classes.
 
@@
     \item[Solar System Ephemerides]
-    \comment{EJT}{APW, you may want to give this item a quick read-over?  If it looks good just delete this comment}
-    Also new is support for computing ephemeris of major solar system bodies and outputting the resulting positions as coordinate objects. 
-    These ephemerides can be computed either using analytic approximations from ERFA (which requires no data download beyond the source code), or from downloaded JPL ephemerides (which requires the \package{jplephem}\footnote{\url{https://github.com/brandon-rhodes/python-jplephem}} optional dependency).
-    The \texttt{get\_body} and \texttt{get\_body\_barycentric} functions provide the gateway to this functionality, yielding \texttt{SkyCoord} objects given a specific body and choice of ephemeris source.
+    Also new is support for computing ephemerides of major solar system bodies
+    and outputting the resulting positions as coordinate objects.
+    These ephemerides can be computed either using analytic approximations from
+    ERFA, or from downloaded JPL ephemerides (the latter requires the \package{j
+    plephem}\footnote{\url{https://github.com/brandon-rhodes/python-jplephem}}
+    optional dependency and an internet connection).
+    The \texttt{get\_body} and \texttt{get\_body\_barycentric} functions provide
+    the gateway to this functionality, yielding \texttt{SkyCoord} objects given
+    a specific body and choice of ephemeris source.
 

### 2017-10-04 main.tex
intro for io

--- 2017-10-04 main.tex
@@
 point. In cases where consensus cannot be reached, the
-\astropy\ coordination comitee can decide to close the discussion and
+\astropy\ coordination committee can decide to close the discussion and
 make an executive decision based on the community input on the APE in
@@
 In \astropypkg\ 2.0, one can also opt in to use quantities fully in tables, by using the {\tt QTable} class (see \sectionname~\ref{sec:table}).
-As a result, units in fits tables are also well-supported.
+As a result, units in FITS tables are also well-supported.
 For most other modules, quantities are at least accepted, and often assumed by default.
@@
 
-Q: does it make sense to refer forward to fits support, even though it is 3.0?
+Q: does it make sense to refer forward to FITS support, even though it is 3.0?
 
@@
 
+The \package{astropy.io} subpackage provides support for reading and writing
+various formats: a wide range of ASCII data table formats, FITS, VOTable, etc.
+It also provides a unified interface for reading and writing data with these
+different formats, using the \package{astropy.table} subpackage.
+For many common cases this simplifies the process of file I/O and reduce the
+need to master the separate details of all the I/O packages within Astropy.
+% This functionality is still in active development and the number of supported
+% formats will be increasing.
+
 \subsubsection{Unified file read/write interface}
 
-Check when it was added (0.3?). Overview of the supported formats (ascii, fits, votable).
+Check when it was added (0.3?). Overview of the supported formats (ASCII,
+FITS, votable, HTML, JSViewer/Datatables).
 
@@
 
-One subsection per format (if enough new features) ?
+\inlinecomment{SCO}{One subsection per format (if enough new features) ?}
+
+List of key new features:
 
 \begin{itemize}
-\item ascii : fast reader/writer (1.0), HTML tables
-\item fits: lazy loading, command-line scripts (fitsheader, fitsinfo)
+\item ASCII : fast reader/writer (1.0), HTML tables
+\item FITS: lazy loading, command-line scripts (fitsheader, fitsinfo)
 \end{itemize}

### 2017-10-04 main.tex
new features

@@
 
-\begin{itemize}
-\item ASCII : fast reader/writer (1.0), HTML tables
-\item FITS: lazy loading, command-line scripts (fitsheader, fitsinfo)
-\end{itemize}
+\begin{description}
+
+    \item[ASCII: fast reader/writer (v1.0)]
+
+		The \package{astropy.io.ascii} module now includes a significantly faster
+		Cython/C engine for reading and writing ASCII files. This is available
+		for the following formats: basic, commented\_header, csv, no\_header,
+		rdb, and tab.  On average the new engine is about 4 to 5 times faster
+		than the corresponding pure-Python implementation, and is often
+		comparable to the speed of the pandas ASCII file interface. The fast
+		reader has parallel processing option that allows harnessing multiple
+		cores for input parsing to achieve even greater speed gains.
+
+		By default, read() and write() will attempt to use the fast C engine when
+		dealing with compatible formats. Certain features of the full read / write
+		interface are not available in the fast version, in which case the
+		pure-Python version will automatically be used.
+
+    \item[ASCII: HTML tables]
+		TODO.
+
+	\item [FITS: command-line scripts (fitsheader, fitsinfo)]
+		TODO.
+
+	\item [FITS: lazy loading (v1.3)]
+		The \package{astropy.io.fits} sub-package now supports \emph{lazy
+		loading}, where all HDUs are not loaded until they are requested (or
+		the file is closed). This should provide substantial speedups for
+		situations using the convenience functions (e.g., \texttt{getheader()}
+		or \texttt{getdata()}) to get HDU’s that are near the front of a file
+		with many HDU’s.
+
+	\item [Misc: YAML serialization (v1.3)]
+		The new \astropy{astropy.io.misc.yaml} module
+		allows converting astropy objects into a standard YAML format.
+
+\end{description}
 

### 2017-10-04 main.tex
more features

@@
 
+\inlinecomment{SCO}{Pyfits deprecation in favor of io.fits ?}
+\inlinecomment{SCO}{Table and FITS tables}
+
 \subsubsection{Unified file read/write interface}
@@
 
-\subsubsection{Enhanced CSV format}
-
-\subsubsection{ASCII, FITS, etc.}
+\subsubsection{Key new features}
 
 \inlinecomment{SCO}{One subsection per format (if enough new features) ?}
-
-List of key new features:
 
@@
 
-    \item[ASCII: HTML tables]
-		TODO.
+    \item[ASCII: HTML tables (v0.4)]
 
-	\item [FITS: command-line scripts (fitsheader, fitsinfo)]
-		TODO.
+		The \package{astropy.io.ascii} sub-package now provides the capability
+		to read a table within an HTML file or web URL into an astropy
+		\texttt{Table} object. This requires the \package{BeautifulSoup4}
+		package to be installed.  Conversely a \texttt{Table} object can now
+		be written out as an HTML table.
+
+	\item [Enhanced CSV format (v1.0)]
+
+		One of the problems when storing a table in an ASCII format is
+		preserving table meta-data such as comments, keywords and column data
+		types, units, and descriptions. Using the newly defined \emph{Enhanced
+		Character Separated Values} (ECSV) format it is now possible to write
+		a table to an ASCII-format file and read it back with no loss of
+		information. The ECSV format has been designed to be both
+		human-readable and compatible with most simple CSV readers.
+
+	\item [FITS: command-line scripts (\texttt{fitsheader}, \texttt{fitsinfo}, v0.4)]
+
+		The \package{astropy.io.fits} sub-package now provides a command line
+		script for inspecting the header(s) of a FITS file.  Running
+		\texttt{fitsheader file.fits} in a terminal prints the header
+		information to the screen in a human-readable format. Run
+		\texttt{fitsheader --help} to see the full usage documentation.
 
 	\item [FITS: lazy loading (v1.3)]
+
 		The \package{astropy.io.fits} sub-package now supports \emph{lazy
@@
 	\item [Misc: YAML serialization (v1.3)]
-		The new \astropy{astropy.io.misc.yaml} module
-		allows converting astropy objects into a standard YAML format.
+
+		The new \package{astropy.io.misc.yaml} module allows converting
+		astropy objects into a standard YAML format.
 

### 2017-10-05 make_coord_graph.py
add coordinates graph figure

@@ -1,0 +1,36 @@
+import re
+from astropy.coordinates import frame_transform_graph
+from astropy.coordinates.transformations import trans_to_color
+from graphviz import Source
+
+legend = """rankdir=LR
+node [shape=plaintext margin=0]
+  subgraph cluster_01 {
+    key [label=<<table border="0" cellpadding="2" cellspacing="0" cellborder="0">
+      <tr><td align="right" port="i1">AffineTransform</td></tr>
+      <tr><td align="right" port="i2">FunctionTransformWithFiniteDifference</td></tr>
+      <tr><td align="right" port="i3">StaticMatrixTransform</td></tr>
+      <tr><td align="right" port="i4">DynamicMatrixTransform</td></tr>
+      </table>>]
+    key2 [label=<<table border="0" cellpadding="2" cellspacing="0" cellborder="0">
+      <tr><td port="i1">&nbsp;</td></tr>
+      <tr><td port="i2">&nbsp;</td></tr>
+      <tr><td port="i3">&nbsp;</td></tr>
+      <tr><td port="i4">&nbsp;</td></tr>
+      </table>>]
+    key:i1:e -> key2:i1:w [color="#555555"]
+    key:i2:e -> key2:i2:w [color="#d95f02"]
+    key:i3:e -> key2:i3:w [color="#7570b3"]
+    key:i4:e -> key2:i4:w [color="#1b9e77"]
+  }
+"""
+
+raw_src = frame_transform_graph.to_dot_graph(priorities=False)
+
+# Remove the short names / aliases
+pattr = re.compile(r'\\n`[a-z0-9]+`')
+raw_src = pattr.sub('', raw_src)
+raw_src = raw_src[:-1] + '\nsplines=true\n' + legend + '}'
+
+dot = Source(raw_src, engine='neato')
+dot.render('coordinates_graph', cleanup=True)

### 2017-10-05 main.tex

@@
     \item[Solar System Ephemerides]
-    \comment{EJT}{APW, you may want to give this item a quick read-over?  If it looks good just delete this comment}
-    Also new is support for computing ephemeris of major solar system bodies and outputting the resulting positions as coordinate objects.
-    These ephemerides can be computed either using analytic approximations from ERFA (which requires no data download beyond the source code), or from downloaded JPL ephemerides (which requires the \package{jplephem}\footnote{\url{https://github.com/brandon-rhodes/python-jplephem}} optional dependency).
-    The \texttt{get\_body} and \texttt{get\_body\_barycentric} functions provide the gateway to this functionality, yielding \texttt{SkyCoord} objects given a specific body and choice of ephemeris source.
+    Also new is support for computing ephemerides of major solar system bodies
+    and outputting the resulting positions as coordinate objects.
+    These ephemerides can be computed either using analytic approximations from
+    ERFA, or from downloaded JPL ephemerides (the latter requires the \package{j
+    plephem}\footnote{\url{https://github.com/brandon-rhodes/python-jplephem}}
+    optional dependency and an internet connection).
+    The \texttt{get\_body} and \texttt{get\_body\_barycentric} functions provide
+    the gateway to this functionality, yielding \texttt{SkyCoord} objects given
+    a specific body and choice of ephemeris source.
 

### 2017-10-05 main.tex
Fixing spacings

@@
 % write it up
-
+%
+\par A major part of the \astropy{} project is the concept of “Affiliated
+Packages”. An affiliated package is an astronomy-related Python package that
+is not part of the \astropypkg{} core package, but has requested to be
+included as part of the astropy project’s community. These packages support
+the goals and vision of \astropy{} of improving code reuse,
+interoperability, and embracing good coding practices such as testing and
+thorough documentation. \astropypkg{} currently supports both versions of
+Python 2.7+ and Python 3.x, affiliated packages are strongly encouraged to
+support at least Python 3.x.
+%
+\par Affiliated packages contain functionality that is more specialized, or
+have license incompatibility, or have enough external dependencies (e.g. GUI
+libraries) that limit their integration possibility into the core and thus
+they are more suitable to be separate packages. In general we hope that
+becoming an affiliated package is seen as a good way for new and existing
+packages to gain exposure.
+%
+% TODO: write about the process of becoming affiliated, and project packages
+%
 \subsection{Mixin}

### 2017-10-05 main.tex
Converted comment questions to inlinecomments

@@
 \par A major part of the \astropy{} project is the concept of “Affiliated
-Packages”. An affiliated package is an astronomy-related Python package that
+Packages”. An affiliated package is an astronomy-related \python{} package that
 is not part of the \astropypkg{} core package, but has requested to be
@@
 thorough documentation. \astropypkg{} currently supports both versions of
-Python 2.7+ and Python 3.x, affiliated packages are strongly encouraged to
-support at least Python 3.x.
+\python\ 2.7+ and \python\ 3.4, affiliated packages are strongly encouraged to
+support at least \python\ 3.x.
 %
@@
 % Brigitta can writes this up if there's no other taker
-%\inlinecomment{EJT}{Need to create a Zenodo DOI for ERFA and then cite it here.}
-% - reference APE2 for versioning and APE10 for dropping python2 support
-% - shall we maybe refer to the release calendar, too?
-% - should we mention that v3.0 is the exception to the version numbering
-%   scheme we use by not being 2.1?
+\inlinecomment{BMS: TODO}{reference APE2 for versioning and APE10 for dropping python2 support}
+\inlinecomment{BMS}{shall we maybe refer to the release calendar, too?}
+\inlinecomment{BMS}{should we mention that v3.0 is the exception to the
+  version numbering scheme we use by not being 2.1?}
+%
 \par The general scheme for the releases and version numbering that the core
@@
 \label{sec:infrastructure}
-% - should we use links to the appropriate github repo?
-% - should we describe astropy-helpers even though it's future is unsure?
+\inlinecomment{BMS}{should we use links to the appropriate github repo?}
+\inlinecomment{BMS}{should we describe astropy-helpers even though it's future is unsure?}
 %
@@
 % Kelle, Adrian
-% - would astropy learn mature enough to described in the paper, or maybe it should go as a subsection for the next, future of astropy section?
+\inlinecomment{BMS}{would astropy learn mature enough to described in the paper, or maybe it should go as a subsection for the next, future of astropy section?}
 

### 2017-10-06 main.tex
Update on Overleaf.
astropy package is lower case

@@
 \newcommand{\astropy}{Astropy}
-\newcommand{\astropypkg}{\package{Astropy}}
+\newcommand{\astropypkg}{\package{astropy}}
 
@@
 
+\subsection{Support of Astropy}
+
+% This section should be a straight forward/factual description of the current
+% funding and support provided to astropy with the purpose of explaining the 
+% current structure to the community
+
 %\subsection{Difficulty of reversing design choices}
@@
 
-The \texttt{astropy.units} subpackage provides ...
+The \package{astropy.units} subpackage provides ...
 
@@
     \item[Logarithmic units and magnitudes] ...
-    \item[Interaction with \texttt{numpy} arrays] ...
+    \item[Interaction with \package{numpy} arrays] ...
 \end{description}
@@
 \begin{equation}
-y = \frac{x - v_{vmin}}{v_{max} − v_{min}}
+y = \frac{x - v_{vmin}}{v_{max} - v_{min}}
 \end{equation}
@@
 % Brigitta
-\texttt{ci-helpers} is a collection of scripts that empowers package
+\package{ci-helpers} is a collection of scripts that empowers package
 maintainers to control their testing set up and installation process for
@@
 \label{sec:future}
+\subsection{Roadmap for \python\ 3 only support}
 

### 2017-10-17 main.tex
Update on Overleaf.

@@
 \documentclass[modern]{aastex61}
-
+\usepackage{xspace}
 \newcommand{\escapecmd}[1]{\texttt{\detokenize{#1}}}
@@
 % Packages / projects / programming - for consistency!
-\newcommand{\package}[1]{\texttt{#1}}
-\newcommand{\github}{\package{GitHub}}
-\newcommand{\python}{\package{Python}}
-\newcommand{\astropy}{Astropy}
-\newcommand{\astropypkg}{\package{astropy}}
+\newcommand{\package}[1]{\texttt{#1}\xspace}
+\newcommand{\github}{\package{GitHub}\xspace}
+\newcommand{\python}{\package{Python}\xspace}
+\newcommand{\astropy}{Astropy\xspace}
+\newcommand{\astropypkg}{\package{astropy}\xspace}
 
 % For consistency:
-\newcommand{\sectionname}{Section}
-\renewcommand{\figurename}{Figure}
-\newcommand{\equationname}{Equation}
-\renewcommand{\tablename}{Table}
+\newcommand{\sectionname}{Section\xspace}
+\renewcommand{\figurename}{Figure\xspace}
+\newcommand{\equationname}{Equation\xspace}
+\renewcommand{\tablename}{Table\xspace}
 
@@
 \usepackage[colorinlistoftodos]{todonotes}
-\newcommand{\inlinecomment}[2]{\todo[inline]{#1: #2}}
-\newcommand{\comment}[2]{\todo{#1: #2}}
+\newcommand{\inlinecomment}[2]{\todo[inline]{#1: #2}\xspace}
+\newcommand{\comment}[2]{\todo{#1: #2}\xspace}
 
@@
 % free to modify!
-The \astropy\ project supports and fosters the development of open-source
-\python\ packages that provide commonly-needed functionality to the astronomical
+The \astropy project supports and fosters the development of open-source
+\python packages that provide commonly-needed functionality to the astronomical
 community.
-A key element of the project is the \astropy\ core package, which serves as the
+A key element of the project is the \astropy core package, which serves as the
 foundation for more specialized projects and packages.
-In this article, we provide an overview of the organization of the \astropy\
+In this article, we provide an overview of the organization of the \astropy
 project and summarize key features in the core package as of the recent major
@@
 We conclude with a future outlook of planned new features and directions for the
-broader \astropy\ project.
+broader \astropy project.
 \end{abstract}
@@
    \item The goal is to produce a brief and informative paper that covers major
-        \astropy\ principles not mentioned in the first paper, the core v2.0
-        package, and infrastructure in \astropy\ project to support development
+        \astropy principles not mentioned in the first paper, the core v2.0
+        package, and infrastructure in \astropy project to support development
         in \python.
@@
 software packages are (or at least were) supported by large
-institutions, e.g.\ IRAF \citep[developed at NOAO,][]{IRAF}, MIDAS
+institutions, e.g.~IRAF \citep[developed at NOAO,][]{IRAF}, MIDAS
 \citep[developed at ESO,][]{MIDAS}, or ds9 \citep[developed at
@@
 task. Another example of such a common task is dealing with different
-astronomical coordinate systems. The \astropy\ project aims to provide a
-library of core astronomical functionality in the \python\ programming
+astronomical coordinate systems. The \astropy project aims to provide a
+library of core astronomical functionality in the \python programming
 language.
@@
 continuously test the code, build and provide documentation, and
-supply downloadable packages. The \astropy\ project aims to develop and
+supply downloadable packages. The \astropy project aims to develop and
 provide high quality code and documentation according to the best
@@
 
-The first public release of the \astropy\ package is described in
-\cite{astropy}. Since then, the \astropy\ package has been
+The first public release of the \astropy package is described in
+\cite{astropy}. Since then, the \astropy package has been
 used in hundreds of projects, and the scope of the package as grown
@@
 contributing to the project has grown tremendously and an ecosystem
-of packages supporting or affiliated with the \astropy\ core has
+of packages supporting or affiliated with the \astropy core has
 developed. In this paper, we describe the current status of the
-\astropy\ community, the \astropy\ core package, and the \astropy\
+\astropy community, the \astropy core package, and the \astropy\
 ecosystem.
 
-We start by describing the way the \astropy\ project works and is
+We start by describing the way the \astropy project works and is
 organized in \sectionname~\ref{sec:concepts}.  The project develops a core
-package called \astropypkg\ (\sectionname~\ref{sec:core}) and several
+package called \astropypkg (\sectionname~\ref{sec:core}) and several
 separate packages that help setting up the infrastructure for testing,
-documentation etc.\ (\sectionname~\ref{sec:infrastructure}). In
+documentation etc.~(\sectionname~\ref{sec:infrastructure}). In
 \sectionname~\ref{sec:learning} we give an overview of the wealth of
-resources created to teach new users the use of the \astropy\ packages
+resources created to teach new users the use of the \astropy packages
 and how to contribute to the community. We end with a short vision for
-the future of \astropy\ in \sectionname~\ref{sec:future}.
+the future of \astropy in \sectionname~\ref{sec:future}.
 
@@
 %draft by hamogu
-Central to the success of \astropy\ is an open environment where
+Central to the success of \astropy is an open environment where
 anybody can contribute to the code by opening a so-called ``pull
@@
 implemented by different people with different programming styles and
-interfaces. Thus, \astropy\ has a mechanism to more formally propose
-changes to the code management (e.g.\ the release cycle) or to plan
+interfaces. Thus, \astropy has a mechanism to more formally propose
+changes to the code management (e.g.~the release cycle) or to plan
 out major new features. This mechanism is called ``Astropy Proposal
@@
 point. In cases where consensus cannot be reached, the
-\astropy\ coordination committee can decide to close the discussion and
+\astropy coordination committee can decide to close the discussion and
 make an executive decision based on the community input on the APE in
 question. APEs are modeled after the ``Python Enhancement Proposals''
-(PEP) and guide the development of the \python\ programming language.
+(PEP) and guide the development of the \python programming language.
 
@@
 %
-\par A major part of the \astropy{} project is the concept of “Affiliated
-Packages”. An affiliated package is an astronomy-related \python{} package that
-is not part of the \astropypkg{} core package, but has requested to be
+\par A major part of the \astropy project is the concept of “Affiliated
+Packages”. An affiliated package is an astronomy-related \python package that
+is not part of the \astropypkg core package, but has requested to be
 included as part of the astropy project’s community. These packages support
-the goals and vision of \astropy{} of improving code reuse,
+the goals and vision of \astropy of improving code reuse,
 interoperability, and embracing good coding practices such as testing and
-thorough documentation. \astropypkg{} currently supports both versions of
-\python\ 2.7+ and \python\ 3.4, affiliated packages are strongly encouraged to
-support at least \python\ 3.x.
+thorough documentation. \astropypkg currently supports both versions of
+\python~2.7 and \python~3.4+, affiliated packages are strongly encouraged to
+support at least \python~3.x.
 %
@@
 Hence, programs and functions expected to be fed parameters in particular units, as (hopefully) stated in their documentation.
-In \astropypkg\ 0.4, therefore, unit and quantity support was still somewhat spotty, but this has changed greatly.
+In \astropypkg~0.4, therefore, unit and quantity support was still somewhat spotty, but this has changed greatly.
 One of the riskiest classes was angles, where both degrees and radians were ``obvious'' default units to some.
 As a consequence, quantities are most fully integrated in the coordinates module (\sectionname~\ref{sec:coordinates}).
-In \astropypkg\ 2.0, one can also opt in to use quantities fully in tables, by using the {\tt QTable} class (see \sectionname~\ref{sec:table}).
+In \astropypkg~2.0, one can also opt in to use quantities fully in tables, by using the {\tt QTable} class (see \sectionname~\ref{sec:table}).
 As a result, units in FITS tables are also well-supported.
@@
 \par The general scheme for the releases and version numbering that the core
-package has adopted if the following. \astropypkg\ has new feature releases every
+package has adopted if the following. \astropypkg has new feature releases every
 6 months, and between feature releases additional bugfix releases that
@@
 %
-\par The version numbering of \astropypkg\ reflects on the release scheme
+\par The version numbering of \astropypkg reflects on the release scheme
 described above. The core package uses the form x.y.z, where x is advances
@@
 
-The \astropy\ project aims to provide \python-based packages for all tasks that
+The \astropy project aims to provide \python-based packages for all tasks that
 are commonly needed in a large subset of the astronomical community.
-At the foundation is the \astropypkg\ core package, which provides general
+At the foundation is the \astropypkg core package, which provides general
 functionality (e.g., coordinate transformations) or base classes for other
@@
 \inlinecomment{EJT}{Need to create a Zenodo DOI for ERFA and then cite it here.}
+% * <tjenness@lsst.org> 2017-10-16T15:53:18.375Z:
+% 
+% I think it should mention that ERFA is related to SOFA (and cite SOFA).
+% 
+% ^.
 A key concept behind the design of this subpackage is that coordinate
@@
     \item[Local Earth coordinate frames] In addition to representing celestial
-    coordinates, \astropypkg\ now supports specifying positions on the Earth in
+    coordinates, \astropypkg now supports specifying positions on the Earth in
     a number of different geocentric systems with the \texttt{EarthLocation}
     class.
-    With this, \astropypkg\ now supports Earth-location-specific coordinate
+    With this, \astropypkg now supports Earth-location-specific coordinate
     systems such as the altitude-azimuth (\texttt{AltAz}) or horizontal system.
@@
     With this new functionality, many of the common tasks associated with
-    observation planning can now be completed with \astropypkg\ or the
+    observation planning can now be completed with \astropypkg or the
     \astropy-affiliated package \package{astroplan}. \inlinecomment{APW}{TODO: cite zenodo entry for astroplan?}.
@@
 		astropy objects into a standard YAML format. 
+        This can be used beyond \texttt{astropy.io.misc.yaml}: for example, to
+        serialize the metadata of tables before saving to other formats like 
+        HDF5.
 
@@
 
-\astropypkg\ implements `normalized convolution' \citep[e.g.,][]{Knutsson1993}, which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.
+\astropypkg implements `normalized convolution' \citep[e.g.,][]{Knutsson1993}, which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.
 In version $<=1.3$, the direct convolution and fft convolution approaches were not consistent, with fft convolution implementing normalized convolution and direct convolution implementing a different approach.
@@
 \includegraphics[width=\textwidth]{convolution_example.png}
-An example showing different modes of convolution available in the \python\ ecosystem.
+An example showing different modes of convolution available in the \python ecosystem.
 The red x's mark pixels that are set to NaN in the original data (a).
@@
 
-The \astropypkg\ \package{stats} package provides
+The \astropypkg \package{stats} package provides
 statistical tools that are useful for or specific to
@@
 % Brigitta may write this up if there is no other takers
-\par \astropy\ provides a template package that any \python\ package is welcome to
+\par \astropy provides a template package that any \python package is welcome to
 use (many affiliated packages do so). The template contains a ready-to-go
@@
 variables. While the current development is mostly driven by the needs of
-the \astropy\ ecosystem, the actual usage of this package is extremely
+the \astropy ecosystem, the actual usage of this package is extremely
 widespread. Currently we support setups for TravisCI and AppveyorCI.
@@
 \label{sec:future}
-\subsection{Roadmap for \python\ 3 only support}
+\subsection{Roadmap for \python 3 only support}
 
@@
 Who to thank?  numfocus,
+
+CI services? GitHub?
 

### 2017-10-17 main.tex
add frame transform graph figure

@@
 coordinate data when a \texttt{Frame} object is created.
+\figurename~\ref{fig:frame-transform-graph} shows the network of possible
+reference frame transformations as currently implemented in
+\texttt{astropy.coordinates}.
+Custom, user-implemented \texttt{Frame} classes that define transformations to
+any reference frame in this graph can then be transformed to any of the other
+connected frames.
+
+\begin{figure}
+\includegraphics[width=\textwidth]{coordinates_graph.pdf}
+The full graph of possible reference frame transformations implemented in
+\texttt{astropy.coordinates}.
+\label{fig:frame-transform-graph}
+\end{figure}
 
@@
 Finally, panel (d) shows \astropypkg's convolution behavior, where the missing pixels are replaced with values interpolated from their surroundings using the convolution kernel.
+\label{fig:convolution-example}
 \end{figure}

### 2017-10-17 main.tex
Update on Overleaf.

@@
 We then describe the project infrastructure designed to facilitate and support
-development for a broader ecosystem of interoperable packages.
+development for a broader ecosystem of inter-operable packages.
 We conclude with a future outlook of planned new features and directions for the
@@
 % Adrian, Erik
-\inlinecomment{APW}{Do we want to put in a PDF of the transform graph?}
-\inlinecomment{EJT}{I think so?  It looks pretty slick...}
 

### 2017-10-17 main.tex
fix fig captions

--- 2017-10-17 main.tex
@@
 \includegraphics[width=\textwidth]{coordinates_graph.pdf}
+\caption{
     The full graph of possible reference frame transformations implemented in
@@
     \label{fig:frame-transform-graph}
+}
 \end{figure}
@@
 \includegraphics[width=\textwidth]{convolution_example.png}
-An example showing different modes of convolution available in the \python ecosystem.
-The red x's mark pixels that are set to NaN in the original data (a).
-If the data are convolved with a Gaussian kernel on a 9x9 grid using scipy's direct convolution (b), any pixel within range of the original NaN pixels is also set to NaN.
-Panel (c) shows what happens if the NaNs are set to zero first: the originally NaN regions are depressed relative to their surroundings.
-Finally, panel (d) shows \astropypkg's convolution behavior, where the missing pixels are replaced with values interpolated from their surroundings using the convolution kernel.
+\caption{%
+    An example showing different modes of convolution available in the \python
+    ecosystem.  The red x's mark pixels that are set to NaN in the original data
+    (a).  If the data are convolved with a Gaussian kernel on a 9x9 grid using
+    scipy's direct convolution (b), any pixel within range of the original NaN
+    pixels is also set to NaN.  Panel (c) shows what happens if the NaNs are set
+    to zero first: the originally NaN regions are depressed relative to their
+    surroundings.  Finally, panel (d) shows \astropypkg's convolution behavior,
+    where the missing pixels are replaced with values interpolated from their
+    surroundings using the convolution kernel.
     \label{fig:convolution-example}
+}
 \end{figure}

### 2017-10-17 main.tex
Update on Overleaf.

@@
 \label{sec:modeling}
-% Nadia
-% Lim blackbody
+% The whole modeling submodule was missing from the previous paper, so everything really, including compound models, unit support etc.
+% Nadia, Lim
 % Tom R. -- unit support
-The whole modeling submodule was missing from the previous paper, so everything really, including compound models, unit support etc.
+\subsubsection{Overview}
+The \package{astropy.modeling} subpackage provides a framework for representing analytical models and performing model evaluation and fitting.
+Models and fitters are independent of each other, a model can be fit with different fitters and new fitters can be added without changing existing models.
+The framework is designed to be flexible and easily extensible.
+The goal is to have a rich set of models but also make it easy to create new ones if necessary.
+The modeling framework is used in a variety of data analysis tools and is the basis for the Generalized World Coordinate System (GWCS) package (link).
+The unit support in models and fitters make it a unique package for working with astrophysical models.
+
+\subsubsection{Single Model Definition and Evaluation}
+Most models are defined by parameters and maintain an ordered list of parameter names, \texttt{Model.param\_names}.
+A model is instantiated by passing in values (scalars or arrays) for its parameters.
+A parameter is a descriptor that provides a proxy for the value and stores additional information -- default value, default unit, and parameter constraints.
+The value and constraints can be updated by assignment.
+Supported parameter constraints include \texttt{fixed}, and \texttt{tied} parameters, and \texttt{bounds} on parameter values.
+Most models have a fixed parameter set but for some (e.g., polynomials), the number of parameters is defined by another argument (e.g., degree-of-freedom in the case of polynomials).
+Parameters support arithmetic operations and are combined with the inputs during evaluation using the numpy broadcasting rules.
+A model is evaluated by calling it as a function and passing the inputs in as arguments.
+
+Models have \texttt{Model.inverse} property, which returns the analytical inverse, if available, or raises an exception otherwise.
+This is a settable property; i.e., a model instance can be assigned as inverse to another model.
+For example, a polynomial model can be assigned as an inverse for another polynomial model.
+
+Another useful settable property of models is \texttt{Model.bounding\_box}.
+It defines the limits over which the model is significant.
+This greatly improves the efficiency of evaluation when the input range is much larger than the characteristic width of the model itself.
+
+\subsubsection{Model Sets}
+
+\package{astropy.modeling} provides an efficient way to instantiate the same type of model with many different sets of parameter values by passing the \texttt{n\_models=k} keyword, where k is the number of models to instantiate, and providing the values for each parameter as an iterable of size k.
+This creates a model set which is efficiently evaluated.
+Model sets are most useful for efficiently fitting multiple linear models of the same kind.
+
+\subsubsection{Compound Models}
+Single models can be combined using arithmetic expressions.
+The result is also a model, which can further be combined with other models.
+Modeling supports arithmetic (+, -, *, /, and **), join $\&$, and composition $|$ operators.
+The rules for combining models involve matching their inputs and outputs.
+For example, the composition operator, $|$, requires the number of outputs of the left model to be equal to the number of inputs of the right one.
+For the join operator, the total number of inputs must equal the sum of number of inputs of both the left and the right models.
+For all arithmetic operators, the left and the right models must have the same number of inputs and outputs.
+
+\subsubsection{Fitting Models to Data}
+
+\package{astropy.modeling} provides several fitters which are wrappers around some of the \texttt{numpy} and \texttt{scipy.optimize} functions and provide supports for constraints.
+They take a model as input and return a copy of the model with the fitted parameters.
+The goal is to make it easy to extend the fitting framework and create new fitters.
+The optimizers available in astropy 2.0 are Levenberg-Marquardt, Simplex, SLSQP, and LinearLSQFitter (which is based on \texttt{numpy.linalg} that provides exact solution for linear models).
+
+Modeling also supports a plugin system for fitters, which allows using the astropy models with external fitters.
+An example of this is SABA (link), which is a bridge between Sherpa (link) and astropy.modeling, to bring the Sherpa fitters into astropy.
+
+\subsubsection{Creating New Models}
+
+New model classes can be created in two ways:
+\begin{itemize}
+   \item The simplest way is to use the \texttt{custom\_model} decorator in modeling with a user defined function which takes the inputs and model parameters as arguments.
+   \item It is also possible to subclass the \texttt{Model} base class and create an arbitrary complex custom model.
+\end{itemize}
+
+\subsubsection{Unit Support}
+
+% Tom R: unit support description goes here and the sentence below is to be folded in with it.
+
+Unit support in \texttt{modeling} has enabled implementation of the blackbody \citep{Rybicki1979} model, which requires units to make sense.
+It is available in \package{astropy} 2.0 as \texttt{BlackBody1D}.
 
@@
 \subsubsection{WCSAxes}
-% Tom R.
+
+% Tom R. will work on this on Oct 18 and/or 19.
 
@@
 \inlinecomment{BMS}{should we use links to the appropriate github repo?}
+\inlinecomment{PLL}{IMHO a list of GitHub repo links for affil. pkgs. should be in appendix, if included.}
 \inlinecomment{BMS}{should we describe astropy-helpers even though it's future is unsure?}
@@
 the \astropy ecosystem, the actual usage of this package is extremely
-widespread. Currently we support setups for TravisCI and AppveyorCI.
+widespread. Currently we support setups for Travis CI and Appveyor CI.
 %
 \subsection{sphinx extensions}
-% Tom R
+
+% Tom R will work on this on Oct 18 and/or 19
 
@@
 \label{sec:future}
+\inlinecomment{PLL}{In addition to PY3, add some killer features that we plan to implement for 3.0 and beyond?}
 \subsection{Roadmap for \python 3 only support}

### 2017-10-18 main.tex
erfa cite

@@
 Astronomy (ERFA) \texttt{C} library for some of the critical underlying
-transformation machinery.
-\inlinecomment{EJT}{Need to create a Zenodo DOI for ERFA and then cite it here.}
-% * <tjenness@lsst.org> 2017-10-16T15:53:18.375Z:
-%
-% I think it should mention that ERFA is related to SOFA (and cite SOFA).
-%
-% ^.
+transformation machinery \citep{erfa}, which is based on the Standards Of 
+Fundamental Astronomy (SOFA) effort \citep{sofa}.
+
 A key concept behind the design of this subpackage is that coordinate
@@
 
-\inlinecomment{EJT}{ERFA is likely to be referenced somewhere here. should cite the DOI as mentioned in the above ERFA refernce once it exists}
+Uses ERFA \citep{erfa}...
 

### 2017-10-18 main.tex
typo fix
opening quotes

@@
 a platform \footnote{\url{https://github.com/astropy/astropy-APEs}}
-open to the public. In previous APEs a community concensus emerged and
+open to the public. In previous APEs a community consensus emerged and
 APEs are accepted and become the basis for future work at this
@@
 %
-\par A major part of the \astropy project is the concept of “Affiliated
-Packages”. An affiliated package is an astronomy-related \python package that
+\par A major part of the \astropy project is the concept of ``Affiliated
+Packages''. An affiliated package is an astronomy-related \python package that
 is not part of the \astropypkg core package, but has requested to be

### 2017-10-18 main.tex
gwcs link

@@
 6 months, and between feature releases additional bugfix releases that
-contain only bugfixes but no new features. The timing of
+contain only bugfixes but no new features.
+% The timing of
 %
@@
 \subsubsection{Overview}
-The \package{astropy.modeling} subpackage provides a framework for representing analytical models and performing model evaluation and fitting.
-Models and fitters are independent of each other, a model can be fit with different fitters and new fitters can be added without changing existing models.
-The framework is designed to be flexible and easily extensible.
-The goal is to have a rich set of models but also make it easy to create new ones if necessary.
-The modeling framework is used in a variety of data analysis tools and is the basis for the Generalized World Coordinate System (GWCS) package (link).
-The unit support in models and fitters make it a unique package for working with astrophysical models.
+The \package{astropy.modeling} subpackage provides a framework for representing
+analytical models and performing model evaluation and fitting. Models and
+fitters are independent of each other, a model can be fit with different
+fitters and new fitters can be added without changing existing models. The
+framework is designed to be flexible and easily extensible. The goal is to have
+a rich set of models but also make it easy to create new ones if necessary. The
+modeling framework is used in a variety of data analysis tools and is the basis
+for the Generalized World Coordinate System (GWCS)
+package\footnote{\url{https://github.com/spacetelescope/gwcs}}. The
+unit support in models and fitters make it a unique package for working with
+astrophysical models.
 

### 2017-10-18 main.tex
typo

@@
 The \package{visualization} package provides functionality that can be helpful when visualizing data.
-This includes a framework for plotting astronomical images with coordinates with Matplotlib (previously the standalone \package{wcsaxes} package), functionality related to image normaliation (including both scaling and stretching), smart histogram plotting, RGB color image creation from separate images, and custom plotting styles for Matplotlib.
+This includes a framework for plotting astronomical images with coordinates with Matplotlib (previously the standalone \package{wcsaxes} package), functionality related to image normalization (including both scaling and stretching), smart histogram plotting, RGB color image creation from separate images, and custom plotting styles for Matplotlib.
 

### 2017-10-19 main.tex
Update on Overleaf.

@@
 
-\subsubsection{Sigma Clipping}
-
+{\bf Sigma Clipping:}
 Sigma clipping provides a fast method to identify outliers in a distribution.
@@
 
-\subsubsection{Median Absolute Deviation}
-
+{\bf Median Absolute Deviation:}
 The median abosolute deviation (MAD) is a measure of the spread of a distribution and is defined as median(abs(a - median(a))).
@@
 
-\subsubsection{Biweight Estimators}
-
+{\bf Biweight Estimators: }
 A set of functions are included in the \package{stats} package that use the biweight formalism.
@@
 
-\subsubsection{Circular Statistics}
-%steve
+{\bf Circular Statistics: }
+A set of circular statistical estimators based on [XXX] are implemented in the \package{stats} package.
+These functions provide measurements of the circular mean, variance, and moment.
+For all of these functions, they work with both numpy.ndarrays (assumed to be in radians) and Quantity objects.
+In addition, the package includes tests for Raleigh Test [XXX], vtest [XXX], and a function to compute the maximum likelihood estimator for the parameters of the von Mises distribution [XXX].
+
 \subsubsection{Lomb-Scargle Periodograms}
 %jake
-\subsubsection{Ripley's K Function Estimators}
-%ze
+
 \subsubsection{Histogram Binning}

### 2017-10-20 main.tex
small fix and answer some inline comments

@@
 software packages are (or at least were) supported by large
-institutions, e.g.~IRAF \citep[developed at NOAO,][]{IRAF}, MIDAS
+institutions, e.g.\ IRAF \citep[developed at NOAO,][]{IRAF}, MIDAS
 \citep[developed at ESO,][]{MIDAS}, or ds9 \citep[developed at
@@
 %
-\par A major part of the \astropy project is the concept of ``Affiliated
-Packages''. An affiliated package is an astronomy-related \python package that
-is not part of the \astropypkg core package, but has requested to be
-included as part of the astropy project’s community. These packages support
-the goals and vision of \astropy of improving code reuse,
-interoperability, and embracing good coding practices such as testing and
-thorough documentation. \astropypkg currently supports both versions of
-\python~2.7 and \python~3.4+, affiliated packages are strongly encouraged to
-support at least \python~3.x.
+\par A major part of the \astropy project is the concept of
+``Affiliated Packages''. An affiliated package is an astronomy-related
+\python package that is not part of the \astropypkg core package, but
+has requested to be included as part of the astropy project’s
+community. These packages support the goals and vision of \astropy of
+improving code reuse, interoperability, and embracing good coding
+practices such as testing and thorough documentation. \astropypkg
+version 2.0 supports \python~2.7 and \python~3.4+, affiliated packages
+are strongly encouraged to support at least \python~3.x.
 %
@@
 \inlinecomment{BMS}{shall we maybe refer to the release calendar, too?}
+\inlinecomment{hamogu}{I don't think that's necessary. These details are in the docs, but not too important for a general paper.}
 \inlinecomment{BMS}{should we mention that v3.0 is the exception to the
   version numbering scheme we use by not being 2.1?}
+\inlinecomment{hamogu}{No. This is a genral paper, those are details that will be unimportant very soon. }
 %

### 2017-10-20 main.tex
fix

@@
 anybody can contribute to the code by opening a so-called ``pull
-request'' with a new code contribution on an publically available
+request'' with a new code contribution on a publically available
 website\footnote{\url{https://github.com/astropy/astropy}}; this

### 2017-10-20 main.tex
typo

@@
 {\bf Median Absolute Deviation:}
-The median abosolute deviation (MAD) is a measure of the spread of a distribution and is defined as median(abs(a - median(a))).
+The median absolute deviation (MAD) is a measure of the spread of a distribution and is defined as median(abs(a - median(a))).
 For a normal distribution, the MAD is related to the standard deviation by a factor of 1.4826, and a convenience function is available to apply the conversion.

### 2017-10-20 main.tex
Update on Overleaf.

@@
 % free to modify!
-The \astropy project supports and fosters the development of open-source
+The \astropy project supports and fosters the development of open-source and open-development
 \python packages that provide commonly-needed functionality to the astronomical
@@
 website\footnote{\url{https://github.com/astropy/astropy}}; this
-request is then reviewed by a maintainer responsible for the specific
+request is then reviewed by at least one of the maintainers responsible for the specific
 sub-package and possibly merged into the main code base. Most bug
@@
 %
-\par A major part of the \astropy project is the concept of
+\par A major part of the \astropy~project is the concept of
 ``Affiliated Packages''. An affiliated package is an astronomy-related
-\python package that is not part of the \astropypkg core package, but
-has requested to be included as part of the astropy project’s
-community. These packages support the goals and vision of \astropy of
+\python~package that is not part of the \astropypkg~core package, but
+has requested to be included as part of the \astropy project's
+community. These packages support the goals and vision of \astropy~of
 improving code reuse, interoperability, and embracing good coding
-practices such as testing and thorough documentation. \astropypkg
+practices such as testing and thorough documentation. \astropypkg{}
 version 2.0 supports \python~2.7 and \python~3.4+, affiliated packages
@@
 libraries) that limit their integration possibility into the core and thus
-they are more suitable to be separate packages. In general we hope that
-becoming an affiliated package is seen as a good way for new and existing
-packages to gain exposure.
+they are more suitable to be separate packages. Starting as an affiliate 
+package is also seen as a good strategy for functionality that is aimed for
+the \astropypkg~core but is currently undergo rapid development and can 
+benefit from a different release cycle while stabilizing its API. 
 %
-% TODO: write about the process of becoming affiliated, and project packages
+\par In general we hope that becoming an affiliated package is seen as 
+a good way for new and existing packages to gain exposure.
+%
+\inlinecomment{BMS}{TODO: write about the process of becoming affiliated, and project packages}
 %
@@
 % just here for completeness at the moment
-
+\inlinecomment{BMS}{I suggest to order the subsection lexicographically as reading the draft the current order seemed very random (unlike at the docs page where they the grouping logic is obvious)}
 \subsection{Units and quantities}

### 2017-10-20 main.tex
Update on Overleaf.

@@
 At the foundation is the \astropypkg core package, which provides general
-functionality (e.g., coordinate transformations) or base classes for other
+functionality (e.g., coordinate transformations, reading and writing astronomical
+files) or base classes for other
 packages to utilize for a common interface (e.g., \texttt{NDData}).
@@
     observation planning can now be completed with \astropypkg or the
-    \astropy-affiliated package \package{astroplan}. \inlinecomment{APW}{TODO: cite zenodo entry for astroplan?}.
+    \astropy-affiliated package \package{astroplan}\citep{astroplan_AAS}. 
+    \inlinecomment{APW}{TODO: cite zenodo entry for astroplan?}
+    \inlinecomment{BMS}{better to cite the submitted or soon to be submitted paper}
 

### 2017-10-20 main.tex
Update on Overleaf.

@@
 
+\inlinecomment{BMS}{The itemizations below look very weird being boldface under a much less prominent subsection title. would it be nicer in the final version if we leave it as is in the draft?}
+
 % \subsection{Analytic Functions}
@@
     \inlinecomment{APW}{TODO: cite zenodo entry for astroplan?}
-    \inlinecomment{BMS}{better to cite the submitted or soon to be submitted paper}
+    \inlinecomment{BMS}{better to cite the submitted or soon to be submitted paper, I made a placeholder for it.}
 
@@
 
-Q: does it make sense to refer forward to FITS support, even though it is 3.0?
+\inlinecomment{SCO}{Q: does it make sense to refer forward to FITS support, even though it is 3.0?}
+\inlinecomment{BMS}{what about moving it into the future section below?}
 
@@
 
-Check when it was added (0.3?). Overview of the supported formats (ASCII,
+TODO: Check when it was added (0.3?). Overview of the supported formats (ASCII,
 FITS, votable, HTML, JSViewer/Datatables).
@@
 \inlinecomment{SCO}{One subsection per format (if enough new features) ?}
+\inlinecomment{BMS}{Do we really need to mention the old version numbers in the list below when a feature was added?}
 
@@
 \end{description}
+
+\inlinecomment{BMS}{Maybe move the command line tools into a separate subsection to highlight them (even though we mostly only have fits related scripts)?
+They are supposed to be used more frequently by individual users.}
 

### 2017-10-20 main.tex
Update on Overleaf.

@@
 
+Several classes are provided for determining intervals and for normalizing values in this interval to the [0:1] range.
 In addition, classes are provided in order to identify lower and upper limits for a dataset based on specific algorithms (such as using percentiles).
-
-Identifying lower and upper limits, as well as re-normalizing, is described in the Intervals and Normalization section, while stretching is described in the Stretching section.
 
@@
 
-%\subsection{Utils}
+\subsection{Utils}
 % Lim
@@
 
-The \astropypkg \package{stats} package provides
+The \package{astropy.stats} package provides
 statistical tools that are useful for or specific to
-astronomy and are not found in other \python\
+astronomy and are not found in or extend the available
+functionality of other \python\
 statistics packages such as \package{scipy}
@@
 
+%
 \subsubsection{Robust Statistical Estimators}
+\inlinecomment{BMS}{Can we highlight in a sentence for each of the ones below how they are different from e.g. the scipy equivalents?}
 

### 2017-10-20 main.tex
Update on Overleaf.

@@
 
-Several classes are provided for determining intervals and for normalizing values in this interval to the [0:1] range.
-In addition, classes are provided in order to identify lower and upper limits for a dataset based on specific algorithms (such as using percentiles).
+Several classes are provided for determining intervals (e.g. using image percentiles) and for normalizing values in this interval to the [0:1] range.
+
+\package{Matplotlib} allows a custom normalization and stretch to be used when displaying data by passing a normalization object.
+The \package{visualization} package also provides a normalization class that wraps the interval and stretching objects into a normalization object that \package{matplotlib} understands.
 
@@
 % include images
+
+Lupton et al.
+(2004) describe an “optimal” algorithm for producing red-green- blue composite images from three separate high-dynamic range arrays.
+This method is implemented in make_lupton_rgb as a convenience wraper function and an associated set of classes to provide alternate scalings.
+The SDSS SkyServer color images were made using a variation on this technique.
 

### 2017-10-20 main.tex
Update on Overleaf.
Some more inline comments

@@
 
+The package also provides the a histogram function, which is a generalization of \package{matplotlib}’s histogram function, to allow for more flexible specification of histogram bins.
+The function provides several methods of automatically tuning the histogram bin size.
+It has a syntax identical \package{matplotlib}’s histogram function, with the exception of the bins parameter, which allows specification of one of four different methods for automatic bin selection.
+
 \subsubsection{Creating color RGB images}
@@
 (2004) describe an “optimal” algorithm for producing red-green- blue composite images from three separate high-dynamic range arrays.
-This method is implemented in make_lupton_rgb as a convenience wraper function and an associated set of classes to provide alternate scalings.
+The \package{visualization} package provies a convenience function to create such an image.
+It also includes an associated set of classes to provide alternate scalings.
 The SDSS SkyServer color images were made using a variation on this technique.
@@
 
+\inlinecomment{BMS}{What about pytest-astropy, should we inlude it here, or
+  for the future section?}
 % \section{State of the Ecosystem}
@@
 \label{sec:future}
-\inlinecomment{PLL}{In addition to PY3, add some killer features that we plan to implement for 3.0 and beyond?}
+\inlinecomment{PLL}{In addition to PY3, add some killer features that we
+  plan to implement for 3.0 and beyond?}
+\inlinecomment{BMS}{Some killer features we already know about to definitely
+have may be mentioned here. e.g. functionality of astropy-healpix? or the
+performance/speedup focus of the 3.1 release?}
+\inlinecomment{BMS}{should we mention the refactored infra here?
+  e.g. pytest-astropy and sphinx-astropy?}
 \subsection{Roadmap for \python 3 only support}

### 2017-10-20 main.tex
Update on Overleaf.

--- 2017-10-20 main.tex
@@
 
+The package also provides the a histogram function, which is a generalization of \package{matplotlib}’s histogram function, to allow for more flexible specification of histogram bins.
+The function provides several methods of automatically tuning the histogram bin size.
+It has a syntax identical to matplotlib’s plt.hist function, with the exception of the bins parameter, which allows specification of one of four different methods for automatic bin selection.
+
 \subsubsection{Creating color RGB images}

### 2017-10-20 main.tex
Update on Overleaf.

@@
 The function provides several methods of automatically tuning the histogram bin size.
-It has a syntax identical to matplotlib’s plt.hist function, with the exception of the bins parameter, which allows specification of one of four different methods for automatic bin selection.
+It has a syntax identical \package{matplotlib}’s histogram function, with the exception of the bins parameter, which allows specification of one of four different methods for automatic bin selection.
 

### 2017-10-20 main.tex
Update on Overleaf.

--- 2017-10-20 main.tex
@@
 The function provides several methods of automatically tuning the histogram bin size.
-It has a syntax identical \package{matplotlib}’s histogram function, with the exception of the bins parameter, which allows specification of one of four different methods for automatic bin selection.
+It has a syntax identical \package{matplotlib}’s histogram function (with the exception of the bins parameter), which allows specification of one of four different methods for automatic bin selection.
 

### 2017-10-20 main.tex
Update on Overleaf.

@@
 \subsection{Coordination of Astropy}
-% Kelle
+\inlinecomment{Kelle}
 
@@
 \subsection{Astropy development model, astropy ecosystem}
-% Erik
+\inlinecomment{Needs writing by EJT}
+
 This subsection should include some basic statistics about the contributors, commits, line of code etc. up to the 2.0 release when we know it.
@@
 %
-\inlinecomment{BMS}{TODO: write about the process of becoming affiliated, and project packages}
+\inlinecomment{BMS}{TODO: write about the process of becoming affiliated, and project packages into the future section below}
 %
-\subsection{Mixin}
+%\subsection{Mixin}
 
-\subsection{Accuracy testing across many different implementation}
+%\subsection{Accuracy testing across many different implementation}
 
@@
 \label{sec:units}
-% Marten, Adrian
+\inlinecomment{Marten, Adrian}{}
 
@@
 \subsection{Constants}
-% David S.
+
+\inlinecomment{David S.}
+
 versioning
@@
 
+\inlinecomment{Tom, Marten?}
+
 \inlinecomment{SCO}{Q: does it make sense to refer forward to FITS support, even though it is 3.0?}
@@
 
-\subsubsection{NDDdata}
-% Matt C., Michael, or Steve C.
-% Larry (nddata.utils)
-%NOTE (Larry), The package is nddata, which includes the NDData object.  %Don't forget the nddata.utils functionality (e.g. Cutout2D, block\_reduce, %etc.).
+\subsubsection{nddata}
+
+\inlinecomment{Matt C., Steve C.?}
+
+NDData object:
+
+%Larry:  Don't forget the nddata.utils functionality (e.g. Cutout2D, block\_reduce, %etc.).
 
@@
 \label{sec:table}
-% Tom A.
+
+\inlinecomment{Tom A.}
+
 QTable is new, mixin columns for time and coordinates. Table operations were added in v0.3
@@
 
+One of the most common tasks by astronomers dealing with observational data is to make figures with images that include the correct coordinates (formatted e.g. as sexagesimal values) and optiona
+The \package{visualization} package
 % Tom R. will work on this on Oct 18 and/or 19.
@@
 \subsubsection{Creating color RGB images}
-% include images
-
-Lupton et al.
-(2004) describe an “optimal” algorithm for producing red-green- blue composite images from three separate high-dynamic range arrays.
+\citep{Lupton2004} describe an “optimal” algorithm for producing red-green- blue composite images from three separate high-dynamic range arrays.
 The \package{visualization} package provies a convenience function to create such an image.
@@
 The SDSS SkyServer color images were made using a variation on this technique.
+% mention LSST contribution (Zenodo ref?)
+% include images here
 
-\subsection{Utils}
+%\subsection{Utils}
 % Lim
@@
 \inlinecomment{BMS}{Can we highlight in a sentence for each of the ones below how they are different from e.g. the scipy equivalents?}
+\inlinecomment{LDB}{Thanks.  I did this for sigma clipping.  Scipy doesn't have functions for the others...}
 
@@
 The process can be iterated to further reject outliers.
+It should be noted that the \package{scipy} sigma clipping function provides a subset of functionality of the \package{astropy.stats} function.
+The \package{astropy.stats} version can take a masked array as input and it allows the user to specify the number of iterations, the data axis on which to perform the clipping, and the functions used to calculate the center and standard deviation in the data.
 
@@
 The median absolute deviation (MAD) is a measure of the spread of a distribution and is defined as median(abs(a - median(a))).
-For a normal distribution, the MAD is related to the standard deviation by a factor of 1.4826, and a convenience function is available to apply the conversion.
+For a normal distribution, the MAD is related to the standard deviation by a factor of 1.4826 (the normal inverse cumulative distribution function evaluated at probabilty $P=3/4$), and a convenience function is available to apply the conversion.
 
@@
 A set of functions are included in the \package{stats} package that use the biweight formalism.
-These functions have long been used in astronomy, particularly to calculate the velocity dispersion of galaxy clusters [XXX].
+These functions have long been used in astronomy, particularly to calculate the velocity dispersion of galaxy clusters \citep{Beers1990}.
 
@@
   for the future section?}
+\inlinecomment{PLL}{pytest-astropy is v3, right?}
 % \section{State of the Ecosystem}
@@
 
-\section{Learning Astropy}
-\label{sec:learning}
+%\section{Learning Astropy}
+%\label{sec:learning}
 % Kelle, Adrian
-\inlinecomment{BMS}{would astropy learn mature enough to described in the paper, or maybe it should go as a subsection for the next, future of astropy section?}
+%\inlinecomment{BMS}{would astropy learn mature enough to described in the paper, or maybe it should go as a subsection for the next, future of astropy section?}
 
-Explain components: Documentation, Tutorials, and lessons
+%Explain components: Documentation, Tutorials, and lessons
 
@@
 Summary
-
+learning astropy 
 \acknowledgments
@@
           \package{scipy} (\url{https://www.scipy.org/}),
-          \package{matplotlib} (\url{https://matplotlib.org/}),
+          \package{matplotlib} (\url{https://matplotlib.org/})
+          \package{Cython}(\url{http://cython.org}),
           }
@@
 
+\appendix
+\section{List of Affiliated Packages}
+
 \end{document}

### 2017-10-20 main.tex
Update on Overleaf.

@@
 
-One of the most common tasks by astronomers dealing with observational data is to make figures with images that include the correct coordinates (formatted e.g. as sexagesimal values) and optiona
-The \package{visualization} package
-% Tom R. will work on this on Oct 18 and/or 19.
+One of the most common tasks by astronomers dealing with observational data is to make figures with images that include the correct coordinates and optionally with a coordinate grid.
+The challenge however is that the conceptual coordinate axes (such as longitude/latitude) need not be lined up with the pixel axes of the image.
+The \package{visualization.wcsaxes} subpackage implements a generalized way of making figures from an image array and a world coordinate system (WCS) object that provides the transformation between pixel and 'world' coordinates.
+World coordinates can be for example right ascension and declination, but can also include for example velocity, wavelength, frequency, time, and so on.
+The main features from this subpackage include the ability to control which axes to show which coordinate on (for example showing longitude ticks on the top and bottom axes and latitude on the left and right axes), controlling the spacing of the ticks either by specifying the positions to use or providing a tick spacing or an average number of ticks that should be present on each axis, controlling the visibility of the grid/graticule, and overlaying different coordinate systems
 
@@
 
-%
 \subsubsection{Robust Statistical Estimators}
-\inlinecomment{BMS}{Can we highlight in a sentence for each of the ones below how they are different from e.g. the scipy equivalents?}
-\inlinecomment{LDB}{Thanks.  I did this for sigma clipping.  Scipy doesn't have functions for the others...}
 
@@
 
-CI services? GitHub?
+Software/services to thank: GitHub. Travis CI, Appveyor, CircleCI.
 

### 2017-10-20 main.tex
Update on Overleaf.

@@
 World coordinates can be for example right ascension and declination, but can also include for example velocity, wavelength, frequency, time, and so on.
-The main features from this subpackage include the ability to control which axes to show which coordinate on (for example showing longitude ticks on the top and bottom axes and latitude on the left and right axes), controlling the spacing of the ticks either by specifying the positions to use or providing a tick spacing or an average number of ticks that should be present on each axis, controlling the visibility of the grid/graticule, and overlaying different coordinate systems
+The main features from this subpackage include the ability to control which axes to show which coordinate on (for example showing longitude ticks on the top and bottom axes and latitude on the left and right axes), controlling the spacing of the ticks either by specifying the positions to use or providing a tick spacing or an average number of ticks that should be present on each axis, setting the format for the tick labels to ones commonly used by astronomers, controlling the visibility of the grid/graticule, and overlaying ticks, labels, and/or grid lines from different coordinate systems.
+In addition, it is possible to pass data with more than two dimensions and slice on-the-fly.
+Finally, it is possible to define non-rectangular frames, such as for example for Aitoff projections.
+
+This subpackage differs from APLpy \citep{aplpy} in that the latter focuses on providing a very high-level interface to plotting that requires very few lines of code to get a good result, whereas WCSAxes defines an interface that is much closer to that of Matplotlib \citep{matplotlib}, and makes it possible to make significantly more advanced visualizations.
 
@@
 \subsubsection{Creating color RGB images}
-\citep{Lupton2004} describe an “optimal” algorithm for producing red-green- blue composite images from three separate high-dynamic range arrays.
-The \package{visualization} package provies a convenience function to create such an image.
+
+\citep{Lupton2004} describe an “optimal” algorithm for producing red-green-blue (RGB) composite images from three separate high-dynamic range arrays.
+The \package{visualization} package provides a convenience function to create such an image.
 It also includes an associated set of classes to provide alternate scalings.
+This functionality was contributed by developers from the Large Synoptic Survey Telescope (LSST) and serves as an example of contribution to Astropy from a more traditional engineering organization \citep{lsst_astropy}.
+
 The SDSS SkyServer color images were made using a variation on this technique.
-% mention LSST contribution (Zenodo ref?)
-% include images here
+% Larry TODO:  include RGB image here
 
@@
 
-Robust statistics provide reliable estimates of basic statistics for complex distributions.
+Robust statistics provide reliable estimates of basic statistics for complex distributions that largely mitigate the effects of outliers.
 The \package{stats} package includes several robust statistical functions that are commonly used in astronomy.
-This includes methods for rejecting outliers as well as statistical description of the underlying distributions.
+This includes sigma clipping methods to rejecting outliers, median absolute deviation functions, and biweight estimators, which have been used to calculate the velocity dispersion of galaxy clusters \citep{Beers1990}.
 
-{\bf Sigma Clipping:}
-Sigma clipping provides a fast method to identify outliers in a distribution.
-For a distribution of points, a center and a standard deviation are calculated.
-Values which are a set number of sigma times the standard deviation away from the center are rejected.
-The process can be iterated to further reject outliers.
-It should be noted that the \package{scipy} sigma clipping function provides a subset of functionality of the \package{astropy.stats} function.
-The \package{astropy.stats} version can take a masked array as input and it allows the user to specify the number of iterations, the data axis on which to perform the clipping, and the functions used to calculate the center and standard deviation in the data.
-
-{\bf Median Absolute Deviation:}
-The median absolute deviation (MAD) is a measure of the spread of a distribution and is defined as median(abs(a - median(a))).
-For a normal distribution, the MAD is related to the standard deviation by a factor of 1.4826 (the normal inverse cumulative distribution function evaluated at probabilty $P=3/4$), and a convenience function is available to apply the conversion.
-
-{\bf Biweight Estimators: }
-A set of functions are included in the \package{stats} package that use the biweight formalism.
-These functions have long been used in astronomy, particularly to calculate the velocity dispersion of galaxy clusters \citep{Beers1990}.
-
-{\bf Circular Statistics: }
+{\subsubsection{Circular Statistics}
 A set of circular statistical estimators based on [XXX] are implemented in the \package{stats} package.
@@
 
-\inlinecomment{BMS}{What about pytest-astropy, should we inlude it here, or
-  for the future section?}
-\inlinecomment{PLL}{pytest-astropy is v3, right?}
+%\inlinecomment{BMS}{What about pytest-astropy, should we inlude it here, or
+%  for the future section?}
+%\inlinecomment{PLL}{pytest-astropy is v3, right?}
 % \section{State of the Ecosystem}
@@
 
-Software/services to thank: GitHub. Travis CI, Appveyor, CircleCI.
+Software/services to thank: GitHub. Travis CI, Appveyor, CircleCI. Read the Docs.
 
@@
           \package{numpy} (\citealt{numpy}),
-          \package{scipy} (\url{https://www.scipy.org/}),
-          \package{matplotlib} (\url{https://matplotlib.org/})
-          \package{Cython}(\url{http://cython.org}),
+          \package{scipy} (\citealt{scipy}),
+          \package{matplotlib} (\citealt{matplotlib})
+          \package{Cython}(\citealt{cython}),
           }

### 2017-10-20 main.tex
Update on Overleaf.

@@
 
-% Tom R: unit support description goes here and the sentence below is to be folded in with it.
-
-Unit support in \texttt{modeling} has enabled implementation of the blackbody \citep{Rybicki1979} model, which requires units to make sense.
-It is available in \package{astropy} 2.0 as \texttt{BlackBody1D}.
+The \package{modeling} package now supports the representation, evaluation and fitting of models using \texttt{Quantity} objects, which attach units to scalar values or arrays of values.
+In practice, this means that one can for example fit a model to data with units and get parameters that also have units out, or initialize a model with parameters with units and evaluating it using input values with different but equivalent units.
+Using this, we have implemented a blackbody model (\texttt{BlackBody1D}) that can be used to fit observed fluxes in a variety of units and as a function of different units of spectral coordinates.
 
@@
 
+\label{sec:stretch}
+
 The \package{visualization} package provides a framework for transforming values in images (and more generally any arrays), typically for the purpose of visualization.
@@
 
-\subsubsection{WCSAxes}
+\subsubsection{Plotting image data with world coordinates}
 
@@
 This subpackage differs from APLpy \citep{aplpy} in that the latter focuses on providing a very high-level interface to plotting that requires very few lines of code to get a good result, whereas WCSAxes defines an interface that is much closer to that of Matplotlib \citep{matplotlib}, and makes it possible to make significantly more advanced visualizations.
+An example of a visualization made with \package{wcsaxes} is shown in Figure~\ref{fig:wcsaxes} -- this example illustrates the ability to overlay multiple coordinate systems and customize which ticks/labels are shown on which axes around the image.
+This also uses the image stretching functionality from Section~\ref{sec:stretch} to show the image in a square root stretch (automatically updating the tick positions in the colorbar).
+
+\begin{figure}
+\includegraphics[width=\textwidth]{cygnus_x_spitzer.pdf}
+\caption{%
+An example of figure made using the \package{visualization.wcsaxes} subpackage, using \textit{Spitzer}/IRAC 8.0$\mu$m data from the Cygnus-X Spitzer Legacy survey \citep{cygnusx}.
+\label{fig:wcsaxes}
+}
+\end{figure}
 
@@
 
-\citep{Lupton2004} describe an “optimal” algorithm for producing red-green-blue (RGB) composite images from three separate high-dynamic range arrays.
-The \package{visualization} package provides a convenience function to create such an image.
+\cite{Lupton2004} describe an “optimal” algorithm for producing red-green-blue (RGB) composite images from three separate high-dynamic range arrays.
+The \package{visualization} package provides a convenience function to create such a color image.
 It also includes an associated set of classes to provide alternate scalings.
@@
 
-The SDSS SkyServer color images were made using a variation on this technique.
-% Larry TODO:  include RGB image here
+The Sloan Digital Sky Survey (SDSS) SkyServer color images were made using a variation on this technique.
+As an example, in \figurename~\ref{fig:ngc6977} we show an RGB color image of the Hickson 88 group, centered near NGC~6977.
+This image was generated from SDSS images using the \package{astropy.visualization} tools.
+
+\begin{figure}
+\includegraphics[width=\textwidth]{ngc6977.png}
+\caption{An RGB color image of the region near the Hickson 88 group
+constructed from SDSS images and the \package{astropy.visualization}
+tools.
+\label{fig:ngc6977}}
+\end{figure}
 
@@
 \subsubsection{Lomb-Scargle Periodograms}
-%jake
+Periodic analysis of unevenly-spaced time series is common across subfields of Astronomy.
+The \package{stats} package includes several efficient implementations of the Lomb-Scargle periodogram \citep{Lomb76, Scargle82} and several generalizations, floating mean models \citep{Zechmeister09}, truncated Fourier models \citep{Bretthorst2003}, and appropriate handling of heteroscedastic uncertainties.
+Importantly, the implementations make use of several fast and scalable computational approaches \citep[e.g.][]{Press89, Palmer09}, and so can be applied to much larger datasets than algorithms available in, e.g.
+\package{scipy.stats} (\citealt{scipy}).
+Much of the Lomb-Scargle code in AstroPy has been adapted from previously-published open-source code \citep{astroML, VanderPlas2015}.
 
-\subsubsection{Histogram Binning}
-%jake
+\subsubsection{Bayesian Blocks and Histogram Binning}
+AstroPy also includes an implementation of {\it Bayesian Blocks} \citep{Scargle2013}, an algorithm for analysis of break-points in non-periodic astronomical time-series.
+One interesting application of Bayesian Blocks is its use in determining optimal histogram binnings, and in particular binnings with unequal bin sizes.
+This code was adapted, with several improvements, from the \package{astroML} package \citep{astroML}.
+
+\inlinecomment{JTV}{Should we include an example BB histogram from the astropy docs?}
 
@@
 %
-\subsection{sphinx extensions}
+\subsection{Sphinx extensions}
 
-% Tom R will work on this on Oct 18 and/or 19
+The documentation for many Python packages the core \package{astropy} package as well as for all packages in the Astropy ecosystem is written using the Sphinx package.
+This package makes it possible to write the documentation using plain text files that follow a markup language called reStructuredText, and Sphinx can then transform this into HTML or \LaTeX documentation.
+As part of the project, we have developed a few extensions that facilitate generating documentation for a large project like Astropy.
+One of the main extensions we have developed is \package{sphinx-automodapi}\footnote{\url{http://sphinx-automodapi.readthedocs.io}}, which makes it easy with a single reStructuredText command to generate a set of documentation pages listing all the available classes, functions, and attributes in any given Python module.
+
+\inlinecomment{TPR}{We should put the releases of sphinx-automodapi on Zenodo and cite this}
+
+% TODO: need to put releases of sphinx-automodapi on Zenodo!
 

### 2017-10-21 main.tex
add general section at end of article

@@
 I picked ds9 becase (a) it's wider known (e.g.
-in the X-ray sounity) and (b) because it is an example of a widely used tool with institutional support that is NOT a large package.
+in the X-ray community) and (b) because it is an example of a widely used tool with institutional support that is NOT a large package.
 TOPCAT would have been another example if we want to expand that list.
   SAO,][]{ds9}. These packages tend to address a wide range of users
-and they typically provide some level of documentation and user
-support. Other packages are developed foremost by individual research
-groups and used mostly in work by members of this group. Those
+and typically provide some level of documentation and user
+support is provided. Other packages are developed foremost by individual research
+groups and used mostly in work by members of the group. Those
 packages can address more specialized needs, but are not necessarily
@@
 some cases be insufficient for new users and the quality of the
-software, i.e. the robustness and the level of testing that has been
+software, i.e.\ the robustness and the level of testing that has been
 performed to ensure correctness, is not always clear. On the other
@@
 consuming to implement the FITS standard correctly and
-programming is much faster when using an existing library perform this
+programming is much faster when using an existing library to perform this
 task. Another example of such a common task is dealing with different
@@
 are available which can help with tasks that are not astronomy specific but
-might be performed in the course of astronomical research, e.g., presenting
+might be performed in the course of astronomical research, e.g.\ presenting
 results on websites or interfacing with databases.
@@
 \cite{astropy}. Since then, the \astropy package has been
-used in hundreds of projects, and the scope of the package as grown
+used in hundreds of projects, and the scope of the package has grown
 considerably. At the same time, the community of astronomers
@@
 separate packages that help setting up the infrastructure for testing,
-documentation etc.~(\sectionname~\ref{sec:infrastructure}). In
-\sectionname~\ref{sec:learning} we give an overview of the wealth of
-resources created to teach new users the use of the \astropy packages
-and how to contribute to the community. We end with a short vision for
-the future of \astropy in \sectionname~\ref{sec:future}.
+documentation etc.\ (\sectionname~\ref{sec:infrastructure}). 
+We end with a short vision for
+the future of \astropy in particular and astronomical software in general
+in \sectionname~\ref{sec:future}.
 
@@
 package is also seen as a good strategy for functionality that is aimed for
-the \astropypkg~core but is currently undergo rapid development and can 
+the \astropypkg~core but is initially undergoing rapid development and can 
 benefit from a different release cycle while stabilizing its API. 
@@
 They are supposed to be used more frequently by individual users.}
+\inlinecomment{hamogu}{MY feeling is that this section is too detailed already. If I had written it, I would not have mentioned the scripts at all.}
 
@@
 
-The \package{astropy.stats} package provides
-statistical tools that are useful for or specific to
-astronomy and are not found in or extend the available
-functionality of other \python\
-statistics packages such as \package{scipy}
-\citep{scipy} or \package{statsmodels}
-\citep{seabold2010statsmodels}.   The
-\package{stats} package contains a range of
-different functionality used by many different
-disciplines in astronomy.   It is not a complete set
-of statistic tools, but rather a still growing
-collection of useful features.
+The \package{astropy.stats} package provides statistical tools that
+are useful for or specific to astronomy and are not found in or extend
+the available functionality of other \python\ statistics packages such
+as \package{scipy} \citep{scipy} or \package{statsmodels}
+\citep{seabold2010statsmodels}.  The \package{stats} package contains
+a range of different functionality used by many different disciplines
+in astronomy.  It is not a complete set of statistic tools, but rather
+a still growing collection of useful features.
 
@@
 learning astropy
+
+\section{Outlook}
+\label{sec:outlook}
+\inlinecomment{hamogu}{This may be merged into the section above once
+  that is fleshed out a little more.}  As shown above the development
+of the \astropypkg package is making good progress, helping
+astronomers worldwide to perform many daily tasks such as planning
+observations, analyzing data or simulation results, and writing
+publications. The strong emphasis that the \astropy project puts on
+reliability and code correctness helps users to trust the calculations
+performed with \astropypkg and to publish reproducable results. More
+functionality is added to the core package and more and more
+affiliated packages support more specialized needs.
+
+At the same time, \astropy is spreading awareness of best practices in
+software development. This is important since most practicing
+astronomers received their education without being taught in computer
+science and software development although a major fraction of almost
+every astronomer's workload today is related to software use and
+development. The \astropypkg package leads by example, showing all interested
+astronomers how modern tools like git verion control or continuous
+integration (code is tested after every change to the source) can
+increase the quality and accessability of astronomical software
+without overly complicating the development cycle. All submitted code
+is reviewed by at least one, but typically more, members of the
+astropy community, providing feedback and allowing contributors to
+improve their skill is developing software without the need for their
+institutions to provide dedicated teaching recources. Thus, the
+\astropy project does not only build the tools needed to perform
+productive astronomical research in an era of increasingly large and
+complex datasets, it also helps to prepare the current and the next
+generation of researchers with the knowledge to adequatly use those
+tools.
+
 \acknowledgments

### 2017-10-23 main.tex
Update on Overleaf.
"IAU SOFA Board" was taken as author name

@@
 TOPCAT would have been another example if we want to expand that list.
+% olebole: TOPCAT is part of Starlink Java. An other examples would be CASA resp. AIPS. I'd rather omit ds9, since it is mainly developed by one person. 
   SAO,][]{ds9}. These packages tend to address a wide range of users
@@
 reliability and code correctness helps users to trust the calculations
-performed with \astropypkg and to publish reproducable results. More
+performed with \astropypkg and to publish reproducible results. More
 functionality is added to the core package and more and more
@@
 development. The \astropypkg package leads by example, showing all interested
-astronomers how modern tools like git verion control or continuous
+astronomers how modern tools like git version control or continuous
 integration (code is tested after every change to the source) can
-increase the quality and accessability of astronomical software
+increase the quality and accessibility of astronomical software
 without overly complicating the development cycle. All submitted code
@@
 improve their skill is developing software without the need for their
-institutions to provide dedicated teaching recources. Thus, the
+institutions to provide dedicated teaching resources. Thus, the
 \astropy project does not only build the tools needed to perform
@@
 complex datasets, it also helps to prepare the current and the next
-generation of researchers with the knowledge to adequatly use those
+generation of researchers with the knowledge to adequately use those
 tools.

### 2017-10-24 main.tex
reference to Jammalamadaka & Sengupta

@@
 {\subsubsection{Circular Statistics}
-A set of circular statistical estimators based on [XXX] are implemented in the \package{stats} package.
-These functions provide measurements of the circular mean, variance, and moment.
-For all of these functions, they work with both numpy.ndarrays (assumed to be in radians) and Quantity objects.
-In addition, the package includes tests for Raleigh Test [XXX], vtest [XXX], and a function to compute the maximum likelihood estimator for the parameters of the von Mises distribution [XXX].
+
+A set of circular statistical estimators based on \citet{JammalamadakaSengupta}
+are implemented in the \package{stats} package.  These functions provide
+measurements of the circular mean, variance, and moment.   For all of these
+functions, they work with both \texttt{numpy.ndarrays} (assumed to be in
+radians) and \texttt{Quantity} objects.  In addition, the package includes
+tests for Raleigh Test [XXX], vtest [XXX], and a function to compute the
+maximum likelihood estimator for the parameters of the von Mises distribution
+[XXX].
 

### 2017-10-24 main.tex
typo

@@
 radians) and \texttt{Quantity} objects.  In addition, the package includes
-tests for Raleigh Test [XXX], vtest [XXX], and a function to compute the
+tests for Rayleigh Test [XXX], vtest [XXX], and a function to compute the
 maximum likelihood estimator for the parameters of the von Mises distribution

### 2017-10-24 main.tex
Rayleigh test reference

--- 2017-10-24 main.tex
@@
 radians) and \texttt{Quantity} objects.  In addition, the package includes
-tests for Raleigh Test [XXX], vtest [XXX], and a function to compute the
-maximum likelihood estimator for the parameters of the von Mises distribution
-[XXX].
+tests for Rayleigh Test \citep{wilkie83}, vtest [XXX], and a function to
+compute the maximum likelihood estimator for the parameters of the von Mises
+distribution [XXX].
 

### 2017-10-24 main.tex
opening quotes

@@
 The challenge however is that the conceptual coordinate axes (such as longitude/latitude) need not be lined up with the pixel axes of the image.
-The \package{visualization.wcsaxes} subpackage implements a generalized way of making figures from an image array and a world coordinate system (WCS) object that provides the transformation between pixel and 'world' coordinates.
+The \package{visualization.wcsaxes} subpackage implements a generalized way of making figures from an image array and a world coordinate system (WCS) object that provides the transformation between pixel and `world' coordinates.
 World coordinates can be for example right ascension and declination, but can also include for example velocity, wavelength, frequency, time, and so on.

### 2017-10-24 main.tex
remove whitespace
\@ before period

@@
 into a detailed implementation. APEs are again edited and discussed on
-a platform \footnote{\url{https://github.com/astropy/astropy-APEs}}
+a platform\footnote{\url{https://github.com/astropy/astropy-APEs}}
 open to the public. In previous APEs a community consensus emerged and
@@
 \par Long-term support (LTS) releases continue to receive bugfixes for 2
-years with no changes to the API. They are ideal for pipelines and other
+years with no changes to the API\@. They are ideal for pipelines and other
 applications where API stability is essential. The latest LTS release is

### 2017-10-24 main.tex
unwanted space in caption
Update on Overleaf.

@@
 \includegraphics[width=\textwidth]{coordinates_graph.pdf}
-\caption{
+\caption{%
     The full graph of possible reference frame transformations implemented in
@@
 Periodic analysis of unevenly-spaced time series is common across subfields of Astronomy.
-The \package{stats} package includes several efficient implementations of the Lomb-Scargle periodogram \citep{Lomb76, Scargle82} and several generalizations, floating mean models \citep{Zechmeister09}, truncated Fourier models \citep{Bretthorst2003}, and appropriate handling of heteroscedastic uncertainties.
-Importantly, the implementations make use of several fast and scalable computational approaches \citep[e.g.][]{Press89, Palmer09}, and so can be applied to much larger datasets than algorithms available in, e.g.
+The \package{stats} package now includes several efficient implementations of the Lomb-Scargle periodogram \citep{Lomb76, Scargle82} and several generalizations, including floating mean models \citep{Zechmeister09}, truncated Fourier models \citep{Bretthorst2003}, and appropriate handling of heteroscedastic uncertainties.
+Importantly, the implementations make use of several fast and scalable computational approaches \citep[e.g.][]{Press89, Palmer09}, and so can be applied to much larger datasets than Lomb-Scargle algorithms available in, e.g.
 \package{scipy.stats} (\citealt{scipy}).
@@
 This code was adapted, with several improvements, from the \package{astroML} package \citep{astroML}.
+An example of a histogram fit using the Bayesian blocks algorithm is shown in the right panel of \figurename\ref{fig:bayes-blocks-hist}.
 
-\inlinecomment{JTV}{Should we include an example BB histogram from the astropy docs?}
+\begin{figure}
+\includegraphics[width=\textwidth]{bayesian_blocks_hist.pdf}
+\caption{%
+    A histogram with irregular bins, fit using the Bayesian blocks
+    algorithm. The left panel shows a standard histogram using
+    \package{matplotlib}'s default of 10 bins. The right panel shows
+    the same histogram with bin widths determined by the Bayesian
+    blocks model. The model is such that relevant features of the data
+    distribution are much more apparent.
+    \label{fig:bayes-blocks-hist}
+}
+\end{figure}
 

### 2017-10-24 make_bayesian_blocks_hist.py

@@ -1,0 +1,31 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from astropy.visualization import hist
+
+# generate some complicated data
+rng = np.random.RandomState(0)
+t = np.concatenate([-5 + 1.8 * rng.standard_cauchy(500),
+                    -4 + 0.8 * rng.standard_cauchy(2000),
+                    -1 + 0.3 * rng.standard_cauchy(500),
+                    2 + 0.8 * rng.standard_cauchy(1000),
+                    4 + 1.5 * rng.standard_cauchy(1000)])
+
+# truncate to a reasonable range
+t = t[(t > -15) & (t < 15)]
+
+# draw histograms with two different bin widths
+fig, ax = plt.subplots(1, 2, figsize=(10, 4))
+hist_kwds = dict(histtype='stepfilled', alpha=0.5, normed=True)
+
+fig.subplots_adjust(left=0.1, right=0.95, bottom=0.15)
+
+ax[0].hist(t, **hist_kwds)
+ax[0].set(xlabel='t', ylabel='P(t)')
+ax[0].set_title('plt.hist()', fontdict=dict(family='monospace'))
+
+hist(t, bins='blocks', ax=ax[1], **hist_kwds)
+ax[1].set_xlabel('t')
+ax[1].set_ylabel('P(t)')
+ax[1].set_title('hist(t, bins="blocks")', fontdict=dict(family='monospace'))
+
+plt.savefig('bayesian_blocks_hist.pdf')

### 2017-10-24 registry.tex
affiliated packages

\href{https://github.com/astropy/astroscrappy}{Astro-SCRAPPY} & Yes & \href{https://pypi.python.org/pypi/astroscrappy}{astroscrappy} & Curtis McCully \\
\href{https://github.com/astropy/astroplan}{astroplan} & No & \href{https://pypi.python.org/pypi/astroplan}{astroplan} & Brett Morris \\
\href{http://github.com/astropy/astroquery.git}{astroquery} & Yes & \href{https://pypi.python.org/pypi/astroquery}{astroquery} & Adam Ginsburg and Brigitta Sipocz \\
\href{http://github.com/astropy/ccdproc.git}{ccdproc} & Yes & \href{https://pypi.python.org/pypi/ccdproc}{ccdproc} & Steven Crawford, Matt Craig, and Michael Seifert \\
\href{https://github.com/jesford/cluster-lensing}{cluster-lensing} & No & \href{https://pypi.python.org/pypi/cluster-lensing}{cluster-lensing} & Jes Ford \\
\href{https://github.com/adrn/gala}{gala} & Yes & \href{https://pypi.python.org/pypi/astro-gala}{astro-gala} & Adrian Price-Whelan \\
\href{https://github.com/jobovy/galpy}{galpy} & Yes & \href{https://pypi.python.org/pypi/galpy}{galpy} & Jo Bovy \\
\href{http://github.com/gammapy/gammapy.git}{gammapy} & No & \href{https://pypi.python.org/pypi/gammapy}{gammapy} & Christoph Deil \\
\href{http://github.com/ejeschke/ginga}{ginga} & Yes & \href{https://pypi.python.org/pypi/ginga}{ginga} & Eric Jeschke and Pey-Lian Lim \\
\href{https://github.com/glue-viz/glue.git}{Glue} & Yes & \href{https://pypi.python.org/pypi/glueviz}{glueviz} & Chris Beaumont and Thomas Robitaille \\
\href{https://github.com/spacetelescope/gwcs.git}{gwcs} & No & \href{https://pypi.python.org/pypi/gwcs}{gwcs} & Nadia Dencheva \\
\href{https://github.com/astropy/halotools}{Halotools} & Yes & \href{https://pypi.python.org/pypi/halotools}{halotools} & Andrew Hearin \\
\href{http://github.com/spacetelescope/imexam}{imexam} & No & \href{https://pypi.python.org/pypi/imexam}{imexam} & Megan Sosey \\
\href{https://github.com/Chandra-MARX/marxs}{marxs} & Yes & \href{https://pypi.python.org/pypi/marxs}{marxs} & Hans Moritz Günther (hamogu) \\
\href{https://github.com/astropy/montage-wrapper}{montage-wrapper} & Yes & \href{https://pypi.python.org/pypi/montage-wrapper}{montage-wrapper} & Thomas Robitaille \\
\href{https://github.com/zblz/naima}{naima} & Yes & \href{https://pypi.python.org/pypi/naima}{naima} & Victor Zabalza \\
\href{http://github.com/astropy/photutils.git}{photutils} & No & \href{https://pypi.python.org/pypi/photutils}{photutils} & Larry Bradley and Brigitta Sipocz \\
\href{http://github.com/weaverba137/pydl.git}{PyDL} & No & \href{https://pypi.python.org/pypi/pydl}{pydl} & Benjamin Alan Weaver \\
\href{https://github.com/olebole/python-cpl}{python-cpl} & No & \href{https://pypi.python.org/pypi/python-cpl}{python-cpl} & Ole Streicher \\
\href{https://github.com/astrofrog/reproject.git}{reproject} & Yes & \href{https://pypi.python.org/pypi/reproject}{reproject} & Thomas Robitaille \\
\href{http://github.com/sncosmo/sncosmo}{sncosmo} & Yes & \href{https://pypi.python.org/pypi/sncosmo}{sncosmo} & Kyle Barbary \\
\href{https://github.com/radio-astro-tools/spectral-cube}{spectral-cube} & Yes & \href{https://pypi.python.org/pypi/spectral-cube}{spectral-cube} & Adam Ginsburg \\
\href{http://github.com/astropy/specutils.git}{specutils} & No & \href{https://pypi.python.org/pypi/specutils}{specutils} & Nicholas Earl, Adam Ginsburg, Steve Crawford \\

### 2017-10-24 affiliated.py

@@ -1,0 +1,20 @@
+import json
+import re
+
+
+with open('registry.json') as data_file:
+    data = json.load(data_file)
+
+package_list = sorted(data['packages'], key=lambda k: k['name'].lower()) 
+
+stable_dict = {False: 'No', True: 'Yes'}
+
+with open("registry.tex", "w") as f:
+    for item in package_list:
+        if not item['provisional']:
+            f.write('\\href{{{0}}}{{{1}}} & {2} & '
+                    '\\href{{https://pypi.python.org/pypi/{3}}}{{{3}}} & {4} '
+                    '\\\\\n'.format(item["repo_url"], item["name"],
+                                    stable_dict[item["stable"]],
+                                    item['pypi_name'],
+                                    re.sub(' <.*?>', '', item["maintainer"])))

### 2017-10-24 registry_prov.tex
provisionally accepted packages

\href{http://github.com/aplpy/aplpy.git}{APLpy} & Yes & \href{https://pypi.python.org/pypi/APLpy}{APLpy} & Thomas Robitaille and Eli Bressert \\
\href{http://github.com/astroML/astroML}{astroML} & Yes & \href{https://pypi.python.org/pypi/astroML}{astroML} & Jake Vanderplas \\
\href{https://github.com/StingraySoftware/HENDRICS}{HENDRICS} & Yes & \href{https://pypi.python.org/pypi/hendrics}{hendrics} & Matteo Bachetti \\
\href{https://github.com/RiceMunk/omnifit}{omnifit} & Yes & \href{https://pypi.python.org/pypi/omnifit}{omnifit} & Aleksi Suutarinen \\
\href{https://github.com/astropy/pyregion.git}{pyregion} & Yes & \href{https://pypi.python.org/pypi/pyregion}{pyregion} & Jae-Joon Lee \\
\href{https://github.com/pyvirtobs/pyvo.git}{PyVO} & No & \href{https://pypi.python.org/pypi/pyvo}{pyvo} & Stefan Becker \\
\href{https://github.com/spacetelescope/spherical_geometry.git}{spherical\_geometry} & No & \href{https://pypi.python.org/pypi/spherical-geometry}{spherical-geometry} & Bernie Simon and Michael Droettboom \\

### 2017-10-24 affiliated.py

@@ -9,12 +9,17 @@ package_list = sorted(data['packages'], key=lambda k: k['name'].lower())
 
 stable_dict = {False: 'No', True: 'Yes'}
 
-with open("registry.tex", "w") as f:
+row = ('\\href{{{0}}}{{{1}}} & {2} & '
+      '\\href{{https://pypi.python.org/pypi/{3}}}{{{3}}} & {4} \\\\\n')
+
+with open("registry.tex", "w") as f1, open("registry_prov.tex", "w") as f2:
     for item in package_list:
         if not item['provisional']:
-            f.write('\\href{{{0}}}{{{1}}} & {2} & '
-                    '\\href{{https://pypi.python.org/pypi/{3}}}{{{3}}} & {4} '
-                    '\\\\\n'.format(item["repo_url"], item["name"],
-                                    stable_dict[item["stable"]],
-                                    item['pypi_name'],
-                                    re.sub(' <.*?>', '', item["maintainer"])))
+            f1.write(row.format(item["repo_url"], item["name"],
+                                stable_dict[item["stable"]], item['pypi_name'],
+                                re.sub(' <.*?>', '', item["maintainer"])))
+        else:
+            f2.write(row.format(item["repo_url"], 
+                                re.sub('_', '\_', item["name"]),
+                                stable_dict[item["stable"]], item['pypi_name'],
+                                re.sub(' <.*?>', '', item["maintainer"])))

### 2017-10-24 main.tex
affiliated packages
provisionally accepted packages
Update on Overleaf.

@@
 \documentclass[modern]{aastex61}
+\usepackage{hyperref}
 \usepackage{xspace}
+\usepackage{booktabs}
 \newcommand{\escapecmd}[1]{\texttt{\detokenize{#1}}}
@@
 The \package{stats} package includes several robust statistical functions that are commonly used in astronomy.
-This includes sigma clipping methods to rejecting outliers, median absolute deviation functions, and biweight estimators, which have been used to calculate the velocity dispersion of galaxy clusters \citep{Beers1990}.
+This includes sigma clipping methods for rejecting outliers, median absolute deviation functions, and biweight estimators, which have been used to calculate the velocity dispersion of galaxy clusters \citep{Beers1990}.
 
@@
 
+\begin{table}[h]
+  \centering
+  \caption{Registry of affiliated packages.}
+  \label{tab:registry}
+  \begin{tabular}{cccc}
+    \toprule
+    Package Name  & Stable & PyPI Name & Maintainer \\
+    \midrule
+      \input{registry.tex}
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+\begin{table}[h]
+  \centering
+  \caption{Registry of provisionally accepted affiliated packages.}
+  \label{tab:registry_prov}
+  \begin{tabular}{cccc}
+    \toprule
+    Package Name  & Stable & PyPI Name & Maintainer \\
+    \midrule
+      \input{registry_prov.tex}
+    \bottomrule
+  \end{tabular}
+\end{table}
+
 \end{document}

### 2017-10-25 main.tex
UTF-8 input encoding for maintainer's names
Names in registry.json have special characters
update on Overleaf

@@
 \usepackage{booktabs}
+\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
 \newcommand{\escapecmd}[1]{\texttt{\detokenize{#1}}}
@@
 \par In addition to astronomy related packages and libraries, the \astropy\
-Project also contains and supports several infrastructure package that are
+Project also contains and supports several infrastructure packages that are
 very generic. The following sections describes the most widely used

### 2017-10-26 main.tex
typo
update on Overleaf

@@
 \par The general scheme for the releases and version numbering that the core
-package has adopted if the following. \astropypkg has new feature releases every
+package has adopted is the following. \astropypkg has new feature releases every
 6 months, and between feature releases additional bugfix releases that
@@
 \par The version numbering of \astropypkg reflects on the release scheme
-described above. The core package uses the form x.y.z, where x is advances
+described above. The core package uses the form x.y.z, where x is advanced
 on LTS, y is advanced for a non-LTS feature release, and z is advanced on

### 2017-10-26 main.tex
remove line break

@@
     These ephemerides can be computed either using analytic approximations from
-    ERFA, or from downloaded JPL ephemerides (the latter requires the \package{j
-    plephem}\footnote{\url{https://github.com/brandon-rhodes/python-jplephem}}
+    ERFA, or from downloaded JPL ephemerides (the latter requires the
+    \package{jplephem}\footnote{\url{https://github.com/brandon-rhodes/python-jplephem}}
     optional dependency and an internet connection).

### 2017-10-26 main.tex
links

@@
 
-Modeling also supports a plugin system for fitters, which allows using the astropy models with external fitters.
-An example of this is SABA (link), which is a bridge between Sherpa (link) and astropy.modeling, to bring the Sherpa fitters into astropy.
+Modeling also supports a plugin system for fitters, which allows using the
+astropy models with external fitters. An example of this is
+SABA\footnote{\url{https://github.com/astropy/saba}}, which is a bridge between
+Sherpa\footnote{\url{http://cxc.cfa.harvard.edu/contrib/sherpa/}}
+and astropy.modeling, to bring the Sherpa fitters into astropy.
 

### 2017-10-26 main.tex
typo

@@
 
-The package also provides the a histogram function, which is a generalization of \package{matplotlib}’s histogram function, to allow for more flexible specification of histogram bins.
-The function provides several methods of automatically tuning the histogram bin size.
-It has a syntax identical \package{matplotlib}’s histogram function (with the exception of the bins parameter), which allows specification of one of four different methods for automatic bin selection.
+The package also provides the a histogram function, which is a generalization
+of \package{matplotlib}’s histogram function, to allow for more flexible
+specification of histogram bins.  The function provides several methods of
+automatically tuning the histogram bin size. It has a syntax identical to
+\package{matplotlib}’s histogram function (with the exception of the bins
+parameter), which allows specification of one of four different methods for
+automatic bin selection.
 

### 2017-10-26 main.tex
quotes
latex macro

@@
 
-\cite{Lupton2004} describe an “optimal” algorithm for producing red-green-blue (RGB) composite images from three separate high-dynamic range arrays.
+\cite{Lupton2004} describe an ``optimal'' algorithm for producing red-green-blue (RGB) composite images from three separate high-dynamic range arrays.
 The \package{visualization} package provides a convenience function to create such a color image.
@@
 
-The documentation for many Python packages the core \package{astropy} package as well as for all packages in the Astropy ecosystem is written using the Sphinx package.
-This package makes it possible to write the documentation using plain text files that follow a markup language called reStructuredText, and Sphinx can then transform this into HTML or \LaTeX documentation.
-As part of the project, we have developed a few extensions that facilitate generating documentation for a large project like Astropy.
-One of the main extensions we have developed is \package{sphinx-automodapi}\footnote{\url{http://sphinx-automodapi.readthedocs.io}}, which makes it easy with a single reStructuredText command to generate a set of documentation pages listing all the available classes, functions, and attributes in any given Python module.
+The documentation for many Python packages the core \package{astropy} package
+as well as for all packages in the Astropy ecosystem is written using the
+Sphinx package. This package makes it possible to write the documentation using
+plain text files that follow a markup language called reStructuredText, and
+Sphinx can then transform this into HTML or \LaTeX{} documentation. As part of
+the project, we have developed a few extensions that facilitate generating
+documentation for a large project like Astropy. One of the main extensions we
+have developed is
+\package{sphinx-automodapi}\footnote{\url{http://sphinx-automodapi.readthedocs.io}},
+which makes it easy with a single reStructuredText command to generate a set of
+documentation pages listing all the available classes, functions, and
+attributes in any given Python module.
 

### 2017-10-26 main.tex
packages section

@@
 
+\subsection{Distribution packages}
+
+\astropy is available from several of the Python distributions for scientific
+computing, such as Anaconda or Enthought Canopy, which include also some of
+\astropy's affiliated packages.
+Alternatively, \astropy can be readily installed from the Python Package Index
+(PyPI) using pip, the recommended command-line tool for installing Python packages
+that is included by default since Python 2 $\geq$ 2.7.9 and Python 3 $\geq$ 3.4.
+For most recent \astropy releases, pre-built wheel distributions are obtainable
+for Windows, Mac OS X and Linux systems from PyPI that provide faster
+installation compared to the source distribution.  Optionally, the version of
+the package and the dependencies needed to run or build the software are given
+by a specifier to the pip package manager as described in PEP 440\footnote{For
+more detailed installation instructions and optional flags see
+\url{http://docs.astropy.org/en/stable/install.html#installing-astropy}}.
+Packaged versions of \astropy are also available for several
+operating systems that are managed by a system's package manager,
+including Debian, Ubuntu, Fedora, Gentoo, Arch Linux, Mac OS X (e.g.,
+via brew, macports or fink) and FreeBSD.  However, on occasion these packages
+may be outdated compared with the latest stable release of \astropy accessible
+from the PyPI.
+
 \subsection{Support of Astropy}

### 2017-10-26 main.tex
tweak

@@
 For most recent \astropy releases, pre-built wheel distributions are obtainable
-for Windows, Mac OS X and Linux systems from PyPI that provide faster
+from PyPI for Windows, Mac OS X and Linux systems that provide faster
 installation compared to the source distribution.  Optionally, the version of

### 2017-10-27 main.tex
Update on Overleaf.

@@
 \subsection{Coordination of Astropy}
-\inlinecomment{Kelle}
+\inlinecomment{EJT}
 
@@
 
-\astropy is available from several of the Python distributions for scientific
+\astropypkg is available from several of the Python distributions for scientific
+% * <mattwcraig@gmail.com> 2017-10-27T07:13:51.093Z:
+% 
+% > \astropypkg i
+% I changed a few of the macros in here to refer to the package rather than the project because it is the package being discussed here.
+% 
+% ^.
 computing, such as Anaconda or Enthought Canopy, which include also some of
 \astropy's affiliated packages.
-Alternatively, \astropy can be readily installed from the Python Package Index
+Alternatively, \astropypkg can be readily installed from the Python Package Index
 (PyPI) using pip, the recommended command-line tool for installing Python packages
 that is included by default since Python 2 $\geq$ 2.7.9 and Python 3 $\geq$ 3.4.
-For most recent \astropy releases, pre-built wheel distributions are obtainable
+For most recent \astropypkg releases, pre-built wheel distributions are obtainable
 from PyPI for Windows, Mac OS X and Linux systems that provide faster
@@
 more detailed installation instructions and optional flags see
-\url{http://docs.astropy.org/en/stable/install.html#installing-astropy}}.
+\url{http://docs.astropy.org/en/stable/install.html\#installing-astropy}}.
+
 Packaged versions of \astropy are also available for several
@@
 may be outdated compared with the latest stable release of \astropy accessible
-from the PyPI.
-
-\subsection{Support of Astropy}
-
+from the PyPI. Pre-built binary conda packages for all of the affiliated packages are also available  via the \texttt{astropy} conda channel for the three majot platforms.
+% * <mattwcraig@gmail.com> 2017-10-27T07:16:27.310Z:
+% 
+% > re-built binary conda packages
+% Feel free to remove if this is too detailed. I do think the available of the whole ecosystem across all platforms has helped speed its adoption.
+% 
+% ^.
+
+%\subsection{Support of Astropy}
+% Removing unless this gets written about in 
+% a later version
 % This section should be a straight forward/factual description of the current
@@
     \astropy-affiliated package \package{astroplan}\citep{astroplan_AAS}. 
-    \inlinecomment{APW}{TODO: cite zenodo entry for astroplan?}
-    \inlinecomment{BMS}{better to cite the submitted or soon to be submitted paper, I made a placeholder for it.}
+%    \inlinecomment{APW}{TODO: cite zenodo entry for astroplan?}
+%    \inlinecomment{BMS}{better to cite the submitted or soon to be submitted paper, I made a placeholder for it.}
 
@@
 
-\inlinecomment{Matt C., Steve C.?}
-
-NDData object:
+\inlinecomment{Should I mention the fact that there will be changes coming to 3.0?}
+
+The \package{astropy.nddata} subpackage provides three types of functionality: concrete classes for representing multi-dimensional gridded data like CCD images and utilities for manipulating multi-dimensional images and high-level classes that define an interface for representing generic gridded data that is intended primarily for developers of other packages.
+
+The \texttt{CCDData} class provides I/O to FITS files and uses data structures from \astropypkg, like WCS, to represent the contents of a file abstractly.
+This class supports basic arithmetic operations on image, including error propagation in limited cases and slicing of images that also appropriately slices the image mask and error arrays, if present.
+
+The \package{astropy.nddata.utils} module provides utilities that can operate on either plain NumPy arrays or any of the classes in the \package{astropy.nddata} subpackage.
+It features a class for representing two-dimensional image cutouts, allowing one to easily link pixels in the cutout to pixels in the original image or from the image to the cutout, and to overlay the cutout on images.
+Functions to enlarge or reduce an image by doing block replication or reduction are also provided.
+
+At a higher level, classes are provided which define a minimal interface for gridded data with attributes for accessing metadata, WCS and other common traits.
+These serve as a useful base for package authors wishing to develop their own classes for specific use cases and as containers for exchanging gridded data.
 
@@
 
+The \package{cosmology} package contains classes for representing different cosmologies and functions for calculating commonly used quantities such as look-back time and distance.
+The package was described in detail in \cite{astropy}.
+The  default cosmology in \astropy v2.0 is given by the values in \cite{2016A&A...594A..13P}
+
 \subsection{Statistics}
@@
 radians) and \texttt{Quantity} objects.  In addition, the package includes
-tests for Rayleigh Test \citep{wilkie83}, vtest [XXX], and a function to
-compute the maximum likelihood estimator for the parameters of the von Mises
-distribution [XXX].
+tests for Rayleigh Test, vtest, and a function to compute the maximum likelihood estimator for the parameters of the von Mises
+distribution.
 
@@
 \label{sec:infrastructure}
-\inlinecomment{BMS}{should we use links to the appropriate github repo?}
-\inlinecomment{PLL}{IMHO a list of GitHub repo links for affil. pkgs. should be in appendix, if included.}
+%\inlinecomment{BMS}{should we use links to the appropriate github repo?}
+%\inlinecomment{PLL}{IMHO a list of GitHub repo links for affil. pkgs. should be in appendix, if included.}
 \inlinecomment{BMS}{should we describe astropy-helpers even though it's future is unsure?}
@@
 \par In addition to astronomy related packages and libraries, the \astropy\
-Project also contains and supports several infrastructure packages that are
+Project also maintains and distributes several infrastructure packages that are
 very generic. The following sections describes the most widely used
@@
 % Brigitta may write this up if there is no other takers
-\par \astropy provides a template package that any \python package is welcome to
+\par \astropy provides a \package{package-template}\footnote{\url{https://github.com/astropy/package-template/}}
+package that any \python package is welcome to
 use (many affiliated packages do so). The template contains a ready-to-go
@@
 % Brigitta
-\package{ci-helpers} is a collection of scripts that empowers package
-maintainers to control their testing set up and installation process for
+\package{ci-helpers}\footnote{\url{https://github.com/astropy/ci-helpers}} is a
+collection of scripts that empowers package maintainers to control their testing
+set up and installation process for
 various continuous integration services via a set of environment

### 2017-10-27 main.tex
Update on Overleaf.

@@
 
-The \package{astropy.nddata} subpackage provides three types of functionality: concrete classes for representing multi-dimensional gridded data like CCD images and utilities for manipulating multi-dimensional images and high-level classes that define an interface for representing generic gridded data that is intended primarily for developers of other packages.
-
-The \texttt{CCDData} class provides I/O to FITS files and uses data structures from \astropypkg, like WCS, to represent the contents of a file abstractly.
-This class supports basic arithmetic operations on image, including error propagation in limited cases and slicing of images that also appropriately slices the image mask and error arrays, if present.
+The \package{astropy.nddata} supackage provides three types of functionality: an abstract interface for representing generic arbitary-dimensional datasets intended primarily for developers of other packages and concrete classes building on this interface and utilities for manipulating these kind of datasets.
+
+The \texttt{NDDataBase} class provides the abstract interface for gridded data with attributes for accessing metadata, the world-coordinate system (WCS), uncertainty and other traits.
+Building on this interface the \texttt{NDData} class provides a minimally working implementation for storing NumPy arrays.
+These classes serve as useful base for package authors wishing to develop their own classes for specific use cases and as containers for exchanging gridded data.
+
+The concrete classes \texttt{NDDataRef}, \texttt{NDDataArray} and \texttt{CCDData} extend the storing functionality with options to do basic arithmetic (addition, subtraction, multiplication and division) including error propagation in limited cases and slicing of the dataset based on grid coordinates appropriately handling mask, errors, and units, if present.
+Additionally \texttt{CCDData} also provides I/O from and to FITS files and uses data structures from \astropypkg, like WCS, to represent the contents of a file abstractly.
 
@@
 
-At a higher level, classes are provided which define a minimal interface for gridded data with attributes for accessing metadata, WCS and other common traits.
-These serve as a useful base for package authors wishing to develop their own classes for specific use cases and as containers for exchanging gridded data.
+\inlinecomment{Should we mention that Cutout2D supports WCS to pixel conversions?}
 

### 2017-10-27 main.tex
typo

@@
 may be outdated compared with the latest stable release of \astropy accessible
-from the PyPI. Pre-built binary conda packages for all of the affiliated packages are also available  via the \texttt{astropy} conda channel for the three majot platforms.
+from the PyPI. Pre-built binary conda packages for all of the affiliated packages are also available  via the \texttt{astropy} conda channel for the three major platforms.
 % * <mattwcraig@gmail.com> 2017-10-27T07:16:27.310Z:

### 2017-10-27 main.tex
typo

@@
 
-The \package{astropy.nddata} supackage provides three types of functionality: an abstract interface for representing generic arbitary-dimensional datasets intended primarily for developers of other packages and concrete classes building on this interface and utilities for manipulating these kind of datasets.
+The \package{astropy.nddata} supackage provides three types of functionality:
+an abstract interface for representing generic arbitrary-dimensional datasets
+intended primarily for developers of other packages and concrete classes
+building on this interface and utilities for manipulating these kind of
+datasets.
 

### 2017-10-27 main.tex
PyPI

@@
 \astropy's affiliated packages.
-Alternatively, \astropypkg can be readily installed from the Python Package Index
-(PyPI) using pip, the recommended command-line tool for installing Python packages
+Alternatively, \astropypkg can be readily installed from the Python Package
+Index\footnote{\url{https://pypi.python.org/pypi}} (PyPI) using pip, the
+recommended command-line tool for installing Python packages
 that is included by default since Python 2 $\geq$ 2.7.9 and Python 3 $\geq$ 3.4.

### 2017-10-27 main.tex
Update on Overleaf.

@@
 \newcommand{\package}[1]{\texttt{#1}\xspace}
-\newcommand{\github}{\package{GitHub}\xspace}
-\newcommand{\python}{\package{Python}\xspace}
+\newcommand{\github}{\package{GitHub}}
+\newcommand{\python}{\package{Python}}
 \newcommand{\astropy}{Astropy\xspace}
-\newcommand{\astropypkg}{\package{astropy}\xspace}
+\newcommand{\astropypkg}{\package{astropy}}
 
@@
 developed. In this paper, we describe the current status of the
-\astropy community, the \astropy core package, and the \astropy\
+\astropy community, the \astropypkg core package, and the \astropy
 ecosystem.
@@
 %
-\par A major part of the \astropy~project is the concept of
+\par A major part of the \astropy project is the concept of
 ``Affiliated Packages''. An affiliated package is an astronomy-related
-\python~package that is not part of the \astropypkg~core package, but
+\python~package that is not part of the \astropypkg core package, but
 has requested to be included as part of the \astropy project's
-community. These packages support the goals and vision of \astropy~of
+community. These packages support the goals and vision of \astropy of
 improving code reuse, interoperability, and embracing good coding
@@
 an abstract interface for representing generic arbitrary-dimensional datasets
-intended primarily for developers of other packages and concrete classes
+intended primarily for developers of other packages, concrete classes
 building on this interface and utilities for manipulating these kind of
@@
 The \package{astropy.nddata.utils} module provides utilities that can operate on either plain NumPy arrays or any of the classes in the \package{astropy.nddata} subpackage.
-It features a class for representing two-dimensional image cutouts, allowing one to easily link pixels in the cutout to pixels in the original image or from the image to the cutout, and to overlay the cutout on images.
+It features a class for representing two-dimensional image cutouts, allowing one to easily link pixels in the cutout to pixels in the original image or from the image to the cutout, to convert between world and pixel coordinates in the cutout and to overlay the cutout on images.
 Functions to enlarge or reduce an image by doing block replication or reduction are also provided.
@@
 \inlinecomment{Should we mention that Cutout2D supports WCS to pixel conversions?}
+
+\inlinecomment{Yes, done.}
 
@@
 The goal is to make it easy to extend the fitting framework and create new fitters.
-The optimizers available in astropy 2.0 are Levenberg-Marquardt, Simplex, SLSQP, and LinearLSQFitter (which is based on \texttt{numpy.linalg} that provides exact solution for linear models).
+The optimizers available in \astropypkg 2.0 are Levenberg-Marquardt, Simplex, SLSQP, and LinearLSQFitter (which is based on \texttt{numpy.linalg} that provides exact solution for linear models).
 
@@
 astropy models with external fitters. An example of this is
-SABA\footnote{\url{https://github.com/astropy/saba}}, which is a bridge between
+\package{SABA}\footnote{\url{https://github.com/astropy/saba}}, which is a bridge between
 Sherpa\footnote{\url{http://cxc.cfa.harvard.edu/contrib/sherpa/}}
-and astropy.modeling, to bring the Sherpa fitters into astropy.
+and \package{astropy.modeling}, to bring the Sherpa fitters into astropy.
 
@@
 %
-\par In addition to astronomy related packages and libraries, the \astropy\
-Project also maintains and distributes several infrastructure packages that are
-very generic. The following sections describes the most widely used
-selection of them.
+\par In addition to astronomy related packages and libraries, the \astropy
+Project also maintains and distributes several generic purpose infrastructure packages.
+The following sections describes the most widely used selection of them.
 %
@@
 % Brigitta may write this up if there is no other takers
-\par \astropy provides a \package{package-template}\footnote{\url{https://github.com/astropy/package-template/}}
-package that any \python package is welcome to
-use (many affiliated packages do so). The template contains a ready-to-go
-package layout. It provides infrastructure such as documentation tools,
-testing framework and CI templates and configurations, Cython integration,
-and documentation on how to make it all work.
+%
+\par \astropy provides the \package{package-template}\footnote{\url{https://github.com/astropy/package-template/}}
+package. Using this template, any \python package can make use of the ready-to-go package
+layout, setup, installation and documentation infrastructure developed originally for the
+\astropypkg core package and affiliated packages maintained by the \astropy. It also provides
+a testing framework, CI templates and configurations, Cython integration, and documentation
+on how to make it all work.
 %
@@
 % Brigitta
+%
 \package{ci-helpers}\footnote{\url{https://github.com/astropy/ci-helpers}} is a
@@
 
-dropping \python 2 support, growths of affiliated packages
-Summary
-learning astropy
+dropping \python{} 2 support, growths of affiliated packages
+
+\subsection{Learning astropy}
 
@@
 is reviewed by at least one, but typically more, members of the
-astropy community, providing feedback and allowing contributors to
+\astropy community, providing feedback and allowing contributors to
 improve their skill is developing software without the need for their

### 2017-10-28 main.tex
comment out section that's realistically not going to get written
coordination stuff

@@
 % free to modify!
-The \astropy project supports and fosters the development of open-source and open-development
+The \astropy project supports and fosters the development of open-source and openly-developed
 \python packages that provide commonly-needed functionality to the astronomical
@@
 \subsection{Coordination of Astropy}
-\inlinecomment{EJT}
+From its inception, \astropy has required coordination to ensure the project as a whole and its coding efforts are consistent and reasonably efficient.
+While many Python projects adopt a ``Benevolent Dictator For Life'' (BDFL) model, Astropy has instead opted for a coordination \emph{committee}.
+This is in part due to the nature of the project as a large-scale collaboration between many contributors with many interests, and in part due to simply the amount of work that needs to get done.
+In part for the latter reason, the project has expanded the committee from three to four members from 2016 on.
+
+In the code itself, the coordination committee primarily acts to work toward consensus, or when consensus is difficult to achieve, generally acts as ``tie-breaker.''
+The committee also oversees affiliated package applications to ensure they are in keeping with \astropy's vision and philosophy, as well as the associated processes procedures.
+Additionally, the committee oversees the assignment of roles (primarily driven by already-existing contributions), and increasingly has acted as the ``face'' of the Project, providing contact with organizations like NumFOCUS (The body that holds any potential funding in trust for \astropy) or the AAS.
 
@@
 
-\subsubsection{Accuracy and comparison of coordinate system definitions}
+%\subsubsection{Accuracy and comparison of coordinate system definitions}
 % Erik?

### 2017-10-29 main.tex
Update on Overleaf.

@@
 % olebole: TOPCAT is part of Starlink Java. An other examples would be CASA resp. AIPS. I'd rather omit ds9, since it is mainly developed by one person.
+% timj: Starlink originally developed TOPCAT. Starlink is much better an example than DS9.
 SAO,][]{ds9}. These packages tend to address a wide range of users
@@
 \inlinecomment{BMS: TODO}{reference APE2 for versioning and APE10 for dropping python2 support}
+\inlinecomment{TR}{added a reference to APE10, will add APE2 once we upload that one to Zenodo}
+
 \inlinecomment{BMS}{shall we maybe refer to the release calendar, too?}
@@
 also the last one that supports \python 2, and will receive bug fixes until the
-end of 2019.
+end of 2019 \citep{ape10}.
 %

### 2017-10-29 main.tex
Update on Overleaf.

@@
 
+\subsubsection{Accuracy of coordinate transformations}
+
+In order to check the accuracy of the coordinate transformations in \package{astropy.coordinates}, we have set up a set of benchmarks that we use to compare transformations between a set of coordinate frames for a number of packages \footnote{\url{http://www.astropy.org/coordinates-benchmark/summary.html}}.
+
 \end{description}

### 2017-10-29 registry.tex
added citations to affiliated package table

@@
-\href{https://github.com/astropy/astroscrappy}{Astro-SCRAPPY} & Yes & \href{https://pypi.python.org/pypi/astroscrappy}{astroscrappy} & Curtis McCully \\
-\href{https://github.com/astropy/astroplan}{astroplan} & No & \href{https://pypi.python.org/pypi/astroplan}{astroplan} & Brett Morris \\
-\href{http://github.com/astropy/astroquery.git}{astroquery} & Yes & \href{https://pypi.python.org/pypi/astroquery}{astroquery} & Adam Ginsburg and Brigitta Sipocz \\
-\href{http://github.com/astropy/ccdproc.git}{ccdproc} & Yes & \href{https://pypi.python.org/pypi/ccdproc}{ccdproc} & Steven Crawford, Matt Craig, and Michael Seifert \\
-\href{https://github.com/jesford/cluster-lensing}{cluster-lensing} & No & \href{https://pypi.python.org/pypi/cluster-lensing}{cluster-lensing} & Jes Ford \\
-\href{https://github.com/adrn/gala}{gala} & Yes & \href{https://pypi.python.org/pypi/astro-gala}{astro-gala} & Adrian Price-Whelan \\
-\href{https://github.com/jobovy/galpy}{galpy} & Yes & \href{https://pypi.python.org/pypi/galpy}{galpy} & Jo Bovy \\
-\href{http://github.com/gammapy/gammapy.git}{gammapy} & No & \href{https://pypi.python.org/pypi/gammapy}{gammapy} & Christoph Deil \\
-\href{http://github.com/ejeschke/ginga}{ginga} & Yes & \href{https://pypi.python.org/pypi/ginga}{ginga} & Eric Jeschke and Pey-Lian Lim \\
-\href{https://github.com/glue-viz/glue.git}{Glue} & Yes & \href{https://pypi.python.org/pypi/glueviz}{glueviz} & Chris Beaumont and Thomas Robitaille \\
-\href{https://github.com/spacetelescope/gwcs.git}{gwcs} & No & \href{https://pypi.python.org/pypi/gwcs}{gwcs} & Nadia Dencheva \\
-\href{https://github.com/astropy/halotools}{Halotools} & Yes & \href{https://pypi.python.org/pypi/halotools}{halotools} & Andrew Hearin \\
-\href{http://github.com/spacetelescope/imexam}{imexam} & No & \href{https://pypi.python.org/pypi/imexam}{imexam} & Megan Sosey \\
-\href{https://github.com/Chandra-MARX/marxs}{marxs} & Yes & \href{https://pypi.python.org/pypi/marxs}{marxs} & Hans Moritz Günther (hamogu) \\
-\href{https://github.com/astropy/montage-wrapper}{montage-wrapper} & Yes & \href{https://pypi.python.org/pypi/montage-wrapper}{montage-wrapper} & Thomas Robitaille \\
-\href{https://github.com/zblz/naima}{naima} & Yes & \href{https://pypi.python.org/pypi/naima}{naima} & Victor Zabalza \\
-\href{http://github.com/astropy/photutils.git}{photutils} & No & \href{https://pypi.python.org/pypi/photutils}{photutils} & Larry Bradley and Brigitta Sipocz \\
-\href{http://github.com/weaverba137/pydl.git}{PyDL} & No & \href{https://pypi.python.org/pypi/pydl}{pydl} & Benjamin Alan Weaver \\
-\href{https://github.com/olebole/python-cpl}{python-cpl} & No & \href{https://pypi.python.org/pypi/python-cpl}{python-cpl} & Ole Streicher \\
-\href{https://github.com/astrofrog/reproject.git}{reproject} & Yes & \href{https://pypi.python.org/pypi/reproject}{reproject} & Thomas Robitaille \\
-\href{http://github.com/sncosmo/sncosmo}{sncosmo} & Yes & \href{https://pypi.python.org/pypi/sncosmo}{sncosmo} & Kyle Barbary \\
-\href{https://github.com/radio-astro-tools/spectral-cube}{spectral-cube} & Yes & \href{https://pypi.python.org/pypi/spectral-cube}{spectral-cube} & Adam Ginsburg \\
-\href{http://github.com/astropy/specutils.git}{specutils} & No & \href{https://pypi.python.org/pypi/specutils}{specutils} & Nicholas Earl, Adam Ginsburg, Steve Crawford \\
+\href{https://github.com/astropy/astroscrappy}{Astro-SCRAPPY} & Yes & \href{https://pypi.python.org/pypi/astroscrappy}{astroscrappy} & Curtis McCully & \citealt{astroscrappy} \\
+\href{https://github.com/astropy/astroplan}{astroplan} & No & \href{https://pypi.python.org/pypi/astroplan}{astroplan} & Brett Morris & \citealt{astroplan_AAS}\\
+\href{http://github.com/astropy/astroquery}{astroquery} & Yes & \href{https://pypi.python.org/pypi/astroquery}{astroquery} & Adam Ginsburg and Brigitta Sipocz & \citealt{astroquery}\\
+\href{http://github.com/astropy/ccdproc}{ccdproc} & Yes & \href{https://pypi.python.org/pypi/ccdproc}{ccdproc} & Steven Crawford, Matt Craig, and Michael Seifert & \citealt{ccdproc}\\
+\href{https://github.com/jesford/cluster-lensing}{cluster-lensing} & No & \href{https://pypi.python.org/pypi/cluster-lensing}{cluster-lensing} & Jes Ford & \citealt{clusterlensing} \\
+\href{https://github.com/adrn/gala}{gala} & Yes & \href{https://pypi.python.org/pypi/astro-gala}{astro-gala} & Adrian Price-Whelan & \citealt{gala}\\
+\href{https://github.com/jobovy/galpy}{galpy} & Yes & \href{https://pypi.python.org/pypi/galpy}{galpy} & Jo Bovy & \citealt{galpy}\\
+\href{http://github.com/gammapy/gammapy}{gammapy} & No & \href{https://pypi.python.org/pypi/gammapy}{gammapy} & Christoph Deil & \citealt{gammapy}\\
+\href{http://github.com/ejeschke/ginga}{ginga} & Yes & \href{https://pypi.python.org/pypi/ginga}{ginga} & Eric Jeschke and Pey-Lian Lim & \\
+\href{https://github.com/glue-viz/glue}{Glue} & Yes & \href{https://pypi.python.org/pypi/glueviz}{glueviz} & Chris Beaumont and Thomas Robitaille & \citealt{glue}\\
+\href{https://github.com/spacetelescope/gwcs}{gwcs} & No & \href{https://pypi.python.org/pypi/gwcs}{gwcs} & Nadia Dencheva & \\
+\href{https://github.com/astropy/halotools}{Halotools} & Yes & \href{https://pypi.python.org/pypi/halotools}{halotools} & Andrew Hearin & \citealt{halotools}\\
+\href{http://github.com/spacetelescope/imexam}{imexam} & No & \href{https://pypi.python.org/pypi/imexam}{imexam} & Megan Sosey & \\
+\href{https://github.com/Chandra-MARX/marxs}{marxs} & Yes & \href{https://pypi.python.org/pypi/marxs}{marxs} & Hans Moritz Günther (hamogu) & \citealt{marxs}\\
+\href{https://github.com/astropy/montage-wrapper}{montage-wrapper} & Yes & \href{https://pypi.python.org/pypi/montage-wrapper}{montage-wrapper} & Thomas Robitaille & \\
+\href{https://github.com/zblz/naima}{naima} & Yes & \href{https://pypi.python.org/pypi/naima}{naima} & Victor Zabalza & \citealt{naima}\\
+\href{http://github.com/astropy/photutils}{photutils} & No & \href{https://pypi.python.org/pypi/photutils}{photutils} & Larry Bradley and Brigitta Sipocz & \citealt{photutils} \\
+\href{http://github.com/weaverba137/pydl}{PyDL} & No & \href{https://pypi.python.org/pypi/pydl}{pydl} & Benjamin Alan Weaver & \\
+\href{https://github.com/olebole/python-cpl}{python-cpl} & No & \href{https://pypi.python.org/pypi/python-cpl}{python-cpl} & Ole Streicher & \\
+\href{https://github.com/astrofrog/reproject}{reproject} & Yes & \href{https://pypi.python.org/pypi/reproject}{reproject} & Thomas Robitaille & \\
+\href{http://github.com/sncosmo/sncosmo}{sncosmo} & Yes & \href{https://pypi.python.org/pypi/sncosmo}{sncosmo} & Kyle Barbary & \citealt{sncosmo}\\
+\href{https://github.com/radio-astro-tools/spectral-cube}{spectral-cube} & Yes & \href{https://pypi.python.org/pypi/spectral-cube}{spectral-cube} & Adam Ginsburg & \citealt{spectralcube}\\
+\href{http://github.com/astropy/specutils}{specutils} & No & \href{https://pypi.python.org/pypi/specutils}{specutils} & Nicholas Earl, Adam Ginsburg, Steve Crawford & \\

### 2017-10-29 registry_prov.tex
added citations to affiliated package table

@@
-\href{http://github.com/aplpy/aplpy.git}{APLpy} & Yes & \href{https://pypi.python.org/pypi/APLpy}{APLpy} & Thomas Robitaille and Eli Bressert \\
+\href{http://github.com/aplpy/aplpy}{APLpy} & Yes & \href{https://pypi.python.org/pypi/APLpy}{APLpy} & Thomas Robitaille and Eli Bressert \\
 \href{http://github.com/astroML/astroML}{astroML} & Yes & \href{https://pypi.python.org/pypi/astroML}{astroML} & Jake Vanderplas \\
@@
 \href{https://github.com/RiceMunk/omnifit}{omnifit} & Yes & \href{https://pypi.python.org/pypi/omnifit}{omnifit} & Aleksi Suutarinen \\
-\href{https://github.com/astropy/pyregion.git}{pyregion} & Yes & \href{https://pypi.python.org/pypi/pyregion}{pyregion} & Jae-Joon Lee \\
-\href{https://github.com/pyvirtobs/pyvo.git}{PyVO} & No & \href{https://pypi.python.org/pypi/pyvo}{pyvo} & Stefan Becker \\
-\href{https://github.com/spacetelescope/spherical_geometry.git}{spherical\_geometry} & No & \href{https://pypi.python.org/pypi/spherical-geometry}{spherical-geometry} & Bernie Simon and Michael Droettboom \\
+\href{https://github.com/astropy/pyregion}{pyregion} & Yes & \href{https://pypi.python.org/pypi/pyregion}{pyregion} & Jae-Joon Lee \\
+\href{https://github.com/pyvirtobs/pyvo}{PyVO} & No & \href{https://pypi.python.org/pypi/pyvo}{pyvo} & Stefan Becker \\
+\href{https://github.com/spacetelescope/spherical_geometry}{spherical\_geometry} & No & \href{https://pypi.python.org/pypi/spherical-geometry}{spherical-geometry} & Bernie Simon and Michael Droettboom \\

### 2017-10-29 main.tex
added citations to affiliated package table
Update on Overleaf.
another column

@@
 In order to check the accuracy of the coordinate transformations in \package{astropy.coordinates}, we have set up a set of benchmarks that we use to compare transformations between a set of coordinate frames for a number of packages \footnote{\url{http://www.astropy.org/coordinates-benchmark/summary.html}}.
+Since
+no package can be guaranteed to implement all transformations to arbitrary precision, and since some transformations are sometimes subject to interpretation of standards (in particular in the case of Galactic coordinates), we do not designate any of the existing packages as the 'ground truth' but instead compare each tool to all other tools to find.
+
+The benchmarks are set up as follows - we have generated a standard set of 1000 pairs of random longitudes/latitudes that we use in all benchmarks.
+Each benchmark is then defined using an input and output coordinate frame, and if relevant we
+
+Table \textbf{TODO} shows an example of comparison
 
@@
   \label{tab:registry}
-  \begin{tabular}{cccc}
+  \begin{tabular}{ccccc}
     \toprule
-    Package Name  & Stable & PyPI Name & Maintainer \\
+    Package Name  & Stable & PyPI Name & Maintainer & Citation \\
     \midrule

### 2017-10-29 main.tex
Update on Overleaf.

@@
 
-The benchmarks are set up as follows - we have generated a standard set of 1000 pairs of random longitudes/latitudes that we use in all benchmarks.
-Each benchmark is then defined using an input and output coordinate frame, and if relevant we
+The benchmarks are meant to evolve over time and include an increasing variety of cases.
+At the moment, the benchmarks are set up as follows - we have generated a standard set of 1000 pairs of random longitudes/latitudes that we use in all benchmarks.
+Each benchmark is then defined using an input and output coordinate frame, using , and for now we set the epoch of observation to J2000, and the frame to J2000 in the case of the FK5 and ecliptic frames and B1950 for the FK4 frame.
 

### 2017-10-29 main.tex
Update on Overleaf.

@@
 
+\inlinecomment{TR}{This is a first draft and I need to dig into the details again to finish some of the text, and I also need to make the table/figure}.
+
 In order to check the accuracy of the coordinate transformations in \package{astropy.coordinates}, we have set up a set of benchmarks that we use to compare transformations between a set of coordinate frames for a number of packages \footnote{\url{http://www.astropy.org/coordinates-benchmark/summary.html}}.
@@
 no package can be guaranteed to implement all transformations to arbitrary precision, and since some transformations are sometimes subject to interpretation of standards (in particular in the case of Galactic coordinates), we do not designate any of the existing packages as the 'ground truth' but instead compare each tool to all other tools to find.
+The benchmarks are thus useful beyond the Astropy project since they allow all of the tools to be compared to all other tools.
+The tools included in the benchmark at the moment include astropy, kapteyn, novas, palpy, pyast, and pyslalib.
+\textbf{NEED REFS}
 
@@
 At the moment, the benchmarks are set up as follows - we have generated a standard set of 1000 pairs of random longitudes/latitudes that we use in all benchmarks.
-Each benchmark is then defined using an input and output coordinate frame, using , and for now we set the epoch of observation to J2000, and the frame to J2000 in the case of the FK5 and ecliptic frames and B1950 for the FK4 frame.
-
-Table \textbf{TODO} shows an example of comparison
+Each benchmark is then defined using an input and output coordinate frame, using all combinations of FK4, FK5, Galactic, ICRS and Ecliptic frames.
+For now we set the epoch of observation to J2000, and the frame to J2000 in the case of the FK5 and ecliptic frames and B1950 for the FK4 frame, but in future we plan to include a larger variety of epochs and equinoxes, as well as tests of conversion to/from Altitude/Azimuth.
+
+For each benchmark, we convert the 1000 longitudes/latitudes from the input/output frame with all tools and quantify the comparison by looking at the median, minimum, maximum, and standard deviation of the absolute separation of the output coordinates from each pair of tools.
+Table \textbf{TODO} gives an example of the relative accuracy of the conversion from Galactic to FK4 coordinates for all pairs of tools.
+This shows that \textbf{Need to add discussion here}.
+
+The benchmarks also include all-sky plots that show trends in accuracy over the sky and can help diagnose issues.
+Figure \textbf{TODO} shows an example of the accuracy of the conversion from XX to XX and \textbf{insert insightful result here}.
 

### 2017-10-29 main.tex
2.3

--- 2017-10-29 main.tex
@@
 
-\subsection{Astropy development model, astropy ecosystem}
-\inlinecomment{Needs writing by EJT}
-
-This subsection should include some basic statistics about the contributors, commits, line of code etc. up to the 2.0 release when we know it.
+\subsection{Astropy development model}
+\inlinecomment{Adrian started this, but needs some filling in by EJT}
+
+Code is contributed to the \astropypkg core package or modified through ``pull
+requests'' (via \github) that often contain several \texttt{git} commits.
+Pull requests may fix bugs, implement new features, or improve or modify the
+infrastructure that supports the development and maintenance of the package.
+Individual pull requests are generally limited to a single conceptual addition
+or modification to make code review tractable.
+Pull requests that modify or add code to a specific subpackage must be reviewed
+and approved by one of the subpackage maintainers before it is merged into the
+core codebase.
+Bugs and feature requests are reported via the \github issue tracker and labeled
+with a set of possible labels that help classify and organize the issues.
+The development workflow is detailed in the \astropypkg
+documentation.\footnote{\emph{How to make a code contribution}, \url{http://docs.
+astropy.org/en/stable/development/workflow/development_workflow.html}}
+
+As of version XX, \astropypkg contains XX lines of code contributed by XX unique
+contributors over XX \texttt{git} commits.
+The majority of the commits were and are contributed by a subset of the
+contributor pool: XX percent of the commits were contributed by XX contributors.
 

### 2017-10-31 main.tex
Update on Overleaf.
learn section

@@
 
+\end{description}
+
 \subsubsection{Accuracy of coordinate transformations}
@@
 Figure \textbf{TODO} shows an example of the accuracy of the conversion from XX to XX and \textbf{insert insightful result here}.
-
-\end{description}
 
@@
 
-{\subsubsection{Circular Statistics}
+\subsubsection{Circular Statistics}
 
@@
 
-\subsection{Learning astropy}
+\subsection{Learn Astropy}
+% Adrian
+
+The \astropypkg core package documentation contains narrative descriptions of
+the package functionality along with detailed usage notes for functions,
+classes, and modules.
+While useful as a reference and for more advanced \python users, it is not the
+right entry-point for all users or learning environments.
+In the near future, we will launch a new resource for learning to use both the
+\astropypkg core package and the many packages in the broader \astropy
+ecosystem, under the name '\emph{Learn Astropy}.'
+
+The new \emph{Learn Astropy} site will present several different ways to engage
+with the \astropy ecosystem:
+\begin{description}
+    \item[Documentation] The \astropypkg and affiliated package documentation
+        contain the complete description of a package with all requisite
+        details, including usage, dependencies, and examples.
+        The pages will largely remain as-is, but will be focused towards more
+        intermediate users and as a reference resource.
+    \item[Examples] These are stand-alone code snippets that live in the
+        \astropypkg documentation that demonstrate a specific functionality
+        within a subpackage.
+        The \astropypkg core package documentation will then gain a new ``index
+        of examples'' that links to all of the code or demonstrative examples
+        within any documentation page.
+    \item[Tutorials] The \astropy tutorials are step-by-step demonstrations of
+        common tasks that incorporate several packages or subpackages.
+        Tutorials are more extended and comprehensive than examples, may contain
+        exercises for the users, and are generally geared towards workshops or
+        teaching.
+        Several tutorials already
+        exist\footnote{\url{http://tutorials.astropy.org/}} and are being
+        actively expanded.
+    \item[Guides] These are long-form narrative, comprehensive,
+        conceptually-focused documents (roughly one book chapter in length)
+        providing stand-alone introductions to core packages in addition to the
+        underlying astronomical concepts.
+        These are less specific and more conceptual than tutorials.
+        For example, ``using \astropypkg and \package{ccdproc} to reduce imaging
+        data.''
+\end{description}
+We encourage any users who wish to see specific material to either contribute or
+comment on these efforts via the \astropy mailing list or \astropy-tutorials
+\github repository.\footnote{\url{https://github.com/astropy/astropy-tutorials}}
 

### 2017-10-31 main.tex
Update on Overleaf.

@@
 
-As of version XX, \astropypkg contains XX lines of code contributed by XX unique
-contributors over XX \texttt{git} commits.
-The majority of the commits were and are contributed by a subset of the
-contributor pool: XX percent of the commits were contributed by XX contributors.
+As of version 2.0, \astropypkg contains $212244$ lines of code \footnote{This line count includes comments, as these are often as important for maintainability as the code itself.
+Without comments there are $142197$ lines of code} contributed by $232$ unique
+contributors over $19270$ \texttt{git} commits.
+The commit distribution follows an approximate power-law (with log-slope of $\sim -0.47$), meaning most of the commits were and are contributed by a relatively small fraction of the contributor pool.
+$\sim 50$ percent of the commits were contributed by the top $4$ contributors, while $\sim 90$ percent of the commits came from the top $24$.
 

### 2017-10-31 main.tex
affiliated package table in landscape mode
change table to deluxetable environment
opening quote

@@
 \astropypkg core package and the many packages in the broader \astropy
-ecosystem, under the name '\emph{Learn Astropy}.'
+ecosystem, under the name `\emph{Learn Astropy}.'
 
@@
 
-\begin{table}[h]
-  \centering
-  \caption{Registry of affiliated packages.}
+\begin{longrotatetable}
+  \begin{deluxetable*}{ccccc}
+    \tablecaption{Registry of affiliated packages.}
     \label{tab:registry}
-  \begin{tabular}{ccccc}
-    \toprule
-    Package Name  & Stable & PyPI Name & Maintainer & Citation \\
-    \midrule
+    \tablehead{
+        \colhead{Package Name} &
+        \colhead{Stable} &
+        \colhead{PyPI Name} &
+        \colhead{Maintainer} &
+        \colhead{Citation}
+      }
+      \startdata
         \input{registry.tex}
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-\begin{table}[h]
-  \centering
-  \caption{Registry of provisionally accepted affiliated packages.}
+      \enddata
+  \end{deluxetable*}
+\end{longrotatetable}
+
+\begin{deluxetable*}{cccc}
+  \tablecaption{Registry of provisionally accepted affiliated packages.}
   \label{tab:registry_prov}
-  \begin{tabular}{cccc}
-    \toprule
-    Package Name  & Stable & PyPI Name & Maintainer \\
-    \midrule
+    \tablehead{
+        \colhead{Package Name} &
+        \colhead{Stable} &
+        \colhead{PyPI Name} &
+        \colhead{Maintainer}
+      }
+    \startdata
       \input{registry_prov.tex}
-    \bottomrule
-  \end{tabular}
-\end{table}
+    \enddata
+\end{deluxetable*}
 

### 2017-10-31 main.tex
spell out AAS

@@
 The committee also oversees affiliated package applications to ensure they are in keeping with \astropy's vision and philosophy, as well as the associated processes procedures.
-Additionally, the committee oversees the assignment of roles (primarily driven by already-existing contributions), and increasingly has acted as the ``face'' of the Project, providing contact with organizations like NumFOCUS (The body that holds any potential funding in trust for \astropy) or the AAS.
+Additionally, the committee oversees the assignment of roles (primarily driven by already-existing contributions), and increasingly has acted as the ``face'' of the Project, providing contact with organizations like NumFOCUS (The body that holds any potential funding in trust for \astropy) or the American Astronomical Society (AAS).
 

### 2017-10-31 main.tex
comment
remove unneeded packages
acknowledgments
opening quote

@@
 \documentclass[modern]{aastex61}
-\usepackage{hyperref}
 \usepackage{xspace}
-\usepackage{booktabs}
 \usepackage[utf8]{inputenc}
@@
 %draft by hamogu
+\inlinecomment{TODO}{subpackage vs sub-package need to be standardized throughout the paper}
+
 Central to the success of \astropy is an open environment where
@@
 Since
-no package can be guaranteed to implement all transformations to arbitrary precision, and since some transformations are sometimes subject to interpretation of standards (in particular in the case of Galactic coordinates), we do not designate any of the existing packages as the 'ground truth' but instead compare each tool to all other tools to find.
+no package can be guaranteed to implement all transformations to arbitrary precision, and since some transformations are sometimes subject to interpretation of standards (in particular in the case of Galactic coordinates), we do not designate any of the existing packages as the `ground truth' but instead compare each tool to all other tools to find.
 The benchmarks are thus useful beyond the Astropy project since they allow all of the tools to be compared to all other tools.
@@
 
-Who to thank?  numfocus,
+Who to thank?  numfocus, GSOC, Python Software Foundation
 

### 2017-10-31 main.tex
remove whitespace

@@
 
-As of version 2.0, \astropypkg contains $212244$ lines of code \footnote{This line count includes comments, as these are often as important for maintainability as the code itself.
+As of version 2.0, \astropypkg contains $212244$ lines of code\footnote{This line count includes comments, as these are often as important for maintainability as the code itself.
 Without comments there are $142197$ lines of code} contributed by $232$ unique

### 2017-11-01 main.tex
Update on Overleaf.

@@
 
-The \package{astropy.units} subpackage provides ...
-
-\subsubsection{Key new features}
-
-\begin{description}
-    \item[Speed improvements] ...
-    \item[Logarithmic units and magnitudes] ...
-    \item[Interaction with \package{numpy} arrays] ...
-\end{description}
+The \package{Units} and \package{Quantities} packages were described in detail in \cite{astropy}.
+
+%\subsubsection{Key new features}
+
+%\begin{description}
+%    \item[Speed improvements] ...
+%    \item[Logarithmic units and magnitudes] ...
+%    \item[Interaction with \package{numpy} arrays] ...
+%\end{description}
 
@@
 
-versioning
+The \package{Constants} package provides useful physical constants as quantities.
+The package was described in \cite{astropy}.
+\package{Constants} now include their own version to track when their values are adjusted.
 
@@
 
-\inlinecomment{SCO}{Q: does it make sense to refer forward to FITS support, even though it is 3.0?}
-\inlinecomment{BMS}{what about moving it into the future section below?}
-
-Uses ERFA \citep{erfa}...
+\inlinecomment{SCO}{Q: does it make sense to refer forward to FITS support, even though it is 3.0?-- If you want to say something add it to the future section, but I'd say no.}
+
+Time and date functionality, especially those relevant to astronomy, are dealt by the \package{Time} package.
+The package was described in detail in \cite{astropy}.
+The \package{Time} package is currently built on ERFA \citep{erfa}, which replicates the functionality of SOFA \cite{sofa} but is licensed under a three-clause BSD license.
 
@@
 
-\inlinecomment{Should I mention the fact that there will be changes coming to 3.0?}
+\inlinecomment{Should I mention the fact that there will be changes coming to 3.0? -- If you want to say something add it to the future section}
 
@@
 
-QTable is new, mixin columns for time and coordinates. Table operations were added in v0.3
+The \package{Tables} package provides wrappers to \package{NumPy} structure arrays, which can contain heterogeneous data sets.
+The package was described in detail in \cite{astropy}.
+Tables now has the ability to work with other astropy classes including Quantities, Time, and Coordinates.
+In addition, operations can also be performed on Tables.
+
+%QTable is new, mixin columns for time and coordinates. Table operations were added in v0.3
 
@@
   e.g. pytest-astropy and sphinx-astropy?}
-\subsection{Roadmap for \python 3 only support}
-
-dropping \python{} 2 support, growths of affiliated packages
+\inlinecomment{SMC}{I've added a rough first draft -- please feel free to edit}
+%\subsection{Roadmap for \python 3 only support}
+
+Development has continued after the release of v2.0 of \package{astropy}.
+The most significant development for the next release will be removing python 2 support \cite{python 3 APE}.
+While the v2.0 release is a ‘long term stable’ release )meaning that it will be supported through 2019 in both python 2 and python 3), the v3.0 \package{astropy} release will only support python 3.
+This will allow the use of the new functionality in python 3, simplify the code base, and reducing the testing overhead.
+The v3.0 release is currently scheduled for December 2017.
+
+In the release cycle after v3.0, the \astropy project will focus on optimization of the code and improved documentation for the v3.1 release.
+To prepare for this release, software for testing and monitoring the performance of the code are being developed.
+Less new functionality may be introduced in this release, but the focus will be primarily on improved performance.
+In addition, a new suite of tutorials and documentation are being prepared for this release.
+
+Beyond the core code, the \astropy project is also further developing the affiliated packages.
+This includes elevating a suite of packages into part of the core project.
+While these may not be integrated into the core code, these projects provide code that is useful to the astronomical community and meet the testing and documentation standards of \astropy.
+Some of these new efforts includes an initiative to develop tools for spectroscopy , integration of LSST software , and packages to support HEALPIX projection.
 

### 2017-11-03 main.tex
Update on Overleaf.

@@
 
-\inlinecomment{David S.}
-
-The \package{Constants} package provides useful physical constants as quantities.
-The package was described in \cite{astropy}.
-\package{Constants} now include their own version to track when their values are adjusted.
+%David S.
+
+The \package{Constants} package provides a selection of physical and astronomical
+constants as quantities.  A brief description was given in \cite{astropy}. 
+For version 2.0, constants have been organized into modules for specific versions.
+Physical constants include CODATA2014 and CODATA2010 versions. Astronomical constants
+are organized into IAU2015 and IAU2012 versions to roughly indicate their sources.
+The CODATA2014 and IAU2015 versions are combined into the default ASTROPYCONST20
+version. For astropy v1.3 and earlier, the ASTROPYCONST13 namespace is available;
+however when using previous versions of the constants, \package{Constants} should be used
+directly; \package{astropy.units} will be initialized to the ASTROPYCONST20 versions.
+
+Astronomers using \package{Constants} should take particular note of the constants
+provided for Earth, Jupiter and the Sun. Following IAU 2015 Resolution B3, nominal
+values are now given for masses and radii. The nominal values will not change as
+estimates of these proper
 

### 2017-11-03 registry.tex
added ginga
bibliography

@@
 \href{http://github.com/gammapy/gammapy}{gammapy} & No & \href{https://pypi.python.org/pypi/gammapy}{gammapy} & Christoph Deil & \citealt{gammapy}\\
-\href{http://github.com/ejeschke/ginga}{ginga} & Yes & \href{https://pypi.python.org/pypi/ginga}{ginga} & Eric Jeschke and Pey-Lian Lim & \\
+\href{http://github.com/ejeschke/ginga}{ginga} & Yes & \href{https://pypi.python.org/pypi/ginga}{ginga} & Eric Jeschke and Pey-Lian Lim & \citealt{ginga}\\
 \href{https://github.com/glue-viz/glue}{Glue} & Yes & \href{https://pypi.python.org/pypi/glueviz}{glueviz} & Chris Beaumont and Thomas Robitaille & \citealt{glue}\\
-\href{https://github.com/spacetelescope/gwcs}{gwcs} & No & \href{https://pypi.python.org/pypi/gwcs}{gwcs} & Nadia Dencheva & \\
+\href{https://github.com/spacetelescope/gwcs}{gwcs} & No & \href{https://pypi.python.org/pypi/gwcs}{gwcs} & Nadia Dencheva & \citealt{gwcs}\\
 \href{https://github.com/astropy/halotools}{Halotools} & Yes & \href{https://pypi.python.org/pypi/halotools}{halotools} & Andrew Hearin & \citealt{halotools}\\

### 2017-11-03 main.tex
Update on Overleaf.

--- 2017-11-01 main.tex
@@
 
-\inlinecomment{David S.}
-
-The \package{Constants} package provides useful physical constants as quantities.
-The package was described in \cite{astropy}.
-\package{Constants} now include their own version to track when their values are adjusted.
+%David S.
+
+The \package{Constants} package provides a selection of physical and astronomical
+constants as quantities.  A brief description was given in \cite{astropy}. 
+For version 2.0, constants have been organized into modules for specific versions.
+Physical constants include \texttt{codata2014} \citep{codata2014}
+and \texttt{codata2010} versions. Astronomical constants are organized 
+into \texttt{iau2015} and 
+\texttt{iau2012} modules to roughly indicate their sources.
+The \texttt{codata2014} and \texttt{iau2015} versions are combined 
+into the default \texttt{astropyconst20}
+version. For astropy v1.3 and earlier, the \texttt{astropyconst13} 
+namespace is available;
+however when using previous versions of the constants, 
+\package{Constants} should be used
+directly, since  \package{astropy.units} will be initialized to the 
+\texttt{astropyconst20} versions.
+
+Astronomers using \package{Constants} should take particular note of the
+constants provided for Earth, Jupiter and the Sun. Following IAU 2015 
+Resolution B3 \citep{iau2015b3}, nominal
+values are now given for mass parameters and radii. The nominal values 
+will not change even as ``current best estimates'' are updated.
+
+\inlinecomment{DavidS: we'd like to build on this to allow use of a
+context manager for selecting a version of constants. Here, or in the Future
+section?}
 

### 2017-11-06 registry.tex
python cpl

@@
 \href{http://github.com/weaverba137/pydl}{PyDL} & No & \href{https://pypi.python.org/pypi/pydl}{pydl} & Benjamin Alan Weaver & \\
-\href{https://github.com/olebole/python-cpl}{python-cpl} & No & \href{https://pypi.python.org/pypi/python-cpl}{python-cpl} & Ole Streicher & \\
+\href{https://github.com/olebole/python-cpl}{python-cpl} & No & \href{https://pypi.python.org/pypi/python-cpl}{python-cpl} & Ole Streicher & \citealt{pythoncpl}\\
 \href{https://github.com/astrofrog/reproject}{reproject} & Yes & \href{https://pypi.python.org/pypi/reproject}{reproject} & Thomas Robitaille & \\

### 2017-11-08 main.tex
Update on Overleaf.

@@
 
-\section*{\textit{Notes and guidelines (to be removed)}}
+l\section*{\textit{Notes and guidelines (to be removed)}}
 
@@
 
+\inlinecomment{Tom R}{at the moment this section doesn't take into account that APEs can be unrelated to code (e.g. APE 8 for the code of conduct)}
+
 Central to the success of \astropy is an open environment where
@@
 needed, how it should be implemented, and what the interface will
-be. These APEs are discussed and refined before much work is invested
+be \citep{ape1}. These APEs are discussed and refined before much work is invested
 into a detailed implementation. APEs are again edited and discussed on
@@
 % Brigitta can writes this up if there's no other taker
-\inlinecomment{BMS: TODO}{reference APE2 for versioning and APE10 for dropping python2 support}
-\inlinecomment{TR}{added a reference to APE10, will add APE2 once we upload that one to Zenodo}
-
 \inlinecomment{BMS}{shall we maybe refer to the release calendar, too?}
@@
 6 months, and between feature releases additional bugfix releases that
-contain only bugfixes but no new features.
+contain only bugfixes but no new features \citep{ape2}.
 % The timing of
@@
 Fundamental Astronomy (SOFA) effort \citep{sofa}.
+% timj: The preferred SOFA reference is usually https://ui.adsabs.harvard.edu/#abs/2011SchpJ...611404H/abstract rather than a URL to the SOFA web site.
 
@@
 
-\inlinecomment{Should we mention that Cutout2D supports WCS to pixel conversions?}
-
-\inlinecomment{Yes, done.}
-
 %Larry:  Don't forget the nddata.utils functionality (e.g. Cutout2D, block\_reduce, %etc.).
@@
 \label{sec:table}
-
-\inlinecomment{Tom A.}
 
@@
 
-\inlinecomment{SCO}{Pyfits deprecation in favor of io.fits ?}
-\inlinecomment{SCO}{Table and FITS tables}
-
-\subsubsection{Unified file read/write interface}
-
-TODO: Check when it was added (0.3?). Overview of the supported formats (ASCII,
-FITS, votable, HTML, JSViewer/Datatables).
+%\inlinecomment{SCO}{Pyfits deprecation in favor of io.fits ?}
+%\inlinecomment{SCO}{Table and FITS tables}
+
+%\subsubsection{Unified file read/write interface}
+
+%\inlinecomment{Check when it was added (0.3?). Overview of the supported formats (ASCII,FITS, votable, HTML, JSViewer/Datatables).}
 
@@
 
-\inlinecomment{SCO}{One subsection per format (if enough new features) ?}
-\inlinecomment{BMS}{Do we really need to mention the old version numbers in the list below when a feature was added?}
-
 \begin{description}
 
-    \item[ASCII: fast reader/writer (v1.0)]
+    \item[ASCII: fast reader/writer]
 
@@
 
-    \item[ASCII: HTML tables (v0.4)]
+    \item[ASCII: HTML tables]
 
@@
 
-	\item [Enhanced CSV format (v1.0)]
+	\item [Enhanced CSV format ]
 
@@
 
-	\item [FITS: command-line scripts (\texttt{fitsheader}, \texttt{fitsinfo}, v0.4)]
+	\item [FITS: command-line scripts (\texttt{fitsheader}, \texttt{fitsinfo})]
 
@@
 
-	\item [FITS: lazy loading (v1.3)]
+	\item [FITS: lazy loading ]
 
@@
 
-	\item [Misc: YAML serialization (v1.3)]
+	\item [Misc: YAML serialization ]
 
@@
 
-\inlinecomment{BMS}{Maybe move the command line tools into a separate subsection to highlight them (even though we mostly only have fits related scripts)?
+%\inlinecomment{BMS}{Maybe move the command line tools into a separate subsection to highlight them (even though we mostly only have fits related scripts)?
 They are supposed to be used more frequently by individual users.}
-\inlinecomment{hamogu}{MY feeling is that this section is too detailed already. If I had written it, I would not have mentioned the scripts at all.}
+%\inlinecomment{hamogu}{MY feeling is that this section is too detailed already. If I had written it, I would not have mentioned the scripts at all.}
 
@@
 This functionality was contributed by developers from the Large Synoptic Survey Telescope (LSST) and serves as an example of contribution to Astropy from a more traditional engineering organization \citep{lsst_astropy}.
+% Please cite the final SPIE paper here rather than the presentation slides at that conference.
+% https://ui.adsabs.harvard.edu/#abs/2016SPIE.9913E..0GJ/abstract (I'm not sure how to edit the bib file on overleaf)
 
@@
 Development has continued after the release of v2.0 of \package{astropy}.
-The most significant development for the next release will be removing python 2 support \cite{python 3 APE}.
+The most significant development for the next release will be removing python 2 support \cite{ape10}.
 While the v2.0 release is a ‘long term stable’ release )meaning that it will be supported through 2019 in both python 2 and python 3), the v3.0 \package{astropy} release will only support python 3.

### 2017-11-10 main.tex
Address Tom Rs comments about APE section

@@
 
-l\section*{\textit{Notes and guidelines (to be removed)}}
+\section*{\textit{Notes and guidelines (to be removed)}}
 
@@
 
+\section*{Global TODO items}
+\begin{itemize}
+    \item subpackage vs sub-package need to be standardized throughout the paper
+    \item spell check!
+\end{itemize}
+
 \section{Introduction} \label{sec:intro}
@@
 
-At the same time, an ecosystem of tools, programs, and webservices
+At the same time, an ecosystem of tools, programs, and web services
 has become available that makes it easier to collaborate on code development,
@@
 %draft by hamogu
-\inlinecomment{TODO}{subpackage vs sub-package need to be standardized throughout the paper}
-
-\inlinecomment{Tom R}{at the moment this section doesn't take into account that APEs can be unrelated to code (e.g. APE 8 for the code of conduct)}
-
-Central to the success of \astropy is an open environment where
-anybody can contribute to the code by opening a so-called ``pull
-request'' with a new code contribution on a publically available
-website\footnote{\url{https://github.com/astropy/astropy}}; this
-request is then reviewed by at least one of the maintainers responsible for the specific
-sub-package and possibly merged into the main code base. Most bug
-fixes and small features are contributed in this way. However, this
-model leads to ``organic'' growth where different features are
+%edited by Adrian PW
+
+Central to the success of \astropy is an open environment where anybody can
+contribute to the project by opening a so-called ``pull request'' with a new
+contribution on a publically available
+website\footnote{\url{https://github.com/astropy/astropy}}.
+This request is then reviewed by at least one of the maintainers responsible for
+the specific subpackage or content and is possibly merged into the main code
+base.
+Most bug fixes, documentation edits, and small features are contributed in this
+way.
+However, this model leads to ``organic'' growth where different features are
 implemented by different people with different programming styles and
-interfaces. Thus, \astropy has a mechanism to more formally propose
-changes to the code management (e.g.~the release cycle) or to plan
-out major new features. This mechanism is called ``Astropy Proposal
-for Enhancement'' (APE). In an APE one or more authors lay out a
-vision for a new feature, including a rationale why this feature is
-needed, how it should be implemented, and what the interface will
-be \citep{ape1}. These APEs are discussed and refined before much work is invested
-into a detailed implementation. APEs are again edited and discussed on
-a platform\footnote{\url{https://github.com/astropy/astropy-APEs}}
-open to the public. In previous APEs a community consensus emerged and
-APEs are accepted and become the basis for future work at this
-point. In cases where consensus cannot be reached, the
+interfaces.
+Thus, \astropy has a mechanism to more formally propose significant changes to
+the core package (e.g., the release cycle; \citealt{ape2}), to plan out major
+new features, or institute new organization-wide policies (e.g.,
+\citealt{ape8}}).
+This mechanism is called ``Astropy Proposal for Enhancement'' (APE) and are
+modeled after the ``Python Enhancement Proposals'' (PEP) and guide the
+development of the \python programming language.
+In an APE one or more authors describe in detail the proposed changes or
+additions, including a rationale for the changes, how these changes will be
+implemented, and, in the case of code, what the interface will be \citep{ape1}.
+The APEs are discussed and refined by the community before much work is invested
+into a detailed implementation; anyone is welcome to contribute to these
+discussions during the open consideration period by leaving comments on the
+respective pull request.\footnote{\url{https://github.com/astropy/astropy-APEs}}
+In previous APEs a community consensus emerged and APEs are accepted and become
+the basis for future work at this point.
+In cases where consensus cannot be reached, the
 \astropy coordination committee can decide to close the discussion and
-make an executive decision based on the community input on the APE in
-question. APEs are modeled after the ``Python Enhancement Proposals''
-(PEP) and guide the development of the \python programming language.
+make an executive decision based on the community input on the APE in question.
 

### 2017-11-10 main.tex
subpackage

@@
 \begin{itemize}
-    \item subpackage vs sub-package need to be standardized throughout the paper
+    \item subpackage not sub-package!
     \item spell check!
@@
 
-		The \package{astropy.io.ascii} sub-package now provides the capability
+		The \package{astropy.io.ascii} subpackage now provides the capability
 		to read a table within an HTML file or web URL into an astropy
@@
 
-		The \package{astropy.io.fits} sub-package now provides a command line
+		The \package{astropy.io.fits} subpackage now provides a command line
 		script for inspecting the header(s) of a FITS file.  Running
@@
 
-		The \package{astropy.io.fits} sub-package now supports \emph{lazy
+		The \package{astropy.io.fits} subpackage now supports \emph{lazy
 		loading}, where all HDUs are not loaded until they are requested (or

### 2017-11-10 main.tex
clean up dev model section

@@
 \subsection{APEs - Astropy Proposals for Enhancement}
-%draft by hamogu
-%edited by Adrian PW
+% draft by hamogu
+% edited by Adrian PW
 
@@
 \subsection{Astropy development model}
-\inlinecomment{Adrian started this, but needs some filling in by EJT}
+% draft by Adrian PW and Erik T.
 
@@
 
-As of version 2.0, \astropypkg contains $212244$ lines of code\footnote{This line count includes comments, as these are often as important for maintainability as the code itself.
-Without comments there are $142197$ lines of code} contributed by $232$ unique
-contributors over $19270$ \texttt{git} commits.
-The commit distribution follows an approximate power-law (with log-slope of $\sim -0.47$), meaning most of the commits were and are contributed by a relatively small fraction of the contributor pool.
-$\sim 50$ percent of the commits were contributed by the top $4$ contributors, while $\sim 90$ percent of the commits came from the top $24$.
+As of version 2.0, \astropypkg contains $212244$ lines of code\footnote{This
+line count includes comments, as these are often as important for
+maintainability as the code itself.  Without comments there are $142197$ lines
+of code.} contributed by $232$ unique contributors over $19270$ \texttt{git}
+commits.
+The commit distribution follows an approximate power-law (with log-slope of
+$\sim -0.47$), meaning most of the commits were and are contributed by a
+relatively small fraction of the contributor pool.
+$\approx 50$ percent of the commits were contributed by the top $4$
+contributors, while $\sim 90$ percent of the commits came from the top $24$
+contributors.
 

### 2017-11-10 main.tex
some editing and fix sofa citation

@@
 \label{sec:concepts}
-% Anyone want to take this??
 
 \subsection{Coordination of Astropy}
+% draft by ??
+% edited by Adrian PW
+
 From its inception, \astropy has required coordination to ensure the project as a whole and its coding efforts are consistent and reasonably efficient.
-While many Python projects adopt a ``Benevolent Dictator For Life'' (BDFL) model, Astropy has instead opted for a coordination \emph{committee}.
+While many Python projects adopt a ``Benevolent Dictator For Life'' (BDFL) model, \astropy has instead opted for a \emph{coordination committee}.
 This is in part due to the nature of the project as a large-scale collaboration between many contributors with many interests, and in part due to simply the amount of work that needs to get done.
-In part for the latter reason, the project has expanded the committee from three to four members from 2016 on.
-
-In the code itself, the coordination committee primarily acts to work toward consensus, or when consensus is difficult to achieve, generally acts as ``tie-breaker.''
-The committee also oversees affiliated package applications to ensure they are in keeping with \astropy's vision and philosophy, as well as the associated processes procedures.
-Additionally, the committee oversees the assignment of roles (primarily driven by already-existing contributions), and increasingly has acted as the ``face'' of the Project, providing contact with organizations like NumFOCUS (The body that holds any potential funding in trust for \astropy) or the American Astronomical Society (AAS).
+In part for the latter reason, the project has expanded the committee from three to four members starting in 2016.
+
+For resolving disagreements about the \astropypkg core package or other \astropy-managed code, the coordination committee primarily acts to work toward consensus, or when consensus is difficult to achieve, generally acts as ``tie-breaker.''
+The committee also oversees affiliated package applications to ensure they are in keeping with \astropy's vision and philosophy, as well as the associated procedures.
+Additionally, the committee oversees the assignment of roles (primarily driven by already-existing contributions), and increasingly has acted as the ``face'' of the Project, providing contact with organizations like NumFOCUS (the body that holds any potential funding in trust for \astropy) or the American Astronomical Society (AAS).
 
@@
 % write it up
-%
-\par A major part of the \astropy project is the concept of
+% edited by Adrian PW
+
+A major part of the \astropy project is the concept of
 ``Affiliated Packages''. An affiliated package is an astronomy-related
-\python~package that is not part of the \astropypkg core package, but
+\python package that is not part of the \astropypkg core package, but
 has requested to be included as part of the \astropy project's
@@
 improving code reuse, interoperability, and embracing good coding
-practices such as testing and thorough documentation. \astropypkg{}
-version 2.0 supports \python~2.7 and \python~3.4+, affiliated packages
-are strongly encouraged to support at least \python~3.x.
-%
-\par Affiliated packages contain functionality that is more specialized, or
-have license incompatibility, or have enough external dependencies (e.g. GUI
-libraries) that limit their integration possibility into the core and thus
-they are more suitable to be separate packages. Starting as an affiliate
-package is also seen as a good strategy for functionality that is aimed for
-the \astropypkg~core but is initially undergoing rapid development and can
-benefit from a different release cycle while stabilizing its API.
-%
-\par In general we hope that becoming an affiliated package is seen as
+practices such as testing and thorough documentation.
+Affiliated packages contain functionality that is more specialized,
+have license incompatibilities, or have external dependencies (e.g., GUI
+libraries) that make these packages more suitable to be separate from the
+\astropypkg core package.
+Affiliated packages may also be used to develop substantial, new functionality
+that will eventually be incorporated into the \astropypkg core package: as
+initially separate packages, the typically rapid development or new,
+experimental features may benefit from having a release cycle that is not tied
+to the \astropypkg core.
+
+In general we hope that becoming an affiliated package is seen as
 a good way for new and existing packages to gain exposure.
@@
 \inlinecomment{BMS}{TODO: write about the process of becoming affiliated, and project packages into the future section below}
-%
+
 %\subsection{Mixin}
@@
 % Brigitta can writes this up if there's no other taker
-\inlinecomment{BMS}{shall we maybe refer to the release calendar, too?}
-\inlinecomment{hamogu}{I don't think that's necessary. These details are in the docs, but not too important for a general paper.}
-\inlinecomment{BMS}{should we mention that v3.0 is the exception to the
-  version numbering scheme we use by not being 2.1?}
-\inlinecomment{hamogu}{No. This is a genral paper, those are details that will be unimportant very soon. }
-%
-\par The general scheme for the releases and version numbering that the core
-package has adopted is the following. \astropypkg has new feature releases every
-6 months, and between feature releases additional bugfix releases that
-contain only bugfixes but no new features \citep{ape2}.
-% The timing of
-%
-\par Long-term support (LTS) releases continue to receive bugfixes for 2
-years with no changes to the API\@. They are ideal for pipelines and other
-applications where API stability is essential. The latest LTS release is
-also the last one that supports \python 2, and will receive bug fixes until the
-end of 2019 \citep{ape10}.
-%
-\par The version numbering of \astropypkg reflects on the release scheme
-described above. The core package uses the form x.y.z, where x is advanced
-on LTS, y is advanced for a non-LTS feature release, and z is advanced on
-bugfix releases.
+% edited by Adrian PW
+
+As detailed in APE 2 \citep{ape2}, the \astropypkg release schedule
+
+The \astropypkg has a regular release schedule consisting of new significant
+releases every 6 months, with bugfix releases as needed \citep{ape2}.
+The major releases will contain new features or any significant changes, whereas
+the bugfix releases only contain fixes to code or documentation but no new
+features.
+Some versions are additionally designated as ``Long-term support'' (LTS)
+releases, which continue to receive bugfixes for 2 years following the release
+with no changes to the API.
+The LTS versions are ideal for pipelines and other applications where API
+stability is essential.
+The latest LTS release (v2.0) is also the last one that supports \python 2, and
+will receive bug fixes until the end of 2019 \citep{ape10}.
+
+The version numbering of the \astropypkg core package reflects this release
+scheme: the core package version number uses the form x.y.z, where ``x'' is
+advanced for LTS releases, ``y'' is advanced for non-LTS feature releases, and
+``z'' is advanced for bugfix releases.
 
@@
 Fundamental Astronomy (SOFA) effort \citep{sofa}.
-% timj: The preferred SOFA reference is usually https://ui.adsabs.harvard.edu/#abs/2011SchpJ...611404H/abstract rather than a URL to the SOFA web site.
 
@@
     \astropy-affiliated package \package{astroplan}\citep{astroplan_AAS}.
-%    \inlinecomment{APW}{TODO: cite zenodo entry for astroplan?}
-%    \inlinecomment{BMS}{better to cite the submitted or soon to be submitted paper, I made a placeholder for it.}
 

### 2017-11-10 main.tex
remove comment
units draft

@@
 We start by describing the way the \astropy project works and is
-organized in \sectionname~\ref{sec:concepts}.  The project develops a core
+organized in \sectionname~\ref{sec:org}.  The project develops a core
 package called \astropypkg (\sectionname~\ref{sec:core}) and several
@@
 
-\section{Major concepts}
-\label{sec:concepts}
+\section{Organization and infrastructure}
+\label{sec:org}
 
@@
 
-\subsection{Use of Quantities across package}
-% Marten and Tom R.
-
-{\bf Very rough first text!}
-
-Historically, it has been unusual to keep units as part of numbers, especially as speed was often deemed essential and quantities used to be slower than regular arrays.
-Hence, programs and functions expected to be fed parameters in particular units, as (hopefully) stated in their documentation.
-In \astropypkg~0.4, therefore, unit and quantity support was still somewhat spotty, but this has changed greatly.
-One of the riskiest classes was angles, where both degrees and radians were ``obvious'' default units to some.
-As a consequence, quantities are most fully integrated in the coordinates module (\sectionname~\ref{sec:coordinates}).
-In \astropypkg~2.0, one can also opt in to use quantities fully in tables, by using the {\tt QTable} class (see \sectionname~\ref{sec:table}).
-As a result, units in FITS tables are also well-supported.
-For most other modules, quantities are at least accepted, and often assumed by default.
-
-In the process, some standard wrappers have been defined that make defining functions that require quantities as input simpler.
-As an extension of this, we plan to define wrappers for functions that work on numbers that will automatically convert quantities to any required units.
-
 \subsection{Release cycle and Long Term Support}
@@
 \inlinecomment{BMS}{I suggest to order the subsection lexicographically as reading the draft the current order seemed very random (unlike at the docs page where they the grouping logic is obvious)}
-\subsection{Units and quantities}
-\label{sec:units}
-\inlinecomment{Marten, Adrian}{}
-
-The \package{Units} and \package{Quantities} packages were described in detail in \cite{astropy}.
-
-%\subsubsection{Key new features}
-
-%\begin{description}
-%    \item[Speed improvements] ...
-%    \item[Logarithmic units and magnitudes] ...
-%    \item[Interaction with \package{numpy} arrays] ...
-%\end{description}
+
+\subsection{Units and quantities}\label{sec:units}
+% Adrian, Marten
+
+% TODO: should this just be called "Units"? all other sections in here look like
+% they are named by the subpackage name -- quantity is an object within the
+% package
+
+The \texttt{astropy.units} subpackage adds support for representing units and
+numbers with associated units (``quantities'') in code.
+Historically, quantities in code have often been represented simply as numbers,
+with units implied or noted via comments in the code because of considerations
+about speed: having units associated with numbers inherently adds overhead to
+numerical operations.
+In \texttt{astropy.units}, \texttt{Quantity} objects subclass the \texttt{numpy}
+array object and has been designed with speed in mind.
+As of \astropypkg version 2.0, units and quantities are prevalent in most other
+\astropypkg subpackages and are thus a key concept for using the package as a
+whole.
+The motivation and key concepts behind this subpackage were described in detail
+in the previous paper \citep{astropy}, and thus here we primarily highlight new
+features and improvements.
+
+\begin{description}
+    \item[Speed improvements] ...
+    \item[Logarithmic units and magnitudes] ...
+    \item[Using quantities in tables] In \astropypkg~2.0, one can also opt in to
+        use quantities fully in tables, by using the {\tt QTable} class (see
+        \sectionname~\ref{sec:table}). As a result, units in FITS tables are also
+        well-supported. For most other modules, quantities are at least
+        accepted, and often assumed by default.
+    \item[Defining functions that require quantities] In the process, some
+        standard wrappers have been defined that make defining functions that
+        require quantities as input simpler. As an extension of this, we plan to
+        define wrappers for functions that work on numbers that will
+        automatically convert quantities to any required units.
+    \item[Interaction with \package{numpy} arrays] ...
+\end{description}
 
@@
 % Commenting out unless a clear statement is added
-
-%\section{Learning Astropy}
-%\label{sec:learning}
-% Kelle, Adrian
-%\inlinecomment{BMS}{would astropy learn mature enough to described in the paper, or maybe it should go as a subsection for the next, future of astropy section?}
-
-%Explain components: Documentation, Tutorials, and lessons
 

### 2017-11-10 main.tex
typo
more units

@@
 new features, or institute new organization-wide policies (e.g.,
-\citealt{ape8}}).
+\citealt{ape8}).
 This mechanism is called ``Astropy Proposal for Enhancement'' (APE) and are
@@
 
+\inlinecomment{APW}{This needs to be finished:}
 In general we hope that becoming an affiliated package is seen as
@@
 \label{sec:core}
-
+% Adrian
 The \astropy project aims to provide \python-based packages for all tasks that
@@
 whole.
+Units are intimately entwined in the definition of astronomical coordinates and
+thus nearly all functionality in the \texttt{astropy.coordinates} subpackage
+(see \sectionname~\ref{sec:coordinates}) depends on this functionality.
+For most other subpackages, quantities are at least accepted, and often expected
+by default.
+
 The motivation and key concepts behind this subpackage were described in detail
@@
 \begin{description}
-    \item[Speed improvements] ...
-    \item[Logarithmic units and magnitudes] ...
-    \item[Using quantities in tables] In \astropypkg~2.0, one can also opt in to
-        use quantities fully in tables, by using the {\tt QTable} class (see
-        \sectionname~\ref{sec:table}). As a result, units in FITS tables are also
-        well-supported. For most other modules, quantities are at least
-        accepted, and often assumed by default.
-    \item[Defining functions that require quantities] In the process, some
-        standard wrappers have been defined that make defining functions that
-        require quantities as input simpler. As an extension of this, we plan to
-        define wrappers for functions that work on numbers that will
-        automatically convert quantities to any required units.
-    \item[Interaction with \package{numpy} arrays] ...
+    \item[Speed improvements] \inlinecomment{TODO}{Marten}
+    \item[Logarithmic units and magnitudes] \inlinecomment{TODO}{Marten}
+    \item[Using quantities in tables] The \texttt{astropy.table} subpackage (see
+        \sectionname~\ref{sec:table}) now supports using quantities in tables
+        with the \texttt{QTable} class.
+        As a result, units specified in FITS tables are supported, and tables
+        with quantities can be read and written to various file formats.
+    \item[Defining functions that require quantities] When writing code or
+        functions that expect \texttt{Quantity} objects, we often want to
+        enforce that the input units have the correct type.
+        For example, we may want to require only length-type \texttt{Quantity}
+        objects.
+        These requirements often lead to implementing repetitive code for
+        validating \texttt{Quantity} inputs.
+        \texttt{astropy.units} now provides a \python decorator
+        (\texttt{quantity_input}) that does this verification automatically.
+    \item[Interaction with \package{numpy} arrays] \inlinecomment{TODO}{Marten}
 \end{description}

### 2017-11-10 main.tex
logarithmic

@@
     \item[Speed improvements] \inlinecomment{TODO}{Marten}
-    \item[Logarithmic units and magnitudes] \inlinecomment{TODO}{Marten}
+    \item[Logarithmic units and magnitudes] By default, taking the logarithm of
+        a \texttt{Quantity} object with non-dimensionless units intentionally
+        fails.
+        However, some well-known units are actually logarithmic quantities,
+        where the logarithm of the value is taken with respect to some reference
+        value.
+        Examples include astronomical magnitudes, which are logarithmic fluxes,
+        and decibels, which are more generic logarithmic ratios of quantities.
+        Logarithmic, relative units are now supported in \texttt{astropy.units}.
     \item[Using quantities in tables] The \texttt{astropy.table} subpackage (see

### 2017-11-10 main.tex
remove duplication

@@
 
-As detailed in APE 2 \citep{ape2}, the \astropypkg release schedule
-
 The \astropypkg has a regular release schedule consisting of new significant
@@
         \texttt{astropy.units} now provides a \python decorator
-        (\texttt{quantity_input}) that does this verification automatically.
+        (\texttt{quantity\_input}) that does this verification automatically.
     \item[Interaction with \package{numpy} arrays] \inlinecomment{TODO}{Marten}

### 2017-11-10 main.tex
units section

@@
 
-\subsection{Units and quantities}\label{sec:units}
-% Adrian, Marten
-
-% TODO: should this just be called "Units"? all other sections in here look like
-% they are named by the subpackage name -- quantity is an object within the
-% package
+\subsection{Units}\label{sec:units}
+% Adrian
 
 The \texttt{astropy.units} subpackage adds support for representing units and
-numbers with associated units (``quantities'') in code.
+numbers with associated units --- ``quantities'' --- in code.
 Historically, quantities in code have often been represented simply as numbers,
@@
 \begin{description}
-    \item[Speed improvements] \inlinecomment{TODO}{Marten}
+    \item[Interaction with \package{numpy} arrays] The \texttt{Quantity} object
+        is now a subclass of the \texttt{numpy.ndarray} object and therefore
+        works well with many of the functions in \texttt{numpy} that support
+        array operations. For example, \texttt{Quantity} objects with angular
+        units can be passed in to the trigonometric functions implemented in
+        \texttt{numpy} (e.g., \texttt{numpy.cos}) and do the right thing: the
+        units are internally converted to radians (what the \texttt{numpy}
+        trigonometric functions expect) before being passed to \texttt{numpy}.
+    \item[Speed improvements] The \texttt{Quantity} object is now significantly
+        faster than in early versions of \astropypkg. This is in large part due
+        to the fact that \texttt{Quantity} subclasses the \texttt{numpy.ndarray}
+        object, but even relative to more recent versions of \astropypkg,
+        operations with \texttt{Quantity} objects are generally faster. This is
+        largely thanks to improvements in the way \texttt{numpy} arrays can be
+        subclassed.
     \item[Logarithmic units and magnitudes] By default, taking the logarithm of
@@
         validating \texttt{Quantity} inputs.
-        \texttt{astropy.units} now provides a \python decorator
-        (\texttt{quantity\_input}) that does this verification automatically.
-    \item[Interaction with \package{numpy} arrays] \inlinecomment{TODO}{Marten}
+        \texttt{astropy.units} now provides a \python decorator,
+        \texttt{quantity\_input()}, that does this verification automatically.
 \end{description}

### 2017-11-10 main.tex
edit constants

@@
 \subsection{Constants}
-
-%David S.
-
-The \package{Constants} package provides a selection of physical and astronomical
-constants as quantities.  A brief description was given in \cite{astropy}.
-For version 2.0, constants have been organized into modules for specific versions.
-Physical constants include \texttt{codata2014} \citep{codata2014}
-and \texttt{codata2010} versions. Astronomical constants are organized
-into \texttt{iau2015} and
-\texttt{iau2012} modules to roughly indicate their sources.
-The \texttt{codata2014} and \texttt{iau2015} versions are combined
-into the default \texttt{astropyconst20}
-version. For astropy v1.3 and earlier, the \texttt{astropyconst13}
-namespace is available;
-however when using previous versions of the constants,
-\package{Constants} should be used
-directly, since  \package{astropy.units} will be initialized to the
-\texttt{astropyconst20} versions.
-
-Astronomers using \package{Constants} should take particular note of the
-constants provided for Earth, Jupiter and the Sun. Following IAU 2015
-Resolution B3 \citep{iau2015b3}, nominal
-values are now given for mass parameters and radii. The nominal values
-will not change even as ``current best estimates'' are updated.
+% David S.
+% Edited by Adrian PW
+
+The \texttt{astropy.constants} subpackage provides a selection of physical and
+astronomical constants as \texttt{Quantity} objects (see
+\sectionname~\ref{sec:units}).
+A brief description of this package was given in \citep{astropy}.
+In version 2.0, the built-in constants have been organized into modules for
+specific versions of the constant values.
+For example, physical constants have \texttt{codata2014} \citep{codata2014} and
+\texttt{codata2010} versions.
+Astronomical constants are organized into \texttt{iau2015} and \texttt{iau2012}
+modules to indicate their sources (resolutions from the International
+Astronomical Union, IAU).
+The \texttt{codata2014} and \texttt{iau2015} versions are combined into the
+default constant value version: \texttt{astropyconst20}.
+For compatibility with \astropypkg version 1.3 and earlier, the \texttt{astropyconst13}
+namespace is still available and provides access to the adopted versions of the
+constants from earlier versions of \astropypkg.
+To use previous versions of the constants as \emph{units} (e.g., solar masses),
+the values from the desired namespace have to be imported directly; with version
+2.0, \texttt{astropy.units} uses the \texttt{astropyconst20} versions.
+
+Astronomers using \texttt{astropy.constants} should take particular note of the
+constants provided for Earth, Jupiter, and the Sun.
+Following IAU 2015 Resolution B3 \citep{iau2015b3}, nominal values are now given
+for mass parameters and radii.
+The nominal values will not change even as ``current best estimates'' are
+updated.
 

### 2017-11-11 main.tex
remove comment
major edits to the introduction

@@
 % first draft by Moritz (hamogu)
-All astronomical research makes use of software in some way and
-astronomy as a field has long supported the development of specialized
-software tools for different astronomical tasks. Some of those
-software packages are (or at least were) supported by large
-institutions, e.g.\ IRAF \citep[developed at NOAO,][]{IRAF}, MIDAS
-\citep[developed at ESO,][]{MIDAS}, or ds9 \citep[developed at
-% * <bsipocz@gmail.com> 2017-09-28T21:05:00.569Z:
-%
-% > or ds9
-% probably starlink is a better example as being a large package of software similarly to IRAF and MIDAS rather than a single tool.
-%
-% ^.
-% hamogu: Feel free ot swap in Starlink, if you think that's more appropriate.
-I picked ds9 becase (a) it's wider known (e.g.
-in the X-ray community) and (b) because it is an example of a widely used tool with institutional support that is NOT a large package.
-TOPCAT would have been another example if we want to expand that list.
-% olebole: TOPCAT is part of Starlink Java. An other examples would be CASA resp. AIPS. I'd rather omit ds9, since it is mainly developed by one person.
-% timj: Starlink originally developed TOPCAT. Starlink is much better an example than DS9.
-SAO,][]{ds9}. These packages tend to address a wide range of users
-and typically provide some level of documentation and user
-support is provided. Other packages are developed foremost by individual research
-groups and used mostly in work by members of the group. Those
-packages can address more specialized needs, but are not necessarily
-available to the community and even if they are, documentation can in
-some cases be insufficient for new users and the quality of the
-software, i.e.\ the robustness and the level of testing that has been
-performed to ensure correctness, is not always clear. On the other
-hand, there are also many widely used, well documented, high quality
-software packages which are developed by individuals or small groups.
-
-The implementation of astronomical software, be it for a package meant
-for wide distribution or scripts and programs for a specific research
-project, can be eased by the use of a library that provides core
-functionality that is common to many astronomical tasks. Reading and
-writing FITS files is one example where it is time
-consuming to implement the FITS standard correctly and
-programming is much faster when using an existing library to perform this
-task. Another example of such a common task is dealing with different
-astronomical coordinate systems. The \astropy project aims to provide a
-library of core astronomical functionality in the \python programming
-language.
-
-\python\footnote{\url{https://www.python.org/}} is an increasingly popular
+% heavily edited by Adrian PW - let me know if you want to revert anything!
+All astronomical research makes use of software in some way.
+Astronomy as a field has thus long supported the development of specialized
+software tools for astronomical tasks, from software packages that enable
+individualized scientific research to data reduction tools and pipelines that
+enable collaborations and survey operations.
+Some such software packages are or were supported by large institutions and are
+intended for a wide range of users.
+These packages typically provide some level of documentation and user support or
+training.
+Other packages are developed by individual researchers or research groups and
+are then typically used by smaller groups for more domain-specific purposes.
+Whether for a package meant for wide distribution or for scripts and programs
+for a specific research project, the implementation of astronomical software can
+be eased through the use of a library that provides core functionality that is
+common to many astronomical tasks.
+The users of such software then also benefit from a community and ecosystem
+built around a common foundation.
+The \astropy project has grown to become this community, and the \astropypkg
+core package a feature-rich library for \python-based astronomical software.
+
+The development of the \astropypkg core package began as a largely
+community-driven effort to standardize core functionality for astronomical
+software in \python.
+In this way, its genesis differs from but builds upon many substantial and
+former astronomical software development efforts that were commissioned or
+initiated through large institutional support, for example IRAF \citep[developed
+at NOAO;][]{IRAF}, MIDAS \citep[developed at ESO;][]{MIDAS}, or Starlink
+\citep[originally developed by a consortium of UK institutions and now
+maintained by the East Asian Observatory;][]{starlink1982,starlink2013}.
+% More recently, community-driven efforts have seen significant success in the astronomical sciences \citep{yt}
+
+The \astropypkg core package is now a feature-rich library of sufficiently
+general tools and classes that supports the development of more specialized
+code.
+An example of such functionality is reading and writing FITS files: it would be
+time consuming and impractical for multiple groups to implement the FITS
+standard \citep{FITS} and maintain software for such a general-purpose need.
+Another example of such a common task is in dealing with representations of and
+transformations between astronomical coordinate systems.
+The \astropy project aims to provide an open-source, open-development core
+package (\astropypkg) and an ecosystem of \emph{affiliated packages} that
+support astronomical functionality in the \python programming language.
+
+\python\footnote{\url{https://www.python.org/}} is an increasingly popular,
 general-purpose scripting language that is available under a permissive open
-source software licence free of charge for all major operating systems. Stable
-and well-developed packages provide support for array arithmetic
-\citep[\package{numpy},][]{numpy}, a wide variety of functions for scientific
-computing \citep[\package{scipy},][]{numpy}, and publication-quality plotting
-\citep[\package{matplotlib},][]{matplotlib}. Tens of thousands of other packages
+source software license free of charge for all major operating systems.
+Stable and well-developed packages provide support for array arithmetic
+\citep[\package{numpy};][]{numpy}, a wide variety of functions for scientific
+computing \citep[\package{scipy};][]{numpy}, and publication-quality plotting
+\citep[\package{matplotlib};][]{matplotlib}. Tens of thousands of other packages
 are available which can help with tasks that are not astronomy specific but
-might be performed in the course of astronomical research, e.g.\ presenting
-results on websites or interfacing with databases.
-
-At the same time, an ecosystem of tools, programs, and web services
-has become available that makes it easier to collaborate on code development,
-continuously test the code, build and provide documentation, and
-supply downloadable packages. The \astropy project aims to develop and
-provide high quality code and documentation according to the best
-practices in software development. The project makes use of these
-tools to do so without central institutional oversight.
-
-The first public release of the \astropy package is described in
-\cite{astropy}. Since then, the \astropy package has been
+might be performed in the course of astronomical research, for example interfacing with databases or statistical inference.
+
+\python has become especially popular in the quantitative sciences, especially
+where researchers must simultaneously produce research, perform data analysis,
+and develop software.
+A large part of this success owes itself to a vibrant community of developers
+and a continuously-growing ecosystem of tools and web services that enable
+easier collaboration on software development, easier writing and sharing
+documentation, and continuous testing and validation of software.
+More recently, package managers such as Anaconda\url{https://anaconda.org/} have
+streamlined the installation process for most packages, therefore significantly
+reducing the barrier to entry for using many such libraries.
+
+The \astropy project aims to develop and provide high quality code and
+documentation according to the best practices in software development.
+The project makes use of these tools to do so without central institutional
+oversight.
+The first public release of the \astropypkg package is described in
+\cite{astropy}. Since then, the \astropypkg package has been
 used in hundreds of projects, and the scope of the package has grown
@@
 contributing to the project has grown tremendously and an ecosystem
-of packages supporting or affiliated with the \astropy core has
-developed. In this paper, we describe the current status of the
-\astropy community, the \astropypkg core package, and the \astropy
-ecosystem.
-
-We start by describing the way the \astropy project works and is
-organized in \sectionname~\ref{sec:org}.  The project develops a core
-package called \astropypkg (\sectionname~\ref{sec:core}) and several
-separate packages that help setting up the infrastructure for testing,
-documentation etc.\ (\sectionname~\ref{sec:infrastructure}).
-We end with a short vision for
+of packages supporting or affiliated with the \astropypkg core has
+developed.
+In this paper, we describe the current status of the \astropy community and the
+\astropypkg core package and discuss goals for future development
+
+We start by describing the way the \astropy project functions and is organized
+in \sectionname~\ref{sec:org}. We then describe the main software efforts
+developed by the \astropy project itself: a core package called \astropypkg
+(\sectionname~\ref{sec:core}) and several separate packages that help maintain
+the infrastructure for, e.g., testing and documentation
+(\sectionname~\ref{sec:infrastructure}). We end with a short vision for
 the future of \astropy in particular and astronomical software in general
@@
 
-\inlinecomment{DavidS: we'd like to build on this to allow use of a
-context manager for selecting a version of constants. Here, or in the Future
-section?}
-
 \subsection{Coordinates}

### 2017-11-11 main.tex
footnotes

@@
 contribution on a publically available
-website\footnote{\url{https://github.com/astropy/astropy}}.
+website.\footnote{\url{https://github.com/astropy/astropy}}
 This request is then reviewed by at least one of the maintainers responsible for

### 2017-11-11 main.tex
not specialized

@@
 All astronomical research makes use of software in some way.
-Astronomy as a field has thus long supported the development of specialized
-software tools for astronomical tasks, from software packages that enable
-individualized scientific research to data reduction tools and pipelines that
-enable collaborations and survey operations.
+Astronomy as a field has thus long supported the development of software tools
+for astronomical tasks, from software packages that enable individualized
+scientific research to data reduction tools and pipelines that enable
+collaborations and survey operations.
 Some such software packages are or were supported by large institutions and are

### 2017-11-11 main.tex
footnote anaconda

@@
 documentation, and continuous testing and validation of software.
-More recently, package managers such as Anaconda\url{https://anaconda.org/} have
-streamlined the installation process for most packages, therefore significantly
-reducing the barrier to entry for using many such libraries.
+More recently, package managers such as
+Anaconda\footnote{\url{https://anaconda.org/}} have streamlined the installation
+process for most packages, therefore significantly reducing the barrier to entry
+for using many such libraries.
 

### 2017-11-11 main.tex
some minor cleaning up

@@
 % Adrian, Erik
-
-\subsubsection{Overview}
 The \package{astropy.coordinates} subpackage is designed to support representing
@@
 
-\subsubsection{Key new features}
+In what follows, we briefly highlight key new features in
+\texttt{astropy.coordinates}.
 
@@
 Figure \textbf{TODO} shows an example of the accuracy of the conversion from XX to XX and \textbf{insert insightful result here}.
-
-%\subsubsection{Accuracy and comparison of coordinate system definitions}
-% Erik?
 

### 2017-11-11 main.tex
approx not sim

@@
 The commit distribution follows an approximate power-law (with log-slope of
-$\sim -0.47$), meaning most of the commits were and are contributed by a
+$\approx -0.47$), meaning most of the commits were and are contributed by a
 relatively small fraction of the contributor pool.

### 2017-11-11 main.tex
Update on Overleaf.

@@
     \item spell check!
+    \item check consistent astropy usage
 \end{itemize}
@@
 % heavily edited by Adrian PW - let me know if you want to revert anything!
-All astronomical research makes use of software in some way.
-Astronomy as a field has thus long supported the development of software tools
-for astronomical tasks, from software packages that enable individualized
-scientific research to data reduction tools and pipelines that enable
-collaborations and survey operations.
-Some such software packages are or were supported by large institutions and are
-intended for a wide range of users.
-These packages typically provide some level of documentation and user support or
+All astronomical research makes use of software in some way.  Astronomy as a field has thus long supported the development of software tools
+for astronomical tasks: from scripts that enable individualized scientific research to software packages that enable collaborations to data reduction pipelines for survey operations.
+Some software packages are or were supported by large institutions and are intended for a wide range of users. These packages typically provide some level of documentation and user support or
 training.
@@
 general tools and classes that supports the development of more specialized
-code.
-An example of such functionality is reading and writing FITS files: it would be
+code. An example of such functionality is reading and writing FITS files: it would be
 time consuming and impractical for multiple groups to implement the FITS
@@
 
-For resolving disagreements about the \astropypkg core package or other \astropy-managed code, the coordination committee primarily acts to work toward consensus, or when consensus is difficult to achieve, generally acts as ``tie-breaker.''
+For resolving disagreements about the \astropypkg core package or other \astropy-managed code, the coordination committee primarily acts to work toward consensus, or when consensus is difficult to achieve, generally acts as a ``tie-breaker.''
 The committee also oversees affiliated package applications to ensure they are in keeping with \astropy's vision and philosophy, as well as the associated procedures.
@@
 \astropypkg implements `normalized convolution' \citep[e.g.,][]{Knutsson1993}, which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.
-In version $<=1.3$, the direct convolution and fft convolution approaches were not consistent, with fft convolution implementing normalized convolution and direct convolution implementing a different approach.
+An example of this is given in \figurename \ref{fig:convolution-example}.
+In version $<=1.3$, the direct convolution and fast fourier transform (fft) convolution approaches were not consistent, with fft convolution implementing normalized convolution and direct convolution implementing a different approach.
 As of v2.0, the two methods are consistent and include a suite of consistency checks.
@@
 Development has continued after the release of v2.0 of \package{astropy}.
-The most significant development for the next release will be removing python 2 support \cite{ape10}.
-While the v2.0 release is a ‘long term stable’ release )meaning that it will be supported through 2019 in both python 2 and python 3), the v3.0 \package{astropy} release will only support python 3.
+The most significant development for the next release will be removing python 2 support \citep{ape10}.
+While the v2.0 release is a ‘long term stable’ release (meaning that it will be supported through 2019 in both python 2 and python 3), the v3.0 \package{astropy} release will only support python 3.
 This will allow the use of the new functionality in python 3, simplify the code base, and reducing the testing overhead.
@@
 To prepare for this release, software for testing and monitoring the performance of the code are being developed.
-Less new functionality may be introduced in this release, but the focus will be primarily on improved performance.
+Less functionality may be introduced in this release while the focus will be primarily on improved performance.
 In addition, a new suite of tutorials and documentation are being prepared for this release.
@@
 While these may not be integrated into the core code, these projects provide code that is useful to the astronomical community and meet the testing and documentation standards of \astropy.
-Some of these new efforts includes an initiative to develop tools for spectroscopy , integration of LSST software , and packages to support HEALPIX projection.
+Some of these new efforts includes an initiative to develop tools for spectroscopy, integration of LSST software, and packages to support HEALPIX projection.
 
@@
 The \astropypkg core package documentation contains narrative descriptions of
-the package functionality along with detailed usage notes for functions,
-classes, and modules.
+the package functionality along with detailed usage notes for functions, classes, and modules.
 While useful as a reference and for more advanced \python users, it is not the
@@
 
+\inlinecomment{SMC: Can a brief description of each code be added?}
 \begin{longrotatetable}

### 2017-11-12 main.tex
keywords
time section

@@
 
-%% Keywords should appear after the \end{abstract} command.
-%% See the online documentation for the full list of available subject
-%% keywords and the rules for their use.
-\keywords{}
+% Adrian PW: how are there still no software keywords in AAS journals?!?
+\keywords{
+    Astrophysics - Instrumentation and Methods for Astrophysics
+    ---
+    methods: data analysis
+    ---
+    methods: miscellaneous
+}
 
@@
 \label{sec:time}
-
-\inlinecomment{Tom, Marten?}
-
-\inlinecomment{SCO}{Q: does it make sense to refer forward to FITS support, even though it is 3.0?-- If you want to say something add it to the future section, but I'd say no.}
-
-Time and date functionality, especially those relevant to astronomy, are dealt by the \package{Time} package.
-The package was described in detail in \cite{astropy}.
-The \package{Time} package is currently built on ERFA \citep{erfa}, which replicates the functionality of SOFA \cite{sofa} but is licensed under a three-clause BSD license.
+% Tom, Marten?
+% edited by Adrian PW
+
+The \package{astropy.time} subpackage focuses on supporting time scales (e.g.,
+UTC, TAI, UT1) and time formats (e.g., Julian date, modified Julian date) that
+are commonly used in astronomy, for example, to calculate barycentric
+corrections or sidereal times.
+The core functionality is currently built on the ERFA (\citealt{erfa}) C
+library, which replicates the Standards of Fundamental Astronomy (SOFA;
+\citealt{sofa}) but is licensed under a three-clause BSD license.
+The package was described in detail in \cite{astropy} and thus, in what follows,
+we only highlight significant changes or new features.
+
+\begin{description}
+    \item[TODO] todo...
+    \item[TODO] todo...
+\end{description}
 
@@
 
-\inlinecomment{SMC: Can a brief description of each code be added?}
+\inlinecomment{SMC}{Can a brief description of each code be added?}
+
 \begin{longrotatetable}

### 2017-11-12 main.tex
time new features
Update on Overleaf.

@@
 
-In order to check the accuracy of the coordinate transformations in \package{astropy.coordinates}, we have set up a set of benchmarks that we use to compare transformations between a set of coordinate frames for a number of packages \footnote{\url{http://www.astropy.org/coordinates-benchmark/summary.html}}.
+In order to check the accuracy of the coordinate transformations in \package{astropy.coordinates}, we have created a set of benchmarks that we use to compare transformations between a set of coordinate frames for a number of packages \footnote{\url{http://www.astropy.org/coordinates-benchmark/summary.html}}.
 Since
@@
 The benchmarks are thus useful beyond the Astropy project since they allow all of the tools to be compared to all other tools.
-The tools included in the benchmark at the moment include astropy, kapteyn, novas, palpy, pyast, and pyslalib.
-\textbf{NEED REFS}
+The tools included in the benchmark at the moment include the astropy core package, Kapteyn \citep{kapteyn}, NOVAS \citep{novas}, PALpy \citep{pal}, PyAST \citep[a wrapper for AST, described in][]{ast}, PyTPM\footnote{\url{https://github.com/phn/pytpm}}, PyEphem \citep{pyephem}, and pySLALIB \citep[a Python wrapper for SLALIB, described in][]{slalib}.
 
@@
 For now we set the epoch of observation to J2000, and the frame to J2000 in the case of the FK5 and ecliptic frames and B1950 for the FK4 frame, but in future we plan to include a larger variety of epochs and equinoxes, as well as tests of conversion to/from Altitude/Azimuth.
-
 For each benchmark, we convert the 1000 longitudes/latitudes from the input/output frame with all tools and quantify the comparison by looking at the median, minimum, maximum, and standard deviation of the absolute separation of the output coordinates from each pair of tools.
-Table \textbf{TODO} gives an example of the relative accuracy of the conversion from Galactic to FK4 coordinates for all pairs of tools.
-This shows that \textbf{Need to add discussion here}.
-
-The benchmarks also include all-sky plots that show trends in accuracy over the sky and can help diagnose issues.
-Figure \textbf{TODO} shows an example of the accuracy of the conversion from XX to XX and \textbf{insert insightful result here}.
+Table \ref{tab:coordinate_benchmarks} gives an example of the relative accuracy of the conversion from FK4 to Galactic coordinates for all pairs of tools.
+This shows for example that astropy, Kapteyn and PyTPM agree perfectly (to the precision shown), while PALpy, pySLALIB, and PyAST also agree perfectly amongst themselves, but show an offset of around 0.2\arcsec with the former three packages.
+Finally, PyEphem disagrees with other packages by 0.4-0.8\arcsec.
+These values are only meant to be illustrative and will change over time as the benchmarks are refined and packages are updated.
+
+\begin{table}
+\caption{Comparison of the accuracy of the FK4 to Galactic transformation between different packages.\label{tab:coordinate_benchmarks}}
+\begin{tabular}{llcccc}
+\hline
+\hline
+Package 1 & Package 2 & Median & Mean & Maximum & Std. Dev. \\
+          &           & arcsec & arcsec & arcsec & arcsec \\
+\hline
+astropy  &  kapteyn  & 0.000  & 0.000 & 0.000 & 0.000 \\
+\nodata  &  palpy    & 0.218  & 0.196 & 0.249 & 0.056 \\
+\nodata  &  pyast    & 0.218  & 0.196 & 0.249 & 0.056 \\
+\nodata  &  pyephem  & 0.459  & 0.458 & 0.860 & 0.231 \\
+\nodata  &  pyslalib & 0.218  & 0.196 & 0.249 & 0.056 \\
+\nodata  &  pytpm    & 0.000  & 0.000 & 0.000 & 0.000 \\
+kapteyn  &  palpy    & 0.218  & 0.196 & 0.249 & 0.056 \\
+\nodata  &  pyast    & 0.218  & 0.196 & 0.249 & 0.056 \\
+\nodata  &  pyephem  & 0.459  & 0.458 & 0.860 & 0.231 \\
+\nodata  &  pyslalib & 0.218  & 0.196 & 0.249 & 0.056 \\
+\nodata  &  pytpm    & 0.000  & 0.000 & 0.000 & 0.000 \\
+palpy    &  pyast    & 0.000  & 0.000 & 0.000 & 0.000 \\
+\nodata    &  pyephem  & 0.563  & 0.570 & 1.012 & 0.253 \\
+\nodata    &  pyslalib & 0.000  & 0.000 & 0.000 & 0.000 \\
+\nodata    &  pytpm    & 0.218  & 0.196 & 0.249 & 0.056 \\
+pyast    &  pyephem  & 0.563  & 0.570 & 1.012 & 0.253 \\
+\nodata    &  pyslalib & 0.000  & 0.000 & 0.000 & 0.000 \\
+\nodata    &  pytpm    & 0.218  & 0.196 & 0.249 & 0.056 \\
+pyephem  &  pyslalib & 0.563  & 0.570 & 1.012 & 0.253 \\
+\nodata  &  pytpm    & 0.459  & 0.458 & 0.860 & 0.231 \\
+pyslalib &  pytpm    & 0.218  & 0.196 & 0.249 & 0.056 \\
+\hline
+\end{tabular}
+\end{table}
 
@@
 \begin{description}
-    \item[TODO] todo...
-    \item[TODO] todo...
+    \item[Barycentric and Heliocentric corrections] TODO: added in v1.2, but maybe worth mentioning?
+    \item[As columns in \texttt{Table} objects] todo...
 \end{description}
@@
 \subsubsection{nddata}
-
-\inlinecomment{Should I mention the fact that there will be changes coming to 3.0? -- If you want to say something add it to the future section}
 

### 2017-11-12 main.tex
center the coord table
time section

@@
 \begin{table}
-\caption{Comparison of the accuracy of the FK4 to Galactic transformation between different packages.\label{tab:coordinate_benchmarks}}
+\begin{center}
 \begin{tabular}{llcccc}
@@
 \end{tabular}
+\end{center}
+\caption{Comparison of the accuracy of the FK4 to Galactic transformation between different packages.\label{tab:coordinate_benchmarks}}
 \end{table}
@@
 \label{sec:time}
-% Tom, Marten?
-% edited by Adrian PW
+% Adrian PW
 
@@
 UTC, TAI, UT1) and time formats (e.g., Julian date, modified Julian date) that
-are commonly used in astronomy, for example, to calculate barycentric
-corrections or sidereal times.
-The core functionality is currently built on the ERFA (\citealt{erfa}) C
+are commonly used in astronomy.
+This functionality is needed, for example, to calculate barycentric corrections
+or sidereal times.
+\package{astropy.time} is currently built on the ERFA (\citealt{erfa}) C
 library, which replicates the Standards of Fundamental Astronomy (SOFA;
 \citealt{sofa}) but is licensed under a three-clause BSD license.
-The package was described in detail in \cite{astropy} and thus, in what follows,
-we only highlight significant changes or new features.
+The package was described in detail in previous work \citep{astropy} and has
+stayed stable for the last several versions of \astropypkg.
+Thus, in what follows, we only highlight significant changes or new features
+since the previous \astropy paper.
 
 \begin{description}
-    \item[Barycentric and Heliocentric corrections] TODO: added in v1.2, but maybe worth mentioning?
-    \item[As columns in \texttt{Table} objects] todo...
+    \item[Barycentric and Heliocentric corrections] Detailed eclipse or transit
+        timing requires accounting for light travel time differences from the
+        source to the observatory because of the Earth's motion.
+        It is therefore common to instead convert times to the Solar System
+        barycenter or heliocenter where the relative timing of photons is
+        standardized.
+        With the location of a source on the sky (i.e. a \texttt{SkyCoord}
+        object), the location of an observatory on Earth (i.e. an
+        \texttt{EarthLocation} object), and time values as \texttt{Time}
+        objects, the time corrections to shift to the solar system barycenter or
+        heliocenter can now be computed with \package{astropy.time} using the
+        \texttt{light\_travel\_time} method of a \texttt{Time} object.
+    \item[\texttt{Time} objects in \texttt{Table}'s] \texttt{Time} objects can
+        now be added as columns in \package{astropy.table} \texttt{Table}
+        objects.
+        This is described in more detail in \sectionname~\ref{sec:table} with
+        the concept of a ``mixin'' column type.
 \end{description}

### 2017-11-12 main.tex
nddata

@@
 
-\subsection{Data arrays}
+\subsection{Data containers}
 
@@
 
-The \package{astropy.nddata} supackage provides three types of functionality:
-an abstract interface for representing generic arbitrary-dimensional datasets
-intended primarily for developers of other packages, concrete classes
-building on this interface and utilities for manipulating these kind of
+The \package{astropy.nddata} supackage provides three types of functionality: an
+abstract interface for representing generic arbitrary-dimensional datasets
+intended primarily for subclassing by developers of other packages, concrete
+classes building on this interface, and utilities for manipulating these kind of
 datasets.
 
-The \texttt{NDDataBase} class provides the abstract interface for gridded data with attributes for accessing metadata, the world-coordinate system (WCS), uncertainty and other traits.
+The \texttt{NDDataBase} class provides the abstract interface for gridded data
+with attributes for accessing metadata, the world-coordinate system (WCS),
+uncertainty arrays matched to the data shape, and other traits.
 Building on this interface the \texttt{NDData} class provides a minimally working implementation for storing NumPy arrays.

### 2017-11-12 main.tex
grammar

@@
         \texttt{light\_travel\_time} method of a \texttt{Time} object.
-    \item[\texttt{Time} objects in \texttt{Table}'s] \texttt{Time} objects can
-        now be added as columns in \package{astropy.table} \texttt{Table}
-        objects.
-        This is described in more detail in \sectionname~\ref{sec:table} with
-        the concept of a ``mixin'' column type.
+    \item[\texttt{Time} objects as \texttt{Table} columns] \texttt{Time} objects
+        can now be added as columns in \package{astropy.table} \texttt{Table}
+        objects. This is described in more detail in
+        \sectionname~\ref{sec:table} with the concept of a ``mixin'' column
+        type.
 \end{description}

### 2017-11-12 main.tex
nddata

@@
 uncertainty arrays matched to the data shape, and other traits.
-Building on this interface the \texttt{NDData} class provides a minimally working implementation for storing NumPy arrays.
-These classes serve as useful base for package authors wishing to develop their own classes for specific use cases and as containers for exchanging gridded data.
-
-The concrete classes \texttt{NDDataRef}, \texttt{NDDataArray} and \texttt{CCDData} extend the storing functionality with options to do basic arithmetic (addition, subtraction, multiplication and division) including error propagation in limited cases and slicing of the dataset based on grid coordinates appropriately handling mask, errors, and units, if present.
-Additionally \texttt{CCDData} also provides I/O from and to FITS files and uses data structures from \astropypkg, like WCS, to represent the contents of a file abstractly.
-
-The \package{astropy.nddata.utils} module provides utilities that can operate on either plain NumPy arrays or any of the classes in the \package{astropy.nddata} subpackage.
-It features a class for representing two-dimensional image cutouts, allowing one to easily link pixels in the cutout to pixels in the original image or from the image to the cutout, to convert between world and pixel coordinates in the cutout and to overlay the cutout on images.
+Building on this interface, the \texttt{NDData} class provides a minimal working implementation for storing \package{numpy} arrays.
+These classes serve as useful base classes for package authors wishing to develop their own classes for specific use cases and as containers for exchanging gridded data.
+
+The classes \texttt{NDDataRef}, \texttt{NDDataArray}, and \texttt{CCDData} extend the base storing functionality with options to do basic arithmetic (addition, subtraction, multiplication, and division) including error propagation in limited cases and slicing of the dataset based on grid coordinates that appropriately handles masking, errors, and units (if present).
+Additionally, the \texttt{CCDData} class also provides reading and writing from and to FITS files and uses data structures from \astropypkg, like \texttt{WCS}, to represent the contents of a file abstractly.
+
+The \package{astropy.nddata.utils} module provides utilities that can operate on either plain \package{numpy} arrays or any of the classes in the \package{astropy.nddata} subpackage.
+It features a class for representing two-dimensional image cutouts, allowing one to easily link pixels in the cutout to pixels in the original image or from the image to the cutout, to convert between world and pixel coordinates in the cutout, and to overlay the cutout on images.
 Functions to enlarge or reduce an image by doing block replication or reduction are also provided.
-
-%Larry:  Don't forget the nddata.utils functionality (e.g. Cutout2D, block\_reduce, %etc.).
 

### 2017-11-12 main.tex
tables

@@
 
-The \package{Tables} package provides wrappers to \package{NumPy} structure arrays, which can contain heterogeneous data sets.
+The \package{astropy.table} package provides wrappers to \package{numpy} structure arrays, which can contain heterogeneous data sets.
 The package was described in detail in \cite{astropy}.
-Tables now has the ability to work with other astropy classes including Quantities, Time, and Coordinates.
+Tables now has the ability to work with other \astropypkg classes including \texttt{Quantity}, \texttt{Time}, and \texttt{SkyCoord}.
 In addition, operations can also be performed on Tables.
 
+We summarize key new features or updates to \package{astropy.table} below.
 %QTable is new, mixin columns for time and coordinates. Table operations were added in v0.3
+
+\inlinecomment{Adrian PW}{The new features below need filling in.}
+
+\begin{description}
+    \item[QTable] TODO...quantity tables
+    \item[Mixin columns for time and coordinates] TODO...
+\end{description}
 

### 2017-11-13 main.tex
ack line
list of new features for Table

--- 2017-11-12 main.tex
@@
 \label{sec:table}
-
-The \package{Tables} package provides wrappers to \package{NumPy} structure arrays, which can contain heterogeneous data sets.
-The package was described in detail in \cite{astropy}.
-Tables now has the ability to work with other astropy classes including Quantities, Time, and Coordinates.
-In addition, operations can also be performed on Tables.
-
-%QTable is new, mixin columns for time and coordinates. Table operations were added in v0.3
+% fleshed out / edited by Adrian PW
+
+The \package{astropy.table} subpackage provides functionality for representing
+and manipulating heterogeneous data.
+\inlinecomment{APW:}{Need more introduction to the table subpackage!}
+The package was described in detail in \cite{astropy}; we summarize key new
+features or updates to \package{astropy.table} below.
+
+\begin{description}
+    \item[Support for grouped table operations] Some tables contain data that
+        naturally form groups.
+        For example, a table of photometry for galaxies, stars, and quasars.
+        We may then want to split the table or a column into these groups and
+        compute some statistic on the data, or filter the groups based on some
+        criteria.
+        Grouped operations are now supported by \texttt{Table} objects,
+        mainly through the \texttt{group\_by()} method and subsequent operations
+        on the grouped version of the table or column.
+    \item[Support for table concatenation] Tables can be combined in several
+        different ways.
+        If two tables have the same rows, we may want to stack them
+        ``vertically'' to create a new table with the same columns but all rows.
+        If two tables are row-matched but have distinct columns, we may want to
+        stack them ``horizontally'' to create a new table with the same rows
+        but all columns.
+        For other situations, more general table concatenations or joins are
+        also possible when two tables share some common columns.
+        All three of these operations are now possible with \texttt{Table}
+        objects through the \texttt{vstack}, \texttt{hstack}, and \texttt{join}
+        functions in \package{astropy.table}.
+    \item[Mixin columns for time and coordinates] The default data containers
+        for \texttt{Table} objects are \texttt{Column} objects.
+        However, sometimes the data for a given column is better represented as
+        a \texttt{Quantity}, or a sky coordinate (\texttt{SkyCoord}), or an
+        astronomical \texttt{Time} object.
+        The \texttt{Table} object now supports these and other objects to serve
+        as array-like containers for column data through the ``mixin'' protocol.
+    \item[Transform to and from \texttt{Pandas} \texttt{DataFrame} objects]
+        \texttt{Table} objects can now be created from a \texttt{DataFrame}
+        object (\texttt{from\_pandas()}), or exported to a \texttt{DataFrame}
+        object (\texttt{to\_pandas()}).
+        \texttt{DataFrame} objects do not support multi-dimensional array
+        columns, so this conversion will fail if the source \texttt{Table}
+        object contains any such columns.
+\end{description}
 
@@
 
-Software/services to thank: GitHub. Travis CI, Appveyor, CircleCI. Read the Docs.
-
-%% Similar to \facility{}, there is the optional \software command to allow
-%% authors a place to specify which programs were used during the creation of
-%% the manusscript. Authors should list each code and include either a
-%% citation or url to the code inside ()s when available.
+We thank the many web services that make developing and maintaining this package
+feasible, such as GitHub, Travis CI, Appveyor, CircleCI, and Read the Docs.
 
@@
           \package{scipy} (\citealt{scipy}),
-          \package{matplotlib} (\citealt{matplotlib})
+          \package{matplotlib} (\citealt{matplotlib}),
           \package{Cython}(\citealt{cython}),

### 2017-11-13 main.tex
reorganize astropy.io

@@
 \inlinecomment{APW:}{Need more introduction to the table subpackage!}
-The package was described in detail in \cite{astropy}; we summarize key new
-features or updates to \package{astropy.table} below.
-
+The package was described in detail in \cite{astropy}.
+
+We summarize key new features or updates to \package{astropy.table} below:
 \begin{description}
@@
 The \package{astropy.io} subpackage provides support for reading and writing
-various formats: a wide range of ASCII data table formats, FITS, VOTable, etc.
+data to a variety of ASCII and binary file formats, such as a wide range of
+ASCII data table formats, FITS, and VOTable.
 It also provides a unified interface for reading and writing data with these
-different formats, using the \package{astropy.table} subpackage.
-For many common cases this simplifies the process of file I/O and reduce the
-need to master the separate details of all the I/O packages within Astropy.
+different formats using the \package{astropy.table} subpackage.
+For many common cases this simplifies the process of file input/output and
+reduces the need to master the separate details of all the I/O packages within
+\astropypkg.
 % This functionality is still in active development and the number of supported
@@
 
-\subsubsection{Key new features}
-
+We summarize key new features or updates to \package{astropy.io} below,
+organized by sub-subpackage:
 \begin{description}
 
-    \item[ASCII: fast reader/writer]
+    \item [Enhanced CSV format ]
+
+        One of the problems when storing a table in an ASCII format is
+        preserving table meta-data such as comments, keywords and column data
+        types, units, and descriptions. Using the newly defined \emph{Enhanced
+        Character Separated Values} (ECSV) format it is now possible to write
+        a table to an ASCII-format file and read it back with no loss of
+        information. The ECSV format has been designed to be both
+        human-readable and compatible with most simple CSV readers.
+
+    \item[\texttt{.ascii}: fast reader/writer]
 
@@
 
-    \item[ASCII: HTML tables]
+    \item[\texttt{.ascii}: HTML tables]
 
@@
 
-	\item [Enhanced CSV format ]
-
-		One of the problems when storing a table in an ASCII format is
-		preserving table meta-data such as comments, keywords and column data
-		types, units, and descriptions. Using the newly defined \emph{Enhanced
-		Character Separated Values} (ECSV) format it is now possible to write
-		a table to an ASCII-format file and read it back with no loss of
-		information. The ECSV format has been designed to be both
-		human-readable and compatible with most simple CSV readers.
-
-	\item [FITS: command-line scripts (\texttt{fitsheader}, \texttt{fitsinfo})]
+	\item [\texttt{.fits}: command-line scripts (\texttt{fitsheader}, \texttt{fitsinfo})]
 
@@
 
-	\item [FITS: lazy loading ]
+	\item [\texttt{.fits}: lazy loading ]
 
@@
 
-	\item [Misc: YAML serialization ]
+	\item [\texttt{.misc}: YAML serialization ]
 

### 2017-11-13 main.tex
edit convolution

@@
 An example of this is given in \figurename \ref{fig:convolution-example}.
-In version $<=1.3$, the direct convolution and fast fourier transform (fft) convolution approaches were not consistent, with fft convolution implementing normalized convolution and direct convolution implementing a different approach.
-As of v2.0, the two methods are consistent and include a suite of consistency checks.
+In versions $<=1.3$, the direct convolution and Fast Fourier Transform (FFT) convolution approaches were not consistent, with FFT convolution implementing normalized convolution and direct convolution implementing a different approach.
+As of version 2.0, the two methods are consistent and include a suite of consistency checks.
 

### 2017-11-13 main.tex
package

@@
 
-The \package{visualization} package provides functionality that can be helpful when visualizing data.
-This includes a framework for plotting astronomical images with coordinates with Matplotlib (previously the standalone \package{wcsaxes} package), functionality related to image normalization (including both scaling and stretching), smart histogram plotting, RGB color image creation from separate images, and custom plotting styles for Matplotlib.
+The \package{astropy.visualization} subpackage provides functionality that can be helpful when visualizing data.
+This includes a framework for plotting astronomical images with coordinates with \package{matplotlib} (previously the standalone \package{wcsaxes} package), functionality related to image normalization (including both scaling and stretching), smart histogram plotting, RGB color image creation from separate images, and custom plotting styles for \package{matplotlib}.
 

### 2017-11-13 main.tex
Update on Overleaf.

@@
 \usepackage[T1]{fontenc}
+\usepackage{ulem}
 \newcommand{\escapecmd}[1]{\texttt{\detokenize{#1}}}
@@
     \item If your subpackage was not included, then please describe the
-        sub-package on level with what was in the first paper, and highlight any
+        subpackage on level with what was in the first paper, and highlight any
         major features in it. Typical length should be equivalent to one page
@@
 \begin{itemize}
-    \item subpackage not sub-package!
+    \item \sout{subpackage not sub-package!} BMS: checked as done 13/11
     \item spell check!
@@
 \subsection{Coordination of Astropy}
-% draft by ??
+% draft by ?? (BMS thinks Erik)
 % edited by Adrian PW
@@
 
-\subsection{Distribution packages}
-
-\astropypkg is available from several of the Python distributions for scientific
+\subsection{Distribution of packages}
+
+The \astropypkg core package is available from several of the Python distributions for scientific
 % * <mattwcraig@gmail.com> 2017-10-27T07:13:51.093Z:
@@
 \label{sec:future}
-\inlinecomment{PLL}{In addition to PY3, add some killer features that we
-  plan to implement for 3.0 and beyond?}
-\inlinecomment{BMS}{Some killer features we already know about to definitely
-have may be mentioned here. e.g. functionality of astropy-healpix? or the
-performance/speedup focus of the 3.1 release?}
+% First draft by SMC
+% edited by BMS
+
+%\inlinecomment{PLL}{In addition to PY3, add some killer features that we
+%  plan to implement for 3.0 and beyond?}
+%\inlinecomment{BMS}{Some killer features we already know about to definitely
+%have may be mentioned here. e.g. functionality of astropy-healpix? or the
+%performance/speedup focus of the 3.1 release?}
 \inlinecomment{BMS}{should we mention the refactored infra here?
   e.g. pytest-astropy and sphinx-astropy?}
-\inlinecomment{SMC}{I've added a rough first draft -- please feel free to edit}
-%\subsection{Roadmap for \python 3 only support}
-
-Development has continued after the release of v2.0 of \package{astropy}.
-The most significant development for the next release will be removing python 2 support \citep{ape10}.
-While the v2.0 release is a ‘long term stable’ release (meaning that it will be supported through 2019 in both python 2 and python 3), the v3.0 \package{astropy} release will only support python 3.
-This will allow the use of the new functionality in python 3, simplify the code base, and reducing the testing overhead.
-The v3.0 release is currently scheduled for December 2017.
-
-In the release cycle after v3.0, the \astropy project will focus on optimization of the code and improved documentation for the v3.1 release.
-To prepare for this release, software for testing and monitoring the performance of the code are being developed.
-Less functionality may be introduced in this release while the focus will be primarily on improved performance.
-In addition, a new suite of tutorials and documentation are being prepared for this release.
-
-Beyond the core code, the \astropy project is also further developing the affiliated packages.
-This includes elevating a suite of packages into part of the core project.
-While these may not be integrated into the core code, these projects provide code that is useful to the astronomical community and meet the testing and documentation standards of \astropy.
-Some of these new efforts includes an initiative to develop tools for spectroscopy, integration of LSST software, and packages to support HEALPIX projection.
-
+%\inlinecomment{SMC}{I've added a rough first draft -- please feel free to edit}
+%
+\par Development has already been continued after the release of v2.0 of
+\astropypkg. The most significant development for the next release will
+be removing python 2 support \citep{ape10}, the v3.0 \astropypkg release
+will only support python 3.  This will allow the use of the new
+functionality in python 3, simplify the code base, and reducing the
+testing overhead.   The v3.0 release is currently scheduled for January
+2018.
+%
+\par In the next major release after v3.0, scheduled for the summer of 
+2018, the focus will be on optimization of the code and improved 
+documentation. To prepare for this release, software for testing and 
+monitoring the performance of the code are being developed.   Less 
+functionality may be introduced in this release while the focus will be 
+primarily on improved performance.  In addition, a new suite of tutorials 
+and documentation are being prepared for this release.
+%
+\par Beyond the core code, the \astropy project is also further 
+developing the affiliated packages.  This includes elevating a suite of 
+packages into part of the core project. While these may not be integrated 
+into the \astropypkg core code, these projects provide code that is 
+useful to the astronomical community and meet the testing and 
+documentation standards of \astropy.   Some of these new efforts includes 
+an initiative to develop tools for spectroscopy 
+\citep[\package{specutils}, \package{specreduc}, \package{specviz}]
+{ape13}, integration of LSST software, and packages to support HEALPIX 
+projection% \citep{astropy-healpix}
+.
+\inlinecomment{BMS}{TODO: uncomment references of packages once they are available}
 \subsection{Learn Astropy}

### 2017-11-13 main.tex
misc cleanup (tab->spaces, \python, ...)

@@
         will need to include code in your section, please add it to a separate
-        Python module (.py file) and include it in this repository.
+        \python module (.py file) and include it in this repository.
     \item Use \escapecmd{\sectionname} not ``Section,'' \escapecmd{\figurename}
@@
 
-From its inception, \astropy has required coordination to ensure the project as a whole and its coding efforts are consistent and reasonably efficient.
-While many Python projects adopt a ``Benevolent Dictator For Life'' (BDFL) model, \astropy has instead opted for a \emph{coordination committee}.
-This is in part due to the nature of the project as a large-scale collaboration between many contributors with many interests, and in part due to simply the amount of work that needs to get done.
-In part for the latter reason, the project has expanded the committee from three to four members starting in 2016.
+From its inception, \astropy has required coordination to ensure the project
+as a whole and its coding efforts are consistent and reasonably efficient.
+While many \python projects adopt a ``Benevolent Dictator For Life'' (BDFL)
+model, \astropy has instead opted for a \emph{coordination committee}.  This
+is in part due to the nature of the project as a large-scale collaboration
+between many contributors with many interests, and in part due to simply the
+amount of work that needs to get done.  In part for the latter reason, the
+project has expanded the committee from three to four members starting in
+2016.
 
@@
 
-The \astropypkg core package is available from several of the Python distributions for scientific
+The \astropypkg core package is available from several of the \python distributions for scientific
 % * <mattwcraig@gmail.com> 2017-10-27T07:13:51.093Z:
@@
 Index\footnote{\url{https://pypi.python.org/pypi}} (PyPI) using pip, the
-recommended command-line tool for installing Python packages
-that is included by default since Python 2 $\geq$ 2.7.9 and Python 3 $\geq$ 3.4.
+recommended command-line tool for installing \python packages
+that is included by default since \python 2 $\geq$ 2.7.9 and \python 3 $\geq$ 3.4.
 For most recent \astropypkg releases, pre-built wheel distributions are obtainable
@@
 
-    \item [Enhanced CSV format ]
+    \item [Enhanced CSV format]
 
@@
         rdb, and tab.  On average the new engine is about 4 to 5 times faster
-		than the corresponding pure-Python implementation, and is often
+        than the corresponding pure-\python implementation, and is often
         comparable to the speed of the pandas ASCII file interface. The fast
@@
 
-		By default, read() and write() will attempt to use the fast C engine when
-		dealing with compatible formats. Certain features of the full read / write
-		interface are not available in the fast version, in which case the
-		pure-Python version will automatically be used.
+        By default, \texttt{read()} and \texttt{write()} will attempt to use
+        the fast C engine when dealing with compatible formats. Certain
+        features of the full read / write interface are not available in the
+        fast version, in which case the pure-\python version will automatically
+        be used.
 
@@
 
-The documentation for many Python packages the core \package{astropy} package
+The documentation for many \python packages the core \package{astropy} package
 as well as for all packages in the Astropy ecosystem is written using the
@@
 documentation pages listing all the available classes, functions, and
-attributes in any given Python module.
+attributes in any given \python module.
 
@@
           \package{matplotlib} (\citealt{matplotlib}),
-          \package{Cython}(\citealt{cython}),
+          \package{Cython} (\citealt{cython}),
           }

### 2017-11-13 main.tex
Add ECSV APE reference

@@
 different formats using the \package{astropy.table} subpackage.
-For many common cases this simplifies the process of file input/output and
+For many common cases this simplifies the process of file input and output and
 reduces the need to master the separate details of all the I/O packages within
 \astropypkg.
-% This functionality is still in active development and the number of supported
-% formats will be increasing.
 
@@
         types, units, and descriptions. Using the newly defined \emph{Enhanced
-        Character Separated Values} (ECSV) format it is now possible to write
-        a table to an ASCII-format file and read it back with no loss of
-        information. The ECSV format has been designed to be both
-        human-readable and compatible with most simple CSV readers.
+        Character Separated Values} (ECSV,  \citet{ape6}) format it is now
+        possible to write a table to an ASCII-format file and read it back
+        with no loss of information. The ECSV format has been designed to be
+        both human-readable and compatible with most simple CSV readers.
 

### 2017-11-13 main.tex
Update on Overleaf.

@@
 In this way, its genesis differs from but builds upon many substantial and
+% * <bsipocz@gmail.com> 2017-11-13T13:13:08.884Z:
+% 
+% how do astroy builds upon these? or it's more like builds upon the developer experience?
+% 
+% 
+% ^.
 former astronomical software development efforts that were commissioned or
@@
 % More recently, community-driven efforts have seen significant success in the astronomical sciences \citep{yt}
-
+\inlinecomment{BMS}{I like the idea to reference yt here}
+%
+The \astropy project aims to provide an open-source, open-development core
+package (\astropypkg) and an ecosystem of \emph{affiliated packages} that
+support astronomical functionality in the \python programming language.
 The \astropypkg core package is now a feature-rich library of sufficiently
@@
 transformations between astronomical coordinate systems.
-The \astropy project aims to provide an open-source, open-development core
-package (\astropypkg) and an ecosystem of \emph{affiliated packages} that
-support astronomical functionality in the \python programming language.
 

### 2017-11-13 main.tex
ascii (add pandas citation) and fits scripts

@@
 
-    \item[\texttt{.ascii}: fast reader/writer]
-
-        The \package{astropy.io.ascii} module now includes a significantly faster
-        Cython/C engine for reading and writing ASCII files. This is available
-        for the following formats: basic, commented\_header, csv, no\_header,
-        rdb, and tab.  On average the new engine is about 4 to 5 times faster
-        than the corresponding pure-\python implementation, and is often
-        comparable to the speed of the pandas ASCII file interface. The fast
-        reader has parallel processing option that allows harnessing multiple
-        cores for input parsing to achieve even greater speed gains.
+    \item[\texttt{.ascii}: fast readers and writers]
+
+        The \package{astropy.io.ascii} module now includes a significantly
+        faster Cython/C engine for reading and writing ASCII files. This is
+        available for the following formats: \texttt{basic},
+        \texttt{commented\_header}, \texttt{csv}, \texttt{no\_header},
+        \texttt{rdb}, and \texttt{tab}.  On average the new engine is about
+        4 to 5 times faster than the corresponding pure-\python
+        implementation, and is often comparable to the speed of the
+        \package{Pandas} \citep{pandas} ASCII file interface.  The fast
+        reader has parallel processing option that allows harnessing
+        multiple cores for input parsing to achieve even greater speed
+        gains.
 
@@
 
-        The \package{astropy.io.fits} subpackage now provides a command line
-        script for inspecting the header(s) of a FITS file.  Running
-        \texttt{fitsheader file.fits} in a terminal prints the header
-        information to the screen in a human-readable format. Run
-        \texttt{fitsheader --help} to see the full usage documentation.
+        The \package{astropy.io.fits} subpackage now provides command-line
+        scripts for printing a summary of the HDUs in a FITS file(s)
+        (\texttt{fitsinfo file.fits}) and for printing the header information
+        to the screen in a human-readable format (\texttt{fitsheader
+        file.fits}).
 
@@
         or \texttt{getdata()}) to get HDU’s that are near the front of a file
-        with many HDU’s.
+        with many HDUs.
 

### 2017-11-13 main.tex
Update on Overleaf.

@@
 new features, or institute new organization-wide policies (e.g.,
-\citealt{ape8}).
+code of conduct; \citealt{ape8}).
 This mechanism is called ``Astropy Proposal for Enhancement'' (APE) and are

### 2017-11-13 main.tex
Update on Overleaf.

@@
 % draft by Adrian PW and Erik T.
-
+\inlinecomment{BMS}{Move this subsection before the APE one, as that one has some repeated content in the first sentences that belongs here}
 Code is contributed to the \astropypkg core package or modified through ``pull

### 2017-11-13 main.tex
Update on Overleaf.

@@
 %
-The \astropy project aims to provide an open-source, open-development core
-package (\astropypkg) and an ecosystem of \emph{affiliated packages} that
-support astronomical functionality in the \python programming language.
-The \astropypkg core package is now a feature-rich library of sufficiently
-general tools and classes that supports the development of more specialized
-code. An example of such functionality is reading and writing FITS files: it would be
-time consuming and impractical for multiple groups to implement the FITS
-standard \citep{FITS} and maintain software for such a general-purpose need.
-Another example of such a common task is in dealing with representations of and
-transformations between astronomical coordinate systems.
 

### 2017-11-13 main.tex
edits to modeling

--- 2017-11-13 main.tex
@@
 %
-The \astropy project aims to provide an open-source, open-development core
-package (\astropypkg) and an ecosystem of \emph{affiliated packages} that
-support astronomical functionality in the \python programming language.
-The \astropypkg core package is now a feature-rich library of sufficiently
-general tools and classes that supports the development of more specialized
-code. An example of such functionality is reading and writing FITS files: it would be
-time consuming and impractical for multiple groups to implement the FITS
-standard \citep{FITS} and maintain software for such a general-purpose need.
-Another example of such a common task is in dealing with representations of and
-transformations between astronomical coordinate systems.
-
 \python\footnote{\url{https://www.python.org/}} is an increasingly popular,
@@
 for using many such libraries.
+
+The \astropy project aims to provide an open-source, open-development core
+package (\astropypkg) and an ecosystem of \emph{affiliated packages} that
+support astronomical functionality in the \python programming language.
+The \astropypkg core package is now a feature-rich library of sufficiently
+general tools and classes that supports the development of more specialized
+code. An example of such functionality is reading and writing FITS files: it would be
+time consuming and impractical for multiple groups to implement the FITS
+standard \citep{FITS} and maintain software for such a general-purpose need.
+Another example of such a common task is in dealing with representations of and
+transformations between astronomical coordinate systems.
 
@@
 The \package{astropy.modeling} subpackage provides a framework for representing
-analytical models and performing model evaluation and fitting. Models and
-fitters are independent of each other, a model can be fit with different
+analytical models and performing model evaluation and parameter fitting. Models and
+fitters are independent of each other: a model can be fit with different
 fitters and new fitters can be added without changing existing models. The
@@
 for the Generalized World Coordinate System (GWCS)
-package\footnote{\url{https://github.com/spacetelescope/gwcs}}. The
-unit support in models and fitters make it a unique package for working with
-astrophysical models.
+package.\footnote{\url{https://github.com/spacetelescope/gwcs}}
+The recently-added support for \package{astropy.units} in models and fitters
+make it a uniquely powerful package for working with astrophysical models.
 
@@
 Most models have a fixed parameter set but for some (e.g., polynomials), the number of parameters is defined by another argument (e.g., degree-of-freedom in the case of polynomials).
-Parameters support arithmetic operations and are combined with the inputs during evaluation using the numpy broadcasting rules.
+Parameters support arithmetic operations and are combined with the inputs during evaluation using the \package{numpy} broadcasting rules.
 A model is evaluated by calling it as a function and passing the inputs in as arguments.
 
-Models have \texttt{Model.inverse} property, which returns the analytical inverse, if available, or raises an exception otherwise.
-This is a settable property; i.e., a model instance can be assigned as inverse to another model.
-For example, a polynomial model can be assigned as an inverse for another polynomial model.
+Models have a \texttt{Model.inverse} property, which returns the analytical inverse, if available, or raises an exception otherwise.
+This is a settable property; i.e.
+a model instance can be assigned as inverse to another model.
+For example, a polynomial model can be assigned as an inverse to another polynomial model.
 
 Another useful settable property of models is \texttt{Model.bounding\_box}.
-It defines the limits over which the model is significant.
+This attribute sets the domain over which the model is defined.
 This greatly improves the efficiency of evaluation when the input range is much larger than the characteristic width of the model itself.
@@
 
-\package{astropy.modeling} provides an efficient way to instantiate the same type of model with many different sets of parameter values by passing the \texttt{n\_models=k} keyword, where k is the number of models to instantiate, and providing the values for each parameter as an iterable of size k.
-This creates a model set which is efficiently evaluated.
+\package{astropy.modeling} provides an efficient way to instantiate the same type of model with many different sets of parameter values by passing the \texttt{n\_models} argument on instantiation, which sets the number of models to instantiate.
+The the values for each parameter in the model set must be passed as iterables of size \texttt{n_models}.
+This creates a model set that can be efficiently evaluated.
 Model sets are most useful for efficiently fitting multiple linear models of the same kind.
@@
 \subsubsection{Compound Models}
-Single models can be combined using arithmetic expressions.
+Models can be combined using arithmetic expressions.
 The result is also a model, which can further be combined with other models.
-Modeling supports arithmetic (+, -, *, /, and **), join $\&$, and composition $|$ operators.
+Modeling supports arithmetic (+, -, *, /, and **), join ($\&$), and composition ($|$) operators.
 The rules for combining models involve matching their inputs and outputs.
@@
 
-\package{astropy.modeling} provides several fitters which are wrappers around some of the \texttt{numpy} and \texttt{scipy.optimize} functions and provide supports for constraints.
-They take a model as input and return a copy of the model with the fitted parameters.
-The goal is to make it easy to extend the fitting framework and create new fitters.
-The optimizers available in \astropypkg 2.0 are Levenberg-Marquardt, Simplex, SLSQP, and LinearLSQFitter (which is based on \texttt{numpy.linalg} that provides exact solution for linear models).
+\package{astropy.modeling} provides several fitters which are wrappers around some of the \texttt{numpy} and \texttt{scipy.optimize} functions and provide support for specifying parameter constraints.
+The fitters take a model and data as input and return a copy of the model with the optimized parameter values set.
+The goal is to make it easy to extend the fitting framework to create new fitters.
+The optimizers available in \astropypkg version 2.0 are Levenberg--Marquardt, Simplex, SLSQP, and LinearLSQFitter (which is based on \texttt{numpy.linalg} that provides exact solution for linear models).
+
+\inlinecomment{APW}{Add citations for the different optimizaton algorithms in paragraph above?}
 
 Modeling also supports a plugin system for fitters, which allows using the
-astropy models with external fitters. An example of this is
+\astropypk models with external fitters. An example of this is
 \package{SABA}\footnote{\url{https://github.com/astropy/saba}}, which is a bridge between
 Sherpa\footnote{\url{http://cxc.cfa.harvard.edu/contrib/sherpa/}}
-and \package{astropy.modeling}, to bring the Sherpa fitters into astropy.
+and \package{astropy.modeling}, to bring the Sherpa fitters into \astropypkg.
 
@@
 New model classes can be created in two ways:
-\begin{itemize}
-   \item The simplest way is to use the \texttt{custom\_model} decorator in modeling with a user defined function which takes the inputs and model parameters as arguments.
-   \item It is also possible to subclass the \texttt{Model} base class and create an arbitrary complex custom model.
-\end{itemize}
+\begin{enumerate}
+   \item The simplest way is to use the \texttt{custom\_model} decorator in modeling with a user-defined function that takes the inputs and model parameters as arguments.
+   \item It is also possible to subclass the \texttt{Model} base class and create an arbitrarily complex custom model.
+\end{enumerate}
 
@@
 
-The \package{modeling} package now supports the representation, evaluation and fitting of models using \texttt{Quantity} objects, which attach units to scalar values or arrays of values.
-In practice, this means that one can for example fit a model to data with units and get parameters that also have units out, or initialize a model with parameters with units and evaluating it using input values with different but equivalent units.
-Using this, we have implemented a blackbody model (\texttt{BlackBody1D}) that can be used to fit observed fluxes in a variety of units and as a function of different units of spectral coordinates.
+The \package{modeling} package now supports the representation, evaluation, and fitting of models using \texttt{Quantity} objects, which attach units to scalar values or arrays of values.
+In practice, this means that one can, for example, fit a model to data with units and get parameters that also have units out, or initialize a model with parameters with units and evaluate it using input values with different but equivalent units.
+Using this, we have implemented a blackbody model (\texttt{BlackBody1D}) that can be used to fit observed fluxes in a variety of units and as a function of different units of spectral coordinates (e.g., wavelength or frequency).
 

### 2017-11-13 main.tex
visualization

@@
 \astropypkg implements `normalized convolution' \citep[e.g.,][]{Knutsson1993}, which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.
-An example of this is given in \figurename \ref{fig:convolution-example}.
+An example of this is given in \figurename~\ref{fig:convolution-example}.
 In versions $<=1.3$, the direct convolution and Fast Fourier Transform (FFT) convolution approaches were not consistent, with FFT convolution implementing normalized convolution and direct convolution implementing a different approach.
@@
 
-The \package{visualization} package provides a framework for transforming values in images (and more generally any arrays), typically for the purpose of visualization.
+\package{astropy.visualization} provides a framework for transforming values in images (and more generally any arrays), typically for the purpose of visualization.
 Two main types of transformations are normalization and stretching of image values.
 
-Normalization transforms the images values to the [0:1] range using lower and upper limits where $x$ represents the values in the original image:
-
+Normalization transforms the images values to the range $[0,1]$ using lower and upper limits $(v_{\rm min}, v_{\rm max})$
 \begin{equation}
-y = \frac{x - v_{vmin}}{v_{max} - v_{min}}
+y = \frac{x - v_{\rm min}}{v_{\rm max} - v_{\rm min}}
 \end{equation}
-
-Stretching transforms the image values in the [0:1] range to the [0:1] range using a linear or non-linear function:
+where $x$ represents the values in the original image.
+
+Stretching transforms the image values in the range $[0,1]$ again to the range $[0,1]$ using a linear or non-linear function
 \begin{equation}
-z = f(y)
+z = f(y) \quad .
 \end{equation}
 
-Several classes are provided for determining intervals (e.g. using image percentiles) and for normalizing values in this interval to the [0:1] range.
-
-\package{Matplotlib} allows a custom normalization and stretch to be used when displaying data by passing a normalization object.
-The \package{visualization} package also provides a normalization class that wraps the interval and stretching objects into a normalization object that \package{matplotlib} understands.
+Several classes are provided for automatically determining intervals (e.g., using image percentiles) and for normalizing values in this interval to the $[0,1]$ range.
+
+\package{matplotlib} allows a custom normalization and stretch to be used when displaying data by passing a normalization object.
+The \package{astropy.visualization} package also provides a normalization class that wraps the interval and stretching objects into a normalization object that \package{matplotlib} understands.
 
@@
 
-One of the most common tasks by astronomers dealing with observational data is to make figures with images that include the correct coordinates and optionally with a coordinate grid.
-The challenge however is that the conceptual coordinate axes (such as longitude/latitude) need not be lined up with the pixel axes of the image.
-The \package{visualization.wcsaxes} subpackage implements a generalized way of making figures from an image array and a world coordinate system (WCS) object that provides the transformation between pixel and `world' coordinates.
-World coordinates can be for example right ascension and declination, but can also include for example velocity, wavelength, frequency, time, and so on.
+Astronomers dealing with observational imaging commonly need to make figures with images that include the correct coordinates and optionally display a coordinate grid.
+The challenge, however, is that the conceptual coordinate axes (such as longitude/latitude) need not be lined up with the pixel axes of the image.
+The \package{astropy.visualization.wcsaxes} subpackage implements a generalized way of making figures from an image array and a world coordinate system (WCS) object that provides the transformation between pixel and `world' coordinates.
+
+World coordinates can be, for example, right ascension and declination, but can also include, for example, velocity, wavelength, frequency, or time.
 The main features from this subpackage include the ability to control which axes to show which coordinate on (for example showing longitude ticks on the top and bottom axes and latitude on the left and right axes), controlling the spacing of the ticks either by specifying the positions to use or providing a tick spacing or an average number of ticks that should be present on each axis, setting the format for the tick labels to ones commonly used by astronomers, controlling the visibility of the grid/graticule, and overlaying ticks, labels, and/or grid lines from different coordinate systems.
 In addition, it is possible to pass data with more than two dimensions and slice on-the-fly.
-Finally, it is possible to define non-rectangular frames, such as for example for Aitoff projections.
-
-This subpackage differs from APLpy \citep{aplpy} in that the latter focuses on providing a very high-level interface to plotting that requires very few lines of code to get a good result, whereas WCSAxes defines an interface that is much closer to that of Matplotlib \citep{matplotlib}, and makes it possible to make significantly more advanced visualizations.
-An example of a visualization made with \package{wcsaxes} is shown in Figure~\ref{fig:wcsaxes} -- this example illustrates the ability to overlay multiple coordinate systems and customize which ticks/labels are shown on which axes around the image.
-This also uses the image stretching functionality from Section~\ref{sec:stretch} to show the image in a square root stretch (automatically updating the tick positions in the colorbar).
+Finally, it is possible to define non-rectangular frames, such as, for example, Aitoff projections.
+
+This subpackage differs from \package{APLpy} \citep{aplpy} in that the latter focuses on providing a very high-level interface to plotting that requires very few lines of code to get a good result, whereas WCSAxes defines an interface that is much closer to that of \package{matplotlib} \citep{matplotlib}.
+This enables significantly more advanced visualizations.
+
+An example of a visualization made with \package{wcsaxes} is shown in \figurename~\ref{fig:wcsaxes} -- this example illustrates the ability to overlay multiple coordinate systems and customize which ticks/labels are shown on which axes around the image.
+This also uses the image stretching functionality from \sectionname~\ref{sec:stretch} to show the image in a square root stretch (automatically updating the tick positions in the colorbar).
 
@@
 \caption{%
-An example of figure made using the \package{visualization.wcsaxes} subpackage, using \textit{Spitzer}/IRAC 8.0$\mu$m data from the Cygnus-X Spitzer Legacy survey \citep{cygnusx}.
+An example of figure made using the \package{astropy.visualization.wcsaxes} subpackage, using \textit{Spitzer}/IRAC 8.0$\mu$m data from the Cygnus-X \textit{Spitzer} Legacy survey \citep{cygnusx}.
 \label{fig:wcsaxes}
@@
 
-The package also provides the a histogram function, which is a generalization
-of \package{matplotlib}’s histogram function, to allow for more flexible
-specification of histogram bins.  The function provides several methods of
-automatically tuning the histogram bin size. It has a syntax identical to
-\package{matplotlib}’s histogram function (with the exception of the bins
-parameter), which allows specification of one of four different methods for
-automatic bin selection.
+\package{astropy.visualization} also provides a histogram function, which is a
+generalization of \package{matplotlib}’s histogram function, to allow for more
+flexible specification of histogram bins.  The function provides several methods
+of automatically tuning the histogram bin size. It has a syntax identical to
+\package{matplotlib}’s histogram function, with the exception of the \texttt{bins}
+parameter, which allows specification of one of four different methods for
+automatic bin selection: `blocks', `knuth', `scott', or `freedman'.
 
@@
 \cite{Lupton2004} describe an ``optimal'' algorithm for producing red-green-blue (RGB) composite images from three separate high-dynamic range arrays.
-The \package{visualization} package provides a convenience function to create such a color image.
+The \package{astropy.visualization} subpackage provides a convenience function to create such a color image.
 It also includes an associated set of classes to provide alternate scalings.
-This functionality was contributed by developers from the Large Synoptic Survey Telescope (LSST) and serves as an example of contribution to Astropy from a more traditional engineering organization \citep{lsst_astropy}.
-% Please cite the final SPIE paper here rather than the presentation slides at that conference.
-% https://ui.adsabs.harvard.edu/#abs/2016SPIE.9913E..0GJ/abstract (I'm not sure how to edit the bib file on overleaf)
+This functionality was contributed by developers from the Large Synoptic Survey Telescope (LSST) and serves as an example of contribution to Astropy from a more traditional engineering organization \citep{Jennes2016}.
 

### 2017-11-13 main.tex
period
stats edits

@@
 The package was described in detail in \cite{astropy}.
-The  default cosmology in \astropy v2.0 is given by the values in \cite{2016A&A...594A..13P}
+The default cosmology in \astropy version 2.0 is given by the values in \cite{2016A&A...594A..13P}.
 
 \subsection{Statistics}
+% Edited by Adrian PW
 
@@
 are useful for or specific to astronomy and are not found in or extend
-the available functionality of other \python\ statistics packages such
+the available functionality of other \python statistics packages such
 as \package{scipy} \citep{scipy} or \package{statsmodels}
-\citep{seabold2010statsmodels}.  The \package{stats} package contains
-a range of different functionality used by many different disciplines
+\citep{seabold2010statsmodels}.  \package{astropy.stats} contains
+a range of functionality used by many different disciplines
 in astronomy. It is not a complete set of statistic tools, but rather
@@
 
-The current review process for contributions to the \package{stats} package includes review of the code, documentation, testing, and scientific merit of the inclusion.
+% The current review process for contributions to the \package{astropy.stats} package includes review of the code, documentation, testing, and scientific merit of the inclusion.
 When necessary, scientific reviewers outside of the maintainers will be sought for their input on new pull requests.
 
-In this section, we describe these tools that provide a range of different functionality including robust statistical estimators, circular statistics, periodograms, spatial statistics, and histogram binning.
+In this section, we describe these tools, including robust statistical estimators, circular statistics, periodograms, spatial statistics, and histogram binning.
 
@@
 Robust statistics provide reliable estimates of basic statistics for complex distributions that largely mitigate the effects of outliers.
-The \package{stats} package includes several robust statistical functions that are commonly used in astronomy.
-This includes sigma clipping methods for rejecting outliers, median absolute deviation functions, and biweight estimators, which have been used to calculate the velocity dispersion of galaxy clusters \citep{Beers1990}.
+\package{astropy.stats} includes several robust statistical functions that are commonly used in astronomy, such as sigma clipping methods for rejecting outliers, median absolute deviation functions, and biweight estimators, which have been used to calculate the velocity dispersion of galaxy clusters \citep{Beers1990}.
 
@@
 A set of circular statistical estimators based on \citet{JammalamadakaSengupta}
-are implemented in the \package{stats} package.  These functions provide
+are implemented in \package{astropy.stats}.  These functions provide
 measurements of the circular mean, variance, and moment.   For all of these
 functions, they work with both \texttt{numpy.ndarrays} (assumed to be in
-radians) and \texttt{Quantity} objects.  In addition, the package includes
-tests for Rayleigh Test, vtest, and a function to compute the maximum likelihood estimator for the parameters of the von Mises
-distribution.
+radians) and \texttt{Quantity} objects.  In addition, the subpackage includes
+tests for Rayleigh Test, vtest, and a function to compute the maximum likelihood
+estimator for the parameters of the von Mises distribution.
 
 \subsubsection{Lomb-Scargle Periodograms}
-Periodic analysis of unevenly-spaced time series is common across subfields of Astronomy.
-The \package{stats} package now includes several efficient implementations of the Lomb-Scargle periodogram \citep{Lomb76, Scargle82} and several generalizations, including floating mean models \citep{Zechmeister09}, truncated Fourier models \citep{Bretthorst2003}, and appropriate handling of heteroscedastic uncertainties.
-Importantly, the implementations make use of several fast and scalable computational approaches \citep[e.g.][]{Press89, Palmer09}, and so can be applied to much larger datasets than Lomb-Scargle algorithms available in, e.g.
-\package{scipy.stats} (\citealt{scipy}).
+
+Periodic analysis of unevenly-spaced time series is common across many subfields of astronomy.
+The \package{astropy.stats} package now includes several efficient implementations of the Lomb-Scargle periodogram \citep{Lomb76, Scargle82} and several generalizations, including floating mean models \citep{Zechmeister09}, truncated Fourier models \citep{Bretthorst2003}, and appropriate handling of heteroscedastic uncertainties.
+Importantly, the implementations make use of several fast and scalable computational approaches \citep[e.g.,][]{Press89, Palmer09}, and so can be applied to much larger datasets than Lomb-Scargle algorithms available in, e.g., \package{scipy.stats} (\citealt{scipy}).
 Much of the Lomb-Scargle code in AstroPy has been adapted from previously-published open-source code \citep{astroML, VanderPlas2015}.
@@
 \subsubsection{Bayesian Blocks and Histogram Binning}
-AstroPy also includes an implementation of {\it Bayesian Blocks} \citep{Scargle2013}, an algorithm for analysis of break-points in non-periodic astronomical time-series.
+\astropypkg also includes an implementation of {\it Bayesian Blocks} \citep{Scargle2013}, an algorithm for analysis of break-points in non-periodic astronomical time-series.
 One interesting application of Bayesian Blocks is its use in determining optimal histogram binnings, and in particular binnings with unequal bin sizes.
 This code was adapted, with several improvements, from the \package{astroML} package \citep{astroML}.
-An example of a histogram fit using the Bayesian blocks algorithm is shown in the right panel of \figurename\ref{fig:bayes-blocks-hist}.
+An example of a histogram fit using the Bayesian blocks algorithm is shown in the right panel of \figurename~\ref{fig:bayes-blocks-hist}.
 

### 2017-11-13 main.tex
infrastructure

@@
 \package{astropy.modeling} provides an efficient way to instantiate the same type of model with many different sets of parameter values by passing the \texttt{n\_models} argument on instantiation, which sets the number of models to instantiate.
-The the values for each parameter in the model set must be passed as iterables of size \texttt{n_models}.
+The the values for each parameter in the model set must be passed as iterables of size \texttt{n\_models}.
 This creates a model set that can be efficiently evaluated.
@@
 Modeling also supports a plugin system for fitters, which allows using the
-\astropypk models with external fitters. An example of this is
+\astropypkg models with external fitters. An example of this is
 \package{SABA}\footnote{\url{https://github.com/astropy/saba}}, which is a bridge between
@@
 
-\section{Infrastructure for affiliated packages}
+\section{Infrastructure for Astropy affiliated packages}
+
 \label{sec:infrastructure}
-%\inlinecomment{BMS}{should we use links to the appropriate github repo?}
-%\inlinecomment{PLL}{IMHO a list of GitHub repo links for affil. pkgs. should be in appendix, if included.}
 \inlinecomment{BMS}{should we describe astropy-helpers even though it's future is unsure?}
-%
-\par In addition to astronomy related packages and libraries, the \astropy
-Project also maintains and distributes several generic purpose infrastructure packages.
-The following sections describes the most widely used selection of them.
-%
+% Text also edited by Adrian PW
+
+In addition to astronomy-specific packages and libraries, the \astropy Project
+also maintains and distributes several general-purpose infrastructure packages
+that help with the maintenance and upkeep of the \astropypkg core package and
+other affiliated packages.
+The following sections describes the most widely-used infrastructure packages
+developed by the \astropy Project.
+
 \subsection{Package template}
 % Brigitta may write this up if there is no other takers
-%
-\par \astropy provides the \package{package-template}\footnote{\url{https://github.com/astropy/package-template/}}
-package. Using this template, any \python package can make use of the ready-to-go package
-layout, setup, installation and documentation infrastructure developed originally for the
-\astropypkg core package and affiliated packages maintained by the \astropy. It also provides
-a testing framework, CI templates and configurations, Cython integration, and documentation
-on how to make it all work.
-%
+
+\astropy provides a package template --- as a separate \github repository,
+\package{astropy/package-template}\footnote{\url{https://github.com/astropy/package-t
+emplate/}} --- that aims to simplify setting up packaging, testing, and
+documentation builds for developers of affiliated packages or
+\astropypkg-dependent packages.
+Any \python package can make use of this ready-to-go package layout, setup,
+installation, and \package{Sphinx} documentation build infrastructure that was
+originally developed for the \astropypkg core package and affiliated packages
+maintained by the \astropy project.
+The package template also provides a testing framework, template configurations
+for continuous integration services, and \package{Cython} build support.
+
 \subsection{Continuous integration helpers}
 % Brigitta
-%
-\package{ci-helpers}\footnote{\url{https://github.com/astropy/ci-helpers}} is a
-collection of scripts that empowers package maintainers to control their testing
-set up and installation process for
-various continuous integration services via a set of environment
-variables. While the current development is mostly driven by the needs of
-the \astropy ecosystem, the actual usage of this package is extremely
-widespread. Currently we support setups for Travis CI and Appveyor CI.
-%
+
+\astropy also provides a set of scripts for setting up and configuring
+continuous integration (CI) services as a \github repository,
+\package{astropy/ci-helpers}\footnote{\url{https://github.com/astropy/ci-helpers}}
+These tools aim to empower package maintainers to control their testing set up
+and installation process for various continuous integration services through a
+set of environment variables.
+While the current development is mostly driven by the needs of the \astropy
+ecosystem, the actual usage of this package is extremely widespread. The current
+tools support configuration for Travis CI and Appveyor CI.
+
 \subsection{Sphinx extensions}
 
-The documentation for many \python packages the core \package{astropy} package
-as well as for all packages in the Astropy ecosystem is written using the
-Sphinx package. This package makes it possible to write the documentation using
-plain text files that follow a markup language called reStructuredText, and
-Sphinx can then transform this into HTML or \LaTeX{} documentation. As part of
-the project, we have developed a few extensions that facilitate generating
-documentation for a large project like Astropy. One of the main extensions we
-have developed is
+The documentation for many \python packages, the core \astropypkg package, and
+for all packages in the \astropy ecosystem is written using the
+\package{Sphinx} documentation build system.
+\package{Sphinx} makes it possible to write documentation using plain text files
+that follow a markup language called ``reStructuredText,'' which are then
+transformed into HTML or \LaTeX{} documentation during the documentation build
+process.
+For the \astropy project, we have developed a few \package{Sphinx} extensions
+that facilitate automatically generating API documentation for large projects,
+like the \astropypkg core package.
+The main extension we have developed is
 \package{sphinx-automodapi}\footnote{\url{http://sphinx-automodapi.readthedocs.io}},
 which makes it easy with a single reStructuredText command to generate a set of
-documentation pages listing all the available classes, functions, and
-attributes in any given \python module.
+documentation pages listing all of the available classes, functions, and
+attributes in a given \python module.
 
@@
 
-% TODO: need to put releases of sphinx-automodapi on Zenodo!
-
-%\inlinecomment{BMS}{What about pytest-astropy, should we inlude it here, or
-%  for the future section?}
-%\inlinecomment{PLL}{pytest-astropy is v3, right?}
 % \section{State of the Ecosystem}

### 2017-11-13 main.tex
future

@@
 continuous integration (CI) services as a \github repository,
-\package{astropy/ci-helpers}\footnote{\url{https://github.com/astropy/ci-helpers}}
+\package{astropy/ci-helpers}.\footnote{\url{https://github.com/astropy/ci-helpers}}
 These tools aim to empower package maintainers to control their testing set up
@@
 % edited by BMS
-
-%\inlinecomment{PLL}{In addition to PY3, add some killer features that we
-%  plan to implement for 3.0 and beyond?}
-%\inlinecomment{BMS}{Some killer features we already know about to definitely
-%have may be mentioned here. e.g. functionality of astropy-healpix? or the
-%performance/speedup focus of the 3.1 release?}
+% edited again by Adrian PW
+
+Following the release of version 2.0, development on the next major version of
+the \astropypkg core package (version 3.0) has already begun.
+On top of planned changes and additions to the core package, we also plan to
+overhaul the \astropy educational and learning materials, and further refactor
+and generalize the infrastructure utilities developed for the core package for
+the benefit of the community.
+
 \inlinecomment{BMS}{should we mention the refactored infra here?
   e.g. pytest-astropy and sphinx-astropy?}
-%\inlinecomment{SMC}{I've added a rough first draft -- please feel free to edit}
-%
-\par Development has already been continued after the release of v2.0 of
-\astropypkg. The most significant development for the next release will
-be removing python 2 support \citep{ape10}, the v3.0 \astropypkg release
-will only support python 3.  This will allow the use of the new
-functionality in python 3, simplify the code base, and reducing the
-testing overhead.   The v3.0 release is currently scheduled for January
-2018.
-%
+
+\subsection{Future versions of the \astropypkg core package}
+
+One of the most significant changes coming in this next major release will be
+removing support for \python 2 \citep{ape10}: future versions of \astropypkg
+will only support \python 3.5 and higher.
+Removing \python 2 support will allow the use of new, \python 3-only features,
+will simplify the code base, and reduce the testing overhead for the package.
+\astropypkg version 3.0 is currently scheduled for January 2018.
+
 \par In the next major release after v3.0, scheduled for the summer of
@@
 \inlinecomment{BMS}{TODO: uncomment references of packages once they are available}
+
 \subsection{Learn Astropy}

### 2017-11-13 main.tex
more future

@@
 
-\subsection{Future versions of the \astropypkg core package}
+\subsection{Future versions of the \astropypkg core and affiliated packages}
 
@@
 
-\par In the next major release after v3.0, scheduled for the summer of
+In the next major release after version 3.0, scheduled for the summer of
 2018, the focus will be on optimization of the code and improved
-documentation. To prepare for this release, software for testing and
-monitoring the performance of the code are being developed.   Less
-functionality may be introduced in this release while the focus will be
-primarily on improved performance.  In addition, a new suite of tutorials
-and documentation are being prepared for this release.
-%
-\par Beyond the core code, the \astropy project is also further
-developing the affiliated packages.  This includes elevating a suite of
-packages into part of the core project. While these may not be integrated
-into the \astropypkg core code, these projects provide code that is
-useful to the astronomical community and meet the testing and
-documentation standards of \astropy.   Some of these new efforts includes
-an initiative to develop tools for spectroscopy
-\citep[\package{specutils}, \package{specreduc}, \package{specviz}]
+documentation.
+To prepare for this release, we are preparing software for testing, evaluating,
+and monitoring the performance of the code.
+Less functionality may be introduced in this release while the focus will be
+primarily on improved performance.
+
+Beyond the core code, the \astropy project is also further developing the
+\astropy-managed affiliated packages.
+While these may not be integrated into the \astropypkg core package, these
+projects provide code that is useful to the astronomical community and meet the
+testing and documentation standards of \astropy.
+Some of these new efforts includes an initiative to develop tools for
+spectroscopy \citep[\package{specutils}, \package{specreduc}, \package{specviz}]
 {ape13}, integration of LSST software, and packages to support HEALPIX
-projection% \citep{astropy-healpix}
-.
+projection. %\citep{astropy-healpix}
 \inlinecomment{BMS}{TODO: uncomment references of packages once they are available}
@@
 The \astropypkg core package documentation contains narrative descriptions of
-the package functionality along with detailed usage notes for functions, classes, and modules.
+the package functionality along with detailed usage notes for functions,
+classes, and modules.
 While useful as a reference and for more advanced \python users, it is not the

### 2017-11-13 main.tex
conclusion

@@
 
-\section{Outlook}
-\label{sec:outlook}
-\inlinecomment{hamogu}{This may be merged into the section above once
-  that is fleshed out a little more.}  As shown above the development
-of the \astropypkg package is making good progress, helping
-astronomers worldwide to perform many daily tasks such as planning
-observations, analyzing data or simulation results, and writing
-publications. The strong emphasis that the \astropy project puts on
-reliability and code correctness helps users to trust the calculations
-performed with \astropypkg and to publish reproducible results. More
-functionality is added to the core package and more and more
-affiliated packages support more specialized needs.
-
-At the same time, \astropy is spreading awareness of best practices in
-software development. This is important since most practicing
-astronomers received their education without being taught in computer
-science and software development although a major fraction of almost
-every astronomer's workload today is related to software use and
-development. The \astropypkg package leads by example, showing all interested
-astronomers how modern tools like git version control or continuous
-integration (code is tested after every change to the source) can
-increase the quality and accessibility of astronomical software
-without overly complicating the development cycle. All submitted code
-is reviewed by at least one, but typically more, members of the
-\astropy community, providing feedback and allowing contributors to
-improve their skill is developing software without the need for their
-institutions to provide dedicated teaching resources. Thus, the
-\astropy project does not only build the tools needed to perform
-productive astronomical research in an era of increasingly large and
-complex datasets, it also helps to prepare the current and the next
-generation of researchers with the knowledge to adequately use those
-tools.
+\section{Conclusion}
+\label{sec:conclusion}
+% Renamed and edited by Adrian PW
+
+The development of the \astropypkg package and cultivation of the \astropy
+ecosystem is still maintaining significant growth while improving stability,
+breadth, and reliability.
+As the \astropypkg core package becomes more mature, several subpackages have
+reached stability with a rich set of features that help astronomers worldwide to
+perform many daily tasks such as planning observations, analyzing data or
+simulation results, and writing publications.
+The strong emphasis that the \astropy project puts on reliability and code
+correctness helps users to trust the calculations performed with \astropypkg and
+to publish reproducible results.
+At the same time, the \astropy ecosystem and core package are growing: new
+functionality is still being contributed, and new affiliated packages are being
+developed to support more specialized needs.
+
+The \astropy project is also spreading awareness of best practices in
+community-driven software development.
+This is important as most practicing astronomers were not explicitly taught
+computer science and software development, despite the fact that a major
+fraction of nearly every astronomer's workload today is related to software use
+and development.
+The \astropypkg package leads by example, showing all interested astronomers how
+modern tools like \texttt{git} version control or continuous integration can
+increase the quality, accessibility, and discoverability of astronomical
+software without overly complicating the development cycle.
+Within \astropy, all submitted code is reviewed by at least one, but typically
+more, members of the \astropy community, who provide feedback to contributors
+to help improve their skills.
+As a community, we follow an explicit code of conduct \citep{ape8} and treat all
+contributors and users with respect, provide a harassment-free environment, and
+encourage and welcome new contributions from all.
+Thus, while the \astropy project provides and develops software and tools
+essential to modern astronomical research, it also helps to prepare the current
+and next generation of researchers with the knowledge to adequately use,
+develop, and contribute to those tools within conscientious and welcoming
+community.
 

### 2017-11-13 main.tex
grammar

@@
 and next generation of researchers with the knowledge to adequately use,
-develop, and contribute to those tools within conscientious and welcoming
+develop, and contribute to those tools within a conscientious and welcoming
 community.

### 2017-11-14 main.tex
switch APE and development model sections

@@
 community.
-A key element of the project is the \astropy core package, which serves as the
+A key element of the project is the \astropy core package \astropypkg, which serves as the
 foundation for more specialized projects and packages.
@@
 All astronomical research makes use of software in some way.  Astronomy as a field has thus long supported the development of software tools
-for astronomical tasks: from scripts that enable individualized scientific research to software packages that enable collaborations to data reduction pipelines for survey operations.
+for astronomical tasks: from scripts that enable individual scientific research to software packages for small collaborations to data reduction pipelines for survey operations.
 Some software packages are or were supported by large institutions and are intended for a wide range of users. These packages typically provide some level of documentation and user support or
@@
 
-\python has become especially popular in the quantitative sciences, especially
+\python has become especially popular in the quantitative sciences,
 where researchers must simultaneously produce research, perform data analysis,
@@
 and a continuously-growing ecosystem of tools and web services that enable
-easier collaboration on software development, easier writing and sharing
-documentation, and continuous testing and validation of software.
+easier collaboration on software development, easier writing and sharing of
+software documentation, and continuous testing and validation of software.
 More recently, package managers such as
@@
 In this paper, we describe the current status of the \astropy community and the
-\astropypkg core package and discuss goals for future development
+\astropypkg core package and discuss goals for future development.
 
@@
 between many contributors with many interests, and in part due to simply the
-amount of work that needs to get done.  In part for the latter reason, the
+amount of work that needs to get done.  For the latter reason, the
 project has expanded the committee from three to four members starting in
@@
 
+\subsection{Astropy development model}
+% draft by Adrian PW and Erik T.
+Code is contributed to the \astropypkg core package or modified through ``pull
+requests'' (via \github) that often contain several \texttt{git} commits.
+Pull requests may fix bugs, implement new features, or improve or modify the
+infrastructure that supports the development and maintenance of the package.
+Individual pull requests are generally limited to a single conceptual addition
+or modification to make code review tractable.
+Pull requests that modify or add code to a specific subpackage must be reviewed
+and approved by one of the subpackage maintainers before it is merged into the
+core codebase.
+Bugs and feature requests are reported via the \github issue tracker and labeled
+with a set of possible labels that help classify and organize the issues.
+The development workflow is detailed in the \astropypkg
+documentation.\footnote{\emph{How to make a code contribution}, \url{http://docs.
+astropy.org/en/stable/development/workflow/development_workflow.html}}
+
+As of version 2.0, \astropypkg contains $212244$ lines of code\footnote{This
+line count includes comments, as these are often as important for
+maintainability as the code itself.  Without comments there are $142197$ lines
+of code.} contributed by $232$ unique contributors over $19270$ \texttt{git}
+commits.
+The commit distribution follows an approximate power-law (with log-slope of
+$\approx -0.47$), meaning most of the commits were and are contributed by a
+relatively small fraction of the contributor pool.
+Roughly half of the commits were contributed by the top $4$
+contributors, while $\sim 90$ percent of the commits came from the top $24$
+contributors.
+
 \subsection{APEs - Astropy Proposals for Enhancement}
@@
 Central to the success of \astropy is an open environment where anybody can
-contribute to the project by opening a so-called ``pull request'' with a new
-contribution on a publically available
-website.\footnote{\url{https://github.com/astropy/astropy}}
-This request is then reviewed by at least one of the maintainers responsible for
-the specific subpackage or content and is possibly merged into the main code
-base.
-Most bug fixes, documentation edits, and small features are contributed in this
-way.
+contribute to the project.
 However, this model leads to ``organic'' growth where different features are
@@
 make an executive decision based on the community input on the APE in question.
-
-\subsection{Astropy development model}
-% draft by Adrian PW and Erik T.
-\inlinecomment{BMS}{Move this subsection before the APE one, as that one has some repeated content in the first sentences that belongs here}
-Code is contributed to the \astropypkg core package or modified through ``pull
-requests'' (via \github) that often contain several \texttt{git} commits.
-Pull requests may fix bugs, implement new features, or improve or modify the
-infrastructure that supports the development and maintenance of the package.
-Individual pull requests are generally limited to a single conceptual addition
-or modification to make code review tractable.
-Pull requests that modify or add code to a specific subpackage must be reviewed
-and approved by one of the subpackage maintainers before it is merged into the
-core codebase.
-Bugs and feature requests are reported via the \github issue tracker and labeled
-with a set of possible labels that help classify and organize the issues.
-The development workflow is detailed in the \astropypkg
-documentation.\footnote{\emph{How to make a code contribution}, \url{http://docs.
-astropy.org/en/stable/development/workflow/development_workflow.html}}
-
-As of version 2.0, \astropypkg contains $212244$ lines of code\footnote{This
-line count includes comments, as these are often as important for
-maintainability as the code itself.  Without comments there are $142197$ lines
-of code.} contributed by $232$ unique contributors over $19270$ \texttt{git}
-commits.
-The commit distribution follows an approximate power-law (with log-slope of
-$\approx -0.47$), meaning most of the commits were and are contributed by a
-relatively small fraction of the contributor pool.
-$\approx 50$ percent of the commits were contributed by the top $4$
-contributors, while $\sim 90$ percent of the commits came from the top $24$
-contributors.
 

### 2017-11-14 main.tex
Finish affiliated package section

@@
 % edited by Adrian PW
-
+\label{sect:coordcom}
 From its inception, \astropy has required coordination to ensure the project
@@
 This mechanism is called ``Astropy Proposal for Enhancement'' (APE) and are
-modeled after the ``Python Enhancement Proposals'' (PEP) and guide the
+modeled after the ``Python Enhancement Proposals'' (PEP) that guide the
 development of the \python programming language.
@@
 Affiliated packages may also be used to develop substantial, new functionality
-that will eventually be incorporated into the \astropypkg core package: as
-initially separate packages, the typically rapid development or new,
-experimental features may benefit from having a release cycle that is not tied
+that will eventually be incorporated into the \astropypkg core package. 
+Initially separate packages with typically rapid initial development and new experimental features benefit from having a release cycle that is not tied
 to the \astropypkg core.
-
-\inlinecomment{APW}{This needs to be finished:}
-In general we hope that becoming an affiliated package is seen as
-a good way for new and existing packages to gain exposure.
-%
-\inlinecomment{BMS}{TODO: write about the process of becoming affiliated, and project packages into the future section below}
+Affiliated pacakges are listed on the main astropy website and advertized to the community through astropy mailing lists, so becoming an affiliated package is sa good way for new and existing packages to gain exposure while at the same time promoting \astropy's high standard for code and documentation quality.
+This process of listing and promoting affiliated packages is one way in which the \astropy project tries to help with code reuse in the astronomical community.
+Packages can become affilited to \astropy by applying for this status on a public mailing list.
+The coordination comittee (sect.~\ref{sect:coordcom}) reviews such requests and issues recommendations for the improvement of a package where possible.
 

### 2017-11-14 main.tex
Update on Overleaf.

@@
 community.
-A key element of the project is the \astropy core package \astropypkg, which serves as the
+A key element of the \astropy project is the core package \astropypkg, which serves as the
 foundation for more specialized projects and packages.
@@
 The commit distribution follows an approximate power-law (with log-slope of
-$\approx -0.47$), meaning most of the commits were and are contributed by a
+$\approx -0.47$) \inlinecomment{AG}{round to -0.5?  This is astronomy, after all.}, meaning most of the commits were and are contributed by a
 relatively small fraction of the contributor pool.
@@
 Thus, \astropy has a mechanism to more formally propose significant changes to
-the core package (e.g., the release cycle; \citealt{ape2}), to plan out major
+the core package (e.g., the release cycle; \citealt{ape2})\inlinecomment{AG}{Is the release cycle really part of the core package?
+That's how this reads.
+Is there something more concretely linked to the code we can use as an example here?}, to plan out major
 new features, or institute new organization-wide policies (e.g.,
@@
 development of the \python programming language.
-In an APE one or more authors describe in detail the proposed changes or
+In an APE, one or more authors describe in detail the proposed changes or
 additions, including a rationale for the changes, how these changes will be
@@
 practices such as testing and thorough documentation.
+
 Affiliated packages contain functionality that is more specialized,
@@
 \astropypkg core package.
-Affiliated packages may also be used to develop substantial, new functionality
+Affiliated packages may also be used to develop substantial new functionality
 that will eventually be incorporated into the \astropypkg core package. 
-Initially separate packages with typically rapid initial development and new experimental features benefit from having a release cycle that is not tied
-to the \astropypkg core.
-Affiliated pacakges are listed on the main astropy website and advertized to the community through astropy mailing lists, so becoming an affiliated package is sa good way for new and existing packages to gain exposure while at the same time promoting \astropy's high standard for code and documentation quality.
-This process of listing and promoting affiliated packages is one way in which the \astropy project tries to help with code reuse in the astronomical community.
-Packages can become affilited to \astropy by applying for this status on a public mailing list.
-The coordination comittee (sect.~\ref{sect:coordcom}) reviews such requests and issues recommendations for the improvement of a package where possible.
+New functionality benefits from having a rapid development and release cycle that is not tied to that of the \astropypkg core.
+% AG: rephrased this.
+%Initially separate packages with typically rapid initial development and new experimental features benefit from having a release cycle that is not tied to the
+
+Affiliated packages are listed on the main astropy website and advertised to the community through astropy mailing lists, so becoming an affiliated package is a good way for new and existing packages to gain exposure while at the same time promoting \astropy's high standard for code and documentation quality.
+This process of listing and promoting affiliated packages is one way in which the \astropy project tries to help with \inlinecomment{AG}{Increase?} code reuse in the astronomical community.
+
+Packages can become affiliated to \astropy by applying for this status on a public mailing list.
+The coordination committee (sect.~\ref{sect:coordcom}) reviews such requests and issues recommendations for the improvement of a package where possible.
 
@@
 
-The \astropypkg has a regular release schedule consisting of new significant
+\astropypkg has a regular release schedule consisting of new significant
 releases every 6 months, with bugfix releases as needed \citep{ape2}.

### 2017-11-14 main.tex
change description to subsubsection to avoid awkward layout

--- 2017-11-14 main.tex
@@
 
-The \astropypkg has a regular release schedule consisting of new significant
+The \astropypkg package has a regular release schedule consisting of new significant
 releases every 6 months, with bugfix releases as needed \citep{ape2}.
-The major releases will contain new features or any significant changes, whereas
+The major releases contain new features or any significant changes, whereas
 the bugfix releases only contain fixes to code or documentation but no new
@@
 from PyPI for Windows, Mac OS X and Linux systems that provide faster
-installation compared to the source distribution.  Optionally, the version of
-the package and the dependencies needed to run or build the software are given
-by a specifier to the pip package manager as described in PEP 440\footnote{For
-more detailed installation instructions and optional flags see
-\url{http://docs.astropy.org/en/stable/install.html\#installing-astropy}}.
+installation compared to the source distribution.
+% hamogu: I think that's too detailed for a journal paper.
+%     It's in the docs if anyone needs it.
+%Optionally, the version of
+%the package and the dependencies needed to run or build the software are given
+%by a specifier to the pip package manager as described in PEP 440\footnote{For
+%more detailed installation instructions and optional flags see
+%\url{http://docs.astropy.org/en/stable/install.html\#installing-astropy}}.
 
@@
 may be outdated compared with the latest stable release of \astropy accessible
-from the PyPI. Pre-built binary conda packages for all of the affiliated packages are also available  via the \texttt{astropy} conda channel for the three major platforms.
+from the PyPI. Pre-built binary conda packages for all of the affiliated packages are also available  via the \texttt{astropy} conda channel for Linux, Max OS X, and MS Windows.
 % * <mattwcraig@gmail.com> 2017-10-27T07:16:27.310Z:
@@
 
-\inlinecomment{BMS}{The itemizations below look very weird being boldface under a much less prominent subsection title. would it be nicer in the final version if we leave it as is in the draft?}
-
 % \subsection{Analytic Functions}
@@
 In \texttt{astropy.units}, \texttt{Quantity} objects subclass the \texttt{numpy}
-array object and has been designed with speed in mind.
+array object and have been designed with speed in mind.
 As of \astropypkg version 2.0, units and quantities are prevalent in most other
@@
 
-\begin{description}
-    \item[Interaction with \package{numpy} arrays] The \texttt{Quantity} object
+\subsubsection{Interaction with \package{numpy} arrays}
+
+The \texttt{Quantity} object
         is now a subclass of the \texttt{numpy.ndarray} object and therefore
@@
         trigonometric functions expect) before being passed to \texttt{numpy}.
-    \item[Speed improvements] The \texttt{Quantity} object is now significantly
+
+\subsubsection{Speed improvements} The \texttt{Quantity} object is now significantly
         faster than in early versions of \astropypkg. This is in large part due
@@
         subclassed.
-    \item[Logarithmic units and magnitudes] By default, taking the logarithm of
+
+\subsubsection{Logarithmic units and magnitudes}
+        By default, taking the logarithm of
         a \texttt{Quantity} object with non-dimensionless units intentionally
@@
         Logarithmic, relative units are now supported in \texttt{astropy.units}.
-    \item[Using quantities in tables] The \texttt{astropy.table} subpackage (see
+
+\subsubsection{Using quantities in tables}
+
+        The \texttt{astropy.table} subpackage (see
         \sectionname~\ref{sec:table}) now supports using quantities in tables
@@
         with quantities can be read and written to various file formats.
-    \item[Defining functions that require quantities] When writing code or
+
+\subsubsection{Defining functions that require quantities}
+        When writing code or
         functions that expect \texttt{Quantity} objects, we often want to
@@
         \texttt{quantity\_input()}, that does this verification automatically.
-\end{description}
 
@@
 ascension, declination, and distance from solar system barycenter) or Cartesian
-coordinates ($x$, $y$, $z$ with the origin at ).
+coordinates ($x$, $y$, $z$ with the origin at barycenter).
 They can therefore change representations independent of being transformed to
@@
 
-\begin{description}
-    \item[Local Earth coordinate frames] In addition to representing celestial
+\subsubsection{Local Earth coordinate frames}
+In addition to representing celestial
     coordinates, \astropypkg now supports specifying positions on the Earth in
@@
 
-    \item[Proper motion and velocity transformations]
+\subsubsection{Proper motion and velocity transformations}
     In addition to positional coordinate data, the \texttt{Frame} classes now
@@
 
-    \item[Derivatives of coordinate representations]
+\subsubsection{Derivatives of coordinate representations}
     As mentioned above, the \texttt{Representation} classes act like
@@
 
-    \item[Solar System Ephemerides]
+\subsubsection{Solar System Ephemerides}
     Also new is support for computing ephemerides of major solar system bodies
@@
     optional dependency and an internet connection).
-    The \texttt{get\_body} and \texttt{get\_body\_barycentric} functions provide
-    the gateway to this functionality, yielding \texttt{SkyCoord} objects given
-    a specific body and choice of ephemeris source.
-
-\end{description}
+    % hamogu: I think the specific names of functions can be in the docs
+    % and don't need to be repeated here.
+    %The \texttt{get\_body} and \texttt{get\_body\_barycentric} functions provide
+    %the gateway to this functionality, yielding \texttt{SkyCoord} objects given
+    %a specific body and choice of ephemeris source.
 
@@
 
-\begin{description}
-    \item[Barycentric and Heliocentric corrections] Detailed eclipse or transit
+\subsubsection{Barycentric and Heliocentric corrections}
+Detailed eclipse or transit
         timing requires accounting for light travel time differences from the
@@
         \texttt{light\_travel\_time} method of a \texttt{Time} object.
-    \item[\texttt{Time} objects as \texttt{Table} columns] \texttt{Time} objects
+\subsubsection{\texttt{Time} objects as \texttt{Table} columns} \texttt{Time} objects
         can now be added as columns in \package{astropy.table} \texttt{Table}
@@
         type.
-\end{description}
 
@@
 
-We summarize key new features or updates to \package{astropy.table} below:
-\begin{description}
-    \item[Support for grouped table operations] Some tables contain data that
-        naturally form groups.
-        For example, a table of photometry for galaxies, stars, and quasars.
-        We may then want to split the table or a column into these groups and
+Next, we summarize key new features or updates to \package{astropy.table}.
+
+\subsubsection{Support for grouped table operations}
+Tables can contain data that naturally form groups, for example monitoring of an object in different bands.
+We may then want to split the table or a column into these groups (in this example: observations in different filters)  and
 compute some statistic on the data, or filter the groups based on some
 criteria.
-        Grouped operations are now supported by \texttt{Table} objects,
-        mainly through the \texttt{group\_by()} method and subsequent operations
-        on the grouped version of the table or column.
-    \item[Support for table concatenation] Tables can be combined in several
+Grouped operations are now supported by \texttt{Table} objects.
+%,
+%mainly through the \texttt{group\_by()} method and subsequent operations
+%on the grouped version of the table or column.
+
+\subsubsection{Support for table concatenation}
+Tables can be combined in several
 different ways.
@@
 also possible when two tables share some common columns.
-        All three of these operations are now possible with \texttt{Table}
-        objects through the \texttt{vstack}, \texttt{hstack}, and \texttt{join}
-        functions in \package{astropy.table}.
-    \item[Mixin columns for time and coordinates] The default data containers
-        for \texttt{Table} objects are \texttt{Column} objects.
-        However, sometimes the data for a given column is better represented as
-        a \texttt{Quantity}, or a sky coordinate (\texttt{SkyCoord}), or an
-        astronomical \texttt{Time} object.
-        The \texttt{Table} object now supports these and other objects to serve
+%All three of these operations are now possible with \texttt{Table}
+%objects through the \texttt{vstack}, \texttt{hstack}, and \texttt{join}
+%functions in \package{astropy.table}.
+
+\subsubsection{Mixin columns for time and coordinates}
+The \texttt{Table} object now supports \texttt{Quantity}, sky coordinate (\texttt{SkyCoord}),
+astronomical \texttt{Time} objects and and other objects to serve
 as array-like containers for column data through the ``mixin'' protocol.
-    \item[Transform to and from \texttt{Pandas} \texttt{DataFrame} objects]
-        \texttt{Table} objects can now be created from a \texttt{DataFrame}
-        object (\texttt{from\_pandas()}), or exported to a \texttt{DataFrame}
-        object (\texttt{to\_pandas()}).
-        \texttt{DataFrame} objects do not support multi-dimensional array
-        columns, so this conversion will fail if the source \texttt{Table}
-        object contains any such columns.
-\end{description}
+
+%hamogu: I've commented this out.
+% I think it's very specific and not relevant to non-developers.
+% If we want to keep it, we need to add at least 102 senteces about what Pandas
+% is and I think that's more text than is warrented for this feature.
+
+%\subsubsection{Transform to and from \texttt{Pandas} \texttt{DataFrame} objects}
+%\texttt{Table} objects can now be created from a \texttt{DataFrame}
+%object (\texttt{from\_pandas()}), or exported to a \texttt{DataFrame}
+%object (\texttt{to\_pandas()}).
+%\texttt{DataFrame} objects do not support multi-dimensional array
+%columns, so this conversion will fail if the source \texttt{Table}
+%object contains any such columns.
 
@@
 We summarize key new features or updates to \package{astropy.io} below,
-organized by sub-subpackage:
-\begin{description}
-
-    \item [Enhanced CSV format]
+organized by sub-subpackage.
+
+\subsubsection{Enhanced CSV format}
 
@@
 
-    \item[\texttt{.ascii}: fast readers and writers]
+\subsubsection{\texttt{.ascii}: fast readers and writers}
 
@@
 
-    \item[\texttt{.ascii}: HTML tables]
+\subsubsection{\texttt{.ascii}: HTML tables}
 
@@
 
-    \item [\texttt{.fits}: command-line scripts (\texttt{fitsheader}, \texttt{fitsinfo})]
+\subsubsection{\texttt{.fits}: command-line scripts (\texttt{fitsheader}, \texttt{fitsinfo})}
 
@@
 
-    \item [\texttt{.fits}: lazy loading ]
+\subsubsection{\texttt{.fits}: lazy loading }
 
@@
 
-    \item [\texttt{.misc}: YAML serialization ]
+\subsubsection{\texttt{.misc}: YAML serialization}
 
@@
         HDF5.
-
-\end{description}
 

### 2017-11-14 main.tex
modle edits

@@
         faster Cython/C engine for reading and writing ASCII files. This is
-        available for the following formats: \texttt{basic},
-        \texttt{commented\_header}, \texttt{csv}, \texttt{no\_header},
-        \texttt{rdb}, and \texttt{tab}.  On average the new engine is about
+        available for the most common formats.
+
+ %following formats: \texttt{basic},
+  %      \texttt{commented\_header}, \texttt{csv}, \texttt{no\_header},
+        %      \texttt{rdb}, and \texttt{tab}.
+        On average the new engine is about
         4 to 5 times faster than the corresponding pure-\python
@@
 package.\footnote{\url{https://github.com/spacetelescope/gwcs}}
-The recently-added support for \package{astropy.units} in models and fitters
-make it a uniquely powerful package for working with astrophysical models.
+
+% hamogu: I comented this out because we don't have prrof that it's
+% ``uniquly'' useful. THe developers of e.g. ISIS, Sherpa, for even IRAF
+% will probably disagree.
+%The recently-added support for \package{astropy.units} in models and fitters
+%make it a uniquely powerful package for working with astrophysical models.
 
 \subsubsection{Single Model Definition and Evaluation}
+\inlinecomment{hamogu: I tihnk this is too techical. I know it's a complex subpackage but I had trouble understanding this section even as a regular user.}
 Most models are defined by parameters and maintain an ordered list of parameter names, \texttt{Model.param\_names}.
@@
 Parameters support arithmetic operations and are combined with the inputs during evaluation using the \package{numpy} broadcasting rules.
-A model is evaluated by calling it as a function and passing the inputs in as arguments.
+A model is evaluated by calling it as a function.
 
@@
 \package{astropy.modeling} provides an efficient way to instantiate the same type of model with many different sets of parameter values by passing the \texttt{n\_models} argument on instantiation, which sets the number of models to instantiate.
-The the values for each parameter in the model set must be passed as iterables of size \texttt{n\_models}.
-This creates a model set that can be efficiently evaluated.
-Model sets are most useful for efficiently fitting multiple linear models of the same kind.
+This creates a model set that can be efficiently evaluated for example, in PSF (point spread function) photometry, all objects in an image will have a PSF of the same functional form, but with different positions and amplitides.
 
@@
 For all arithmetic operators, the left and the right models must have the same number of inputs and outputs.
+An example of a compound model could be a spectrum with interstellar absorption.
+The stellar spectrum and the interstellar extinction are represented by separate models, but the observed spectrum is fitted with a compoud model that combines both.
 

### 2017-11-14 main.tex
use more \astropy

@@
 
-Affiliated packages are listed on the main astropy website and advertised to the community through astropy mailing lists, so becoming an affiliated package is a good way for new and existing packages to gain exposure while at the same time promoting \astropy's high standard for code and documentation quality.
+Affiliated packages are listed on the main \astropy website and advertised to the community through \astropy mailing lists, so becoming an affiliated package is a good way for new and existing packages to gain exposure while at the same time promoting \astropy's high standard for code and documentation quality.
 This process of listing and promoting affiliated packages is one way in which the \astropy project tries to help with \inlinecomment{AG}{Increase?} code reuse in the astronomical community.
@@
 no package can be guaranteed to implement all transformations to arbitrary precision, and since some transformations are sometimes subject to interpretation of standards (in particular in the case of Galactic coordinates), we do not designate any of the existing packages as the `ground truth' but instead compare each tool to all other tools to find.
-The benchmarks are thus useful beyond the Astropy project since they allow all of the tools to be compared to all other tools.
-The tools included in the benchmark at the moment include the astropy core package, Kapteyn \citep{kapteyn}, NOVAS \citep{novas}, PALpy \citep{pal}, PyAST \citep[a wrapper for AST, described in][]{ast}, PyTPM\footnote{\url{https://github.com/phn/pytpm}}, PyEphem \citep{pyephem}, and pySLALIB \citep[a Python wrapper for SLALIB, described in][]{slalib}.
+The benchmarks are thus useful beyond the \astropy project since they allow all of the tools to be compared to all other tools.
+The tools included in the benchmark at the moment include the \astropypkg core package, Kapteyn \citep{kapteyn}, NOVAS \citep{novas}, PALpy \citep{pal}, PyAST \citep[a wrapper for AST, described in][]{ast}, PyTPM\footnote{\url{https://github.com/phn/pytpm}}, PyEphem \citep{pyephem}, and pySLALIB \citep[a Python wrapper for SLALIB, described in][]{slalib}.
 
@@
 Table \ref{tab:coordinate_benchmarks} gives an example of the relative accuracy of the conversion from FK4 to Galactic coordinates for all pairs of tools.
-This shows for example that astropy, Kapteyn and PyTPM agree perfectly (to the precision shown), while PALpy, pySLALIB, and PyAST also agree perfectly amongst themselves, but show an offset of around 0.2\arcsec with the former three packages.
+This shows for example that \astropy, Kapteyn and PyTPM agree perfectly (to the precision shown), while PALpy, pySLALIB, and PyAST also agree perfectly amongst themselves, but show an offset of around 0.2\arcsec with the former three packages.
 Finally, PyEphem disagrees with other packages by 0.4-0.8\arcsec.
@@
 It also includes an associated set of classes to provide alternate scalings.
-This functionality was contributed by developers from the Large Synoptic Survey Telescope (LSST) and serves as an example of contribution to Astropy from a more traditional engineering organization \citep{Jennes2016}.
+This functionality was contributed by developers from the Large Synoptic Survey Telescope (LSST) and serves as an example of contribution to \astropy from a more traditional engineering organization \citep{Jennes2016}.
 
@@
 Importantly, the implementations make use of several fast and scalable computational approaches \citep[e.g.,][]{Press89, Palmer09}, and so can be applied to much larger datasets than Lomb-Scargle algorithms available in, e.g., \package{scipy.stats} (\citealt{scipy}).
-Much of the Lomb-Scargle code in AstroPy has been adapted from previously-published open-source code \citep{astroML, VanderPlas2015}.
+Much of the Lomb-Scargle code in \astropy has been adapted from previously-published open-source code \citep{astroML, VanderPlas2015}.
 

### 2017-11-14 make_ngc6977_image.py
Update on Overleaf.

@@ -1,0 +1,21 @@
+from astropy.io import fits
+from astropy.utils.data import get_pkg_data_filename
+from astropy.visualization import make_lupton_rgb
+
+# load the data
+g_name = get_pkg_data_filename('visualization/reprojected_sdss_g.fits.bz2')
+r_name = get_pkg_data_filename('visualization/reprojected_sdss_r.fits.bz2')
+i_name = get_pkg_data_filename('visualization/reprojected_sdss_i.fits.bz2')
+g = fits.open(g_name)[0].data
+r = fits.open(r_name)[0].data
+i = fits.open(i_name)[0].data
+
+# extract a smaller region around the Hickson 88 group
+slc = (slice(0, 285), slice(33, 318))
+gp = g[slc]
+rp = r[slc]
+ip = i[slc]
+
+# make the figure
+rgb = make_lupton_rgb(ip*0.8, rp, gp*1.3, Q=10, stretch=0.4,
+                      filename='ngc6977.png')

### 2017-11-15 main.tex
minor edits

@@
 % Adrian PW: how are there still no software keywords in AAS journals?!?
-\keywords{
+\keywords{%
     Astrophysics - Instrumentation and Methods for Astrophysics
@@
 Packages can become affiliated to \astropy by applying for this status on a public mailing list.
-The coordination committee (sect.~\ref{sect:coordcom}) reviews such requests and issues recommendations for the improvement of a package where possible.
+The coordination committee (\sectionname~\ref{sect:coordcom}) reviews such requests and issues recommendations for the improvement of a package where possible.
 
@@
 releases, which continue to receive bugfixes for 2 years following the release
-with no changes to the API.
+with no changes to the API\@.
 The LTS versions are ideal for pipelines and other applications where API
@@
 including Debian, Ubuntu, Fedora, Gentoo, Arch Linux, Mac OS X (e.g.,
-via brew, macports or fink) and FreeBSD.  However, on occasion these packages
+via brew, macports or fink) and FreeBSD\@.  However, on occasion these packages
 may be outdated compared with the latest stable release of \astropy accessible
-from the PyPI. Pre-built binary conda packages for all of the affiliated packages are also available  via the \texttt{astropy} conda channel for Linux, Max OS X, and MS Windows.
+from the PyPI\@. Pre-built binary conda packages for all of the affiliated packages are also available  via the \texttt{astropy} conda channel for Linux, Max OS X, and MS Windows.
 % * <mattwcraig@gmail.com> 2017-10-27T07:16:27.310Z:
@@
 
-In order to check the accuracy of the coordinate transformations in \package{astropy.coordinates}, we have created a set of benchmarks that we use to compare transformations between a set of coordinate frames for a number of packages \footnote{\url{http://www.astropy.org/coordinates-benchmark/summary.html}}.
+In order to check the accuracy of the coordinate transformations in \package{astropy.coordinates}, we have created a set of benchmarks that we use to compare transformations between a set of coordinate frames for a number of packages\footnote{\url{http://www.astropy.org/coordinates-benchmark/summary.html}}.
 Since
@@
 For each benchmark, we convert the 1000 longitudes/latitudes from the input/output frame with all tools and quantify the comparison by looking at the median, minimum, maximum, and standard deviation of the absolute separation of the output coordinates from each pair of tools.
-Table \ref{tab:coordinate_benchmarks} gives an example of the relative accuracy of the conversion from FK4 to Galactic coordinates for all pairs of tools.
+\tablename~\ref{tab:coordinate_benchmarks} gives an example of the relative accuracy of the conversion from FK4 to Galactic coordinates for all pairs of tools.
 This shows for example that \astropy, Kapteyn and PyTPM agree perfectly (to the precision shown), while PALpy, pySLALIB, and PyAST also agree perfectly amongst themselves, but show an offset of around 0.2\arcsec with the former three packages.
-Finally, PyEphem disagrees with other packages by 0.4-0.8\arcsec.
+Finally, PyEphem disagrees with other packages by 0.4--0.8\arcsec.
 These values are only meant to be illustrative and will change over time as the benchmarks are refined and packages are updated.
@@
 An example of a compound model could be a spectrum with interstellar absorption.
-The stellar spectrum and the interstellar extinction are represented by separate models, but the observed spectrum is fitted with a compoud model that combines both.
+The stellar spectrum and the interstellar extinction are represented by separate models, but the observed spectrum is fitted with a compound model that combines both.
 

### 2017-11-16 main.tex
Update on Overleaf.

@@
 
+\inlinecomment{Tom R}{the 'this community' above is a bit too general - do we mean it is the only community in astronomy, or in the Python astronomy world?
+I'd change this to either 'to become this community for Python astronomy software' or 'to become such a community'.
+For instance yt had a community before we came along for the simulation community, so I want to make sure we don't claim we are the only community out there.}
+
 The development of the \astropypkg core package began as a largely
@@
 %
+\inlinecomment{Tom R}{Python calls itself a programming language or general-purpose language, not specifically scripting language. I would remove 'scripting' below.}
+
 \python\footnote{\url{https://www.python.org/}} is an increasingly popular,
@@
 source software license free of charge for all major operating systems.
-Stable and well-developed packages provide support for array arithmetic
+Stable and well-developed packages provide support for array representation and arithmetic
 \citep[\package{numpy};][]{numpy}, a wide variety of functions for scientific
@@
 commits.
-The commit distribution follows an approximate power-law (with log-slope of
+The commit distribution \inlinecomment{Tom R}{too vague, maybe 'the distribution of number of commits as a function of ...'} follows an approximate power-law (with log-slope of
 $\approx -0.47$) \inlinecomment{AG}{round to -0.5?  This is astronomy, after all.}, meaning most of the commits were and are contributed by a
@@
 discussions during the open consideration period by leaving comments on the
-respective pull request.\footnote{\url{https://github.com/astropy/astropy-APEs}}
+respective pull request.\footnote{\url{https://github.com/astropy/astropy-APEs}} \inlinecomment{Tom R}{first mention of a pull request in the context of an APE - need to make it clear that APEs are proposed by PRs}
 In previous APEs a community consensus emerged and APEs are accepted and become
@@
 Alternatively, \astropypkg can be readily installed from the Python Package
-Index\footnote{\url{https://pypi.python.org/pypi}} (PyPI) using pip, the
+Index\footnote{\url{https://pypi.python.org/pypi}} (PyPI) 
+\inlinecomment{Tom R}{make footnote link directly to astropy on PyPI?}
+using pip, the
 recommended command-line tool for installing \python packages
 that is included by default since \python 2 $\geq$ 2.7.9 and \python 3 $\geq$ 3.4.
+
+\inlinecomment{Tom R}{is this actually true?
+I installed Python 3.6 from source recently and it didn't have the pip command readily available.
+What it does have is the ensurepip module, but we might want to be careful how we phrase this here.
+Maybe just remove mention of pip being included by default?}
 For most recent \astropypkg releases, pre-built wheel distributions are obtainable
@@
 may be outdated compared with the latest stable release of \astropy accessible
-from the PyPI\@. Pre-built binary conda packages for all of the affiliated packages are also available  via the \texttt{astropy} conda channel for Linux, Max OS X, and MS Windows.
+from the PyPI\@. Pre-built binary conda packages for all of the affiliated packages are also available  via the \texttt{astropy} conda channel for Linux, Mac OS X, and MS Windows.
 % * <mattwcraig@gmail.com> 2017-10-27T07:16:27.310Z:
@@
 \inlinecomment{BMS}{I suggest to order the subsection lexicographically as reading the draft the current order seemed very random (unlike at the docs page where they the grouping logic is obvious)}
+\inlinecomment{Tom R}{the only issue is if we rely on having e.g. units described first if they are used later}
 
@@
 array object and have been designed with speed in mind.
+
+\inlinecomment{Tom R}{I think saying 'subclass' here is too detailed and is mentioned below in 3.1.1 if needed - 'make it possible to attach units to numpy arrays' or something like that?}
+
 As of \astropypkg version 2.0, units and quantities are prevalent in most other
@@
 
-\subsubsection{Speed improvements} The \texttt{Quantity} object is now significantly
+\subsubsection{Speed improvements}
+
+\inlinecomment{Tom R}{I wonder if we might just want to mention at the top level that performance has been improved in places? This seems a bit too detailed}
+
+The \texttt{Quantity} object is now significantly
         faster than in early versions of \astropypkg. This is in large part due
@@
 \subsubsection{Using quantities in tables}
+
+\inlinecomment{Tom R}{this is a new feature of table, not units, so I think we don't want to mention this here}
 
@@
 For compatibility with \astropypkg version 1.3 and earlier, the \texttt{astropyconst13}
-namespace is still available and provides access to the adopted versions of the
+namespace \inlinecomment{Tom R}{jargon alert: 'namespace'} is still available and provides access to the adopted versions of the
 constants from earlier versions of \astropypkg.
@@
 \subsubsection{Derivatives of coordinate representations}
+
+\inlinecomment{Tom R}{does this really warrant a separate section or is it just a byproduct of the velocity stuff that can be mentioned in 3.3.2?}
+
     As mentioned above, the \texttt{Representation} classes act like
@@
 \subsubsection{Accuracy of coordinate transformations}
-
-\inlinecomment{TR}{This is a first draft and I need to dig into the details again to finish some of the text, and I also need to make the table/figure}.
 
@@
 \citealt{sofa}) but is licensed under a three-clause BSD license.
-The package was described in detail in previous work \citep{astropy} and has
+The package was described in detail in  \citet{astropy} and has
 stayed stable for the last several versions of \astropypkg.
@@
 
+\inlinecomment{Tom R}{I would remove this tiny section. As for units, I think we should only mention the whole mixin stuff in the table section, not for every single object that can go in a table}
+
 \subsection{Data containers}
@@
 
+\inlinecomment{Tom R}{this is waaaaay too short and jargony. It's a very cool feature that deserves more reader-friendly text!}
+
 %hamogu: I've commented this out.
@@
 organized by sub-subpackage.
+
+\inlinecomment{Tom R}{is a sub-subpackage a thing, or is it just 'subpackage' all the way down?}
 
@@
 with many HDUs.
+
+\inlinecomment{Tom R}{too detailed? I don't think we need to mention every single performance enhancement, right?}
 

### 2017-11-16 main.tex
Remove BeautifulSoup

@@
 For instance yt had a community before we came along for the simulation community, so I want to make sure we don't claim we are the only community out there.}
+\inlinecomment{Perry G}{Agreed}
 
@@
 %
-\inlinecomment{Tom R}{Python calls itself a programming language or general-purpose language, not specifically scripting language. I would remove 'scripting' below.}
-
 \python\footnote{\url{https://www.python.org/}} is an increasingly popular,
-general-purpose scripting language that is available under a permissive open
+general-purpose programming language that is available under a permissive open
 source software license free of charge for all major operating systems.
@@
 Thus, \astropy has a mechanism to more formally propose significant changes to
-the core package (e.g., the release cycle; \citealt{ape2})\inlinecomment{AG}{Is the release cycle really part of the core package?
-That's how this reads.
-Is there something more concretely linked to the code we can use as an example here?}, to plan out major
-new features, or institute new organization-wide policies (e.g.,
-code of conduct; \citealt{ape8}).
+the core package (e.g., re-writing the coordinates subpackage; \citealt{ape5}),
+to plan out major new features (e.g., a new file format; \citealt{ape6}), or
+institute new organization-wide policies (e.g., adopting a code of conduct;
+\citealt{ape8}).
 This mechanism is called ``Astropy Proposal for Enhancement'' (APE) and are
@@
 into a detailed implementation; anyone is welcome to contribute to these
-discussions during the open consideration period by leaving comments on the
-respective pull request.\footnote{\url{https://github.com/astropy/astropy-APEs}} \inlinecomment{Tom R}{first mention of a pull request in the context of an APE - need to make it clear that APEs are proposed by PRs}
+discussions during the open consideration period. APEs are proposed via pull
+requests on a dedicated GitHub repository\footnote{\url{https://github.com/astropy/astropy-APEs}},
+and anyone can therefore read the proposed APEs and leave comments in-line.
 In previous APEs a community consensus emerged and APEs are accepted and become
@@
 \inlinecomment{Tom R}{make footnote link directly to astropy on PyPI?}
-using pip, the
-recommended command-line tool for installing \python packages
-that is included by default since \python 2 $\geq$ 2.7.9 and \python 3 $\geq$ 3.4.
-
-\inlinecomment{Tom R}{is this actually true?
-I installed Python 3.6 from source recently and it didn't have the pip command readily available.
-What it does have is the ensurepip module, but we might want to be careful how we phrase this here.
-Maybe just remove mention of pip being included by default?}
+using \texttt{pip}, the standard command-line tool for installing \python packages.
 For most recent \astropypkg releases, pre-built wheel distributions are obtainable
@@
 
+\inlinecomment{Perry G}{Agreeing with Tom below, I would avoid using terms like subclass, decorators, mixin, namespace, (and perhaps even class, instead using objects consistently; this is no place to be pendantic about the distinction between classes and objects; even to the extent of adding a qualifying sentence somewhere like: "In this paper we will use object when we mean object or classes; in software there are important distinctions between the two terms, but they are not relevant in this paper."), and the like and replace them with more generic descriptions, e.g., "extended", or "tools to make defining functions that can use quantities simple to write" }
 \inlinecomment{Tom R}{I think saying 'subclass' here is too detailed and is mentioned below in 3.1.1 if needed - 'make it possible to attach units to numpy arrays' or something like that?}
@@
 These values are only meant to be illustrative and will change over time as the benchmarks are refined and packages are updated.
-
+\inlinecomment{Perry G}{Wouldn't the table be better represented as a matrices?
+Or perhaps as a matrix as a crude image with colors or intensities representing the size of the quantity.
+Is the difference between median and mean significant enough to warrant showing both?
+A link to the actual numbers may satisfy readers that want the exact values, but I suspect the majority don't need to see that precision.}
 \begin{table}
@@
 
+\inlinecomment{Perry G}{Some mention that some of these are inspired by Pandas?}
 \subsubsection{Support for grouped table operations}
@@
 to read a table within an HTML file or web URL into an astropy
-\texttt{Table} object. This requires the \package{BeautifulSoup4}
-package to be installed.  Conversely a \texttt{Table} object can now
+\texttt{Table} object. Conversely a \texttt{Table} object can now
 be written out as an HTML table.

### 2017-11-16 main.tex
Update on Overleaf.

--- 2017-11-16 main.tex
@@
 \inlinecomment{Tom R}{Python calls itself a programming language or general-purpose language, not specifically scripting language. I would remove 'scripting' below.}
-
+\inlinecomment{Perry G}{Yes, it's time to drop the scripting adjective; it's far more general than that now.}
 \python\footnote{\url{https://www.python.org/}} is an increasingly popular,

### 2017-11-18 main.tex
Improve text related to commit distribution

@@
 commits.
-The commit distribution \inlinecomment{Tom R}{too vague, maybe 'the distribution of number of commits as a function of ...'} follows an approximate power-law (with log-slope of
-$\approx -0.47$) \inlinecomment{AG}{round to -0.5?  This is astronomy, after all.}, meaning most of the commits were and are contributed by a
+The distribution of number of commits as a function of number of contributors
+follows an approximate power-law (with log-slope of
+$\approx -0.5$), meaning most of the commits were and are contributed by a
 relatively small fraction of the contributor pool.

### 2017-11-18 main.tex
Link directly to astropy project on PyPI

@@
 
-\section*{\textit{Notes and guidelines (to be removed)}}
-
-\begin{itemize}
-   \item The goal is to produce a brief and informative paper that covers major
-        \astropy principles not mentioned in the first paper, the core v2.0
-        package, and infrastructure in \astropy project to support development
-        in \python.
-    \item We don't plan on including code in this paper, but if you think you
-        will need to include code in your section, please add it to a separate
-        \python module (.py file) and include it in this repository.
-    \item Use \escapecmd{\sectionname} not ``Section,'' \escapecmd{\figurename}
-        not ``Figure''
-    \item Use \escapecmd{\astropypkg} for the astropy package,
-        \escapecmd{\astropy} for the astropy project, \escapecmd{\python} not
-        ``Python''
-    \item If your subpackage was included in Paper I, then please just include a
-        note on what the package does, a reference to paper I, and any new major
-        updates to your package
-    \item If your subpackage was not included, then please describe the
-        subpackage on level with what was in the first paper, and highlight any
-        major features in it. Typical length should be equivalent to one page
-        (single-column).
-    \item Please make sure you are logged into Overleaf or pushing a commit with
-        your information to be able to track the contributors to the paper.
-
-\end{itemize}
-
-\section*{Global TODO items}
-\begin{itemize}
-    \item \sout{subpackage not sub-package!} BMS: checked as done 13/11
-    \item spell check!
-    \item check consistent astropy usage
-\end{itemize}
-
 \section{Introduction} \label{sec:intro}
@@
 built around a common foundation.
-The \astropy project has grown to become this community, and the \astropypkg
-core package a feature-rich library for \python-based astronomical software.
-
-\inlinecomment{Tom R}{the 'this community' above is a bit too general - do we mean it is the only community in astronomy, or in the Python astronomy world?
+The \astropy project has grown to become this community for \python astronomy
+software, and the \astropypkg core package a feature-rich \python library.
+
+%\inlinecomment{Tom R}{the 'this community' above is a bit too general - do we mean it is the only community in astronomy, or in the Python astronomy world?
 I'd change this to either 'to become this community for Python astronomy software' or 'to become such a community'.
 For instance yt had a community before we came along for the simulation community, so I want to make sure we don't claim we are the only community out there.}
-\inlinecomment{Perry G}{Agreed}
+%\inlinecomment{Perry G}{Agreed}
 
@@
 maintained by the East Asian Observatory;][]{starlink1982,starlink2013}.
-% More recently, community-driven efforts have seen significant success in the astronomical sciences \citep{yt}
-\inlinecomment{BMS}{I like the idea to reference yt here}
+More recently, community-driven efforts have seen significant success in the astronomical sciences \citep{yt}
+%\inlinecomment{BMS}{I like the idea to reference yt here}
 %
-\inlinecomment{Tom R}{Python calls itself a programming language or general-purpose language, not specifically scripting language. I would remove 'scripting' below.}
-\inlinecomment{Perry G}{Yes, it's time to drop the scripting adjective; it's far more general than that now.}
 \python\footnote{\url{https://www.python.org/}} is an increasingly popular,
-general-purpose scripting language that is available under a permissive open
+general-purpose programming language that is available under a permissive open
 source software license free of charge for all major operating systems.
@@
 Affiliated packages are listed on the main \astropy website and advertised to the community through \astropy mailing lists, so becoming an affiliated package is a good way for new and existing packages to gain exposure while at the same time promoting \astropy's high standard for code and documentation quality.
-This process of listing and promoting affiliated packages is one way in which the \astropy project tries to help with \inlinecomment{AG}{Increase?} code reuse in the astronomical community.
+This process of listing and promoting affiliated packages is one way in which the \astropy project tries to increase code reuse in the astronomical community.
 
@@
 The coordination committee (\sectionname~\ref{sect:coordcom}) reviews such requests and issues recommendations for the improvement of a package where possible.
-
-%\subsection{Mixin}
 
@@
 Alternatively, \astropypkg can be readily installed from the Python Package
-Index\footnote{\url{https://pypi.python.org/pypi}} (PyPI)
-\inlinecomment{Tom R}{make footnote link directly to astropy on PyPI?}
-using pip, the
-recommended command-line tool for installing \python packages
-that is included by default since \python 2 $\geq$ 2.7.9 and \python 3 $\geq$ 3.4.
-
-\inlinecomment{Tom R}{is this actually true?
-I installed Python 3.6 from source recently and it didn't have the pip command readily available.
-What it does have is the ensurepip module, but we might want to be careful how we phrase this here.
-Maybe just remove mention of pip being included by default?}
+Index\footnote{\url{https://pypi.org/project/astropy}} (PyPI)
+using \texttt{pip}, the standard command-line tool for installing \python packages.
 For most recent \astropypkg releases, pre-built wheel distributions are obtainable
@@
 In this section, we highlight new features introduced or substantially improved
-since version v0.2 (previously described in \citealt{astropy}).
+since version v0.2 (previously described in \citealt{astropy}).  The \astropypkg
+provides a full log of changes \footnote{https://github.com/astropy/astropy/blob/master/CHANGES.rst}
+over the course of the entire project and more details about individual
+subpackages are available in the documentation \footnote{http://docs.astropy.org/en/stable/}.
+Beyond what is mentioned below, most subpackages have seen increased performance
+since the release of the v0.2 package.
 
@@
 % just here for completeness at the moment
-\inlinecomment{BMS}{I suggest to order the subsection lexicographically as reading the draft the current order seemed very random (unlike at the docs page where they the grouping logic is obvious)}
-\inlinecomment{Tom R}{the only issue is if we rely on having e.g. units described first if they are used later}
+%\inlinecomment{BMS}{I suggest to order the subsection lexicographically as reading the draft the current order seemed very random (unlike at the docs page where they the grouping logic is obvious)}
+%\inlinecomment{Tom R}{the only issue is if we rely on having e.g. units described first if they are used later}
 
@@
 numerical operations.
-In \texttt{astropy.units}, \texttt{Quantity} objects subclass the \texttt{numpy}
+In \texttt{astropy.units}, \texttt{Quantity} objects extend \texttt{numpy}
 array object and have been designed with speed in mind.
 
-\inlinecomment{Perry G}{Agreeing with Tom below, I would avoid using terms like subclass, decorators, mixin, namespace, (and perhaps even class, instead using objects consistently; this is no place to be pendantic about the distinction between classes and objects; even to the extent of adding a qualifying sentence somewhere like: "In this paper we will use object when we mean object or classes; in software there are important distinctions between the two terms, but they are not relevant in this paper."), and the like and replace them with more generic descriptions, e.g., "extended", or "tools to make defining functions that can use quantities simple to write" }
-\inlinecomment{Tom R}{I think saying 'subclass' here is too detailed and is mentioned below in 3.1.1 if needed - 'make it possible to attach units to numpy arrays' or something like that?}
+%\inlinecomment{Perry G}{Agreeing with Tom below, I would avoid using terms like subclass, decorators, mixin, namespace, (and perhaps even class, instead using objects consistently; this is no place to be pendantic about the distinction between classes and objects; even to the extent of adding a qualifying sentence somewhere like: "In this paper we will use object when we mean object or classes; in software there are important distinctions between the two terms, but they are not relevant in this paper."), and the like and replace them with more generic descriptions, e.g., "extended", or "tools to make defining functions that can use quantities simple to write" }
+%\inlinecomment{Tom R}{I think saying 'subclass' here is too detailed and is mentioned below in 3.1.1 if needed - 'make it possible to attach units to numpy arrays' or something like that?}
 
@@
 
-The \texttt{Quantity} object
-        is now a subclass of the \texttt{numpy.ndarray} object and therefore
+The \texttt{Quantity} object extends
+the \texttt{numpy.ndarray} object and therefore
 works well with many of the functions in \texttt{numpy} that support
 array operations. For example, \texttt{Quantity} objects with angular
-        units can be passed in to the trigonometric functions implemented in
-        \texttt{numpy} (e.g., \texttt{numpy.cos}) and do the right thing: the
-        units are internally converted to radians (what the \texttt{numpy}
+units can be directly passed in to the trigonometric functions implemented in
+\texttt{numpy}. The units are internally converted to radians (what the \texttt{numpy}
 trigonometric functions expect) before being passed to \texttt{numpy}.
 
-\subsubsection{Speed improvements}
-
-\inlinecomment{Tom R}{I wonder if we might just want to mention at the top level that performance has been improved in places? This seems a bit too detailed}
-
-The \texttt{Quantity} object is now significantly
-        faster than in early versions of \astropypkg. This is in large part due
-        to the fact that \texttt{Quantity} subclasses the \texttt{numpy.ndarray}
-        object, but even relative to more recent versions of \astropypkg,
-        operations with \texttt{Quantity} objects are generally faster. This is
-        largely thanks to improvements in the way \texttt{numpy} arrays can be
-        subclassed.
+%\subsubsection{Speed improvements}
+
+%\inlinecomment{Tom R}{I wonder if we might just want to mention at the top level that performance has been improved in places? This seems a bit too detailed}
+
+%The \texttt{Quantity} object is now significantly
+        %faster than in early versions of \astropypkg. This is in large part due
+        %to the fact that \texttt{Quantity} subclasses the \texttt{numpy.ndarray}
+        %object, but even relative to more recent versions of \astropypkg,
+        %operations with \texttt{Quantity} objects are generally faster. This is
+        %largely thanks to improvements in the way \texttt{numpy} arrays can be
+        %subclassed.
 
@@
         Logarithmic, relative units are now supported in \texttt{astropy.units}.
-
-\subsubsection{Using quantities in tables}
-
-\inlinecomment{Tom R}{this is a new feature of table, not units, so I think we don't want to mention this here}
-
-        The \texttt{astropy.table} subpackage (see
-        \sectionname~\ref{sec:table}) now supports using quantities in tables
-        with the \texttt{QTable} class.
-        As a result, units specified in FITS tables are supported, and tables
-        with quantities can be read and written to various file formats.
 
@@
 default constant value version: \texttt{astropyconst20}.
-For compatibility with \astropypkg version 1.3 and earlier, the \texttt{astropyconst13}
-namespace \inlinecomment{Tom R}{jargon alert: 'namespace'} is still available and provides access to the adopted versions of the
+For compatibility with \astropypkg version 1.3,  \texttt{astropyconst13}
+is available and provides access to the adopted versions of the
 constants from earlier versions of \astropypkg.
 To use previous versions of the constants as \emph{units} (e.g., solar masses),
-the values from the desired namespace have to be imported directly; with version
+the values have to be imported directly; with version
 2.0, \texttt{astropy.units} uses the \texttt{astropyconst20} versions.
@@
 
-\subsubsection{Derivatives of coordinate representations}
-
-\inlinecomment{Tom R}{does this really warrant a separate section or is it just a byproduct of the velocity stuff that can be mentioned in 3.3.2?}
-
-    As mentioned above, the \texttt{Representation} classes act like
-    three-dimensional vectors.
-    \texttt{astropy.coordinates} now also supports handling first derivatives of
-    vectors / representations through the new \texttt{Differential} classes.
-    The \texttt{Differential} classes are currently used internally within the
-    \texttt{Frame} classes to store the velocity data.
+%\subsubsection{Derivatives of coordinate representations}
+
+%\inlinecomment{Tom R}{does this really warrant a separate section or is it just a byproduct of the velocity stuff that can be mentioned in 3.3.2?}
+
+    %As mentioned above, the \texttt{Representation} classes act like
+    %three-dimensional vectors.
+    %\texttt{astropy.coordinates} now also supports handling first derivatives of
+    %vectors / representations through the new \texttt{Differential} classes.
+    %The \texttt{Differential} classes are currently used internally within the
+    %\texttt{Frame} classes to store the velocity data.
 
@@
 These values are only meant to be illustrative and will change over time as the benchmarks are refined and packages are updated.
-\inlinecomment{Perry G}{Wouldn't the table be better represented as a matrices?
+%\inlinecomment{Perry G}{Wouldn't the table be better represented as a matrices?
 Or perhaps as a matrix as a crude image with colors or intensities representing the size of the quantity.
@@
         \texttt{light\_travel\_time} method of a \texttt{Time} object.
-\subsubsection{\texttt{Time} objects as \texttt{Table} columns} \texttt{Time} objects
-        can now be added as columns in \package{astropy.table} \texttt{Table}
-        objects. This is described in more detail in
-        \sectionname~\ref{sec:table} with the concept of a ``mixin'' column
-        type.
-
-\inlinecomment{Tom R}{I would remove this tiny section. As for units, I think we should only mention the whole mixin stuff in the table section, not for every single object that can go in a table}
 
@@
 \inlinecomment{Perry G}{Some mention that some of these are inspired by Pandas?}
+
 \subsubsection{Support for grouped table operations}
-Tables can contain data that naturally form groups, for example monitoring of an object in different bands.
-We may then want to split the table or a column into these groups (in this example: observations in different filters)  and
-compute some statistic on the data, or filter the groups based on some
-criteria.
-Grouped operations are now supported by \texttt{Table} objects.
-%,
-%mainly through the \texttt{group\_by()} method and subsequent operations
-%on the grouped version of the table or column.
+
+A table can contain data that naturally forms groups -- for example it may
+contain multiple observations of a few sources at different points in time
+and in different bands. We may then want to split the table into groups based
+on the combination of source observed and the band, and then combine the
+results for each combination of source and band in some way (for example finding
+the mean or standard deviation of the fluxes or magnitudes over time) or filter
+the groups based on user-defined criteria. These kinds of grouping and
+aggregation operations are now fully supported by \texttt{Table} objects.
 
 \subsubsection{Support for table concatenation}
-Tables can be combined in several
-different ways.
-If two tables have the same rows, we may want to stack them
-``vertically'' to create a new table with the same columns but all rows.
-If two tables are row-matched but have distinct columns, we may want to
-stack them ``horizontally'' to create a new table with the same rows
-but all columns.
-For other situations, more general table concatenations or joins are
-also possible when two tables share some common columns.
-%All three of these operations are now possible with \texttt{Table}
-%objects through the \texttt{vstack}, \texttt{hstack}, and \texttt{join}
-%functions in \package{astropy.table}.
-
-\subsubsection{Mixin columns for time and coordinates}
-The \texttt{Table} object now supports \texttt{Quantity}, sky coordinate (\texttt{SkyCoord}),
-astronomical \texttt{Time} objects and and other objects to serve
-as array-like containers for column data through the ``mixin'' protocol.
-
-\inlinecomment{Tom R}{this is waaaaay too short and jargony. It's a very cool feature that deserves more reader-friendly text!}
-
-%hamogu: I've commented this out.
-% I think it's very specific and not relevant to non-developers.
-% If we want to keep it, we need to add at least 102 senteces about what Pandas
-% is and I think that's more text than is warrented for this feature.
-
-%\subsubsection{Transform to and from \texttt{Pandas} \texttt{DataFrame} objects}
-%\texttt{Table} objects can now be created from a \texttt{DataFrame}
-%object (\texttt{from\_pandas()}), or exported to a \texttt{DataFrame}
-%object (\texttt{to\_pandas()}).
-%\texttt{DataFrame} objects do not support multi-dimensional array
-%columns, so this conversion will fail if the source \texttt{Table}
-%object contains any such columns.
+
+\texttt{Table} objects can now be combined in several different ways. If two
+tables have the same rows, we may want to stack them ``vertically'' to create a
+new table with the same columns but all rows. If two tables are row-matched but
+have distinct columns, we may want to stack them ``horizontally'' to create a
+new table with the same rows but all columns. For other situations, more general
+table concatenations or joins are also possible when two tables share some
+common columns.
+
+\subsubsection{Using astropy objects in tables}
+
+The \texttt{Table} object now allows \texttt{Quantity} objects, celestial
+coordinate objects (\texttt{SkyCoord}), and date/time objects (\texttt{Time}) to
+be used as columns, and also provides a general way for other user-defined
+objects to be used as columns. This makes it possible for example to easily
+represent catalogs of sources or time series as in Astropy, and having both the
+benefits of the \texttt{Table} object (such as accessing specific rows/columns
+or groups of rows/columns, combining tables, and so on) and the benefits of e.g.
+the \texttt{SkyCoord} or \texttt{Time} classes (such as converting the
+coordinates to a different frame, or accessing the date/time as a modified
+Julian date or in another time scale).
 
@@
 
-%\inlinecomment{SCO}{Pyfits deprecation in favor of io.fits ?}
 %\inlinecomment{SCO}{Table and FITS tables}
@@
 
-We summarize key new features or updates to \package{astropy.io} below,
-organized by sub-subpackage.
-
-\inlinecomment{Tom R}{is a sub-subpackage a thing, or is it just 'subpackage' all the way down?}
-
-\subsubsection{Enhanced CSV format}
+% We summarize key new features or updates to \package{astropy.io} below,
+% organized by sub-subpackage.
+
+% \inlinecomment{Tom R}{is a sub-subpackage a thing, or is it just 'subpackage' all the way down?}
+
+\subsubsection{ASCII}
+% \subsubsection{Enhanced CSV format}
 
@@
 preserving table meta-data such as comments, keywords and column data
-types, units, and descriptions. Using the newly defined \emph{Enhanced
-Character Separated Values} (ECSV,  \citet{ape6}) format it is now
+types, units, and descriptions. The newly defined \emph{Enhanced
+Character Separated Values} (ECSV,  \citet{ape6}) format makes it
 possible to write a table to an ASCII-format file and read it back
@@
 
-\subsubsection{\texttt{.ascii}: fast readers and writers}
-
-The \package{astropy.io.ascii} module now includes a significantly
-faster Cython/C engine for reading and writing ASCII files. This is
-available for the most common formats.
-
-%following formats: \texttt{basic},
-%      \texttt{commented\_header}, \texttt{csv}, \texttt{no\_header},
-%      \texttt{rdb}, and \texttt{tab}.
-On average the new engine is about
-4 to 5 times faster than the corresponding pure-\python
-implementation, and is often comparable to the speed of the
-\package{Pandas} \citep{pandas} ASCII file interface.  The fast
-reader has parallel processing option that allows harnessing
-multiple cores for input parsing to achieve even greater speed
-gains.
-
-By default, \texttt{read()} and \texttt{write()} will attempt to use
-the fast C engine when dealing with compatible formats. Certain
-features of the full read / write interface are not available in the
-fast version, in which case the pure-\python version will automatically
-be used.
-
-\subsubsection{\texttt{.ascii}: HTML tables}
+% \subsubsection{\texttt{.ascii}: fast readers and writers}
+
+The \package{astropy.io.ascii} subpackage now includes a significantly faster
+Cython/C engine for reading and writing ASCII files. This is available for the
+most common formats.  On average the new engine is about 4 to 5 times faster
+than the corresponding pure-\python implementation, and is often comparable to
+the speed of the \package{Pandas} \citep{pandas} ASCII file interface.  The
+fast reader has parallel processing option that allows harnessing multiple
+cores for input parsing to achieve even greater speed gains.  By default,
+\texttt{read()} and \texttt{write()} will attempt to use the fast C engine
+when dealing with compatible formats. Certain features of the full read
+/ write interface are not available in the fast version, in which case the
+pure-\python version will automatically be used.
+
+% \subsubsection{\texttt{.ascii}: HTML tables}
 
@@
 to read a table within an HTML file or web URL into an astropy
-\texttt{Table} object. This requires the \package{BeautifulSoup4}
-package to be installed.  Conversely a \texttt{Table} object can now
+\texttt{Table} object. Conversely a \texttt{Table} object can now
 be written out as an HTML table.
 
-\subsubsection{\texttt{.fits}: command-line scripts (\texttt{fitsheader}, \texttt{fitsinfo})}
-
-The \package{astropy.io.fits} subpackage now provides command-line
-scripts for printing a summary of the HDUs in a FITS file(s)
-(\texttt{fitsinfo file.fits}) and for printing the header information
-to the screen in a human-readable format (\texttt{fitsheader
-file.fits}).
-
-\subsubsection{\texttt{.fits}: lazy loading }
-
-The \package{astropy.io.fits} subpackage now supports \emph{lazy
-loading}, where all HDUs are not loaded until they are requested (or
-the file is closed). This should provide substantial speedups for
-situations using the convenience functions (e.g., \texttt{getheader()}
-or \texttt{getdata()}) to get HDU’s that are near the front of a file
-with many HDUs.
-
-\inlinecomment{Tom R}{too detailed? I don't think we need to mention every single performance enhancement, right?}
-
-\subsubsection{\texttt{.misc}: YAML serialization}
-
-The new \package{astropy.io.misc.yaml} module allows converting
-astropy objects into a standard YAML format.
-This can be used beyond \texttt{astropy.io.misc.yaml}: for example, to
-serialize the metadata of tables before saving to other formats like
-HDF5.
+\subsubsection{FITS}
+
+The \package{astropy.io.fits} subpackage started as a direct port of the
+PyFITS project \citep{PyFITS}. Therefore it is pretty stable, with mostly bug
+fixes but also a few new features and performance improvements.  The API
+remains compatible with PyFITS, which is now deprecated in favor of
+\astropypkg.
+
+Command-line scripts are now available for printing a summary of the HDUs in
+a FITS file(s) (\texttt{fitsinfo}) and for printing the header information to
+the screen in a human-readable format (\texttt{fitsheader}).
+
+FITS files are now loaded \emph{lazily} (the default behavior, which can be
+deactivated if needed), where all HDUs are not loaded until they are
+requested. This should provide substantial speedups for situations using the
+convenience functions (e.g., \texttt{getheader()} or \texttt{getdata()}) to
+get HDU’s that are near the front of a file with many HDUs.
+
+% \inlinecomment{Tom R}{too detailed? I don't think we need to mention every single performance enhancement, right?}
+
+% \subsubsection{\texttt{.misc}: YAML serialization}
+
+% The new \package{astropy.io.misc.yaml} module allows converting astropy
+% objects into a standard YAML format.  This can be used beyond
+% \texttt{astropy.io.misc.yaml}: for example, to serialize the metadata of
+% tables before saving to other formats like HDF5.
 
@@
 \subsubsection{Single Model Definition and Evaluation}
-\inlinecomment{hamogu: I tihnk this is too techical. I know it's a complex subpackage but I had trouble understanding this section even as a regular user.}
+
+%\inlinecomment{hamogu: I tihnk this is too techical. I know it's a complex subpackage but I had trouble understanding this section even as a regular user.}
+
 Most models are defined by parameters and maintain an ordered list of parameter names, \texttt{Model.param\_names}.
@@
 
-\inlinecomment{APW}{Add citations for the different optimizaton algorithms in paragraph above?}
+%\inlinecomment{APW}{Add citations for the different optimizaton algorithms in paragraph above?}
 
@@
    \item The simplest way is to use the \texttt{custom\_model} decorator in modeling with a user-defined function that takes the inputs and model parameters as arguments.
-   \item It is also possible to subclass the \texttt{Model} base class and create an arbitrarily complex custom model.
+   \item It is also possible to create an arbitrarily complex custom model based on the \texttt{Model} class.
 \end{enumerate}
@@
 \label{sec:infrastructure}
-\inlinecomment{BMS}{should we describe astropy-helpers even though it's future is unsure?}
+%\inlinecomment{BMS}{should we describe astropy-helpers even though it's future is unsure?}
 % Text also edited by Adrian PW
@@
 
-\inlinecomment{TPR}{We should put the releases of sphinx-automodapi on Zenodo and cite this}
+%\inlinecomment{TPR}{We should put the releases of sphinx-automodapi on Zenodo and cite this}
 
@@
 
-\inlinecomment{BMS}{should we mention the refactored infra here?
-  e.g. pytest-astropy and sphinx-astropy?}
+%\inlinecomment{BMS}{should we mention the refactored infra here?  e.g. pytest-astropy and sphinx-astropy?}
 
@@
 projection. %\citep{astropy-healpix}
-\inlinecomment{BMS}{TODO: uncomment references of packages once they are available}
+%\inlinecomment{BMS}{TODO: uncomment references of packages once they are available}
 
@@
 
-\inlinecomment{SMC}{Can a brief description of each code be added?}
+%\inlinecomment{SMC}{Can a brief description of each code be added?}
 

### 2017-11-18 main.tex
Remove mention of pip being included by default with Python

--- 2017-11-18 main.tex
@@
 commits.
-The distribution of number of commits as a function of number of contributors
-follows an approximate power-law (with log-slope of
-$\approx -0.5$), meaning most of the commits were and are contributed by a
+The commit distribution \inlinecomment{Tom R}{too vague, maybe 'the distribution of number of commits as a function of ...'} follows an approximate power-law (with log-slope of
+$\approx -0.47$) \inlinecomment{AG}{round to -0.5?  This is astronomy, after all.}, meaning most of the commits were and are contributed by a
 relatively small fraction of the contributor pool.
@@
 \inlinecomment{Tom R}{make footnote link directly to astropy on PyPI?}
-using pip, the
-recommended command-line tool for installing \python packages
-that is included by default since \python 2 $\geq$ 2.7.9 and \python 3 $\geq$ 3.4.
-
-\inlinecomment{Tom R}{is this actually true?
-I installed Python 3.6 from source recently and it didn't have the pip command readily available.
-What it does have is the ensurepip module, but we might want to be careful how we phrase this here.
-Maybe just remove mention of pip being included by default?}
+using pip, the standard command-line tool for installing \python packages.
 For most recent \astropypkg releases, pre-built wheel distributions are obtainable

### 2017-11-18 main.tex
Improvements to table section and simplify mention of mixin columns

@@
 
-%\subsection{Mixin}
-
 %\subsection{Accuracy testing across many different implementation}
@@
 \inlinecomment{Tom R}{make footnote link directly to astropy on PyPI?}
-using pip, the standard command-line tool for installing \python packages.
+using pip, the
+recommended command-line tool for installing \python packages
+that is included by default since \python 2 $\geq$ 2.7.9 and \python 3 $\geq$ 3.4.
+
+\inlinecomment{Tom R}{is this actually true?
+I installed Python 3.6 from source recently and it didn't have the pip command readily available.
+What it does have is the ensurepip module, but we might want to be careful how we phrase this here.
+Maybe just remove mention of pip being included by default?}
 For most recent \astropypkg releases, pre-built wheel distributions are obtainable

### 2017-11-18 main.tex

--- 2017-11-18 main.tex
@@
 %
-\inlinecomment{Tom R}{Python calls itself a programming language or general-purpose language, not specifically scripting language. I would remove 'scripting' below.}
-\inlinecomment{Perry G}{Yes, it's time to drop the scripting adjective; it's far more general than that now.}
 \python\footnote{\url{https://www.python.org/}} is an increasingly popular,
-general-purpose scripting language that is available under a permissive open
+general-purpose programming language that is available under a permissive open
 source software license free of charge for all major operating systems.

### 2017-11-18 build-paper-travis.sh
build pdf and push to orphan branch

@@ -1,0 +1,14 @@
+#!/bin/bash -x
+
+# Build the paper
+make
+
+# Push to GitHub
+if [ -n "$GITHUB_API_KEY" ]; then
+  cd $TRAVIS_BUILD_DIR
+  git checkout --orphan $TRAVIS_BRANCH-pdf
+  git rm -rf .
+  git add -f main.pdf
+  git -c user.name='travis' -c user.email='travis' commit -m "building the paper"
+  git push -q -f https://$GITHUB_USER:$GITHUB_API_KEY@github.com/$TRAVIS_REPO_SLUG $TRAVIS_BRANCH-pdf
+fi

### 2017-11-18 build-paper-travis.sh
don't push pdf if a PR build

@@ -4,7 +4,7 @@
 make
 
 # Push to GitHub
-if [ -n "$GITHUB_API_KEY" ]; then
+if [ -n "$GITHUB_API_KEY" ] && ["$TRAVIS_PULL_REQUEST" = "false"]; then
   cd $TRAVIS_BUILD_DIR
   git checkout --orphan $TRAVIS_BRANCH-pdf
   git rm -rf .

### 2017-11-18 main.tex
addressing review

--- 2017-11-18 main.tex
@@
 %
+\inlinecomment{Tom R}{Python calls itself a programming language or general-purpose language, not specifically scripting language. I would remove 'scripting' below.}
+\inlinecomment{Perry G}{Yes, it's time to drop the scripting adjective; it's far more general than that now.}
 \python\footnote{\url{https://www.python.org/}} is an increasingly popular,
-general-purpose programming language that is available under a permissive open
+general-purpose scripting language that is available under a permissive open
 source software license free of charge for all major operating systems.

### 2017-11-19 build-paper-travis.sh
fix boolean var

@@ -4,7 +4,7 @@
 make
 
 # Push to GitHub
-if [ -n "$GITHUB_API_KEY" ] && ["$TRAVIS_PULL_REQUEST" = "false"]; then
+if [ -n "$GITHUB_API_KEY" ] && ["$TRAVIS_PULL_REQUEST" = false]; then
   cd $TRAVIS_BUILD_DIR
   git checkout --orphan $TRAVIS_BRANCH-pdf
   git rm -rf .

### 2017-11-19 build-paper-travis.sh
argh, fix spaces in bash if

@@ -4,7 +4,7 @@
 make
 
 # Push to GitHub
-if [ -n "$GITHUB_API_KEY" ] && ["$TRAVIS_PULL_REQUEST" = false]; then
+if [ -n "$GITHUB_API_KEY" ] && [ "$TRAVIS_PULL_REQUEST" = false ]; then
   cd $TRAVIS_BUILD_DIR
   git checkout --orphan $TRAVIS_BRANCH-pdf
   git rm -rf .

### 2017-11-20 main.tex
Group ascii and fits items

@@
 to read a table within an HTML file or web URL into an astropy
-\texttt{Table} object. This requires the \package{BeautifulSoup4}
-package to be installed.  Conversely a \texttt{Table} object can now
+\texttt{Table} object. Conversely a \texttt{Table} object can now
 be written out as an HTML table.
 
-\subsubsection{\texttt{.fits}: command-line scripts (\texttt{fitsheader}, \texttt{fitsinfo})}
+\subsubsection{FITS}
+% \subsubsection{\texttt{.fits}: command-line scripts (\texttt{fitsheader}, \texttt{fitsinfo})}
 
@@
 scripts for printing a summary of the HDUs in a FITS file(s)
-(\texttt{fitsinfo file.fits}) and for printing the header information
-to the screen in a human-readable format (\texttt{fitsheader
-file.fits}).
-
-\subsubsection{\texttt{.fits}: lazy loading }
+(\texttt{fitsinfo}) and for printing the header information
+to the screen in a human-readable format (\texttt{fitsheader}).
+
+% \subsubsection{\texttt{.fits}: lazy loading }
 
@@
 
-\inlinecomment{Tom R}{too detailed? I don't think we need to mention every single performance enhancement, right?}
-
-\subsubsection{\texttt{.misc}: YAML serialization}
-
-The new \package{astropy.io.misc.yaml} module allows converting
-astropy objects into a standard YAML format.
-This can be used beyond \texttt{astropy.io.misc.yaml}: for example, to
-serialize the metadata of tables before saving to other formats like
-HDF5.
+% \inlinecomment{Tom R}{too detailed? I don't think we need to mention every single performance enhancement, right?}
+
+% \subsubsection{\texttt{.misc}: YAML serialization}
+
+% The new \package{astropy.io.misc.yaml} module allows converting astropy
+% objects into a standard YAML format.  This can be used beyond
+% \texttt{astropy.io.misc.yaml}: for example, to serialize the metadata of
+% tables before saving to other formats like HDF5.
 

### 2017-11-20 main.tex
fits section

@@
 \subsubsection{FITS}
-% \subsubsection{\texttt{.fits}: command-line scripts (\texttt{fitsheader}, \texttt{fitsinfo})}
-
-The \package{astropy.io.fits} subpackage now provides command-line
-scripts for printing a summary of the HDUs in a FITS file(s)
-(\texttt{fitsinfo}) and for printing the header information
-to the screen in a human-readable format (\texttt{fitsheader}).
-
-% \subsubsection{\texttt{.fits}: lazy loading }
-
-The \package{astropy.io.fits} subpackage now supports \emph{lazy
-loading}, where all HDUs are not loaded until they are requested (or
-the file is closed). This should provide substantial speedups for
-situations using the convenience functions (e.g., \texttt{getheader()}
-or \texttt{getdata()}) to get HDU’s that are near the front of a file
-with many HDUs.
+
+The \package{astropy.io.fits} subpackage started as a direct port of the
+PyFITS project. Therefore it is pretty stable, with mostly bug fixes but also
+a few new features and performance improvements.  The API remains compatible
+with PyFITS, which is now deprecated in favor of Astropy.
+
+Command-line scripts are now available for printing a summary of the HDUs in
+a FITS file(s) (\texttt{fitsinfo}) and for printing the header information to
+the screen in a human-readable format (\texttt{fitsheader}).
+
+FITS files are now loaded \emph{lazily} (the default behavior, which can be
+deactivated if needed), where all HDUs are not loaded until they are requested
+(or the file is closed). This should provide substantial speedups for
+situations using the convenience functions (e.g., \texttt{getheader()} or
+\texttt{getdata()}) to get HDU’s that are near the front of a file with many
+HDUs.
 

### 2017-11-20 main.tex

--- 2017-11-20 main.tex
@@
 The \package{astropy.io.fits} subpackage started as a direct port of the
-PyFITS project. Therefore it is pretty stable, with mostly bug fixes but also
-a few new features and performance improvements.  The API remains compatible
-with PyFITS, which is now deprecated in favor of Astropy.
+PyFITS project \citep{PyFITS}. Therefore it is pretty stable, with mostly bug
+fixes but also a few new features and performance improvements.  The API
+remains compatible with PyFITS, which is now deprecated in favor of
+\astropypkg.
 
@@
 FITS files are now loaded \emph{lazily} (the default behavior, which can be
-deactivated if needed), where all HDUs are not loaded until they are requested
-(or the file is closed). This should provide substantial speedups for
-situations using the convenience functions (e.g., \texttt{getheader()} or
-\texttt{getdata()}) to get HDU’s that are near the front of a file with many
-HDUs.
+deactivated if needed), where all HDUs are not loaded until they are
+requested. This should provide substantial speedups for situations using the
+convenience functions (e.g., \texttt{getheader()} or \texttt{getdata()}) to
+get HDU’s that are near the front of a file with many HDUs.
 

### 2017-11-20 main.tex
address community comment

--- 2017-11-20 main.tex
@@
 built around a common foundation.
-The \astropy project has grown to become this community, and the \astropypkg
-core package a feature-rich library for \python-based astronomical software.
-
-\inlinecomment{Tom R}{the 'this community' above is a bit too general - do we mean it is the only community in astronomy, or in the Python astronomy world?
+The \astropy project has grown to become this community for \python astronomy
+software, and the \astropypkg core package a feature-rich library for
+\python-based astronomical software.
+
+%\inlinecomment{Tom R}{the 'this community' above is a bit too general - do we mean it is the only community in astronomy, or in the Python astronomy world?
 I'd change this to either 'to become this community for Python astronomy software' or 'to become such a community'.
 For instance yt had a community before we came along for the simulation community, so I want to make sure we don't claim we are the only community out there.}
-\inlinecomment{Perry G}{Agreed}
+%\inlinecomment{Perry G}{Agreed}
 
@@
 
+%\inlinecomment{SCO}{Pyfits deprecation in favor of io.fits ?}
 %\inlinecomment{SCO}{Table and FITS tables}
@@
 
-% We summarize key new features or updates to \package{astropy.io} below,
-% organized by sub-subpackage.
-
-% \inlinecomment{Tom R}{is a sub-subpackage a thing, or is it just 'subpackage' all the way down?}
-
-\subsubsection{ASCII}
-% \subsubsection{Enhanced CSV format}
+We summarize key new features or updates to \package{astropy.io} below,
+organized by sub-subpackage.
+
+\inlinecomment{Tom R}{is a sub-subpackage a thing, or is it just 'subpackage' all the way down?}
+
+\subsubsection{Enhanced CSV format}
 
@@
 preserving table meta-data such as comments, keywords and column data
-types, units, and descriptions. The newly defined \emph{Enhanced
-Character Separated Values} (ECSV,  \citet{ape6}) format makes it
+types, units, and descriptions. Using the newly defined \emph{Enhanced
+Character Separated Values} (ECSV,  \citet{ape6}) format it is now
 possible to write a table to an ASCII-format file and read it back
@@
 
-% \subsubsection{\texttt{.ascii}: fast readers and writers}
-
-The \package{astropy.io.ascii} subpackage now includes a significantly faster
-Cython/C engine for reading and writing ASCII files. This is available for the
-most common formats.  On average the new engine is about 4 to 5 times faster
-than the corresponding pure-\python implementation, and is often comparable to
-the speed of the \package{Pandas} \citep{pandas} ASCII file interface.  The
-fast reader has parallel processing option that allows harnessing multiple
-cores for input parsing to achieve even greater speed gains.  By default,
-\texttt{read()} and \texttt{write()} will attempt to use the fast C engine
-when dealing with compatible formats. Certain features of the full read
-/ write interface are not available in the fast version, in which case the
-pure-\python version will automatically be used.
-
-% \subsubsection{\texttt{.ascii}: HTML tables}
+\subsubsection{\texttt{.ascii}: fast readers and writers}
+
+The \package{astropy.io.ascii} module now includes a significantly
+faster Cython/C engine for reading and writing ASCII files. This is
+available for the most common formats.
+
+%following formats: \texttt{basic},
+%      \texttt{commented\_header}, \texttt{csv}, \texttt{no\_header},
+%      \texttt{rdb}, and \texttt{tab}.
+On average the new engine is about
+4 to 5 times faster than the corresponding pure-\python
+implementation, and is often comparable to the speed of the
+\package{Pandas} \citep{pandas} ASCII file interface.  The fast
+reader has parallel processing option that allows harnessing
+multiple cores for input parsing to achieve even greater speed
+gains.
+
+By default, \texttt{read()} and \texttt{write()} will attempt to use
+the fast C engine when dealing with compatible formats. Certain
+features of the full read / write interface are not available in the
+fast version, in which case the pure-\python version will automatically
+be used.
+
+\subsubsection{\texttt{.ascii}: HTML tables}
 
@@
 to read a table within an HTML file or web URL into an astropy
-\texttt{Table} object. Conversely a \texttt{Table} object can now
+\texttt{Table} object. This requires the \package{BeautifulSoup4}
+package to be installed.  Conversely a \texttt{Table} object can now
 be written out as an HTML table.
 
-\subsubsection{FITS}
-
-The \package{astropy.io.fits} subpackage started as a direct port of the
-PyFITS project \citep{PyFITS}. Therefore it is pretty stable, with mostly bug
-fixes but also a few new features and performance improvements.  The API
-remains compatible with PyFITS, which is now deprecated in favor of
-\astropypkg.
-
-Command-line scripts are now available for printing a summary of the HDUs in
-a FITS file(s) (\texttt{fitsinfo}) and for printing the header information to
-the screen in a human-readable format (\texttt{fitsheader}).
-
-FITS files are now loaded \emph{lazily} (the default behavior, which can be
-deactivated if needed), where all HDUs are not loaded until they are
-requested. This should provide substantial speedups for situations using the
-convenience functions (e.g., \texttt{getheader()} or \texttt{getdata()}) to
-get HDU’s that are near the front of a file with many HDUs.
-
-% \inlinecomment{Tom R}{too detailed? I don't think we need to mention every single performance enhancement, right?}
-
-% \subsubsection{\texttt{.misc}: YAML serialization}
-
-% The new \package{astropy.io.misc.yaml} module allows converting astropy
-% objects into a standard YAML format.  This can be used beyond
-% \texttt{astropy.io.misc.yaml}: for example, to serialize the metadata of
-% tables before saving to other formats like HDF5.
+\subsubsection{\texttt{.fits}: command-line scripts (\texttt{fitsheader}, \texttt{fitsinfo})}
+
+The \package{astropy.io.fits} subpackage now provides command-line
+scripts for printing a summary of the HDUs in a FITS file(s)
+(\texttt{fitsinfo file.fits}) and for printing the header information
+to the screen in a human-readable format (\texttt{fitsheader
+file.fits}).
+
+\subsubsection{\texttt{.fits}: lazy loading }
+
+The \package{astropy.io.fits} subpackage now supports \emph{lazy
+loading}, where all HDUs are not loaded until they are requested (or
+the file is closed). This should provide substantial speedups for
+situations using the convenience functions (e.g., \texttt{getheader()}
+or \texttt{getdata()}) to get HDU’s that are near the front of a file
+with many HDUs.
+
+\inlinecomment{Tom R}{too detailed? I don't think we need to mention every single performance enhancement, right?}
+
+\subsubsection{\texttt{.misc}: YAML serialization}
+
+The new \package{astropy.io.misc.yaml} module allows converting
+astropy objects into a standard YAML format.
+This can be used beyond \texttt{astropy.io.misc.yaml}: for example, to
+serialize the metadata of tables before saving to other formats like
+HDF5.
 

### 2017-11-20 main.tex
udpate based on @bsipocz suggestion
added back in yt reference

@@
 The \astropy project has grown to become this community for \python astronomy
-software, and the \astropypkg core package a feature-rich library for
-\python-based astronomical software.
+software, and the \astropypkg core package a feature-rich \python library.
 
@@
 maintained by the East Asian Observatory;][]{starlink1982,starlink2013}.
-% More recently, community-driven efforts have seen significant success in the astronomical sciences \citep{yt}
-\inlinecomment{BMS}{I like the idea to reference yt here}
+More recently, community-driven efforts have seen significant success in the astronomical sciences \citep{yt}
+%\inlinecomment{BMS}{I like the idea to reference yt here}
 %

### 2017-11-20 main.tex
added AG increase

--- 2017-11-20 main.tex
@@
 built around a common foundation.
-The \astropy project has grown to become this community for \python astronomy
-software, and the \astropypkg core package a feature-rich library for
-\python-based astronomical software.
-
-%\inlinecomment{Tom R}{the 'this community' above is a bit too general - do we mean it is the only community in astronomy, or in the Python astronomy world?
+The \astropy project has grown to become this community, and the \astropypkg
+core package a feature-rich library for \python-based astronomical software.
+
+\inlinecomment{Tom R}{the 'this community' above is a bit too general - do we mean it is the only community in astronomy, or in the Python astronomy world?
 I'd change this to either 'to become this community for Python astronomy software' or 'to become such a community'.
 For instance yt had a community before we came along for the simulation community, so I want to make sure we don't claim we are the only community out there.}
-%\inlinecomment{Perry G}{Agreed}
+\inlinecomment{Perry G}{Agreed}
 

### 2017-11-20 main.tex
moved Perry comment to issue

@@
 Affiliated packages are listed on the main \astropy website and advertised to the community through \astropy mailing lists, so becoming an affiliated package is a good way for new and existing packages to gain exposure while at the same time promoting \astropy's high standard for code and documentation quality.
-This process of listing and promoting affiliated packages is one way in which the \astropy project tries to increase code reuse in the astronomical community.
+This process of listing and promoting affiliated packages is one way in which the \astropy project tries to help with \inlinecomment{AG}{Increase?} code reuse in the astronomical community.
 

### 2017-11-20 main.tex
remove most instances of subclass and namespace

@@
 
-The \texttt{Quantity} object
-        is now a subclass of the \texttt{numpy.ndarray} object and therefore
+The \texttt{Quantity} object extends 
+the \texttt{numpy.ndarray} object and therefore
 works well with many of the functions in \texttt{numpy} that support
 array operations. For example, \texttt{Quantity} objects with angular
-        units can be passed in to the trigonometric functions implemented in
-        \texttt{numpy} (e.g., \texttt{numpy.cos}) and do the right thing: the
-        units are internally converted to radians (what the \texttt{numpy}
+units can be directly passed in to the trigonometric functions implemented in
+\texttt{numpy}. The units are internally converted to radians (what the \texttt{numpy}
 trigonometric functions expect) before being passed to \texttt{numpy}.
 
-\subsubsection{Speed improvements}
-
-\inlinecomment{Tom R}{I wonder if we might just want to mention at the top level that performance has been improved in places? This seems a bit too detailed}
-
-The \texttt{Quantity} object is now significantly
-        faster than in early versions of \astropypkg. This is in large part due
-        to the fact that \texttt{Quantity} subclasses the \texttt{numpy.ndarray}
-        object, but even relative to more recent versions of \astropypkg,
-        operations with \texttt{Quantity} objects are generally faster. This is
-        largely thanks to improvements in the way \texttt{numpy} arrays can be
-        subclassed.
+%\subsubsection{Speed improvements}
+
+%\inlinecomment{Tom R}{I wonder if we might just want to mention at the top level that performance has been improved in places? This seems a bit too detailed}
+
+%The \texttt{Quantity} object is now significantly
+        %faster than in early versions of \astropypkg. This is in large part due
+        %to the fact that \texttt{Quantity} subclasses the \texttt{numpy.ndarray}
+        %object, but even relative to more recent versions of \astropypkg,
+        %operations with \texttt{Quantity} objects are generally faster. This is
+        %largely thanks to improvements in the way \texttt{numpy} arrays can be
+        %subclassed.
 
@@
    \item The simplest way is to use the \texttt{custom\_model} decorator in modeling with a user-defined function that takes the inputs and model parameters as arguments.
-   \item It is also possible to subclass the \texttt{Model} base class and create an arbitrarily complex custom model.
+   \item It is also possible to create an arbitrarily complex custom model baed on the \texttt{Model} class.
 \end{enumerate}

### 2017-11-20 main.tex
update core intro text

@@
 In this section, we highlight new features introduced or substantially improved
-since version v0.2 (previously described in \citealt{astropy}).
+since version v0.2 (previously described in \citealt{astropy}).  The \astropkg 
+provides a full log of changes \footnote{https://github.com/astropy/astropy/blob/master/CHANGES.rst} 
+over the course of the entire project and more details about individual 
+subpackages are available in the documentation \footnote{http://docs.astropy.org/en/stable/}.  
+Beyond what is mentioned below, most subpackages have seen increased performance
+since the release of the v0.2 package.
 

### 2017-11-20 main.tex
fixed typo
removed notes and todo

--- 2017-11-20 main.tex
@@
 }
-
-\section*{\textit{Notes and guidelines (to be removed)}}
-
-\begin{itemize}
-   \item The goal is to produce a brief and informative paper that covers major
-        \astropy principles not mentioned in the first paper, the core v2.0
-        package, and infrastructure in \astropy project to support development
-        in \python.
-    \item We don't plan on including code in this paper, but if you think you
-        will need to include code in your section, please add it to a separate
-        \python module (.py file) and include it in this repository.
-    \item Use \escapecmd{\sectionname} not ``Section,'' \escapecmd{\figurename}
-        not ``Figure''
-    \item Use \escapecmd{\astropypkg} for the astropy package,
-        \escapecmd{\astropy} for the astropy project, \escapecmd{\python} not
-        ``Python''
-    \item If your subpackage was included in Paper I, then please just include a
-        note on what the package does, a reference to paper I, and any new major
-        updates to your package
-    \item If your subpackage was not included, then please describe the
-        subpackage on level with what was in the first paper, and highlight any
-        major features in it. Typical length should be equivalent to one page
-        (single-column).
-    \item Please make sure you are logged into Overleaf or pushing a commit with
-        your information to be able to track the contributors to the paper.
-
-\end{itemize}
-
-\section*{Global TODO items}
-\begin{itemize}
-    \item \sout{subpackage not sub-package!} BMS: checked as done 13/11
-    \item spell check!
-    \item check consistent astropy usage
-\end{itemize}
 
@@
 In this section, we highlight new features introduced or substantially improved
-since version v0.2 (previously described in \citealt{astropy}).  The \astropkg 
-provides a full log of changes \footnote{https://github.com/astropy/astropy/blob/master/CHANGES.rst} 
-over the course of the entire project and more details about individual 
-subpackages are available in the documentation \footnote{http://docs.astropy.org/en/stable/}.  
-Beyond what is mentioned below, most subpackages have seen increased performance
-since the release of the v0.2 package.
+since version v0.2 (previously described in \citealt{astropy}).
 
@@
 % just here for completeness at the moment
-%\inlinecomment{BMS}{I suggest to order the subsection lexicographically as reading the draft the current order seemed very random (unlike at the docs page where they the grouping logic is obvious)}
-%\inlinecomment{Tom R}{the only issue is if we rely on having e.g. units described first if they are used later}
+\inlinecomment{BMS}{I suggest to order the subsection lexicographically as reading the draft the current order seemed very random (unlike at the docs page where they the grouping logic is obvious)}
+\inlinecomment{Tom R}{the only issue is if we rely on having e.g. units described first if they are used later}
 
@@
 numerical operations.
-In \texttt{astropy.units}, \texttt{Quantity} objects extend \texttt{numpy}
+In \texttt{astropy.units}, \texttt{Quantity} objects subclass the \texttt{numpy}
 array object and have been designed with speed in mind.
 
-%\inlinecomment{Perry G}{Agreeing with Tom below, I would avoid using terms like subclass, decorators, mixin, namespace, (and perhaps even class, instead using objects consistently; this is no place to be pendantic about the distinction between classes and objects; even to the extent of adding a qualifying sentence somewhere like: "In this paper we will use object when we mean object or classes; in software there are important distinctions between the two terms, but they are not relevant in this paper."), and the like and replace them with more generic descriptions, e.g., "extended", or "tools to make defining functions that can use quantities simple to write" }
-%\inlinecomment{Tom R}{I think saying 'subclass' here is too detailed and is mentioned below in 3.1.1 if needed - 'make it possible to attach units to numpy arrays' or something like that?}
+\inlinecomment{Perry G}{Agreeing with Tom below, I would avoid using terms like subclass, decorators, mixin, namespace, (and perhaps even class, instead using objects consistently; this is no place to be pendantic about the distinction between classes and objects; even to the extent of adding a qualifying sentence somewhere like: "In this paper we will use object when we mean object or classes; in software there are important distinctions between the two terms, but they are not relevant in this paper."), and the like and replace them with more generic descriptions, e.g., "extended", or "tools to make defining functions that can use quantities simple to write" }
+\inlinecomment{Tom R}{I think saying 'subclass' here is too detailed and is mentioned below in 3.1.1 if needed - 'make it possible to attach units to numpy arrays' or something like that?}
 
@@
 
-The \texttt{Quantity} object extends 
-the \texttt{numpy.ndarray} object and therefore
+The \texttt{Quantity} object
+        is now a subclass of the \texttt{numpy.ndarray} object and therefore
         works well with many of the functions in \texttt{numpy} that support
         array operations. For example, \texttt{Quantity} objects with angular
-units can be directly passed in to the trigonometric functions implemented in
-\texttt{numpy}. The units are internally converted to radians (what the \texttt{numpy}
+        units can be passed in to the trigonometric functions implemented in
+        \texttt{numpy} (e.g., \texttt{numpy.cos}) and do the right thing: the
+        units are internally converted to radians (what the \texttt{numpy}
         trigonometric functions expect) before being passed to \texttt{numpy}.
 
-%\subsubsection{Speed improvements}
-
-%\inlinecomment{Tom R}{I wonder if we might just want to mention at the top level that performance has been improved in places? This seems a bit too detailed}
-
-%The \texttt{Quantity} object is now significantly
-        %faster than in early versions of \astropypkg. This is in large part due
-        %to the fact that \texttt{Quantity} subclasses the \texttt{numpy.ndarray}
-        %object, but even relative to more recent versions of \astropypkg,
-        %operations with \texttt{Quantity} objects are generally faster. This is
-        %largely thanks to improvements in the way \texttt{numpy} arrays can be
-        %subclassed.
+\subsubsection{Speed improvements}
+
+\inlinecomment{Tom R}{I wonder if we might just want to mention at the top level that performance has been improved in places? This seems a bit too detailed}
+
+The \texttt{Quantity} object is now significantly
+        faster than in early versions of \astropypkg. This is in large part due
+        to the fact that \texttt{Quantity} subclasses the \texttt{numpy.ndarray}
+        object, but even relative to more recent versions of \astropypkg,
+        operations with \texttt{Quantity} objects are generally faster. This is
+        largely thanks to improvements in the way \texttt{numpy} arrays can be
+        subclassed.
 
@@
 default constant value version: \texttt{astropyconst20}.
-For compatibility with \astropypkg version 1.3,  \texttt{astropyconst13}
-is available and provides access to the adopted versions of the
+For compatibility with \astropypkg version 1.3 and earlier, the \texttt{astropyconst13}
+namespace \inlinecomment{Tom R}{jargon alert: 'namespace'} is still available and provides access to the adopted versions of the
 constants from earlier versions of \astropypkg.
 To use previous versions of the constants as \emph{units} (e.g., solar masses),
-the values have to be imported directly; with version
+the values from the desired namespace have to be imported directly; with version
 2.0, \texttt{astropy.units} uses the \texttt{astropyconst20} versions.
@@
    \item The simplest way is to use the \texttt{custom\_model} decorator in modeling with a user-defined function that takes the inputs and model parameters as arguments.
-   \item It is also possible to create an arbitrarily complex custom model baed on the \texttt{Model} class.
+   \item It is also possible to subclass the \texttt{Model} base class and create an arbitrarily complex custom model.
 \end{enumerate}

### 2017-11-20 main.tex
added section on support

@@
 }
+
+\section*{\textit{Notes and guidelines (to be removed)}}
+
+\begin{itemize}
+   \item The goal is to produce a brief and informative paper that covers major
+        \astropy principles not mentioned in the first paper, the core v2.0
+        package, and infrastructure in \astropy project to support development
+        in \python.
+    \item We don't plan on including code in this paper, but if you think you
+        will need to include code in your section, please add it to a separate
+        \python module (.py file) and include it in this repository.
+    \item Use \escapecmd{\sectionname} not ``Section,'' \escapecmd{\figurename}
+        not ``Figure''
+    \item Use \escapecmd{\astropypkg} for the astropy package,
+        \escapecmd{\astropy} for the astropy project, \escapecmd{\python} not
+        ``Python''
+    \item If your subpackage was included in Paper I, then please just include a
+        note on what the package does, a reference to paper I, and any new major
+        updates to your package
+    \item If your subpackage was not included, then please describe the
+        subpackage on level with what was in the first paper, and highlight any
+        major features in it. Typical length should be equivalent to one page
+        (single-column).
+    \item Please make sure you are logged into Overleaf or pushing a commit with
+        your information to be able to track the contributors to the paper.
+
+\end{itemize}
+
+\section*{Global TODO items}
+\begin{itemize}
+    \item \sout{subpackage not sub-package!} BMS: checked as done 13/11
+    \item spell check!
+    \item check consistent astropy usage
+\end{itemize}
 
@@
 
-%\subsection{Support of Astropy}
+\subsection{Support of Astropy}
+
+The \astropy project, as of the v2.0 release, does not receive any direct financial support for
+the development of the \astropypkg.  Development of the \astropypkg is supported
+through contributions by individuals to work on astropy in their own personal
+time, contributions from individuals or groups to work on \astropy as 
+part of a research project, or contributions from institutes that allocate 
+people to work on \astropy. 
+A list of organizations that have contributed to \astropy
+are listed in the Acknowledgements.  
+Different models have been proposed for the support of astropy 
+(ie. \cite{2016arXiv161003159M}), 
+but a sustainable, community-based model has not yet been established.
+The astropy project has the ability to accept financial contributions 
+(individual or institutes) through the NumFOCUS organization\footnote{NumFOCUS 
+is a 501(c)(3) nonprofit that supports and promotes world-class, innovative, 
+open source scientific computing.},  
+which generally covers the direct costs incurred by the \astropy project
+along with supporting
+
 % Removing unless this gets written about in

### 2017-11-20 main.tex
Improve text

@@
 built around a common foundation.
-The \astropy project has grown to become this community for \python astronomy
-software, and the \astropypkg core package a feature-rich \python library.
-
-%\inlinecomment{Tom R}{the 'this community' above is a bit too general - do we mean it is the only community in astronomy, or in the Python astronomy world?
+The \astropy project has grown to become this community, and the \astropypkg
+core package a feature-rich library for \python-based astronomical software.
+
+\inlinecomment{Tom R}{the 'this community' above is a bit too general - do we mean it is the only community in astronomy, or in the Python astronomy world?
 I'd change this to either 'to become this community for Python astronomy software' or 'to become such a community'.
 For instance yt had a community before we came along for the simulation community, so I want to make sure we don't claim we are the only community out there.}
-%\inlinecomment{Perry G}{Agreed}
+\inlinecomment{Perry G}{Agreed}
 
@@
 maintained by the East Asian Observatory;][]{starlink1982,starlink2013}.
-More recently, community-driven efforts have seen significant success in the astronomical sciences \citep{yt}
-%\inlinecomment{BMS}{I like the idea to reference yt here}
+% More recently, community-driven efforts have seen significant success in the astronomical sciences \citep{yt}
+\inlinecomment{BMS}{I like the idea to reference yt here}
 %
+\inlinecomment{Tom R}{Python calls itself a programming language or general-purpose language, not specifically scripting language. I would remove 'scripting' below.}
+\inlinecomment{Perry G}{Yes, it's time to drop the scripting adjective; it's far more general than that now.}
 \python\footnote{\url{https://www.python.org/}} is an increasingly popular,
-general-purpose programming language that is available under a permissive open
+general-purpose scripting language that is available under a permissive open
 source software license free of charge for all major operating systems.
@@
 of code.} contributed by $232$ unique contributors over $19270$ \texttt{git}
-commits.
-The commit distribution \inlinecomment{Tom R}{too vague, maybe 'the distribution of number of commits as a function of ...'} follows an approximate power-law (with log-slope of
-$\approx -0.47$) \inlinecomment{AG}{round to -0.5?  This is astronomy, after all.}, meaning most of the commits were and are contributed by a
+commits. We can divide up the commits by
+contributor and construct a distribution which is the number of commits
+for each contributor versus the rank of the contributor (where 1 is the
+contributor who has made the most commits, 2 is the contributor with the
+second most commits, and so on). When doing this, we find that this distribution
+follows an approximate power-law (with log-slope of
+$\approx -0.5$), meaning most of the commits were and are contributed by a
 relatively small fraction of the contributor pool.
@@
 Thus, \astropy has a mechanism to more formally propose significant changes to
-the core package (e.g., re-writing the coordinates subpackage; \citealt{ape5}),
-to plan out major new features (e.g., a new file format; \citealt{ape6}), or
-institute new organization-wide policies (e.g., adopting a code of conduct;
-\citealt{ape8}).
+the core package (e.g., the release cycle; \citealt{ape2})\inlinecomment{AG}{Is the release cycle really part of the core package?
+That's how this reads.
+Is there something more concretely linked to the code we can use as an example here?}, to plan out major
+new features, or institute new organization-wide policies (e.g.,
+code of conduct; \citealt{ape8}).
 This mechanism is called ``Astropy Proposal for Enhancement'' (APE) and are
@@
 into a detailed implementation; anyone is welcome to contribute to these
-discussions during the open consideration period. APEs are proposed via pull
-requests on a dedicated GitHub repository\footnote{\url{https://github.com/astropy/astropy-APEs}},
-and anyone can therefore read the proposed APEs and leave comments in-line.
+discussions during the open consideration period by leaving comments on the
+respective pull request.\footnote{\url{https://github.com/astropy/astropy-APEs}} \inlinecomment{Tom R}{first mention of a pull request in the context of an APE - need to make it clear that APEs are proposed by PRs}
 In previous APEs a community consensus emerged and APEs are accepted and become
@@
 The coordination committee (\sectionname~\ref{sect:coordcom}) reviews such requests and issues recommendations for the improvement of a package where possible.
+
+%\subsection{Mixin}
 
@@
 \inlinecomment{Tom R}{make footnote link directly to astropy on PyPI?}
-using \texttt{pip}, the standard command-line tool for installing \python packages.
+using pip, the
+recommended command-line tool for installing \python packages
+that is included by default since \python 2 $\geq$ 2.7.9 and \python 3 $\geq$ 3.4.
+
+\inlinecomment{Tom R}{is this actually true?
+I installed Python 3.6 from source recently and it didn't have the pip command readily available.
+What it does have is the ensurepip module, but we might want to be careful how we phrase this here.
+Maybe just remove mention of pip being included by default?}
 For most recent \astropypkg releases, pre-built wheel distributions are obtainable
@@
 
-\subsection{Support of Astropy}
-
-The \astropy project, as of the v2.0 release, does not receive any direct financial support for
-the development of the \astropypkg.  Development of the \astropypkg is supported
-through contributions by individuals to work on astropy in their own personal
-time, contributions from individuals or groups to work on \astropy as 
-part of a research project, or contributions from institutes that allocate 
-people to work on \astropy. 
-A list of organizations that have contributed to \astropy
-are listed in the Acknowledgements.  
-Different models have been proposed for the support of astropy 
-(ie. \cite{2016arXiv161003159M}), 
-but a sustainable, community-based model has not yet been established.
-The astropy project has the ability to accept financial contributions 
-(individual or institutes) through the NumFOCUS organization\footnote{NumFOCUS 
-is a 501(c)(3) nonprofit that supports and promotes world-class, innovative, 
-open source scientific computing.},  
-which generally covers the direct costs incurred by the \astropy project
-along with supporting
-
+%\subsection{Support of Astropy}
 % Removing unless this gets written about in
@@
         Logarithmic, relative units are now supported in \texttt{astropy.units}.
+
+\subsubsection{Using quantities in tables}
+
+\inlinecomment{Tom R}{this is a new feature of table, not units, so I think we don't want to mention this here}
+
+        The \texttt{astropy.table} subpackage (see
+        \sectionname~\ref{sec:table}) now supports using quantities in tables
+        with the \texttt{QTable} class.
+        As a result, units specified in FITS tables are supported, and tables
+        with quantities can be read and written to various file formats.
 
@@
 These values are only meant to be illustrative and will change over time as the benchmarks are refined and packages are updated.
-%\inlinecomment{Perry G}{Wouldn't the table be better represented as a matrices?
+\inlinecomment{Perry G}{Wouldn't the table be better represented as a matrices?
 Or perhaps as a matrix as a crude image with colors or intensities representing the size of the quantity.
@@
         \texttt{light\_travel\_time} method of a \texttt{Time} object.
+\subsubsection{\texttt{Time} objects as \texttt{Table} columns} \texttt{Time} objects
+        can now be added as columns in \package{astropy.table} \texttt{Table}
+        objects. This is described in more detail in
+        \sectionname~\ref{sec:table} with the concept of a ``mixin'' column
+        type.
+
+\inlinecomment{Tom R}{I would remove this tiny section. As for units, I think we should only mention the whole mixin stuff in the table section, not for every single object that can go in a table}
 
@@
 \inlinecomment{Perry G}{Some mention that some of these are inspired by Pandas?}
-
 \subsubsection{Support for grouped table operations}
-
-A table can contain data that naturally forms groups -- for example it may
-contain multiple observations of a few sources at different points in time
-and in different bands. We may then want to split the table into groups based
-on the combination of source observed and the band, and then combine the
-results for each combination of source and band in some way (for example finding
-the mean or standard deviation of the fluxes or magnitudes over time) or filter
-the groups based on user-defined criteria. These kinds of grouping and
-aggregation operations are now fully supported by \texttt{Table} objects.
+Tables can contain data that naturally form groups, for example monitoring of an object in different bands.
+We may then want to split the table or a column into these groups (in this example: observations in different filters)  and
+compute some statistic on the data, or filter the groups based on some
+criteria.
+Grouped operations are now supported by \texttt{Table} objects.
+%,
+%mainly through the \texttt{group\_by()} method and subsequent operations
+%on the grouped version of the table or column.
 
 \subsubsection{Support for table concatenation}
-
-\texttt{Table} objects can now be combined in several different ways. If two
-tables have the same rows, we may want to stack them ``vertically'' to create a
-new table with the same columns but all rows. If two tables are row-matched but
-have distinct columns, we may want to stack them ``horizontally'' to create a
-new table with the same rows but all columns. For other situations, more general
-table concatenations or joins are also possible when two tables share some
-common columns.
-
-\subsubsection{Using astropy objects in tables}
-
-The \texttt{Table} object now allows \texttt{Quantity} objects, celestial
-coordinate objects (\texttt{SkyCoord}), and date/time objects (\texttt{Time}) to
-be used as columns, and also provides a general way for other user-defined
-objects to be used as columns. This makes it possible for example to easily
-represent catalogs of sources or time series as in Astropy, and having both the
-benefits of the \texttt{Table} object (such as accessing specific rows/columns
-or groups of rows/columns, combining tables, and so on) and the benefits of e.g.
-the \texttt{SkyCoord} or \texttt{Time} classes (such as converting the
-coordinates to a different frame, or accessing the date/time as a modified
-Julian date or in another time scale).
+Tables can be combined in several
+different ways.
+If two tables have the same rows, we may want to stack them
+``vertically'' to create a new table with the same columns but all rows.
+If two tables are row-matched but have distinct columns, we may want to
+stack them ``horizontally'' to create a new table with the same rows
+but all columns.
+For other situations, more general table concatenations or joins are
+also possible when two tables share some common columns.
+%All three of these operations are now possible with \texttt{Table}
+%objects through the \texttt{vstack}, \texttt{hstack}, and \texttt{join}
+%functions in \package{astropy.table}.
+
+\subsubsection{Mixin columns for time and coordinates}
+The \texttt{Table} object now supports \texttt{Quantity}, sky coordinate (\texttt{SkyCoord}),
+astronomical \texttt{Time} objects and and other objects to serve
+as array-like containers for column data through the ``mixin'' protocol.
+
+\inlinecomment{Tom R}{this is waaaaay too short and jargony. It's a very cool feature that deserves more reader-friendly text!}
+
+%hamogu: I've commented this out.
+% I think it's very specific and not relevant to non-developers.
+% If we want to keep it, we need to add at least 102 senteces about what Pandas
+% is and I think that's more text than is warrented for this feature.
+
+%\subsubsection{Transform to and from \texttt{Pandas} \texttt{DataFrame} objects}
+%\texttt{Table} objects can now be created from a \texttt{DataFrame}
+%object (\texttt{from\_pandas()}), or exported to a \texttt{DataFrame}
+%object (\texttt{to\_pandas()}).
+%\texttt{DataFrame} objects do not support multi-dimensional array
+%columns, so this conversion will fail if the source \texttt{Table}
+%object contains any such columns.
 
@@
 \label{sec:infrastructure}
-%\inlinecomment{BMS}{should we describe astropy-helpers even though it's future is unsure?}
+\inlinecomment{BMS}{should we describe astropy-helpers even though it's future is unsure?}
 % Text also edited by Adrian PW
@@
 
-%\inlinecomment{BMS}{should we mention the refactored infra here?  e.g. pytest-astropy and sphinx-astropy?}
+\inlinecomment{BMS}{should we mention the refactored infra here?
+  e.g. pytest-astropy and sphinx-astropy?}
 
@@
 projection. %\citep{astropy-healpix}
-%\inlinecomment{BMS}{TODO: uncomment references of packages once they are available}
+\inlinecomment{BMS}{TODO: uncomment references of packages once they are available}
 
@@
 
-%\inlinecomment{SMC}{Can a brief description of each code be added?}
+\inlinecomment{SMC}{Can a brief description of each code be added?}
 

### 2017-11-21 main.tex
edits from tom

--- 2017-11-20 main.tex
@@
 the development of the \astropypkg.  Development of the \astropypkg is supported
-through contributions by individuals to work on astropy in their own personal
-time, contributions from individuals or groups to work on \astropy as 
+by individuals who work on \astropy project in their own personal
+time, by individuals or groups to work on \astropy as 
 part of a research project, or contributions from institutes that allocate 
@@
 are listed in the Acknowledgements.  
-Different models have been proposed for the support of astropy 
-(ie. \cite{2016arXiv161003159M}), 
-but a sustainable, community-based model has not yet been established.
-The astropy project has the ability to accept financial contributions 
+Different models have been proposed for support of \astropy in the future 
+(ie. \cite{2016arXiv161003159M}), but a long-term plan
+for sustainability has not yet been established.
+The \astropy project has the ability to accept financial contributions 
 (individual or institutes) through the NumFOCUS organization\footnote{NumFOCUS 
@@
 open source scientific computing.},  
-which generally covers the direct costs incurred by the \astropy project
-along with supporting
+which generally covers the direct costs incurred by the \astropy project.
 

### 2017-11-21 main.tex
Minor wording changes

--- 2017-11-20 main.tex
@@
 commits. We can divide up the commits by
-contributor and construct a distribution which is the number of commits
-for each contributor versus the rank of the contributor (where 1 is the
-contributor who has made the most commits, 2 is the contributor with the
-second most commits, and so on). When doing this, we find that this distribution
+contributor and construct a distribution of the number of commits
+per contributor ordered by decreasing number of commits. When doing this,
+we find that this distribution
 follows an approximate power-law (with log-slope of

### 2017-11-21 main.tex
More minor wording

--- 2017-11-21 main.tex
@@
 
-\subsection{Support of Astropy}
-
-The \astropy project, as of the v2.0 release, does not receive any direct financial support for
-the development of the \astropypkg.  Development of the \astropypkg is supported
-by individuals who work on \astropy project in their own personal
-time, by individuals or groups to work on \astropy as 
-part of a research project, or contributions from institutes that allocate 
-people to work on \astropy. 
-A list of organizations that have contributed to \astropy
-are listed in the Acknowledgements.  
-Different models have been proposed for support of \astropy in the future 
-(ie. \cite{2016arXiv161003159M}), but a long-term plan
-for sustainability has not yet been established.
-The \astropy project has the ability to accept financial contributions 
-(individual or institutes) through the NumFOCUS organization\footnote{NumFOCUS 
-is a 501(c)(3) nonprofit that supports and promotes world-class, innovative, 
-open source scientific computing.},  
-which generally covers the direct costs incurred by the \astropy project.
-
+%\subsection{Support of Astropy}
 % Removing unless this gets written about in

### 2017-11-21 main.tex
fix typo

@@
 In this section, we highlight new features introduced or substantially improved
-since version v0.2 (previously described in \citealt{astropy}).  The \astropkg 
+since version v0.2 (previously described in \citealt{astropy}).  The \astropypkg
 provides a full log of changes \footnote{https://github.com/astropy/astropy/blob/master/CHANGES.rst}

### 2017-11-21 main.tex

@@
 \newcommand{\escapecmd}[1]{\texttt{\detokenize{#1}}}
+
+% To allow putting figures in a subdir
+\graphicspath{{figures/}}
 
@@
 Alternatively, \astropypkg can be readily installed from the Python Package
-Index\footnote{\url{https://pypi.python.org/pypi}} (PyPI)
-\inlinecomment{Tom R}{make footnote link directly to astropy on PyPI?}
+Index\footnote{\url{https://pypi.org/project/astropy}} (PyPI)
 using \texttt{pip}, the standard command-line tool for installing \python packages.

### 2017-11-21 main.tex

--- 2017-11-21 main.tex
@@
 of code.} contributed by $232$ unique contributors over $19270$ \texttt{git}
-commits.
-The commit distribution \inlinecomment{Tom R}{too vague, maybe 'the distribution of number of commits as a function of ...'} follows an approximate power-law (with log-slope of
-$\approx -0.47$) \inlinecomment{AG}{round to -0.5?  This is astronomy, after all.}, meaning most of the commits were and are contributed by a
+commits. We can construct a distribution of the number of commits
+per contributor ordered by decreasing number of commits. When doing this,
+we find that this distribution
+follows an approximate power-law (with log-slope of
+$\approx -0.5$), meaning most of the commits were and are contributed by a
 relatively small fraction of the contributor pool.

### 2017-11-22 main.tex
update commits section with new figure

@@
 
+\begin{figure}
+\includegraphics[width=\textwidth]{ncommits.pdf}
+\caption{%
+    \emph{Left panel}: Distribution of number of commits per committer.
+    \emph{Right panel}: Cumulative number of commits to the \astropypkg core
+    package over time.
+    \label{fig:ncommits}
+}
+\end{figure}
+
 As of version 2.0, \astropypkg contains $212244$ lines of code\footnote{This
@@
 of code.} contributed by $232$ unique contributors over $19270$ \texttt{git}
-commits. We can construct a distribution of the number of commits
-per contributor ordered by decreasing number of commits. When doing this,
-we find that this distribution
-follows an approximate power-law (with log-slope of
-$\approx -0.5$), meaning most of the commits were and are contributed by a
-relatively small fraction of the contributor pool.
-Roughly half of the commits were contributed by the top $4$
-contributors, while $\sim 90$ percent of the commits came from the top $24$
-contributors.
+commits.
+\figurename~\ref{fig:ncommits}, left, shows the distribution of total number of
+commits per contributor as of November 2017; from this, it's clear that most
+commits were and are contributed by a relatively small fraction of the
+contributor pool.
+\figurename~\ref{fig:ncommits}, right, shows the number of contributors as a
+function of time since the genesis of the \astropypkg core package.
 

### 2017-11-22 figures/commits_figure.py

@@ -1,0 +1,114 @@
+"""
+This is a subset of the functionality in astropy/astropy-tools in the
+visualizations_demographics subdirectory.
+"""
+
+from datetime import datetime
+import os
+import pandas as pd
+import numpy as np
+from matplotlib import pyplot as plt
+
+def generate_commit_stats_file(filename='gitlogstats.csv', overwrite=False,
+                               astropy_path=None):
+    """
+    Running this will generate a file in the current directory that stores the
+    statistics to make generating lots of plots easier.  Delete the file or
+    set `overwrite` to True to always re-generate the statistics.
+    """
+    if os.path.isfile(filename) and not overwrite:
+        return pd.read_csv(filename)
+
+    else:
+        import subprocess
+        import tempfile
+
+        # cmd = 'git log --use-mailmap --no-merges --format=format:\"%H\",\"%aI\",\"%aN\",\"%cN\"'.split()
+        cmd = 'git log --use-mailmap --format=format:\"%H\",\"%aI\",\"%aN\",\"%cN\"'.split()
+        output = subprocess.check_output(cmd, cwd=astropy_path)
+        output = output.decode('utf-8')
+
+        with tempfile.NamedTemporaryFile(mode='w+') as f:
+            f.write(output)
+            df = pd.read_csv(f.name, names=['commit', 'date', 'author',
+                                            'committer'])
+
+        df.to_csv(filename)
+        return df
+
+
+def commits_plot(astropy_path, ax=None, **hist_kw):
+
+    df = generate_commit_stats_file(astropy_path=astropy_path)
+    n_commits = df.groupby('author').size()
+
+    if ax is None:
+        fig, ax = plt.subplots(1, 1, figsize=(6,5))
+
+    _bins = np.logspace(0, 3.5, 16)
+    hist_kw.setdefault('histtype', 'stepfilled')
+    ax.hist(n_commits, bins=_bins, **hist_kw)
+
+    ax.set_xscale('log')
+    ax.set_yscale('log')
+    ax.set_xlabel('number of commits')
+    ax.set_ylabel('number of committers')
+
+    ax.plot(_bins, 150*_bins**-0.5, marker='')
+
+    xticks = [1, 10, 100, 1000]
+    ax.set_xticks(xticks)
+    ax.set_xticklabels([str(tick) for tick in xticks])
+
+    yticks = [1, 10, 100]
[…]

### 2017-11-22 main.tex
remove distribution section and add setence to release section

--- 2017-11-21 main.tex
@@
 
-\subsection{Distribution of packages}
-
-The \astropypkg core package is available from several of the \python distributions for scientific
-% * <mattwcraig@gmail.com> 2017-10-27T07:13:51.093Z:
-%
-% > \astropypkg i
-% I changed a few of the macros in here to refer to the package rather than the project because it is the package being discussed here.
-%
-% ^.
-computing, such as Anaconda or Enthought Canopy, which include also some of
-\astropy's affiliated packages.
-Alternatively, \astropypkg can be readily installed from the Python Package
-Index\footnote{\url{https://pypi.org/project/astropy}} (PyPI)
-using \texttt{pip}, the standard command-line tool for installing \python packages.
-For most recent \astropypkg releases, pre-built wheel distributions are obtainable
-from PyPI for Windows, Mac OS X and Linux systems that provide faster
-installation compared to the source distribution.
-% hamogu: I think that's too detailed for a journal paper.
-%     It's in the docs if anyone needs it.
-%Optionally, the version of
-%the package and the dependencies needed to run or build the software are given
-%by a specifier to the pip package manager as described in PEP 440\footnote{For
-%more detailed installation instructions and optional flags see
-%\url{http://docs.astropy.org/en/stable/install.html\#installing-astropy}}.
-
-Packaged versions of \astropy are also available for several
-operating systems that are managed by a system's package manager,
-including Debian, Ubuntu, Fedora, Gentoo, Arch Linux, Mac OS X (e.g.,
-via brew, macports or fink) and FreeBSD\@.  However, on occasion these packages
-may be outdated compared with the latest stable release of \astropy accessible
-from the PyPI\@. Pre-built binary conda packages for all of the affiliated packages are also available  via the \texttt{astropy} conda channel for Linux, Mac OS X, and MS Windows.
-% * <mattwcraig@gmail.com> 2017-10-27T07:16:27.310Z:
-%
-% > re-built binary conda packages
-% Feel free to remove if this is too detailed. I do think the available of the whole ecosystem across all platforms has helped speed its adoption.
-%
-% ^.
+The released versions of the \astropypkg core package are available from several
+of the \python distributions for scientific computing (e.g.,
+\href{http://anaconda.org}{Anaconda}) and from the \python Package Index
+(PyPI).\footnote{See the installation documentation for more information:
+\url{http://docs.astropy.org/en/stable/install.html}}
 

### 2017-11-22 main.tex
make links

@@
 since version v0.2 (previously described in \citealt{astropy}).  The \astropypkg
-provides a full log of changes \footnote{https://github.com/astropy/astropy/blob/master/CHANGES.rst}
+provides a full log of changes \footnote{\url{https://github.com/astropy/astropy/blob/master/CHANGES.rst}}
 over the course of the entire project and more details about individual
-subpackages are available in the documentation \footnote{http://docs.astropy.org/en/stable/}.
+subpackages are available in the documentation \footnote{\url{http://docs.astropy.org/en/stable/}}.
 Beyond what is mentioned below, most subpackages have seen increased performance

### 2017-11-22 main.tex
Edits from Erik on support

--- 2017-11-22 main.tex
@@
 \newcommand{\escapecmd}[1]{\texttt{\detokenize{#1}}}
-
-% To allow putting figures in a subdir
-\graphicspath{{figures/}}
 
@@
 
-\begin{figure}
-\includegraphics[width=\textwidth]{ncommits.pdf}
-\caption{%
-    \emph{Left panel}: Distribution of number of commits per committer.
-    \emph{Right panel}: Cumulative number of commits to the \astropypkg core
-    package over time.
-    \label{fig:ncommits}
-}
-\end{figure}
-
 As of version 2.0, \astropypkg contains $212244$ lines of code\footnote{This
@@
 commits.
-\figurename~\ref{fig:ncommits}, left, shows the distribution of total number of
-commits per contributor as of November 2017; from this, it's clear that most
-commits were and are contributed by a relatively small fraction of the
-contributor pool.
-\figurename~\ref{fig:ncommits}, right, shows the number of contributors as a
-function of time since the genesis of the \astropypkg core package.
+The commit distribution \inlinecomment{Tom R}{too vague, maybe 'the distribution of number of commits as a function of ...'} follows an approximate power-law (with log-slope of
+$\approx -0.47$) \inlinecomment{AG}{round to -0.5?  This is astronomy, after all.}, meaning most of the commits were and are contributed by a
+relatively small fraction of the contributor pool.
+Roughly half of the commits were contributed by the top $4$
+contributors, while $\sim 90$ percent of the commits came from the top $24$
+contributors.
 
@@
 
-%\subsection{Support of Astropy}
+\subsection{Support of Astropy}
+
+The \astropy project, as of the v2.0 release, does not receive any direct financial support for
+the development of the \astropypkg.  Development of the \astropypkg is supported
+by individuals who work on \astropy project in their own personal
+time, by individuals or groups to work on \astropy as 
+part of a research project, or contributions from institutions that allocate 
+people to work on \astropy. 
+A list of organizations that have contributed to \astropy in this manner
+are listed in the Acknowledgements.  
+Different funding models have been proposed for support of \astropy in the future 
+(ie. \cite{2016arXiv161003159M}), but a long-term plan
+for sustainability has not yet been established.
+The \astropy project has the ability to accept financial contributions 
+(individual or institutes) through the NumFOCUS organization\footnote{NumFOCUS 
+is a 501(c)(3) nonprofit that supports and promotes world-class, innovative, 
+open source scientific computing.},  
+which, has so far, covered the direct costs incurred by the \astropy project.
+
 % Removing unless this gets written about in
@@
 In this section, we highlight new features introduced or substantially improved
-since version v0.2 (previously described in \citealt{astropy}).  The \astropypkg
-provides a full log of changes \footnote{https://github.com/astropy/astropy/blob/master/CHANGES.rst}
-over the course of the entire project and more details about individual
-subpackages are available in the documentation \footnote{http://docs.astropy.org/en/stable/}.
-Beyond what is mentioned below, most subpackages have seen increased performance
-since the release of the v0.2 package.
+since version v0.2 (previously described in \citealt{astropy}).
 
@@
 
-The \texttt{Quantity} object extends
-the \texttt{numpy.ndarray} object and therefore
+The \texttt{Quantity} object
+        is now a subclass of the \texttt{numpy.ndarray} object and therefore
         works well with many of the functions in \texttt{numpy} that support
         array operations. For example, \texttt{Quantity} objects with angular
-units can be directly passed in to the trigonometric functions implemented in
-\texttt{numpy}. The units are internally converted to radians (what the \texttt{numpy}
+        units can be passed in to the trigonometric functions implemented in
+        \texttt{numpy} (e.g., \texttt{numpy.cos}) and do the right thing: the
+        units are internally converted to radians (what the \texttt{numpy}
         trigonometric functions expect) before being passed to \texttt{numpy}.
 
-%\subsubsection{Speed improvements}
-
-%\inlinecomment{Tom R}{I wonder if we might just want to mention at the top level that performance has been improved in places? This seems a bit too detailed}
-
-%The \texttt{Quantity} object is now significantly
-        %faster than in early versions of \astropypkg. This is in large part due
-        %to the fact that \texttt{Quantity} subclasses the \texttt{numpy.ndarray}
-        %object, but even relative to more recent versions of \astropypkg,
-        %operations with \texttt{Quantity} objects are generally faster. This is
-        %largely thanks to improvements in the way \texttt{numpy} arrays can be
-        %subclassed.
+\subsubsection{Speed improvements}
+
+\inlinecomment{Tom R}{I wonder if we might just want to mention at the top level that performance has been improved in places? This seems a bit too detailed}
+
+The \texttt{Quantity} object is now significantly
+        faster than in early versions of \astropypkg. This is in large part due
+        to the fact that \texttt{Quantity} subclasses the \texttt{numpy.ndarray}
+        object, but even relative to more recent versions of \astropypkg,
+        operations with \texttt{Quantity} objects are generally faster. This is
+        largely thanks to improvements in the way \texttt{numpy} arrays can be
+        subclassed.
 
@@
 
-%\subsubsection{Derivatives of coordinate representations}
-
-%\inlinecomment{Tom R}{does this really warrant a separate section or is it just a byproduct of the velocity stuff that can be mentioned in 3.3.2?}
-
-    %As mentioned above, the \texttt{Representation} classes act like
-    %three-dimensional vectors.
-    %\texttt{astropy.coordinates} now also supports handling first derivatives of
-    %vectors / representations through the new \texttt{Differential} classes.
-    %The \texttt{Differential} classes are currently used internally within the
-    %\texttt{Frame} classes to store the velocity data.
+\subsubsection{Derivatives of coordinate representations}
+
+\inlinecomment{Tom R}{does this really warrant a separate section or is it just a byproduct of the velocity stuff that can be mentioned in 3.3.2?}
+
+    As mentioned above, the \texttt{Representation} classes act like
+    three-dimensional vectors.
+    \texttt{astropy.coordinates} now also supports handling first derivatives of
+    vectors / representations through the new \texttt{Differential} classes.
+    The \texttt{Differential} classes are currently used internally within the
+    \texttt{Frame} classes to store the velocity data.
 
@@
 \subsubsection{Single Model Definition and Evaluation}
-
-%\inlinecomment{hamogu: I tihnk this is too techical. I know it's a complex subpackage but I had trouble understanding this section even as a regular user.}
-
+\inlinecomment{hamogu: I tihnk this is too techical. I know it's a complex subpackage but I had trouble understanding this section even as a regular user.}
 Most models are defined by parameters and maintain an ordered list of parameter names, \texttt{Model.param\_names}.
@@
 
-%\inlinecomment{APW}{Add citations for the different optimizaton algorithms in paragraph above?}
+\inlinecomment{APW}{Add citations for the different optimizaton algorithms in paragraph above?}
 
@@
    \item The simplest way is to use the \texttt{custom\_model} decorator in modeling with a user-defined function that takes the inputs and model parameters as arguments.
-   \item It is also possible to create an arbitrarily complex custom model based on the \texttt{Model} class.
+   \item It is also possible to subclass the \texttt{Model} base class and create an arbitrarily complex custom model.
 \end{enumerate}
@@
 
-%\inlinecomment{TPR}{We should put the releases of sphinx-automodapi on Zenodo and cite this}
+\inlinecomment{TPR}{We should put the releases of sphinx-automodapi on Zenodo and cite this}
 

### 2017-11-22 main.tex
small edit

--- 2017-11-22 main.tex
@@
 commits.
-The commit distribution \inlinecomment{Tom R}{too vague, maybe 'the distribution of number of commits as a function of ...'} follows an approximate power-law (with log-slope of
-$\approx -0.47$) \inlinecomment{AG}{round to -0.5?  This is astronomy, after all.}, meaning most of the commits were and are contributed by a
-relatively small fraction of the contributor pool.
-Roughly half of the commits were contributed by the top $4$
-contributors, while $\sim 90$ percent of the commits came from the top $24$
-contributors.
+\figurename~\ref{fig:ncommits}, left, shows the distribution of total number of
+commits per contributor as of November 2017; from this, it is clear that most
+commits were and are contributed by a relatively small fraction of the
+contributor pool.
+\figurename~\ref{fig:ncommits}, right, shows the number of contributors as a
+function of time since the genesis of the \astropypkg core package.
 
@@
 
-The released versions of the \astropypkg core package are available from several
-of the \python distributions for scientific computing (e.g.,
-\href{http://anaconda.org}{Anaconda}) and from the \python Package Index
-(PyPI).\footnote{See the installation documentation for more information:
-\url{http://docs.astropy.org/en/stable/install.html}}
+\subsection{Distribution of packages}
+
+The \astropypkg core package is available from several of the \python distributions for scientific
+% * <mattwcraig@gmail.com> 2017-10-27T07:13:51.093Z:
+%
+% > \astropypkg i
+% I changed a few of the macros in here to refer to the package rather than the project because it is the package being discussed here.
+%
+% ^.
+computing, such as Anaconda or Enthought Canopy, which include also some of
+\astropy's affiliated packages.
+Alternatively, \astropypkg can be readily installed from the Python Package
+Index\footnote{\url{https://pypi.python.org/pypi}} (PyPI)
+\inlinecomment{Tom R}{make footnote link directly to astropy on PyPI?}
+using \texttt{pip}, the standard command-line tool for installing \python packages.
+For most recent \astropypkg releases, pre-built wheel distributions are obtainable
+from PyPI for Windows, Mac OS X and Linux systems that provide faster
+installation compared to the source distribution.
+% hamogu: I think that's too detailed for a journal paper.
+%     It's in the docs if anyone needs it.
+%Optionally, the version of
+%the package and the dependencies needed to run or build the software are given
+%by a specifier to the pip package manager as described in PEP 440\footnote{For
+%more detailed installation instructions and optional flags see
+%\url{http://docs.astropy.org/en/stable/install.html\#installing-astropy}}.
+
+Packaged versions of \astropy are also available for several
+operating systems that are managed by a system's package manager,
+including Debian, Ubuntu, Fedora, Gentoo, Arch Linux, Mac OS X (e.g.,
+via brew, macports or fink) and FreeBSD\@.  However, on occasion these packages
+may be outdated compared with the latest stable release of \astropy accessible
+from the PyPI\@. Pre-built binary conda packages for all of the affiliated packages are also available  via the \texttt{astropy} conda channel for Linux, Mac OS X, and MS Windows.
+% * <mattwcraig@gmail.com> 2017-10-27T07:16:27.310Z:
+%
+% > re-built binary conda packages
+% Feel free to remove if this is too detailed. I do think the available of the whole ecosystem across all platforms has helped speed its adoption.
+%
+% ^.
 

### 2017-11-22 main.tex
add tom's suggestion

@@
 \figurename~\ref{fig:ncommits}, left, shows the distribution of total number of
-commits per contributor as of November 2017; from this, it is clear that most
-commits were and are contributed by a relatively small fraction of the
-contributor pool.
+commits per contributor as of November 2017.
+This distribution shows that the \astropypkg core package has been developed by
+a broad contributor base, with a core team of developers having added over 1000
+commits to the repository, and a smooth distribution of contribution level down
+to a single commit.
+In this sense, the development of the core package has been a true community
+effort and is not dominated by a single individual.
+It is also important to note that the number of commits is only a rough metric
+of contribution, as a single commit could be a critical fix in the package or a
+fix for a typographical error.
 \figurename~\ref{fig:ncommits}, right, shows the number of contributors as a

### 2017-11-22 figures/commits_figure.py
fill under curve

@@ -83,12 +83,14 @@ def commits_vs_time(astropy_path, ax=None, **hist_kw):
     if ax is None:
         fig, ax = plt.subplots(1, 1, figsize=(6,5))
 
-    ax.plot(np.cumsum(commits_per_day), marker='', drawstyle='steps')
+    n_commits = np.cumsum(commits_per_day)
+    plt.fill_between(n_commits.index, 0, np.array(n_commits))
 
     ax.set_xlabel('year')
     ax.set_ylabel('number of commits')
 
-    ax.set_xlim(datetime(2011,1,1), datetime(2018,1,1))
+    ax.set_xlim(datetime(2011,6,1), datetime(2018,1,1))
+    ax.set_ylim(0, 21000)
 
 
 if __name__ == "__main__":

### 2017-11-22 main.tex
Explain second plot
stable not master

--- 2017-11-22 main.tex
@@
 commits.
-\figurename~\ref{fig:ncommits}, left, shows the distribution of total number of
-commits per contributor as of November 2017; from this, it is clear that most
-commits were and are contributed by a relatively small fraction of the
-contributor pool.
-\figurename~\ref{fig:ncommits}, right, shows the number of contributors as a
-function of time since the genesis of the \astropypkg core package.
+The commit distribution \inlinecomment{Tom R}{too vague, maybe 'the distribution of number of commits as a function of ...'} follows an approximate power-law (with log-slope of
+$\approx -0.47$) \inlinecomment{AG}{round to -0.5?  This is astronomy, after all.}, meaning most of the commits were and are contributed by a
+relatively small fraction of the contributor pool.
+Roughly half of the commits were contributed by the top $4$
+contributors, while $\sim 90$ percent of the commits came from the top $24$
+contributors.
 
@@
 
-\subsection{Distribution of packages}
-
-The \astropypkg core package is available from several of the \python distributions for scientific
-% * <mattwcraig@gmail.com> 2017-10-27T07:13:51.093Z:
-%
-% > \astropypkg i
-% I changed a few of the macros in here to refer to the package rather than the project because it is the package being discussed here.
-%
-% ^.
-computing, such as Anaconda or Enthought Canopy, which include also some of
-\astropy's affiliated packages.
-Alternatively, \astropypkg can be readily installed from the Python Package
-Index\footnote{\url{https://pypi.python.org/pypi}} (PyPI)
-\inlinecomment{Tom R}{make footnote link directly to astropy on PyPI?}
-using \texttt{pip}, the standard command-line tool for installing \python packages.
-For most recent \astropypkg releases, pre-built wheel distributions are obtainable
-from PyPI for Windows, Mac OS X and Linux systems that provide faster
-installation compared to the source distribution.
-% hamogu: I think that's too detailed for a journal paper.
-%     It's in the docs if anyone needs it.
-%Optionally, the version of
-%the package and the dependencies needed to run or build the software are given
-%by a specifier to the pip package manager as described in PEP 440\footnote{For
-%more detailed installation instructions and optional flags see
-%\url{http://docs.astropy.org/en/stable/install.html\#installing-astropy}}.
-
-Packaged versions of \astropy are also available for several
-operating systems that are managed by a system's package manager,
-including Debian, Ubuntu, Fedora, Gentoo, Arch Linux, Mac OS X (e.g.,
-via brew, macports or fink) and FreeBSD\@.  However, on occasion these packages
-may be outdated compared with the latest stable release of \astropy accessible
-from the PyPI\@. Pre-built binary conda packages for all of the affiliated packages are also available  via the \texttt{astropy} conda channel for Linux, Mac OS X, and MS Windows.
-% * <mattwcraig@gmail.com> 2017-10-27T07:16:27.310Z:
-%
-% > re-built binary conda packages
-% Feel free to remove if this is too detailed. I do think the available of the whole ecosystem across all platforms has helped speed its adoption.
-%
-% ^.
+The released versions of the \astropypkg core package are available from several
+of the \python distributions for scientific computing (e.g.,
+\href{http://anaconda.org}{Anaconda}) and from the \python Package Index
+(PyPI).\footnote{See the installation documentation for more information:
+\url{http://docs.astropy.org/en/stable/install.html}}
 
@@
 since version v0.2 (previously described in \citealt{astropy}).  The \astropypkg
-provides a full log of changes \footnote{https://github.com/astropy/astropy/blob/master/CHANGES.rst}
+provides a full log of changes \footnote{\url{https://github.com/astropy/astropy/blob/stable/CHANGES.rst}}
 over the course of the entire project and more details about individual
-subpackages are available in the documentation \footnote{http://docs.astropy.org/en/stable/}.
+subpackages are available in the documentation \footnote{\url{http://docs.astropy.org/en/stable/}}.
 Beyond what is mentioned below, most subpackages have seen increased performance

### 2017-11-22 main.tex
tweak wording

@@
 \url{http://docs.astropy.org/en/stable/install.html}}
+Effort has been made to make \astropypkg available and easily installable across
+all platforms; the package is constantly tested on different platforms as part
+of our suite of continuous integration tests.
 

### 2017-11-22 main.tex
reword the commit distribution discussion

--- 2017-11-22 main.tex
@@
 commits per contributor as of November 2017.
-This distribution shows that the \astropypkg core package has been developed by
-a broad contributor base, with a core team of developers having added over 1000
-commits to the repository, and a smooth distribution of contribution level down
+The relative flatness of this distribution (as demonstrated by its log-slope of 
+-0.5) shows that the \astropypkg core package has been developed by a broad
+contributor base.  A leading group of 6 developers have each added over 1000
+commits to the repository, with $\sim 20$ more in a core team with at least 
+100.  But there is a smooth distribution of contribution level from 100 down
 to a single commit.
@@
 function of time since the genesis of the \astropypkg core package.
+The package is still healthy: new commits are and have been contributed at a
+steady rate throughout its existence.
 

### 2017-11-22 main.tex
some minor edits to erik's addition

@@
 commits per contributor as of November 2017.
-The relative flatness of this distribution (as demonstrated by its log-slope of 
--0.5) shows that the \astropypkg core package has been developed by a broad
+The relative flatness of this distribution (as demonstrated by its log-log slope of
+$-0.5$) shows that the \astropypkg core package has been developed by a broad
 contributor base.  A leading group of 6 developers have each added over 1000
-commits to the repository, with $\sim 20$ more in a core team with at least 
-100.  But there is a smooth distribution of contribution level from 100 down
-to a single commit.
+commits to the repository, and $\sim 20$ more core contributors with at least
+100 commits.
+However, the distribution of contribution level (number of commits) continues
+from 100 down to a single commit.
 In this sense, the development of the core package has been a true community

### 2017-11-22 main.tex

--- 2017-11-22 main.tex
@@
 commits.
-The commit distribution \inlinecomment{Tom R}{too vague, maybe 'the distribution of number of commits as a function of ...'} follows an approximate power-law (with log-slope of
-$\approx -0.47$) \inlinecomment{AG}{round to -0.5?  This is astronomy, after all.}, meaning most of the commits were and are contributed by a
-relatively small fraction of the contributor pool.
-Roughly half of the commits were contributed by the top $4$
-contributors, while $\sim 90$ percent of the commits came from the top $24$
-contributors.
+\figurename~\ref{fig:ncommits}, left, shows the distribution of total number of
+commits per contributor as of November 2017.
+The relative flatness of this distribution (as demonstrated by its log-log slope of
+$-0.5$) shows that the \astropypkg core package has been developed by a broad
+contributor base.  A leading group of 6 developers have each added over 1000
+commits to the repository, and $\sim 20$ more core contributors with at least
+100 commits.
+However, the distribution of contribution level (number of commits) continues
+from 100 down to a single commit.
+In this sense, the development of the core package has been a true community
+effort and is not dominated by a single individual.
+It is also important to note that the number of commits is only a rough metric
+of contribution, as a single commit could be a critical fix in the package or a
+fix for a typographical error.
+\figurename~\ref{fig:ncommits}, right, shows the number of contributors as a
+function of time since the genesis of the \astropypkg core package.
+The package is still healthy: new commits are and have been contributed at a
+steady rate throughout its existence.
 

### 2017-11-22 main.tex
a few nitpicky edits

--- 2017-11-22 main.tex
@@
 commits.
-\figurename~\ref{fig:ncommits}, left, shows the distribution of total number of
-commits per contributor as of November 2017.
-The relative flatness of this distribution (as demonstrated by its log-slope of 
--0.5) shows that the \astropypkg core package has been developed by a broad
-contributor base.  A leading group of 6 developers have each added over 1000
-commits to the repository, with $\sim 20$ more in a core team with at least 
-100.  But there is a smooth distribution of contribution level from 100 down
-to a single commit.
-In this sense, the development of the core package has been a true community
-effort and is not dominated by a single individual.
-It is also important to note that the number of commits is only a rough metric
-of contribution, as a single commit could be a critical fix in the package or a
-fix for a typographical error.
-\figurename~\ref{fig:ncommits}, right, shows the number of contributors as a
-function of time since the genesis of the \astropypkg core package.
-The package is still healthy: new commits are and have been contributed at a
-steady rate throughout its existence.
+The commit distribution \inlinecomment{Tom R}{too vague, maybe 'the distribution of number of commits as a function of ...'} follows an approximate power-law (with log-slope of
+$\approx -0.47$) \inlinecomment{AG}{round to -0.5?  This is astronomy, after all.}, meaning most of the commits were and are contributed by a
+relatively small fraction of the contributor pool.
+Roughly half of the commits were contributed by the top $4$
+contributors, while $\sim 90$ percent of the commits came from the top $24$
+contributors.
 
@@
 
-%\subsection{Support of Astropy}
+\subsection{Support of Astropy}
+
+The \astropy project, as of the v2.0 release, does not receive any direct financial support for
+the development of the \astropypkg.  Development of the \astropypkg is supported
+by individuals who work on \astropy project in their own personal
+time, by individuals or groups to work on \astropy as
+part of a research project, or contributions from institutions that allocate
+people to work on \astropy.
+A list of organizations that have contributed to \astropy in this manner
+can be found in the Acknowledgements.
+Different funding models have been proposed for support of \astropy in the future
+(e.g., \cite{2016arXiv161003159M}), but a long-term plan
+for sustainability has not yet been established.
+The \astropy project has the ability to accept financial contributions
+(individual or institutes) through the NumFOCUS organization\footnote{NumFOCUS
+is a 501(c)(3) nonprofit that supports and promotes world-class, innovative,
+open source scientific computing.},
+which, has so far, covered the direct costs incurred by the \astropy project.
+
 % Removing unless this gets written about in

### 2017-11-22 main.tex
small edits

@@
 maintained by the East Asian Observatory;][]{starlink1982,starlink2013}.
-More recently, community-driven efforts have seen significant success in the astronomical sciences \citep{yt}
-%\inlinecomment{BMS}{I like the idea to reference yt here}
-%
+More recently, community-driven efforts have seen significant success in the astronomical sciences \citep{yt}.
 \python\footnote{\url{https://www.python.org/}} is an increasingly popular,
@@
 and manipulating heterogeneous data.
-\inlinecomment{APW:}{Need more introduction to the table subpackage!}
+%\inlinecomment{APW:}{Need more introduction to the table subpackage!}
 The package was described in detail in \cite{astropy}.
@@
 
-\inlinecomment{Perry G}{Some mention that some of these are inspired by Pandas?}
+%\inlinecomment{Perry G}{Some mention that some of these are inspired by Pandas?}
 

### 2017-11-22 main.tex
fix broken \url{} to docs.astropy.org

@@
 The development workflow is detailed in the \astropypkg
-documentation.\footnote{\emph{How to make a code contribution}, \url{http://docs.
-astropy.org/en/stable/development/workflow/development_workflow.html}}
+documentation.\footnote{\emph{How to make a code contribution},
+\url{http://docs.astropy.org/en/stable/development/workflow/development_workflow.html}}
 

### 2017-11-22 main.tex
fix broken \url{} to package-template

@@
 \astropy provides a package template --- as a separate \github repository,
-\package{astropy/package-template}\footnote{\url{https://github.com/astropy/package-t
-emplate/}} --- that aims to simplify setting up packaging, testing, and
+\package{astropy/package-template}\footnote{\url{https://github.com/astropy/package-template/}}
+--- that aims to simplify setting up packaging, testing, and
 documentation builds for developers of affiliated packages or

### 2017-11-23 main.tex
Suggested typos and minor modifications
Further notes:
* Shouldn't one use the traditional "0\farcs 2" rather than "0.2\arcsec"?
* one should uniformize footnote placement, before of after punctuation: "xxx\footnote{yyy}." vs. "xxx.\footnote{yyy}"
* one should uniformize dash length (-- vs. ---) and surroundings (space before or after)
* one should uniformize quotes, `xxx' vs. ``xxx''.

--- 2017-11-22 main.tex
@@
 \citep[\package{numpy};][]{numpy}, a wide variety of functions for scientific
-computing \citep[\package{scipy};][]{numpy}, and publication-quality plotting
+computing \citep[\package{scipy};][]{scipy}, and publication-quality plotting
 \citep[\package{matplotlib};][]{matplotlib}. Tens of thousands of other packages
@@
 Different funding models have been proposed for support of \astropy in the future
-(e.g., \cite{2016arXiv161003159M}), but a long-term plan
+(e.g., \citealt{2016arXiv161003159M}), but a long-term plan
 for sustainability has not yet been established.
@@
 since version v0.2 (previously described in \citealt{astropy}).  The \astropypkg
-provides a full log of changes \footnote{\url{https://github.com/astropy/astropy/blob/stable/CHANGES.rst}}
+provides a full log of changes\footnote{\url{https://github.com/astropy/astropy/blob/stable/CHANGES.rst}}
 over the course of the entire project and more details about individual
-subpackages are available in the documentation \footnote{\url{http://docs.astropy.org/en/stable/}}.
+subpackages are available in the documentation\footnote{\url{http://docs.astropy.org/en/stable/}}.
 Beyond what is mentioned below, most subpackages have seen increased performance
@@
 \sectionname~\ref{sec:units}).
-A brief description of this package was given in \citep{astropy}.
+A brief description of this package was given in \cite{astropy}.
 In version 2.0, the built-in constants have been organized into modules for
@@
 For now we set the epoch of observation to J2000, and the frame to J2000 in the case of the FK5 and ecliptic frames and B1950 for the FK4 frame, but in future we plan to include a larger variety of epochs and equinoxes, as well as tests of conversion to/from Altitude/Azimuth.
-For each benchmark, we convert the 1000 longitudes/latitudes from the input/output frame with all tools and quantify the comparison by looking at the median, minimum, maximum, and standard deviation of the absolute separation of the output coordinates from each pair of tools.
+For each benchmark, we convert the 1000 longitudes/latitudes from the input/output frame with all tools and quantify the comparison by looking at the median, mean, maximum, and standard deviation of the absolute separation of the output coordinates from each pair of tools.
 \tablename~\ref{tab:coordinate_benchmarks} gives an example of the relative accuracy of the conversion from FK4 to Galactic coordinates for all pairs of tools.
@@
 
-\subsubsection{nddata}
-
-The \package{astropy.nddata} supackage provides three types of functionality: an
+\subsubsection{\package{nddata}}
+
+The \package{astropy.nddata} subpackage provides three types of functionality: an
 abstract interface for representing generic arbitrary-dimensional datasets
@@
 \texttt{Table} objects can now be combined in several different ways. If two
-tables have the same rows, we may want to stack them ``vertically'' to create a
+tables have the same columns, we may want to stack them ``vertically'' to create a
 new table with the same columns but all rows. If two tables are row-matched but
@@
 
-\subsection{io}
+\subsection{\package{io}}
 % Simon
@@
 types, units, and descriptions. The newly defined \emph{Enhanced
-Character Separated Values} (ECSV,  \citet{ape6}) format makes it
+Character Separated Values} (ECSV,  \citealt{ape6}) format makes it
 possible to write a table to an ASCII-format file and read it back
@@
 \package{astropy.modeling} provides an efficient way to instantiate the same type of model with many different sets of parameter values by passing the \texttt{n\_models} argument on instantiation, which sets the number of models to instantiate.
-This creates a model set that can be efficiently evaluated for example, in PSF (point spread function) photometry, all objects in an image will have a PSF of the same functional form, but with different positions and amplitides.
+This creates a model set that can be efficiently evaluated for example, in PSF (point spread function) photometry, all objects in an image will have a PSF of the same functional form, but with different positions and amplitudes.
 
@@
 
-The \package{modeling} package now supports the representation, evaluation, and fitting of models using \texttt{Quantity} objects, which attach units to scalar values or arrays of values.
+The \package{astropy.modeling} subpackage now supports the representation, evaluation, and fitting of models using \texttt{Quantity} objects, which attach units to scalar values or arrays of values.
 In practice, this means that one can, for example, fit a model to data with units and get parameters that also have units out, or initialize a model with parameters with units and evaluate it using input values with different but equivalent units.
@@
 
-\astropypkg implements `normalized convolution' \citep[e.g.,][]{Knutsson1993}, which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.
+The \package{astropy.convolution} subpackage implements `normalized convolution' \citep[e.g.,][]{Knutsson1993}, which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.
 An example of this is given in \figurename~\ref{fig:convolution-example}.
-In versions $<=1.3$, the direct convolution and Fast Fourier Transform (FFT) convolution approaches were not consistent, with FFT convolution implementing normalized convolution and direct convolution implementing a different approach.
+In versions $\leq 1.3$, the direct convolution and Fast Fourier Transform (FFT) convolution approaches were not consistent, with FFT convolution implementing normalized convolution and direct convolution implementing a different approach.
 As of version 2.0, the two methods are consistent and include a suite of consistency checks.
@@
     ecosystem.  The red x's mark pixels that are set to NaN in the original data
-    (a).  If the data are convolved with a Gaussian kernel on a 9x9 grid using
+    (a).  If the data are convolved with a Gaussian kernel on a $9\times 9$ grid using
     scipy's direct convolution (b), any pixel within range of the original NaN
@@
 
-This subpackage differs from \package{APLpy} \citep{aplpy} in that the latter focuses on providing a very high-level interface to plotting that requires very few lines of code to get a good result, whereas WCSAxes defines an interface that is much closer to that of \package{matplotlib} \citep{matplotlib}.
+This subpackage differs from \package{APLpy} \citep{aplpy} in that the latter focuses on providing a very high-level interface to plotting that requires very few lines of code to get a good result, whereas \package{wcsaxes} defines an interface that is much closer to that of \package{matplotlib} \citep{matplotlib}.
 This enables significantly more advanced visualizations.
@@
 \caption{%
-An example of figure made using the \package{astropy.visualization.wcsaxes} subpackage, using \textit{Spitzer}/IRAC 8.0$\mu$m data from the Cygnus-X \textit{Spitzer} Legacy survey \citep{cygnusx}.
+An example of figure made using the \package{astropy.visualization.wcsaxes} subpackage, using \textit{Spitzer}/IRAC 8.0~$.0\mu$m data from the Cygnus-X \textit{Spitzer} Legacy survey \citep{cygnusx}.
 \label{fig:wcsaxes}
@@
 \package{astropy.visualization} also provides a histogram function, which is a
-generalization of \package{matplotlib}’s histogram function, to allow for more
+generalization of \texttt{matplotlib}’s histogram function, to allow for more
 flexible specification of histogram bins.  The function provides several methods
 of automatically tuning the histogram bin size. It has a syntax identical to
-\package{matplotlib}’s histogram function, with the exception of the \texttt{bins}
+\texttt{matplotlib}’s histogram function, with the exception of the \texttt{bins}
 parameter, which allows specification of one of four different methods for

### 2017-11-24 main.tex
Rephrasing the motivation section for choosing Python

--- 2017-11-22 main.tex
@@
 More recently, community-driven efforts have seen significant success in the astronomical sciences \citep{yt}.
-\python\footnote{\url{https://www.python.org/}} is an increasingly popular,
-general-purpose programming language that is available under a permissive open
-source software license free of charge for all major operating systems.
-Stable and well-developed packages provide support for array representation and arithmetic
-\citep[\package{numpy};][]{numpy}, a wide variety of functions for scientific
-computing \citep[\package{scipy};][]{numpy}, and publication-quality plotting
-\citep[\package{matplotlib};][]{matplotlib}. Tens of thousands of other packages
-are available which can help with tasks that are not astronomy specific but
-might be performed in the course of astronomical research, for example interfacing with databases or statistical inference.
-
-\python has become especially popular in the quantitative sciences,
-where researchers must simultaneously produce research, perform data analysis,
-and develop software.
-A large part of this success owes itself to a vibrant community of developers
-and a continuously-growing ecosystem of tools and web services that enable
-easier collaboration on software development, easier writing and sharing of
-software documentation, and continuous testing and validation of software.
-More recently, package managers such as
-Anaconda\footnote{\url{https://anaconda.org/}} have streamlined the installation
-process for most packages, therefore significantly reducing the barrier to entry
-for using many such libraries.
+
+\python\footnote{\url{https://www.python.org/}} is an increasingly popular, general-purpose
+programming language that is available under a permissive open source software license free of
+charge for all major operating systems. The programming language has become especially popular
+in the quantitative sciences, where researchers must simultaneously produce research, perform 
+data analysis and develop software. A large part of this success owes itself to the vibrant 
+community of developers and a continuously-growing ecosystem of tools, web services and stable
+well-developed packages that enable easier collaboration on software development, easier 
+writing and sharing of software documentation and continuous testing and validation of 
+software. While the programming language provides support for array representation \& 
+arithmetic \citep[\package{numpy};][]{numpy}, a wide variety of functions for scientific 
+computing \citep[\package{scipy};][]{numpy}, publication-quality plotting 
+\citep[\package{matplotlib};][]{matplotlib}, tens of thousands of other high quality and easy 
+to use packages are available which can help with tasks that are not astronomy specific but 
+might be performed in the course of astronomical research, for example, interfacing with 
+databases or statistical inferences. More recently, the development of package managers such as
+Anaconda\footnote{\url{https://anaconda.org/}} have streamlined the installation process for
+most packages significantly reducing the barrier to entry for using many such libraries.
 
@@
 The development workflow is detailed in the \astropypkg
-documentation.\footnote{\emph{How to make a code contribution},
-\url{http://docs.astropy.org/en/stable/development/workflow/development_workflow.html}}
+documentation.\footnote{\emph{How to make a code contribution}, \url{http://docs.
+astropy.org/en/stable/development/workflow/development_workflow.html}}
 

### 2017-11-24 main.tex
Edits to phrasing in 'support' paragraph.

--- 2017-11-22 main.tex
@@
 \renewcommand{\tablename}{Table\xspace}
+
+% Words that should not be hyphenated
+\hyphenation{NumFOCUS}
 
@@
 The \astropy project, as of the v2.0 release, does not receive any direct financial support for
-the development of the \astropypkg.  Development of the \astropypkg is supported
-by individuals who work on \astropy project in their own personal
-time, by individuals or groups to work on \astropy as
+the development of \astropypkg.  Development of the software, all supporting materials, and community support is provided
+by individuals who work on the \astropy project in their own personal
+time, by individuals or groups contributing to \astropy as
 part of a research project, or contributions from institutions that allocate
@@
 can be found in the Acknowledgements.
-Different funding models have been proposed for support of \astropy in the future
+Different funding models have been proposed for support of \astropy
 (e.g., \cite{2016arXiv161003159M}), but a long-term plan
@@
 The \astropy project has the ability to accept financial contributions
-(individual or institutes) through the NumFOCUS organization\footnote{NumFOCUS
+from institutions or individuals through the NumFOCUS\footnote{NumFOCUS
 is a 501(c)(3) nonprofit that supports and promotes world-class, innovative,
-open source scientific computing.},
-which, has so far, covered the direct costs incurred by the \astropy project.
+open source scientific computing.} organization. NumFOCUS has to date covered the direct costs incurred by the \astropy project.
 
@@
 since version v0.2 (previously described in \citealt{astropy}).  The \astropypkg
-provides a full log of changes \footnote{\url{https://github.com/astropy/astropy/blob/stable/CHANGES.rst}}
+provides a full log of changes\footnote{\url{https://github.com/astropy/astropy/blob/stable/CHANGES.rst}}
 over the course of the entire project and more details about individual
-subpackages are available in the documentation \footnote{\url{http://docs.astropy.org/en/stable/}}.
+subpackages are available in the documentation.\footnote{\url{http://docs.astropy.org/en/stable/}}
 Beyond what is mentioned below, most subpackages have seen increased performance
@@
 \astropy provides a package template --- as a separate \github repository,
-\package{astropy/package-template}\footnote{\url{https://github.com/astropy/package-template/}}
---- that aims to simplify setting up packaging, testing, and
+\package{astropy/package-template}\footnote{\url{https://github.com/astropy/package-t
+emplate/}} --- that aims to simplify setting up packaging, testing, and
 documentation builds for developers of affiliated packages or

### 2017-11-25 main.tex

--- 2017-11-24 main.tex
@@
 More recently, community-driven efforts have seen significant success in the astronomical sciences \citep{yt}.
-
-\python\footnote{\url{https://www.python.org/}} is an increasingly popular, general-purpose
-programming language that is available under a permissive open source software license free of
-charge for all major operating systems. The programming language has become especially popular
-in the quantitative sciences, where researchers must simultaneously produce research, perform 
-data analysis and develop software. A large part of this success owes itself to the vibrant 
-community of developers and a continuously-growing ecosystem of tools, web services and stable
-well-developed packages that enable easier collaboration on software development, easier 
-writing and sharing of software documentation and continuous testing and validation of 
-software. While the programming language provides support for array representation \& 
-arithmetic \citep[\package{numpy};][]{numpy}, a wide variety of functions for scientific 
-computing \citep[\package{scipy};][]{numpy}, publication-quality plotting 
-\citep[\package{matplotlib};][]{matplotlib}, tens of thousands of other high quality and easy 
-to use packages are available which can help with tasks that are not astronomy specific but 
-might be performed in the course of astronomical research, for example, interfacing with 
-databases or statistical inferences. More recently, the development of package managers such as
-Anaconda\footnote{\url{https://anaconda.org/}} have streamlined the installation process for
-most packages significantly reducing the barrier to entry for using many such libraries.
+\python\footnote{\url{https://www.python.org/}} is an increasingly popular,
+general-purpose programming language that is available under a permissive open
+source software license free of charge for all major operating systems.
+Stable and well-developed packages provide support for array representation and arithmetic
+\citep[\package{numpy};][]{numpy}, a wide variety of functions for scientific
+computing \citep[\package{scipy};][]{numpy}, and publication-quality plotting
+\citep[\package{matplotlib};][]{matplotlib}. Tens of thousands of other packages
+are available which can help with tasks that are not astronomy specific but
+might be performed in the course of astronomical research, for example interfacing with databases or statistical inference.
+
+\python has become especially popular in the quantitative sciences,
+where researchers must simultaneously produce research, perform data analysis,
+and develop software.
+A large part of this success owes itself to a vibrant community of developers
+and a continuously-growing ecosystem of tools and web services that enable
+easier collaboration on software development, easier writing and sharing of
+software documentation, and continuous testing and validation of software.
+More recently, package managers such as
+Anaconda\footnote{\url{https://anaconda.org/}} have streamlined the installation
+process for most packages, therefore significantly reducing the barrier to entry
+for using many such libraries.
 
@@
 \caption{%
-    A histogram with irregular bins, fit using the Bayesian blocks
-    algorithm. The left panel shows a standard histogram using
-    \package{matplotlib}'s default of 10 bins. The right panel shows
-    the same histogram with bin widths determined by the Bayesian
-    blocks model. The model is such that relevant features of the data
-    distribution are much more apparent.
+    Three approaches to a 1D histogram:
+    {\it left:} a standard histogram using \package{matplotlib}'s default of 10 bins.
+    {\it center:} a histogram with the number of equal-width bins determined automatically using \package{numpy}'s {\tt bins='auto'}.
+    {\it right:} a histogram created with \package{astropy}, with irregularly-spaced bins computed via the Bayesian Blocks algorithm.
+    Compared to regularly-spaced bins, the irregular bin widths give a more accurate visual representation of features in the dataset at various scales.
     \label{fig:bayes-blocks-hist}

### 2017-11-26 main.tex

@@
 arithmetic \citep[\package{numpy};][]{numpy}, a wide variety of functions for scientific 
-computing \citep[\package{scipy};][]{numpy}, publication-quality plotting 
+computing \citep[\package{scipy};][]{scipy}, publication-quality plotting 
 \citep[\package{matplotlib};][]{matplotlib}, tens of thousands of other high quality and easy 
@@
 can be found in the Acknowledgements.
+
+Different funding models have been proposed for support of \astropy in the future
+(e.g., \citealt{2016arXiv161003159M}), but a long-term plan
 Different funding models have been proposed for support of \astropy
-(e.g., \cite{2016arXiv161003159M}), but a long-term plan
+(e.g., \citealt{2016arXiv161003159M}), but a long-term plan
 for sustainability has not yet been established.

### 2017-11-27 main.tex
Correct grammar and unify verbiage
Consistently and correctly use plural 'Quantity objects' everywhere (instead of 'the quantity object')

@@
 In \texttt{astropy.units}, \texttt{Quantity} objects extend \texttt{numpy}
-array object and have been designed with speed in mind.
+array objects and have been designed with speed in mind.
 
@@
 
-The \texttt{Quantity} object extends
-the \texttt{numpy.ndarray} object and therefore
-works well with many of the functions in \texttt{numpy} that support
+\texttt{Quantity} objects extend
+\texttt{numpy.ndarray} objects and therefore
+work well with many of the functions in \texttt{numpy} that support
 array operations. For example, \texttt{Quantity} objects with angular

### 2017-11-27 main.tex

--- 2017-11-26 main.tex
@@
 
-Different funding models have been proposed for support of \astropy in the future
-(e.g., \citealt{2016arXiv161003159M}), but a long-term plan
 Different funding models have been proposed for support of \astropy

### 2017-11-28 main.tex

@@
 Since
-no package can be guaranteed to implement all transformations to arbitrary precision, and since some transformations are sometimes subject to interpretation of standards (in particular in the case of Galactic coordinates), we do not designate any of the existing packages as the `ground truth' but instead compare each tool to all other tools to find.
+no package can be guaranteed to implement all transformations to arbitrary precision, and since some transformations are sometimes subject to interpretation of standards (in particular in the case of Galactic coordinates), we do not designate any of the existing packages as the `ground truth' but instead compare each tool to all other tools.
 The benchmarks are thus useful beyond the \astropy project since they allow all of the tools to be compared to all other tools.

### 2017-11-30 main.tex

@@
 in the quantitative sciences, where researchers must simultaneously produce research, perform
-data analysis and develop software. A large part of this success owes itself to the vibrant 
-community of developers and a continuously-growing ecosystem of tools, web services and stable
+data analysis, and develop software. A large part of this success owes itself to the vibrant
+community of developers and a continuously-growing ecosystem of tools, web services, and stable
 well-developed packages that enable easier collaboration on software development, easier
-writing and sharing of software documentation and continuous testing and validation of 
-software. While the programming language provides support for array representation \& 
+writing and sharing of software documentation, and continuous testing and validation of
+software. While the programming language provides support for array representation and
 arithmetic \citep[\package{numpy};][]{numpy}, a wide variety of functions for scientific
-computing \citep[\package{scipy};][]{scipy}, publication-quality plotting 
-\citep[\package{matplotlib};][]{matplotlib}, tens of thousands of other high quality and easy 
-to use packages are available which can help with tasks that are not astronomy specific but 
-might be performed in the course of astronomical research, for example, interfacing with 
+computing \citep[\package{scipy};][]{scipy}, and publication-quality plotting
+\citep[\package{matplotlib};][]{matplotlib}, tens of thousands of other high-quality and easy-to-use
+packages are available, which can help with tasks that are not astronomy specific but
+might be performed in the course of astronomical research; e.g., interfacing with
 databases or statistical inferences. More recently, the development of package managers such as
 Anaconda\footnote{\url{https://anaconda.org/}} have streamlined the installation process for
-most packages significantly reducing the barrier to entry for using many such libraries.
-
-The \astropy project aims to provide an open-source, open-development core
+most packages, significantly reducing the entry barrier for using many such libraries.
+
+The \astropy project aims to provide an open-source and open-development core
 package (\astropypkg) and an ecosystem of \emph{affiliated packages} that
@@
 general tools and classes that supports the development of more specialized
-code. An example of such functionality is reading and writing FITS files: it would be
+code. An example of such functionality is reading and writing FITS files: It would be
 time consuming and impractical for multiple groups to implement the FITS
@@
 
-The \astropy project aims to develop and provide high quality code and
+The \astropy project aims to develop and provide high-quality code and
 documentation according to the best practices in software development.
@@
 \cite{astropy}. Since then, the \astropypkg package has been
-used in hundreds of projects, and the scope of the package has grown
-considerably. At the same time, the community of astronomers
+used in hundreds of projects and the scope of the package has grown
+considerably. At the same time, the scientific community
 contributing to the project has grown tremendously and an ecosystem
@@
 documentation.\footnote{\emph{How to make a code contribution},
-\url{http://docs.astropy.org/en/stable/development/workflow/development_workflow.html}}
+\url{http://docs.astropy.org/en/latest/development/workflow/development_workflow.html}}
 

### 2017-12-01 main.tex
Edits for Sections 2.3 to 2.5, inclusive.

@@
 contribute to the project.
-However, this model leads to ``organic'' growth where different features are
+This model leads to an ``organic'' growth, where different features are
 implemented by different people with different programming styles and
@@
 additions, including a rationale for the changes, how these changes will be
-implemented, and, in the case of code, what the interface will be \citep{ape1}.
+implemented, and in the case of code, what the interface will be \citep{ape1}.
 The APEs are discussed and refined by the community before much work is invested
@@
 discussions during the open consideration period. APEs are proposed via pull
-requests on a dedicated GitHub repository\footnote{\url{https://github.com/astropy/astropy-APEs}},
-and anyone can therefore read the proposed APEs and leave comments in-line.
-In previous APEs a community consensus emerged and APEs are accepted and become
-the basis for future work at this point.
+requests on a dedicated GitHub repository\footnote{\url{https://github.com/astropy/astropy-APEs}};
+anyone can therefore read the proposed APEs and leave in-line comments.
+When a community consensus emerge, the APEs are accepted and become
+the basis for future work.
 In cases where consensus cannot be reached, the
-\astropy coordination committee can decide to close the discussion and
+\astropy coordination committee may decide to close the discussion and
 make an executive decision based on the community input on the APE in question.
@@
 community. These packages support the goals and vision of \astropy of
-improving code reuse, interoperability, and embracing good coding
+improving code re-use, interoperability, and embracing good coding
 practices such as testing and thorough documentation.
@@
 Affiliated packages may also be used to develop substantial new functionality
-that will eventually be incorporated into the \astropypkg core package.
-New functionality benefits from having a rapid development and release cycle that is not tied to that of the \astropypkg core.
+that will eventually be incorporated into the \astropypkg core package
+(e.g., \texttt{wcsaxes}).
+New functionality benefits from having a rapid development and release cycle that is not tied to that of the \astropypkg core (\sectionname~\ref{sect:releasecycle}).
 % AG: rephrased this.
@@
 
-Affiliated packages are listed on the main \astropy website and advertised to the community through \astropy mailing lists, so becoming an affiliated package is a good way for new and existing packages to gain exposure while at the same time promoting \astropy's high standard for code and documentation quality.
-This process of listing and promoting affiliated packages is one way in which the \astropy project tries to increase code reuse in the astronomical community.
+Affiliated packages are listed on the main \astropy website and advertised to the community through \astropy mailing lists.
+Therefore, becoming an affiliated package is a good way for new and existing packages to gain exposure while promoting \astropy's high standard for code and documentation quality.
+This process of listing and promoting affiliated packages is one way in which the \astropy project tries to increase code re-use in the astronomical community.
 
 Packages can become affiliated to \astropy by applying for this status on a public mailing list.
-The coordination committee (\sectionname~\ref{sect:coordcom}) reviews such requests and issues recommendations for the improvement of a package where possible.
+The coordination committee (\sectionname~\ref{sect:coordcom}) reviews such requests and issues recommendations for the improvement of a package, where applicable.
 
@@
 \subsection{Release cycle and Long Term Support}
+\label{sect:releasecycle}
 % This could also include information about the development cycle
@@
 Some versions are additionally designated as ``Long-term support'' (LTS)
-releases, which continue to receive bugfixes for 2 years following the release
+releases, which continue to receive bug fixes for 2 years following the release
 with no changes to the API\@.
-The LTS versions are ideal for pipelines and other applications where API
+The LTS versions are ideal for pipelines and other applications, where API
 stability is essential.
-The latest LTS release (v2.0) is also the last one that supports \python 2, and
+The latest LTS release (v2.0) is also the last one that supports \python 2; It
 will receive bug fixes until the end of 2019 \citep{ape10}.
@@
 The version numbering of the \astropypkg core package reflects this release
-scheme: the core package version number uses the form x.y.z, where ``x'' is
-advanced for LTS releases, ``y'' is advanced for non-LTS feature releases, and
-``z'' is advanced for bugfix releases.
+scheme: the core package version number uses the form \texttt{x.y.z}, where ``x'' is
+advanced for LTS releases, ``y'' for non-LTS feature releases, and
+``z'' for bugfix releases.
 

### 2017-12-04 main.tex
Update main.tex
If I'm reading it right, BlackBody1D fits flux densities, not fluxes - correct?

@@
 fix for a typographical error.
-\figurename~\ref{fig:ncommits}, right, shows the number of contributors as a
+\figurename~\ref{fig:ncommits}, right, shows the number of commits as a
 function of time since the genesis of the \astropypkg core package.
@@
 In practice, this means that one can, for example, fit a model to data with units and get parameters that also have units out, or initialize a model with parameters with units and evaluate it using input values with different but equivalent units.
-Using this, we have implemented a blackbody model (\texttt{BlackBody1D}) that can be used to fit observed fluxes in a variety of units and as a function of different units of spectral coordinates (e.g., wavelength or frequency).
+Using this, we have implemented a blackbody model (\texttt{BlackBody1D}) that can be used to fit observed flux densities in a variety of units and as a function of different units of spectral coordinates (e.g., wavelength or frequency).
 

### 2017-12-04 main.tex
edit to circular statistics sub-section
add introductory sentence
edit to models unit support sub-section
I think "fluxes" should be "flux densities" when discussing BlackBody1D (?)
Edits for Sections 2.6 to 3.3.4, inclusive

--- 2017-12-01 main.tex
@@
 The \astropy project, as of the v2.0 release, does not receive any direct financial support for
-the development of \astropypkg.  Development of the software, all supporting materials, and community support is provided
+the development of \astropypkg.  Development of the software, all supporting materials, and community support are provided
 by individuals who work on the \astropy project in their own personal
@@
 is a 501(c)(3) nonprofit that supports and promotes world-class, innovative,
-open source scientific computing.} organization. NumFOCUS has to date covered the direct costs incurred by the \astropy project.
+open source scientific computing.} organization. NumFOCUS has, to date, covered the direct costs incurred by the \astropy project.
 
@@
 At the foundation is the \astropypkg core package, which provides general
-functionality (e.g., coordinate transformations, reading and writing astronomical
-files) or base classes for other
+functionality (e.g., coordinate transformations, reading and writing
+astronomical files, and units) or base classes for other
 packages to utilize for a common interface (e.g., \texttt{NDData}).
@@
 
-As of \astropypkg version 2.0, units and quantities are prevalent in most other
-\astropypkg subpackages and are thus a key concept for using the package as a
-whole.
-Units are intimately entwined in the definition of astronomical coordinates and
-thus nearly all functionality in the \texttt{astropy.coordinates} subpackage
-(see \sectionname~\ref{sec:coordinates}) depends on this functionality.
-For most other subpackages, quantities are at least accepted, and often expected
+As of \astropypkg version 2.0, units and quantities, prevalent in most of its
+subpackages, have become a key concept for using the package as a whole.
+Units are intimately entwined in the definition of astronomical coordinates;
+Thus, nearly all functionality in the \texttt{astropy.coordinates} subpackage
+(see \sectionname~\ref{sec:coordinates}) depends on them.
+For most other subpackages, quantities are at least accepted and often expected
 by default.
@@
 The motivation and key concepts behind this subpackage were described in detail
-in the previous paper \citep{astropy}, and thus here we primarily highlight new
-features and improvements.
+in the previous paper \citep{astropy}. Therefore, we primarily highlight new
+features and improvements here.
 
@@
         functions that expect \texttt{Quantity} objects, we often want to
-        enforce that the input units have the correct type.
+        enforce that the input units have the correct physical type.
         For example, we may want to require only length-type \texttt{Quantity}
@@
 Each of the \texttt{Frame} classes define their own component names and
-preferred \texttt{Representation} class.
+preferred \texttt{Representation} classes.
 The frame-specific component names map to corresponding components on the
@@
 data.
-For most frames the preferred representation is spherical, although this is
+For most frames, the preferred representation is spherical, although this is
 determined primarily by the common use in the astronomical community.
@@
 \texttt{astropy.coordinates}.
-Custom, user-implemented \texttt{Frame} classes that define transformations to
+Custom user-implemented \texttt{Frame} classes that define transformations to
 any reference frame in this graph can then be transformed to any of the other
@@
 Instead, \texttt{astropy.coordinates} provides a high-level interface to
-representing astronomical coordinates through the \texttt{SkyCoord} class.
-The \texttt{SkyCoord} class was designed to provide a single class that
+representing astronomical coordinates through the \texttt{SkyCoord} class,
+which was designed to provide a single class that
 accepts a wide range of possible inputs.
@@
     In addition to positional coordinate data, the \texttt{Frame} classes now
-    also support velocity data.
+    also support velocity.
     As the default representation for most frames is spherical, most of the
@@
     cases the transformed velocity components have limited accuracy because the
-    transformations are done numerically.
-    The visualization of the coordinate frame transform graph highlights which
+    transformations are done numerically instead of analytically.
+    \figurename~\ref{fig:frame-transform-graph} highlights which
     velocity transformations can be done exactly and which transformations are
@@
     These ephemerides can be computed either using analytic approximations from
-    ERFA, or from downloaded JPL ephemerides (the latter requires the
+    ERFA or from downloaded JPL ephemerides (the latter requires the
     \package{jplephem}\footnote{\url{https://github.com/brandon-rhodes/python-jplephem}}
@@
 Since
-no package can be guaranteed to implement all transformations to arbitrary precision, and since some transformations are sometimes subject to interpretation of standards (in particular in the case of Galactic coordinates), we do not designate any of the existing packages as the `ground truth' but instead compare each tool to all other tools.
+no package can be guaranteed to implement all transformations to arbitrary precision and some transformations are sometimes subject to interpretation of standards (in particular in the case of Galactic coordinates), we do not designate any of the existing packages as the ``ground truth'' but instead compare each tool to all other tools.
 The benchmarks are thus useful beyond the \astropy project since they allow all of the tools to be compared to all other tools.
@@
 The benchmarks are meant to evolve over time and include an increasing variety of cases.
-At the moment, the benchmarks are set up as follows - we have generated a standard set of 1000 pairs of random longitudes/latitudes that we use in all benchmarks.
-Each benchmark is then defined using an input and output coordinate frame, using all combinations of FK4, FK5, Galactic, ICRS and Ecliptic frames.
-For now we set the epoch of observation to J2000, and the frame to J2000 in the case of the FK5 and ecliptic frames and B1950 for the FK4 frame, but in future we plan to include a larger variety of epochs and equinoxes, as well as tests of conversion to/from Altitude/Azimuth.
+At the moment, the benchmarks are set up as follows -- we have generated a standard set of 1000 pairs of random longitudes/latitudes that we use in all benchmarks.
+Each benchmark is then defined using an input and output coordinate frame, using all combinations of FK4, FK5, Galactic, ICRS, and Ecliptic frames.
+For now, we set the epoch of observation to J2000.
+We also set the frame to J2000 (for FK5 and Ecliptic) and B1950 (for FK4).
+In the future, we plan to include a larger variety of epochs and equinoxes, as well as tests of conversion to/from Altitude/Azimuth.
 For each benchmark, we convert the 1000 longitudes/latitudes from the input/output frame with all tools and quantify the comparison by looking at the median, mean, maximum, and standard deviation of the absolute separation of the output coordinates from each pair of tools.
+
 \tablename~\ref{tab:coordinate_benchmarks} gives an example of the relative accuracy of the conversion from FK4 to Galactic coordinates for all pairs of tools.
-This shows for example that \astropy, Kapteyn and PyTPM agree perfectly (to the precision shown), while PALpy, pySLALIB, and PyAST also agree perfectly amongst themselves, but show an offset of around 0.2\arcsec with the former three packages.
+This shows, for example, that \astropy, Kapteyn, and PyTPM agree perfectly (to the precision shown), while PALpy, pySLALIB, and PyAST also agree perfectly amongst themselves.
+However, there is an offset of around 0.2\arcsec\space with the former three packages.
 Finally, PyEphem disagrees with other packages by 0.4--0.8\arcsec.
-These values are only meant to be illustrative and will change over time as the benchmarks are refined and packages are updated.
+These values are only meant to be illustrative and will change over time as the benchmarks are refined and the packages updated.
 %\inlinecomment{Perry G}{Wouldn't the table be better represented as a matrices?
@@
 \caption{%
-An example of figure made using the \package{astropy.visualization.wcsaxes} subpackage, using \textit{Spitzer}/IRAC 8.0~$.0\mu$m data from the Cygnus-X \textit{Spitzer} Legacy survey \citep{cygnusx}.
+An example of figure made using the \package{astropy.visualization.wcsaxes} subpackage, using \textit{Spitzer}/IRAC 8.0~$\mu$m data from the Cygnus-X \textit{Spitzer} Legacy survey \citep{cygnusx}.
 \label{fig:wcsaxes}
@@
 
+Astronomers often need to compute statistics of quantities evaluated on a circle, such as sky direction or polarization angle.
 A set of circular statistical estimators based on \citet{JammalamadakaSengupta}

### 2017-12-06 main.tex
flesh out acknowledgements

@@
 
-\acknowledgments
-
-Who to thank?  numfocus, GSOC, Python Software Foundation
-
-We thank the many web services that make developing and maintaining this package
-feasible, such as GitHub, Travis CI, Appveyor, CircleCI, and Read the Docs.
+\acknowledgments The \astropy community is supported by and makes use
+of a number of organizations and services outside the traditional
+academic community. We thank Google for financing and organizing the
+Google Summer of Code (GSoC) program, that has funded severals
+students per year to work on \astropy related projects over the
+summer. These students ofter turn into long-term contributors. We also
+thank numfocus and the Python Software Foundation for financial
+support for various needs. Within the academic community, we thank
+institutions that make it possible that astronomers and programmers on
+their staff can contribute (part of) their time to the development of
+\astropy projects. Furthermore, the \astropy packages would not exisit
+in their current form without a number of webservices for code
+hosting, continuous integration, and documentation; in particular,
+\astropy heavily relies on GitHub, Travis CI, Appveyor, CircleCI, and
+Read the Docs.  \astropypkg integrates with the SIMBAD database,
+operated at CDS, Strasbourg, France.
 

### 2017-12-06 main.tex
Address concerns in #50
Remove wording that requires Python specific coding knowledge ("decorator")
and add a general "who's the audience for this article" to the intro.

Fixes #50

--- 2017-12-04 main.tex
@@
 \section{Introduction} \label{sec:intro}
-% first draft by Moritz (hamogu)
-% heavily edited by Adrian PW - let me know if you want to revert anything!
 All astronomical research makes use of software in some way.  Astronomy as a field has thus long supported the development of software tools
@@
 software, and the \astropypkg core package a feature-rich \python library.
-
-%\inlinecomment{Tom R}{the 'this community' above is a bit too general - do we mean it is the only community in astronomy, or in the Python astronomy world?
-I'd change this to either 'to become this community for Python astronomy software' or 'to become such a community'.
-For instance yt had a community before we came along for the simulation community, so I want to make sure we don't claim we are the only community out there.}
-%\inlinecomment{Perry G}{Agreed}
 
@@
 in \sectionname~\ref{sec:future}.
+
+This article is not intended as an introduction to \astropypkg, nor does it replace the \astropypkg documentation.
+Instead, it describes the way the \astropy community works and organizes and the current state of the \astropypkg package.
 
@@
         objects.
-        These requirements often lead to implementing repetitive code for
-        validating \texttt{Quantity} inputs.
-        \texttt{astropy.units} now provides a \python decorator,
-        \texttt{quantity\_input()}, that does this verification automatically.
+        \texttt{astropy.units} provides a tool called \texttt{quantity\_input()}
+        that can perform this varification automatically to avoid repetitive
+        code.
 
@@
 Most models are defined by parameters and maintain an ordered list of parameter names, \texttt{Model.param\_names}.
-A model is instantiated by passing in values (scalars or arrays) for its parameters.
+A model is constructed by passing in values (scalars or arrays) for its parameters.
 A parameter is a descriptor that provides a proxy for the value and stores additional information -- default value, default unit, and parameter constraints.
@@
 This is a settable property; i.e.
-a model instance can be assigned as inverse to another model.
+a model can be assigned as inverse to another model.
 For example, a polynomial model can be assigned as an inverse to another polynomial model.
@@
 
-\package{astropy.modeling} provides an efficient way to instantiate the same type of model with many different sets of parameter values by passing the \texttt{n\_models} argument on instantiation, which sets the number of models to instantiate.
+\package{astropy.modeling} provides an efficient way to set up the same type of model with many different sets of parameter values.
 This creates a model set that can be efficiently evaluated for example, in PSF (point spread function) photometry, all objects in an image will have a PSF of the same functional form, but with different positions and amplitudes.
@@
 \subsubsection{Creating New Models}
-
-New model classes can be created in two ways:
-\begin{enumerate}
-   \item The simplest way is to use the \texttt{custom\_model} decorator in modeling with a user-defined function that takes the inputs and model parameters as arguments.
-   \item It is also possible to create an arbitrarily complex custom model based on the \texttt{Model} class.
-\end{enumerate}
+If arithmetic combinations of existing models is not sufficient, new model classes can be defined in different ways.
+The \package{astropy.modeling} provides tools to turn a simple function into a full-featured model, but it also allows to extend the build-in model class with arbitrary code.
 

### 2017-12-06 main.tex
Break a few paragraphs from single very long line into more sensible lengths.

@@
 
-In order to check the accuracy of the coordinate transformations in \package{astropy.coordinates}, we have created a set of benchmarks that we use to compare transformations between a set of coordinate frames for a number of packages\footnote{\url{http://www.astropy.org/coordinates-benchmark/summary.html}}.
-Since
-no package can be guaranteed to implement all transformations to arbitrary precision, and since some transformations are sometimes subject to interpretation of standards (in particular in the case of Galactic coordinates), we do not designate any of the existing packages as the `ground truth' but instead compare each tool to all other tools.
-The benchmarks are thus useful beyond the \astropy project since they allow all of the tools to be compared to all other tools.
-The tools included in the benchmark at the moment include the \astropypkg core package, Kapteyn \citep{kapteyn}, NOVAS \citep{novas}, PALpy \citep{pal}, PyAST \citep[a wrapper for AST, described in][]{ast}, PyTPM\footnote{\url{https://github.com/phn/pytpm}}, PyEphem \citep{pyephem}, and pySLALIB \citep[a Python wrapper for SLALIB, described in][]{slalib}.
-
-The benchmarks are meant to evolve over time and include an increasing variety of cases.
-At the moment, the benchmarks are set up as follows - we have generated a standard set of 1000 pairs of random longitudes/latitudes that we use in all benchmarks.
-Each benchmark is then defined using an input and output coordinate frame, using all combinations of FK4, FK5, Galactic, ICRS and Ecliptic frames.
-For now we set the epoch of observation to J2000, and the frame to J2000 in the case of the FK5 and ecliptic frames and B1950 for the FK4 frame, but in future we plan to include a larger variety of epochs and equinoxes, as well as tests of conversion to/from Altitude/Azimuth.
-For each benchmark, we convert the 1000 longitudes/latitudes from the input/output frame with all tools and quantify the comparison by looking at the median, mean, maximum, and standard deviation of the absolute separation of the output coordinates from each pair of tools.
-\tablename~\ref{tab:coordinate_benchmarks} gives an example of the relative accuracy of the conversion from FK4 to Galactic coordinates for all pairs of tools.
-This shows for example that \astropy, Kapteyn and PyTPM agree perfectly (to the precision shown), while PALpy, pySLALIB, and PyAST also agree perfectly amongst themselves, but show an offset of around 0.2\arcsec with the former three packages.
-Finally, PyEphem disagrees with other packages by 0.4--0.8\arcsec.
-These values are only meant to be illustrative and will change over time as the benchmarks are refined and packages are updated.
+In order to check the accuracy of the coordinate transformations in
+\package{astropy.coordinates}, we have created a set of benchmarks that we use
+to compare transformations between a set of coordinate frames for a number of
+packages\footnote{\url{http://www.astropy.org/coordinates-benchmark/summary.html}}.
+Since no package can be guaranteed to implement all transformations to
+arbitrary precision and some transformations are sometimes subject to
+interpretation of standards (in particular in the case of Galactic coordinates),
+we do not designate any of the existing packages as the ``ground truth'' but
+instead compare each tool to all other tools. The benchmarks are thus useful
+beyond the \astropy project since they allow all of the tools to be compared to
+all other tools. The tools included in the benchmark at the moment include the
+\astropypkg core package, Kapteyn \citep{kapteyn}, NOVAS \citep{novas},
+PALpy \citep{pal}, PyAST \citep[a wrapper for AST, described in][]{ast},
+PyTPM\footnote{\url{https://github.com/phn/pytpm}}, PyEphem \citep{pyephem},
+and pySLALIB \citep[a Python wrapper for SLALIB, described in][]{slalib}.
+
+The benchmarks are meant to evolve over time and include an increasing variety
+of cases. At the moment, the benchmarks are set up as follows --
+we have generated a standard set of 1000 pairs of random longitudes/latitudes
+that we use in all benchmarks. Each benchmark is then defined using an input
+and output coordinate frame, using all combinations of FK4, FK5, Galactic,
+ICRS, and Ecliptic frames. For now, we set the epoch of observation to J2000.
+We also set the frame to J2000 (for FK5 and Ecliptic) and B1950 (for FK4).
+In the future, we plan to include a larger variety of epochs and equinoxes,
+as well as tests of conversion to/from Altitude/Azimuth. For each benchmark,
+we convert the 1000 longitudes/latitudes from the input/output frame with all
+tools and quantify the comparison by looking at the median, mean, maximum,
+and standard deviation of the absolute separation of the output coordinates
+from each pair of tools.
+
+\tablename~\ref{tab:coordinate_benchmarks} gives an example of the relative
+accuracy of the conversion from FK4 to Galactic coordinates for all pairs of
+tools. This shows, for example, that \astropy, Kapteyn, and PyTPM agree
+perfectly (to the precision shown), while PALpy, pySLALIB, and PyAST also
+agree perfectly amongst themselves. However, there is an offset of around
+0.2\arcsec\space with the former three packages. Finally, PyEphem disagrees
+with other packages by 0.4--0.8\arcsec. These values are only meant to be
+illustrative and will change over time as the benchmarks are refined and the
+packages updated.
 %\inlinecomment{Perry G}{Wouldn't the table be better represented as a matrices?
@@
 In practice, this means that one can, for example, fit a model to data with units and get parameters that also have units out, or initialize a model with parameters with units and evaluate it using input values with different but equivalent units.
-Using this, we have implemented a blackbody model (\texttt{BlackBody1D}) that can be used to fit observed flux densities in a variety of units and as a function of different units of spectral coordinates (e.g., wavelength or frequency).
+Using this, we have implemented a blackbody model (\texttt{BlackBody1D}) that can be used to fit observed fluxes in a variety of units and as a function of different units of spectral coordinates (e.g., wavelength or frequency).
 

### 2017-12-06 main.tex
Address review comments.

@@
 spherical angles are Galactic longitude (\texttt{l}) and latitude (\texttt{b}).
-Each of the \texttt{Frame} classes define their own component names and
-preferred \texttt{Representation} classes.
+Each \texttt{Frame} class defines its own component names and preferred \texttt{Representation} class.
 The frame-specific component names map to corresponding components on the
@@
     In addition to positional coordinate data, the \texttt{Frame} classes now
-    also support velocity.
+    also support velocity data.
     As the default representation for most frames is spherical, most of the

### 2017-12-06 main.tex
fix numfocus spelling

--- 2017-12-06 main.tex
@@
 
-\acknowledgments
-
-Who to thank?  numfocus, GSOC, Python Software Foundation
-
-We thank the many web services that make developing and maintaining this package
-feasible, such as GitHub, Travis CI, Appveyor, CircleCI, and Read the Docs.
+\acknowledgments The \astropy community is supported by and makes use
+of a number of organizations and services outside the traditional
+academic community. We thank Google for financing and organizing the
+Google Summer of Code (GSoC) program, that has funded severals
+students per year to work on \astropy related projects over the
+summer. These students ofter turn into long-term contributors. We also
+thank NumFOCUS and the Python Software Foundation for financial
+support for various needs. Within the academic community, we thank
+institutions that make it possible that astronomers and programmers on
+their staff can contribute (part of) their time to the development of
+\astropy projects. Furthermore, the \astropy packages would not exisit
+in their current form without a number of webservices for code
+hosting, continuous integration, and documentation; in particular,
+\astropy heavily relies on GitHub, Travis CI, Appveyor, CircleCI, and
+Read the Docs.  \astropypkg integrates with the SIMBAD database,
+operated at CDS, Strasbourg, France.
 

### 2017-12-06 main.tex
address reviews

--- 2017-12-06 main.tex
@@
 in \sectionname~\ref{sec:future}.
+
+This article is not intended as an introduction to \astropypkg, nor does it replace the \astropypkg documentation.
+Instead, it describes the way the \astropy community is organized and the current state of the \astropypkg package.
 
@@
 
-\package{astropy.modeling} provides an efficient way to instantiate the same type of model with many different sets of parameter values by passing the \texttt{n\_models} argument on instantiation, which sets the number of models to instantiate.
-This creates a model set that can be efficiently evaluated for example, in PSF (point spread function) photometry, all objects in an image will have a PSF of the same functional form, but with different positions and amplitudes.
+\package{astropy.modeling} provides an efficient way to set up the same type of model with many different sets of parameter values.
+This creates a model set that can be efficiently evaluated.
+For example, in PSF (point spread function) photometry, all objects in an image will have a PSF of the same functional form, but with different positions and amplitudes.
 
@@
 \subsubsection{Creating New Models}
-
-New model classes can be created in two ways:
-\begin{enumerate}
-   \item The simplest way is to use the \texttt{custom\_model} decorator in modeling with a user-defined function that takes the inputs and model parameters as arguments.
-   \item It is also possible to create an arbitrarily complex custom model based on the \texttt{Model} class.
-\end{enumerate}
+If arithmetic combinations of existing models is not sufficient, new model classes can be defined in different ways.
+The \package{astropy.modeling} provides tools to turn a simple function into a full-featured model, but it also allows extending the build-in model class with arbitrary code.
 
@@
 
-\acknowledgments The \astropy community is supported by and makes use
-of a number of organizations and services outside the traditional
-academic community. We thank Google for financing and organizing the
-Google Summer of Code (GSoC) program, that has funded severals
-students per year to work on \astropy related projects over the
-summer. These students ofter turn into long-term contributors. We also
-thank NumFOCUS and the Python Software Foundation for financial
-support for various needs. Within the academic community, we thank
-institutions that make it possible that astronomers and programmers on
-their staff can contribute (part of) their time to the development of
-\astropy projects. Furthermore, the \astropy packages would not exisit
-in their current form without a number of webservices for code
-hosting, continuous integration, and documentation; in particular,
-\astropy heavily relies on GitHub, Travis CI, Appveyor, CircleCI, and
-Read the Docs.  \astropypkg integrates with the SIMBAD database,
-operated at CDS, Strasbourg, France.
+\acknowledgments
+
+Who to thank?  numfocus, GSOC, Python Software Foundation
+
+We thank the many web services that make developing and maintaining this package
+feasible, such as GitHub, Travis CI, Appveyor, CircleCI, and Read the Docs.
 

### 2017-12-06 registry.tex
add imexam

@@
 \href{https://github.com/astropy/halotools}{Halotools} & Yes & \href{https://pypi.python.org/pypi/halotools}{halotools} & Andrew Hearin & \citealt{halotools}\\
-\href{http://github.com/spacetelescope/imexam}{imexam} & No & \href{https://pypi.python.org/pypi/imexam}{imexam} & Megan Sosey & \\
+\href{http://github.com/spacetelescope/imexam}{imexam} & No & \href{https://pypi.python.org/pypi/imexam}{imexam} & Megan Sosey & \citealt{imexam} \\
 \href{https://github.com/Chandra-MARX/marxs}{marxs} & Yes & \href{https://pypi.python.org/pypi/marxs}{marxs} & Hans Moritz Günther (hamogu) & \citealt{marxs}\\
@@
 \href{http://github.com/astropy/photutils}{photutils} & No & \href{https://pypi.python.org/pypi/photutils}{photutils} & Larry Bradley and Brigitta Sipocz & \citealt{photutils} \\
-\href{http://github.com/weaverba137/pydl}{PyDL} & No & \href{https://pypi.python.org/pypi/pydl}{pydl} & Benjamin Alan Weaver & \\
+\href{http://github.com/weaverba137/pydl}{PyDL} & No & \href{https://pypi.python.org/pypi/pydl}{pydl} & Benjamin Alan Weaver & \citealt{pydl}\\
 \href{https://github.com/olebole/python-cpl}{python-cpl} & No & \href{https://pypi.python.org/pypi/python-cpl}{python-cpl} & Ole Streicher & \citealt{pythoncpl}\\

### 2017-12-07 main.tex
Edits for Section 3.4 to 3.5.5, inclusive

@@
 standardized.
-        With the location of a source on the sky (i.e. a \texttt{SkyCoord}
-        object), the location of an observatory on Earth (i.e. an
+With the location of a source on the sky (i.e., a \texttt{SkyCoord}
+object), the location of an observatory on Earth (i.e., an
 \texttt{EarthLocation} object), and time values as \texttt{Time}
@@
 with attributes for accessing metadata, the world-coordinate system (WCS),
-uncertainty arrays matched to the data shape, and other traits.
-Building on this interface, the \texttt{NDData} class provides a minimal working implementation for storing \package{numpy} arrays.
-These classes serve as useful base classes for package authors wishing to develop their own classes for specific use cases and as containers for exchanging gridded data.
-
-The classes \texttt{NDDataRef}, \texttt{NDDataArray}, and \texttt{CCDData} extend the base storing functionality with options to do basic arithmetic (addition, subtraction, multiplication, and division) including error propagation in limited cases and slicing of the dataset based on grid coordinates that appropriately handles masking, errors, and units (if present).
-Additionally, the \texttt{CCDData} class also provides reading and writing from and to FITS files and uses data structures from \astropypkg, like \texttt{WCS}, to represent the contents of a file abstractly.
-
-The \package{astropy.nddata.utils} module provides utilities that can operate on either plain \package{numpy} arrays or any of the classes in the \package{astropy.nddata} subpackage.
-It features a class for representing two-dimensional image cutouts, allowing one to easily link pixels in the cutout to pixels in the original image or from the image to the cutout, to convert between world and pixel coordinates in the cutout, and to overlay the cutout on images.
-Functions to enlarge or reduce an image by doing block replication or reduction are also provided.
+uncertainty arrays matched to the shape of the data, and other traits.
+Building on this interface, the \texttt{NDData} class provides a minimal
+working implementation for storing \package{numpy} arrays. These classes serve
+as useful base classes for package authors wishing to develop their own classes
+for specific use cases and as containers for exchanging gridded data.
+
+The classes \texttt{NDDataRef}, \texttt{NDDataArray}, and \texttt{CCDData}
+extend the base storage functionality with options to do basic arithmetic
+(addition, subtraction, multiplication, and division), including error
+propagation in limited cases, and slicing of the dataset based on grid
+coordinates that appropriately handles masking, errors, and units (if present).
+Additionally, the \texttt{CCDData} class also provides reading and writing from
+and to FITS files and uses data structures from \astropypkg, like \texttt{WCS},
+to represent the file contents abstractly.
+
+The \package{astropy.nddata.utils} module provides utilities that can operate
+on either plain \package{numpy} arrays or any of the classes in the
+\package{astropy.nddata} subpackage. It features a class for representing
+two-dimensional image cutouts, allowing one to easily link pixels in the cutout
+to those in the original image or vice versa, to convert
+between world and pixel coordinates in the cutout, and to overlay the cutout
+on images. Functions to enlarge or reduce an image by doing block replication
+or reduction are also provided.
 
@@
 The package was described in detail in \cite{astropy}.
-
-Next, we summarize key new features or updates to \package{astropy.table}.
+Thus, in what follows, we only summarize key new features or updates to
+\package{astropy.table} since the previous \astropy paper.
 
@@
 
-A table can contain data that naturally forms groups -- for example it may
+A table can contain data that naturally form groups; For example, it may
 contain multiple observations of a few sources at different points in time
-and in different bands. We may then want to split the table into groups based
-on the combination of source observed and the band, and then combine the
-results for each combination of source and band in some way (for example finding
+and in different bands. Then, we may want to split the table into groups based
+on the combination of source observed and the band, after which we combine the
+results for each combination of source and band in some way (e.g., finding
 the mean or standard deviation of the fluxes or magnitudes over time) or filter
@@
 have distinct columns, we may want to stack them ``horizontally'' to create a
-new table with the same rows but all columns. For other situations, more general
-table concatenations or joins are also possible when two tables share some
-common columns.
+new table with the same rows but all columns. For other situations, more generic
+table concatenation or joining are also possible when two tables share some
+columns.
 
@@
 
-The \texttt{Table} object now allows \texttt{Quantity} objects, celestial
-coordinate objects (\texttt{SkyCoord}), and date/time objects (\texttt{Time}) to
-be used as columns, and also provides a general way for other user-defined
-objects to be used as columns. This makes it possible for example to easily
-represent catalogs of sources or time series as in Astropy, and having both the
-benefits of the \texttt{Table} object (such as accessing specific rows/columns
-or groups of rows/columns, combining tables, and so on) and the benefits of e.g.
-the \texttt{SkyCoord} or \texttt{Time} classes (such as converting the
-coordinates to a different frame, or accessing the date/time as a modified
-Julian date or in another time scale).
+The \texttt{Table} object now allows \texttt{Quantity}, celestial
+coordinate (\texttt{SkyCoord}), and date/time (\texttt{Time}) objects to
+be used as columns. It also provides a general way for other user-defined
+objects to be used as columns. This makes it possible, for instance, to easily
+represent catalogs of sources or time series as in \astropy, while having both the
+benefits of the \texttt{Table} object (e.g., accessing specific rows/columns
+or groups of them and combining tables) and of, for example,
+the \texttt{SkyCoord} or the \texttt{Time} classes (e.g., converting the
+coordinates to a different frame or accessing the date/time in the desired time scale).
 
@@
 % Tom R. -- unit support
-\subsubsection{Overview}
+
 The \package{astropy.modeling} subpackage provides a framework for representing
@@
 
-In the next major release after version 3.0, scheduled for the summer of
-2018, the focus will be on optimization of the code and improved
+In the next major release after version 3.0, scheduled for
+mid-2018, the focus will be on optimization of the code and improved
 documentation.

### 2017-12-07 main.tex
To make southern hemisphere happy

--- 2017-12-06 main.tex
@@
 
-In the next major release after version 3.0, scheduled for the summer of
-2018, the focus will be on optimization of the code and improved
+In the next major release after version 3.0, scheduled for around
+mid-2018, the focus will be on optimization of the code and improved
 documentation.

### 2017-12-07 main.tex

@@
 
-In the next major release after version 3.0, scheduled for around
-mid-2018, the focus will be on optimization of the code and improved
+In the next major release after version 3.0, scheduled for the summer of
+2018, the focus will be on optimization of the code and improved
 documentation.

### 2017-12-07 main.tex
Refine modeling intro

--- 2017-12-07 main.tex
@@
 are then typically used by smaller groups for more domain-specific purposes.
-Whether for a package meant for wide distribution or for scripts and programs
-for a specific research project, the implementation of astronomical software can
-be eased through the use of a library that provides core functionality that is
-common to many astronomical tasks.
-The users of such software then also benefit from a community and ecosystem
-built around a common foundation.
+Both in packages meant for wider distribution and in scripts specific to
+particular research projects, a library that addresses common astronomical tasks
+simplifies the software development process.
+The users of such a library then also benefit from a community and ecosystem
+built around a shared foundation.
 The \astropy project has grown to become this community for \python astronomy
@@
 writing and sharing of software documentation, and continuous testing and validation of
-software. While the programming language provides support for array representation and
+software. While dedicated libraries provide support for array representation and
 arithmetic \citep[\package{numpy};][]{numpy}, a wide variety of functions for scientific
@@
 databases or statistical inferences. More recently, the development of package managers such as
-Anaconda\footnote{\url{https://anaconda.org/}} have streamlined the installation process for
-most packages, significantly reducing the entry barrier for using many such libraries.
+Anaconda\footnote{\url{https://anaconda.org/}} has significantly streamlined the installation
+process for many libraries, lowering many barriers to entry.
 
@@
 new table with the same rows but all columns. For other situations, more generic
-table concatenation or joining are also possible when two tables share some
+table concatenation or join are also possible when two tables share some
 columns.
@@
 
-The \package{astropy.modeling} subpackage provides a framework for representing
-analytical models and performing model evaluation and parameter fitting. Models and
-fitters are independent of each other: a model can be fit with different
+Tha \package{astropy.modeling} subpackage provides a framework for representing
+analytical models and performing model evaluation and parameter fitting.
+The main motivation for it was creating a framework
+which allows arbitrary combination of models to support the Generalized World
+Coordinate System (GWCS) package.\footnote{\url{https://github.com/spacetelescope/gwcs}}
+The current FITS WCS model lacks the flexibility to represent
+arbitrary distortions and does not meet the needs of many types of current instrumentation.
+The addition of units to modeling made it attractive for representing
+and fitting astrophysical models in various data analysis tools.
+
+Models and fitters are independent of each other: a model can be fit with different
 fitters and new fitters can be added without changing existing models. The
 framework is designed to be flexible and easily extensible. The goal is to have
-a rich set of models but also make it easy to create new ones if necessary. The
-modeling framework is used in a variety of data analysis tools and is the basis
-for the Generalized World Coordinate System (GWCS)
-package.\footnote{\url{https://github.com/spacetelescope/gwcs}}
+a rich set of models, but to also facilitate creating new ones, if necessary.
 
@@
 
-Most models are defined by parameters and maintain an ordered list of parameter names, \texttt{Model.param\_names}.
-A model is constructed by passing in values (scalars or arrays) for its parameters.
-A parameter is a descriptor that provides a proxy for the value and stores additional information -- default value, default unit, and parameter constraints.
-The value and constraints can be updated by assignment.
-Supported parameter constraints include \texttt{fixed}, and \texttt{tied} parameters, and \texttt{bounds} on parameter values.
-Most models have a fixed parameter set but for some (e.g., polynomials), the number of parameters is defined by another argument (e.g., degree-of-freedom in the case of polynomials).
-Parameters support arithmetic operations and are combined with the inputs during evaluation using the \package{numpy} broadcasting rules.
+Models are defined by their parameters and initialized by providing values for them. The
+names of the parameters are stored in a list, \texttt{Model.param\_names}. Parameters are complex objects.
+They store additional information -- default value, default unit, and parameter constraints. Parameter
+values and constraints can be updated by assignment. Supported constraints include \texttt{fixed},
+and \texttt{tied} parameters, and \texttt{bounds} on parameter values. The framework supports also models
+for which the the number of parameters and their names are defined by another argument.
+A typical example is a polynomial model defined by its degree.
 A model is evaluated by calling it as a function.
 
-Models have a \texttt{Model.inverse} property, which returns the analytical inverse, if available, or raises an exception otherwise.
-This is a settable property; i.e.
-a model can be assigned as inverse to another model.
-For example, a polynomial model can be assigned as an inverse to another polynomial model.
+If an analytical inverse of a model exists it is already defined and can be
+accessed  by calling \texttt{Model.inverse}. In addition, \texttt{Model.inverse} can be assigned
+another model which represents a computed inverse.
 

### 2017-12-07 main.tex
Apparently join can be a noun

@@
 are then typically used by smaller groups for more domain-specific purposes.
-Both in packages meant for wider distribution and in scripts specific to
-particular research projects, a library that addresses common astronomical tasks
-simplifies the software development process.
-The users of such a library then also benefit from a community and ecosystem
-built around a shared foundation.
+Whether for a package meant for wide distribution or for scripts and programs
+for a specific research project, the implementation of astronomical software can
+be eased through the use of a library that provides core functionality that is
+common to many astronomical tasks.
+The users of such software then also benefit from a community and ecosystem
+built around a common foundation.
 The \astropy project has grown to become this community for \python astronomy
@@
 writing and sharing of software documentation, and continuous testing and validation of
-software. While dedicated libraries provide support for array representation and
+software. While the programming language provides support for array representation and
 arithmetic \citep[\package{numpy};][]{numpy}, a wide variety of functions for scientific
@@
 databases or statistical inferences. More recently, the development of package managers such as
-Anaconda\footnote{\url{https://anaconda.org/}} has significantly streamlined the installation
-process for many libraries, lowering many barriers to entry.
+Anaconda\footnote{\url{https://anaconda.org/}} have streamlined the installation process for
+most packages, significantly reducing the entry barrier for using many such libraries.
 
@@
 
-Tha \package{astropy.modeling} subpackage provides a framework for representing
-analytical models and performing model evaluation and parameter fitting.
-The main motivation for it was creating a framework
-which allows arbitrary combination of models to support the Generalized World
-Coordinate System (GWCS) package.\footnote{\url{https://github.com/spacetelescope/gwcs}}
-The current FITS WCS model lacks the flexibility to represent
-arbitrary distortions and does not meet the needs of many types of current instrumentation.
-The addition of units to modeling made it attractive for representing
-and fitting astrophysical models in various data analysis tools.
-
-Models and fitters are independent of each other: a model can be fit with different
+The \package{astropy.modeling} subpackage provides a framework for representing
+analytical models and performing model evaluation and parameter fitting. Models and
+fitters are independent of each other: a model can be fit with different
 fitters and new fitters can be added without changing existing models. The
 framework is designed to be flexible and easily extensible. The goal is to have
-a rich set of models, but to also facilitate creating new ones, if necessary.
+a rich set of models but also make it easy to create new ones if necessary. The
+modeling framework is used in a variety of data analysis tools and is the basis
+for the Generalized World Coordinate System (GWCS)
+package.\footnote{\url{https://github.com/spacetelescope/gwcs}}
 
@@
 
-Models are defined by their parameters and initialized by providing values for them. The
-names of the parameters are stored in a list, \texttt{Model.param\_names}. Parameters are complex objects.
-They store additional information -- default value, default unit, and parameter constraints. Parameter
-values and constraints can be updated by assignment. Supported constraints include \texttt{fixed},
-and \texttt{tied} parameters, and \texttt{bounds} on parameter values. The framework supports also models
-for which the the number of parameters and their names are defined by another argument.
-A typical example is a polynomial model defined by its degree.
+Most models are defined by parameters and maintain an ordered list of parameter names, \texttt{Model.param\_names}.
+A model is constructed by passing in values (scalars or arrays) for its parameters.
+A parameter is a descriptor that provides a proxy for the value and stores additional information -- default value, default unit, and parameter constraints.
+The value and constraints can be updated by assignment.
+Supported parameter constraints include \texttt{fixed}, and \texttt{tied} parameters, and \texttt{bounds} on parameter values.
+Most models have a fixed parameter set but for some (e.g., polynomials), the number of parameters is defined by another argument (e.g., degree-of-freedom in the case of polynomials).
+Parameters support arithmetic operations and are combined with the inputs during evaluation using the \package{numpy} broadcasting rules.
 A model is evaluated by calling it as a function.
 
-If an analytical inverse of a model exists it is already defined and can be
-accessed  by calling \texttt{Model.inverse}. In addition, \texttt{Model.inverse} can be assigned
-another model which represents a computed inverse.
+Models have a \texttt{Model.inverse} property, which returns the analytical inverse, if available, or raises an exception otherwise.
+This is a settable property; i.e.
+a model can be assigned as inverse to another model.
+For example, a polynomial model can be assigned as an inverse to another polynomial model.
 

### 2017-12-08 main.tex
intro: word-smithing
Removes the redundancy of "many such" in original phrasing.

--- 2017-12-07 main.tex
@@
 databases or statistical inferences. More recently, the development of package managers such as
-Anaconda\footnote{\url{https://anaconda.org/}} have streamlined the installation process for
-most packages, significantly reducing the entry barrier for using many such libraries.
+Anaconda\footnote{\url{https://anaconda.org/}} has significantly streamlined the installation
+process for many libraries, lowering any barriers to entry.
 

### 2017-12-08 main.tex
intro: remove two non-sequitur sentences
The point of this paragraph is to briefly state the relevant history, and to describe the current state of astropy.

A general statement about aims would belong further up (I'm not sure where, so I did not put it anywhere). The object of "these tools" in original wording was not clear.
Edits for Section 3.6

--- 2017-12-08 main.tex
@@
 different formats using the \package{astropy.table} subpackage.
-For many common cases this simplifies the process of file input and output and
+For many common cases, this simplifies the process of file input and output (I/O) and
 reduces the need to master the separate details of all the I/O packages within
@@
 The \package{astropy.io.ascii} subpackage now includes a significantly faster
-Cython/C engine for reading and writing ASCII files. This is available for the
-most common formats.  On average the new engine is about 4 to 5 times faster
-than the corresponding pure-\python implementation, and is often comparable to
-the speed of the \package{Pandas} \citep{pandas} ASCII file interface.  The
+Cython/C engine for reading and writing ASCII files. This is available for most
+of the common formats.  On average, the new engine is about 4 to 5 times faster
+than the corresponding pure-\python implementation and is often comparable to
+the speed of the \package{pandas} \citep{pandas} ASCII file interface.  The
 fast reader has parallel processing option that allows harnessing multiple
 cores for input parsing to achieve even greater speed gains.  By default,
-\texttt{read()} and \texttt{write()} will attempt to use the fast C engine
+\texttt{read()} and \texttt{write()} will attempt to use the fast Cython/C engine
 when dealing with compatible formats. Certain features of the full read
-/ write interface are not available in the fast version, in which case the
+/ write interface are unavailable in the fast version, in which case the
 pure-\python version will automatically be used.
@@
 The \package{astropy.io.ascii} subpackage now provides the capability
-to read a table within an HTML file or web URL into an astropy
-\texttt{Table} object. Conversely a \texttt{Table} object can now
+to read a table within an HTML file or web URL into an \astropypkg
+\texttt{Table} object. Conversely, a \texttt{Table} object can now
 be written out as an HTML table.
@@
 The \package{astropy.io.fits} subpackage started as a direct port of the
-PyFITS project \citep{PyFITS}. Therefore it is pretty stable, with mostly bug
+PyFITS project \citep{PyFITS}. Therefore, it is pretty stable, with mostly bug
 fixes but also a few new features and performance improvements.  The API
-remains compatible with PyFITS, which is now deprecated in favor of
+remains mostly compatible with PyFITS, which is now deprecated in favor of
 \astropypkg.
@@
 Command-line scripts are now available for printing a summary of the HDUs in
-a FITS file(s) (\texttt{fitsinfo}) and for printing the header information to
+FITS file(s) (\texttt{fitsinfo}) and for printing the header information to
 the screen in a human-readable format (\texttt{fitsheader}).
 
-FITS files are now loaded \emph{lazily} (the default behavior, which can be
-deactivated if needed), where all HDUs are not loaded until they are
-requested. This should provide substantial speedups for situations using the
+FITS files are now loaded \emph{lazily} (this default behavior can be
+deactivated, if needed), where all HDUs are not loaded until
+requested. This should provide substantial speed-ups when using the
 convenience functions (e.g., \texttt{getheader()} or \texttt{getdata()}) to
-get HDU’s that are near the front of a file with many HDUs.
+get an HDU that is near the front of many in a file.
 

### 2017-12-08 main.tex
Breaking very long lines into shorter lines

@@
 In this way, its genesis differs from but builds upon many substantial and
-% * <bsipocz@gmail.com> 2017-11-13T13:13:08.884Z:
-%
-% how do astroy builds upon these? or it's more like builds upon the developer experience?
-%
-%
-% ^.
 former astronomical software development efforts that were commissioned or
@@
 documentation according to the best practices in software development.
-The project makes use of these tools to do so without central institutional
-oversight.
+The project makes use of different tools and web services to reach those
+goals without central institutional oversight.
 The first public release of the \astropypkg package is described in
@@
 For resolving disagreements about the \astropypkg core package or other \astropy-managed code, the coordination committee primarily acts to work toward consensus, or when consensus is difficult to achieve, generally acts as a ``tie-breaker.''
-The committee also oversees affiliated package applications to ensure they are in keeping with \astropy's vision and philosophy, as well as the associated procedures.
+The committee also oversees affiliated package applications to ensure they are
+in keeping with \astropy's vision and
+philosophy,\footnote{\url{http://docs.astropy.org/en/stable/development/vision.html}}
+as well as the associated procedures.
 Additionally, the committee oversees the assignment of roles (primarily driven by already-existing contributions), and increasingly has acted as the ``face'' of the Project, providing contact with organizations like NumFOCUS (the body that holds any potential funding in trust for \astropy) or the American Astronomical Society (AAS).
@@
 \citealt{ape8}).
-This mechanism is called ``Astropy Proposal for Enhancement'' (APE) and are
+This mechanism is called ``Astropy Proposal for Enhancement'' (APE) and is
 modeled after the ``Python Enhancement Proposals'' (PEP) that guide the
@@
 anyone can therefore read the proposed APEs and leave in-line comments.
-When a community consensus emerge, the APEs are accepted and become
+When a community consensus emerges, the APEs are accepted and become
 the basis for future work.
@@
 stability is essential.
-The latest LTS release (v2.0) is also the last one that supports \python 2; It
-will receive bug fixes until the end of 2019 \citep{ape10}.
+The latest LTS release (version 2.0) is also the last one that supports \python
+2; it will receive bug fixes until the end of 2019 \citep{ape10}.
 
@@
 all platforms; the package is constantly tested on different platforms as part
-of our suite of continuous integration tests.
+of a suite of continuous integration tests.
 
@@
 
-The \astropy project, as of the v2.0 release, does not receive any direct financial support for
-the development of \astropypkg.  Development of the software, all supporting materials, and community support are provided
+The \astropy project, as of the version 2.0 release, does not receive any direct
+financial support for the development of \astropypkg.
+Development of the software, all supporting materials, and community support are provided
 by individuals who work on the \astropy project in their own personal
@@
 A list of organizations that have contributed to \astropy in this manner
-can be found in the Acknowledgements.
+can be found in the Acknowledgments.
 
@@
 
-%\subsection{Difficulty of reversing design choices}
-%Deciding if a feature should be included
-%difficulty to decide where general use ends and "handy feature for some" starts, i.e. how to reject PRs or deal with maintenance burden
-
-\section{Astropy Core Package v2.0}
+\section{Astropy Core Package version 2.0}
 \label{sec:core}
@@
 In this section, we highlight new features introduced or substantially improved
-since version v0.2 (previously described in \citealt{astropy}).  The \astropypkg
+since version 0.2 (previously described in \citealt{astropy}).  The \astropypkg
+package
 provides a full log of changes\footnote{\url{https://github.com/astropy/astropy/blob/stable/CHANGES.rst}}
@@
 Beyond what is mentioned below, most subpackages have seen increased performance
-since the release of the v0.2 package.
-
-% \subsection{Analytic Functions}
-% moved to models and depreciated --
-% just here for completeness at the moment
-%\inlinecomment{BMS}{I suggest to order the subsection lexicographically as reading the draft the current order seemed very random (unlike at the docs page where they the grouping logic is obvious)}
-%\inlinecomment{Tom R}{the only issue is if we rely on having e.g. units described first if they are used later}
+since the release of the version 0.2 package.
 
@@
 
-%\inlinecomment{Perry G}{Agreeing with Tom below, I would avoid using terms like subclass, decorators, mixin, namespace, (and perhaps even class, instead using objects consistently; this is no place to be pendantic about the distinction between classes and objects; even to the extent of adding a qualifying sentence somewhere like: "In this paper we will use object when we mean object or classes; in software there are important distinctions between the two terms, but they are not relevant in this paper."), and the like and replace them with more generic descriptions, e.g., "extended", or "tools to make defining functions that can use quantities simple to write" }
-%\inlinecomment{Tom R}{I think saying 'subclass' here is too detailed and is mentioned below in 3.1.1 if needed - 'make it possible to attach units to numpy arrays' or something like that?}
-
 As of \astropypkg version 2.0, units and quantities, prevalent in most of its
@@
 Units are intimately entwined in the definition of astronomical coordinates;
-Thus, nearly all functionality in the \texttt{astropy.coordinates} subpackage
+thus, nearly all functionality in the \texttt{astropy.coordinates} subpackage
 (see \sectionname~\ref{sec:coordinates}) depends on them.
@@
 trigonometric functions expect) before being passed to \texttt{numpy}.
-
-%\subsubsection{Speed improvements}
-
-%\inlinecomment{Tom R}{I wonder if we might just want to mention at the top level that performance has been improved in places? This seems a bit too detailed}
-
-%The \texttt{Quantity} object is now significantly
-        %faster than in early versions of \astropypkg. This is in large part due
-        %to the fact that \texttt{Quantity} subclasses the \texttt{numpy.ndarray}
-        %object, but even relative to more recent versions of \astropypkg,
-        %operations with \texttt{Quantity} objects are generally faster. This is
-        %largely thanks to improvements in the way \texttt{numpy} arrays can be
-        %subclassed.
 
@@
         \texttt{astropy.units} provides a tool called \texttt{quantity\_input()}
-        that can perform this varification automatically to avoid repetitive
+        that can perform this verification automatically to avoid repetitive
         code.
@@
 various astronomical reference systems.
-For example, in the ICRS frame, longitude and latitude are right ascension
+For example, in the ICRS frame, the spherical angles are right ascension
 (\texttt{ra}) and declination (\texttt{dec}), whereas in the Galactic frame, the
@@
     \texttt{astropy.coordinates}.
+    Arrows indicate transformations from one frame to another.
+    Arrows that point back to the same frame indicate self-transformations that
+    involve a change of reference frame parameters (e.g., equinox).
     \label{fig:frame-transform-graph}
@@
     transformations are done numerically instead of analytically.
-    \figurename~\ref{fig:frame-transform-graph} highlights which
-    velocity transformations can be done exactly and which transformations are
-    done using a finite-difference scheme.
     The low-level interface for specifying and transforming velocity data (see
     the next point) is currently experimental.
-    As such, in v2.0, only the \texttt{Frame} classes (and not the
+    As such, in version 2.0, only the \texttt{Frame} classes (and not the
     \texttt{SkyCoord} class) support handling velocities.
-
-%\subsubsection{Derivatives of coordinate representations}
-
-%\inlinecomment{Tom R}{does this really warrant a separate section or is it just a byproduct of the velocity stuff that can be mentioned in 3.3.2?}
-
-    %As mentioned above, the \texttt{Representation} classes act like
-    %three-dimensional vectors.
-    %\texttt{astropy.coordinates} now also supports handling first derivatives of
-    %vectors / representations through the new \texttt{Differential} classes.
-    %The \texttt{Differential} classes are currently used internally within the
-    %\texttt{Frame} classes to store the velocity data.
 
@@
     optional dependency and an internet connection).
-    % hamogu: I think the specific names of functions can be in the docs
-    % and don't need to be repeated here.
-    %The \texttt{get\_body} and \texttt{get\_body\_barycentric} functions provide
-    %the gateway to this functionality, yielding \texttt{SkyCoord} objects given
-    %a specific body and choice of ephemeris source.
 
@@
 astropy  &  kapteyn  & 0.000  & 0.000 & 0.000 & 0.000 \\
+\nodata  &  pytpm    & 0.000  & 0.000 & 0.000 & 0.000 \\
 \nodata  &  palpy    & 0.218  & 0.196 & 0.249 & 0.056 \\
 \nodata  &  pyast    & 0.218  & 0.196 & 0.249 & 0.056 \\
+\nodata  &  pyslalib & 0.218  & 0.196 & 0.249 & 0.056 \\
 \nodata  &  pyephem  & 0.459  & 0.458 & 0.860 & 0.231 \\
+kapteyn  &  pytpm    & 0.000  & 0.000 & 0.000 & 0.000 \\
+\nodata  &  palpy    & 0.218  & 0.196 & 0.249 & 0.056 \\
+\nodata  &  pyast    & 0.218  & 0.196 & 0.249 & 0.056 \\
 \nodata  &  pyslalib & 0.218  & 0.196 & 0.249 & 0.056 \\
-\nodata  &  pytpm    & 0.000  & 0.000 & 0.000 & 0.000 \\
-kapteyn  &  palpy    & 0.218  & 0.196 & 0.249 & 0.056 \\
+\nodata  &  pyephem  & 0.459  & 0.458 & 0.860 & 0.231 \\
+pytpm    &  palpy    & 0.218  & 0.196 & 0.249 & 0.056 \\
 \nodata  &  pyast    & 0.218  & 0.196 & 0.249 & 0.056 \\
+\nodata  &  pyslalib & 0.218  & 0.196 & 0.249 & 0.056 \\
 \nodata  &  pyephem  & 0.459  & 0.458 & 0.860 & 0.231 \\
-\nodata  &  pyslalib & 0.218  & 0.196 & 0.249 & 0.056 \\
-\nodata  &  pytpm    & 0.000  & 0.000 & 0.000 & 0.000 \\
 palpy    &  pyast    & 0.000  & 0.000 & 0.000 & 0.000 \\
+\nodata  &  pyslalib & 0.000  & 0.000 & 0.000 & 0.000 \\
 \nodata  &  pyephem  & 0.563  & 0.570 & 1.012 & 0.253 \\
-\nodata    &  pyslalib & 0.000  & 0.000 & 0.000 & 0.000 \\
-\nodata    &  pytpm    & 0.218  & 0.196 & 0.249 & 0.056 \\
-pyast    &  pyephem  & 0.563  & 0.570 & 1.012 & 0.253 \\
-\nodata    &  pyslalib & 0.000  & 0.000 & 0.000 & 0.000 \\
-\nodata    &  pytpm    & 0.218  & 0.196 & 0.249 & 0.056 \\
-pyephem  &  pyslalib & 0.563  & 0.570 & 1.012 & 0.253 \\
-\nodata  &  pytpm    & 0.459  & 0.458 & 0.860 & 0.231 \\
-pyslalib &  pytpm    & 0.218  & 0.196 & 0.249 & 0.056 \\
+pyast    &  pyslalib & 0.000  & 0.000 & 0.000 & 0.000 \\
+\nodata  &  pyephem  & 0.563  & 0.570 & 1.012 & 0.253 \\
+pyslalib &  pyephem  & 0.563  & 0.570 & 1.012 & 0.253 \\
 \hline
@@
 \end{table}
+
+\begin{figure}
+  \includegraphics[width=\textwidth]{coordinates-benchmark.pdf}
+  \caption{
+    Comparison matrix of the accuracy values shown on
+    table~\ref{tab:coordinate_benchmarks} of the FK4 to Galactic transformation
+    between the different packages. Each comparison block shows four squares
+    representing the median, mean, maximum and standard deviation going from
+    left to right and bottom to top.
+    \label{fig:coordinate_benchmarks}
+  }
+\end{figure}
 
@@
 and manipulating heterogeneous data.
-%\inlinecomment{APW:}{Need more introduction to the table subpackage!}
 The package was described in detail in \cite{astropy}.
@@
 
-%\inlinecomment{Perry G}{Some mention that some of these are inspired by Pandas?}
-
 \subsubsection{Support for grouped table operations}
 
-A table can contain data that naturally form groups; For example, it may
+A table can contain data that naturally form groups; for example, it may
 contain multiple observations of a few sources at different points in time
@@
 
-\subsubsection{Using astropy objects in tables}
+\subsubsection{Using Astropy objects in tables}
 
@@
 objects to be used as columns. This makes it possible, for instance, to easily
-represent catalogs of sources or time series as in \astropy, while having both the
+represent catalogs of sources or time series in \astropy, while having both the
 benefits of the \texttt{Table} object (e.g., accessing specific rows/columns
@@
 
-%\inlinecomment{SCO}{Table and FITS tables}
-
-%\subsubsection{Unified file read/write interface}
-
-%\inlinecomment{Check when it was added (0.3?). Overview of the supported formats (ASCII,FITS, votable, HTML, JSViewer/Datatables).}
-
-% We summarize key new features or updates to \package{astropy.io} below,
-% organized by sub-subpackage.
-
-% \inlinecomment{Tom R}{is a sub-subpackage a thing, or is it just 'subpackage' all the way down?}
-
 \subsubsection{ASCII}
-% \subsubsection{Enhanced CSV format}
 
@@
 both human-readable and compatible with most simple CSV readers.
-
-% \subsubsection{\texttt{.ascii}: fast readers and writers}
 
@@
 
-% \subsubsection{\texttt{.ascii}: HTML tables}
-
 The \package{astropy.io.ascii} subpackage now provides the capability
 to read a table within an HTML file or web URL into an \astropypkg
-\texttt{Table} object. Conversely, a \texttt{Table} object can now
+\texttt{Table} object. A \texttt{Table} object can now also
 be written out as an HTML table.
@@
 convenience functions (e.g., \texttt{getheader()} or \texttt{getdata()}) to
-get an HDU that is near the front of many in a file.
-
-% \inlinecomment{Tom R}{too detailed? I don't think we need to mention every single performance enhancement, right?}
-
-% \subsubsection{\texttt{.misc}: YAML serialization}
-
-% The new \package{astropy.io.misc.yaml} module allows converting astropy
-% objects into a standard YAML format.  This can be used beyond
-% \texttt{astropy.io.misc.yaml}: for example, to serialize the metadata of
-% tables before saving to other formats like HDF5.
-
-%\inlinecomment{BMS}{Maybe move the command line tools into a separate subsection to highlight them (even though we mostly only have fits related scripts)?
-They are supposed to be used more frequently by individual users.}
-%\inlinecomment{hamogu}{MY feeling is that this section is too detailed already. If I had written it, I would not have mentioned the scripts at all.}
+get an HDU that is near the beginning in a file with many HDUs.
 
@@
 The \package{astropy.modeling} subpackage provides a framework for representing
-analytical models and performing model evaluation and parameter fitting. Models and
-fitters are independent of each other: a model can be fit with different
+analytical models and performing model evaluation and parameter fitting.
+The main motivation for this functionality was to create a framework that
+allows arbitrary combination of models to support the Generalized World
+Coordinate System (GWCS) package.\footnote{\url{https://github.com/spacetelescope/gwcs}}
+The current FITS WCS specification lacks the flexibility to represent
+arbitrary distortions and does not meet the needs of many types of current instrumentation.
+The fact that the \astropypkg modeling framework now supports propagating
+units also makes it a useful tool for representing and fitting astrophysical
+models within data analysis tools.
+
+Models and fitters are independent of each other: a model can be fit with different
 fitters and new fitters can be added without changing existing models. The
 framework is designed to be flexible and easily extensible. The goal is to have
-a rich set of models but also make it easy to create new ones if necessary. The
-modeling framework is used in a variety of data analysis tools and is the basis
-for the Generalized World Coordinate System (GWCS)
-package.\footnote{\url{https://github.com/spacetelescope/gwcs}}
-
-% hamogu: I comented this out because we don't have prrof that it's
-% ``uniquly'' useful. THe developers of e.g. ISIS, Sherpa, for even IRAF
-% will probably disagree.
-%The recently-added support for \package{astropy.units} in models and fitters
-%make it a uniquely powerful package for working with astrophysical models.
+a rich set of models, but to also facilitate creating new ones, if necessary.
 
 \subsubsection{Single Model Definition and Evaluation}
-
-%\inlinecomment{hamogu: I tihnk this is too techical. I know it's a complex subpackage but I had trouble understanding this section even as a regular user.}
 
@@
 and \texttt{tied} parameters, and \texttt{bounds} on parameter values. The framework supports also models
-for which the the number of parameters and their names are defined by another argument.
+for which the number of parameters and their names are defined by another argument.
 A typical example is a polynomial model defined by its degree.
@@
 
-If an analytical inverse of a model exists it is already defined and can be
+If an analytical inverse of a model exists it can be
 accessed  by calling \texttt{Model.inverse}. In addition, \texttt{Model.inverse} can be assigned
@@
 The goal is to make it easy to extend the fitting framework to create new fitters.
-The optimizers available in \astropypkg version 2.0 are Levenberg--Marquardt, Simplex, SLSQP, and LinearLSQFitter (which is based on \texttt{numpy.linalg} that provides exact solution for linear models).
-
-%\inlinecomment{APW}{Add citations for the different optimizaton algorithms in paragraph above?}
+The optimizers available in \astropypkg version 2.0 are Levenberg--Marquardt, Simplex, SLSQP, and LinearLSQFitter (which is based on \texttt{numpy.linalg} that provides exact solutions for linear models).
 
@@
 \package{SABA}\footnote{\url{https://github.com/astropy/saba}}, which is a bridge between
-Sherpa\footnote{\url{http://cxc.cfa.harvard.edu/contrib/sherpa/}}
+Sherpa \citep{sherpa},
 and \package{astropy.modeling}, to bring the Sherpa fitters into \astropypkg.
@@
 
-The \package{astropy.convolution} subpackage implements `normalized convolution' \citep[e.g.,][]{Knutsson1993}, which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.
+The \package{astropy.convolution} subpackage implements
+``normalized convolution'' \citep[e.g.,][]{Knutsson1993}, which is an image
+reconstruction technique in which missing data are ignored during the
+convolution and replaced with values interpolated using the kernel.
 An example of this is given in \figurename~\ref{fig:convolution-example}.
-In versions $\leq 1.3$, the direct convolution and Fast Fourier Transform (FFT) convolution approaches were not consistent, with FFT convolution implementing normalized convolution and direct convolution implementing a different approach.
-As of version 2.0, the two methods are consistent and include a suite of consistency checks.
+In versions $\leq 1.3$, the direct convolution and Fast Fourier Transform (FFT)
+convolution approaches were not consistent, with FFT convolution implementing
+normalized convolution and direct convolution implementing a different approach.
+As of version 2.0, the two methods are consistent and include a suite of
+consistency checks.
 
 \begin{figure}
-\includegraphics[width=\textwidth]{convolution_example.png}
+\includegraphics[width=\textwidth]{convolution_example}
 \caption{%
     An example showing different modes of convolution available in the \python
-    ecosystem.  The red x's mark pixels that are set to NaN in the original data
+    ecosystem.  The red x's mark pixels that are set to \texttt{NaN} in the original data
     (a).  If the data are convolved with a Gaussian kernel on a $9\times 9$ grid using
-    scipy's direct convolution (b), any pixel within range of the original NaN
-    pixels is also set to NaN.  Panel (c) shows what happens if the NaNs are set
-    to zero first: the originally NaN regions are depressed relative to their
+    \package{scipy}'s direct convolution (b), any pixel within range of the original \texttt{NaN}
+    pixels is also set to \texttt{NaN}.  Panel (c) shows what happens if the \texttt{NaN}s are set
+    to zero first: the originally \texttt{NaN} regions are depressed relative to their
     surroundings.  Finally, panel (d) shows \astropypkg's convolution behavior,
@@
 
-The \package{astropy.visualization} subpackage provides functionality that can be helpful when visualizing data.
-This includes a framework for plotting astronomical images with coordinates with \package{matplotlib} (previously the standalone \package{wcsaxes} package), functionality related to image normalization (including both scaling and stretching), smart histogram plotting, RGB color image creation from separate images, and custom plotting styles for \package{matplotlib}.
+The \package{astropy.visualization} subpackage provides functionality that can
+be helpful when visualizing data. This includes a framework for plotting
+astronomical images with coordinates with \package{matplotlib} (previously the
+standalone \package{wcsaxes} package), functionality related to image
+normalization (including both scaling and stretching), smart histogram
+plotting, RGB color image creation from separate images, and custom plotting
+styles for \package{matplotlib}.
 
@@
 
-\package{astropy.visualization} provides a framework for transforming values in images (and more generally any arrays), typically for the purpose of visualization.
-Two main types of transformations are normalization and stretching of image values.
-
-Normalization transforms the images values to the range $[0,1]$ using lower and upper limits $(v_{\rm min}, v_{\rm max})$
+\package{astropy.visualization} provides a framework for transforming values in
+images (and more generally any arrays), typically for the purpose of
+visualization. Two main types of transformations are normalization and
+stretching of image values.
+
+Normalization transforms the images values to the range $[0,1]$ using lower and
+upper limits $(v_{\rm min}, v_{\rm max})$
 \begin{equation}
@@
 
-Stretching transforms the image values in the range $[0,1]$ again to the range $[0,1]$ using a linear or non-linear function
+Stretching transforms the image values in the range $[0,1]$ again to the range
+$[0,1]$ using a linear or non-linear function
 \begin{equation}
@@
 
-Several classes are provided for automatically determining intervals (e.g., using image percentiles) and for normalizing values in this interval to the $[0,1]$ range.
-
-\package{matplotlib} allows a custom normalization and stretch to be used when displaying data by passing a normalization object.
-The \package{astropy.visualization} package also provides a normalization class that wraps the interval and stretching objects into a normalization object that \package{matplotlib} understands.
+Several classes are provided for automatically determining intervals
+(e.g., using image percentiles) and for normalizing values in this interval to
+the $[0,1]$ range.
+
+\package{matplotlib} allows a custom normalization and stretch to be used when
+displaying data by passing a normalization object.
+The \package{astropy.visualization} package also provides a normalization class
+that wraps the interval and stretching objects into a normalization object that
+\package{matplotlib} understands.
 
@@
 
-Astronomers dealing with observational imaging commonly need to make figures with images that include the correct coordinates and optionally display a coordinate grid.
-The challenge, however, is that the conceptual coordinate axes (such as longitude/latitude) need not be lined up with the pixel axes of the image.
-The \package{astropy.visualization.wcsaxes} subpackage implements a generalized way of making figures from an image array and a world coordinate system (WCS) object that provides the transformation between pixel and `world' coordinates.
-
-World coordinates can be, for example, right ascension and declination, but can also include, for example, velocity, wavelength, frequency, or time.
-The main features from this subpackage include the ability to control which axes to show which coordinate on (for example showing longitude ticks on the top and bottom axes and latitude on the left and right axes), controlling the spacing of the ticks either by specifying the positions to use or providing a tick spacing or an average number of ticks that should be present on each axis, setting the format for the tick labels to ones commonly used by astronomers, controlling the visibility of the grid/graticule, and overlaying ticks, labels, and/or grid lines from different coordinate systems.
-In addition, it is possible to pass data with more than two dimensions and slice on-the-fly.
-Finally, it is possible to define non-rectangular frames, such as, for example, Aitoff projections.
-
-This subpackage differs from \package{APLpy} \citep{aplpy} in that the latter focuses on providing a very high-level interface to plotting that requires very few lines of code to get a good result, whereas \package{wcsaxes} defines an interface that is much closer to that of \package{matplotlib} \citep{matplotlib}.
+Astronomers dealing with observational imaging commonly need to make figures
+with images that include the correct coordinates and optionally display a
+coordinate grid. The challenge, however, is that the conceptual coordinate axes
+(such as longitude/latitude) need not be lined up with the pixel axes of the
+image. The \package{astropy.visualization.wcsaxes} subpackage implements a
+generalized way of making figures from an image array and a world coordinate
+system (WCS) object that provides the transformation between pixel and
+``world'' coordinates.
+
+World coordinates can be, for example, right ascension and declination, but can
+also include, for example, velocity, wavelength, frequency, or time.
+The main features from this subpackage include the ability to control which
+axes to show which coordinate on (for example showing longitude ticks on the
+top and bottom axes and latitude on the left and right axes), controlling the
+spacing of the ticks either by specifying the positions to use or providing a
+tick spacing or an average number of ticks that should be present on each axis,
+setting the format for the tick labels to ones commonly used by astronomers,
+controlling the visibility of the grid/graticule, and overlaying ticks, labels,
+and/or grid lines from different coordinate systems. In addition, it is
+possible to pass data with more than two dimensions and slice on-the-fly.
+Finally, it is possible to define non-rectangular frames, such as, for example,
+Aitoff projections.
+
+This subpackage differs from \package{APLpy} \citep{aplpy} in that the latter
+focuses on providing a very high-level interface to plotting that requires very
+few lines of code to get a good result, whereas \package{wcsaxes} defines an
+interface that is much closer to that of \package{matplotlib} \citep{matplotlib}.
 This enables significantly more advanced visualizations.
 
-An example of a visualization made with \package{wcsaxes} is shown in \figurename~\ref{fig:wcsaxes} -- this example illustrates the ability to overlay multiple coordinate systems and customize which ticks/labels are shown on which axes around the image.
-This also uses the image stretching functionality from \sectionname~\ref{sec:stretch} to show the image in a square root stretch (automatically updating the tick positions in the colorbar).
+An example of a visualization made with \package{wcsaxes} is shown in
+\figurename~\ref{fig:wcsaxes} -- this example illustrates the ability to
+overlay multiple coordinate systems and customize which ticks/labels are shown
+on which axes around the image. This also uses the image stretching
+functionality from \sectionname~\ref{sec:stretch} to show the image in a square
+root stretch (automatically updating the tick positions in the colorbar).
 
@@
 \caption{%
-An example of figure made using the \package{astropy.visualization.wcsaxes} subpackage, using \textit{Spitzer}/IRAC 8.0~$\mu$m data from the Cygnus-X \textit{Spitzer} Legacy survey \citep{cygnusx}.
+An example of figure made using the \package{astropy.visualization.wcsaxes}
+subpackage, using \textit{Spitzer}/IRAC 8.0~$\mu$m data from the Cygnus-X
+\textit{Spitzer} Legacy survey \citep{cygnusx}.
 \label{fig:wcsaxes}
@@
 
-\cite{Lupton2004} describe an ``optimal'' algorithm for producing red-green-blue (RGB) composite images from three separate high-dynamic range arrays.
-The \package{astropy.visualization} subpackage provides a convenience function to create such a color image.
-It also includes an associated set of classes to provide alternate scalings.
-This functionality was contributed by developers from the Large Synoptic Survey Telescope (LSST) and serves as an example of contribution to \astropy from a more traditional engineering organization \citep{Jennes2016}.
-
-The Sloan Digital Sky Survey (SDSS) SkyServer color images were made using a variation on this technique.
-As an example, in \figurename~\ref{fig:ngc6977} we show an RGB color image of the Hickson 88 group, centered near NGC~6977.
-This image was generated from SDSS images using the \package{astropy.visualization} tools.
+\cite{Lupton2004} describe an ``optimal'' algorithm for producing
+red-green-blue (RGB) composite images from three separate high-dynamic range
+arrays. The \package{astropy.visualization} subpackage provides a convenience
+function to create such a color image.  It also includes an associated set of
+classes to provide alternate scalings.
+This functionality was contributed by developers from the Large Synoptic Survey
+Telescope (LSST) and serves as an example of contribution to \astropy from a
+more traditional engineering organization \citep{Jennes2016}.
+
+The Sloan Digital Sky Survey (SDSS) SkyServer color images were made using a
+variation on this technique.  As an example, in \figurename~\ref{fig:ngc6977}
+we show an RGB color image of the Hickson 88 group, centered near NGC~6977.
+This image was generated from SDSS images using the
+\package{astropy.visualization} tools.
 
@@
 
-The \package{cosmology} package contains classes for representing different cosmologies and functions for calculating commonly used quantities such as look-back time and distance.
-The package was described in detail in \cite{astropy}.
-The default cosmology in \astropy version 2.0 is given by the values in \cite{2016A&A...594A..13P}.
+The \package{cosmology} package contains classes for representing different
+cosmologies and functions for calculating commonly used quantities such as
+look-back time and distance.   The package was described in detail in
+\cite{astropy}.  The default cosmology in \astropypkg version 2.0 is given by
+the values in \cite{2016A&A...594A..13P}.
 
@@
 
-% The current review process for contributions to the \package{astropy.stats} package includes review of the code, documentation, testing, and scientific merit of the inclusion.
-When necessary, scientific reviewers outside of the maintainers will be sought for their input on new pull requests.
-
-In this section, we describe these tools, including robust statistical estimators, circular statistics, periodograms, spatial statistics, and histogram binning.
-
 % Steve C.: overview, circular stats,
@@
 Importantly, the implementations make use of several fast and scalable computational approaches \citep[e.g.,][]{Press89, Palmer09}, and so can be applied to much larger datasets than Lomb-Scargle algorithms available in, e.g., \package{scipy.stats} (\citealt{scipy}).
-Much of the Lomb-Scargle code in \astropy has been adapted from previously-published open-source code \citep{astroML, VanderPlas2015}.
+Much of the Lomb-Scargle code in \astropypkg has been adapted from previously-published open-source code \citep{astroML, VanderPlas2015}.
 
@@
     {\it center:} a histogram with the number of equal-width bins determined automatically using \package{numpy}'s {\tt bins='auto'}.
-    {\it right:} a histogram created with \package{astropy}, with irregularly-spaced bins computed via the Bayesian Blocks algorithm.
+    {\it right:} a histogram created with \astropypkg, with irregularly-spaced bins computed via the Bayesian Blocks algorithm.
     Compared to regularly-spaced bins, the irregular bin widths give a more accurate visual representation of features in the dataset at various scales.
@@
 \label{sec:infrastructure}
-%\inlinecomment{BMS}{should we describe astropy-helpers even though it's future is unsure?}
 % Text also edited by Adrian PW
@@
 
-%\inlinecomment{TPR}{We should put the releases of sphinx-automodapi on Zenodo and cite this}
-
-% \section{State of the Ecosystem}
-% Commenting out unless a clear statement is added
-
 \section{The future of the Astropy project}
@@
 
-%\inlinecomment{BMS}{should we mention the refactored infra here?  e.g. pytest-astropy and sphinx-astropy?}
-
-\subsection{Future versions of the \astropypkg core and affiliated packages}
+\subsection{Future versions of the Astropy core and affiliated packages}
 
@@
 We encourage any users who wish to see specific material to either contribute or
-comment on these efforts via the \astropy mailing list or \astropy-tutorials
+comment on these efforts via the \astropy mailing list or \package{astropy/astropy-tutorials}
 \github repository.\footnote{\url{https://github.com/astropy/astropy-tutorials}}
@@
 to help improve their skills.
-As a community, we follow an explicit code of conduct \citep{ape8} and treat all
-contributors and users with respect, provide a harassment-free environment, and
-encourage and welcome new contributions from all.
+As a community, \astropy follows an explicit code of conduct \citep{ape8} and treats all
+contributors and users with respect, provides a harassment-free environment, and
+encourages and welcomes new contributions from all.
 Thus, while the \astropy project provides and develops software and tools
@@
 
-\acknowledgments
-
-Who to thank?  numfocus, GSOC, Python Software Foundation
-
-We thank the many web services that make developing and maintaining this package
-feasible, such as GitHub, Travis CI, Appveyor, CircleCI, and Read the Docs.
+\acknowledgments The \astropy community is supported by and makes use
+of a number of organizations and services outside the traditional
+academic community. We thank Google for financing and organizing the
+Google Summer of Code (GSoC) program, that has funded severals
+students per year to work on \astropy related projects over the
+summer. These students often turn into long-term contributors. We also
+thank NumFOCUS and the Python Software Foundation for financial
+support. Within the academic community, we thank
+institutions that make it possible that astronomers and other developers on
+their staff can contribute their time to the development of
+\astropy projects.
+
+Furthermore, the \astropy packages would not exist
+in their current form without a number of web services for code
+hosting, continuous integration, and documentation; in particular,
+\astropy heavily relies on GitHub, Travis CI, Appveyor, CircleCI, and
+Read the Docs.
+
+\astropypkg interfaces with the SIMBAD database,
+operated at CDS, Strasbourg, France. It also makes use of the ERFA library \citep{erfa},
+which in turn derives from the IAU SOFA Collection\footnote{\url{http://www.iausofa.org}} developed by the International Astronomical Union Standards of Fundamental Astronomy \citep{sofa}.
 
@@
           \package{Cython} (\citealt{cython}),
+          \package{SOFA} (\citealt{sofa}),
+          \package{ERFA} (\citealt{erfa})
           }
@@
 \appendix
+
 \section{List of Affiliated Packages}
-
-%\inlinecomment{SMC}{Can a brief description of each code be added?}
 

### 2017-12-08 main.tex
Edits from Sections 3.8 to 6, inclusive

@@
 % draft by Adrian PW and Erik T.
-Code is contributed to the \astropypkg core package or modified through ``pull
+code is contributed to the \astropypkg core package or modified through ``pull
 requests'' (via \github) that often contain several \texttt{git} commits.
@@
 all platforms; the package is constantly tested on different platforms as part
-of a suite of continuous integration tests.
+of a suite of continuous integration (CI) tests.
 
@@
 financial support for the development of \astropypkg.
-Development of the software, all supporting materials, and community support are provided
-by individuals who work on the \astropy project in their own personal
-time, by individuals or groups contributing to \astropy as
-part of a research project, or contributions from institutions that allocate
-people to work on \astropy.
+Development of the software, all supporting materials, and community support are
+provided by individuals who work on the \astropy project in their own personal
+time, by individuals or groups contributing to \astropy as part of a research
+project, or contributions from institutions that allocate people to work on
+\astropy.
 A list of organizations that have contributed to \astropy in this manner
@@
 
-\section{Astropy Core Package version 2.0}
+%\subsection{Difficulty of reversing design choices}
+%Deciding if a feature should be included
+%difficulty to decide where general use ends and "handy feature for some" starts, i.e. how to reject PRs or deal with maintenance burden
+
+\section{Astropy Core Package Version 2.0}
 \label{sec:core}
@@
 The \texttt{NDDataBase} class provides the abstract interface for gridded data
-with attributes for accessing metadata, the world-coordinate system (WCS),
+with attributes for accessing metadata, the world coordinate system (WCS),
 uncertainty arrays matched to the shape of the data, and other traits.
@@
 The \package{astropy.convolution} subpackage implements
-``normalized convolution'' \citep[e.g.,][]{Knutsson1993}, which is an image
-reconstruction technique in which missing data are ignored during the
-convolution and replaced with values interpolated using the kernel.
+``normalized convolution'' \citep[e.g.,][]{Knutsson1993} that is an image
+reconstruction technique, in which missing data are ignored during the
+convolution and replaced with values interpolated using the kernel;
 An example of this is given in \figurename~\ref{fig:convolution-example}.
-In versions $\leq 1.3$, the direct convolution and Fast Fourier Transform (FFT)
-convolution approaches were not consistent, with FFT convolution implementing
-normalized convolution and direct convolution implementing a different approach.
-As of version 2.0, the two methods are consistent and include a suite of
+In \astropypkg versions $\leq 1.3$, the direct convolution and Fast Fourier Transform (FFT)
+convolution approaches were inconsistent, with the latter implementing
+normalized convolution, while the former a different approach.
+As of version 2.0, the two methods now agree and include a suite of
 consistency checks.
@@
     An example showing different modes of convolution available in the \python
-    ecosystem.  The red x's mark pixels that are set to \texttt{NaN} in the original data
-    (a).  If the data are convolved with a Gaussian kernel on a $9\times 9$ grid using
+    ecosystem.  The red x's mark pixels that are set to \texttt{NaN} in the
+    original data (a).  If the data are convolved with a Gaussian kernel on a
+    $9\times 9$ grid using
     \package{scipy}'s direct convolution (b), any pixel within range of the original \texttt{NaN}
-    pixels is also set to \texttt{NaN}.  Panel (c) shows what happens if the \texttt{NaN}s are set
-    to zero first: the originally \texttt{NaN} regions are depressed relative to their
-    surroundings.  Finally, panel (d) shows \astropypkg's convolution behavior,
-    where the missing pixels are replaced with values interpolated from their
-    surroundings using the convolution kernel.
+    pixels is also set to \texttt{NaN}.  Panel (c) shows what happens if the
+    \texttt{NaN}s are set to zero first: the originally \texttt{NaN} regions are
+    depressed relative to their surroundings.  Finally, panel (d) shows
+    \astropypkg's convolution behavior, where the missing pixels are replaced
+    with values interpolated from their surroundings using the convolution
+    kernel.
     \label{fig:convolution-example}
@@
 The \package{astropy.visualization} subpackage provides functionality that can
-be helpful when visualizing data. This includes a framework for plotting
-astronomical images with coordinates with \package{matplotlib} (previously the
-standalone \package{wcsaxes} package), functionality related to image
+be helpful when visualizing data. This includes a framework (previously the
+standalone \package{wcsaxes} package) for plotting
+astronomical images with coordinates with \package{matplotlib}, functionality related to image
 normalization (including both scaling and stretching), smart histogram
-plotting, RGB color image creation from separate images, and custom plotting
-styles for \package{matplotlib}.
+plotting, red-green-blue (RGB) color image creation from separate images,
+and custom plotting styles for \package{matplotlib}.
 
@@
 
-Normalization transforms the images values to the range $[0,1]$ using lower and
-upper limits $(v_{\rm min}, v_{\rm max})$
+Normalization transforms the image values to the range $[0,1]$ using lower and
+upper limits $(v_{\rm min}, v_{\rm max})$,
 \begin{equation}
-y = \frac{x - v_{\rm min}}{v_{\rm max} - v_{\rm min}}
+y = \frac{x - v_{\rm min}}{v_{\rm max} - v_{\rm min}} \quad ,
 \end{equation}
@@
 Stretching transforms the image values in the range $[0,1]$ again to the range
-$[0,1]$ using a linear or non-linear function
+$[0,1]$ using a linear or non-linear function,
 \begin{equation}
@@
 \package{matplotlib} allows a custom normalization and stretch to be used when
-displaying data by passing a normalization object.
+displaying data by passing in a normalization object.
 The \package{astropy.visualization} package also provides a normalization class
-that wraps the interval and stretching objects into a normalization object that
+that wraps the interval and stretches objects into a normalization object that
 \package{matplotlib} understands.
@@
 system (WCS) object that provides the transformation between pixel and
-``world'' coordinates.
+world coordinates.
 
@@
 The main features from this subpackage include the ability to control which
-axes to show which coordinate on (for example showing longitude ticks on the
+axes to show which coordinate on (e.g., showing longitude ticks on the
 top and bottom axes and latitude on the left and right axes), controlling the
@@
 possible to pass data with more than two dimensions and slice on-the-fly.
-Finally, it is possible to define non-rectangular frames, such as, for example,
-Aitoff projections.
-
-This subpackage differs from \package{APLpy} \citep{aplpy} in that the latter
+Last but not least, it is also able to define non-rectangular frames, such as,
+for example, Aitoff projections.
+
+This subpackage differs from \package{APLpy} \citep{aplpy}, in that the latter
 focuses on providing a very high-level interface to plotting that requires very
@@
 An example of a visualization made with \package{wcsaxes} is shown in
-\figurename~\ref{fig:wcsaxes} -- this example illustrates the ability to
+\figurename~\ref{fig:wcsaxes}; This example illustrates the ability to
 overlay multiple coordinate systems and customize which ticks/labels are shown
 on which axes around the image. This also uses the image stretching
-functionality from \sectionname~\ref{sec:stretch} to show the image in a square
-root stretch (automatically updating the tick positions in the colorbar).
+functionality from \sectionname~\ref{sec:stretch} to show the image in a
+square-root stretch (automatically updating the tick positions in the colorbar).
 
@@
 \package{astropy.visualization} also provides a histogram function, which is a
-generalization of \texttt{matplotlib}’s histogram function, to allow for more
+generalization of \texttt{matplotlib}’s histogram function, to allow for a more
 flexible specification of histogram bins.  The function provides several methods
@@
 parameter, which allows specification of one of four different methods for
-automatic bin selection: `blocks', `knuth', `scott', or `freedman'.
+automatic bin selection: ``blocks'', ``knuth'', ``scott'', or ``freedman''.
 
@@
 \cite{Lupton2004} describe an ``optimal'' algorithm for producing
-red-green-blue (RGB) composite images from three separate high-dynamic range
+RGB composite images from three separate high-dynamic range
 arrays. The \package{astropy.visualization} subpackage provides a convenience
@@
 The Sloan Digital Sky Survey (SDSS) SkyServer color images were made using a
-variation on this technique.  As an example, in \figurename~\ref{fig:ngc6977}
+variation on this technique.  As an example, in \figurename~\ref{fig:ngc6977},
 we show an RGB color image of the Hickson 88 group, centered near NGC~6977.
@@
 The \package{astropy.stats} package provides statistical tools that
-are useful for or specific to astronomy and are not found in or extend
-the available functionality of other \python statistics packages such
+are useful for astronomy and are either not found in or extend
+the available functionality of other \python statistics packages, such
 as \package{scipy} \citep{scipy} or \package{statsmodels}
@@
 a range of functionality used by many different disciplines
-in astronomy. It is not a complete set of statistic tools, but rather
+in astronomy. It is not a complete set of statistical tools, but rather
 a still growing collection of useful features.
@@
 
-Robust statistics provide reliable estimates of basic statistics for complex distributions that largely mitigate the effects of outliers.
-\package{astropy.stats} includes several robust statistical functions that are commonly used in astronomy, such as sigma clipping methods for rejecting outliers, median absolute deviation functions, and biweight estimators, which have been used to calculate the velocity dispersion of galaxy clusters \citep{Beers1990}.
+Robust statistics provide reliable estimates of basic statistics for complex
+distributions that largely mitigate the effects of outliers.
+\package{astropy.stats} includes several robust statistical functions that are
+commonly used in astronomy, such as sigma clipping methods for rejecting
+outliers, median absolute deviation functions, and biweight estimators,
+which have been used to calculate the velocity dispersion of galaxy clusters
+\citep{Beers1990}.
 
@@
 
-Astronomers often need to compute statistics of quantities evaluated on a circle, such as sky direction or polarization angle.
+Astronomers often need to compute statistics of quantities evaluated on a
+circle, such as sky direction or polarization angle.
 A set of circular statistical estimators based on \citet{JammalamadakaSengupta}
@@
 radians) and \texttt{Quantity} objects.  In addition, the subpackage includes
-tests for Rayleigh Test, vtest, and a function to compute the maximum likelihood
-estimator for the parameters of the von Mises distribution.
+tests for Rayleigh Test, \texttt{vtest}, and a function to compute the maximum
+likelihood estimator for the parameters of the von Mises distribution.
 
@@
 
-Periodic analysis of unevenly-spaced time series is common across many subfields of astronomy.
-The \package{astropy.stats} package now includes several efficient implementations of the Lomb-Scargle periodogram \citep{Lomb76, Scargle82} and several generalizations, including floating mean models \citep{Zechmeister09}, truncated Fourier models \citep{Bretthorst2003}, and appropriate handling of heteroscedastic uncertainties.
-Importantly, the implementations make use of several fast and scalable computational approaches \citep[e.g.,][]{Press89, Palmer09}, and so can be applied to much larger datasets than Lomb-Scargle algorithms available in, e.g., \package{scipy.stats} (\citealt{scipy}).
-Much of the Lomb-Scargle code in \astropypkg has been adapted from previously-published open-source code \citep{astroML, VanderPlas2015}.
+Periodic analysis of unevenly-spaced time series is common across many
+sub-fields of astronomy. The \package{astropy.stats} package now includes
+several efficient implementations of the Lomb-Scargle periodogram
+\citep{Lomb76, Scargle82} and several generalizations, including floating mean
+models \citep{Zechmeister09}, truncated Fourier models \citep{Bretthorst2003},
+and appropriate handling of heteroscedastic uncertainties.
+Importantly, the implementations make use of several fast and scalable
+computational approaches \citep[e.g.,][]{Press89, Palmer09}, and thus can be
+applied to much larger datasets than Lomb-Scargle algorithms available in,
+e.g., \package{scipy.stats} (\citealt{scipy}). Much of the Lomb-Scargle code
+in \astropypkg has been adapted from previously-published open-source code
+\citep{astroML, VanderPlas2015}.
 
 \subsubsection{Bayesian Blocks and Histogram Binning}
-\astropypkg also includes an implementation of {\it Bayesian Blocks} \citep{Scargle2013}, an algorithm for analysis of break-points in non-periodic astronomical time-series.
-One interesting application of Bayesian Blocks is its use in determining optimal histogram binnings, and in particular binnings with unequal bin sizes.
-This code was adapted, with several improvements, from the \package{astroML} package \citep{astroML}.
-An example of a histogram fit using the Bayesian blocks algorithm is shown in the right panel of \figurename~\ref{fig:bayes-blocks-hist}.
+\package{astropy.stats} also includes an implementation of
+{\it Bayesian Blocks} \citep{Scargle2013}, an algorithm for analysis of
+break-points in non-periodic astronomical time-series. One interesting
+application of Bayesian Blocks is its use in determining optimal histogram
+binnings, particularly binnings with unequal bin sizes.
+This code was adapted, with several improvements, from the \package{astroML}
+package \citep{astroML}. An example of a histogram fit using the Bayesian
+Blocks algorithm is shown in the right panel of
+\figurename~\ref{fig:bayes-blocks-hist}.
 
@@
 also maintains and distributes several general-purpose infrastructure packages
-that help with the maintenance and upkeep of the \astropypkg core package and
+that assist the maintenance and upkeep of the \astropypkg core package and
 other affiliated packages.
-The following sections describes the most widely-used infrastructure packages
+The following sections describe the most widely-used infrastructure packages
 developed by the \astropy Project.
@@
 \astropy also provides a set of scripts for setting up and configuring
-continuous integration (CI) services as a \github repository,
+CI services as a \github repository,
 \package{astropy/ci-helpers}.\footnote{\url{https://github.com/astropy/ci-helpers}}
-These tools aim to empower package maintainers to control their testing set up
-and installation process for various continuous integration services through a
+These tools aim to empower package maintainers to control their testing setup
+and installation process for various CI services through a
 set of environment variables.
@@
 
-The documentation for many \python packages, the core \astropypkg package, and
-for all packages in the \astropy ecosystem is written using the
+The documentation for many \python packages, including
+all the packages in the \astropy ecosystem, is written using the
 \package{Sphinx} documentation build system.
-\package{Sphinx} makes it possible to write documentation using plain text files
-that follow a markup language called ``reStructuredText,'' which are then
-transformed into HTML or \LaTeX{} documentation during the documentation build
-process.
-For the \astropy project, we have developed a few \package{Sphinx} extensions
+\package{Sphinx} supports writing documentation using plain text files
+that follow a markup language called \texttt{reStructuredText} (RST).
+These files are then transformed into HTML, PDF, or \LaTeX{} documents
+during the documentation build process.
+For the \astropy project, we have developed several \package{Sphinx} extensions
 that facilitate automatically generating API documentation for large projects,
@@
 \package{sphinx-automodapi}\footnote{\url{http://sphinx-automodapi.readthedocs.io}},
-which makes it easy with a single reStructuredText command to generate a set of
-documentation pages listing all of the available classes, functions, and
+which provides a convenient single RST command to generate a set of
+documentation pages, listing all of the available classes, functions, and
 attributes in a given \python module.
@@
 On top of planned changes and additions to the core package, we also plan to
-overhaul the \astropy educational and learning materials, and further refactor
-and generalize the infrastructure utilities developed for the core package for
-the benefit of the community.
+overhaul the \astropy educational/learning materials and further
+generalize the infrastructure utilities originally developed for the core
+package for the benefit of the community.
 
@@
 One of the most significant changes coming in this next major release will be
-removing support for \python 2 \citep{ape10}: future versions of \astropypkg
-will only support \python 3.5 and higher.
-Removing \python 2 support will allow the use of new, \python 3-only features,
-will simplify the code base, and reduce the testing overhead for the package.
+removing the support for \python 2 \citep{ape10}: future versions of \astropypkg
+will only support \python 3.5 or higher.
+Removing \python 2 support will allow the use of new \python 3-only features,
+simplify the code base, and reduce the testing overhead for the package.
 \astropypkg version 3.0 is currently scheduled for January 2018.
@@
 In the next major release after version 3.0, scheduled for
-mid-2018, the focus will be on optimization of the code and improved
-documentation.
-To prepare for this release, we are preparing software for testing, evaluating,
-and monitoring the performance of the code.
-Less functionality may be introduced in this release while the focus will be
-primarily on improved performance.
+mid-2018, the focus will be on algorithm optimization and
+documentation improvement.
+To prepare for this release, we are subjecting the core package to testing,
+evaluation, and performance monitoring.
+As a result, less new functionality may be introduced as a trade-off for
+better performance.
 
@@
 While these may not be integrated into the \astropypkg core package, these
-projects provide code that is useful to the astronomical community and meet the
+projects provide code that are useful to the astronomical community and meet the
 testing and documentation standards of \astropy.
-Some of these new efforts includes an initiative to develop tools for
+Some of these new efforts include an initiative to develop tools for
 spectroscopy \citep[\package{specutils}, \package{specreduc}, \package{specviz}]
-{ape13}, integration of LSST software, and packages to support HEALPIX
+{ape13}, integration of LSST software, and support for HEALPIX
 projection. %\citep{astropy-healpix}
@@
 
-The \astropypkg core package documentation contains narrative descriptions of
-the package functionality along with detailed usage notes for functions,
+The \astropypkg core package's documentation contains narrative descriptions of
+the package's functionality, along with detailed usage notes for functions,
 classes, and modules.
-While useful as a reference and for more advanced \python users, it is not the
-right entry-point for all users or learning environments.
+While useful as a reference for more experienced \python users, it is not the
+proper entry-point for other users or learning environments.
 In the near future, we will launch a new resource for learning to use both the
 \astropypkg core package and the many packages in the broader \astropy
-ecosystem, under the name `\emph{Learn Astropy}.'
+ecosystem, under the name \emph{Learn Astropy}.
 
@@
     \item[Documentation] The \astropypkg and affiliated package documentation
-        contain the complete description of a package with all requisite
+        contains the complete description of a package with all requisite
         details, including usage, dependencies, and examples.
@@
         Tutorials are more extended and comprehensive than examples, may contain
-        exercises for the users, and are generally geared towards workshops or
-        teaching.
+        exercises for the users, and are generally geared towards pedagogical
+        activities.
         Several tutorials already
@@
         actively expanded.
-    \item[Guides] These are long-form narrative, comprehensive,
-        conceptually-focused documents (roughly one book chapter in length)
+    \item[Guides] These are long-form narrative, comprehensive, and
+        conceptually-focused documents (roughly one book chapter in length),
         providing stand-alone introductions to core packages in addition to the
         underlying astronomical concepts.
-        These are less specific and more conceptual than tutorials.
+        These are less specific and more conceptual than tutorials;
         For example, ``using \astropypkg and \package{ccdproc} to reduce imaging
@@
 The development of the \astropypkg package and cultivation of the \astropy
-ecosystem is still maintaining significant growth while improving stability,
+ecosystem are still maintaining significant growth while improving in stability,
 breadth, and reliability.
@@
 reached stability with a rich set of features that help astronomers worldwide to
-perform many daily tasks such as planning observations, analyzing data or
+perform many daily tasks, such as planning observations, analyzing data or
 simulation results, and writing publications.
-The strong emphasis that the \astropy project puts on reliability and code
-correctness helps users to trust the calculations performed with \astropypkg and
+The strong emphasis that the \astropy project puts on reliability and high coding
+standards helps users to trust the calculations performed with \astropypkg and
 to publish reproducible results.
-At the same time, the \astropy ecosystem and core package are growing: new
-functionality is still being contributed, and new affiliated packages are being
+At the same time, the \astropy ecosystem and core package are both growing: new
+functionality is still being contributed and new affiliated packages are being
 developed to support more specialized needs.
@@
 computer science and software development, despite the fact that a major
-fraction of nearly every astronomer's workload today is related to software use
+fraction of many astronomers' workload today is related to software use
 and development.
 The \astropypkg package leads by example, showing all interested astronomers how
-modern tools like \texttt{git} version control or continuous integration can
+modern tools like \texttt{git} version control or CI testing can
 increase the quality, accessibility, and discoverability of astronomical

### 2017-12-08 main.tex
Ops typo

@@
 % draft by Adrian PW and Erik T.
-code is contributed to the \astropypkg core package or modified through ``pull
+Code is contributed to the \astropypkg core package or modified through ``pull
 requests'' (via \github) that often contain several \texttt{git} commits.

### 2017-12-08 main.tex
Final edit to my edits

@@
 image. The \package{astropy.visualization.wcsaxes} subpackage implements a
-generalized way of making figures from an image array and a world coordinate
-system (WCS) object that provides the transformation between pixel and
-world coordinates.
+generalized way of making figures from an image array and a WCS object
+that provides the transformation between pixel and world coordinates.
 
@@
 While these may not be integrated into the \astropypkg core package, these
-projects provide code that are useful to the astronomical community and meet the
+projects provide code that is useful to the astronomical community and meet the
 testing and documentation standards of \astropy.

### 2017-12-08 main.tex

@@
 In this way, its genesis differs from but builds upon many substantial and
+% * <bsipocz@gmail.com> 2017-11-13T13:13:08.884Z:
+%
+% how do astroy builds upon these? or it's more like builds upon the developer experience?
+%
+%
+% ^.
 former astronomical software development efforts that were commissioned or
@@
 documentation according to the best practices in software development.
-The project makes use of different tools and web services to reach those
-goals without central institutional oversight.
+The project makes use of these tools to do so without central institutional
+oversight.
 The first public release of the \astropypkg package is described in
@@
 For resolving disagreements about the \astropypkg core package or other \astropy-managed code, the coordination committee primarily acts to work toward consensus, or when consensus is difficult to achieve, generally acts as a ``tie-breaker.''
-The committee also oversees affiliated package applications to ensure they are
-in keeping with \astropy's vision and
-philosophy,\footnote{\url{http://docs.astropy.org/en/stable/development/vision.html}}
-as well as the associated procedures.
+The committee also oversees affiliated package applications to ensure they are in keeping with \astropy's vision and philosophy, as well as the associated procedures.
 Additionally, the committee oversees the assignment of roles (primarily driven by already-existing contributions), and increasingly has acted as the ``face'' of the Project, providing contact with organizations like NumFOCUS (the body that holds any potential funding in trust for \astropy) or the American Astronomical Society (AAS).
@@
 \citealt{ape8}).
-This mechanism is called ``Astropy Proposal for Enhancement'' (APE) and is
+This mechanism is called ``Astropy Proposal for Enhancement'' (APE) and are
 modeled after the ``Python Enhancement Proposals'' (PEP) that guide the
@@
 anyone can therefore read the proposed APEs and leave in-line comments.
-When a community consensus emerges, the APEs are accepted and become
+When a community consensus emerge, the APEs are accepted and become
 the basis for future work.
@@
 stability is essential.
-The latest LTS release (version 2.0) is also the last one that supports \python
-2; it will receive bug fixes until the end of 2019 \citep{ape10}.
+The latest LTS release (v2.0) is also the last one that supports \python 2; It
+will receive bug fixes until the end of 2019 \citep{ape10}.
 
@@
 all platforms; the package is constantly tested on different platforms as part
-of a suite of continuous integration (CI) tests.
+of our suite of continuous integration tests.
 
@@
 
-The \astropy project, as of the version 2.0 release, does not receive any direct
-financial support for the development of \astropypkg.
-Development of the software, all supporting materials, and community support are
-provided by individuals who work on the \astropy project in their own personal
-time, by individuals or groups contributing to \astropy as part of a research
-project, or contributions from institutions that allocate people to work on
-\astropy.
+The \astropy project, as of the v2.0 release, does not receive any direct financial support for
+the development of \astropypkg.  Development of the software, all supporting materials, and community support are provided
+by individuals who work on the \astropy project in their own personal
+time, by individuals or groups contributing to \astropy as
+part of a research project, or contributions from institutions that allocate
+people to work on \astropy.
 A list of organizations that have contributed to \astropy in this manner
-can be found in the Acknowledgments.
+can be found in the Acknowledgements.
 
@@
 
-\section{Astropy Core Package Version 2.0}
+\section{Astropy Core Package v2.0}
 \label{sec:core}
@@
 In this section, we highlight new features introduced or substantially improved
-since version 0.2 (previously described in \citealt{astropy}).  The \astropypkg
-package
+since version v0.2 (previously described in \citealt{astropy}).  The \astropypkg
 provides a full log of changes\footnote{\url{https://github.com/astropy/astropy/blob/stable/CHANGES.rst}}
@@
 Beyond what is mentioned below, most subpackages have seen increased performance
-since the release of the version 0.2 package.
+since the release of the v0.2 package.
+
+% \subsection{Analytic Functions}
+% moved to models and depreciated --
+% just here for completeness at the moment
+%\inlinecomment{BMS}{I suggest to order the subsection lexicographically as reading the draft the current order seemed very random (unlike at the docs page where they the grouping logic is obvious)}
+%\inlinecomment{Tom R}{the only issue is if we rely on having e.g. units described first if they are used later}
 
@@
 
+%\inlinecomment{Perry G}{Agreeing with Tom below, I would avoid using terms like subclass, decorators, mixin, namespace, (and perhaps even class, instead using objects consistently; this is no place to be pendantic about the distinction between classes and objects; even to the extent of adding a qualifying sentence somewhere like: "In this paper we will use object when we mean object or classes; in software there are important distinctions between the two terms, but they are not relevant in this paper."), and the like and replace them with more generic descriptions, e.g., "extended", or "tools to make defining functions that can use quantities simple to write" }
+%\inlinecomment{Tom R}{I think saying 'subclass' here is too detailed and is mentioned below in 3.1.1 if needed - 'make it possible to attach units to numpy arrays' or something like that?}
+
 As of \astropypkg version 2.0, units and quantities, prevalent in most of its
@@
 Units are intimately entwined in the definition of astronomical coordinates;
-thus, nearly all functionality in the \texttt{astropy.coordinates} subpackage
+Thus, nearly all functionality in the \texttt{astropy.coordinates} subpackage
 (see \sectionname~\ref{sec:coordinates}) depends on them.
@@
 trigonometric functions expect) before being passed to \texttt{numpy}.
+
+%\subsubsection{Speed improvements}
+
+%\inlinecomment{Tom R}{I wonder if we might just want to mention at the top level that performance has been improved in places? This seems a bit too detailed}
+
+%The \texttt{Quantity} object is now significantly
+        %faster than in early versions of \astropypkg. This is in large part due
+        %to the fact that \texttt{Quantity} subclasses the \texttt{numpy.ndarray}
+        %object, but even relative to more recent versions of \astropypkg,
+        %operations with \texttt{Quantity} objects are generally faster. This is
+        %largely thanks to improvements in the way \texttt{numpy} arrays can be
+        %subclassed.
 
@@
         \texttt{astropy.units} provides a tool called \texttt{quantity\_input()}
-        that can perform this verification automatically to avoid repetitive
+        that can perform this varification automatically to avoid repetitive
         code.
@@
 various astronomical reference systems.
-For example, in the ICRS frame, the spherical angles are right ascension
+For example, in the ICRS frame, longitude and latitude are right ascension
 (\texttt{ra}) and declination (\texttt{dec}), whereas in the Galactic frame, the
@@
     \texttt{astropy.coordinates}.
-    Arrows indicate transformations from one frame to another.
-    Arrows that point back to the same frame indicate self-transformations that
-    involve a change of reference frame parameters (e.g., equinox).
     \label{fig:frame-transform-graph}
@@
     transformations are done numerically instead of analytically.
+    \figurename~\ref{fig:frame-transform-graph} highlights which
+    velocity transformations can be done exactly and which transformations are
+    done using a finite-difference scheme.
     The low-level interface for specifying and transforming velocity data (see
     the next point) is currently experimental.
-    As such, in version 2.0, only the \texttt{Frame} classes (and not the
+    As such, in v2.0, only the \texttt{Frame} classes (and not the
     \texttt{SkyCoord} class) support handling velocities.
+
+%\subsubsection{Derivatives of coordinate representations}
+
+%\inlinecomment{Tom R}{does this really warrant a separate section or is it just a byproduct of the velocity stuff that can be mentioned in 3.3.2?}
+
+    %As mentioned above, the \texttt{Representation} classes act like
+    %three-dimensional vectors.
+    %\texttt{astropy.coordinates} now also supports handling first derivatives of
+    %vectors / representations through the new \texttt{Differential} classes.
+    %The \texttt{Differential} classes are currently used internally within the
+    %\texttt{Frame} classes to store the velocity data.
 
@@
     optional dependency and an internet connection).
+    % hamogu: I think the specific names of functions can be in the docs
+    % and don't need to be repeated here.
+    %The \texttt{get\_body} and \texttt{get\_body\_barycentric} functions provide
+    %the gateway to this functionality, yielding \texttt{SkyCoord} objects given
+    %a specific body and choice of ephemeris source.
 
@@
 astropy  &  kapteyn  & 0.000  & 0.000 & 0.000 & 0.000 \\
-\nodata  &  pytpm    & 0.000  & 0.000 & 0.000 & 0.000 \\
 \nodata  &  palpy    & 0.218  & 0.196 & 0.249 & 0.056 \\
 \nodata  &  pyast    & 0.218  & 0.196 & 0.249 & 0.056 \\
+\nodata  &  pyephem  & 0.459  & 0.458 & 0.860 & 0.231 \\
 \nodata  &  pyslalib & 0.218  & 0.196 & 0.249 & 0.056 \\
+\nodata  &  pytpm    & 0.000  & 0.000 & 0.000 & 0.000 \\
+kapteyn  &  palpy    & 0.218  & 0.196 & 0.249 & 0.056 \\
+\nodata  &  pyast    & 0.218  & 0.196 & 0.249 & 0.056 \\
 \nodata  &  pyephem  & 0.459  & 0.458 & 0.860 & 0.231 \\
-kapteyn  &  pytpm    & 0.000  & 0.000 & 0.000 & 0.000 \\
-\nodata  &  palpy    & 0.218  & 0.196 & 0.249 & 0.056 \\
-\nodata  &  pyast    & 0.218  & 0.196 & 0.249 & 0.056 \\
 \nodata  &  pyslalib & 0.218  & 0.196 & 0.249 & 0.056 \\
-\nodata  &  pyephem  & 0.459  & 0.458 & 0.860 & 0.231 \\
-pytpm    &  palpy    & 0.218  & 0.196 & 0.249 & 0.056 \\
-\nodata  &  pyast    & 0.218  & 0.196 & 0.249 & 0.056 \\
-\nodata  &  pyslalib & 0.218  & 0.196 & 0.249 & 0.056 \\
-\nodata  &  pyephem  & 0.459  & 0.458 & 0.860 & 0.231 \\
+\nodata  &  pytpm    & 0.000  & 0.000 & 0.000 & 0.000 \\
 palpy    &  pyast    & 0.000  & 0.000 & 0.000 & 0.000 \\
+\nodata    &  pyephem  & 0.563  & 0.570 & 1.012 & 0.253 \\
 \nodata    &  pyslalib & 0.000  & 0.000 & 0.000 & 0.000 \\
-\nodata  &  pyephem  & 0.563  & 0.570 & 1.012 & 0.253 \\
-pyast    &  pyslalib & 0.000  & 0.000 & 0.000 & 0.000 \\
-\nodata  &  pyephem  & 0.563  & 0.570 & 1.012 & 0.253 \\
-pyslalib &  pyephem  & 0.563  & 0.570 & 1.012 & 0.253 \\
+\nodata    &  pytpm    & 0.218  & 0.196 & 0.249 & 0.056 \\
+pyast    &  pyephem  & 0.563  & 0.570 & 1.012 & 0.253 \\
+\nodata    &  pyslalib & 0.000  & 0.000 & 0.000 & 0.000 \\
+\nodata    &  pytpm    & 0.218  & 0.196 & 0.249 & 0.056 \\
+pyephem  &  pyslalib & 0.563  & 0.570 & 1.012 & 0.253 \\
+\nodata  &  pytpm    & 0.459  & 0.458 & 0.860 & 0.231 \\
+pyslalib &  pytpm    & 0.218  & 0.196 & 0.249 & 0.056 \\
 \hline
@@
 \end{table}
-
-\begin{figure}
-  \includegraphics[width=\textwidth]{coordinates-benchmark.pdf}
-  \caption{
-    Comparison matrix of the accuracy values shown on
-    table~\ref{tab:coordinate_benchmarks} of the FK4 to Galactic transformation
-    between the different packages. Each comparison block shows four squares
-    representing the median, mean, maximum and standard deviation going from
-    left to right and bottom to top.
-    \label{fig:coordinate_benchmarks}
-  }
-\end{figure}
 
@@
 The \texttt{NDDataBase} class provides the abstract interface for gridded data
-with attributes for accessing metadata, the world coordinate system (WCS),
+with attributes for accessing metadata, the world-coordinate system (WCS),
 uncertainty arrays matched to the shape of the data, and other traits.
@@
 and manipulating heterogeneous data.
+%\inlinecomment{APW:}{Need more introduction to the table subpackage!}
 The package was described in detail in \cite{astropy}.
@@
 
+%\inlinecomment{Perry G}{Some mention that some of these are inspired by Pandas?}
+
 \subsubsection{Support for grouped table operations}
 
-A table can contain data that naturally form groups; for example, it may
+A table can contain data that naturally form groups; For example, it may
 contain multiple observations of a few sources at different points in time
@@
 
-\subsubsection{Using Astropy objects in tables}
+\subsubsection{Using astropy objects in tables}
 
@@
 objects to be used as columns. This makes it possible, for instance, to easily
-represent catalogs of sources or time series in \astropy, while having both the
+represent catalogs of sources or time series as in \astropy, while having both the
 benefits of the \texttt{Table} object (e.g., accessing specific rows/columns
@@
 different formats using the \package{astropy.table} subpackage.
-For many common cases, this simplifies the process of file input and output (I/O) and
+For many common cases this simplifies the process of file input and output and
 reduces the need to master the separate details of all the I/O packages within
@@
 
+%\inlinecomment{SCO}{Table and FITS tables}
+
+%\subsubsection{Unified file read/write interface}
+
+%\inlinecomment{Check when it was added (0.3?). Overview of the supported formats (ASCII,FITS, votable, HTML, JSViewer/Datatables).}
+
+% We summarize key new features or updates to \package{astropy.io} below,
+% organized by sub-subpackage.
+
+% \inlinecomment{Tom R}{is a sub-subpackage a thing, or is it just 'subpackage' all the way down?}
+
 \subsubsection{ASCII}
+% \subsubsection{Enhanced CSV format}
 
@@
 
+% \subsubsection{\texttt{.ascii}: fast readers and writers}
+
 The \package{astropy.io.ascii} subpackage now includes a significantly faster
-Cython/C engine for reading and writing ASCII files. This is available for most
-of the common formats.  On average, the new engine is about 4 to 5 times faster
-than the corresponding pure-\python implementation and is often comparable to
-the speed of the \package{pandas} \citep{pandas} ASCII file interface.  The
+Cython/C engine for reading and writing ASCII files. This is available for the
+most common formats.  On average the new engine is about 4 to 5 times faster
+than the corresponding pure-\python implementation, and is often comparable to
+the speed of the \package{Pandas} \citep{pandas} ASCII file interface.  The
 fast reader has parallel processing option that allows harnessing multiple
 cores for input parsing to achieve even greater speed gains.  By default,
-\texttt{read()} and \texttt{write()} will attempt to use the fast Cython/C engine
+\texttt{read()} and \texttt{write()} will attempt to use the fast C engine
 when dealing with compatible formats. Certain features of the full read
-/ write interface are unavailable in the fast version, in which case the
+/ write interface are not available in the fast version, in which case the
 pure-\python version will automatically be used.
 
+% \subsubsection{\texttt{.ascii}: HTML tables}
+
 The \package{astropy.io.ascii} subpackage now provides the capability
-to read a table within an HTML file or web URL into an \astropypkg
-\texttt{Table} object. A \texttt{Table} object can now also
+to read a table within an HTML file or web URL into an astropy
+\texttt{Table} object. Conversely a \texttt{Table} object can now
 be written out as an HTML table.
@@
 The \package{astropy.io.fits} subpackage started as a direct port of the
-PyFITS project \citep{PyFITS}. Therefore, it is pretty stable, with mostly bug
+PyFITS project \citep{PyFITS}. Therefore it is pretty stable, with mostly bug
 fixes but also a few new features and performance improvements.  The API
-remains mostly compatible with PyFITS, which is now deprecated in favor of
+remains compatible with PyFITS, which is now deprecated in favor of
 \astropypkg.
@@
 Command-line scripts are now available for printing a summary of the HDUs in
-FITS file(s) (\texttt{fitsinfo}) and for printing the header information to
+a FITS file(s) (\texttt{fitsinfo}) and for printing the header information to
 the screen in a human-readable format (\texttt{fitsheader}).
 
-FITS files are now loaded \emph{lazily} (this default behavior can be
-deactivated, if needed), where all HDUs are not loaded until
-requested. This should provide substantial speed-ups when using the
+FITS files are now loaded \emph{lazily} (the default behavior, which can be
+deactivated if needed), where all HDUs are not loaded until they are
+requested. This should provide substantial speedups for situations using the
 convenience functions (e.g., \texttt{getheader()} or \texttt{getdata()}) to
-get an HDU that is near the beginning in a file with many HDUs.
+get HDU’s that are near the front of a file with many HDUs.
+
+% \inlinecomment{Tom R}{too detailed? I don't think we need to mention every single performance enhancement, right?}
+
+% \subsubsection{\texttt{.misc}: YAML serialization}
+
+% The new \package{astropy.io.misc.yaml} module allows converting astropy
+% objects into a standard YAML format.  This can be used beyond
+% \texttt{astropy.io.misc.yaml}: for example, to serialize the metadata of
+% tables before saving to other formats like HDF5.
+
+%\inlinecomment{BMS}{Maybe move the command line tools into a separate subsection to highlight them (even though we mostly only have fits related scripts)?
+They are supposed to be used more frequently by individual users.}
+%\inlinecomment{hamogu}{MY feeling is that this section is too detailed already. If I had written it, I would not have mentioned the scripts at all.}
 
@@
 The \package{astropy.modeling} subpackage provides a framework for representing
-analytical models and performing model evaluation and parameter fitting.
-The main motivation for this functionality was to create a framework that
-allows arbitrary combination of models to support the Generalized World
-Coordinate System (GWCS) package.\footnote{\url{https://github.com/spacetelescope/gwcs}}
-The current FITS WCS specification lacks the flexibility to represent
-arbitrary distortions and does not meet the needs of many types of current instrumentation.
-The fact that the \astropypkg modeling framework now supports propagating
-units also makes it a useful tool for representing and fitting astrophysical
-models within data analysis tools.
-
-Models and fitters are independent of each other: a model can be fit with different
+analytical models and performing model evaluation and parameter fitting. Models and
+fitters are independent of each other: a model can be fit with different
 fitters and new fitters can be added without changing existing models. The
 framework is designed to be flexible and easily extensible. The goal is to have
-a rich set of models, but to also facilitate creating new ones, if necessary.
+a rich set of models but also make it easy to create new ones if necessary. The
+modeling framework is used in a variety of data analysis tools and is the basis
+for the Generalized World Coordinate System (GWCS)
+package.\footnote{\url{https://github.com/spacetelescope/gwcs}}
+
+% hamogu: I comented this out because we don't have prrof that it's
+% ``uniquly'' useful. THe developers of e.g. ISIS, Sherpa, for even IRAF
+% will probably disagree.
+%The recently-added support for \package{astropy.units} in models and fitters
+%make it a uniquely powerful package for working with astrophysical models.
 
@@
 
-Models are defined by their parameters and initialized by providing values for them. The
-names of the parameters are stored in a list, \texttt{Model.param\_names}. Parameters are complex objects.
-They store additional information -- default value, default unit, and parameter constraints. Parameter
-values and constraints can be updated by assignment. Supported constraints include \texttt{fixed},
-and \texttt{tied} parameters, and \texttt{bounds} on parameter values. The framework supports also models
-for which the number of parameters and their names are defined by another argument.
-A typical example is a polynomial model defined by its degree.
+%\inlinecomment{hamogu: I tihnk this is too techical. I know it's a complex subpackage but I had trouble understanding this section even as a regular user.}
+
+Most models are defined by parameters and maintain an ordered list of parameter names, \texttt{Model.param\_names}.
+A model is constructed by passing in values (scalars or arrays) for its parameters.
+A parameter is a descriptor that provides a proxy for the value and stores additional information -- default value, default unit, and parameter constraints.
+The value and constraints can be updated by assignment.
+Supported parameter constraints include \texttt{fixed}, and \texttt{tied} parameters, and \texttt{bounds} on parameter values.
+Most models have a fixed parameter set but for some (e.g., polynomials), the number of parameters is defined by another argument (e.g., degree-of-freedom in the case of polynomials).
+Parameters support arithmetic operations and are combined with the inputs during evaluation using the \package{numpy} broadcasting rules.
 A model is evaluated by calling it as a function.
 
-If an analytical inverse of a model exists it can be
-accessed  by calling \texttt{Model.inverse}. In addition, \texttt{Model.inverse} can be assigned
-another model which represents a computed inverse.
+Models have a \texttt{Model.inverse} property, which returns the analytical inverse, if available, or raises an exception otherwise.
+This is a settable property; i.e.
+a model can be assigned as inverse to another model.
+For example, a polynomial model can be assigned as an inverse to another polynomial model.
 
@@
 The goal is to make it easy to extend the fitting framework to create new fitters.
-The optimizers available in \astropypkg version 2.0 are Levenberg--Marquardt, Simplex, SLSQP, and LinearLSQFitter (which is based on \texttt{numpy.linalg} that provides exact solutions for linear models).
+The optimizers available in \astropypkg version 2.0 are Levenberg--Marquardt, Simplex, SLSQP, and LinearLSQFitter (which is based on \texttt{numpy.linalg} that provides exact solution for linear models).
+
+%\inlinecomment{APW}{Add citations for the different optimizaton algorithms in paragraph above?}
 
@@
 \package{SABA}\footnote{\url{https://github.com/astropy/saba}}, which is a bridge between
-Sherpa \citep{sherpa},
+Sherpa\footnote{\url{http://cxc.cfa.harvard.edu/contrib/sherpa/}}
 and \package{astropy.modeling}, to bring the Sherpa fitters into \astropypkg.
@@
 
-The \package{astropy.convolution} subpackage implements
-``normalized convolution'' \citep[e.g.,][]{Knutsson1993} that is an image
-reconstruction technique, in which missing data are ignored during the
-convolution and replaced with values interpolated using the kernel;
+The \package{astropy.convolution} subpackage implements `normalized convolution' \citep[e.g.,][]{Knutsson1993}, which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.
 An example of this is given in \figurename~\ref{fig:convolution-example}.
-In \astropypkg versions $\leq 1.3$, the direct convolution and Fast Fourier Transform (FFT)
-convolution approaches were inconsistent, with the latter implementing
-normalized convolution, while the former a different approach.
-As of version 2.0, the two methods now agree and include a suite of
-consistency checks.
+In versions $\leq 1.3$, the direct convolution and Fast Fourier Transform (FFT) convolution approaches were not consistent, with FFT convolution implementing normalized convolution and direct convolution implementing a different approach.
+As of version 2.0, the two methods are consistent and include a suite of consistency checks.
 
 \begin{figure}
-\includegraphics[width=\textwidth]{convolution_example}
+\includegraphics[width=\textwidth]{convolution_example.png}
 \caption{%
     An example showing different modes of convolution available in the \python
-    ecosystem.  The red x's mark pixels that are set to \texttt{NaN} in the
-    original data (a).  If the data are convolved with a Gaussian kernel on a
-    $9\times 9$ grid using
-    \package{scipy}'s direct convolution (b), any pixel within range of the original \texttt{NaN}
-    pixels is also set to \texttt{NaN}.  Panel (c) shows what happens if the
-    \texttt{NaN}s are set to zero first: the originally \texttt{NaN} regions are
-    depressed relative to their surroundings.  Finally, panel (d) shows
-    \astropypkg's convolution behavior, where the missing pixels are replaced
-    with values interpolated from their surroundings using the convolution
-    kernel.
+    ecosystem.  The red x's mark pixels that are set to NaN in the original data
+    (a).  If the data are convolved with a Gaussian kernel on a $9\times 9$ grid using
+    scipy's direct convolution (b), any pixel within range of the original NaN
+    pixels is also set to NaN.  Panel (c) shows what happens if the NaNs are set
+    to zero first: the originally NaN regions are depressed relative to their
+    surroundings.  Finally, panel (d) shows \astropypkg's convolution behavior,
+    where the missing pixels are replaced with values interpolated from their
+    surroundings using the convolution kernel.
     \label{fig:convolution-example}
@@
 
-The \package{astropy.visualization} subpackage provides functionality that can
-be helpful when visualizing data. This includes a framework (previously the
-standalone \package{wcsaxes} package) for plotting
-astronomical images with coordinates with \package{matplotlib}, functionality related to image
-normalization (including both scaling and stretching), smart histogram
-plotting, red-green-blue (RGB) color image creation from separate images,
-and custom plotting styles for \package{matplotlib}.
+The \package{astropy.visualization} subpackage provides functionality that can be helpful when visualizing data.
+This includes a framework for plotting astronomical images with coordinates with \package{matplotlib} (previously the standalone \package{wcsaxes} package), functionality related to image normalization (including both scaling and stretching), smart histogram plotting, RGB color image creation from separate images, and custom plotting styles for \package{matplotlib}.
 
@@
 
-\package{astropy.visualization} provides a framework for transforming values in
-images (and more generally any arrays), typically for the purpose of
-visualization. Two main types of transformations are normalization and
-stretching of image values.
-
-Normalization transforms the image values to the range $[0,1]$ using lower and
-upper limits $(v_{\rm min}, v_{\rm max})$,
+\package{astropy.visualization} provides a framework for transforming values in images (and more generally any arrays), typically for the purpose of visualization.
+Two main types of transformations are normalization and stretching of image values.
+
+Normalization transforms the images values to the range $[0,1]$ using lower and upper limits $(v_{\rm min}, v_{\rm max})$
 \begin{equation}
-y = \frac{x - v_{\rm min}}{v_{\rm max} - v_{\rm min}} \quad ,
+y = \frac{x - v_{\rm min}}{v_{\rm max} - v_{\rm min}}
 \end{equation}
@@
 
-Stretching transforms the image values in the range $[0,1]$ again to the range
-$[0,1]$ using a linear or non-linear function,
+Stretching transforms the image values in the range $[0,1]$ again to the range $[0,1]$ using a linear or non-linear function
 \begin{equation}
@@
 
-Several classes are provided for automatically determining intervals
-(e.g., using image percentiles) and for normalizing values in this interval to
-the $[0,1]$ range.
-
-\package{matplotlib} allows a custom normalization and stretch to be used when
-displaying data by passing in a normalization object.
-The \package{astropy.visualization} package also provides a normalization class
-that wraps the interval and stretches objects into a normalization object that
-\package{matplotlib} understands.
+Several classes are provided for automatically determining intervals (e.g., using image percentiles) and for normalizing values in this interval to the $[0,1]$ range.
+
+\package{matplotlib} allows a custom normalization and stretch to be used when displaying data by passing a normalization object.
+The \package{astropy.visualization} package also provides a normalization class that wraps the interval and stretching objects into a normalization object that \package{matplotlib} understands.
 
@@
 
-Astronomers dealing with observational imaging commonly need to make figures
-with images that include the correct coordinates and optionally display a
-coordinate grid. The challenge, however, is that the conceptual coordinate axes
-(such as longitude/latitude) need not be lined up with the pixel axes of the
-image. The \package{astropy.visualization.wcsaxes} subpackage implements a
-generalized way of making figures from an image array and a WCS object
-that provides the transformation between pixel and world coordinates.
-
-World coordinates can be, for example, right ascension and declination, but can
-also include, for example, velocity, wavelength, frequency, or time.
-The main features from this subpackage include the ability to control which
-axes to show which coordinate on (e.g., showing longitude ticks on the
-top and bottom axes and latitude on the left and right axes), controlling the
-spacing of the ticks either by specifying the positions to use or providing a
-tick spacing or an average number of ticks that should be present on each axis,
-setting the format for the tick labels to ones commonly used by astronomers,
-controlling the visibility of the grid/graticule, and overlaying ticks, labels,
-and/or grid lines from different coordinate systems. In addition, it is
-possible to pass data with more than two dimensions and slice on-the-fly.
-Last but not least, it is also able to define non-rectangular frames, such as,
-for example, Aitoff projections.
-
-This subpackage differs from \package{APLpy} \citep{aplpy}, in that the latter
-focuses on providing a very high-level interface to plotting that requires very
-few lines of code to get a good result, whereas \package{wcsaxes} defines an
-interface that is much closer to that of \package{matplotlib} \citep{matplotlib}.
+Astronomers dealing with observational imaging commonly need to make figures with images that include the correct coordinates and optionally display a coordinate grid.
+The challenge, however, is that the conceptual coordinate axes (such as longitude/latitude) need not be lined up with the pixel axes of the image.
+The \package{astropy.visualization.wcsaxes} subpackage implements a generalized way of making figures from an image array and a world coordinate system (WCS) object that provides the transformation between pixel and `world' coordinates.
+
+World coordinates can be, for example, right ascension and declination, but can also include, for example, velocity, wavelength, frequency, or time.
+The main features from this subpackage include the ability to control which axes to show which coordinate on (for example showing longitude ticks on the top and bottom axes and latitude on the left and right axes), controlling the spacing of the ticks either by specifying the positions to use or providing a tick spacing or an average number of ticks that should be present on each axis, setting the format for the tick labels to ones commonly used by astronomers, controlling the visibility of the grid/graticule, and overlaying ticks, labels, and/or grid lines from different coordinate systems.
+In addition, it is possible to pass data with more than two dimensions and slice on-the-fly.
+Finally, it is possible to define non-rectangular frames, such as, for example, Aitoff projections.
+
+This subpackage differs from \package{APLpy} \citep{aplpy} in that the latter focuses on providing a very high-level interface to plotting that requires very few lines of code to get a good result, whereas \package{wcsaxes} defines an interface that is much closer to that of \package{matplotlib} \citep{matplotlib}.
 This enables significantly more advanced visualizations.
 
-An example of a visualization made with \package{wcsaxes} is shown in
-\figurename~\ref{fig:wcsaxes}; This example illustrates the ability to
-overlay multiple coordinate systems and customize which ticks/labels are shown
-on which axes around the image. This also uses the image stretching
-functionality from \sectionname~\ref{sec:stretch} to show the image in a
-square-root stretch (automatically updating the tick positions in the colorbar).
+An example of a visualization made with \package{wcsaxes} is shown in \figurename~\ref{fig:wcsaxes} -- this example illustrates the ability to overlay multiple coordinate systems and customize which ticks/labels are shown on which axes around the image.
+This also uses the image stretching functionality from \sectionname~\ref{sec:stretch} to show the image in a square root stretch (automatically updating the tick positions in the colorbar).
 
@@
 \caption{%
-An example of figure made using the \package{astropy.visualization.wcsaxes}
-subpackage, using \textit{Spitzer}/IRAC 8.0~$\mu$m data from the Cygnus-X
-\textit{Spitzer} Legacy survey \citep{cygnusx}.
+An example of figure made using the \package{astropy.visualization.wcsaxes} subpackage, using \textit{Spitzer}/IRAC 8.0~$\mu$m data from the Cygnus-X \textit{Spitzer} Legacy survey \citep{cygnusx}.
 \label{fig:wcsaxes}
@@
 \package{astropy.visualization} also provides a histogram function, which is a
-generalization of \texttt{matplotlib}’s histogram function, to allow for a more
+generalization of \texttt{matplotlib}’s histogram function, to allow for more
 flexible specification of histogram bins.  The function provides several methods
@@
 parameter, which allows specification of one of four different methods for
-automatic bin selection: ``blocks'', ``knuth'', ``scott'', or ``freedman''.
+automatic bin selection: `blocks', `knuth', `scott', or `freedman'.
 
@@
 
-\cite{Lupton2004} describe an ``optimal'' algorithm for producing
-RGB composite images from three separate high-dynamic range
-arrays. The \package{astropy.visualization} subpackage provides a convenience
-function to create such a color image.  It also includes an associated set of
-classes to provide alternate scalings.
-This functionality was contributed by developers from the Large Synoptic Survey
-Telescope (LSST) and serves as an example of contribution to \astropy from a
-more traditional engineering organization \citep{Jennes2016}.
-
-The Sloan Digital Sky Survey (SDSS) SkyServer color images were made using a
-variation on this technique.  As an example, in \figurename~\ref{fig:ngc6977},
-we show an RGB color image of the Hickson 88 group, centered near NGC~6977.
-This image was generated from SDSS images using the
-\package{astropy.visualization} tools.
+\cite{Lupton2004} describe an ``optimal'' algorithm for producing red-green-blue (RGB) composite images from three separate high-dynamic range arrays.
+The \package{astropy.visualization} subpackage provides a convenience function to create such a color image.
+It also includes an associated set of classes to provide alternate scalings.
+This functionality was contributed by developers from the Large Synoptic Survey Telescope (LSST) and serves as an example of contribution to \astropy from a more traditional engineering organization \citep{Jennes2016}.
+
+The Sloan Digital Sky Survey (SDSS) SkyServer color images were made using a variation on this technique.
+As an example, in \figurename~\ref{fig:ngc6977} we show an RGB color image of the Hickson 88 group, centered near NGC~6977.
+This image was generated from SDSS images using the \package{astropy.visualization} tools.
 
@@
 
-The \package{cosmology} package contains classes for representing different
-cosmologies and functions for calculating commonly used quantities such as
-look-back time and distance.   The package was described in detail in
-\cite{astropy}.  The default cosmology in \astropypkg version 2.0 is given by
-the values in \cite{2016A&A...594A..13P}.
+The \package{cosmology} package contains classes for representing different cosmologies and functions for calculating commonly used quantities such as look-back time and distance.
+The package was described in detail in \cite{astropy}.
+The default cosmology in \astropy version 2.0 is given by the values in \cite{2016A&A...594A..13P}.
 
@@
 The \package{astropy.stats} package provides statistical tools that
-are useful for astronomy and are either not found in or extend
-the available functionality of other \python statistics packages, such
+are useful for or specific to astronomy and are not found in or extend
+the available functionality of other \python statistics packages such
 as \package{scipy} \citep{scipy} or \package{statsmodels}
@@
 a range of functionality used by many different disciplines
-in astronomy. It is not a complete set of statistical tools, but rather
+in astronomy. It is not a complete set of statistic tools, but rather
 a still growing collection of useful features.
+
+% The current review process for contributions to the \package{astropy.stats} package includes review of the code, documentation, testing, and scientific merit of the inclusion.
+When necessary, scientific reviewers outside of the maintainers will be sought for their input on new pull requests.
+
+In this section, we describe these tools, including robust statistical estimators, circular statistics, periodograms, spatial statistics, and histogram binning.
 
@@
 
-Robust statistics provide reliable estimates of basic statistics for complex
-distributions that largely mitigate the effects of outliers.
-\package{astropy.stats} includes several robust statistical functions that are
-commonly used in astronomy, such as sigma clipping methods for rejecting
-outliers, median absolute deviation functions, and biweight estimators,
-which have been used to calculate the velocity dispersion of galaxy clusters
-\citep{Beers1990}.
+Robust statistics provide reliable estimates of basic statistics for complex distributions that largely mitigate the effects of outliers.
+\package{astropy.stats} includes several robust statistical functions that are commonly used in astronomy, such as sigma clipping methods for rejecting outliers, median absolute deviation functions, and biweight estimators, which have been used to calculate the velocity dispersion of galaxy clusters \citep{Beers1990}.
 
@@
 
-Astronomers often need to compute statistics of quantities evaluated on a
-circle, such as sky direction or polarization angle.
+Astronomers often need to compute statistics of quantities evaluated on a circle, such as sky direction or polarization angle.
 A set of circular statistical estimators based on \citet{JammalamadakaSengupta}
@@
 radians) and \texttt{Quantity} objects.  In addition, the subpackage includes
-tests for Rayleigh Test, \texttt{vtest}, and a function to compute the maximum
-likelihood estimator for the parameters of the von Mises distribution.
+tests for Rayleigh Test, vtest, and a function to compute the maximum likelihood
+estimator for the parameters of the von Mises distribution.
 
@@
 
-Periodic analysis of unevenly-spaced time series is common across many
-sub-fields of astronomy. The \package{astropy.stats} package now includes
-several efficient implementations of the Lomb-Scargle periodogram
-\citep{Lomb76, Scargle82} and several generalizations, including floating mean
-models \citep{Zechmeister09}, truncated Fourier models \citep{Bretthorst2003},
-and appropriate handling of heteroscedastic uncertainties.
-Importantly, the implementations make use of several fast and scalable
-computational approaches \citep[e.g.,][]{Press89, Palmer09}, and thus can be
-applied to much larger datasets than Lomb-Scargle algorithms available in,
-e.g., \package{scipy.stats} (\citealt{scipy}). Much of the Lomb-Scargle code
-in \astropypkg has been adapted from previously-published open-source code
-\citep{astroML, VanderPlas2015}.
+Periodic analysis of unevenly-spaced time series is common across many subfields of astronomy.
+The \package{astropy.stats} package now includes several efficient implementations of the Lomb-Scargle periodogram \citep{Lomb76, Scargle82} and several generalizations, including floating mean models \citep{Zechmeister09}, truncated Fourier models \citep{Bretthorst2003}, and appropriate handling of heteroscedastic uncertainties.
+Importantly, the implementations make use of several fast and scalable computational approaches \citep[e.g.,][]{Press89, Palmer09}, and so can be applied to much larger datasets than Lomb-Scargle algorithms available in, e.g., \package{scipy.stats} (\citealt{scipy}).
+Much of the Lomb-Scargle code in \astropy has been adapted from previously-published open-source code \citep{astroML, VanderPlas2015}.
 
 \subsubsection{Bayesian Blocks and Histogram Binning}
-\package{astropy.stats} also includes an implementation of
-{\it Bayesian Blocks} \citep{Scargle2013}, an algorithm for analysis of
-break-points in non-periodic astronomical time-series. One interesting
-application of Bayesian Blocks is its use in determining optimal histogram
-binnings, particularly binnings with unequal bin sizes.
-This code was adapted, with several improvements, from the \package{astroML}
-package \citep{astroML}. An example of a histogram fit using the Bayesian
-Blocks algorithm is shown in the right panel of
-\figurename~\ref{fig:bayes-blocks-hist}.
+\astropypkg also includes an implementation of {\it Bayesian Blocks} \citep{Scargle2013}, an algorithm for analysis of break-points in non-periodic astronomical time-series.
+One interesting application of Bayesian Blocks is its use in determining optimal histogram binnings, and in particular binnings with unequal bin sizes.
+This code was adapted, with several improvements, from the \package{astroML} package \citep{astroML}.
+An example of a histogram fit using the Bayesian blocks algorithm is shown in the right panel of \figurename~\ref{fig:bayes-blocks-hist}.
 
@@
     {\it center:} a histogram with the number of equal-width bins determined automatically using \package{numpy}'s {\tt bins='auto'}.
-    {\it right:} a histogram created with \astropypkg, with irregularly-spaced bins computed via the Bayesian Blocks algorithm.
+    {\it right:} a histogram created with \package{astropy}, with irregularly-spaced bins computed via the Bayesian Blocks algorithm.
     Compared to regularly-spaced bins, the irregular bin widths give a more accurate visual representation of features in the dataset at various scales.
@@
 \label{sec:infrastructure}
+%\inlinecomment{BMS}{should we describe astropy-helpers even though it's future is unsure?}
 % Text also edited by Adrian PW
@@
 also maintains and distributes several general-purpose infrastructure packages
-that assist the maintenance and upkeep of the \astropypkg core package and
+that help with the maintenance and upkeep of the \astropypkg core package and
 other affiliated packages.
-The following sections describe the most widely-used infrastructure packages
+The following sections describes the most widely-used infrastructure packages
 developed by the \astropy Project.
@@
 \astropy also provides a set of scripts for setting up and configuring
-CI services as a \github repository,
+continuous integration (CI) services as a \github repository,
 \package{astropy/ci-helpers}.\footnote{\url{https://github.com/astropy/ci-helpers}}
-These tools aim to empower package maintainers to control their testing setup
-and installation process for various CI services through a
+These tools aim to empower package maintainers to control their testing set up
+and installation process for various continuous integration services through a
 set of environment variables.
@@
 
-The documentation for many \python packages, including
-all the packages in the \astropy ecosystem, is written using the
+The documentation for many \python packages, the core \astropypkg package, and
+for all packages in the \astropy ecosystem is written using the
 \package{Sphinx} documentation build system.
-\package{Sphinx} supports writing documentation using plain text files
-that follow a markup language called \texttt{reStructuredText} (RST).
-These files are then transformed into HTML, PDF, or \LaTeX{} documents
-during the documentation build process.
-For the \astropy project, we have developed several \package{Sphinx} extensions
+\package{Sphinx} makes it possible to write documentation using plain text files
+that follow a markup language called ``reStructuredText,'' which are then
+transformed into HTML or \LaTeX{} documentation during the documentation build
+process.
+For the \astropy project, we have developed a few \package{Sphinx} extensions
 that facilitate automatically generating API documentation for large projects,
@@
 \package{sphinx-automodapi}\footnote{\url{http://sphinx-automodapi.readthedocs.io}},
-which provides a convenient single RST command to generate a set of
-documentation pages, listing all of the available classes, functions, and
+which makes it easy with a single reStructuredText command to generate a set of
+documentation pages listing all of the available classes, functions, and
 attributes in a given \python module.
+
+%\inlinecomment{TPR}{We should put the releases of sphinx-automodapi on Zenodo and cite this}
+
+% \section{State of the Ecosystem}
+% Commenting out unless a clear statement is added
 
@@
 On top of planned changes and additions to the core package, we also plan to
-overhaul the \astropy educational/learning materials and further
-generalize the infrastructure utilities originally developed for the core
-package for the benefit of the community.
-
-\subsection{Future versions of the Astropy core and affiliated packages}
+overhaul the \astropy educational and learning materials, and further refactor
+and generalize the infrastructure utilities developed for the core package for
+the benefit of the community.
+
+%\inlinecomment{BMS}{should we mention the refactored infra here?  e.g. pytest-astropy and sphinx-astropy?}
+
+\subsection{Future versions of the \astropypkg core and affiliated packages}
 
 One of the most significant changes coming in this next major release will be
-removing the support for \python 2 \citep{ape10}: future versions of \astropypkg
-will only support \python 3.5 or higher.
-Removing \python 2 support will allow the use of new \python 3-only features,
-simplify the code base, and reduce the testing overhead for the package.
+removing support for \python 2 \citep{ape10}: future versions of \astropypkg
+will only support \python 3.5 and higher.
+Removing \python 2 support will allow the use of new, \python 3-only features,
+will simplify the code base, and reduce the testing overhead for the package.
 \astropypkg version 3.0 is currently scheduled for January 2018.
@@
 In the next major release after version 3.0, scheduled for
-mid-2018, the focus will be on algorithm optimization and
-documentation improvement.
-To prepare for this release, we are subjecting the core package to testing,
-evaluation, and performance monitoring.
-As a result, less new functionality may be introduced as a trade-off for
-better performance.
+mid-2018, the focus will be on optimization of the code and improved
+documentation.
+To prepare for this release, we are preparing software for testing, evaluating,
+and monitoring the performance of the code.
+Less functionality may be introduced in this release while the focus will be
+primarily on improved performance.
 
@@
 testing and documentation standards of \astropy.
-Some of these new efforts include an initiative to develop tools for
+Some of these new efforts includes an initiative to develop tools for
 spectroscopy \citep[\package{specutils}, \package{specreduc}, \package{specviz}]
-{ape13}, integration of LSST software, and support for HEALPIX
+{ape13}, integration of LSST software, and packages to support HEALPIX
 projection. %\citep{astropy-healpix}
@@
 
-The \astropypkg core package's documentation contains narrative descriptions of
-the package's functionality, along with detailed usage notes for functions,
+The \astropypkg core package documentation contains narrative descriptions of
+the package functionality along with detailed usage notes for functions,
 classes, and modules.
-While useful as a reference for more experienced \python users, it is not the
-proper entry-point for other users or learning environments.
+While useful as a reference and for more advanced \python users, it is not the
+right entry-point for all users or learning environments.
 In the near future, we will launch a new resource for learning to use both the
 \astropypkg core package and the many packages in the broader \astropy
-ecosystem, under the name \emph{Learn Astropy}.
+ecosystem, under the name `\emph{Learn Astropy}.'
 
@@
     \item[Documentation] The \astropypkg and affiliated package documentation
-        contains the complete description of a package with all requisite
+        contain the complete description of a package with all requisite
         details, including usage, dependencies, and examples.
@@
         Tutorials are more extended and comprehensive than examples, may contain
-        exercises for the users, and are generally geared towards pedagogical
-        activities.
+        exercises for the users, and are generally geared towards workshops or
+        teaching.
         Several tutorials already
@@
         actively expanded.
-    \item[Guides] These are long-form narrative, comprehensive, and
-        conceptually-focused documents (roughly one book chapter in length),
+    \item[Guides] These are long-form narrative, comprehensive,
+        conceptually-focused documents (roughly one book chapter in length)
         providing stand-alone introductions to core packages in addition to the
         underlying astronomical concepts.
-        These are less specific and more conceptual than tutorials;
+        These are less specific and more conceptual than tutorials.
         For example, ``using \astropypkg and \package{ccdproc} to reduce imaging
@@
 We encourage any users who wish to see specific material to either contribute or
-comment on these efforts via the \astropy mailing list or \package{astropy/astropy-tutorials}
+comment on these efforts via the \astropy mailing list or \astropy-tutorials
 \github repository.\footnote{\url{https://github.com/astropy/astropy-tutorials}}
@@
 The development of the \astropypkg package and cultivation of the \astropy
-ecosystem are still maintaining significant growth while improving in stability,
+ecosystem is still maintaining significant growth while improving stability,
 breadth, and reliability.
@@
 reached stability with a rich set of features that help astronomers worldwide to
-perform many daily tasks, such as planning observations, analyzing data or
+perform many daily tasks such as planning observations, analyzing data or
 simulation results, and writing publications.
-The strong emphasis that the \astropy project puts on reliability and high coding
-standards helps users to trust the calculations performed with \astropypkg and
+The strong emphasis that the \astropy project puts on reliability and code
+correctness helps users to trust the calculations performed with \astropypkg and
 to publish reproducible results.
-At the same time, the \astropy ecosystem and core package are both growing: new
-functionality is still being contributed and new affiliated packages are being
+At the same time, the \astropy ecosystem and core package are growing: new
+functionality is still being contributed, and new affiliated packages are being
 developed to support more specialized needs.
@@
 computer science and software development, despite the fact that a major
-fraction of many astronomers' workload today is related to software use
+fraction of nearly every astronomer's workload today is related to software use
 and development.
 The \astropypkg package leads by example, showing all interested astronomers how
-modern tools like \texttt{git} version control or CI testing can
+modern tools like \texttt{git} version control or continuous integration can
 increase the quality, accessibility, and discoverability of astronomical
@@
 to help improve their skills.
-As a community, \astropy follows an explicit code of conduct \citep{ape8} and treats all
-contributors and users with respect, provides a harassment-free environment, and
-encourages and welcomes new contributions from all.
+As a community, we follow an explicit code of conduct \citep{ape8} and treat all
+contributors and users with respect, provide a harassment-free environment, and
+encourage and welcome new contributions from all.
 Thus, while the \astropy project provides and develops software and tools
@@
 
-\acknowledgments The \astropy community is supported by and makes use
-of a number of organizations and services outside the traditional
-academic community. We thank Google for financing and organizing the
-Google Summer of Code (GSoC) program, that has funded severals
-students per year to work on \astropy related projects over the
-summer. These students often turn into long-term contributors. We also
-thank NumFOCUS and the Python Software Foundation for financial
-support. Within the academic community, we thank
-institutions that make it possible that astronomers and other developers on
-their staff can contribute their time to the development of
-\astropy projects.
-
-Furthermore, the \astropy packages would not exist
-in their current form without a number of web services for code
-hosting, continuous integration, and documentation; in particular,
-\astropy heavily relies on GitHub, Travis CI, Appveyor, CircleCI, and
-Read the Docs.
-
-\astropypkg interfaces with the SIMBAD database,
-operated at CDS, Strasbourg, France. It also makes use of the ERFA library \citep{erfa},
-which in turn derives from the IAU SOFA Collection\footnote{\url{http://www.iausofa.org}} developed by the International Astronomical Union Standards of Fundamental Astronomy \citep{sofa}.
+\acknowledgments
+
+Who to thank?  numfocus, GSOC, Python Software Foundation
+
+We thank the many web services that make developing and maintaining this package
+feasible, such as GitHub, Travis CI, Appveyor, CircleCI, and Read the Docs.
 
@@
           \package{Cython} (\citealt{cython}),
-          \package{SOFA} (\citealt{sofa}),
-          \package{ERFA} (\citealt{erfa})
           }
@@
 \appendix
-
 \section{List of Affiliated Packages}
+
+%\inlinecomment{SMC}{Can a brief description of each code be added?}
 

### 2017-12-08 main.tex
intro: any->many

--- 2017-12-08 main.tex
@@
 are then typically used by smaller groups for more domain-specific purposes.
-Both in packages meant for wider distribution and in scripts specific to 
-particular research projects, a library that addresses common astronomical tasks
-simplifies the software development process.
-The users of such a library then also benefit from a community and ecosystem
-built around a shared foundation.
+Whether for a package meant for wide distribution or for scripts and programs
+for a specific research project, the implementation of astronomical software can
+be eased through the use of a library that provides core functionality that is
+common to many astronomical tasks.
+The users of such software then also benefit from a community and ecosystem
+built around a common foundation.
 The \astropy project has grown to become this community for \python astronomy

### 2017-12-08 main.tex
Address comments from Adrian

@@
 The \package{astropy.modeling} subpackage provides a framework for representing
-analytical models and performing model evaluation and parameter fitting. Models and
-fitters are independent of each other: a model can be fit with different
+analytical models and performing model evaluation and parameter fitting.
+The main motivation for this functionality was to create a framework that
+allows arbitrary combination of models to support the Generalized World
+Coordinate System (GWCS) package.\footnote{\url{https://github.com/spacetelescope/gwcs}}
+The current FITS WCS specification lacks the flexibility to represent
+arbitrary distortions and does not meet the needs of many types of current instrumentation.
+The fact that the \astropypkg modeling framework now supports propagating
+units also makes it a useful tool for representing and fitting astrophysical
+models within data analysis tools.
+
+Models and fitters are independent of each other: a model can be fit with different
 fitters and new fitters can be added without changing existing models. The
 framework is designed to be flexible and easily extensible. The goal is to have
-a rich set of models but also make it easy to create new ones if necessary. The
-modeling framework is used in a variety of data analysis tools and is the basis
-for the Generalized World Coordinate System (GWCS)
-package.\footnote{\url{https://github.com/spacetelescope/gwcs}}
+a rich set of models, but to also facilitate creating new ones, if necessary.
 

### 2017-12-08 main.tex
Address review comments

--- 2017-12-08 main.tex
@@
 The \package{astropy.io.ascii} subpackage now provides the capability
-to read a table within an HTML file or web URL into an astropy
-\texttt{Table} object. Conversely a \texttt{Table} object can now
+to read a table within an HTML file or web URL into an \astropypkg
+\texttt{Table} object. A \texttt{Table} object can now also
 be written out as an HTML table.
@@
 Command-line scripts are now available for printing a summary of the HDUs in
-a FITS file(s) (\texttt{fitsinfo}) and for printing the header information to
+FITS file(s) (\texttt{fitsinfo}) and for printing the header information to
 the screen in a human-readable format (\texttt{fitsheader}).
 
-FITS files are now loaded \emph{lazily} (the default behavior, which can be
-deactivated if needed), where all HDUs are not loaded until they are
-requested. This should provide substantial speedups for situations using the
+FITS files are now loaded \emph{lazily} (this default behavior can be
+deactivated, if needed), where all HDUs are not loaded until
+requested. This should provide substantial speed-ups when using the
 convenience functions (e.g., \texttt{getheader()} or \texttt{getdata()}) to
-get HDU’s that are near the front of a file with many HDUs.
+get an HDU that is near the beginning of many in a file.
 

### 2017-12-08 main.tex
Address one of the comments

@@
 all platforms; the package is constantly tested on different platforms as part
-of our suite of continuous integration tests.
+of a suite of continuous integration (CI) tests.
 
@@
 
-The \astropy project, as of the v2.0 release, does not receive any direct financial support for
-the development of \astropypkg.  Development of the software, all supporting materials, and community support are provided
-by individuals who work on the \astropy project in their own personal
-time, by individuals or groups contributing to \astropy as
-part of a research project, or contributions from institutions that allocate
-people to work on \astropy.
+The \astropy project, as of the version 2.0 release, does not receive any direct
+financial support for the development of \astropypkg.
+Development of the software, all supporting materials, and community support are
+provided by individuals who work on the \astropy project in their own personal
+time, by individuals or groups contributing to \astropy as part of a research
+project, or contributions from institutions that allocate people to work on
+\astropy.
 A list of organizations that have contributed to \astropy in this manner
-can be found in the Acknowledgements.
+can be found in the Acknowledgments.
 
@@
 
-\section{Astropy Core Package v2.0}
+\section{Astropy Core Package Version 2.0}
 \label{sec:core}
@@
 
-% \subsubsection{\texttt{.ascii}: HTML tables}
-
 The \package{astropy.io.ascii} subpackage now provides the capability
@@
 convenience functions (e.g., \texttt{getheader()} or \texttt{getdata()}) to
-get an HDU that is near the beginning of many in a file.
-
-% \inlinecomment{Tom R}{too detailed? I don't think we need to mention every single performance enhancement, right?}
-
-% \subsubsection{\texttt{.misc}: YAML serialization}
-
-% The new \package{astropy.io.misc.yaml} module allows converting astropy
-% objects into a standard YAML format.  This can be used beyond
-% \texttt{astropy.io.misc.yaml}: for example, to serialize the metadata of
-% tables before saving to other formats like HDF5.
-
-%\inlinecomment{BMS}{Maybe move the command line tools into a separate subsection to highlight them (even though we mostly only have fits related scripts)?
-They are supposed to be used more frequently by individual users.}
-%\inlinecomment{hamogu}{MY feeling is that this section is too detailed already. If I had written it, I would not have mentioned the scripts at all.}
+get an HDU that is near the beginning in a file with many HDUs.
 
@@
 
-The \package{astropy.convolution} subpackage implements `normalized convolution' \citep[e.g.,][]{Knutsson1993}, which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.
+The \package{astropy.convolution} subpackage implements
+``normalized convolution'' \citep[e.g.,][]{Knutsson1993} that is an image
+reconstruction technique, in which missing data are ignored during the
+convolution and replaced with values interpolated using the kernel;
 An example of this is given in \figurename~\ref{fig:convolution-example}.
-In versions $\leq 1.3$, the direct convolution and Fast Fourier Transform (FFT) convolution approaches were not consistent, with FFT convolution implementing normalized convolution and direct convolution implementing a different approach.
-As of version 2.0, the two methods are consistent and include a suite of consistency checks.
+In \astropypkg versions $\leq 1.3$, the direct convolution and Fast Fourier Transform (FFT)
+convolution approaches were inconsistent, with the latter implementing
+normalized convolution, while the former a different approach.
+As of version 2.0, the two methods now agree and include a suite of
+consistency checks.
 
 \begin{figure}
-\includegraphics[width=\textwidth]{convolution_example.png}
+\includegraphics[width=\textwidth]{convolution_example}
 \caption{%
     An example showing different modes of convolution available in the \python
-    ecosystem.  The red x's mark pixels that are set to NaN in the original data
-    (a).  If the data are convolved with a Gaussian kernel on a $9\times 9$ grid using
-    scipy's direct convolution (b), any pixel within range of the original NaN
-    pixels is also set to NaN.  Panel (c) shows what happens if the NaNs are set
-    to zero first: the originally NaN regions are depressed relative to their
-    surroundings.  Finally, panel (d) shows \astropypkg's convolution behavior,
-    where the missing pixels are replaced with values interpolated from their
-    surroundings using the convolution kernel.
+    ecosystem.  The red x's mark pixels that are set to \texttt{NaN} in the
+    original data (a).  If the data are convolved with a Gaussian kernel on a
+    $9\times 9$ grid using
+    \package{scipy}'s direct convolution (b), any pixel within range of the original \texttt{NaN}
+    pixels is also set to \texttt{NaN}.  Panel (c) shows what happens if the
+    \texttt{NaN}s are set to zero first: the originally \texttt{NaN} regions are
+    depressed relative to their surroundings.  Finally, panel (d) shows
+    \astropypkg's convolution behavior, where the missing pixels are replaced
+    with values interpolated from their surroundings using the convolution
+    kernel.
     \label{fig:convolution-example}
@@
 
-The \package{astropy.visualization} subpackage provides functionality that can be helpful when visualizing data.
-This includes a framework for plotting astronomical images with coordinates with \package{matplotlib} (previously the standalone \package{wcsaxes} package), functionality related to image normalization (including both scaling and stretching), smart histogram plotting, RGB color image creation from separate images, and custom plotting styles for \package{matplotlib}.
+The \package{astropy.visualization} subpackage provides functionality that can
+be helpful when visualizing data. This includes a framework (previously the
+standalone \package{wcsaxes} package) for plotting
+astronomical images with coordinates with \package{matplotlib}, functionality related to image
+normalization (including both scaling and stretching), smart histogram
+plotting, red-green-blue (RGB) color image creation from separate images,
+and custom plotting styles for \package{matplotlib}.
 
@@
 
-\package{astropy.visualization} provides a framework for transforming values in images (and more generally any arrays), typically for the purpose of visualization.
-Two main types of transformations are normalization and stretching of image values.
-
-Normalization transforms the images values to the range $[0,1]$ using lower and upper limits $(v_{\rm min}, v_{\rm max})$
+\package{astropy.visualization} provides a framework for transforming values in
+images (and more generally any arrays), typically for the purpose of
+visualization. Two main types of transformations are normalization and
+stretching of image values.
+
+Normalization transforms the image values to the range $[0,1]$ using lower and
+upper limits $(v_{\rm min}, v_{\rm max})$,
 \begin{equation}
-y = \frac{x - v_{\rm min}}{v_{\rm max} - v_{\rm min}}
+y = \frac{x - v_{\rm min}}{v_{\rm max} - v_{\rm min}} \quad ,
 \end{equation}
@@
 
-Stretching transforms the image values in the range $[0,1]$ again to the range $[0,1]$ using a linear or non-linear function
+Stretching transforms the image values in the range $[0,1]$ again to the range
+$[0,1]$ using a linear or non-linear function,
 \begin{equation}
@@
 
-Several classes are provided for automatically determining intervals (e.g., using image percentiles) and for normalizing values in this interval to the $[0,1]$ range.
-
-\package{matplotlib} allows a custom normalization and stretch to be used when displaying data by passing a normalization object.
-The \package{astropy.visualization} package also provides a normalization class that wraps the interval and stretching objects into a normalization object that \package{matplotlib} understands.
+Several classes are provided for automatically determining intervals
+(e.g., using image percentiles) and for normalizing values in this interval to
+the $[0,1]$ range.
+
+\package{matplotlib} allows a custom normalization and stretch to be used when
+displaying data by passing in a normalization object.
+The \package{astropy.visualization} package also provides a normalization class
+that wraps the interval and stretches objects into a normalization object that
+\package{matplotlib} understands.
 
@@
 
-Astronomers dealing with observational imaging commonly need to make figures with images that include the correct coordinates and optionally display a coordinate grid.
-The challenge, however, is that the conceptual coordinate axes (such as longitude/latitude) need not be lined up with the pixel axes of the image.
-The \package{astropy.visualization.wcsaxes} subpackage implements a generalized way of making figures from an image array and a world coordinate system (WCS) object that provides the transformation between pixel and `world' coordinates.
-
-World coordinates can be, for example, right ascension and declination, but can also include, for example, velocity, wavelength, frequency, or time.
-The main features from this subpackage include the ability to control which axes to show which coordinate on (for example showing longitude ticks on the top and bottom axes and latitude on the left and right axes), controlling the spacing of the ticks either by specifying the positions to use or providing a tick spacing or an average number of ticks that should be present on each axis, setting the format for the tick labels to ones commonly used by astronomers, controlling the visibility of the grid/graticule, and overlaying ticks, labels, and/or grid lines from different coordinate systems.
-In addition, it is possible to pass data with more than two dimensions and slice on-the-fly.
-Finally, it is possible to define non-rectangular frames, such as, for example, Aitoff projections.
-
-This subpackage differs from \package{APLpy} \citep{aplpy} in that the latter focuses on providing a very high-level interface to plotting that requires very few lines of code to get a good result, whereas \package{wcsaxes} defines an interface that is much closer to that of \package{matplotlib} \citep{matplotlib}.
+Astronomers dealing with observational imaging commonly need to make figures
+with images that include the correct coordinates and optionally display a
+coordinate grid. The challenge, however, is that the conceptual coordinate axes
+(such as longitude/latitude) need not be lined up with the pixel axes of the
+image. The \package{astropy.visualization.wcsaxes} subpackage implements a
+generalized way of making figures from an image array and a WCS object
+that provides the transformation between pixel and world coordinates.
+
+World coordinates can be, for example, right ascension and declination, but can
+also include, for example, velocity, wavelength, frequency, or time.
+The main features from this subpackage include the ability to control which
+axes to show which coordinate on (e.g., showing longitude ticks on the
+top and bottom axes and latitude on the left and right axes), controlling the
+spacing of the ticks either by specifying the positions to use or providing a
+tick spacing or an average number of ticks that should be present on each axis,
+setting the format for the tick labels to ones commonly used by astronomers,
+controlling the visibility of the grid/graticule, and overlaying ticks, labels,
+and/or grid lines from different coordinate systems. In addition, it is
+possible to pass data with more than two dimensions and slice on-the-fly.
+Last but not least, it is also able to define non-rectangular frames, such as,
+for example, Aitoff projections.
+
+This subpackage differs from \package{APLpy} \citep{aplpy}, in that the latter
+focuses on providing a very high-level interface to plotting that requires very
+few lines of code to get a good result, whereas \package{wcsaxes} defines an
+interface that is much closer to that of \package{matplotlib} \citep{matplotlib}.
 This enables significantly more advanced visualizations.
 
-An example of a visualization made with \package{wcsaxes} is shown in \figurename~\ref{fig:wcsaxes} -- this example illustrates the ability to overlay multiple coordinate systems and customize which ticks/labels are shown on which axes around the image.
-This also uses the image stretching functionality from \sectionname~\ref{sec:stretch} to show the image in a square root stretch (automatically updating the tick positions in the colorbar).
+An example of a visualization made with \package{wcsaxes} is shown in
+\figurename~\ref{fig:wcsaxes}; This example illustrates the ability to
+overlay multiple coordinate systems and customize which ticks/labels are shown
+on which axes around the image. This also uses the image stretching
+functionality from \sectionname~\ref{sec:stretch} to show the image in a
+square-root stretch (automatically updating the tick positions in the colorbar).
 
@@
 
-\cite{Lupton2004} describe an ``optimal'' algorithm for producing red-green-blue (RGB) composite images from three separate high-dynamic range arrays.
-The \package{astropy.visualization} subpackage provides a convenience function to create such a color image.
-It also includes an associated set of classes to provide alternate scalings.
-This functionality was contributed by developers from the Large Synoptic Survey Telescope (LSST) and serves as an example of contribution to \astropy from a more traditional engineering organization \citep{Jennes2016}.
-
-The Sloan Digital Sky Survey (SDSS) SkyServer color images were made using a variation on this technique.
-As an example, in \figurename~\ref{fig:ngc6977} we show an RGB color image of the Hickson 88 group, centered near NGC~6977.
-This image was generated from SDSS images using the \package{astropy.visualization} tools.
+\cite{Lupton2004} describe an ``optimal'' algorithm for producing
+RGB composite images from three separate high-dynamic range
+arrays. The \package{astropy.visualization} subpackage provides a convenience
+function to create such a color image.  It also includes an associated set of
+classes to provide alternate scalings.
+This functionality was contributed by developers from the Large Synoptic Survey
+Telescope (LSST) and serves as an example of contribution to \astropy from a
+more traditional engineering organization \citep{Jennes2016}.
+
+The Sloan Digital Sky Survey (SDSS) SkyServer color images were made using a
+variation on this technique.  As an example, in \figurename~\ref{fig:ngc6977},
+we show an RGB color image of the Hickson 88 group, centered near NGC~6977.
+This image was generated from SDSS images using the
+\package{astropy.visualization} tools.
 
@@
 a range of functionality used by many different disciplines
-in astronomy. It is not a complete set of statistic tools, but rather
+in astronomy. It is not a complete set of statistical tools, but rather
 a still growing collection of useful features.
-
-% The current review process for contributions to the \package{astropy.stats} package includes review of the code, documentation, testing, and scientific merit of the inclusion.
-When necessary, scientific reviewers outside of the maintainers will be sought for their input on new pull requests.
-
-In this section, we describe these tools, including robust statistical estimators, circular statistics, periodograms, spatial statistics, and histogram binning.
 
@@
 
-Periodic analysis of unevenly-spaced time series is common across many subfields of astronomy.
-The \package{astropy.stats} package now includes several efficient implementations of the Lomb-Scargle periodogram \citep{Lomb76, Scargle82} and several generalizations, including floating mean models \citep{Zechmeister09}, truncated Fourier models \citep{Bretthorst2003}, and appropriate handling of heteroscedastic uncertainties.
-Importantly, the implementations make use of several fast and scalable computational approaches \citep[e.g.,][]{Press89, Palmer09}, and so can be applied to much larger datasets than Lomb-Scargle algorithms available in, e.g., \package{scipy.stats} (\citealt{scipy}).
-Much of the Lomb-Scargle code in \astropy has been adapted from previously-published open-source code \citep{astroML, VanderPlas2015}.
+Periodic analysis of unevenly-spaced time series is common across many
+sub-fields of astronomy. The \package{astropy.stats} package now includes
+several efficient implementations of the Lomb-Scargle periodogram
+\citep{Lomb76, Scargle82} and several generalizations, including floating mean
+models \citep{Zechmeister09}, truncated Fourier models \citep{Bretthorst2003},
+and appropriate handling of heteroscedastic uncertainties.
+Importantly, the implementations make use of several fast and scalable
+computational approaches \citep[e.g.,][]{Press89, Palmer09}, and thus can be
+applied to much larger datasets than Lomb-Scargle algorithms available in,
+e.g., \package{scipy.stats} (\citealt{scipy}). Much of the Lomb-Scargle code
+in \astropypkg has been adapted from previously-published open-source code
+\citep{astroML, VanderPlas2015}.
 
 \subsubsection{Bayesian Blocks and Histogram Binning}
-\astropypkg also includes an implementation of {\it Bayesian Blocks} \citep{Scargle2013}, an algorithm for analysis of break-points in non-periodic astronomical time-series.
-One interesting application of Bayesian Blocks is its use in determining optimal histogram binnings, and in particular binnings with unequal bin sizes.
-This code was adapted, with several improvements, from the \package{astroML} package \citep{astroML}.
-An example of a histogram fit using the Bayesian blocks algorithm is shown in the right panel of \figurename~\ref{fig:bayes-blocks-hist}.
+\package{astropy.stats} also includes an implementation of
+{\it Bayesian Blocks} \citep{Scargle2013}, an algorithm for analysis of
+break-points in non-periodic astronomical time-series. One interesting
+application of Bayesian Blocks is its use in determining optimal histogram
+binnings, particularly binnings with unequal bin sizes.
+This code was adapted, with several improvements, from the \package{astroML}
+package \citep{astroML}. An example of a histogram fit using the Bayesian
+Blocks algorithm is shown in the right panel of
+\figurename~\ref{fig:bayes-blocks-hist}.
 
@@
 \package{sphinx-automodapi}\footnote{\url{http://sphinx-automodapi.readthedocs.io}},
-which makes it easy with a single reStructuredText command to generate a set of
-documentation pages listing all of the available classes, functions, and
+which provides a convenient single RST command to generate a set of
+documentation pages, listing all of the available classes, functions, and
 attributes in a given \python module.
-
-%\inlinecomment{TPR}{We should put the releases of sphinx-automodapi on Zenodo and cite this}
-
-% \section{State of the Ecosystem}
-% Commenting out unless a clear statement is added
 
@@
 On top of planned changes and additions to the core package, we also plan to
-overhaul the \astropy educational and learning materials, and further refactor
-and generalize the infrastructure utilities developed for the core package for
-the benefit of the community.
-
-%\inlinecomment{BMS}{should we mention the refactored infra here?  e.g. pytest-astropy and sphinx-astropy?}
-
-\subsection{Future versions of the \astropypkg core and affiliated packages}
+overhaul the \astropy educational/learning materials and further
+generalize the infrastructure utilities originally developed for the core
+package for the benefit of the community.
+
+\subsection{Future versions of the Astropy core and affiliated packages}
 
 One of the most significant changes coming in this next major release will be
-removing support for \python 2 \citep{ape10}: future versions of \astropypkg
-will only support \python 3.5 and higher.
-Removing \python 2 support will allow the use of new, \python 3-only features,
-will simplify the code base, and reduce the testing overhead for the package.
+removing the support for \python 2 \citep{ape10}: future versions of \astropypkg
+will only support \python 3.5 or higher.
+Removing \python 2 support will allow the use of new \python 3-only features,
+simplify the code base, and reduce the testing overhead for the package.
 \astropypkg version 3.0 is currently scheduled for January 2018.
@@
 testing and documentation standards of \astropy.
-Some of these new efforts includes an initiative to develop tools for
+Some of these new efforts include an initiative to develop tools for
 spectroscopy \citep[\package{specutils}, \package{specreduc}, \package{specviz}]
-{ape13}, integration of LSST software, and packages to support HEALPIX
+{ape13}, integration of LSST software, and support for HEALPIX
 projection. %\citep{astropy-healpix}
@@
 
-The \astropypkg core package documentation contains narrative descriptions of
-the package functionality along with detailed usage notes for functions,
+The documentation of the \astropypkg core package contains narrative descriptions of
+the package's functionality, along with detailed usage notes for functions,
 classes, and modules.
-While useful as a reference and for more advanced \python users, it is not the
-right entry-point for all users or learning environments.
+While useful as a reference for more experienced \python users, it is not the
+proper entry-point for other users or learning environments.
 In the near future, we will launch a new resource for learning to use both the
 \astropypkg core package and the many packages in the broader \astropy
-ecosystem, under the name `\emph{Learn Astropy}.'
+ecosystem, under the name \emph{Learn Astropy}.
 

### 2017-12-09 main.tex
Address review comments

--- 2017-12-08 main.tex
@@
 \section{Introduction} \label{sec:intro}
+% first draft by Moritz (hamogu)
+% heavily edited by Adrian PW - let me know if you want to revert anything!
 All astronomical research makes use of software in some way.  Astronomy as a field has thus long supported the development of software tools
@@
 are then typically used by smaller groups for more domain-specific purposes.
-Both in packages meant for wider distribution and in scripts specific to
-particular research projects, a library that addresses common astronomical tasks
-simplifies the software development process.
-The users of such a library then also benefit from a community and ecosystem
-built around a shared foundation.
+Whether for a package meant for wide distribution or for scripts and programs
+for a specific research project, the implementation of astronomical software can
+be eased through the use of a library that provides core functionality that is
+common to many astronomical tasks.
+The users of such software then also benefit from a community and ecosystem
+built around a common foundation.
 The \astropy project has grown to become this community for \python astronomy
 software, and the \astropypkg core package a feature-rich \python library.
+
+%\inlinecomment{Tom R}{the 'this community' above is a bit too general - do we mean it is the only community in astronomy, or in the Python astronomy world?
+I'd change this to either 'to become this community for Python astronomy software' or 'to become such a community'.
+For instance yt had a community before we came along for the simulation community, so I want to make sure we don't claim we are the only community out there.}
+%\inlinecomment{Perry G}{Agreed}
 
@@
 in \sectionname~\ref{sec:future}.
-
-This article is not intended as an introduction to \astropypkg, nor does it replace the \astropypkg documentation.
-Instead, it describes the way the \astropy community is organized and the current state of the \astropypkg package.
 
@@
 The \astropy project, as of the v2.0 release, does not receive any direct financial support for
-the development of \astropypkg.  Development of the software, all supporting materials, and community support are provided
+the development of \astropypkg.  Development of the software, all supporting materials, and community support is provided
 by individuals who work on the \astropy project in their own personal
@@
 is a 501(c)(3) nonprofit that supports and promotes world-class, innovative,
-open source scientific computing.} organization. NumFOCUS has, to date, covered the direct costs incurred by the \astropy project.
+open source scientific computing.} organization. NumFOCUS has to date covered the direct costs incurred by the \astropy project.
 
@@
 At the foundation is the \astropypkg core package, which provides general
-functionality (e.g., coordinate transformations, reading and writing
-astronomical files, and units) or base classes for other
+functionality (e.g., coordinate transformations, reading and writing astronomical
+files) or base classes for other
 packages to utilize for a common interface (e.g., \texttt{NDData}).
@@
 
-As of \astropypkg version 2.0, units and quantities, prevalent in most of its
-subpackages, have become a key concept for using the package as a whole.
-Units are intimately entwined in the definition of astronomical coordinates;
-Thus, nearly all functionality in the \texttt{astropy.coordinates} subpackage
-(see \sectionname~\ref{sec:coordinates}) depends on them.
-For most other subpackages, quantities are at least accepted and often expected
+As of \astropypkg version 2.0, units and quantities are prevalent in most other
+\astropypkg subpackages and are thus a key concept for using the package as a
+whole.
+Units are intimately entwined in the definition of astronomical coordinates and
+thus nearly all functionality in the \texttt{astropy.coordinates} subpackage
+(see \sectionname~\ref{sec:coordinates}) depends on this functionality.
+For most other subpackages, quantities are at least accepted, and often expected
 by default.
@@
 The motivation and key concepts behind this subpackage were described in detail
-in the previous paper \citep{astropy}. Therefore, we primarily highlight new
-features and improvements here.
+in the previous paper \citep{astropy}, and thus here we primarily highlight new
+features and improvements.
 
@@
         functions that expect \texttt{Quantity} objects, we often want to
-        enforce that the input units have the correct physical type.
+        enforce that the input units have the correct type.
         For example, we may want to require only length-type \texttt{Quantity}
         objects.
-        \texttt{astropy.units} provides a tool called \texttt{quantity\_input()}
-        that can perform this varification automatically to avoid repetitive
-        code.
+        These requirements often lead to implementing repetitive code for
+        validating \texttt{Quantity} inputs.
+        \texttt{astropy.units} now provides a \python decorator,
+        \texttt{quantity\_input()}, that does this verification automatically.
 
@@
 spherical angles are Galactic longitude (\texttt{l}) and latitude (\texttt{b}).
-Each \texttt{Frame} class defines its own component names and preferred \texttt{Representation} class.
+Each of the \texttt{Frame} classes define their own component names and
+preferred \texttt{Representation} class.
 The frame-specific component names map to corresponding components on the
@@
 data.
-For most frames, the preferred representation is spherical, although this is
+For most frames the preferred representation is spherical, although this is
 determined primarily by the common use in the astronomical community.
@@
 \texttt{astropy.coordinates}.
-Custom user-implemented \texttt{Frame} classes that define transformations to
+Custom, user-implemented \texttt{Frame} classes that define transformations to
 any reference frame in this graph can then be transformed to any of the other
@@
 Instead, \texttt{astropy.coordinates} provides a high-level interface to
-representing astronomical coordinates through the \texttt{SkyCoord} class,
-which was designed to provide a single class that
+representing astronomical coordinates through the \texttt{SkyCoord} class.
+The \texttt{SkyCoord} class was designed to provide a single class that
 accepts a wide range of possible inputs.
@@
     cases the transformed velocity components have limited accuracy because the
-    transformations are done numerically instead of analytically.
-    \figurename~\ref{fig:frame-transform-graph} highlights which
+    transformations are done numerically.
+    The visualization of the coordinate frame transform graph highlights which
     velocity transformations can be done exactly and which transformations are
@@
     These ephemerides can be computed either using analytic approximations from
-    ERFA or from downloaded JPL ephemerides (the latter requires the
+    ERFA, or from downloaded JPL ephemerides (the latter requires the
     \package{jplephem}\footnote{\url{https://github.com/brandon-rhodes/python-jplephem}}
@@
 
-In order to check the accuracy of the coordinate transformations in
-\package{astropy.coordinates}, we have created a set of benchmarks that we use
-to compare transformations between a set of coordinate frames for a number of
-packages\footnote{\url{http://www.astropy.org/coordinates-benchmark/summary.html}}.
-Since no package can be guaranteed to implement all transformations to
-arbitrary precision and some transformations are sometimes subject to
-interpretation of standards (in particular in the case of Galactic coordinates),
-we do not designate any of the existing packages as the ``ground truth'' but
-instead compare each tool to all other tools. The benchmarks are thus useful
-beyond the \astropy project since they allow all of the tools to be compared to
-all other tools. The tools included in the benchmark at the moment include the
-\astropypkg core package, Kapteyn \citep{kapteyn}, NOVAS \citep{novas},
-PALpy \citep{pal}, PyAST \citep[a wrapper for AST, described in][]{ast},
-PyTPM\footnote{\url{https://github.com/phn/pytpm}}, PyEphem \citep{pyephem},
-and pySLALIB \citep[a Python wrapper for SLALIB, described in][]{slalib}.
-
-The benchmarks are meant to evolve over time and include an increasing variety
-of cases. At the moment, the benchmarks are set up as follows --
-we have generated a standard set of 1000 pairs of random longitudes/latitudes
-that we use in all benchmarks. Each benchmark is then defined using an input
-and output coordinate frame, using all combinations of FK4, FK5, Galactic,
-ICRS, and Ecliptic frames. For now, we set the epoch of observation to J2000.
-We also set the frame to J2000 (for FK5 and Ecliptic) and B1950 (for FK4).
-In the future, we plan to include a larger variety of epochs and equinoxes,
-as well as tests of conversion to/from Altitude/Azimuth. For each benchmark,
-we convert the 1000 longitudes/latitudes from the input/output frame with all
-tools and quantify the comparison by looking at the median, mean, maximum,
-and standard deviation of the absolute separation of the output coordinates
-from each pair of tools.
-
-\tablename~\ref{tab:coordinate_benchmarks} gives an example of the relative
-accuracy of the conversion from FK4 to Galactic coordinates for all pairs of
-tools. This shows, for example, that \astropy, Kapteyn, and PyTPM agree
-perfectly (to the precision shown), while PALpy, pySLALIB, and PyAST also
-agree perfectly amongst themselves. However, there is an offset of around
-0.2\arcsec\space with the former three packages. Finally, PyEphem disagrees
-with other packages by 0.4--0.8\arcsec. These values are only meant to be
-illustrative and will change over time as the benchmarks are refined and the
-packages updated.
+In order to check the accuracy of the coordinate transformations in \package{astropy.coordinates}, we have created a set of benchmarks that we use to compare transformations between a set of coordinate frames for a number of packages\footnote{\url{http://www.astropy.org/coordinates-benchmark/summary.html}}.
+Since
+no package can be guaranteed to implement all transformations to arbitrary precision, and since some transformations are sometimes subject to interpretation of standards (in particular in the case of Galactic coordinates), we do not designate any of the existing packages as the `ground truth' but instead compare each tool to all other tools.
+The benchmarks are thus useful beyond the \astropy project since they allow all of the tools to be compared to all other tools.
+The tools included in the benchmark at the moment include the \astropypkg core package, Kapteyn \citep{kapteyn}, NOVAS \citep{novas}, PALpy \citep{pal}, PyAST \citep[a wrapper for AST, described in][]{ast}, PyTPM\footnote{\url{https://github.com/phn/pytpm}}, PyEphem \citep{pyephem}, and pySLALIB \citep[a Python wrapper for SLALIB, described in][]{slalib}.
+
+The benchmarks are meant to evolve over time and include an increasing variety of cases.
+At the moment, the benchmarks are set up as follows - we have generated a standard set of 1000 pairs of random longitudes/latitudes that we use in all benchmarks.
+Each benchmark is then defined using an input and output coordinate frame, using all combinations of FK4, FK5, Galactic, ICRS and Ecliptic frames.
+For now we set the epoch of observation to J2000, and the frame to J2000 in the case of the FK5 and ecliptic frames and B1950 for the FK4 frame, but in future we plan to include a larger variety of epochs and equinoxes, as well as tests of conversion to/from Altitude/Azimuth.
+For each benchmark, we convert the 1000 longitudes/latitudes from the input/output frame with all tools and quantify the comparison by looking at the median, mean, maximum, and standard deviation of the absolute separation of the output coordinates from each pair of tools.
+\tablename~\ref{tab:coordinate_benchmarks} gives an example of the relative accuracy of the conversion from FK4 to Galactic coordinates for all pairs of tools.
+This shows for example that \astropy, Kapteyn and PyTPM agree perfectly (to the precision shown), while PALpy, pySLALIB, and PyAST also agree perfectly amongst themselves, but show an offset of around 0.2\arcsec with the former three packages.
+Finally, PyEphem disagrees with other packages by 0.4--0.8\arcsec.
+These values are only meant to be illustrative and will change over time as the benchmarks are refined and packages are updated.
 %\inlinecomment{Perry G}{Wouldn't the table be better represented as a matrices?
@@
         standardized.
-With the location of a source on the sky (i.e., a \texttt{SkyCoord}
-object), the location of an observatory on Earth (i.e., an
+        With the location of a source on the sky (i.e. a \texttt{SkyCoord}
+        object), the location of an observatory on Earth (i.e. an
         \texttt{EarthLocation} object), and time values as \texttt{Time}
@@
 with attributes for accessing metadata, the world-coordinate system (WCS),
-uncertainty arrays matched to the shape of the data, and other traits.
-Building on this interface, the \texttt{NDData} class provides a minimal
-working implementation for storing \package{numpy} arrays. These classes serve
-as useful base classes for package authors wishing to develop their own classes
-for specific use cases and as containers for exchanging gridded data.
-
-The classes \texttt{NDDataRef}, \texttt{NDDataArray}, and \texttt{CCDData}
-extend the base storage functionality with options to do basic arithmetic
-(addition, subtraction, multiplication, and division), including error
-propagation in limited cases, and slicing of the dataset based on grid
-coordinates that appropriately handles masking, errors, and units (if present).
-Additionally, the \texttt{CCDData} class also provides reading and writing from
-and to FITS files and uses data structures from \astropypkg, like \texttt{WCS},
-to represent the file contents abstractly.
-
-The \package{astropy.nddata.utils} module provides utilities that can operate
-on either plain \package{numpy} arrays or any of the classes in the
-\package{astropy.nddata} subpackage. It features a class for representing
-two-dimensional image cutouts, allowing one to easily link pixels in the cutout
-to those in the original image or vice versa, to convert
-between world and pixel coordinates in the cutout, and to overlay the cutout
-on images. Functions to enlarge or reduce an image by doing block replication
-or reduction are also provided.
+uncertainty arrays matched to the data shape, and other traits.
+Building on this interface, the \texttt{NDData} class provides a minimal working implementation for storing \package{numpy} arrays.
+These classes serve as useful base classes for package authors wishing to develop their own classes for specific use cases and as containers for exchanging gridded data.
+
+The classes \texttt{NDDataRef}, \texttt{NDDataArray}, and \texttt{CCDData} extend the base storing functionality with options to do basic arithmetic (addition, subtraction, multiplication, and division) including error propagation in limited cases and slicing of the dataset based on grid coordinates that appropriately handles masking, errors, and units (if present).
+Additionally, the \texttt{CCDData} class also provides reading and writing from and to FITS files and uses data structures from \astropypkg, like \texttt{WCS}, to represent the contents of a file abstractly.
+
+The \package{astropy.nddata.utils} module provides utilities that can operate on either plain \package{numpy} arrays or any of the classes in the \package{astropy.nddata} subpackage.
+It features a class for representing two-dimensional image cutouts, allowing one to easily link pixels in the cutout to pixels in the original image or from the image to the cutout, to convert between world and pixel coordinates in the cutout, and to overlay the cutout on images.
+Functions to enlarge or reduce an image by doing block replication or reduction are also provided.
 
@@
 The package was described in detail in \cite{astropy}.
-Thus, in what follows, we only summarize key new features or updates to
-\package{astropy.table} since the previous \astropy paper.
+
+Next, we summarize key new features or updates to \package{astropy.table}.
 
@@
 
-A table can contain data that naturally form groups; For example, it may
+A table can contain data that naturally forms groups -- for example it may
 contain multiple observations of a few sources at different points in time
-and in different bands. Then, we may want to split the table into groups based
-on the combination of source observed and the band, after which we combine the
-results for each combination of source and band in some way (e.g., finding
+and in different bands. We may then want to split the table into groups based
+on the combination of source observed and the band, and then combine the
+results for each combination of source and band in some way (for example finding
 the mean or standard deviation of the fluxes or magnitudes over time) or filter
@@
 have distinct columns, we may want to stack them ``horizontally'' to create a
-new table with the same rows but all columns. For other situations, more generic
-table concatenation or join are also possible when two tables share some
-columns.
+new table with the same rows but all columns. For other situations, more general
+table concatenations or joins are also possible when two tables share some
+common columns.
 
@@
 
-The \texttt{Table} object now allows \texttt{Quantity}, celestial
-coordinate (\texttt{SkyCoord}), and date/time (\texttt{Time}) objects to
-be used as columns. It also provides a general way for other user-defined
-objects to be used as columns. This makes it possible, for instance, to easily
-represent catalogs of sources or time series as in \astropy, while having both the
-benefits of the \texttt{Table} object (e.g., accessing specific rows/columns
-or groups of them and combining tables) and of, for example,
-the \texttt{SkyCoord} or the \texttt{Time} classes (e.g., converting the
-coordinates to a different frame or accessing the date/time in the desired time scale).
+The \texttt{Table} object now allows \texttt{Quantity} objects, celestial
+coordinate objects (\texttt{SkyCoord}), and date/time objects (\texttt{Time}) to
+be used as columns, and also provides a general way for other user-defined
+objects to be used as columns. This makes it possible for example to easily
+represent catalogs of sources or time series as in Astropy, and having both the
+benefits of the \texttt{Table} object (such as accessing specific rows/columns
+or groups of rows/columns, combining tables, and so on) and the benefits of e.g.
+the \texttt{SkyCoord} or \texttt{Time} classes (such as converting the
+coordinates to a different frame, or accessing the date/time as a modified
+Julian date or in another time scale).
 
@@
 The \package{astropy.io.ascii} subpackage now includes a significantly faster
-Cython/C engine for reading and writing ASCII files. This is available for most
-of the common formats.  On average, the new engine is about 4 to 5 times faster
-than the corresponding pure-\python implementation and is often comparable to
-the speed of the \package{pandas} \citep{pandas} ASCII file interface.  The
+Cython/C engine for reading and writing ASCII files. This is available for the
+most common formats.  On average the new engine is about 4 to 5 times faster
+than the corresponding pure-\python implementation, and is often comparable to
+the speed of the \package{Pandas} \citep{pandas} ASCII file interface.  The
 fast reader has parallel processing option that allows harnessing multiple
 cores for input parsing to achieve even greater speed gains.  By default,
-\texttt{read()} and \texttt{write()} will attempt to use the fast Cython/C engine
+\texttt{read()} and \texttt{write()} will attempt to use the fast C engine
 when dealing with compatible formats. Certain features of the full read
-/ write interface are unavailable in the fast version, in which case the
+/ write interface are not available in the fast version, in which case the
 pure-\python version will automatically be used.
@@
 The \package{astropy.io.ascii} subpackage now provides the capability
-to read a table within an HTML file or web URL into an \astropypkg
-\texttt{Table} object. A \texttt{Table} object can now also
+to read a table within an HTML file or web URL into an astropy
+\texttt{Table} object. Conversely a \texttt{Table} object can now
 be written out as an HTML table.
@@
 Command-line scripts are now available for printing a summary of the HDUs in
-FITS file(s) (\texttt{fitsinfo}) and for printing the header information to
+a FITS file(s) (\texttt{fitsinfo}) and for printing the header information to
 the screen in a human-readable format (\texttt{fitsheader}).
 
-FITS files are now loaded \emph{lazily} (this default behavior can be
-deactivated, if needed), where all HDUs are not loaded until
-requested. This should provide substantial speed-ups when using the
+FITS files are now loaded \emph{lazily} (the default behavior, which can be
+deactivated if needed), where all HDUs are not loaded until they are
+requested. This should provide substantial speedups for situations using the
 convenience functions (e.g., \texttt{getheader()} or \texttt{getdata()}) to
-get an HDU that is near the beginning of many in a file.
+get HDU’s that are near the front of a file with many HDUs.
 
@@
 % Tom R. -- unit support
-
+\subsubsection{Overview}
 The \package{astropy.modeling} subpackage provides a framework for representing
@@
 
-Models are defined by their parameters and initialized by providing values for them. The
-names of the parameters are stored in a list, \texttt{Model.param\_names}. Parameters are complex objects.
-They store additional information -- default value, default unit, and parameter constraints. Parameter
-values and constraints can be updated by assignment. Supported constraints include \texttt{fixed},
-and \texttt{tied} parameters, and \texttt{bounds} on parameter values. The framework supports also models
-for which the the number of parameters and their names are defined by another argument.
-A typical example is a polynomial model defined by its degree.
+Most models are defined by parameters and maintain an ordered list of parameter names, \texttt{Model.param\_names}.
+A model is instantiated by passing in values (scalars or arrays) for its parameters.
+A parameter is a descriptor that provides a proxy for the value and stores additional information -- default value, default unit, and parameter constraints.
+The value and constraints can be updated by assignment.
+Supported parameter constraints include \texttt{fixed}, and \texttt{tied} parameters, and \texttt{bounds} on parameter values.
+Most models have a fixed parameter set but for some (e.g., polynomials), the number of parameters is defined by another argument (e.g., degree-of-freedom in the case of polynomials).
+Parameters support arithmetic operations and are combined with the inputs during evaluation using the \package{numpy} broadcasting rules.
 A model is evaluated by calling it as a function.
 
-If an analytical inverse of a model exists it is already defined and can be
-accessed  by calling \texttt{Model.inverse}. In addition, \texttt{Model.inverse} can be assigned
-another model which represents a computed inverse.
+Models have a \texttt{Model.inverse} property, which returns the analytical inverse, if available, or raises an exception otherwise.
+This is a settable property; i.e.
+a model instance can be assigned as inverse to another model.
+For example, a polynomial model can be assigned as an inverse to another polynomial model.
 
@@
 
-\package{astropy.modeling} provides an efficient way to set up the same type of model with many different sets of parameter values.
-This creates a model set that can be efficiently evaluated.
-For example, in PSF (point spread function) photometry, all objects in an image will have a PSF of the same functional form, but with different positions and amplitudes.
+\package{astropy.modeling} provides an efficient way to instantiate the same type of model with many different sets of parameter values by passing the \texttt{n\_models} argument on instantiation, which sets the number of models to instantiate.
+This creates a model set that can be efficiently evaluated for example, in PSF (point spread function) photometry, all objects in an image will have a PSF of the same functional form, but with different positions and amplitudes.
 
@@
 \subsubsection{Creating New Models}
-If arithmetic combinations of existing models is not sufficient, new model classes can be defined in different ways.
-The \package{astropy.modeling} provides tools to turn a simple function into a full-featured model, but it also allows extending the build-in model class with arbitrary code.
+
+New model classes can be created in two ways:
+\begin{enumerate}
+   \item The simplest way is to use the \texttt{custom\_model} decorator in modeling with a user-defined function that takes the inputs and model parameters as arguments.
+   \item It is also possible to create an arbitrarily complex custom model based on the \texttt{Model} class.
+\end{enumerate}
 
@@
 
-In the next major release after version 3.0, scheduled for
-mid-2018, the focus will be on optimization of the code and improved
+In the next major release after version 3.0, scheduled for the summer of
+2018, the focus will be on optimization of the code and improved
 documentation.
@@
 
-\acknowledgments
-
-Who to thank?  numfocus, GSOC, Python Software Foundation
-
-We thank the many web services that make developing and maintaining this package
-feasible, such as GitHub, Travis CI, Appveyor, CircleCI, and Read the Docs.
+\acknowledgments The \astropy community is supported by and makes use
+of a number of organizations and services outside the traditional
+academic community. We thank Google for financing and organizing the
+Google Summer of Code (GSoC) program, that has funded severals
+students per year to work on \astropy related projects over the
+summer. These students often turn into long-term contributors. We also
+thank numfocus and the Python Software Foundation for financial
+support. Within the academic community, we thank
+institutions that make it possible that developers on
+their staff can contribute their time to the development of
+\astropy projects.
+
+Furthermore, the \astropy packages would not exist
+in their current form without a number of web services for code
+hosting, continuous integration, and documentation; in particular,
+\astropy heavily relies on GitHub, Travis CI, Appveyor, CircleCI, and
+Read the Docs.
+
+\astropypkg interfaces with the SIMBAD database,
+operated at CDS, Strasbourg, France. It also makes use of the ERFA library \citep{erfa}, 
+which in turn derives from the IAU SOFA Collection\footnote{http://www.iausofa.org} developed by the International Astronomical Union Standards of Fundamental Astronomy \citep{sofa}.
 

### 2017-12-09 main.tex
Modified the order of the comparison of the different packages
The table now is ordered so the packages that have a closer agreement
are shown together. This way I find it easier to find how they cluster
between themselves.
comments by bspiorz

@@
 summer. These students often turn into long-term contributors. We also
-thank numfocus and the Python Software Foundation for financial
+thank NumFOCOS and the Python Software Foundation for financial
 support. Within the academic community, we thank
-institutions that make it possible that developers on
+institutions that make it possible that astronomers and other developers on
 their staff can contribute their time to the development of

### 2017-12-10 main.tex
Several very small fixes
In particular:
- typos
- Unify style from "us" to "the astropy project"

@@
 stability is essential.
-The latest LTS release (v2.0) is also the last one that supports \python 2; It
+The latest LTS release (v2.0) is also the last one that supports \python 2; it
 will receive bug fixes until the end of 2019 \citep{ape10}.
@@
 since version v0.2 (previously described in \citealt{astropy}).  The \astropypkg
+package 
 provides a full log of changes\footnote{\url{https://github.com/astropy/astropy/blob/stable/CHANGES.rst}}
@@
 
-A table can contain data that naturally form groups; For example, it may
+A table can contain data that naturally form groups; for example, it may
 contain multiple observations of a few sources at different points in time
@@
 convenience functions (e.g., \texttt{getheader()} or \texttt{getdata()}) to
-get an HDU that is near the beginning of many in a file.
+get an HDU that is near the beginning in a file with many HDUs.
 
@@
 The goal is to make it easy to extend the fitting framework to create new fitters.
-The optimizers available in \astropypkg version 2.0 are Levenberg--Marquardt, Simplex, SLSQP, and LinearLSQFitter (which is based on \texttt{numpy.linalg} that provides exact solution for linear models).
+The optimizers available in \astropypkg version 2.0 are Levenberg--Marquardt, Simplex, SLSQP, and LinearLSQFitter (which is based on \texttt{numpy.linalg} that provides exact solutions for linear models).
 
@@
 
-In this section, we describe these tools, including robust statistical estimators, circular statistics, periodograms, spatial statistics, and histogram binning.
+In this section, we describe these tools. %, including robust statistical estimators, circular statistics, periodograms, spatial statistics, and histogram binning.
 

### 2017-12-10 main.tex
typo

--- 2017-12-09 main.tex
@@
 
-\acknowledgments
-
-Who to thank?  numfocus, GSOC, Python Software Foundation
-
-We thank the many web services that make developing and maintaining this package
-feasible, such as GitHub, Travis CI, Appveyor, CircleCI, and Read the Docs.
+\acknowledgments The \astropy community is supported by and makes use
+of a number of organizations and services outside the traditional
+academic community. We thank Google for financing and organizing the
+Google Summer of Code (GSoC) program, that has funded severals
+students per year to work on \astropy related projects over the
+summer. These students often turn into long-term contributors. We also
+thank NumFOCUS and the Python Software Foundation for financial
+support. Within the academic community, we thank
+institutions that make it possible that astronomers and other developers on
+their staff can contribute their time to the development of
+\astropy projects.
+
+Furthermore, the \astropy packages would not exist
+in their current form without a number of web services for code
+hosting, continuous integration, and documentation; in particular,
+\astropy heavily relies on GitHub, Travis CI, Appveyor, CircleCI, and
+Read the Docs.
+
+\astropypkg interfaces with the SIMBAD database,
+operated at CDS, Strasbourg, France. It also makes use of the ERFA library \citep{erfa},
+which in turn derives from the IAU SOFA Collection\footnote{http://www.iausofa.org} developed by the International Astronomical Union Standards of Fundamental Astronomy \citep{sofa}.
 

### 2017-12-10 figures/convolution_figure.py
add convolution figure generating script and add labels to panels

@@ -1,0 +1,85 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+from astropy.io import fits
+from astropy.utils.data import get_pkg_data_filename
+from astropy.convolution import Gaussian2DKernel
+from scipy.signal import convolve as scipy_convolve
+from astropy.convolution import convolve
+
+
+# Load the data from data.astropy.org
+filename = get_pkg_data_filename('galactic_center/gc_msx_e.fits')
+hdu = fits.open(filename)[0]
+
+# Scale the file to have reasonable numbers
+# (this is mostly so that colorbars don't have too many digits)
+# Also, we crop it so you can see individual pixels
+img = hdu.data[50:90, 60:100] * 1e5
+
+# This example is intended to demonstrate how astropy.convolve and
+# scipy.convolve handle missing data, so we start by setting the
+# brightest pixels to NaN to simulate a "saturated" data set
+img[img > 2e1] = np.nan
+
+# We also create a copy of the data and set those NaNs to zero.  We'll
+# use this for the scipy convolution
+img_zerod = img.copy()
+img_zerod[np.isnan(img)] = 0
+
+# We smooth with a Gaussian kernel with stddev=1
+# It is a 9x9 array
+kernel = Gaussian2DKernel(stddev=1)
+
+# Convolution: scipy's direct convolution mode spreads out NaNs (see
+# panel 2 below)
+scipy_conv = scipy_convolve(img, kernel, mode='same', method='direct')
+
+# scipy's direct convolution mode run on the 'zero'd' image will not
+# have NaNs, but will have some very low value zones where the NaNs were
+# (see panel 3 below)
+scipy_conv_zerod = scipy_convolve(img_zerod, kernel, mode='same',
+                                  method='direct')
+
+# astropy's convolution replaces the NaN pixels with a kernel-weighted
+# interpolation from their neighbors
+astropy_conv = convolve(img, kernel)
+
+
+# Now we do a bunch of plots.  In the first two plots, the originally masked
+# values are marked with red X's
+plt.figure(1, figsize=(12, 12)).clf()
+ax1 = plt.subplot(2, 2, 1)
+im = ax1.imshow(img, vmin=-2., vmax=2.e1, origin='lower',
[…]

### 2017-12-10 main.tex
fix typo

--- 2017-12-10 main.tex
@@
 
-\acknowledgments The \astropy community is supported by and makes use
-of a number of organizations and services outside the traditional
-academic community. We thank Google for financing and organizing the
-Google Summer of Code (GSoC) program, that has funded severals
-students per year to work on \astropy related projects over the
-summer. These students often turn into long-term contributors. We also
-thank NumFOCUS and the Python Software Foundation for financial
-support. Within the academic community, we thank
-institutions that make it possible that astronomers and other developers on
-their staff can contribute their time to the development of
-\astropy projects.
-
-Furthermore, the \astropy packages would not exist
-in their current form without a number of web services for code
-hosting, continuous integration, and documentation; in particular,
-\astropy heavily relies on GitHub, Travis CI, Appveyor, CircleCI, and
-Read the Docs.
-
-\astropypkg interfaces with the SIMBAD database,
-operated at CDS, Strasbourg, France. It also makes use of the ERFA library \citep{erfa},
-which in turn derives from the IAU SOFA Collection\footnote{http://www.iausofa.org} developed by the International Astronomical Union Standards of Fundamental Astronomy \citep{sofa}.
+\acknowledgments
+
+Who to thank?  numfocus, GSOC, Python Software Foundation
+
+We thank the many web services that make developing and maintaining this package
+feasible, such as GitHub, Travis CI, Appveyor, CircleCI, and Read the Docs.
 

### 2017-12-10 main.tex
remove png ext

--- 2017-12-10 main.tex
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{convolution_example.png}
+\includegraphics[width=\textwidth]{convolution_example}
 \caption{%

### 2017-12-10 main.tex
add link and citation to skyserver

@@
 \section{Introduction} \label{sec:intro}
-All astronomical research makes use of software in some way.  Astronomy as a field has thus long supported the development of software tools
-for astronomical tasks: from scripts that enable individual scientific research to software packages for small collaborations to data reduction pipelines for survey operations.
-Some software packages are or were supported by large institutions and are intended for a wide range of users. These packages typically provide some level of documentation and user support or
-training.
+All astronomical research makes use of software in some way.
+Astronomy as a field has thus long supported the development of software tools
+for astronomical tasks, such as scripts that enable individual scientific
+research, software packages for small collaborations, and data reduction
+pipelines for survey operations.
+Some software packages are or were supported by large institutions and are
+intended for a wide range of users.
+These packages therefore typically provide some level of documentation and user
+support or training.
 Other packages are developed by individual researchers or research groups and
 are then typically used by smaller groups for more domain-specific purposes.
-Both in packages meant for wider distribution and in scripts specific to
+For both packages meant for wider distribution and for scripts specific to
 particular research projects, a library that addresses common astronomical tasks
@@
 In this way, its genesis differs from but builds upon many substantial and
-% * <bsipocz@gmail.com> 2017-11-13T13:13:08.884Z:
-%
-% how do astroy builds upon these? or it's more like builds upon the developer experience?
-%
-%
-% ^.
 former astronomical software development efforts that were commissioned or
-initiated through large institutional support, for example IRAF \citep[developed
+initiated through large institutional support, such as IRAF \citep[developed
 at NOAO;][]{IRAF}, MIDAS \citep[developed at ESO;][]{MIDAS}, or Starlink
@@
 maintained by the East Asian Observatory;][]{starlink1982,starlink2013}.
-More recently, community-driven efforts have seen significant success in the astronomical sciences \citep{yt}.
+More recently, community-driven efforts have seen significant success in the astronomical sciences (e.g., \citealt{yt}).
 
@@
 \citep[\package{matplotlib};][]{matplotlib}, tens of thousands of other high-quality and easy-to-use
-packages are available, which can help with tasks that are not astronomy specific but
-might be performed in the course of astronomical research; e.g., interfacing with
-databases or statistical inferences. More recently, the development of package managers such as
-Anaconda\footnote{\url{https://anaconda.org/}} has significantly streamlined the installation
-process for many libraries, lowering many barriers to entry.
+packages are available, which can help with tasks that are not specific to astronomy but
+might be performed in the course of astronomical research, e.g., interfacing with
+databases, or statistical inferences.
+More recently, the development and mainstream adoption of package managers such
+as Anaconda\footnote{\url{https://anaconda.org/}} has significantly streamlined
+the installation process for many libraries, lowering many barriers to entry.
 
@@
 (\sectionname~\ref{sec:infrastructure}). We end with a short vision for
-the future of \astropy in particular and astronomical software in general
-in \sectionname~\ref{sec:future}.
-
-This article is not intended as an introduction to \astropypkg, nor does it replace the \astropypkg documentation.
-Instead, it describes the way the \astropy community is organized and the current state of the \astropypkg package.
+the future of \astropy and astronomical software in general in
+\sectionname~\ref{sec:future}.
+
+This article is not intended as an introduction to \astropypkg, nor does it
+replace the \astropypkg documentation. Instead, it describes the way the
+\astropy community is organized and the current state of the \astropypkg
+package.
 
@@
 For resolving disagreements about the \astropypkg core package or other \astropy-managed code, the coordination committee primarily acts to work toward consensus, or when consensus is difficult to achieve, generally acts as a ``tie-breaker.''
-The committee also oversees affiliated package applications to ensure they are in keeping with \astropy's vision and philosophy, as well as the associated procedures.
-Additionally, the committee oversees the assignment of roles (primarily driven by already-existing contributions), and increasingly has acted as the ``face'' of the Project, providing contact with organizations like NumFOCUS (the body that holds any potential funding in trust for \astropy) or the American Astronomical Society (AAS).
+The committee also oversees affiliated package applications to ensure that they
+are in keeping with \astropy's vision and
+philosophy,\footnote{\url{http://docs.astropy.org/en/stable/development/vision.html}}
+as well as the associated procedures.
+Additionally, the committee oversees the assignment of roles (primarily driven by already-existing contributions), and increasingly has acted as the ``face'' of the Project, providing contact with organizations like NumFOCUS (the body that holds any potential funding in trust for \astropy) and the American Astronomical Society (AAS).
 
@@
 contributor base.  A leading group of 6 developers have each added over 1000
-commits to the repository, and $\sim 20$ more core contributors with at least
-100 commits.
+commits to the repository, and $\sim 20$ more core contributors have contributed
+at least 100 commits.
 However, the distribution of contribution level (number of commits) continues
@@
 
-A major part of the \astropy project is the concept of
-``Affiliated Packages''. An affiliated package is an astronomy-related
+A major part of the \astropy project is the concept of ``Affiliated Packages.''
+An affiliated package is an astronomy-related
 \python package that is not part of the \astropypkg core package, but
@@
 
-Affiliated packages are listed on the main \astropy website and advertised to the community through \astropy mailing lists.
-Therefore, becoming an affiliated package is a good way for new and existing packages to gain exposure while promoting \astropy's high standard for code and documentation quality.
-This process of listing and promoting affiliated packages is one way in which the \astropy project tries to increase code re-use in the astronomical community.
+Affiliated packages are listed on the main \astropy website and advertised to
+the community through \astropy mailing lists; a list of current affiliated
+packages is included in \tablename~\ref{tab:registry}.
+Becoming an affiliated package is a good way for new and existing packages to
+gain exposure while promoting \astropy's high standard for code and
+documentation quality.
+This process of listing and promoting affiliated packages is one way in which
+the \astropy project tries to increase code re-use in the astronomical
+community.
 
@@
 stability is essential.
-The latest LTS release (v2.0) is also the last one that supports \python 2; it
-will receive bug fixes until the end of 2019 \citep{ape10}.
+The latest LTS release (version 2.0) is also the last one that supports \python
+2; it will receive bug fixes until the end of 2019 \citep{ape10}.
 
@@
 
-% Removing unless this gets written about in
-% a later version
-% This section should be a straight forward/factual description of the current
-% funding and support provided to astropy with the purpose of explaining the
-% current structure to the community
-
-%\subsection{Difficulty of reversing design choices}
-%Deciding if a feature should be included
-%difficulty to decide where general use ends and "handy feature for some" starts, i.e. how to reject PRs or deal with maintenance burden
-
-\section{Astropy Core Package v2.0}
+\section{Astropy Core Package Version 2.0}
 \label{sec:core}
@@
 In this section, we highlight new features introduced or substantially improved
-since version v0.2 (previously described in \citealt{astropy}).  The \astropypkg
+since version 0.2 (previously described in \citealt{astropy}).  The \astropypkg
 package
@@
 
-\tablename~\ref{tab:coordinate_benchmarks} gives an example of the relative
-accuracy of the conversion from FK4 to Galactic coordinates for all pairs of
-tools. This shows, for example, that \astropy, Kapteyn, and PyTPM agree
-perfectly (to the precision shown), while PALpy, pySLALIB, and PyAST also
-agree perfectly amongst themselves. However, there is an offset of around
-0.2\arcsec\space with the former three packages. Finally, PyEphem disagrees
-with other packages by 0.4--0.8\arcsec. These values are only meant to be
-illustrative and will change over time as the benchmarks are refined and the
-packages updated.
-%\inlinecomment{Perry G}{Wouldn't the table be better represented as a matrices?
-Or perhaps as a matrix as a crude image with colors or intensities representing the size of the quantity.
-Is the difference between median and mean significant enough to warrant showing both?
-A link to the actual numbers may satisfy readers that want the exact values, but I suspect the majority don't need to see that precision.}
-\begin{table}
-\begin{center}
-\begin{tabular}{llcccc}
-\hline
-\hline
-Package 1 & Package 2 & Median & Mean & Maximum & Std. Dev. \\
-          &           & arcsec & arcsec & arcsec & arcsec \\
-\hline
-astropy  &  kapteyn  & 0.000  & 0.000 & 0.000 & 0.000 \\
-\nodata  &  palpy    & 0.218  & 0.196 & 0.249 & 0.056 \\
-\nodata  &  pyast    & 0.218  & 0.196 & 0.249 & 0.056 \\
-\nodata  &  pyephem  & 0.459  & 0.458 & 0.860 & 0.231 \\
-\nodata  &  pyslalib & 0.218  & 0.196 & 0.249 & 0.056 \\
-\nodata  &  pytpm    & 0.000  & 0.000 & 0.000 & 0.000 \\
-kapteyn  &  palpy    & 0.218  & 0.196 & 0.249 & 0.056 \\
-\nodata  &  pyast    & 0.218  & 0.196 & 0.249 & 0.056 \\
-\nodata  &  pyephem  & 0.459  & 0.458 & 0.860 & 0.231 \\
-\nodata  &  pyslalib & 0.218  & 0.196 & 0.249 & 0.056 \\
-\nodata  &  pytpm    & 0.000  & 0.000 & 0.000 & 0.000 \\
-palpy    &  pyast    & 0.000  & 0.000 & 0.000 & 0.000 \\
-\nodata    &  pyephem  & 0.563  & 0.570 & 1.012 & 0.253 \\
-\nodata    &  pyslalib & 0.000  & 0.000 & 0.000 & 0.000 \\
-\nodata    &  pytpm    & 0.218  & 0.196 & 0.249 & 0.056 \\
-pyast    &  pyephem  & 0.563  & 0.570 & 1.012 & 0.253 \\
-\nodata    &  pyslalib & 0.000  & 0.000 & 0.000 & 0.000 \\
-\nodata    &  pytpm    & 0.218  & 0.196 & 0.249 & 0.056 \\
-pyephem  &  pyslalib & 0.563  & 0.570 & 1.012 & 0.253 \\
-\nodata  &  pytpm    & 0.459  & 0.458 & 0.860 & 0.231 \\
-pyslalib &  pytpm    & 0.218  & 0.196 & 0.249 & 0.056 \\
-\hline
-\end{tabular}
-\end{center}
-\caption{Comparison of the accuracy of the FK4 to Galactic transformation between different packages.\label{tab:coordinate_benchmarks}}
-\end{table}
+\figurename~\ref{fig:coordinate_benchmarks} visualizes the relative accuracy of
+the conversion from FK4 to Galactic coordinates for all pairs of tools that
+implement this transformation.
+In this figure, the color of the cell indicates the maximum difference (in
+arcseconds) between the two tools over the 1000 longitude-latitude pairs tested.
+This figure shows, for example, that \astropypkg, Kapteyn, and PyTPM agree with
+sub-milliarcsecond differences (light colors, small differences), while PALpy,
+pySLALIB, and PyAST also agree amongst themselves.
+However, there is an offset of around 0.2\arcsec\space between the two groups.
+Finally, PyEphem disagrees with all other packages by 0.4--0.8\arcsec (darker
+colors, large differences).
+These values are only meant to be illustrative and will change over time as the
+benchmarks are refined and the packages updated.
+
+\begin{figure}
+  \includegraphics[width=\textwidth]{coordinates-benchmark.pdf}
+  \caption{
+    Comparison matrix of the maximum difference between longitude-latitude
+    values in a set of 1000 random points transformed from FK4 to Galactic
+    with the different packages.
+    Darker colors (larger differences) are more significant disagreements.
+    \label{fig:coordinate_benchmarks}
+  }
+\end{figure}
 
@@
 \package{astropy.table} since the previous \astropy paper.
-
-%\inlinecomment{Perry G}{Some mention that some of these are inspired by Pandas?}
 
@@
 get an HDU that is near the beginning in a file with many HDUs.
-
-% \inlinecomment{Tom R}{too detailed? I don't think we need to mention every single performance enhancement, right?}
-
-% \subsubsection{\texttt{.misc}: YAML serialization}
-
-% The new \package{astropy.io.misc.yaml} module allows converting astropy
-% objects into a standard YAML format.  This can be used beyond
-% \texttt{astropy.io.misc.yaml}: for example, to serialize the metadata of
-% tables before saving to other formats like HDF5.
-
-%\inlinecomment{BMS}{Maybe move the command line tools into a separate subsection to highlight them (even though we mostly only have fits related scripts)?
-They are supposed to be used more frequently by individual users.}
-%\inlinecomment{hamogu}{MY feeling is that this section is too detailed already. If I had written it, I would not have mentioned the scripts at all.}
 
@@
 
-% hamogu: I comented this out because we don't have prrof that it's
-% ``uniquly'' useful. THe developers of e.g. ISIS, Sherpa, for even IRAF
-% will probably disagree.
-%The recently-added support for \package{astropy.units} in models and fitters
-%make it a uniquely powerful package for working with astrophysical models.
-
 \subsubsection{Single Model Definition and Evaluation}
-
-%\inlinecomment{hamogu: I tihnk this is too techical. I know it's a complex subpackage but I had trouble understanding this section even as a regular user.}
 
@@
 The goal is to make it easy to extend the fitting framework to create new fitters.
-The optimizers available in \astropypkg version 2.0 are Levenberg--Marquardt, Simplex, SLSQP, and LinearLSQFitter (which is based on \texttt{numpy.linalg} that provides exact solutions for linear models).
-
-%\inlinecomment{APW}{Add citations for the different optimizaton algorithms in paragraph above?}
+The optimizers available in \astropypkg version 2.0 are Levenberg--Marquardt (\texttt{scipy.optimize.leastsq}), Simplex (\texttt{scipy.optimize.fmin}), SLSQP (\texttt{scipy.optimize.slsqp}), and LinearLSQFitter (\texttt{numpy.linalg.lstsq} which provides exact solutions for linear models).
 
@@
 
-The \package{astropy.convolution} subpackage implements `normalized convolution' \citep[e.g.,][]{Knutsson1993}, which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.
-An example of this is given in \figurename~\ref{fig:convolution-example}.
-In versions $\leq 1.3$, the direct convolution and Fast Fourier Transform (FFT) convolution approaches were not consistent, with FFT convolution implementing normalized convolution and direct convolution implementing a different approach.
-As of version 2.0, the two methods are consistent and include a suite of consistency checks.
+The \package{astropy.convolution} subpackage implements
+\textit{normalized convolution} \citep[e.g.,][]{Knutsson1993}, an image
+reconstruction technique in which missing data are ignored during the
+convolution and replaced with values interpolated using the kernel.
+An example is given in \figurename~\ref{fig:convolution-example}.
+In \astropypkg versions $\leq 1.3$, the direct convolution and Fast Fourier Transform (FFT)
+convolution approaches were inconsistent, with only the latter implementing
+normalized convolution.
+As of version 2.0, the two methods now agree and include a suite of
+consistency checks.
 
@@
     An example showing different modes of convolution available in the \python
-    ecosystem.  The red x's mark pixels that are set to NaN in the original data
-    (a).  If the data are convolved with a Gaussian kernel on a $9\times 9$ grid using
-    scipy's direct convolution (b), any pixel within range of the original NaN
-    pixels is also set to NaN.  Panel (c) shows what happens if the NaNs are set
-    to zero first: the originally NaN regions are depressed relative to their
-    surroundings.  Finally, panel (d) shows \astropypkg's convolution behavior,
-    where the missing pixels are replaced with values interpolated from their
-    surroundings using the convolution kernel.
+    ecosystem.  The red x's mark pixels that are set to \texttt{NaN} in the
+    original data (a).  If the data are convolved with a Gaussian kernel on a
+    $9\times 9$ grid using
+    \package{scipy}'s direct convolution (b), any pixel within range of the original \texttt{NaN}
+    pixels is also set to \texttt{NaN}.  Panel (c) shows what happens if the
+    \texttt{NaN}s are set to zero first: the originally \texttt{NaN} regions are
+    depressed relative to their surroundings.  Finally, panel (d) shows
+    \astropypkg's convolution behavior, where the missing pixels are replaced
+    with values interpolated from their surroundings using the convolution
+    kernel.
     \label{fig:convolution-example}
@@
 
-\cite{Lupton2004} describe an ``optimal'' algorithm for producing red-green-blue (RGB) composite images from three separate high-dynamic range arrays.
-The \package{astropy.visualization} subpackage provides a convenience function to create such a color image.
-It also includes an associated set of classes to provide alternate scalings.
-This functionality was contributed by developers from the Large Synoptic Survey Telescope (LSST) and serves as an example of contribution to \astropy from a more traditional engineering organization \citep{Jennes2016}.
-
-The Sloan Digital Sky Survey (SDSS) SkyServer color images were made using a variation on this technique.
-As an example, in \figurename~\ref{fig:ngc6977} we show an RGB color image of the Hickson 88 group, centered near NGC~6977.
-This image was generated from SDSS images using the \package{astropy.visualization} tools.
+\cite{Lupton2004} describe an ``optimal'' algorithm for producing
+RGB composite images from three separate high-dynamic range
+arrays. The \package{astropy.visualization} subpackage provides a convenience
+function to create such a color image.  It also includes an associated set of
+classes to provide alternate scalings.
+This functionality was contributed by developers from the Large Synoptic Survey
+Telescope (LSST) and serves as an example of contribution to \astropy from a
+more traditional engineering organization \citep{Jennes2016}.
+
+The Sloan Digital Sky Survey (SDSS) SkyServer color images were made using a
+variation on this technique.  As an example, in \figurename~\ref{fig:ngc6977},
+we show an RGB color image of the Hickson 88 group, centered near
+NGC~6977.\footnote{\url{http://skyserver.sdss.org/dr13/en/tools/chart/navi.aspx?ra=313.12381&dec=-5.74611}
+This image was generated from SDSS images using the
+\package{astropy.visualization} tools.
 
@@
 a range of functionality used by many different disciplines
-in astronomy. It is not a complete set of statistic tools, but rather
+in astronomy. It is not a complete set of statistical tools, but rather
 a still growing collection of useful features.
-
-% The current review process for contributions to the \package{astropy.stats} package includes review of the code, documentation, testing, and scientific merit of the inclusion.
-When necessary, scientific reviewers outside of the maintainers will be sought for their input on new pull requests.
-
-In this section, we describe these tools. %, including robust statistical estimators, circular statistics, periodograms, spatial statistics, and histogram binning.
 
@@
 Within \astropy, all submitted code is reviewed by at least one, but typically
-more, members of the \astropy community, who provide feedback to contributors
-to help improve their skills.
+more, members of the \astropy community, who provide feedback to contributors,
+which helps to improve their skills.
 As a community, \astropy follows an explicit code of conduct \citep{ape8} and treats all
@@
 operated at CDS, Strasbourg, France. It also makes use of the ERFA library \citep{erfa},
-which in turn derives from the IAU SOFA Collection\footnote{http://www.iausofa.org} developed by the International Astronomical Union Standards of Fundamental Astronomy \citep{sofa}.
+which in turn derives from the IAU SOFA Collection\footnote{\url{http://www.iausofa.org}} developed by the International Astronomical Union Standards of Fundamental Astronomy \citep{sofa}.
 
@@
 \appendix
+
 \section{List of Affiliated Packages}
 
-%\inlinecomment{SMC}{Can a brief description of each code be added?}
-
 \begin{longrotatetable}
-  \begin{deluxetable*}{ccccc}
+    \begin{deluxetable*}{cccp{3in}c}
     \tablecaption{Registry of affiliated packages.}
@@
 
-\begin{deluxetable*}{cccc}
+\begin{deluxetable*}{cccp{3in}c}
   \tablecaption{Registry of provisionally accepted affiliated packages.}
@@
         \colhead{PyPI Name} &
-        \colhead{Maintainer}
+        \colhead{Maintainer} &
+        \colhead{Citation}
       }

### 2017-12-10 main.tex
typos

@@
 we show an RGB color image of the Hickson 88 group, centered near
-NGC~6977.\footnote{\url{http://skyserver.sdss.org/dr13/en/tools/chart/navi.aspx?ra=313.12381&dec=-5.74611}
+NGC~6977.\footnote{\url{http://skyserver.sdss.org/dr13/en/tools/chart/navi.aspx?ra=313.12381&dec=-5.74611}}
 This image was generated from SDSS images using the

### 2017-12-10 figures/make_ngc6977_image.py
make rgb figure 2 panel

@@ -1,21 +1,55 @@
 from astropy.io import fits
+import astropy.units as u
 from astropy.utils.data import get_pkg_data_filename
-from astropy.visualization import make_lupton_rgb
+from astropy.visualization import make_lupton_rgb, astropy_mpl_style
+from astropy.wcs import WCS
+import matplotlib.pyplot as plt
+plt.style.use(astropy_mpl_style)
 
 # load the data
 g_name = get_pkg_data_filename('visualization/reprojected_sdss_g.fits.bz2')
 r_name = get_pkg_data_filename('visualization/reprojected_sdss_r.fits.bz2')
 i_name = get_pkg_data_filename('visualization/reprojected_sdss_i.fits.bz2')
-g = fits.open(g_name)[0].data
-r = fits.open(r_name)[0].data
-i = fits.open(i_name)[0].data
+
+g = fits.open(g_name)[0]
+r = fits.open(r_name)[0]
+i = fits.open(i_name)[0]
 
 # extract a smaller region around the Hickson 88 group
 slc = (slice(0, 285), slice(33, 318))
-gp = g[slc]
-rp = r[slc]
-ip = i[slc]
+gp = g.data[slc]
+rp = r.data[slc]
+ip = i.data[slc]
 
-# make the figure
-rgb = make_lupton_rgb(ip*0.8, rp, gp*1.3, Q=10, stretch=0.4,
-                      filename='ngc6977.png')
+# make the figure - stretch 1
+rgb1 = make_lupton_rgb(ip, rp, gp)
+rgb2 = make_lupton_rgb(ip*0.8, rp, gp*1.3, Q=10, stretch=0.4)
+
+wcs = WCS(g.header)
+
+fig, axes = plt.subplots(1, 2, figsize=(8, 4),
+                         sharex=True, sharey=True,
+                         subplot_kw=dict(projection=wcs))
+
+axes[0].imshow(rgb1, origin='lower')
+axes[0].set_title('default parameters', fontsize=18)
+axes[0].set_adjustable('box-forced')
+
+axes[1].imshow(rgb2, origin='lower')
+axes[1].set_title('Q=10, stretch=0.4', fontsize=18)
+axes[1].set_adjustable('box-forced')
+
+for i in [0,1]:
+    lon, lat = axes[i].coords
+    axes[i].coords.grid(True, color='white', ls='solid', alpha=0.4)
+
[…]

### 2017-12-10 main.tex
remove reference to veloicities in figure since colors are removed
add link to vision

--- 2017-12-10 main.tex
@@
     transformations are done numerically instead of analytically.
-    \figurename~\ref{fig:frame-transform-graph} highlights which
-    velocity transformations can be done exactly and which transformations are
-    done using a finite-difference scheme.
     The low-level interface for specifying and transforming velocity data (see

### 2017-12-10 main.tex
clean up more instances of astropy vs astropypkg

@@
 The package was described in detail in \cite{astropy}.
-The default cosmology in \astropy version 2.0 is given by the values in \cite{2016A&A...594A..13P}.
+The default cosmology in \astropypkg version 2.0 is given by the values in \cite{2016A&A...594A..13P}.
 
@@
 
-\subsection{Future versions of the \astropypkg core and affiliated packages}
+\subsection{Future versions of the Astropy core and affiliated packages}
 

### 2017-12-10 main.tex
clean up version 2.0 vs. v2.0

@@
 
-\section{Astropy Core Package v2.0}
+\section{Astropy Core Package version 2.0}
 \label{sec:core}
@@
     the next point) is currently experimental.
-    As such, in v2.0, only the \texttt{Frame} classes (and not the
+    As such, in version 2.0, only the \texttt{Frame} classes (and not the
     \texttt{SkyCoord} class) support handling velocities.

### 2017-12-10 main.tex
spell check. fixes #24

@@
 Beyond what is mentioned below, most subpackages have seen increased performance
-since the release of the v0.2 package.
+since the release of the version 0.2 package.
 
@@
     An example showing different modes of convolution available in the \python
-    ecosystem.  The red x's mark pixels that are set to NaN in the original data
+    ecosystem.  The red x's mark pixels that are set to \texttt{NaN} in the original data
     (a).  If the data are convolved with a Gaussian kernel on a $9\times 9$ grid using
-    scipy's direct convolution (b), any pixel within range of the original NaN
-    pixels is also set to NaN.  Panel (c) shows what happens if the NaNs are set
-    to zero first: the originally NaN regions are depressed relative to their
+    \package{scipy}'s direct convolution (b), any pixel within range of the original \texttt{NaN}
+    pixels is also set to \texttt{NaN}.  Panel (c) shows what happens if the \texttt{NaN}s are set
+    to zero first: the originally \texttt{NaN} regions are depressed relative to their
     surroundings.  Finally, panel (d) shows \astropypkg's convolution behavior,

### 2017-12-11 main.tex
Remove a bunch of old comments - either irrelevant or moved to issues.

--- 2017-12-10 main.tex
@@
 
-%\subsection{Difficulty of reversing design choices}
-%Deciding if a feature should be included
-%difficulty to decide where general use ends and "handy feature for some" starts, i.e. how to reject PRs or deal with maintenance burden
-
 \section{Astropy Core Package version 2.0}
@@
 
-% \subsection{Analytic Functions}
-% moved to models and depreciated --
-% just here for completeness at the moment
-%\inlinecomment{BMS}{I suggest to order the subsection lexicographically as reading the draft the current order seemed very random (unlike at the docs page where they the grouping logic is obvious)}
-%\inlinecomment{Tom R}{the only issue is if we rely on having e.g. units described first if they are used later}
-
 \subsection{Units}\label{sec:units}
@@
 
-%\subsubsection{Derivatives of coordinate representations}
-
-%\inlinecomment{Tom R}{does this really warrant a separate section or is it just a byproduct of the velocity stuff that can be mentioned in 3.3.2?}
-
-    %As mentioned above, the \texttt{Representation} classes act like
-    %three-dimensional vectors.
-    %\texttt{astropy.coordinates} now also supports handling first derivatives of
-    %vectors / representations through the new \texttt{Differential} classes.
-    %The \texttt{Differential} classes are currently used internally within the
-    %\texttt{Frame} classes to store the velocity data.
-
 \subsubsection{Solar System Ephemerides}
@@
 The optimizers available in \astropypkg version 2.0 are Levenberg--Marquardt, Simplex, SLSQP, and LinearLSQFitter (which is based on \texttt{numpy.linalg} that provides exact solutions for linear models).
-
-%\inlinecomment{APW}{Add citations for the different optimizaton algorithms in paragraph above?}
 
@@
 
-% The current review process for contributions to the \package{astropy.stats} package includes review of the code, documentation, testing, and scientific merit of the inclusion.
-When necessary, scientific reviewers outside of the maintainers will be sought for their input on new pull requests.
-
-In this section, we describe these tools. %, including robust statistical estimators, circular statistics, periodograms, spatial statistics, and histogram binning.
-
 % Steve C.: overview, circular stats,
@@
 the benefit of the community.
-
-%\inlinecomment{BMS}{should we mention the refactored infra here?  e.g. pytest-astropy and sphinx-astropy?}
 

### 2017-12-11 main.tex
final comments

@@
 
-The \package{astropy.convolution} subpackage implements `normalized convolution' \citep[e.g.,][]{Knutsson1993}, which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.
+The \package{astropy.convolution} subpackage implements
+``normalized convolution'' \citep[e.g.,][]{Knutsson1993} that is an image
+reconstruction technique, in which missing data are ignored during the
+convolution and replaced with values interpolated using the kernel;
 An example of this is given in \figurename~\ref{fig:convolution-example}.
-In versions $\leq 1.3$, the direct convolution and Fast Fourier Transform (FFT) convolution approaches were not consistent, with FFT convolution implementing normalized convolution and direct convolution implementing a different approach.
-As of version 2.0, the two methods are consistent and include a suite of consistency checks.
+In \astropypkg versions $\leq 1.3$, the direct convolution and Fast Fourier Transform (FFT)
+convolution approaches were inconsistent, with the latter implementing
+normalized convolution, while the former a different approach.
+As of version 2.0, the two methods now agree and include a suite of
+consistency checks.
 
@@
 
-The \package{cosmology} package contains classes for representing different cosmologies and functions for calculating commonly used quantities such as look-back time and distance.
-The package was described in detail in \cite{astropy}.
-The default cosmology in \astropypkg version 2.0 is given by the values in \cite{2016A&A...594A..13P}.
+The \package{cosmology} package contains classes for representing different
+cosmologies and functions for calculating commonly used quantities such as
+look-back time and distance.   The package was described in detail in
+\cite{astropy}.  The default cosmology in \astropypkg version 2.0 is given by
+the values in \cite{2016A&A...594A..13P}.
 

### 2017-12-11 registry.tex

@@
 \href{http://github.com/gammapy/gammapy}{gammapy} & No & \href{https://pypi.python.org/pypi/gammapy}{gammapy} & Christoph Deil & \citealt{gammapy}\\
-\href{http://github.com/ejeschke/ginga}{ginga} & Yes & \href{https://pypi.python.org/pypi/ginga}{ginga} & Eric Jeschke and Pey-Lian Lim & \citealt{ginga}\\
+\href{http://github.com/ejeschke/ginga}{ginga} & Yes & \href{https://pypi.python.org/pypi/ginga}{ginga} & Eric Jeschke and Pey Lian Lim & \citealt{ginga}\\
 \href{https://github.com/glue-viz/glue}{Glue} & Yes & \href{https://pypi.python.org/pypi/glueviz}{glueviz} & Chris Beaumont and Thomas Robitaille & \citealt{glue}\\

### 2017-12-11 main.tex
remove extraneous comment
intro edits

@@
 former astronomical software development efforts that were commissioned or
-initiated through large institutional support, for example IRAF \citep[developed
+initiated through large institutional support, such as IRAF \citep[developed
 at NOAO;][]{IRAF}, MIDAS \citep[developed at ESO;][]{MIDAS}, or Starlink
@@
 open source scientific computing.} organization. NumFOCUS has, to date, covered the direct costs incurred by the \astropy project.
-
-% Removing unless this gets written about in
-% a later version
-% This section should be a straight forward/factual description of the current
-% funding and support provided to astropy with the purpose of explaining the
-% current structure to the community
-
-%\subsection{Difficulty of reversing design choices}
-%Deciding if a feature should be included
-%difficulty to decide where general use ends and "handy feature for some" starts, i.e. how to reject PRs or deal with maintenance burden
 

### 2017-12-11 main.tex
next section edits

@@
 For resolving disagreements about the \astropypkg core package or other \astropy-managed code, the coordination committee primarily acts to work toward consensus, or when consensus is difficult to achieve, generally acts as a ``tie-breaker.''
-The committee also oversees affiliated package applications to ensure they are
-in keeping with \astropy's vision and
+The committee also oversees affiliated package applications to ensure that they
+are in keeping with \astropy's vision and
 philosophy,\footnote{\url{http://docs.astropy.org/en/stable/development/vision.html}}
 as well as the associated procedures.
-Additionally, the committee oversees the assignment of roles (primarily driven by already-existing contributions), and increasingly has acted as the ``face'' of the Project, providing contact with organizations like NumFOCUS (the body that holds any potential funding in trust for \astropy) or the American Astronomical Society (AAS).
+Additionally, the committee oversees the assignment of roles (primarily driven by already-existing contributions), and increasingly has acted as the ``face'' of the Project, providing contact with organizations like NumFOCUS (the body that holds any potential funding in trust for \astropy) and the American Astronomical Society (AAS).
 

### 2017-12-11 figures/make_coord_benchmarks_fig.py
update figure to remove lower triangle

@@ -1,0 +1,87 @@
+"""
+Originally contributed by @dpshelio
+"""
+
+import matplotlib.pyplot as plt
+import numpy as np
+
+cc = [[0, 0], [0, 0]]
+ap = [[0.218, 0.196], [0.249, 0.056]]  # astropy - palpy
+ae = [[0.459, 0.458], [0.860, 0.231]]  # astropy - pyephem
+pe = [[0.563, 0.570], [1.012, 0.253]]  # palpy - pyephem
+data = {'astropy-astropy':   cc,
+        'astropy-kapteyn':   cc, 'kapteyn-astropy':  cc,
+        'astropy-pytpm':     cc, 'pytpm-astropy':    cc,
+        'astropy-palpy':     ap, 'palpy-astropy':    ap,
+        'astropy-pyast':     ap, 'pyast-astropy':    ap,
+        'astropy-pyslalib':  ap, 'pyslalib-astropy': ap,
+        'astropy-pyephem':   ae, 'pyephem-astropy':  ae,
+        'kapteyn-kapteyn':   cc,
+        'kapteyn-pytpm':     cc, 'pytpm-kapteyn':    cc,
+        'kapteyn-palpy':     ap, 'palpy-kapteyn':    ap,
+        'kapteyn-pyast':     ap, 'pyast-kapteyn':    ap,
+        'kapteyn-pyslalib':  ap, 'pyslalib-kapteyn': ap,
+        'kapteyn-pyephem':   ae, 'pyephem-kapteyn':  ae,
+        'pytpm-pytpm':       cc,
+        'pytpm-palpy':       ap, 'palpy-pytpm':      ap,
+        'pytpm-pyast':       ap, 'pyast-pytpm':      ap,
+        'pytpm-pyslalib':    ap, 'pyslalib-pytpm':   ap,
+        'pytpm-pyephem':     ae, 'pyephem-pytpm':    ae,
+        'palpy-palpy':       cc,
+        'palpy-pyast':       cc, 'pyast-palpy':      cc,
+        'palpy-pyslalib':    cc, 'pyslalib-palpy':   cc,
+        'palpy-pyephem':     pe, 'pyephem-palpy':    pe,
+        'pyast-pyast':       cc,
+        'pyast-pyslalib':    cc, 'pyslalib-pyast':   cc,
+        'pyast-pyephem':     pe, 'pyephem-pyast':    pe,
[…]

### 2017-12-11 figures/make_coord_benchmarks_fig.py
label colorbar

@@ -83,5 +83,7 @@ for i in range(0, 2*n):
         ax.plot([i+0.5, i+0.5], [-0.5, np.floor(i+2.5)-0.5], color='#888888', alpha=0.25,
                 **grid_style)
 
-fig.colorbar(c)
+cb = fig.colorbar(c)
+cb.set_label('accuracy metric [arcsec]')
+
 fig.savefig('coordinates-benchmark.pdf')

### 2017-12-11 main.tex
remove benchmarks table

@@
 
-\tablename~\ref{tab:coordinate_benchmarks} gives an example of the relative
-accuracy of the conversion from FK4 to Galactic coordinates for all pairs of
-tools. This shows, for example, that \astropy, Kapteyn, and PyTPM agree
-perfectly (to the precision shown), while PALpy, pySLALIB, and PyAST also
-agree perfectly amongst themselves. However, there is an offset of around
-0.2\arcsec\space with the former three packages. Finally, PyEphem disagrees
-with other packages by 0.4--0.8\arcsec. These values are only meant to be
-illustrative and will change over time as the benchmarks are refined and the
-packages updated.
-%\inlinecomment{Perry G}{Wouldn't the table be better represented as a matrices?
-Or perhaps as a matrix as a crude image with colors or intensities representing the size of the quantity.
-Is the difference between median and mean significant enough to warrant showing both?
-A link to the actual numbers may satisfy readers that want the exact values, but I suspect the majority don't need to see that precision.}
-\begin{table}
-\begin{center}
-\begin{tabular}{llcccc}
-\hline
-\hline
-Package 1 & Package 2 & Median & Mean & Maximum & Std. Dev. \\
-          &           & arcsec & arcsec & arcsec & arcsec \\
-\hline
-astropy  &  kapteyn  & 0.000  & 0.000 & 0.000 & 0.000 \\
-\nodata  &  pytpm    & 0.000  & 0.000 & 0.000 & 0.000 \\
-\nodata  &  palpy    & 0.218  & 0.196 & 0.249 & 0.056 \\
-\nodata  &  pyast    & 0.218  & 0.196 & 0.249 & 0.056 \\
-\nodata  &  pyslalib & 0.218  & 0.196 & 0.249 & 0.056 \\
-\nodata  &  pyephem  & 0.459  & 0.458 & 0.860 & 0.231 \\
-kapteyn  &  pytpm    & 0.000  & 0.000 & 0.000 & 0.000 \\
-\nodata  &  palpy    & 0.218  & 0.196 & 0.249 & 0.056 \\
-\nodata  &  pyast    & 0.218  & 0.196 & 0.249 & 0.056 \\
-\nodata  &  pyslalib & 0.218  & 0.196 & 0.249 & 0.056 \\
-\nodata  &  pyephem  & 0.459  & 0.458 & 0.860 & 0.231 \\
-pytpm    &  palpy    & 0.218  & 0.196 & 0.249 & 0.056 \\
-\nodata  &  pyast    & 0.218  & 0.196 & 0.249 & 0.056 \\
-\nodata  &  pyslalib & 0.218  & 0.196 & 0.249 & 0.056 \\
-\nodata  &  pyephem  & 0.459  & 0.458 & 0.860 & 0.231 \\
-palpy    &  pyast    & 0.000  & 0.000 & 0.000 & 0.000 \\
-\nodata  &  pyslalib & 0.000  & 0.000 & 0.000 & 0.000 \\
-\nodata  &  pyephem  & 0.563  & 0.570 & 1.012 & 0.253 \\
-pyast    &  pyslalib & 0.000  & 0.000 & 0.000 & 0.000 \\
-\nodata  &  pyephem  & 0.563  & 0.570 & 1.012 & 0.253 \\
-pyslalib &  pyephem  & 0.563  & 0.570 & 1.012 & 0.253 \\
-\hline
-\end{tabular}
-\end{center}
-\caption{Comparison of the accuracy of the FK4 to Galactic transformation between different packages.\label{tab:coordinate_benchmarks}}
-\end{table}
+\figurename~\ref{fig:coordinate_benchmarks} visualizes the relative accuracy of
+the conversion from FK4 to Galactic coordinates for all pairs of tools.
+This figure shows, for example, that \astropy, Kapteyn, and PyTPM agree
+perfectly (light colors, small differences), while PALpy, pySLALIB, and PyAST
+also agree perfectly amongst themselves.
+However, there is an offset of around 0.2\arcsec\space with the former three
+packages.
+Finally, PyEphem disagrees with other packages by 0.4--0.8\arcsec.
+These values are only meant to be illustrative and will change over time as the
+benchmarks are refined and the packages updated.
 
@@
   \caption{
-    Comparison matrix of the accuracy values shown on
-    table~\ref{tab:coordinate_benchmarks} of the FK4 to Galactic transformation
-    between the different packages. Each comparison block shows four squares
-    representing the median, mean, maximum and standard deviation going from
-    left to right and bottom to top.
+    Comparison matrix of the accuracy values of the FK4 to Galactic
+    transformation between the different packages. Each comparison block shows
+    four squares representing the median, mean, maximum and standard deviation
+    going from left to right and bottom to top.
     \label{fig:coordinate_benchmarks}

### 2017-12-11 main.tex

--- 2017-12-11 main.tex
@@
 The goal is to make it easy to extend the fitting framework to create new fitters.
-The optimizers available in \astropypkg version 2.0 are Levenberg--Marquardt, Simplex, SLSQP, and LinearLSQFitter (which is based on \texttt{numpy.linalg} that provides exact solutions for linear models).
+The optimizers available in \astropypkg version 2.0 are Levenberg--Marquardt (\texttt{scipy.optimize.leastsq}), Simplex (\texttt{scipy.optimize.fmin}), SLSQP (\texttt{scipy.optimize.slsqp}), and LinearLSQFitter (\texttt{numpy.linalg.lstsq} which provides exact solutions for linear models).
 

### 2017-12-11 figures/make_coord_benchmarks_fig.py
transpose figure

@@ -51,7 +51,7 @@ for i in range(n):
             M[2*j:2*j+2, 2*i:2*i+2] = np.array(data["{}-{}".format(names[j], names[i])])
 
 
-fig, ax = plt.subplots(1, 1, figsize=(7.5,6))
+fig, ax = plt.subplots(1, 1, figsize=(6,8.75))
 
 c = ax.imshow(M, cmap='YlOrBr', zorder=1)
 
@@ -59,31 +59,39 @@ maj_ticks = np.arange(0, 2*n, 2) + 0.5
 
 ax.set_xticks(maj_ticks)
 ax.set_yticks(maj_ticks)
-ax.set_xticklabels(names, fontsize=12)
-ax.set_yticklabels(names, fontsize=12)
-ax.set_xlim(2*n-0.5, -0.5)
+ax.set_xticklabels(names, fontsize=14)
+ax.set_yticklabels(names, fontsize=14)
 
-ax.xaxis.tick_top()
+ax.set_xlim(-0.5, 2*n-2.5+0.01)
+ax.set_ylim(2*n-0.5, 1.5-0.01)
 
 ax.spines['right'].set_visible(False)
-ax.spines['bottom'].set_visible(False)
+ax.spines['top'].set_visible(False)
 
 grid_style = dict(marker='', linewidth=1, zorder=8)
-for i in range(-1, 2*n+1, 2):
-    ax.plot([i-1.5, 2*n], [i+0.5, i+0.5], color='#333333', alpha=0.5,
-            **grid_style)
-    if i < 2*n-1:
-        ax.plot([i+0.5, i+0.5], [-0.5, i+2.5], color='#333333', alpha=0.5,
-                **grid_style)
 
+# "minor" grid
 for i in range(0, 2*n):
-    ax.plot([np.ceil(i-1.5)+0.5, 2*n], [i+0.5, i+0.5], color='#888888', alpha=0.25,
+    ax.plot([-.5, np.floor(i+.5)-.5], [i+0.5, i+0.5], color='#aaaaaa',
             **grid_style)
     if i < 2*n-1:
-        ax.plot([i+0.5, i+0.5], [-0.5, np.floor(i+2.5)-0.5], color='#888888', alpha=0.25,
+        ax.plot([i+0.5, i+0.5], [np.ceil(i+.5)+.5, 2*n], color='#aaaaaa',
                 **grid_style)
 
-cb = fig.colorbar(c)
-cb.set_label('accuracy metric [arcsec]')
[…]

### 2017-12-11 figures/make_coord_benchmarks_fig.py
oops, typo

@@ -45,10 +45,11 @@ n = len(names)
 M = np.zeros((2*n, 2*n))
 for i in range(n):
     for j in range(n):
-        if 2*i < 2*j:
+        if 2*i >= 2*j:
             M[2*j:2*j+2, 2*i:2*i+2] = np.nan
         else:
-            M[2*j:2*j+2, 2*i:2*i+2] = np.array(data["{}-{}".format(names[j], names[i])])
+            M[2*j:2*j+2, 2*i:2*i+2] = np.array(data["{}-{}".format(names[j],
+                                                                   names[i])])
 
 
 fig, ax = plt.subplots(1, 1, figsize=(6,8.75))

### 2017-12-11 figures/make_coord_benchmarks_fig.py
more tweaks

@@ -52,7 +52,7 @@ for i in range(n):
                                                                    names[i])])
 
 
-fig, ax = plt.subplots(1, 1, figsize=(6,8.75))
+fig, ax = plt.subplots(1, 1, figsize=(6,6))
 
 c = ax.imshow(M, cmap='YlOrBr', zorder=1)
 
@@ -87,7 +87,7 @@ for i in range(-1, 2*n+1, 2):
         ax.plot([i+0.5, i+0.5], [i+.5, 2*n], color='#666666',
                 **grid_style)
 
-cbaxes = fig.add_axes([0.125, 0.8, 0.775, 0.025])
+cbaxes = fig.add_axes([0.2, 0.825, 0.7, 0.025])
 cb = fig.colorbar(cax=cbaxes, mappable=c, orientation='horizontal')
 cb.set_label('accuracy metric [arcsec]', labelpad=10, fontsize=20)
 cb.ax.xaxis.set_ticks_position('top')
@@ -95,4 +95,5 @@ cb.ax.xaxis.set_label_position('top')
 [l.set_fontsize(14) for l in cb.ax.xaxis.get_ticklabels()]
 cb.set_clim(0, 1)
 
+fig.subplots_adjust(left=0.2, bottom=0.02)
 fig.savefig('coordinates-benchmark.pdf')

### 2017-12-11 main.tex
guide the colors
tighten up benchmark statements

--- 2017-12-11 main.tex
@@
 the conversion from FK4 to Galactic coordinates for all pairs of tools.
-This figure shows, for example, that \astropy, Kapteyn, and PyTPM agree
-perfectly (light colors, small differences), while PALpy, pySLALIB, and PyAST
-also agree perfectly amongst themselves.
-However, there is an offset of around 0.2\arcsec\space with the former three
-packages.
-Finally, PyEphem disagrees with other packages by 0.4--0.8\arcsec.
+This figure shows, for example, that \astropypkg, Kapteyn, and PyTPM agree with
+sub-milliarcsecond differences (light colors, small differences), while PALpy,
+pySLALIB, and PyAST also agree amongst themselves.
+However, there is an offset of around 0.2\arcsec\space between the two groups.
+Finally, PyEphem disagrees with all other packages by 0.4--0.8\arcsec (darker
+colors, large differences).
 These values are only meant to be illustrative and will change over time as the
@@
     going from left to right and bottom to top.
+    Darker colors (larger differences) are more significant disagreements.
     \label{fig:coordinate_benchmarks}

### 2017-12-11 main.tex
simplify text to refer to max

@@
 the conversion from FK4 to Galactic coordinates for all pairs of tools.
+In this figure, the color of the cell indicates the maximum difference (in
+arcsec) between the two tools over the 1000 longitude-latitude pairs tested.
 This figure shows, for example, that \astropypkg, Kapteyn, and PyTPM agree with
@@
   \caption{
-    Comparison matrix of the accuracy values of the FK4 to Galactic
-    transformation between the different packages. Each comparison block shows
-    four squares representing the median, mean, maximum and standard deviation
-    going from left to right and bottom to top.
+    Comparison matrix of the maximum difference between longitude-latitude
+    values in a set of 1000 random points transformed from FK4 to Galactic
+    with the different packages.
     Darker colors (larger differences) are more significant disagreements.

### 2017-12-11 figures/make_coord_benchmarks_fig.py
only show max diff

@@ -5,10 +5,12 @@ Originally contributed by @dpshelio
 import matplotlib.pyplot as plt
 import numpy as np
 
-cc = [[0, 0], [0, 0]]
-ap = [[0.218, 0.196], [0.249, 0.056]]  # astropy - palpy
-ae = [[0.459, 0.458], [0.860, 0.231]]  # astropy - pyephem
-pe = [[0.563, 0.570], [1.012, 0.253]]  # palpy - pyephem
+# max difference to 3 significant figures:
+cc = 0
+ap = 0.249 # astropy - palpy
+ae = 0.860 # astropy - pyephem
+pe = 1.012 # palpy - pyephem
+
 data = {'astropy-astropy':   cc,
         'astropy-kapteyn':   cc, 'kapteyn-astropy':  cc,
         'astropy-pytpm':     cc, 'pytpm-astropy':    cc,
@@ -42,29 +44,28 @@ names = ['astropy', 'kapteyn', 'pytpm', 'palpy', 'pyast', 'pyslalib', 'pyephem']
 n = len(names)
 
 # Fill a single 2D array with the data to visualize
-M = np.zeros((2*n, 2*n))
+M = np.zeros((n, n))
 for i in range(n):
     for j in range(n):
-        if 2*i >= 2*j:
-            M[2*j:2*j+2, 2*i:2*i+2] = np.nan
+        if i >= j:
+            M[j:j+1, i:i+1] = np.nan
         else:
-            M[2*j:2*j+2, 2*i:2*i+2] = np.array(data["{}-{}".format(names[j],
-                                                                   names[i])])
+            M[j:j+1, i:i+1] = data["{}-{}".format(names[j], names[i])]
 
-
+# Make the figure
 fig, ax = plt.subplots(1, 1, figsize=(6,6))
 
 c = ax.imshow(M, cmap='YlOrBr', zorder=1)
 
-maj_ticks = np.arange(0, 2*n, 2) + 0.5
+maj_ticks = np.arange(0, n, 1)
 
 ax.set_xticks(maj_ticks)
 ax.set_yticks(maj_ticks)
 ax.set_xticklabels(names, fontsize=14)
 ax.set_yticklabels(names, fontsize=14)
 
-ax.set_xlim(-0.5, 2*n-2.5+0.01)
-ax.set_ylim(2*n-0.5, 1.5-0.01)
+ax.set_xlim(-0.5, n-1.5+0.01)
[…]

### 2017-12-11 figures/make_coord_benchmarks_fig.py
bold astropy, default font

@@ -5,6 +5,10 @@ Originally contributed by @dpshelio
 import matplotlib.pyplot as plt
 import numpy as np
 
+from astropy.visualization import astropy_mpl_style
+plt.style.use(astropy_mpl_style)
+plt.rcParams['font.family'] = plt.rcParamsDefault['font.family']
+
 # max difference to 3 significant figures:
 cc = 0
 ap = 0.249 # astropy - palpy
@@ -61,8 +65,12 @@ maj_ticks = np.arange(0, n, 1)
 
 ax.set_xticks(maj_ticks)
 ax.set_yticks(maj_ticks)
-ax.set_xticklabels(names, fontsize=14)
-ax.set_yticklabels(names, fontsize=14)
+ax.set_xticklabels(names, fontsize=11)
+ax.set_yticklabels(names, fontsize=11)
+
+for l in ax.get_xticklabels():
+    if l.get_text() == 'astropy':
+        l.set_fontweight('bold')
 
 ax.set_xlim(-0.5, n-1.5+0.01)
 ax.set_ylim(n-0.5, 0.5-0.01)
@@ -77,15 +85,17 @@ for i in range(0, n):
     ax.plot([-.5, i+.5], [i+0.5, i+0.5], color='#aaaaaa',
             **grid_style)
     ax.plot([i+0.5, i+0.5], [i+.5, n], color='#aaaaaa',
-            **grid_style)
+                **grid_style)
 
 cbaxes = fig.add_axes([0.2, 0.825, 0.7, 0.025])
 cb = fig.colorbar(cax=cbaxes, mappable=c, orientation='horizontal')
-cb.set_label('max. difference [arcsec]', labelpad=10, fontsize=20)
+cb.set_label('max. difference [arcsec]', labelpad=10, fontsize=16)
 cb.ax.xaxis.set_ticks_position('top')
 cb.ax.xaxis.set_label_position('top')
-[l.set_fontsize(16) for l in cb.ax.xaxis.get_ticklabels()]
+[l.set_fontsize(12) for l in cb.ax.xaxis.get_ticklabels()]
 cb.set_clim(0, 1)
+
+ax.grid(False)
 
 fig.subplots_adjust(left=0.2, bottom=0.02)
 fig.savefig('coordinates-benchmark.pdf')

### 2017-12-11 main.tex
spell arcseconds

@@
 In this figure, the color of the cell indicates the maximum difference (in
-arcsec) between the two tools over the 1000 longitude-latitude pairs tested.
+arcseconds) between the two tools over the 1000 longitude-latitude pairs tested.
 This figure shows, for example, that \astropypkg, Kapteyn, and PyTPM agree with

### 2017-12-11 main.tex
clarify why novas is missing. fixes #53

@@
 \figurename~\ref{fig:coordinate_benchmarks} visualizes the relative accuracy of
-the conversion from FK4 to Galactic coordinates for all pairs of tools.
+the conversion from FK4 to Galactic coordinates for all pairs of tools that
+implement this transformation.
 In this figure, the color of the cell indicates the maximum difference (in

### 2017-12-11 registry.tex
update the package registry for affiliated packages

@@
+\href{http://github.com/aplpy/aplpy.git}{APLpy} & Yes & \href{https://pypi.python.org/pypi/APLpy}{APLpy} & Thomas Robitaille and Eli Bressert &  \\
 \href{https://github.com/astropy/astroscrappy}{Astro-SCRAPPY} & Yes & \href{https://pypi.python.org/pypi/astroscrappy}{astroscrappy} & Curtis McCully & \citealt{astroscrappy} \\
-\href{https://github.com/astropy/astroplan}{astroplan} & No & \href{https://pypi.python.org/pypi/astroplan}{astroplan} & Brett Morris & \citealt{astroplan_AAS}\\
-\href{http://github.com/astropy/astroquery}{astroquery} & Yes & \href{https://pypi.python.org/pypi/astroquery}{astroquery} & Adam Ginsburg and Brigitta Sipocz & \citealt{astroquery}\\
-\href{http://github.com/astropy/ccdproc}{ccdproc} & Yes & \href{https://pypi.python.org/pypi/ccdproc}{ccdproc} & Steven Crawford, Matt Craig, and Michael Seifert & \citealt{ccdproc}\\
+\href{http://github.com/astroML/astroML}{astroML} & Yes & \href{https://pypi.python.org/pypi/astroML}{astroML} & Jake Vanderplas &  \\
+\href{https://github.com/astropy/astroplan}{astroplan} & No & \href{https://pypi.python.org/pypi/astroplan}{astroplan} & Brett Morris & \citealt{astroplan_AAS} \\
+\href{http://github.com/astropy/astroquery.git}{astroquery} & Yes & \href{https://pypi.python.org/pypi/astroquery}{astroquery} & Adam Ginsburg and Brigitta Sipocz & \citealt{astroquery} \\
+\href{http://github.com/astropy/ccdproc.git}{ccdproc} & Yes & \href{https://pypi.python.org/pypi/ccdproc}{ccdproc} & Steven Crawford, Matt Craig, and Michael Seifert & \citealt{ccdproc} \\
 \href{https://github.com/jesford/cluster-lensing}{cluster-lensing} & No & \href{https://pypi.python.org/pypi/cluster-lensing}{cluster-lensing} & Jes Ford & \citealt{clusterlensing} \\
-\href{https://github.com/adrn/gala}{gala} & Yes & \href{https://pypi.python.org/pypi/astro-gala}{astro-gala} & Adrian Price-Whelan & \citealt{gala}\\
-\href{https://github.com/jobovy/galpy}{galpy} & Yes & \href{https://pypi.python.org/pypi/galpy}{galpy} & Jo Bovy & \citealt{galpy}\\
-\href{http://github.com/gammapy/gammapy}{gammapy} & No & \href{https://pypi.python.org/pypi/gammapy}{gammapy} & Christoph Deil & \citealt{gammapy}\\
-\href{http://github.com/ejeschke/ginga}{ginga} & Yes & \href{https://pypi.python.org/pypi/ginga}{ginga} & Eric Jeschke and Pey Lian Lim & \citealt{ginga}\\
-\href{https://github.com/glue-viz/glue}{Glue} & Yes & \href{https://pypi.python.org/pypi/glueviz}{glueviz} & Chris Beaumont and Thomas Robitaille & \citealt{glue}\\
-\href{https://github.com/spacetelescope/gwcs}{gwcs} & No & \href{https://pypi.python.org/pypi/gwcs}{gwcs} & Nadia Dencheva & \citealt{gwcs}\\
-\href{https://github.com/astropy/halotools}{Halotools} & Yes & \href{https://pypi.python.org/pypi/halotools}{halotools} & Andrew Hearin & \citealt{halotools}\\
+\href{https://github.com/adrn/gala}{gala} & Yes & \href{https://pypi.python.org/pypi/astro-gala}{astro-gala} & Adrian Price-Whelan & \citealt{gala} \\
+\href{https://github.com/jobovy/galpy}{galpy} & Yes & \href{https://pypi.python.org/pypi/galpy}{galpy} & Jo Bovy & \citealt{galpy} \\
+\href{http://github.com/gammapy/gammapy.git}{gammapy} & No & \href{https://pypi.python.org/pypi/gammapy}{gammapy} & Christoph Deil & \citealt{gammapy} \\
+\href{http://github.com/ejeschke/ginga}{ginga} & Yes & \href{https://pypi.python.org/pypi/ginga}{ginga} & Eric Jeschke and Pey-Lian Lim & \citealt{ginga} \\
+\href{https://github.com/glue-viz/glue.git}{Glue} & Yes & \href{https://pypi.python.org/pypi/glueviz}{glueviz} & Chris Beaumont and Thomas Robitaille & \citealt{glue} \\
+\href{https://github.com/spacetelescope/gwcs.git}{gwcs} & No & \href{https://pypi.python.org/pypi/gwcs}{gwcs} & Nadia Dencheva & \citealt{gwcs} \\
+\href{https://github.com/astropy/halotools}{Halotools} & Yes & \href{https://pypi.python.org/pypi/halotools}{halotools} & Andrew Hearin & \citealt{halotools} \\
+\href{https://github.com/StingraySoftware/HENDRICS}{HENDRICS} & Yes & \href{https://pypi.python.org/pypi/hendrics}{hendrics} & Matteo Bachetti &  \\
+\href{https://github.com/hipspy/hips}{hips} & No & \href{https://pypi.python.org/pypi/hips}{hips} & Christoph Deil and Thomas Boch &  \\
 \href{http://github.com/spacetelescope/imexam}{imexam} & No & \href{https://pypi.python.org/pypi/imexam}{imexam} & Megan Sosey & \citealt{imexam} \\
-\href{https://github.com/Chandra-MARX/marxs}{marxs} & Yes & \href{https://pypi.python.org/pypi/marxs}{marxs} & Hans Moritz Günther (hamogu) & \citealt{marxs}\\
-\href{https://github.com/astropy/montage-wrapper}{montage-wrapper} & Yes & \href{https://pypi.python.org/pypi/montage-wrapper}{montage-wrapper} & Thomas Robitaille & \\
-\href{https://github.com/zblz/naima}{naima} & Yes & \href{https://pypi.python.org/pypi/naima}{naima} & Victor Zabalza & \citealt{naima}\\
-\href{http://github.com/astropy/photutils}{photutils} & No & \href{https://pypi.python.org/pypi/photutils}{photutils} & Larry Bradley and Brigitta Sipocz & \citealt{photutils} \\
-\href{http://github.com/weaverba137/pydl}{PyDL} & No & \href{https://pypi.python.org/pypi/pydl}{pydl} & Benjamin Alan Weaver & \citealt{pydl}\\
-\href{https://github.com/olebole/python-cpl}{python-cpl} & No & \href{https://pypi.python.org/pypi/python-cpl}{python-cpl} & Ole Streicher & \citealt{pythoncpl}\\
-\href{https://github.com/astrofrog/reproject}{reproject} & Yes & \href{https://pypi.python.org/pypi/reproject}{reproject} & Thomas Robitaille & \\
-\href{http://github.com/sncosmo/sncosmo}{sncosmo} & Yes & \href{https://pypi.python.org/pypi/sncosmo}{sncosmo} & Kyle Barbary & \citealt{sncosmo}\\
-\href{https://github.com/radio-astro-tools/spectral-cube}{spectral-cube} & Yes & \href{https://pypi.python.org/pypi/spectral-cube}{spectral-cube} & Adam Ginsburg & \citealt{spectralcube}\\
-\href{http://github.com/astropy/specutils}{specutils} & No & \href{https://pypi.python.org/pypi/specutils}{specutils} & Nicholas Earl, Adam Ginsburg, Steve Crawford & \\
+\href{https://github.com/linetools/linetools}{linetools} & Yes & \href{https://pypi.python.org/pypi/linetools}{linetools} & J. Xavier Prochaska, Nicolas Tejos, and Neil Crighton &  \\
+\href{https://github.com/Chandra-MARX/marxs}{marxs} & Yes & \href{https://pypi.python.org/pypi/marxs}{marxs} & Hans Moritz Günther (hamogu) & \citealt{marxs} \\
+\href{https://github.com/zblz/naima}{naima} & Yes & \href{https://pypi.python.org/pypi/naima}{naima} & Victor Zabalza & \citealt{naima} \\
+\href{https://github.com/RiceMunk/omnifit}{omnifit} & Yes & \href{https://pypi.python.org/pypi/omnifit}{omnifit} & Aleksi Suutarinen &  \\
+\href{http://github.com/astropy/photutils.git}{photutils} & No & \href{https://pypi.python.org/pypi/photutils}{photutils} & Larry Bradley and Brigitta Sipocz & \citealt{photutils} \\
+\href{https://github.com/poliastro/poliastro}{poliastro} & No & \href{https://pypi.python.org/pypi/poliastro}{poliastro} & Juan Luis Cano Rodríguez &  \\
+\href{http://github.com/weaverba137/pydl.git}{PyDL} & No & \href{https://pypi.python.org/pypi/pydl}{pydl} & Benjamin Alan Weaver & \citealt{pydl} \\
+\href{https://github.com/astropy/pyregion.git}{pyregion} & Yes & \href{https://pypi.python.org/pypi/pyregion}{pyregion} & Jae-Joon Lee and Christoph Deil &  \\
+\href{https://github.com/pyspeckit/pyspeckit}{pyspeckit} & Yes & \href{https://pypi.python.org/pypi/pyspeckit}{pyspeckit} & Adam Ginsburg &  \\
+\href{https://github.com/olebole/python-cpl}{python-cpl} & No & \href{https://pypi.python.org/pypi/python-cpl}{python-cpl} & Ole Streicher & \citealt{pythoncpl} \\
+\href{https://github.com/pyvirtobs/pyvo.git}{PyVO} & No & \href{https://pypi.python.org/pypi/pyvo}{pyvo} & Stefan Becker &  \\
+\href{https://github.com/astropy/regions}{regions} & No & \href{https://pypi.python.org/pypi/regions}{regions} & Christoph Deil and Johannes King &  \\
+\href{https://github.com/astrofrog/reproject.git}{reproject} & Yes & \href{https://pypi.python.org/pypi/reproject}{reproject} & Thomas Robitaille &  \\
+\href{http://github.com/sncosmo/sncosmo}{sncosmo} & Yes & \href{https://pypi.python.org/pypi/sncosmo}{sncosmo} & Kyle Barbary & \citealt{sncosmo} \\
+\href{https://github.com/radio-astro-tools/spectral-cube}{spectral-cube} & Yes & \href{https://pypi.python.org/pypi/spectral-cube}{spectral-cube} & Adam Ginsburg & \citealt{spectralcube} \\
+\href{http://github.com/astropy/specutils.git}{specutils} & No & \href{https://pypi.python.org/pypi/specutils}{specutils} & Nicholas Earl, Adam Ginsburg, Steve Crawford, Erik Tollerud &  \\
+\href{https://github.com/StingraySoftware/stingray}{stingray} & No & \href{https://pypi.python.org/pypi/stingray}{stingray} & Daniela Huppenkothen, Matteo Bachetti, Abigail Stevens, Simone Migliari, and Paul Balm &  \\

### 2017-12-11 registry_prov.tex
update the package registry for affiliated packages

@@
-\href{http://github.com/aplpy/aplpy}{APLpy} & Yes & \href{https://pypi.python.org/pypi/APLpy}{APLpy} & Thomas Robitaille and Eli Bressert \\
-\href{http://github.com/astroML/astroML}{astroML} & Yes & \href{https://pypi.python.org/pypi/astroML}{astroML} & Jake Vanderplas \\
-\href{https://github.com/StingraySoftware/HENDRICS}{HENDRICS} & Yes & \href{https://pypi.python.org/pypi/hendrics}{hendrics} & Matteo Bachetti \\
-\href{https://github.com/RiceMunk/omnifit}{omnifit} & Yes & \href{https://pypi.python.org/pypi/omnifit}{omnifit} & Aleksi Suutarinen \\
-\href{https://github.com/astropy/pyregion}{pyregion} & Yes & \href{https://pypi.python.org/pypi/pyregion}{pyregion} & Jae-Joon Lee \\
-\href{https://github.com/pyvirtobs/pyvo}{PyVO} & No & \href{https://pypi.python.org/pypi/pyvo}{pyvo} & Stefan Becker \\
-\href{https://github.com/spacetelescope/spherical_geometry}{spherical\_geometry} & No & \href{https://pypi.python.org/pypi/spherical-geometry}{spherical-geometry} & Bernie Simon and Michael Droettboom \\
+\href{https://github.com/spacetelescope/spherical_geometry.git}{spherical\_geometry} & No & \href{https://pypi.python.org/pypi/spherical-geometry}{spherical-geometry} & Bernie Simon and Michael Droettboom &  \\

### 2017-12-11 affiliated.py

@@ -5,21 +5,33 @@ import re
 with open('registry.json') as data_file:
     data = json.load(data_file)
 
-package_list = sorted(data['packages'], key=lambda k: k['name'].lower()) 
+with open('bib_mapping.json') as data_file:
+    bib_map = json.load(data_file)
+
+package_list = sorted(data['packages'], key=lambda k: k['name'].lower())
 
 stable_dict = {False: 'No', True: 'Yes'}
 
 row = ('\\href{{{0}}}{{{1}}} & {2} & '
-      '\\href{{https://pypi.python.org/pypi/{3}}}{{{3}}} & {4} \\\\\n')
+       '\\href{{https://pypi.python.org/pypi/{3}}}{{{3}}} & {4} & {5} \\\\\n')
 
 with open("registry.tex", "w") as f1, open("registry_prov.tex", "w") as f2:
     for item in package_list:
+
+        citealt = ("\\citealt{{{0}}}".format(bib_map[item["name"]])
+                   if item["name"] in bib_map
+                   else "")
+
         if not item['provisional']:
             f1.write(row.format(item["repo_url"], item["name"],
                                 stable_dict[item["stable"]], item['pypi_name'],
-                                re.sub(' <.*?>', '', item["maintainer"])))
+                                re.sub(' <.*?>', '', item["maintainer"]),
+                                citealt
+                               ))
         else:
             f2.write(row.format(item["repo_url"], 
                                 re.sub('_', '\_', item["name"]),
                                 stable_dict[item["stable"]], item['pypi_name'],
-                                re.sub(' <.*?>', '', item["maintainer"])))
+                                re.sub(' <.*?>', '', item["maintainer"]),
+                                citealt
+                               ))

### 2017-12-11 registry.tex
run affiliated.py: hey, it works!

@@
 \href{https://github.com/astropy/pyregion.git}{pyregion} & Yes & \href{https://pypi.python.org/pypi/pyregion}{pyregion} & Jae-Joon Lee and Christoph Deil &  \\
-\href{https://github.com/pyspeckit/pyspeckit}{pyspeckit} & Yes & \href{https://pypi.python.org/pypi/pyspeckit}{pyspeckit} & Adam Ginsburg &  \\
+\href{https://github.com/pyspeckit/pyspeckit}{pyspeckit} & Yes & \href{https://pypi.python.org/pypi/pyspeckit}{pyspeckit} & Adam Ginsburg & \citealt{pyspeckit} \\
 \href{https://github.com/olebole/python-cpl}{python-cpl} & No & \href{https://pypi.python.org/pypi/python-cpl}{python-cpl} & Ole Streicher & \citealt{pythoncpl} \\

### 2017-12-11 main.tex
add "cite" column to provisional

--- 2017-12-11 main.tex
@@
 the conversion from FK4 to Galactic coordinates for all pairs of tools.
-In this figure, the color of the cell indicates the maximum difference (in
-arcsec) between the two tools over the 1000 longitude-latitude pairs tested.
 This figure shows, for example, that \astropypkg, Kapteyn, and PyTPM agree with
@@
   \caption{
-    Comparison matrix of the maximum difference between longitude-latitude
-    values in a set of 1000 random points transformed from FK4 to Galactic
-    with the different packages.
+    Comparison matrix of the accuracy values of the FK4 to Galactic
+    transformation between the different packages. Each comparison block shows
+    four squares representing the median, mean, maximum and standard deviation
+    going from left to right and bottom to top.
     Darker colors (larger differences) are more significant disagreements.
@@
 The \package{astropy.convolution} subpackage implements
-``normalized convolution'' \citep[e.g.,][]{Knutsson1993} that is an image
-reconstruction technique, in which missing data are ignored during the
-convolution and replaced with values interpolated using the kernel;
-An example of this is given in \figurename~\ref{fig:convolution-example}.
+\textit{normalized convolution} \citep[e.g.,][]{Knutsson1993}, an image
+reconstruction technique in which missing data are ignored during the
+convolution and replaced with values interpolated using the kernel.
+An example is given in \figurename~\ref{fig:convolution-example}.
 In \astropypkg versions $\leq 1.3$, the direct convolution and Fast Fourier Transform (FFT)
-convolution approaches were inconsistent, with the latter implementing
-normalized convolution, while the former a different approach.
+convolution approaches were inconsistent, with only the latter implementing
+normalized convolution.
 As of version 2.0, the two methods now agree and include a suite of

### 2017-12-11 affiliated.py

@@ -29,7 +29,7 @@ with open("registry.tex", "w") as f1, open("registry_prov.tex", "w") as f2:
                                 citealt
                                ))
         else:
-            f2.write(row.format(item["repo_url"], 
+            f2.write(row.format(item["repo_url"],
                                 re.sub('_', '\_', item["name"]),
                                 stable_dict[item["stable"]], item['pypi_name'],
                                 re.sub(' <.*?>', '', item["maintainer"]),

### 2017-12-11 registry.tex
correct several serious issues with table formatting

@@
 \href{http://github.com/spacetelescope/imexam}{imexam} & No & \href{https://pypi.python.org/pypi/imexam}{imexam} & Megan Sosey & \citealt{imexam} \\
-\href{https://github.com/linetools/linetools}{linetools} & Yes & \href{https://pypi.python.org/pypi/linetools}{linetools} & J. Xavier Prochaska, Nicolas Tejos, and Neil Crighton &  \\
-\href{https://github.com/Chandra-MARX/marxs}{marxs} & Yes & \href{https://pypi.python.org/pypi/marxs}{marxs} & Hans Moritz Günther (hamogu) & \citealt{marxs} \\
+\href{https://github.com/linetools/linetools}{linetools} & Yes & \href{https://pypi.python.org/pypi/linetools}{linetools} & \parbox{3in}{J. Xavier Prochaska,  Nicolas Tejos,  and Neil Crighton} &  \\
+\href{https://github.com/Chandra-MARX/marxs}{marxs} & Yes & \href{https://pypi.python.org/pypi/marxs}{marxs} & Hans Moritz Günther & \citealt{marxs} \\
 \href{https://github.com/zblz/naima}{naima} & Yes & \href{https://pypi.python.org/pypi/naima}{naima} & Victor Zabalza & \citealt{naima} \\
@@
 \href{https://github.com/radio-astro-tools/spectral-cube}{spectral-cube} & Yes & \href{https://pypi.python.org/pypi/spectral-cube}{spectral-cube} & Adam Ginsburg & \citealt{spectralcube} \\
-\href{http://github.com/astropy/specutils.git}{specutils} & No & \href{https://pypi.python.org/pypi/specutils}{specutils} & Nicholas Earl, Adam Ginsburg, Steve Crawford, Erik Tollerud &  \\
-\href{https://github.com/StingraySoftware/stingray}{stingray} & No & \href{https://pypi.python.org/pypi/stingray}{stingray} & Daniela Huppenkothen, Matteo Bachetti, Abigail Stevens, Simone Migliari, and Paul Balm &  \\
+\href{http://github.com/astropy/specutils.git}{specutils} & No & \href{https://pypi.python.org/pypi/specutils}{specutils} & \parbox{3in}{Nicholas Earl,  Adam Ginsburg,  Steve Crawford,\par  Erik Tollerud} &  \\
+\href{https://github.com/StingraySoftware/stingray}{stingray} & No & \href{https://pypi.python.org/pypi/stingray}{stingray} & \parbox{3in}{Daniela Huppenkothen,  Matteo Bachetti,  Abigail Stevens,\par  Simone Migliari,  and Paul Balm} &  \\

### 2017-12-11 affiliated.py

@@ -22,16 +22,30 @@ with open("registry.tex", "w") as f1, open("registry_prov.tex", "w") as f2:
                    if item["name"] in bib_map
                    else "")
 
+        maintainer = re.sub(' [<(].*?[>)]', '', item["maintainer"])
+        maintainers = maintainer.split(",")
+        if len(maintainer) > 50: # of characters
+            # newline every 3rd person
+            maintainer = ""
+            for ii, name in enumerate(maintainers):
+                if ii > 0 and (ii+1) % 3 == 0:
+                    maintainer = maintainer+"{0},\par ".format(name)
+                else:
+                    maintainer = maintainer+"{0}, ".format(name)
+
+            maintainer = maintainer.rstrip(",\par ")
+            maintainer = "\\parbox{{3in}}{{{0}}}".format(maintainer)
+
         if not item['provisional']:
             f1.write(row.format(item["repo_url"], item["name"],
                                 stable_dict[item["stable"]], item['pypi_name'],
-                                re.sub(' <.*?>', '', item["maintainer"]),
+                                maintainer,
                                 citealt
                                ))
         else:
             f2.write(row.format(item["repo_url"],
                                 re.sub('_', '\_', item["name"]),
                                 stable_dict[item["stable"]], item['pypi_name'],
-                                re.sub(' <.*?>', '', item["maintainer"]),
+                                maintainer,
                                 citealt
                                ))

### 2017-12-11 registry.tex
remove the overly-complicated table formatting and just put it in the table specification directly

--- 2017-12-11 registry.tex
@@
 \href{https://github.com/linetools/linetools}{linetools} & Yes & \href{https://pypi.python.org/pypi/linetools}{linetools} & J. Xavier Prochaska, Nicolas Tejos, and Neil Crighton &  \\
-\href{https://github.com/Chandra-MARX/marxs}{marxs} & Yes & \href{https://pypi.python.org/pypi/marxs}{marxs} & Hans Moritz Günther (hamogu) & \citealt{marxs} \\
+\href{https://github.com/Chandra-MARX/marxs}{marxs} & Yes & \href{https://pypi.python.org/pypi/marxs}{marxs} & Hans Moritz Günther & \citealt{marxs} \\
 \href{https://github.com/zblz/naima}{naima} & Yes & \href{https://pypi.python.org/pypi/naima}{naima} & Victor Zabalza & \citealt{naima} \\

### 2017-12-11 affiliated.py

@@ -23,18 +23,6 @@ with open("registry.tex", "w") as f1, open("registry_prov.tex", "w") as f2:
                    else "")
 
         maintainer = re.sub(' [<(].*?[>)]', '', item["maintainer"])
-        maintainers = maintainer.split(",")
-        if len(maintainer) > 50: # of characters
-            # newline every 3rd person
-            maintainer = ""
-            for ii, name in enumerate(maintainers):
-                if ii > 0 and (ii+1) % 3 == 0:
-                    maintainer = maintainer+"{0},\par ".format(name)
-                else:
-                    maintainer = maintainer+"{0}, ".format(name)
-
-            maintainer = maintainer.rstrip(",\par ")
-            maintainer = "\\parbox{{3in}}{{{0}}}".format(maintainer)
 
         if not item['provisional']:
             f1.write(row.format(item["repo_url"], item["name"],

### 2017-12-11 main.tex
correct several serious issues with table formatting
remove the overly-complicated table formatting and just put it in the table specification directly

@@
 \figurename~\ref{fig:coordinate_benchmarks} visualizes the relative accuracy of
-the conversion from FK4 to Galactic coordinates for all pairs of tools.
+the conversion from FK4 to Galactic coordinates for all pairs of tools that
+implement this transformation.
+In this figure, the color of the cell indicates the maximum difference (in
+arcseconds) between the two tools over the 1000 longitude-latitude pairs tested.
 This figure shows, for example, that \astropypkg, Kapteyn, and PyTPM agree with
@@
 \begin{longrotatetable}
-  \begin{deluxetable*}{ccccc}
+    \begin{deluxetable*}{cccp{3in}c}
     \tablecaption{Registry of affiliated packages.}

### 2017-12-12 figures/make_ngc6977_image.py
rotate image so tick labels appear correctly

@@ -5,6 +5,10 @@ from astropy.visualization import make_lupton_rgb, astropy_mpl_style
 from astropy.wcs import WCS
 import matplotlib.pyplot as plt
 plt.style.use(astropy_mpl_style)
+plt.rcParams['font.family'] = plt.rcParamsDefault['font.family']
+plt.rcParams['lines.marker'] = ''
+from reproject import reproject_interp
+import numpy as np
 
 # load the data
 g_name = get_pkg_data_filename('visualization/reprojected_sdss_g.fits.bz2')
@@ -15,19 +19,31 @@ g = fits.open(g_name)[0]
 r = fits.open(r_name)[0]
 i = fits.open(i_name)[0]
 
-# extract a smaller region around the Hickson 88 group
-slc = (slice(0, 285), slice(33, 318))
-gp = g.data[slc]
-rp = r.data[slc]
-ip = i.data[slc]
+# Rotate the images
+ang = np.deg2rad(90)
+wcs = WCS(g.header)
+wcs.wcs.cd = wcs.wcs.cd @ np.array([[np.cos(ang),-np.sin(ang)],[np.sin(ang),np.cos(ang)]])
 
-# make the figure - stretch 1
+imgs = []
+for img in [g,r,i]:
+    hdr = img.header
+    hdr = hdr.copy()
+
+    arr, footprint = reproject_interp(img, wcs.to_header(),
+                                      shape_out=(g.header['NAXIS1'], g.header['NAXIS2']))
+    imgs.append(arr)
+
+# extract a smaller region around the Hickson 88 group
+slc = (slice(200, 580), slice(130, 550))
+gp = imgs[0][slc]
+rp = imgs[1][slc]
+ip = imgs[2][slc]
+
+# make the figure - 2 sets of stretch parameters
 rgb1 = make_lupton_rgb(ip, rp, gp)
 rgb2 = make_lupton_rgb(ip*0.8, rp, gp*1.3, Q=10, stretch=0.4)
 
-wcs = WCS(g.header)
-
-fig, axes = plt.subplots(1, 2, figsize=(8, 4),
+fig, axes = plt.subplots(1, 2, figsize=(10, 5.5),
                          sharex=True, sharey=True,
                          subplot_kw=dict(projection=wcs))
 
@@ -39,9 +55,9 @@ axes[1].imshow(rgb2, origin='lower')
[…]

### 2017-12-12 main.tex
more info in caption

@@
 variation on this technique.  As an example, in \figurename~\ref{fig:ngc6977},
-we show an RGB color image of the Hickson 88 group, centered near NGC~6977.
+we show an RGB color image of the Hickson 88 group, centered near
+NGC~6977.\footnote{\url{http://skyserver.sdss.org/dr13/en/tools/chart/navi.aspx?ra=313.12381&dec=-5.74611}}
 This image was generated from SDSS images using the
@@
 tools.
+This example uses \package{astropy.visualization.wcsaxes} to display the
+sky coordinate grid, and the \texttt{astropy.visualization.make\_lupton\_rgb()}
+function to produce the RGB image from three SDSS filter images ($g$, $r$, $i$).
+The left and right panel images show two different parameter choices for the
+stretch and softening parameters (shown in the titles).
 \label{fig:ngc6977}}

### 2017-12-12 figures/make_ngc6977_image.py
fix orientation

@@ -11,18 +11,22 @@ from reproject import reproject_interp
 import numpy as np
 
 # load the data
-g_name = get_pkg_data_filename('visualization/reprojected_sdss_g.fits.bz2')
-r_name = get_pkg_data_filename('visualization/reprojected_sdss_r.fits.bz2')
-i_name = get_pkg_data_filename('visualization/reprojected_sdss_i.fits.bz2')
+# g_name = get_pkg_data_filename('visualization/reprojected_sdss_g.fits.bz2')
+# r_name = get_pkg_data_filename('visualization/reprojected_sdss_r.fits.bz2')
+# i_name = get_pkg_data_filename('visualization/reprojected_sdss_i.fits.bz2')
+g_name = get_pkg_data_filename('hash/fb425fccf6326e34f4566711d8910364')
+r_name = get_pkg_data_filename('hash/e6670142bc3c83936d84bd5d5d331d6a')
+i_name = get_pkg_data_filename('hash/ed6e4146ea0a1d2af0f005dd8ba79282')
 
 g = fits.open(g_name)[0]
 r = fits.open(r_name)[0]
 i = fits.open(i_name)[0]
 
 # Rotate the images
-ang = np.deg2rad(90)
+ang = np.deg2rad(-90)
 wcs = WCS(g.header)
 wcs.wcs.cd = wcs.wcs.cd @ np.array([[np.cos(ang),-np.sin(ang)],[np.sin(ang),np.cos(ang)]])
+wcs.wcs.crpix = tuple([x/2. for x in g.data.shape])
 
 imgs = []
 for img in [g,r,i]:
@@ -34,7 +38,7 @@ for img in [g,r,i]:
     imgs.append(arr)
 
 # extract a smaller region around the Hickson 88 group
-slc = (slice(200, 580), slice(130, 550))
+slc = (slice(None, 400), slice(None))
 gp = imgs[0][slc]
 rp = imgs[1][slc]
 ip = imgs[2][slc]
@@ -43,16 +47,16 @@ ip = imgs[2][slc]
 rgb1 = make_lupton_rgb(ip, rp, gp)
 rgb2 = make_lupton_rgb(ip*0.8, rp, gp*1.3, Q=10, stretch=0.4)
 
-fig, axes = plt.subplots(1, 2, figsize=(10, 5.5),
+fig, axes = plt.subplots(1, 2, figsize=(10, 4),
                          sharex=True, sharey=True,
[…]

### 2017-12-13 figures/make_ngc6977_image.py
remove hash filenames and add comment

@@ -11,18 +11,17 @@ from reproject import reproject_interp
 import numpy as np
 
 # load the data
-# g_name = get_pkg_data_filename('visualization/reprojected_sdss_g.fits.bz2')
-# r_name = get_pkg_data_filename('visualization/reprojected_sdss_r.fits.bz2')
-# i_name = get_pkg_data_filename('visualization/reprojected_sdss_i.fits.bz2')
-g_name = get_pkg_data_filename('hash/fb425fccf6326e34f4566711d8910364')
-r_name = get_pkg_data_filename('hash/e6670142bc3c83936d84bd5d5d331d6a')
-i_name = get_pkg_data_filename('hash/ed6e4146ea0a1d2af0f005dd8ba79282')
+g_name = get_pkg_data_filename('visualization/reprojected_sdss_g.fits.bz2')
+r_name = get_pkg_data_filename('visualization/reprojected_sdss_r.fits.bz2')
+i_name = get_pkg_data_filename('visualization/reprojected_sdss_i.fits.bz2')
 
 g = fits.open(g_name)[0]
 r = fits.open(r_name)[0]
 i = fits.open(i_name)[0]
 
-# Rotate the images
+# Rotate the images: the images are rotated ~90º from the coordinate grid, so
+# as they are by default, the grid tick labels don't appear along the axes. This
+# rotates the images so they are more aligned with the coordinate grid.
 ang = np.deg2rad(-90)
 wcs = WCS(g.header)
 wcs.wcs.cd = wcs.wcs.cd @ np.array([[np.cos(ang),-np.sin(ang)],[np.sin(ang),np.cos(ang)]])

### 2017-12-14 main.tex
added footnote and author input

--- 2017-12-11 main.tex
@@
 
-\author{Astropy Collaboration}
+\author{Astropy Project}
+\footnote{The author list has three parts: the 13 authors that were primary authors of  sections of the paper in order of contribution, the four members of the \astropy Project coordination committee, and contributions to the \astropy Project in alphabetical order.
+The position in the author list does not correspond to contributions to the \astropy Project as a whole.
+A more complete list of contributors to the core package can be found in the \href{https://github.com/astropy/astropy/graphs/contributors}{package repository}, and at the \href{http://www.astropy.org/team.html}{\astropy team webpage}.}
+
+\input{author.tex}
 

### 2017-12-14 author.tex
first draft of author list

\author[0000-0003-0872-7098]{A. M. Price-Whelan}
\affil{Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08544, USA}

\author[0000-0002-3713-6337]{B. M. Sip\H{o}cz}
\affil{TBD}

\author[0000-0003-4243-2840]{H. M. G\"{u}nther}
\affil{Massachusetts Institute of Technology, Kavli Institute for Astrophysics and Space Research, 70 Vassar St., Cambridge, MA 02139, USA}

\author[0000-0003-0079-4114]{P. L. Lim}
\affil{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}

\author[0000-0002-8969-5229]{S. M. Crawford}
\affil{South African Astronomical Observatory, PO Box 9, Observatory 7935, Cape Town, South Africa}

\author{S. Conseil}
\affil{Univ Lyon, Univ Lyon1, Ens de Lyon, CNRS, Centre de Recherche Astrophysique de Lyon UMR5574, F-69230, Saint-Genis- Laval, France}

\author[0000-0003-4401-0430]{D. L. Shupe}
\affil{Caltech/IPAC, 1200 E. California Blvd, Pasadena, CA 91125}

\author[0000-0001-7988-8919]{M. W. Craig}
\affil{Minnesota State University Moorhead/Department of Physics and Astronomy, 1104 7th Ave S, Moorhead, MN 56563}

\author[0000-0002-5686-9632]{N. Dencheva}
\affil{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}

\author[0000-0001-6431-9633]{A. Ginsburg}
\affil{National Radio Astronomy Observatory, 1003 Lopezville Rd, Socorro, NM 87801}

\author[0000-0002-9623-3401]{J. T. VanderPlas}
\affil{eScience Institute, University of Washington, 3910 15th Ave NE, Seattle, WA 98195, USA}

\author[0000-0002-7908-9284]{L. D. Bradley}
\affil{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}

\author[0000-0003-0784-6909]{D. P\'{e}rez-Su\'{a}rez}
\affil{University College London/Research IT Services, Gower St, Bloomsbury, London WC1E 6BT, United Kingdom}

\author[0000-0002-0455-9384]{M. de Val-Borro}
\affil{NASA Goddard Space Flight Center, Astrochemistry Laboratory, 8800 Greenbelt Road, Greenbelt, MD 20771, USA}

\author{T. L. Aldcroft}
\affil{Harvard/Smithsonian Center for Astrophysics, 60 Garden St., Cambridge, MA, 02138, USA}

\author[0000-0002-1821-0650]{K. L. Cruz}
\affil{Department of Physics and Astronomy, Hunter College, City University of New York, 695 Park Avenue, New York, NY 10065}
\affil{Physics, Graduate Center of the City University of New York, New York, NY, USA}
\affil{ Department of Astrophysics, American Museum of Natural History, New York, NY, USA}

\author[0000-0002-8642-1329]{T. P. Robitaille}
\affil{Aperio Software Ltd., Headingley Enterprise and Arts Centre, Bennett Road,  Leeds, LS6 3HN, United Kingdom}

\author[0000-0002-9599-310X]{E. J. Tollerud}
\affil{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}

\author{C. Ardelean}
\affil{Western University/Physics and Astronomy, 1151 Richmond St, London ON, N6A 3K7, Canada}

\author{T. Babej}
\affil{Department of Theoretical Physics \& Astrophysics, Masaryk University, Kotlarska 2, 61137 Brno, Czech Republic}

\author[0000-0002-4576-9337]{M. Bachetti}
\affil{INAF-Osservatorio Astronomico di Cagliari}

\author{A. V. Bakanov}
\affil{}

\author[0000-0001-7821-7195]{S. P. Bamford}
\affil{School of Physics \& Astronomy, University of Nottingham, University Park, Nottingham NG7 2RD, UK}

\author[0000-0002-3306-3484]{G. Barentsen}
\affil{NASA Ames Research Center, Moffett Field, CA 94043, USA}

\author[0000-0003-2767-0090]{P. Barmby}
\affil{University of Western Ontario/Department of Physics \& Astronomy, 1151 Richmond St, London ON N5X4H1 Canada}

\author[0000-0002-9374-2729]{A. Baumbach}
\affil{Heidelberg University, Kirchhoff Institut for Physics, Im Neuenheimer Feld 227, 69116 Heidelberg, Germany}

\author{K. L. Berry}
\affil{}

\author{F. Biscani}
\affil{Max Planck Institute for Astronomy}

\author[0000-0003-0946-6176]{M. Boquien}
\affil{Unidad de Astronomía, Fac. Cs. Básicas, Universidad de Antofagasta, Avda. U. de Antofagasta 02800, Antofagasta, Chile}

\author{K. A. Bostroem}
\affil{UC Davis/Department of Physics, 1 Shields Ave, Davis, CA, 95616, USA}

\author{L. G. Bouma}
\affil{Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08540, USA}

\author[0000-0003-2680-005X]{G. B. Brammer}
\affil{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}

\author{E. M. Bray}
\affil{}

\author{H. Breytenbach}
\affil{South African Astronomical Observatory, PO Box 9, Observatory 7935, Cape Town, South Africa}

\author[0000-0001-8001-0089]{H. Buddelmeijer}
\affil{Leiden Observatory, Leiden University, P.O. Box 9513, 2300 RA, Leiden, The Netherlands}

\author[0000-0003-4428-7835]{D. J. Burke}
\affil{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA, 02138, USA}

\author[0000-0002-7738-5389]{G. Calderone}
\affil{Istituto Nazionale di Astrofisica, via Tiepolo 11 Trieste, Italy}

\author{M. Cara}
\affil{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}

\author{J. V. M. Cardoso}
\affil{Universidade Federal de Campina Grande, Campina Grande, PB 58429-900, Brazil; NASA Ames Research Center, Mountain View, CA 94035, USA; Bay Area Environmental Research Institute, Petaluma, CA 94952, USA}

\author{S. Cheedella}
\affil{Department of Physics, Blacksburg VA, USA}

\author[0000-0002-5317-7518]{Y. Copin}
\affil{Université de Lyon, F-69622, Lyon, France; Université de Lyon 1, Villeurbanne; CNRS/IN2P3, Institut de Physique Nucléaire de Lyon}

\author[0000-0003-1204-3035]{D. Crichton}
\affil{Department of Physics and Astronomy, Johns Hopkins University, Baltimore, MD 21218, USA}

\author{D. D'Avella}
\affil{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}

\author[0000-0002-4198-4005]{C. Deil}
\affil{Max-Planck-Institut f\"ur Kernphysik, PO Box 103980, 69029 Heidelberg, Germany}

\author[0000-0003-0526-3873]{\'{E}. Depagne}
\affil{South African Astronomical Observatory, PO Box 9, Observatory 7935, Cape Town, South Africa}

\author[0000-0002-8134-9591]{J. P. Dietrich}
\affil{Faculty of Physics, Ludwig-Maximilians-Universit\"at, Scheinerstr. 181679 Munich, Germany;Excellence Cluster Universe, Boltzmannstr. 2, 85748 Garching b. M\"unchen, Germany}

\author{A. Donath}
\affil{Max-Planck-Institut f\"ur Kernphysik, PO Box 103980, 69029 Heidelberg, Germany}

\author{T. Erben}
\affil{Argelander-Institut f\"ur Astronomie, Auf dem H\"ugel 71, 53121 Bonn / Germany}

\author[0000-0002-8919-079X]{L. A. Ferreira}
\affil{Instituto de Matemática Estatística e Física – IMEF, Universidade Federal do Rio Grande – FURG, Rio Grande, RS 96203-900, Brazil}

\author{T. Finethy}
\affil{}

\author[0000-0003-4291-1091]{R. T. Fox}
\affil{Unaffiliated}

\author[0000-0002-9853-5673]{L. H. Garrison}
\affil{Harvard-Smithsonian Center for Astrophysics, 60 Garden St., Cambridge, MA, 02138, USA}

\author{S. L. J. Gibbons}
\affil{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge, CB3 0HA, UK}

\author[0000-0001-6431-9633]{A. Ginsburg}
\affil{National Radio Astronomy Observatory, 1003 Lopezville Rd, Socorro, NM 87801}

\author[0000-0001-6431-9633]{A. Ginsburg}
\affil{National Radio Astronomy Observatory, 1003 Lopezville Road Socorro, NM 87801-0387}

\author{D. A. Goldstein}
\affil{Department of Astronomy, UC Berkeley, 501 Campbell Hall \#3411, Berkeley, CA 94720, USA; Berkeley Lab, 1 Cyclotron Road, Berkeley, CA 94720, USA}

\author[0000-0002-0300-3333]{R. Gommers}
\affil{Scion, Private Bag 3020, Rotorua, New Zealand}

\author[0000-0003-4970-2874]{J. P. Greco}
\affil{Department of Astrophysical Sciences,  Princeton University, Princeton, NJ 08544, USA}

\author{P. Greenfield}
\affil{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}

\author[0000-0002-6508-2938]{A. M. Groener}
\affil{Drexel University, Physics Department, Philadelphia, PA 19104, USA}

\author{F. Grollier}
\affil{Independent developer}

\author[0000-0003-2031-7737]{A. Hagen}
\affil{Vizual.ai, 3600 O'Donnell St, Suite 250, Baltimore, MD 21224 ; Dept of Astronomy and Astrophysics, Pennsylvania State University, University Park, PA 16802}

\author{P. Hirst}
\affil{Gemini Observatory, 670 N. Aohoku Pl, Hilo, HI 96720, USA}

\author[0000-0002-8546-9128]{D. Homeier}
\affil{Zentrum f{\"u}r Astronomie der Universit{\"a}t Heidelberg, Landessternwarte, K{\"o}nigstuhl 12, D-69117 Heidelberg, Germany}

\author[0000-0002-4600-7852]{A. J. Horton}
\affil{Australian Astronomical Observatory, 105 Delhi Road, North Ryde NSW 2113, Australia}

\author[0000-0002-0832-2974]{G. Hosseinzadeh}
\affil{Las Cumbres Observatory, 6740 Cortona Drive, Suite 102, Goleta, CA 93117-5575, USA; Department of Physics, University of California, Santa Barbara, CA 93106-9530, USA}

\author{L. Hu}
\affil{Imperial College London,  Kensington, London SW7 2AZ, United Kingdom}

\author[0000-0003-4989-0289]{J. S. Hunkeler}
\affil{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}

\author[0000-0001-5250-2633]{\v{Z}. Ivezi\'{c}}
\affil{Department of Astronomy, University of Washington, Seattle, WA 98155}

\author{A. Jain}
\affil{BITS PILANI/Computer Science, Pilani Campus, Rajasthan, India}

\author[0000-0001-5982-167X]{T. Jenness}
\affil{Large Synoptic Survey Telescope, 950 N Cherry Ave, Tucson, AZ, 85719}

\author{G. Kanarek}
\affil{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}

\author[0000-0002-7612-0469]{S. Kendrew}
\affil{European Space Agency, Space Telescope Science Institute, 3700 San Martin Drive, Baltimore MD 21231, USA}

\author[0000-0002-8211-1892]{N. S. Kern}
\affil{UC Berkeley Department of Astronomy, 501 Campbell Hall, Berkeley, CA, 94709}

\author[0000-0002-0479-7235]{W. E. Kerzendorf}
\affil{European Southern Observatory, Karl-Schwarzschild-Stra{\ss}e 2, 85748 Garching bei M\"{u}nchen, Germany}

\author{A. Khvalko}
\affil{}

\author{J. King}
\affil{Max-Planck-Institut f\"ur Kernphysik, PO Box 103980, 69029 Heidelberg, Germany}

\author[0000-0002-8828-5463]{D. Kirkby}
\affil{Department of Physics and Astronomy, University of California, Irvine, CA 92697, USA}

\author{A. M. Kulkarni}
\affil{College of Engineering Pune/Department of Computer Engineering and IT, Shivajinagar, Pune 411005, India}

\author{A. Kumar}
\affil{Delhi Technological University}

\author[0000-0003-2193-5369]{A. Lee}
\affil{Department of Physics, University of Berkeley, Califonia, CA94709, USA}

\author[0000-0001-5820-475X]{D. Lenz}
\affil{Jet Propulsion Laboratory, California Institute of Technology, 4800 Oak Grove Drive, Pasadena, CA 91109, USA}

\author[0000-0001-7221-855X]{S. P. Littlefair}
\affil{Dept of Physics \& Astronomy, University of Sheffield, Sheffield, S3 7RH, UK}

\author[0000-0003-3270-6844]{Z. Ma}
\affil{Department of Physics and Astronomy, University of Missouri, Columbia, Missouri, 65211, USA}

\author[0000-0002-1395-8694]{D. M. Macleod}
\affil{}

\author[0000-0002-6324-5713]{M. Mastropietro}
\affil{Ghent University}

\author[0000-0001-5807-7893]{C. McCully}
\affil{Las Cumbres Observatory, 6740 Cortona Drive, Suite 102, Goleta, CA 93117-5575, USA; Department of Physics, University of California, Santa Barbara, CA 93106-9530, USA}

\author{S. Montagnac}
\affil{obs-psr}

\author[0000-0003-2528-3409]{B. M. Morris}
\affil{University of Washington}

\author[0000-0003-4217-4642]{S. J. Mumford}
\affil{SP$^{2}$RC, School of Mathematics and Statistics, The University of Sheffield U.K.}

\author[0000-0002-1631-4114]{D. Muna}
\affil{Center for Cosmology and Astroparticle Physics, The Ohio State University, 191 West Woodruff Avenue, Columbus, OH 43210}

\author[0000-0001-6628-8033]{N. A. Murphy}
\affil{Harvard-Smithsonian Center for Astrophysics, 60 Garden St, Cambridge, MA 02138, USA}

\author{S. Nelson}
\affil{Minnesota State University Moorhead, 1104 7th Avenue South Moorhead, MN 56563, United States}

\author[0000-0002-1966-3627]{G. H. Nguyen}
\affil{VNU-HCMC, University of Natural Sciences/Faculty of IT, 227 Nguyen Van Cu St., Ward 4, District 5, Ho Chi Minh City, Vietnam}

\author[0000-0001-8720-5612]{J. P. Ninan}
\affil{The Pennsylvania State University, University Park, PA, USA}

\author{M. N{\"o}the}
\affil{TU Dortmund, Germany}

\author{S. Ogaz}
\affil{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}

\author[0000-0001-7790-5308]{S. Oh}
\affil{Princeton University}

\author{J. K. Parejko}
\affil{Department of Astronomy, University of Washington, Box 351580, Seattle, WA 98195, USA}

\author{N. Parley}
\affil{University of Reading, Whiteknights Campus, Reading RG6 6BX, UK}

\author[0000-0002-9351-6051]{S. Pascual}
\affil{Universidad Complutense de Madrid}

\author{R. Patil}
\affil{}

\author{A. A. Patil}
\affil{Pune Institute of Computer Technology, Pune 411043, India}

\author[0000-0002-9912-5705]{A. L. Plunkett}
\affil{European Southern Observatory, Av. Alonso de C\'{o}rdova 3107, Vitacura, Santiago, Chile}

\author{T. Rastogi}
\affil{}

\author{V. Reddy Janga}
\affil{Indian Institute of Technology, Mechanical Engineering, Kharagpur, India}

\author[0000-0003-1149-6294]{J. Sabater}
\affil{Institute for Astronomy (IfA), University of Edinburgh, Royal Observatory, Blackford Hill, EH9 3HJ Edinburgh, U.K.}

\author{P. Sakurikar}
\affil{IIIT-Hyderabad, India}

\author{M. Seifert}
\affil{}

\author{L. E. Sherbert}
\affil{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}

\author[0000-0003-0477-6220]{H. Sherwood-Taylor}
\affil{}

\author{A. Y. Shih}
\affil{NASA Goddard Space Flight Center, 8800 Greenbelt Road, Greenbelt, MD 20771, USA}

\author{M. T. Silbiger}
\affil{}

\author[0000-0003-2462-7273]{S. Singanamalla}
\affil{Microsoft Research}

\author[0000-0001-9898-5597]{L. P. Singer}
\affil{Astroparticle Physics Laboratory, NASA Goddard Space Flight Center, Code 661, 8800 Greenbelt Rd., Greenbelt, MD 20771, USA}

\author[0000-0003-1585-225X]{P. H. Sladen}
\affil{ARI/ZAH, Heidelberg}

\author{K. A. Sooley}
\affil{}

\author{S. Sornarajah}
\affil{}

\author[0000-0001-7751-1843]{O. Streicher}
\affil{Leibniz Institute for Astrophysics Potsdam (AIP), An der Sternwarte 16, 14482 Potsdam, Germany}

\author[0000-0003-1774-3436]{P. Teuben}
\affil{University of Maryland}

\author{S. W. Thomas}
\affil{Institute of Astronomy, University of Cambridge, Cambridge CB3 0HA, UK}

\author{J. E. H. Turner}
\affil{Gemini Observatory, Casilla 603, La Serena, Chile}

\author{V\'{i}ctor Terr\'{o}n}
\affil{Institute of Astrophysics of Andalusia (IAA-CSIC), Spain}

\author[0000-0002-1343-134X]{L. L. Watkins}
\affil{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}

\author{B. A. Weaver}
\affil{National Optical Astronomy Observatory, 950 N. Cherry Ave., Tucson, AZ 85719}

\author[0000-0003-4824-2087]{J. B. Whitmore}
\affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, VIC 3122, Australia}

\author[0000-0002-2958-4738]{J. Woillez}
\affil{European Southern Observatory - Karl-Schwarzschild-Str. 2, Garching bei München, D-85748, Germany}

\author{J. Xavier Prochaska}
\affil{Astronomy \& Astrophysics, UC Santa Cruz, 1156 High St., Santa Cruz, CA 95064 USA}

\author[0000-0003-2638-7648]{V. Zabalza}
\affil{}

\author[0000-0002-6219-5558]{A. de la Vega}
\affil{Department of Physics and Astronomy, Johns Hopkins University, 3400 N Charles Street, Baltimore, MD 21218}

\author[0000-0002-5830-8505]{M. H. van Kerkwijk}
\affil{Department of Astronomy \& Astrophysics, University of Toronto, 50 Saint George Street, Toronto, ON M5R 3B3, Canada}

### 2017-12-14 author.tex
first draft of the author list

@@
 \author[0000-0002-3713-6337]{B. M. Sip\H{o}cz}
-\affil{TBD}
+%\affil{}
 
@@
 \author[0000-0002-4576-9337]{M. Bachetti}
-\affil{INAF-Osservatorio Astronomico di Cagliari}
+\affil{INAF-Osservatorio Astronomico di Cagliari, via della Scienza 5, I-09047, Selargius, Italy}
 
 \author{A. V. Bakanov}
-\affil{}
+%\affil{}
 
@@
 \author{K. L. Berry}
-\affil{}
+%\affil{}
 
@@
 \author{E. M. Bray}
-\affil{}
+%\affil{}
 
@@
 \author{T. Finethy}
-\affil{}
+%\affil{}
 
 \author[0000-0003-4291-1091]{R. T. Fox}
-\affil{Unaffiliated}
+%\affil{}
 
@@
 \affil{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge, CB3 0HA, UK}
-
-\author[0000-0001-6431-9633]{A. Ginsburg}
-\affil{National Radio Astronomy Observatory, 1003 Lopezville Rd, Socorro, NM 87801}
-
-\author[0000-0001-6431-9633]{A. Ginsburg}
-\affil{National Radio Astronomy Observatory, 1003 Lopezville Road Socorro, NM 87801-0387}
 
@@
 \author{F. Grollier}
-\affil{Independent developer}
+%\affil{}
 
@@
 \author{A. Khvalko}
-\affil{}
+%\affil{}
 
@@
 \author[0000-0002-1395-8694]{D. M. Macleod}
-\affil{}
+%\affil{}
 
 \author[0000-0002-6324-5713]{M. Mastropietro}
-\affil{Ghent University}
+\affil{Department Physics and Astronomy, Ghent University, Krijgslaan 281, S9, B-9000 Gent, Belgium}
 
@@
 \author{S. Montagnac}
-\affil{obs-psr}
+\affil{Puy-Sainte-R\'eparade Observatory}
 
 \author[0000-0003-2528-3409]{B. M. Morris}
-\affil{University of Washington}
+\affil{Astronomy Department, University of Washington, Seattle, WA 98195, USA}
 
@@
 \author{M. N{\"o}the}
-\affil{TU Dortmund, Germany}
+\affil{TU Dortmund, Experimental Physics 5, Otto-Hahn-Str. 4, 44221 Dortmund, Germany}
 
@@
 \author[0000-0001-7790-5308]{S. Oh}
-\affil{Princeton University}
+\affil{Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08544, USA}
 
@@
 \author[0000-0002-9351-6051]{S. Pascual}
-\affil{Universidad Complutense de Madrid}
+\affil{Departamento de Astrofisica, Universidad Complutense de Madrid, Madrid, Spain}
 
 \author{R. Patil}
-\affil{}
+%\affil{}
 
@@
 \author{T. Rastogi}
-\affil{}
+%\affil{}
 
@@
 \author{M. Seifert}
-\affil{}
+%\affil{}
 
@@
 \author[0000-0003-0477-6220]{H. Sherwood-Taylor}
-\affil{}
+%\affil{}
 
@@
 \author{M. T. Silbiger}
-\affil{}
+%\affil{}
 
@@
 \author{K. A. Sooley}
-\affil{}
+%\affil{}
 
 \author{S. Sornarajah}
-\affil{}
+%\affil{}
 
@@
 \author[0000-0003-1774-3436]{P. Teuben}
-\affil{University of Maryland}
+\affil{Astronomy Department, University of Maryland, College Park, MD. 20742, USA}
 
@@
 \author[0000-0003-2638-7648]{V. Zabalza}
-\affil{}
+%\affil{}
 

### 2017-12-14 main.tex
first draft of the author list

@@
 \author{Astropy Project}
-\footnote{The author list has three parts: the 13 authors that were primary authors of  sections of the paper in order of contribution, the four members of the \astropy Project coordination committee, and contributions to the \astropy Project in alphabetical order.
+\footnote{The author list has three parts: the 13 authors that made significant contributions to the  writing of the paper in order of contribution, the four members of the \astropy Project coordination committee, and contributions to the \astropy Project in alphabetical order.
 The position in the author list does not correspond to contributions to the \astropy Project as a whole.
@@
 
-\acknowledgments The \astropy community is supported by and makes use
+\acknowledgments
+
+The \astropy community is supported by and makes use
 of a number of organizations and services outside the traditional

### 2017-12-14 main.tex
update to he acknowledgments

@@
 
-\author{Astropy Project}
-\footnote{The author list has three parts: the 13 authors that made significant contributions to the  writing of the paper in order of contribution, the four members of the \astropy Project coordination committee, and contributions to the \astropy Project in alphabetical order.
-The position in the author list does not correspond to contributions to the \astropy Project as a whole.
-A more complete list of contributors to the core package can be found in the \href{https://github.com/astropy/astropy/graphs/contributors}{package repository}, and at the \href{http://www.astropy.org/team.html}{\astropy team webpage}.}
-
-\input{author.tex}
+\author{Astropy Collaboration}
 
@@
 
+We would like to thank the community that have contributed to \astropy, 
+that have open issues and provided feedback, and have supported the 
+project in a number of different ways.  
+%insert significant contributors to astropy who hav decided not to 
+%be co-authors
+
 The \astropy community is supported by and makes use
@@
 \astropy projects.
+% Add list of institutes
+
+HMG was supported by the National Aeronautics and Space Administration through the 
+Smithsonian Astrophysical Observatory contract SV3-73016 to MIT for Support of the Chandra X-Ray Center, which is
+operated by the Smithsonian Astrophysical Observatory for and on behalf of the National Aeronautics Space 
+Administration under contract NAS8-03060. JTV was supported by the UW eScience Institute, via grants from the Moore
+Foundation, the Sloan Foundation, and the Washington Research Foundation. SMC acknowledges the National Research
+Foundation of South Africa. TLA was supported by NASA contract NAS8-03060. Support for E.J.T. was provided by NASA
+through Hubble Fellowship grant No. 51316.01 awarded by the Space Telescope Science Institute, which is operated by
+the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS 5-26555, as well as a 
+Giacconi Fellowship. MB was supported by the FONDECYT regular project 1170618 and the MINEDUC-UA projects codes 
+ANT 1655 and ANT 1656. DH was supported through the SFB 881 "The Milkyway System" by the German Research Foundation 
+(DFG). WEK was supported by an ESO Fellowship. C.M. is supported by NSF grant AST-1313484. SP was supported by 
+grant AYA2016-75808-R (FEDER) issued by the Spanish government. JEHT was supported by the Gemini Observatory, which
+is operated by the Association of Universities for Research in Astronomy, Inc., on behalf of the international 
+Gemini partnership of Argentina, Brazil, Canada, Chile, and the United States of America.
 

### 2017-12-14 author.tex
fixed unaffiliated
move V names to V in alphabetical
affil is deprecated, now use affiliation

--- 2017-12-14 author.tex
@@
 \author[0000-0003-0872-7098]{A. M. Price-Whelan}
-\affil{Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08544, USA}
+\affiliation{Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08544, USA}
 
 \author[0000-0002-3713-6337]{B. M. Sip\H{o}cz}
-\affil{TBD}
+\affiliation{}
 
 \author[0000-0003-4243-2840]{H. M. G\"{u}nther}
-\affil{Massachusetts Institute of Technology, Kavli Institute for Astrophysics and Space Research, 70 Vassar St., Cambridge, MA 02139, USA}
+\affiliation{Massachusetts Institute of Technology, Kavli Institute for Astrophysics and Space Research, 70 Vassar St., Cambridge, MA 02139, USA}
 
 \author[0000-0003-0079-4114]{P. L. Lim}
-\affil{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
+\affiliation{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
 
 \author[0000-0002-8969-5229]{S. M. Crawford}
-\affil{South African Astronomical Observatory, PO Box 9, Observatory 7935, Cape Town, South Africa}
+\affiliation{South African Astronomical Observatory, PO Box 9, Observatory 7935, Cape Town, South Africa}
 
 \author{S. Conseil}
-\affil{Univ Lyon, Univ Lyon1, Ens de Lyon, CNRS, Centre de Recherche Astrophysique de Lyon UMR5574, F-69230, Saint-Genis- Laval, France}
+\affiliation{Univ Lyon, Univ Lyon1, Ens de Lyon, CNRS, Centre de Recherche Astrophysique de Lyon UMR5574, F-69230, Saint-Genis- Laval, France}
 
 \author[0000-0003-4401-0430]{D. L. Shupe}
-\affil{Caltech/IPAC, 1200 E. California Blvd, Pasadena, CA 91125}
+\affiliation{Caltech/IPAC, 1200 E. California Blvd, Pasadena, CA 91125}
 
 \author[0000-0001-7988-8919]{M. W. Craig}
-\affil{Minnesota State University Moorhead/Department of Physics and Astronomy, 1104 7th Ave S, Moorhead, MN 56563}
+\affiliation{Minnesota State University Moorhead/Department of Physics and Astronomy, 1104 7th Ave S, Moorhead, MN 56563}
 
 \author[0000-0002-5686-9632]{N. Dencheva}
-\affil{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
+\affiliation{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
 
 \author[0000-0001-6431-9633]{A. Ginsburg}
-\affil{National Radio Astronomy Observatory, 1003 Lopezville Rd, Socorro, NM 87801}
+\affiliation{National Radio Astronomy Observatory, 1003 Lopezville Rd, Socorro, NM 87801}
 
 \author[0000-0002-9623-3401]{J. T. VanderPlas}
-\affil{eScience Institute, University of Washington, 3910 15th Ave NE, Seattle, WA 98195, USA}
+\affiliation{eScience Institute, University of Washington, 3910 15th Ave NE, Seattle, WA 98195, USA}
 
 \author[0000-0002-7908-9284]{L. D. Bradley}
-\affil{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
+\affiliation{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
 
 \author[0000-0003-0784-6909]{D. P\'{e}rez-Su\'{a}rez}
-\affil{University College London/Research IT Services, Gower St, Bloomsbury, London WC1E 6BT, United Kingdom}
+\affiliation{University College London/Research IT Services, Gower St, Bloomsbury, London WC1E 6BT, United Kingdom}
 
 \author[0000-0002-0455-9384]{M. de Val-Borro}
-\affil{NASA Goddard Space Flight Center, Astrochemistry Laboratory, 8800 Greenbelt Road, Greenbelt, MD 20771, USA}
+\affiliation{NASA Goddard Space Flight Center, Astrochemistry Laboratory, 8800 Greenbelt Road, Greenbelt, MD 20771, USA}
 
 \author{T. L. Aldcroft}
-\affil{Harvard/Smithsonian Center for Astrophysics, 60 Garden St., Cambridge, MA, 02138, USA}
+\affiliation{Harvard/Smithsonian Center for Astrophysics, 60 Garden St., Cambridge, MA, 02138, USA}
 
 \author[0000-0002-1821-0650]{K. L. Cruz}
-\affil{Department of Physics and Astronomy, Hunter College, City University of New York, 695 Park Avenue, New York, NY 10065}
-\affil{Physics, Graduate Center of the City University of New York, New York, NY, USA}
-\affil{ Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
+\affiliation{Department of Physics and Astronomy, Hunter College, City University of New York, 695 Park Avenue, New York, NY 10065}
+\affiliation{Physics, Graduate Center of the City University of New York, New York, NY, USA}
+\affiliation{ Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
 
 \author[0000-0002-8642-1329]{T. P. Robitaille}
-\affil{Aperio Software Ltd., Headingley Enterprise and Arts Centre, Bennett Road,  Leeds, LS6 3HN, United Kingdom}
+\affiliation{Aperio Software Ltd., Headingley Enterprise and Arts Centre, Bennett Road,  Leeds, LS6 3HN, United Kingdom}
 
 \author[0000-0002-9599-310X]{E. J. Tollerud}
-\affil{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
+\affiliation{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
 
 \author{C. Ardelean}
-\affil{Western University/Physics and Astronomy, 1151 Richmond St, London ON, N6A 3K7, Canada}
+\affiliation{Western University/Physics and Astronomy, 1151 Richmond St, London ON, N6A 3K7, Canada}
 
 \author{T. Babej}
-\affil{Department of Theoretical Physics \& Astrophysics, Masaryk University, Kotlarska 2, 61137 Brno, Czech Republic}
+\affiliation{Department of Theoretical Physics \& Astrophysics, Masaryk University, Kotlarska 2, 61137 Brno, Czech Republic}
 
 \author[0000-0002-4576-9337]{M. Bachetti}
-\affil{INAF-Osservatorio Astronomico di Cagliari}
+\affiliation{INAF-Osservatorio Astronomico di Cagliari, via della Scienza 5, I-09047, Selargius, Italy}
 
 \author{A. V. Bakanov}
-\affil{}
+\affiliation{}
 
 \author[0000-0001-7821-7195]{S. P. Bamford}
-\affil{School of Physics \& Astronomy, University of Nottingham, University Park, Nottingham NG7 2RD, UK}
+\affiliation{School of Physics \& Astronomy, University of Nottingham, University Park, Nottingham NG7 2RD, UK}
 
 \author[0000-0002-3306-3484]{G. Barentsen}
-\affil{NASA Ames Research Center, Moffett Field, CA 94043, USA}
+\affiliation{NASA Ames Research Center, Moffett Field, CA 94043, USA}
 
 \author[0000-0003-2767-0090]{P. Barmby}
-\affil{University of Western Ontario/Department of Physics \& Astronomy, 1151 Richmond St, London ON N5X4H1 Canada}
+\affiliation{University of Western Ontario/Department of Physics \& Astronomy, 1151 Richmond St, London ON N5X4H1 Canada}
 
 \author[0000-0002-9374-2729]{A. Baumbach}
-\affil{Heidelberg University, Kirchhoff Institut for Physics, Im Neuenheimer Feld 227, 69116 Heidelberg, Germany}
+\affiliation{Heidelberg University, Kirchhoff Institut for Physics, Im Neuenheimer Feld 227, 69116 Heidelberg, Germany}
 
 \author{K. L. Berry}
-\affil{}
+\affiliation{}
 
 \author{F. Biscani}
-\affil{Max Planck Institute for Astronomy}
+\affiliation{Max Planck Institute for Astronomy}
 
 \author[0000-0003-0946-6176]{M. Boquien}
-\affil{Unidad de Astronomía, Fac. Cs. Básicas, Universidad de Antofagasta, Avda. U. de Antofagasta 02800, Antofagasta, Chile}
+\affiliation{Unidad de Astronomía, Fac. Cs. Básicas, Universidad de Antofagasta, Avda. U. de Antofagasta 02800, Antofagasta, Chile}
 
 \author{K. A. Bostroem}
-\affil{UC Davis/Department of Physics, 1 Shields Ave, Davis, CA, 95616, USA}
+\affiliation{UC Davis/Department of Physics, 1 Shields Ave, Davis, CA, 95616, USA}
 
 \author{L. G. Bouma}
-\affil{Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08540, USA}
+\affiliation{Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08540, USA}
 
 \author[0000-0003-2680-005X]{G. B. Brammer}
-\affil{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
+\affiliation{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
 
 \author{E. M. Bray}
-\affil{}
+\affiliation{}
 
 \author{H. Breytenbach}
-\affil{South African Astronomical Observatory, PO Box 9, Observatory 7935, Cape Town, South Africa}
+\affiliation{South African Astronomical Observatory, PO Box 9, Observatory 7935, Cape Town, South Africa}
 
 \author[0000-0001-8001-0089]{H. Buddelmeijer}
-\affil{Leiden Observatory, Leiden University, P.O. Box 9513, 2300 RA, Leiden, The Netherlands}
+\affiliation{Leiden Observatory, Leiden University, P.O. Box 9513, 2300 RA, Leiden, The Netherlands}
 
 \author[0000-0003-4428-7835]{D. J. Burke}
-\affil{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA, 02138, USA}
+\affiliation{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA, 02138, USA}
 
 \author[0000-0002-7738-5389]{G. Calderone}
-\affil{Istituto Nazionale di Astrofisica, via Tiepolo 11 Trieste, Italy}
+\affiliation{Istituto Nazionale di Astrofisica, via Tiepolo 11 Trieste, Italy}
 
 \author{M. Cara}
-\affil{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
+\affiliation{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
 
 \author{J. V. M. Cardoso}
-\affil{Universidade Federal de Campina Grande, Campina Grande, PB 58429-900, Brazil; NASA Ames Research Center, Mountain View, CA 94035, USA; Bay Area Environmental Research Institute, Petaluma, CA 94952, USA}
+\affiliation{Universidade Federal de Campina Grande, Campina Grande, PB 58429-900, Brazil; NASA Ames Research Center, Mountain View, CA 94035, USA; Bay Area Environmental Research Institute, Petaluma, CA 94952, USA}
 
 \author{S. Cheedella}
-\affil{Department of Physics, Blacksburg VA, USA}
+\affiliation{Department of Physics, Blacksburg VA, USA}
 
 \author[0000-0002-5317-7518]{Y. Copin}
-\affil{Université de Lyon, F-69622, Lyon, France; Université de Lyon 1, Villeurbanne; CNRS/IN2P3, Institut de Physique Nucléaire de Lyon}
+\affiliation{Université de Lyon, F-69622, Lyon, France; Université de Lyon 1, Villeurbanne; CNRS/IN2P3, Institut de Physique Nucléaire de Lyon}
 
 \author[0000-0003-1204-3035]{D. Crichton}
-\affil{Department of Physics and Astronomy, Johns Hopkins University, Baltimore, MD 21218, USA}
+\affiliation{Department of Physics and Astronomy, Johns Hopkins University, Baltimore, MD 21218, USA}
 
 \author{D. D'Avella}
-\affil{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
+\affiliation{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
 
 \author[0000-0002-4198-4005]{C. Deil}
-\affil{Max-Planck-Institut f\"ur Kernphysik, PO Box 103980, 69029 Heidelberg, Germany}
+\affiliation{Max-Planck-Institut f\"ur Kernphysik, PO Box 103980, 69029 Heidelberg, Germany}
 
 \author[0000-0003-0526-3873]{\'{E}. Depagne}
-\affil{South African Astronomical Observatory, PO Box 9, Observatory 7935, Cape Town, South Africa}
+\affiliation{South African Astronomical Observatory, PO Box 9, Observatory 7935, Cape Town, South Africa}
 
 \author[0000-0002-8134-9591]{J. P. Dietrich}
-\affil{Faculty of Physics, Ludwig-Maximilians-Universit\"at, Scheinerstr. 181679 Munich, Germany;Excellence Cluster Universe, Boltzmannstr. 2, 85748 Garching b. M\"unchen, Germany}
+\affiliation{Faculty of Physics, Ludwig-Maximilians-Universit\"at, Scheinerstr. 181679 Munich, Germany;Excellence Cluster Universe, Boltzmannstr. 2, 85748 Garching b. M\"unchen, Germany}
 
 \author{A. Donath}
-\affil{Max-Planck-Institut f\"ur Kernphysik, PO Box 103980, 69029 Heidelberg, Germany}
+\affiliation{Max-Planck-Institut f\"ur Kernphysik, PO Box 103980, 69029 Heidelberg, Germany}
 
 \author{T. Erben}
-\affil{Argelander-Institut f\"ur Astronomie, Auf dem H\"ugel 71, 53121 Bonn / Germany}
+\affiliation{Argelander-Institut f\"ur Astronomie, Auf dem H\"ugel 71, 53121 Bonn / Germany}
 
 \author[0000-0002-8919-079X]{L. A. Ferreira}
-\affil{Instituto de Matemática Estatística e Física – IMEF, Universidade Federal do Rio Grande – FURG, Rio Grande, RS 96203-900, Brazil}
+\affiliation{Instituto de Matemática Estatística e Física – IMEF, Universidade Federal do Rio Grande – FURG, Rio Grande, RS 96203-900, Brazil}
 
 \author{T. Finethy}
-\affil{}
+\affiliation{}
 
 \author[0000-0003-4291-1091]{R. T. Fox}
-\affil{Unaffiliated}
+\affiliation{}
 
 \author[0000-0002-9853-5673]{L. H. Garrison}
-\affil{Harvard-Smithsonian Center for Astrophysics, 60 Garden St., Cambridge, MA, 02138, USA}
+\affiliation{Harvard-Smithsonian Center for Astrophysics, 60 Garden St., Cambridge, MA, 02138, USA}
 
 \author{S. L. J. Gibbons}
-\affil{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge, CB3 0HA, UK}
-
-\author[0000-0001-6431-9633]{A. Ginsburg}
-\affil{National Radio Astronomy Observatory, 1003 Lopezville Rd, Socorro, NM 87801}
-
-\author[0000-0001-6431-9633]{A. Ginsburg}
-\affil{National Radio Astronomy Observatory, 1003 Lopezville Road Socorro, NM 87801-0387}
+\affiliation{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge, CB3 0HA, UK}
 
 \author{D. A. Goldstein}
-\affil{Department of Astronomy, UC Berkeley, 501 Campbell Hall \#3411, Berkeley, CA 94720, USA; Berkeley Lab, 1 Cyclotron Road, Berkeley, CA 94720, USA}
+\affiliation{Department of Astronomy, UC Berkeley, 501 Campbell Hall \#3411, Berkeley, CA 94720, USA; Berkeley Lab, 1 Cyclotron Road, Berkeley, CA 94720, USA}
 
 \author[0000-0002-0300-3333]{R. Gommers}
-\affil{Scion, Private Bag 3020, Rotorua, New Zealand}
+\affiliation{Scion, Private Bag 3020, Rotorua, New Zealand}
 
 \author[0000-0003-4970-2874]{J. P. Greco}
-\affil{Department of Astrophysical Sciences,  Princeton University, Princeton, NJ 08544, USA}
+\affiliation{Department of Astrophysical Sciences,  Princeton University, Princeton, NJ 08544, USA}
 
 \author{P. Greenfield}
-\affil{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
+\affiliation{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
 
 \author[0000-0002-6508-2938]{A. M. Groener}
-\affil{Drexel University, Physics Department, Philadelphia, PA 19104, USA}
+\affiliation{Drexel University, Physics Department, Philadelphia, PA 19104, USA}
 
 \author{F. Grollier}
-\affil{Independent developer}
+\affiliation{}
 
 \author[0000-0003-2031-7737]{A. Hagen}
-\affil{Vizual.ai, 3600 O'Donnell St, Suite 250, Baltimore, MD 21224 ; Dept of Astronomy and Astrophysics, Pennsylvania State University, University Park, PA 16802}
+\affiliation{Vizual.ai, 3600 O'Donnell St, Suite 250, Baltimore, MD 21224 ; Dept of Astronomy and Astrophysics, Pennsylvania State University, University Park, PA 16802}
 
 \author{P. Hirst}
-\affil{Gemini Observatory, 670 N. Aohoku Pl, Hilo, HI 96720, USA}
+\affiliation{Gemini Observatory, 670 N. Aohoku Pl, Hilo, HI 96720, USA}
 
 \author[0000-0002-8546-9128]{D. Homeier}
-\affil{Zentrum f{\"u}r Astronomie der Universit{\"a}t Heidelberg, Landessternwarte, K{\"o}nigstuhl 12, D-69117 Heidelberg, Germany}
+\affiliation{Zentrum f{\"u}r Astronomie der Universit{\"a}t Heidelberg, Landessternwarte, K{\"o}nigstuhl 12, D-69117 Heidelberg, Germany}
 
 \author[0000-0002-4600-7852]{A. J. Horton}
-\affil{Australian Astronomical Observatory, 105 Delhi Road, North Ryde NSW 2113, Australia}
+\affiliation{Australian Astronomical Observatory, 105 Delhi Road, North Ryde NSW 2113, Australia}
 
 \author[0000-0002-0832-2974]{G. Hosseinzadeh}
-\affil{Las Cumbres Observatory, 6740 Cortona Drive, Suite 102, Goleta, CA 93117-5575, USA; Department of Physics, University of California, Santa Barbara, CA 93106-9530, USA}
+\affiliation{Las Cumbres Observatory, 6740 Cortona Drive, Suite 102, Goleta, CA 93117-5575, USA; Department of Physics, University of California, Santa Barbara, CA 93106-9530, USA}
 
 \author{L. Hu}
-\affil{Imperial College London,  Kensington, London SW7 2AZ, United Kingdom}
+\affiliation{Imperial College London,  Kensington, London SW7 2AZ, United Kingdom}
 
 \author[0000-0003-4989-0289]{J. S. Hunkeler}
-\affil{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
+\affiliation{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
 
 \author[0000-0001-5250-2633]{\v{Z}. Ivezi\'{c}}
-\affil{Department of Astronomy, University of Washington, Seattle, WA 98155}
+\affiliation{Department of Astronomy, University of Washington, Seattle, WA 98155}
 
 \author{A. Jain}
-\affil{BITS PILANI/Computer Science, Pilani Campus, Rajasthan, India}
+\affiliation{BITS PILANI/Computer Science, Pilani Campus, Rajasthan, India}
 
 \author[0000-0001-5982-167X]{T. Jenness}
-\affil{Large Synoptic Survey Telescope, 950 N Cherry Ave, Tucson, AZ, 85719}
+\affiliation{Large Synoptic Survey Telescope, 950 N Cherry Ave, Tucson, AZ, 85719}
 
 \author{G. Kanarek}
-\affil{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
+\affiliation{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
 
 \author[0000-0002-7612-0469]{S. Kendrew}
-\affil{European Space Agency, Space Telescope Science Institute, 3700 San Martin Drive, Baltimore MD 21231, USA}
+\affiliation{European Space Agency, Space Telescope Science Institute, 3700 San Martin Drive, Baltimore MD 21231, USA}
 
 \author[0000-0002-8211-1892]{N. S. Kern}
-\affil{UC Berkeley Department of Astronomy, 501 Campbell Hall, Berkeley, CA, 94709}
+\affiliation{UC Berkeley Department of Astronomy, 501 Campbell Hall, Berkeley, CA, 94709}
 
 \author[0000-0002-0479-7235]{W. E. Kerzendorf}
-\affil{European Southern Observatory, Karl-Schwarzschild-Stra{\ss}e 2, 85748 Garching bei M\"{u}nchen, Germany}
+\affiliation{European Southern Observatory, Karl-Schwarzschild-Stra{\ss}e 2, 85748 Garching bei M\"{u}nchen, Germany}
 
 \author{A. Khvalko}
-\affil{}
+\affiliation{}
 
 \author{J. King}
-\affil{Max-Planck-Institut f\"ur Kernphysik, PO Box 103980, 69029 Heidelberg, Germany}
+\affiliation{Max-Planck-Institut f\"ur Kernphysik, PO Box 103980, 69029 Heidelberg, Germany}
 
 \author[0000-0002-8828-5463]{D. Kirkby}
-\affil{Department of Physics and Astronomy, University of California, Irvine, CA 92697, USA}
+\affiliation{Department of Physics and Astronomy, University of California, Irvine, CA 92697, USA}
 
 \author{A. M. Kulkarni}
-\affil{College of Engineering Pune/Department of Computer Engineering and IT, Shivajinagar, Pune 411005, India}
+\affiliation{College of Engineering Pune/Department of Computer Engineering and IT, Shivajinagar, Pune 411005, India}
 
 \author{A. Kumar}
-\affil{Delhi Technological University}
+\affiliation{Delhi Technological University}
 
 \author[0000-0003-2193-5369]{A. Lee}
-\affil{Department of Physics, University of Berkeley, Califonia, CA94709, USA}
+\affiliation{Department of Physics, University of Berkeley, Califonia, CA94709, USA}
 
 \author[0000-0001-5820-475X]{D. Lenz}
-\affil{Jet Propulsion Laboratory, California Institute of Technology, 4800 Oak Grove Drive, Pasadena, CA 91109, USA}
+\affiliation{Jet Propulsion Laboratory, California Institute of Technology, 4800 Oak Grove Drive, Pasadena, CA 91109, USA}
 
 \author[0000-0001-7221-855X]{S. P. Littlefair}
-\affil{Dept of Physics \& Astronomy, University of Sheffield, Sheffield, S3 7RH, UK}
+\affiliation{Dept of Physics \& Astronomy, University of Sheffield, Sheffield, S3 7RH, UK}
 
 \author[0000-0003-3270-6844]{Z. Ma}
-\affil{Department of Physics and Astronomy, University of Missouri, Columbia, Missouri, 65211, USA}
+\affiliation{Department of Physics and Astronomy, University of Missouri, Columbia, Missouri, 65211, USA}
 
 \author[0000-0002-1395-8694]{D. M. Macleod}
-\affil{}
+\affiliation{}
 
 \author[0000-0002-6324-5713]{M. Mastropietro}
-\affil{Ghent University}
+\affiliation{Department Physics and Astronomy, Ghent University, Krijgslaan 281, S9, B-9000 Gent, Belgium}
 
 \author[0000-0001-5807-7893]{C. McCully}
-\affil{Las Cumbres Observatory, 6740 Cortona Drive, Suite 102, Goleta, CA 93117-5575, USA; Department of Physics, University of California, Santa Barbara, CA 93106-9530, USA}
+\affiliation{Las Cumbres Observatory, 6740 Cortona Drive, Suite 102, Goleta, CA 93117-5575, USA; Department of Physics, University of California, Santa Barbara, CA 93106-9530, USA}
 
 \author{S. Montagnac}
-\affil{obs-psr}
+\affiliation{Puy-Sainte-R\'eparade Observatory}
 
 \author[0000-0003-2528-3409]{B. M. Morris}
-\affil{University of Washington}
+\affiliation{Astronomy Department, University of Washington, Seattle, WA 98195, USA}
 
 \author[0000-0003-4217-4642]{S. J. Mumford}
-\affil{SP$^{2}$RC, School of Mathematics and Statistics, The University of Sheffield U.K.}
+\affiliation{SP$^{2}$RC, School of Mathematics and Statistics, The University of Sheffield U.K.}
 
 \author[0000-0002-1631-4114]{D. Muna}
-\affil{Center for Cosmology and Astroparticle Physics, The Ohio State University, 191 West Woodruff Avenue, Columbus, OH 43210}
+\affiliation{Center for Cosmology and Astroparticle Physics, The Ohio State University, 191 West Woodruff Avenue, Columbus, OH 43210}
 
 \author[0000-0001-6628-8033]{N. A. Murphy}
-\affil{Harvard-Smithsonian Center for Astrophysics, 60 Garden St, Cambridge, MA 02138, USA}
+\affiliation{Harvard-Smithsonian Center for Astrophysics, 60 Garden St, Cambridge, MA 02138, USA}
 
 \author{S. Nelson}
-\affil{Minnesota State University Moorhead, 1104 7th Avenue South Moorhead, MN 56563, United States}
+\affiliation{Minnesota State University Moorhead, 1104 7th Avenue South Moorhead, MN 56563, United States}
 
 \author[0000-0002-1966-3627]{G. H. Nguyen}
-\affil{VNU-HCMC, University of Natural Sciences/Faculty of IT, 227 Nguyen Van Cu St., Ward 4, District 5, Ho Chi Minh City, Vietnam}
+\affiliation{VNU-HCMC, University of Natural Sciences/Faculty of IT, 227 Nguyen Van Cu St., Ward 4, District 5, Ho Chi Minh City, Vietnam}
 
 \author[0000-0001-8720-5612]{J. P. Ninan}
-\affil{The Pennsylvania State University, University Park, PA, USA}
+\affiliation{The Pennsylvania State University, University Park, PA, USA}
 
 \author{M. N{\"o}the}
-\affil{TU Dortmund, Germany}
+\affiliation{TU Dortmund, Experimental Physics 5, Otto-Hahn-Str. 4, 44221 Dortmund, Germany}
 
 \author{S. Ogaz}
-\affil{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
+\affiliation{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
 
 \author[0000-0001-7790-5308]{S. Oh}
-\affil{Princeton University}
+\affiliation{Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08544, USA}
 
 \author{J. K. Parejko}
-\affil{Department of Astronomy, University of Washington, Box 351580, Seattle, WA 98195, USA}
+\affiliation{Department of Astronomy, University of Washington, Box 351580, Seattle, WA 98195, USA}
 
 \author{N. Parley}
-\affil{University of Reading, Whiteknights Campus, Reading RG6 6BX, UK}
+\affiliation{University of Reading, Whiteknights Campus, Reading RG6 6BX, UK}
 
 \author[0000-0002-9351-6051]{S. Pascual}
-\affil{Universidad Complutense de Madrid}
+\affiliation{Departamento de Astrofisica, Universidad Complutense de Madrid, Madrid, Spain}
 
 \author{R. Patil}
-\affil{}
+\affiliation{}
 
 \author{A. A. Patil}
-\affil{Pune Institute of Computer Technology, Pune 411043, India}
+\affiliation{Pune Institute of Computer Technology, Pune 411043, India}
 
 \author[0000-0002-9912-5705]{A. L. Plunkett}
-\affil{European Southern Observatory, Av. Alonso de C\'{o}rdova 3107, Vitacura, Santiago, Chile}
+\affiliation{European Southern Observatory, Av. Alonso de C\'{o}rdova 3107, Vitacura, Santiago, Chile}
 
 \author{T. Rastogi}
-\affil{}
+\affiliation{}
 
 \author{V. Reddy Janga}
-\affil{Indian Institute of Technology, Mechanical Engineering, Kharagpur, India}
+\affiliation{Indian Institute of Technology, Mechanical Engineering, Kharagpur, India}
 
 \author[0000-0003-1149-6294]{J. Sabater}
-\affil{Institute for Astronomy (IfA), University of Edinburgh, Royal Observatory, Blackford Hill, EH9 3HJ Edinburgh, U.K.}
+\affiliation{Institute for Astronomy (IfA), University of Edinburgh, Royal Observatory, Blackford Hill, EH9 3HJ Edinburgh, U.K.}
 
 \author{P. Sakurikar}
-\affil{IIIT-Hyderabad, India}
+\affiliation{IIIT-Hyderabad, India}
 
 \author{M. Seifert}
-\affil{}
+\affiliation{}
 
 \author{L. E. Sherbert}
-\affil{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
+\affiliation{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
 
 \author[0000-0003-0477-6220]{H. Sherwood-Taylor}
-\affil{}
+\affiliation{}
 
 \author{A. Y. Shih}
-\affil{NASA Goddard Space Flight Center, 8800 Greenbelt Road, Greenbelt, MD 20771, USA}
+\affiliation{NASA Goddard Space Flight Center, 8800 Greenbelt Road, Greenbelt, MD 20771, USA}
 
 \author{M. T. Silbiger}
-\affil{}
+\affiliation{}
 
 \author[0000-0003-2462-7273]{S. Singanamalla}
-\affil{Microsoft Research}
+\affiliation{Microsoft Research}
 
 \author[0000-0001-9898-5597]{L. P. Singer}
-\affil{Astroparticle Physics Laboratory, NASA Goddard Space Flight Center, Code 661, 8800 Greenbelt Rd., Greenbelt, MD 20771, USA}
+\affiliation{Astroparticle Physics Laboratory, NASA Goddard Space Flight Center, Code 661, 8800 Greenbelt Rd., Greenbelt, MD 20771, USA}
 
 \author[0000-0003-1585-225X]{P. H. Sladen}
-\affil{ARI/ZAH, Heidelberg}
+\affiliation{ARI/ZAH, Heidelberg}
 
 \author{K. A. Sooley}
-\affil{}
+\affiliation{}
 
 \author{S. Sornarajah}
-\affil{}
+\affiliation{}
 
 \author[0000-0001-7751-1843]{O. Streicher}
-\affil{Leibniz Institute for Astrophysics Potsdam (AIP), An der Sternwarte 16, 14482 Potsdam, Germany}
+\affiliation{Leibniz Institute for Astrophysics Potsdam (AIP), An der Sternwarte 16, 14482 Potsdam, Germany}
 
 \author[0000-0003-1774-3436]{P. Teuben}
-\affil{University of Maryland}
+\affiliation{Astronomy Department, University of Maryland, College Park, MD. 20742, USA}
 
 \author{S. W. Thomas}
-\affil{Institute of Astronomy, University of Cambridge, Cambridge CB3 0HA, UK}
+\affiliation{Institute of Astronomy, University of Cambridge, Cambridge CB3 0HA, UK}
 
 \author{J. E. H. Turner}
-\affil{Gemini Observatory, Casilla 603, La Serena, Chile}
+\affiliation{Gemini Observatory, Casilla 603, La Serena, Chile}
 
 \author{V\'{i}ctor Terr\'{o}n}
-\affil{Institute of Astrophysics of Andalusia (IAA-CSIC), Spain}
+\affiliation{Institute of Astrophysics of Andalusia (IAA-CSIC), Spain}
+
+\author[0000-0002-5830-8505]{M. H. van Kerkwijk}
+\affiliation{Department of Astronomy \& Astrophysics, University of Toronto, 50 Saint George Street, Toronto, ON M5R 3B3, Canada}
+
+\author[0000-0002-6219-5558]{A. de la Vega}
+\affiliation{Department of Physics and Astronomy, Johns Hopkins University, 3400 N Charles Street, Baltimore, MD 21218}
 
 \author[0000-0002-1343-134X]{L. L. Watkins}
-\affil{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
+\affiliation{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
 
 \author{B. A. Weaver}
-\affil{National Optical Astronomy Observatory, 950 N. Cherry Ave., Tucson, AZ 85719}
+\affiliation{National Optical Astronomy Observatory, 950 N. Cherry Ave., Tucson, AZ 85719}
 
 \author[0000-0003-4824-2087]{J. B. Whitmore}
-\affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, VIC 3122, Australia}
+\affiliation{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, VIC 3122, Australia}
 
 \author[0000-0002-2958-4738]{J. Woillez}
-\affil{European Southern Observatory - Karl-Schwarzschild-Str. 2, Garching bei München, D-85748, Germany}
+\affiliation{European Southern Observatory - Karl-Schwarzschild-Str. 2, Garching bei München, D-85748, Germany}
 
 \author{J. Xavier Prochaska}
-\affil{Astronomy \& Astrophysics, UC Santa Cruz, 1156 High St., Santa Cruz, CA 95064 USA}
+\affiliation{Astronomy \& Astrophysics, UC Santa Cruz, 1156 High St., Santa Cruz, CA 95064 USA}
 
 \author[0000-0003-2638-7648]{V. Zabalza}
-\affil{}
-
-\author[0000-0002-6219-5558]{A. de la Vega}
-\affil{Department of Physics and Astronomy, Johns Hopkins University, 3400 N Charles Street, Baltimore, MD 21218}
-
-\author[0000-0002-5830-8505]{M. H. van Kerkwijk}
-\affil{Department of Astronomy \& Astrophysics, University of Toronto, 50 Saint George Street, Toronto, ON M5R 3B3, Canada}
+\affiliation{}

### 2017-12-14 author.tex
collaborations and started necommands

@@
+\newcommand{\affilprinceton}{Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08544, USA}
+\newcommand{\affilmit}{Massachusetts Institute of Technology, Kavli Institute for Astrophysics and Space Research, 70 Vassar St., Cambridge, MA 02139, USA}
+\newcommand{\affilstsci}{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
+
+\collaboration{Primary paper contributors:}
+
 \author[0000-0003-0872-7098]{A. M. Price-Whelan}
-\affiliation{Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08544, USA}
+\affiliation{\affilprinceton}
 
@@
 \author[0000-0003-4243-2840]{H. M. G\"{u}nther}
-\affiliation{Massachusetts Institute of Technology, Kavli Institute for Astrophysics and Space Research, 70 Vassar St., Cambridge, MA 02139, USA}
+\affiliation{\affilmit}
 
 \author[0000-0003-0079-4114]{P. L. Lim}
-\affiliation{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
+\affiliation{\affilstsci}
 
@@
 
+\collaboration{Astropy coordination committee:}
+
 \author{T. L. Aldcroft}
@@
 \affiliation{Physics, Graduate Center of the City University of New York, New York, NY, USA}
-\affiliation{ Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
+\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
 
@@
 \affiliation{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
+
+\collaboration{Astropy contributors:}
 

### 2017-12-14 author.tex
collect common affiliations to avoid spelling errors

@@
-\newcommand{\affilprinceton}{Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08544, USA}
-\newcommand{\affilmit}{Massachusetts Institute of Technology, Kavli Institute for Astrophysics and Space Research, 70 Vassar St., Cambridge, MA 02139, USA}
-\newcommand{\affilstsci}{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
+\newcommand{\afprinceton}{Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08544, USA}
+\newcommand{\afstsci}{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
+\newcommand{\afsaao}{South African Astronomical Observatory, PO Box 9, Observatory 7935, Cape Town, South Africa}
+\newcommand{\afminnstate}{Department of Physics and Astronomy, Minnesota State University Moorhead, 1104 7th Ave S, Moorhead, MN 56563}
+\newcommand{\afgoddard}{NASA Goddard Space Flight Center, 8800 Greenbelt Road, Greenbelt, MD 20771, USA}
+\newcommand{\afcfa}{Harvard-Smithsonian Center for Astrophysics, 60 Garden St., Cambridge, MA, 02138, USA}
+\newcommand{\afwesternontario}{Department of Physics \& Astronomy, University of Western Ontario, 1151 Richmond St, London ON N5X4H1 Canada}
+\newcommand{\afnasaames}{NASA Ames Research Center, Moffett Field, CA 94043, USA}
+\newcommand{\afjhu}{Department of Physics and Astronomy, Johns Hopkins University, Baltimore, MD 21218, USA}
+\newcommand{\afmpik}{Max-Planck-Institut f\"ur Kernphysik, PO Box 103980, 69029 Heidelberg, Germany}
+\newcommand{\afioa}{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge, CB3 0HA, UK}
+\newcommand{\afpennstate}{Dept of Astronomy and Astrophysics, Pennsylvania State University, University Park, PA 16802}
+\newcommand{\afgemini}{Gemini Observatory, 670 N. Aohoku Pl, Hilo, HI 96720, USA}
+\newcommand{\aflco}{Las Cumbres Observatory, 6740 Cortona Drive, Suite 102, Goleta, CA 93117-5575, USA}
+\newcommand{\afucsb}{Department of Physics, University of California, Santa Barbara, CA 93106-9530, USA}
+\newcommand{\afesomunich}{European Southern Observatory, Karl-Schwarzschild-Stra{\ss}e 2, 85748 Garching bei M\"{u}nchen, Germany}
+\newcommand{\afuw}{Department of Astronomy, University of Washington, Seattle, WA 98155}
+\newcommand{\afberkeleyastro}{Department of Astronomy, UC Berkeley, 501 Campbell Hall \#3411, Berkeley, CA 94720, USA}
 
@@
 \author[0000-0003-0872-7098]{A. M. Price-Whelan}
-\affiliation{\affilprinceton}
+\affiliation{\afprinceton}
 
@@
 \author[0000-0003-4243-2840]{H. M. G\"{u}nther}
-\affiliation{\affilmit}
+\affiliation{Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, 70 Vassar St., Cambridge, MA 02139, USA}
 
 \author[0000-0003-0079-4114]{P. L. Lim}
-\affiliation{\affilstsci}
+\affiliation{\afstsci}
 
 \author[0000-0002-8969-5229]{S. M. Crawford}
-\affiliation{South African Astronomical Observatory, PO Box 9, Observatory 7935, Cape Town, South Africa}
+\affiliation{\afsaao}
 
 \author{S. Conseil}
-\affiliation{Univ Lyon, Univ Lyon1, Ens de Lyon, CNRS, Centre de Recherche Astrophysique de Lyon UMR5574, F-69230, Saint-Genis- Laval, France}
+\affiliation{Univ Lyon, Univ Lyon1, Ens de Lyon, CNRS, Centre de Recherche Astrophysique de Lyon UMR5574, F-69230, Saint-Genis-Laval, France}
 
@@
 \author[0000-0001-7988-8919]{M. W. Craig}
-\affiliation{Minnesota State University Moorhead/Department of Physics and Astronomy, 1104 7th Ave S, Moorhead, MN 56563}
+\affiliation{\afminnstate}
 
 \author[0000-0002-5686-9632]{N. Dencheva}
-\affiliation{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
+\affiliation{\afstsci}
 
@@
 \author[0000-0002-7908-9284]{L. D. Bradley}
-\affiliation{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
+\affiliation{\afstsci}
 
@@
 \author[0000-0002-0455-9384]{M. de Val-Borro}
-\affiliation{NASA Goddard Space Flight Center, Astrochemistry Laboratory, 8800 Greenbelt Road, Greenbelt, MD 20771, USA}
+\affiliation{Astrochemistry Laboratory, \afgoddard}
 
@@
 \author{T. L. Aldcroft}
-\affiliation{Harvard/Smithsonian Center for Astrophysics, 60 Garden St., Cambridge, MA, 02138, USA}
+\affiliation{\afcfa}
 
@@
 \author[0000-0002-9599-310X]{E. J. Tollerud}
-\affiliation{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
+\affiliation{\afstsci}
 
@@
 \author{C. Ardelean}
-\affiliation{Western University/Physics and Astronomy, 1151 Richmond St, London ON, N6A 3K7, Canada}
+\affiliation{\afwesternontario}
 
@@
 \author[0000-0002-3306-3484]{G. Barentsen}
-\affiliation{NASA Ames Research Center, Moffett Field, CA 94043, USA}
+\affiliation{\afnasaames}
 
 \author[0000-0003-2767-0090]{P. Barmby}
-\affiliation{University of Western Ontario/Department of Physics \& Astronomy, 1151 Richmond St, London ON N5X4H1 Canada}
+\affiliation{\afwesternontario}
 
@@
 \author{F. Biscani}
-\affiliation{Max Planck Institute for Astronomy}
+\affiliation{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg, Germany}
 
@@
 \author{K. A. Bostroem}
-\affiliation{UC Davis/Department of Physics, 1 Shields Ave, Davis, CA, 95616, USA}
+\affiliation{Department of Physics, UC Davis, 1 Shields Ave, Davis, CA, 95616, USA}
 
 \author{L. G. Bouma}
-\affiliation{Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08540, USA}
+\affiliation{\afprinceton}
 
 \author[0000-0003-2680-005X]{G. B. Brammer}
-\affiliation{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
+\affiliation{\afstsci}
 
@@
 \author{H. Breytenbach}
-\affiliation{South African Astronomical Observatory, PO Box 9, Observatory 7935, Cape Town, South Africa}
+\affiliation{\afsaao}
 
@@
 \author[0000-0003-4428-7835]{D. J. Burke}
-\affiliation{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA, 02138, USA}
+\affiliation{\afcfa}
 
@@
 \author{M. Cara}
-\affiliation{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
+\affiliation{\afstsci}
 
 \author{J. V. M. Cardoso}
-\affiliation{Universidade Federal de Campina Grande, Campina Grande, PB 58429-900, Brazil; NASA Ames Research Center, Mountain View, CA 94035, USA; Bay Area Environmental Research Institute, Petaluma, CA 94952, USA}
+\affiliation{Universidade Federal de Campina Grande, Campina Grande, PB 58429-900, Brazil}
+\affiliation{\afnasaames}
+\affiliation{Bay Area Environmental Research Institute, Petaluma, CA 94952, USA}
 
 \author{S. Cheedella}
-\affiliation{Department of Physics, Blacksburg VA, USA}
+\affiliation{Department of Physics, Virginia Tech, Blacksburg, VA 24061, USA}
 
 \author[0000-0002-5317-7518]{Y. Copin}
-\affiliation{Université de Lyon, F-69622, Lyon, France; Université de Lyon 1, Villeurbanne; CNRS/IN2P3, Institut de Physique Nucléaire de Lyon}
+\affiliation{CNRS/IN2P3, Institut de Physique Nucleaire de Lyon, Universite de Lyon, Universite de Lyon 1, Villeurbanne, F-69622, Lyon, France}
 
 \author[0000-0003-1204-3035]{D. Crichton}
-\affiliation{Department of Physics and Astronomy, Johns Hopkins University, Baltimore, MD 21218, USA}
+\affiliation{\afjhu}
 
 \author{D. D'Avella}
-\affiliation{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
+\affiliation{\afstsci}
 
 \author[0000-0002-4198-4005]{C. Deil}
-\affiliation{Max-Planck-Institut f\"ur Kernphysik, PO Box 103980, 69029 Heidelberg, Germany}
+\affiliation{\afmpik}
 
 \author[0000-0003-0526-3873]{\'{E}. Depagne}
-\affiliation{South African Astronomical Observatory, PO Box 9, Observatory 7935, Cape Town, South Africa}
+\affiliation{\afsaao}
 
 \author[0000-0002-8134-9591]{J. P. Dietrich}
-\affiliation{Faculty of Physics, Ludwig-Maximilians-Universit\"at, Scheinerstr. 181679 Munich, Germany;Excellence Cluster Universe, Boltzmannstr. 2, 85748 Garching b. M\"unchen, Germany}
+\affiliation{Faculty of Physics, Ludwig-Maximilians-Universit\"at, Scheinerstr. 181679 Munich, Germany}
+\affiliation{Excellence Cluster Universe, Boltzmannstr. 2, 85748 Garching b. M\"unchen, Germany}
 
 \author{A. Donath}
-\affiliation{Max-Planck-Institut f\"ur Kernphysik, PO Box 103980, 69029 Heidelberg, Germany}
+\affiliation{\afmpik}
 
 \author{T. Erben}
-\affiliation{Argelander-Institut f\"ur Astronomie, Auf dem H\"ugel 71, 53121 Bonn / Germany}
+\affiliation{Argelander-Institut f\"ur Astronomie, Auf dem H\"ugel 71, 53121 Bonn, Germany}
 
@@
 \author[0000-0002-9853-5673]{L. H. Garrison}
-\affiliation{Harvard-Smithsonian Center for Astrophysics, 60 Garden St., Cambridge, MA, 02138, USA}
+\affiliation{\afcfa}
 
 \author{S. L. J. Gibbons}
-\affiliation{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge, CB3 0HA, UK}
+\affiliation{\afioa}
 
 \author{D. A. Goldstein}
-\affiliation{Department of Astronomy, UC Berkeley, 501 Campbell Hall \#3411, Berkeley, CA 94720, USA; Berkeley Lab, 1 Cyclotron Road, Berkeley, CA 94720, USA}
+\affiliation{\afberkeleyastro}
+\affiliation{Lawrence Berkeley National Laboratory, 1 Cyclotron Road, Berkeley, CA 94720, USA}
 
@@
 \author[0000-0003-4970-2874]{J. P. Greco}
-\affiliation{Department of Astrophysical Sciences,  Princeton University, Princeton, NJ 08544, USA}
+\affiliation{\afprinceton}
 
 \author{P. Greenfield}
-\affiliation{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
+\affiliation{\afstsci}
 
@@
 \author[0000-0003-2031-7737]{A. Hagen}
-\affiliation{Vizual.ai, 3600 O'Donnell St, Suite 250, Baltimore, MD 21224 ; Dept of Astronomy and Astrophysics, Pennsylvania State University, University Park, PA 16802}
+\affiliation{Vizual.ai, 3600 O'Donnell St, Suite 250, Baltimore, MD 21224}
+\affiliation{\afpennstate}
 
 \author{P. Hirst}
-\affiliation{Gemini Observatory, 670 N. Aohoku Pl, Hilo, HI 96720, USA}
+\affiliation{\afgemini}
 
@@
 \author[0000-0002-0832-2974]{G. Hosseinzadeh}
-\affiliation{Las Cumbres Observatory, 6740 Cortona Drive, Suite 102, Goleta, CA 93117-5575, USA; Department of Physics, University of California, Santa Barbara, CA 93106-9530, USA}
+\affiliation{\aflco}
+\affiliation{\afucsb}
 
@@
 \author[0000-0003-4989-0289]{J. S. Hunkeler}
-\affiliation{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
+\affiliation{\afstsci}
 
 \author[0000-0001-5250-2633]{\v{Z}. Ivezi\'{c}}
-\affiliation{Department of Astronomy, University of Washington, Seattle, WA 98155}
+\affiliation{\afuw}
 
@@
 \author{G. Kanarek}
-\affiliation{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
+\affiliation{\afstsci}
 
 \author[0000-0002-7612-0469]{S. Kendrew}
-\affiliation{European Space Agency, Space Telescope Science Institute, 3700 San Martin Drive, Baltimore MD 21231, USA}
+\affiliation{European Space Agency, \afstsci}
 
 \author[0000-0002-8211-1892]{N. S. Kern}
-\affiliation{UC Berkeley Department of Astronomy, 501 Campbell Hall, Berkeley, CA, 94709}
+\affiliation{\afberkeleyastro}
 
 \author[0000-0002-0479-7235]{W. E. Kerzendorf}
-\affiliation{European Southern Observatory, Karl-Schwarzschild-Stra{\ss}e 2, 85748 Garching bei M\"{u}nchen, Germany}
+\affiliation{\afesomunich}
 
@@
 \author{J. King}
-\affiliation{Max-Planck-Institut f\"ur Kernphysik, PO Box 103980, 69029 Heidelberg, Germany}
+\affiliation{\afmpik}
 
@@
 \author[0000-0001-7221-855X]{S. P. Littlefair}
-\affiliation{Dept of Physics \& Astronomy, University of Sheffield, Sheffield, S3 7RH, UK}
+\affiliation{Department of Physics \& Astronomy, University of Sheffield, Sheffield, S3 7RH, UK}
 
@@
 \author[0000-0002-1395-8694]{D. M. Macleod}
-\affiliation{}
+\affiliation{Cardiff University, Cardiff CF24 3AA, UK}
 
@@
 \author[0000-0001-5807-7893]{C. McCully}
-\affiliation{Las Cumbres Observatory, 6740 Cortona Drive, Suite 102, Goleta, CA 93117-5575, USA; Department of Physics, University of California, Santa Barbara, CA 93106-9530, USA}
+\affiliation{\aflco}
+\affiliation{\afucsb}
 
@@
 \author[0000-0003-2528-3409]{B. M. Morris}
-\affiliation{Astronomy Department, University of Washington, Seattle, WA 98195, USA}
+\affiliation{\afuw}
 
 \author[0000-0003-4217-4642]{S. J. Mumford}
-\affiliation{SP$^{2}$RC, School of Mathematics and Statistics, The University of Sheffield U.K.}
+\affiliation{SP$^{2}$RC, School of Mathematics and Statistics, The University of Sheffield, U.K.}
 
@@
 \author[0000-0001-6628-8033]{N. A. Murphy}
-\affiliation{Harvard-Smithsonian Center for Astrophysics, 60 Garden St, Cambridge, MA 02138, USA}
+\affiliation{\afcfa}
 
 \author{S. Nelson}
-\affiliation{Minnesota State University Moorhead, 1104 7th Avenue South Moorhead, MN 56563, United States}
+\affiliation{\afminnstate}
 
@@
 \author[0000-0001-8720-5612]{J. P. Ninan}
-\affiliation{The Pennsylvania State University, University Park, PA, USA}
+\affiliation{\afpennstate}
 
@@
 \author{S. Ogaz}
-\affiliation{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
+\affiliation{\afstsci}
 
 \author[0000-0001-7790-5308]{S. Oh}
-\affiliation{Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08544, USA}
+\affiliation{\afprinceton}
 
 \author{J. K. Parejko}
-\affiliation{Department of Astronomy, University of Washington, Box 351580, Seattle, WA 98195, USA}
+\affiliation{\afuw}
 
@@
 \author{L. E. Sherbert}
-\affiliation{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
+\affiliation{\afstsci}
 
@@
 \author{A. Y. Shih}
-\affiliation{NASA Goddard Space Flight Center, 8800 Greenbelt Road, Greenbelt, MD 20771, USA}
+\affiliation{\afgoddard}
 
@@
 \author[0000-0001-9898-5597]{L. P. Singer}
-\affiliation{Astroparticle Physics Laboratory, NASA Goddard Space Flight Center, Code 661, 8800 Greenbelt Rd., Greenbelt, MD 20771, USA}
+\affiliation{Astroparticle Physics Laboratory, \afgoddard}
 
@@
 \author{S. W. Thomas}
-\affiliation{Institute of Astronomy, University of Cambridge, Cambridge CB3 0HA, UK}
+\affiliation{\afioa}
 
 \author{J. E. H. Turner}
-\affiliation{Gemini Observatory, Casilla 603, La Serena, Chile}
+\affiliation{\afgemini}
 
@@
 \author[0000-0002-6219-5558]{A. de la Vega}
-\affiliation{Department of Physics and Astronomy, Johns Hopkins University, 3400 N Charles Street, Baltimore, MD 21218}
+\affiliation{\afjhu}
 
 \author[0000-0002-1343-134X]{L. L. Watkins}
-\affiliation{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
+\affiliation{\afstsci}
 
@@
 \author[0000-0002-2958-4738]{J. Woillez}
-\affiliation{European Southern Observatory - Karl-Schwarzschild-Str. 2, Garching bei München, D-85748, Germany}
+\affiliation{\afesomunich}
 

### 2017-12-16 main.tex
replace empty affiliation with noaffiliation
Add more intro to table subpackage description and streamline presentation
I;ve added a mention of numpy ans pandas as inspiration for the table
subpackage. Table is not now, and more details can be found in paper 1,
so I think a short mention is enough at this point. I've also removed
intermediate headings, since table is already a subsubsection.

closes #31

--- 2017-12-14 main.tex
@@
 
-\author{Astropy Project}
-\footnote{The author list has three parts: the 13 authors that were primary authors of  sections of the paper in order of contribution, the four members of the \astropy Project coordination committee, and contributions to the \astropy Project in alphabetical order.
-The position in the author list does not correspond to contributions to the \astropy Project as a whole.
-A more complete list of contributors to the core package can be found in the \href{https://github.com/astropy/astropy/graphs/contributors}{package repository}, and at the \href{http://www.astropy.org/team.html}{\astropy team webpage}.}
-
-\input{author.tex}
+\author{Astropy Collaboration}
 
@@
 
-The \package{astropy.table} subpackage provides functionality for representing
-and manipulating heterogeneous data.
-The package was described in detail in \cite{astropy}.
-Thus, in what follows, we only summarize key new features or updates to
-\package{astropy.table} since the previous \astropy paper.
-
-\subsubsection{Support for grouped table operations}
+The \package{astropy.table} subpackage provides functionality for
+representing and manipulating heterogeneous data. In some respects,
+this is similar to \package{numpy} record arrays \citep{numpy} or
+\package{pandas} dataframes \citep{pandas} but with modifications for
+astronomical data. Most notably, tables from \package{astropy.table}
+allow for table or column metadata and can handle
+vectors or arrays as table entries.
+The package was described in
+detail in \cite{astropy}.  Thus, in what follows, we only summarize
+key new features or updates to \package{astropy.table} since the
+previous \astropy paper. These are support for grouped table
+operations, table concatnation, and using array-valued
+\package{astropy} objects as table columns.
 
@@
 
-\subsubsection{Support for table concatenation}
-
 \texttt{Table} objects can now be combined in several different ways. If two
@@
 
-\subsubsection{Using Astropy objects in tables}
-
-The \texttt{Table} object now allows \texttt{Quantity}, celestial
+The \texttt{Table} object now allows array-valued \texttt{Quantity}, celestial
 coordinate (\texttt{SkyCoord}), and date/time (\texttt{Time}) objects to
 be used as columns. It also provides a general way for other user-defined
-objects to be used as columns. This makes it possible, for instance, to easily
+array-like objects to be used as columns.
+This makes it possible, for instance, to easily
 represent catalogs of sources or time series in \astropy, while having both the
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{ngc6977.png}
+\includegraphics[width=\textwidth]{ngc6977}
 \caption{An RGB color image of the region near the Hickson 88 group

### 2017-12-19 main.tex

@@
 
-\author{Astropy Collaboration}
+\author{Astropy Project}
+\noaffiliation
+\footnote{The author list has three parts: the 13 authors that made significant contributions to the  writing of the paper in order of contribution, the four members of the \astropy Project coordination committee, and contributions to the \astropy Project in alphabetical order.
+The position in the author list does not correspond to contributions to the \astropy Project as a whole.
+A more complete list of contributors to the core package can be found in the \href{https://github.com/astropy/astropy/graphs/contributors}{package repository}, and at the \href{http://www.astropy.org/team.html}{\astropy team webpage}.}
+
+\input{author.tex}
 
@@
 vectors or arrays as table entries.
-The package was described in
+The subpackage was described in
 detail in \cite{astropy}.  Thus, in what follows, we only summarize

### 2018-01-04 main.tex

@@
 previous \astropy paper. These are support for grouped table
-operations, table concatnation, and using array-valued
+operations, table concatenation, and using array-valued
 \package{astropy} objects as table columns.
@@
 
+We would like to thank the members of the community that have 
+contributed to \astropy, 
+that have opened issues and provided feedback, and have supported the 
+project in a number of different ways.  We would like to acknowledge
+Alex Conley and Neil Crighton for maintaining the  \package{cosmology} 
+package. 
+%insert significant contributors to astropy who have decided not to 
+%be co-authors
+
 The \astropy community is supported by and makes use
@@
 their staff can contribute their time to the development of
-\astropy projects.
+\astropy projects.  We would like acknowledge the support of the 
+Space Telescope Science Institute, Harvard–Smithsonian Center for Astrophysics, 
+and the South African Astronomical Observatory.
+
+The following individuals would like to recognize support for their personal contributions.
+HMG was supported by the National Aeronautics and Space Administration through the 
+Smithsonian Astrophysical Observatory contract SV3-73016 to MIT for Support of the Chandra X-Ray Center, which is
+operated by the Smithsonian Astrophysical Observatory for and on behalf of the National Aeronautics Space 
+Administration under contract NAS8-03060. JTV was supported by the UW eScience Institute, via grants from the Moore
+Foundation, the Sloan Foundation, and the Washington Research Foundation. SMC acknowledges the National Research
+Foundation of South Africa. TLA was supported by NASA contract NAS8-03060. Support for E.J.T. was provided by NASA
+through Hubble Fellowship grant No. 51316.01 awarded by the Space Telescope Science Institute, which is operated by
+the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS 5-26555, as well as a 
+Giacconi Fellowship. MB was supported by the FONDECYT regular project 1170618 and the MINEDUC-UA projects codes 
+ANT 1655 and ANT 1656. DH was supported through the SFB 881 "The Milkyway System" by the German Research Foundation 
+(DFG). WEK was supported by an ESO Fellowship. C.M. is supported by NSF grant AST-1313484. SP was supported by 
+grant AYA2016-75808-R (FEDER) issued by the Spanish government. JEHT was supported by the Gemini Observatory, which
+is operated by the Association of Universities for Research in Astronomy, Inc., on behalf of the international 
+Gemini partnership of Argentina, Brazil, Canada, Chile, and the United States of America.
 

### 2018-01-04 main.tex
update of the title
fixed cosmology subpackage

@@
 
-The \package{cosmology} package contains classes for representing different
+The \package{cosmology} subpackage contains classes for representing different
 cosmologies and functions for calculating commonly used quantities such as
-look-back time and distance.   The package was described in detail in
+look-back time and distance.   The subpackage was described in detail in
 \cite{astropy}.  The default cosmology in \astropypkg version 2.0 is given by
@@
 Alex Conley and Neil Crighton for maintaining the  \package{cosmology} 
-package. 
+subpackage. 
 %insert significant contributors to astropy who have decided not to 

### 2018-01-04 author.tex
replace empty affiliation with noaffiliation
Postal code University of Toronto
I seem to have initially added that of my home. SIgh...

@@
 
-\collaboration{Primary paper contributors:}
-
 \author[0000-0003-0872-7098]{A. M. Price-Whelan}
@@
 \author[0000-0002-3713-6337]{B. M. Sip\H{o}cz}
-\affiliation{}
+\noaffiliation
 
@@
 
-\collaboration{Astropy coordination committee:}
+\collaboration{(primary paper contributors)}
 
@@
 
-\collaboration{Astropy contributors:}
+\collaboration{(Astropy coordination committee)}
 
@@
 \author{A. V. Bakanov}
-\affiliation{}
+\noaffiliation
 
@@
 \author{K. L. Berry}
-\affiliation{}
+\noaffiliation
 
@@
 \author{E. M. Bray}
-\affiliation{}
+\noaffiliation
 
@@
 \author[0000-0002-5317-7518]{Y. Copin}
-\affiliation{CNRS/IN2P3, Institut de Physique Nucleaire de Lyon, Universite de Lyon, Universite de Lyon 1, Villeurbanne, F-69622, Lyon, France}
+\affiliation{Universit\'e de Lyon, F-69622, Lyon, France; Universit\'e de Lyon 1, Villeurbanne; CNRS/IN2P3, Institut de Physique Nucl\'eaire de Lyon}
 
@@
 
+\author{M. Droettboom}
+\affiliation{\afstsci}
+
 \author{T. Erben}
@@
 \author{T. Finethy}
-\affiliation{}
+\noaffiliation
 
 \author[0000-0003-4291-1091]{R. T. Fox}
-\affiliation{}
+\noaffiliation
 
@@
 \author{F. Grollier}
-\affiliation{}
+\noaffiliation
 
@@
 \author{A. Khvalko}
-\affiliation{}
+\noaffiliation
 
@@
 \author{R. Patil}
-\affiliation{}
+\noaffiliation
 
@@
 
+\author{J. X. Prochaska}
+\affiliation{Astronomy \& Astrophysics, UC Santa Cruz, 1156 High St., Santa Cruz, CA 95064 USA}
+
 \author{T. Rastogi}
-\affiliation{}
+\noaffiliation
 
@@
 \author{M. Seifert}
-\affiliation{}
+\noaffiliation
 
@@
 \author[0000-0003-0477-6220]{H. Sherwood-Taylor}
-\affiliation{}
+\noaffiliation
 
@@
 \author{M. T. Silbiger}
-\affiliation{}
+\noaffiliation
 
@@
 \author{K. A. Sooley}
-\affiliation{}
+\noaffiliation
 
 \author{S. Sornarajah}
-\affiliation{}
+\noaffiliation
 
@@
 \author[0000-0002-5830-8505]{M. H. van Kerkwijk}
-\affiliation{Department of Astronomy \& Astrophysics, University of Toronto, 50 Saint George Street, Toronto, ON M5R 3B3, Canada}
+\affiliation{Department of Astronomy \& Astrophysics, University of Toronto, 50 Saint George Street, Toronto, ON M5S 3H4, Canada}
 
@@
 
-\author{J. Xavier Prochaska}
-\affiliation{Astronomy \& Astrophysics, UC Santa Cruz, 1156 High St., Santa Cruz, CA 95064 USA}
+\author[0000-0003-2638-7648]{V. Zabalza}
+\noaffiliation
 
-\author[0000-0003-2638-7648]{V. Zabalza}
-\affiliation{}
+\collaboration{(Astropy contributors)}

### 2018-01-05 main.tex
correct plural disagreement

@@
 
-\title{The Astropy Project}
+\title{The Astropy Project: Building an inclusive, open science project and status of the v2.0 software}
 
@@
 Pull requests that modify or add code to a specific subpackage must be reviewed
-and approved by one of the subpackage maintainers before it is merged into the
-core codebase.
+and approved by one of the subpackage maintainers before they are merged into
+the core codebase.
 Bugs and feature requests are reported via the \github issue tracker and labeled

### 2018-01-05 main.tex
nix 3x use of 'different' in same sentence
minor grammar

@@
 contribute to the project.
-This model leads to an ``organic'' growth, where different features are
+This model leads to an ``organic'' growth, where features are
 implemented by different people with different programming styles and
@@
 with no changes to the API\@.
-The LTS versions are ideal for pipelines and other applications, where API
+The LTS versions are ideal for pipelines and other applications in which API
 stability is essential.

### 2018-01-05 main.tex
increased -> improved

@@
 subpackages are available in the documentation.\footnote{\url{http://docs.astropy.org/en/stable/}}
-Beyond what is mentioned below, most subpackages have seen increased performance
+Beyond what is mentioned below, most subpackages have seen improved performance
 since the release of the version 0.2 package.

### 2018-01-05 main.tex
rephrased parenthetical
doesn't -> does not (journals don't like such contractions?)

@@
 units can be directly passed in to the trigonometric functions implemented in
-\texttt{numpy}. The units are internally converted to radians (what the \texttt{numpy}
-trigonometric functions expect) before being passed to \texttt{numpy}.
+\texttt{numpy}. The units are internally converted to radians, which is what
+the \texttt{numpy} trigonometric functions expect, before being passed to
+\texttt{numpy}.
 
@@
 
-The typical user doesn't usually have to interact with the \texttt{Frame} or
+The typical user does not usually have to interact with the \texttt{Frame} or
 \texttt{Representation} classes directly.

### 2018-01-05 main.tex
remove "see the next point", because the next point is unrelated.  If there is something else supporting the experimental transformation of velocity data, it would be helpful to reference its section directly

@@
     transformations are done numerically instead of analytically.
-    The low-level interface for specifying and transforming velocity data (see
-    the next point) is currently experimental.
-    As such, in version 2.0, only the \texttt{Frame} classes (and not the
-    \texttt{SkyCoord} class) support handling velocities.
+    The low-level interface for specifying and transforming velocity data  is
+    currently experimental.  As such, in version 2.0, only the \texttt{Frame}
+    classes (and not the \texttt{SkyCoord} class) support handling velocities.
 

### 2018-01-05 main.tex
try to clarify and specify what 'lazy loading' means in terms of FITS files.  I wasn't 100% sure here whether this is referring specifically to lazy loading of all HDUs or lazy loading of all data *in* HDUs - if someone can clarify this further, it would be helpful.

@@
 
-FITS files are now loaded \emph{lazily} (this default behavior can be
-deactivated, if needed), where all HDUs are not loaded until
-requested. This should provide substantial speed-ups when using the
-convenience functions (e.g., \texttt{getheader()} or \texttt{getdata()}) to
-get an HDU that is near the beginning in a file with many HDUs.
+FITS files are now loaded \emph{lazily} by default, i.e., an object
+representing the list of HDUs is created but the data are not loaded into
+memory until requested.  This approach should provide substantial speed-ups
+when using the convenience functions (e.g., \texttt{getheader()} or
+\texttt{getdata()}) to get an HDU that is near the beginning in a file with
+many HDUs.
 

### 2018-01-05 main.tex
word order
add missing word, build->built

@@
 values and constraints can be updated by assignment. Supported constraints include \texttt{fixed},
-and \texttt{tied} parameters, and \texttt{bounds} on parameter values. The framework supports also models
+and \texttt{tied} parameters, and \texttt{bounds} on parameter values. The framework also supports models
 for which the number of parameters and their names are defined by another argument.
@@
 \subsubsection{Creating New Models}
-If arithmetic combinations of existing models is not sufficient, new model classes can be defined in different ways.
-The \package{astropy.modeling} provides tools to turn a simple function into a full-featured model, but it also allows extending the build-in model class with arbitrary code.
+If arithmetic combinations of existing models is not sufficient, new model
+classes can be defined in different ways. The \package{astropy.modeling}
+package provides tools to turn a simple function into a full-featured model,
+but it also allows extending the built-in model class with arbitrary code.
 

### 2018-01-05 main.tex
rephrased Blackbody model to be more stylistically consistent w/other text

@@
 
-The \package{astropy.modeling} subpackage now supports the representation, evaluation, and fitting of models using \texttt{Quantity} objects, which attach units to scalar values or arrays of values.
-In practice, this means that one can, for example, fit a model to data with units and get parameters that also have units out, or initialize a model with parameters with units and evaluate it using input values with different but equivalent units.
-Using this, we have implemented a blackbody model (\texttt{BlackBody1D}) that can be used to fit observed flux densities in a variety of units and as a function of different units of spectral coordinates (e.g., wavelength or frequency).
+The \package{astropy.modeling} subpackage now supports the representation,
+evaluation, and fitting of models using \texttt{Quantity} objects, which attach
+units to scalar values or arrays of values. In practice, this means that one
+can, for example, fit a model to data with units and get parameters that also
+have units out, or initialize a model with parameters with units and evaluate
+it using input values with different but equivalent units. For example, the
+blackbody model (\texttt{BlackBody1D}) can be used to fit observed flux
+densities in a variety of units and as a function of different units of
+spectral coordinates (e.g., wavelength or frequency).
 

### 2018-01-05 main.tex
; -> .

@@
 An example of a visualization made with \package{wcsaxes} is shown in
-\figurename~\ref{fig:wcsaxes}; This example illustrates the ability to
+\figurename~\ref{fig:wcsaxes}. This example illustrates the ability to
 overlay multiple coordinate systems and customize which ticks/labels are shown

### 2018-01-05 main.tex
rephrase
empower -> enable

@@
 are implemented in \package{astropy.stats}.  These functions provide
-measurements of the circular mean, variance, and moment.   For all of these
-functions, they work with both \texttt{numpy.ndarrays} (assumed to be in
-radians) and \texttt{Quantity} objects.  In addition, the subpackage includes
+measurements of the circular mean, variance, and moment.   All of these
+functions work with both \texttt{numpy.ndarrays} (assumed to be in radians) and
+\texttt{Quantity} objects.  In addition, the subpackage includes
 tests for Rayleigh Test, \texttt{vtest}, and a function to compute the maximum
@@
 \package{astropy/ci-helpers}.\footnote{\url{https://github.com/astropy/ci-helpers}}
-These tools aim to empower package maintainers to control their testing setup
+These tools aim to enable package maintainers to control their testing setup
 and installation process for various CI services through a

### 2018-01-05 main.tex
; -> .
'major fraction' -> 'substantial fraction'

@@
         underlying astronomical concepts.
-        These are less specific and more conceptual than tutorials;
+        These are less specific and more conceptual than tutorials.
         For example, ``using \astropypkg and \package{ccdproc} to reduce imaging
@@
 This is important as most practicing astronomers were not explicitly taught
-computer science and software development, despite the fact that a major
+computer science and software development, despite the fact that a substantial
 fraction of many astronomers' workload today is related to software use

### 2018-01-05 main.tex
at least one member [however, the parenthetical is now awkward; consider removing it?]

@@
 Within \astropy, all submitted code is reviewed by at least one, but typically
-more, members of the \astropy community, who provide feedback to contributors,
+more, member of the \astropy community, who provide feedback to contributors,
 which helps to improve their skills.

### 2018-01-05 main.tex
make "skills" less generic

@@
 more, member of the \astropy community, who provide feedback to contributors,
-which helps to improve their skills.
+which helps to improve their software development skills.
 As a community, \astropy follows an explicit code of conduct \citep{ape8} and treats all

### 2018-01-05 author.tex
Add ORCID number
Comma and space before zip code

@@
 
-\author{T. Babej}
+\author[0000-0002-8222-3595]{T. Babej}
 \affiliation{Department of Theoretical Physics \& Astrophysics, Masaryk University, Kotlarska 2, 61137 Brno, Czech Republic}
@@
 \author[0000-0002-8134-9591]{J. P. Dietrich}
-\affiliation{Faculty of Physics, Ludwig-Maximilians-Universit\"at, Scheinerstr. 181679 Munich, Germany}
+\affiliation{Faculty of Physics, Ludwig-Maximilians-Universit\"at, Scheinerstr. 1, 81679 Munich, Germany}
 \affiliation{Excellence Cluster Universe, Boltzmannstr. 2, 85748 Garching b. M\"unchen, Germany}
@@
 \author[0000-0002-6324-5713]{M. Mastropietro}
-\affiliation{Department Physics and Astronomy, Ghent University, Krijgslaan 281, S9, B-9000 Gent, Belgium}
+\affiliation{Department of Physics and Astronomy, Ghent University, Krijgslaan 281, S9, B-9000 Gent, Belgium}
 
@@
 \author{M. N{\"o}the}
-\affiliation{TU Dortmund, Experimental Physics 5, Otto-Hahn-Str. 4, 44221 Dortmund, Germany}
+\affiliation{Experimental Physics 5, TU Dortmund, Otto-Hahn-Str. 4, 44227 Dortmund, Germany}
 

### 2018-01-06 registry.tex
Add poliastro citation

@@
 \href{http://github.com/astropy/photutils.git}{photutils} & No & \href{https://pypi.python.org/pypi/photutils}{photutils} & Larry Bradley and Brigitta Sipocz & \citealt{photutils} \\
-\href{https://github.com/poliastro/poliastro}{poliastro} & No & \href{https://pypi.python.org/pypi/poliastro}{poliastro} & Juan Luis Cano Rodríguez &  \\
+\href{https://github.com/poliastro/poliastro}{poliastro} & No & \href{https://pypi.python.org/pypi/poliastro}{poliastro} & Juan Luis Cano Rodríguez & \citealt{poliastro} \\
 \href{http://github.com/weaverba137/pydl.git}{PyDL} & No & \href{https://pypi.python.org/pypi/pydl}{pydl} & Benjamin Alan Weaver & \citealt{pydl} \\

### 2018-01-07 author.tex
s/Víctor Terrón/V. Terrón — like the other authors
Also, include the city in the affiliation.
Add ORCID number

@@
 
-\author{S. Conseil}
+\author[0000-0002-3657-4191]{S. Conseil}
 \affiliation{Univ Lyon, Univ Lyon1, Ens de Lyon, CNRS, Centre de Recherche Astrophysique de Lyon UMR5574, F-69230, Saint-Genis-Laval, France}
@@
 \author[0000-0001-5982-167X]{T. Jenness}
-\affiliation{Large Synoptic Survey Telescope, 950 N Cherry Ave, Tucson, AZ, 85719}
+\affiliation{Large Synoptic Survey Telescope, 950 N. Cherry Ave., Tucson, AZ, 85719, USA}
 
@@
 \affiliation{Astroparticle Physics Laboratory, \afgoddard}
+\affiliation{Joint Space-Science Institute, University of Maryland, College Park, MD 20742, USA}
 
@@
 
-\author{V\'{i}ctor Terr\'{o}n}
-\affiliation{Institute of Astrophysics of Andalusia (IAA-CSIC), Spain}
+\author{V. Terr\'{o}n}
+\affiliation{Institute of Astrophysics of Andalusia (IAA-CSIC), Granada, Spain}
 
@@
 \author{B. A. Weaver}
-\affiliation{National Optical Astronomy Observatory, 950 N. Cherry Ave., Tucson, AZ 85719}
+\affiliation{National Optical Astronomy Observatory, 950 N. Cherry Ave., Tucson, AZ 85719, USA}
 

### 2018-01-08 author.tex
Normalise Heidelberg postal addresses

@@
 \author{F. Biscani}
-\affiliation{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg, Germany}
+\affiliation{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, 69117 Heidelberg, Germany}
 
@@
 \author[0000-0002-8546-9128]{D. Homeier}
-\affiliation{Zentrum f{\"u}r Astronomie der Universit{\"a}t Heidelberg, Landessternwarte, K{\"o}nigstuhl 12, D-69117 Heidelberg, Germany}
+\affiliation{Zentrum f{\"u}r Astronomie der Universit{\"a}t Heidelberg, Landessternwarte, K{\"o}nigstuhl 12, 69117 Heidelberg, Germany}
 
@@
 \author[0000-0003-1585-225X]{P. H. Sladen}
-\affiliation{ARI/ZAH, Heidelberg}
+\affiliation{Zentrum f{\"u}r Astronomie der Universit{\"a}t Heidelberg, Astronomisches Rechen-Institut, M{\"o}nchhofstra{\ss}e 12--14, 69120 Heidelberg, Germany}
 

### 2018-01-08 main.tex
Fixed typo in io.ascii section
tweak convolution legend to avoid greengrocer's apostrophe

@@
 the speed of the \package{pandas} \citep{pandas} ASCII file interface.  The
-fast reader has parallel processing option that allows harnessing multiple
+fast reader has a parallel processing option that allows harnessing multiple
 cores for input parsing to achieve even greater speed gains.  By default,
@@
     An example showing different modes of convolution available in the \python
-    ecosystem.  The red x's mark pixels that are set to \texttt{NaN} in the
+    ecosystem.  Each red $x$ signifies a pixel that is set to \texttt{NaN} in the
     original data (a).  If the data are convolved with a Gaussian kernel on a

### 2018-01-08 main.tex
Fixed typo in DH acknowledgements

@@
 \section{Introduction} \label{sec:intro}
-All astronomical research makes use of software in some way.
+All modern astronomical research makes use of software in some way.
 Astronomy as a field has thus long supported the development of software tools
@@
     An example showing different modes of convolution available in the \python
-    ecosystem.  Each red $x$ signifies a pixel that is set to \texttt{NaN} in the
+    ecosystem.  The red x's mark pixels that are set to \texttt{NaN} in the
     original data (a).  If the data are convolved with a Gaussian kernel on a

### 2018-01-08 author.tex
add additional affiliation + orcid link

@@
 \newcommand{\afberkeleyastro}{Department of Astronomy, UC Berkeley, 501 Campbell Hall \#3411, Berkeley, CA 94720, USA}
+\newcommand{\afuct}{Department of Astronomy, University of Cape Town, Private Bag X3, Rondebosch 7701, South Africa}
 
@@
 
-\author{H. Breytenbach}
+\author[0000-0001-5391-2386]{H. Breytenbach}
 \affiliation{\afsaao}
+\affiliation{\afuct}
 
@@
 \affiliation{Istituto Nazionale di Astrofisica, via Tiepolo 11 Trieste, Italy}
+
+\author[0000-0002-2187-161X]{J. L. Cano Rodríguez}
+\noaffiliation
 
@@
 
+\author[0000-0003-1714-7415]{N. Earl}
+\affiliation{\afstsci}
+
 \author{T. Erben}
 \affiliation{Argelander-Institut f\"ur Astronomie, Auf dem H\"ugel 71, 53121 Bonn, Germany}
+
+\author{S. Fabbro}
+\affil{National Research Council Herzberg Astronomy \& Astrophysics, 4071 West Saanich Road, Victoria, BC}
 
@@
 
+\author{M. Mueller}
+\affil{Brown University/Department of Mathematics, 151 Thayer Street, Providence, RI 02912, USA}
+
 \author[0000-0003-4217-4642]{S. J. Mumford}
@@
 
+\author[0000-0003-3001-676X]{J. Sick}
+\affil{AURA/LSST, 950 N Cherry Ave, Tucson, 85719}
+
 \author{M. T. Silbiger}
@@
 \affiliation{\afioa}
+
+\author[0000-0002-5445-5401]{G. R. Tremblay}
+\affiliation{{\afcfa}
 

### 2018-01-08 main.tex
edits to the introduction

@@
 pipelines for survey operations.
-Some software packages are or were supported by large institutions and are
+Some software packages are, or were, supported by large institutions and are
 intended for a wide range of users.
@@
 The \astropy project has grown to become this community for \python astronomy
-software, and the \astropypkg core package a feature-rich \python library.
+software, and the \astropypkg core package is a feature-rich \python library.
 
@@
 software in \python.
-In this way, its genesis differs from but builds upon many substantial and
+In this way, its genesis differs from, but builds upon, many substantial and
 former astronomical software development efforts that were commissioned or
@@
 \python\footnote{\url{https://www.python.org/}} is an increasingly popular, general-purpose
-programming language that is available under a permissive open source software license free of
+programming language that is available under a permissive open source software license and is free of
 charge for all major operating systems. The programming language has become especially popular
@@
 as Anaconda\footnote{\url{https://anaconda.org/}} has significantly streamlined
-the installation process for many libraries, lowering many barriers to entry.
+the installation process for many libraries, lowering the barriers to entry.
 
@@
 (\sectionname~\ref{sec:core}) and several separate packages that help maintain
-the infrastructure for, e.g., testing and documentation
+the infrastructure for testing and documentation
 (\sectionname~\ref{sec:infrastructure}). We end with a short vision for

### 2018-01-08 main.tex
added link to repository with paper
added links to CI section and edits

@@
 \begin{abstract}
-% I (Adrian) took a first stab at the abstract, but it needs some work. Feel
-% free to modify!
 The \astropy project supports and fosters the development of open-source and openly-developed
@@
 
-% Adrian PW: how are there still no software keywords in AAS journals?!?
 \keywords{%
@@
 the future of \astropy and astronomical software in general in
-\sectionname~\ref{sec:future}.
+\sectionname~\ref{sec:future}. The full paper, including the code
+to produce the figures, is available in a \github 
+repository\footnote{\url{https://github.com/astropy/astropy-v2.0-paper}}
 
@@
 \subsection{Coordination of Astropy}
-% draft by ?? (BMS thinks Erik)
-% edited by Adrian PW
 \label{sect:coordcom}
@@
 \subsection{Astropy development model}
-% draft by Adrian PW and Erik T.
+
 Code is contributed to the \astropypkg core package or modified through ``pull
-requests'' (via \github) that often contain several \texttt{git} commits.
+requests'' (via \github\footnote{\url{https://github.com/astropy/astropy/}}) 
+that often contain several \texttt{git} commits.
 Pull requests may fix bugs, implement new features, or improve or modify the
@@
 \subsection{APEs - Astropy Proposals for Enhancement}
-% draft by hamogu
-% edited by Adrian PW
 
@@
 \subsection{Concept of affiliated packages}
-% it may be described in previous subsection, if not the Brigitta can try to
-% write it up
-% edited by Adrian PW
 
@@
 New functionality benefits from having a rapid development and release cycle that is not tied to that of the \astropypkg core (\sectionname~\ref{sect:releasecycle}).
-% AG: rephrased this.
-%Initially separate packages with typically rapid initial development and new experimental features benefit from having a release cycle that is not tied to the
 
@@
 
-%\subsection{Accuracy testing across many different implementation}
-
 \subsection{Release cycle and Long Term Support}
 \label{sect:releasecycle}
-% This could also include information about the development cycle
-% Brigitta can writes this up if there's no other taker
-% edited by Adrian PW
 
@@
 all platforms; the package is constantly tested on different platforms as part
-of a suite of continuous integration (CI) tests.
+of a suite of continuous integration tests.
 
@@
 \label{sec:core}
-% Adrian
 The \astropy project aims to provide \python-based packages for all tasks that
@@
 \subsection{Units}\label{sec:units}
-% Adrian
 
@@
 \subsection{Constants}
-% David S.
-% Edited by Adrian PW
 
@@
 \label{sec:coordinates}
-% Adrian, Erik
 The \package{astropy.coordinates} subpackage is designed to support representing
@@
 \label{sec:time}
-% Adrian PW
 
@@
 \label{sec:table}
-% fleshed out / edited by Adrian PW
 
@@
 \subsection{\package{io}}
-% Simon
 
@@
 \label{sec:modeling}
-% The whole modeling submodule was missing from the previous paper, so everything really, including compound models, unit support etc.
-% Nadia, Lim
-% Tom R. -- unit support
 
@@
 \subsection{Convolution}
-% Adam G.
 
@@
 \subsection{Visualization}
-% Larry:  Image visualization (stretching, scaling), RGB
 
@@
 
-%\subsection{Utils}
-% Lim
-
 \subsection{Cosmology}
@@
 \subsection{Statistics}
-% Edited by Adrian PW
 
@@
 a still growing collection of useful features.
-
-% Steve C.: overview, circular stats,
-% Jake V.:  Lomb-scargle, Bayesian blocks
-% Larry:  sigma clipping, biweight stats
-% Ze':  Ripley's K (spatial stats)
 
@@
 \label{sec:infrastructure}
-% Text also edited by Adrian PW
 
@@
 \subsection{Package template}
-% Brigitta may write this up if there is no other takers
 
@@
 \subsection{Continuous integration helpers}
-% Brigitta
 
 \astropy also provides a set of scripts for setting up and configuring
-CI services as a \github repository,
+continuous integration (CI) services as a \github repository,
 \package{astropy/ci-helpers}.\footnote{\url{https://github.com/astropy/ci-helpers}}
@@
 ecosystem, the actual usage of this package is extremely widespread. The current
-tools support configuration for Travis CI and Appveyor CI.
+tools support configuration for Travis CI\footnote{\url{https://travis-ci.org/}} and 
+Appveyor CI\footnote{\url{https://www.appveyor.com/}}.
 
@@
 \label{sec:future}
-% First draft by SMC
-% edited by BMS
-% edited again by Adrian PW
 
@@
 \subsection{Learn Astropy}
-% Adrian
 
@@
 \label{sec:conclusion}
-% Renamed and edited by Adrian PW
 
@@
 subpackage.
-%insert significant contributors to astropy who have decided not to 
-%be co-authors
 

### 2018-01-08 main.tex
Added some clarifications on io.ascii compression support and fast reader capabilities

--- 2018-01-08 main.tex
@@
 \section{Introduction} \label{sec:intro}
-All modern astronomical research makes use of software in some way.
+All astronomical research makes use of software in some way.
 Astronomy as a field has thus long supported the development of software tools
@@
 reduces the need to master the separate details of all the I/O packages within
-\astropypkg.
+\astropypkg. The file interface allows transparent compression of
+the \texttt{gzip}, \texttt{bzip2} and \texttt{lzma} (\texttt{.xz})
+formats; for the latter two if the Python installation was compiled
+with support the respective libraries.
 
@@
 Cython/C engine for reading and writing ASCII files. This is available for most
-of the common formats.  On average, the new engine is about 4 to 5 times faster
+of the common formats. It also offers some additional features like parsing
+of different exponential notation styles, such as commonly produced
+by Fortran programs.  On average, the new engine is about 4 to 5 times faster
 than the corresponding pure-\python implementation and is often comparable to
 the speed of the \package{pandas} \citep{pandas} ASCII file interface.  The
-fast reader has a parallel processing option that allows harnessing multiple
+fast reader has parallel processing option that allows harnessing multiple
 cores for input parsing to achieve even greater speed gains.  By default,
@@
 / write interface are unavailable in the fast version, in which case the
-pure-\python version will automatically be used.
+reader will by default fall back automatically to the pure-\python version.
 
@@
 Giacconi Fellowship. MB was supported by the FONDECYT regular project 1170618 and the MINEDUC-UA projects codes 
-ANT 1655 and ANT 1656. DH was supported through the SFB 881 "The Milkyway System" by the German Research Foundation 
+ANT 1655 and ANT 1656. DH was supported through the SFB 881 ``The
+Milky Way System'' by the German Research Foundation 
 (DFG). WEK was supported by an ESO Fellowship. C.M. is supported by NSF grant AST-1313484. SP was supported by 

### 2018-01-08 main.tex

--- 2018-01-08 main.tex
@@
 Cython/C engine for reading and writing ASCII files. This is available for most
-of the common formats.  On average, the new engine is about 4 to 5 times faster
+of the common formats. It also offers some additional features like parsing
+of different exponential notation styles, such as commonly produced
+by Fortran programs.  On average, the new engine is about 4 to 5 times faster
 than the corresponding pure-\python implementation and is often comparable to

### 2018-01-08 main.tex
Added brief description of HDF5 I/O

--- 2018-01-08 main.tex
@@
 many HDUs.
+
+\subsubsection{HDF5}
+
+The \package{astropy.io.misc.hdf5} subpackage provides support for binary
+read and write access to files in the \emph{Hierarchical Data Format}
+(HDF5), if the \package{h5py} package is installed. Astropy table I/O
+is offered transparently through \texttt{Table.read()} and
+\texttt{Table.write()}, analogously to the other auto-detected
+formats. The keyword \texttt{path='group/subgroup/dataset'} specifies
+the path to the data inside the file's hierarchical structure.
 

### 2018-01-08 main.tex

--- 2018-01-08 main.tex
@@
 data to a variety of ASCII and binary file formats, such as a wide range of
-ASCII data table formats, FITS, and VOTable.
+ASCII data table formats, FITS, HDF5, and VOTable.
 It also provides a unified interface for reading and writing data with these

### 2018-01-08 main.tex
small tweaks to authors footnote

@@
 \noaffiliation
-\footnote{The author list has three parts: the 13 authors that made significant contributions to the  writing of the paper in order of contribution, the four members of the \astropy Project coordination committee, and contributions to the \astropy Project in alphabetical order.
+{\let\thefootnote\relax\footnote{{The author list has three parts: the authors that made significant contributions to the writing of the paper in order of contribution, the four members of the \astropy Project coordination committee, and contributors to the \astropy Project in alphabetical order.
 The position in the author list does not correspond to contributions to the \astropy Project as a whole.
-A more complete list of contributors to the core package can be found in the \href{https://github.com/astropy/astropy/graphs/contributors}{package repository}, and at the \href{http://www.astropy.org/team.html}{\astropy team webpage}.}
+A more complete list of contributors to the core package can be found in the \href{https://github.com/astropy/astropy/graphs/contributors}{package repository}, and at the \href{http://www.astropy.org/team.html}{\astropy team webpage}.}}}
 

### 2018-01-10 main.tex
hyphen
Minor wording changes

@@
 
-\title{The Astropy Project: Building an inclusive, open science project and status of the v2.0 software}
+\title{The Astropy Project: Building an inclusive, open-science project and status of the v2.0 software}
 
@@
 software without overly complicating the development cycle.
-Within \astropy, all submitted code is reviewed by at least one, but typically
-more, member of the \astropy community, who provide feedback to contributors,
-which helps to improve their software development skills.
+Within \astropy, all submitted code is reviewed by at least one (but typically
+more than one) member of the \astropy community. Reviewers provide feedback
+to contributors, which helps to improve contributors' software development skills.
 As a community, \astropy follows an explicit code of conduct \citep{ape8} and treats all

### 2018-02-14 response.txt
File for draft report to referee

We thank the referee for the close reading of the paper and the insightful 
comments.  We provide a response to specific comments from the referee
and ths statistical editor below.

> There are some stylistic issues with the text. I have left comments inline
>  where appropriate.

> More generally, given the technical nature of the work being described here,
> I frequently found myself wanting a small code snippet that demonstrated the 
> new/improved functionality of the packages being described. Perhaps the 
> authors could find a way to include short code examples where appropriate, 
> either inline in the paper body or in the appendix.

> Specific issues that need to be corrected: There are some errors in the paper
> (inline comments left where appropriate), for example, Figure 6 has a fairly 
> major issue with either the wrong caption or the wrong figure but I'm sure 
> this is easily addressed. I have left comments throughout the modified 
> 'main.tex' file in the form `\inlinecomment{REVIEWER}{Comment}`

> More generally I have a few comments/concerns:

> Given the title of this paper, I expected to see more discussion by the 
> authors about the inclusivity of their community. An uber-skeptical reader 
> could make the assessment that the Astropy community has a code of conduct
> therefore believes it's inclusive. I suspect that the community is doing 
> much more than this though... So, has any attempt been made by the authors 
> to quantify the inclusivity of the Astropy community? There's a growing 
> literature in the quantitative social sciences studying open source 
> communities that the authors might want to look into: e.g. the work of 
> Gousios http://www.gousios.gr/publications.html and Vasilescu 
> https://cmustrudel.github.io/publications/ come to mind. Some discussion 
> or attempt to quantify the inclusivity is recommended.

We thank the referee for bringing up this important point. After some discussion
within the Astropy community, it became clear that a section regarding inclusion 
is beyond the scope of the current paper. Quantitative analysis of the Astropy 
community demographics is warranted. However, this is a serious undertaking 
beyond the capabilities of our community, and it may require IRB approval. Based 
on the referee's comment, we have established initial contact with the NumFOCUS 
Diversity & Inclusion in Scientific Computing (DISC) program. Results will not 
be available in time for this paper. We have opted to remove "inclusive" from 
the paper title to make room for future study and dialogue.

> The phase 'open development' is used a few times but isn't really defined or 
> connected to the broader open source ecosystem.  What other communities are 
> working in this way? How novel is 'open development' by their assessment? For 
> example, other communities have adopted policies that encourage community 
> contribution - most notable is the Node.js Foundation's contribution policies
> designed to promote 'Healthy Open Source' 
> https://medium.com/the-node-js-collection/healthy-open-source-967fa8be7951 . 
> How does the Astropy community efforts compare to this?

> A number of times I found myself wondering how the Astropy projects decides 
> whether to build their own package or leverage something available in the 
> scientific Python ecosystem? On the face of it it seems like every decision 
> made by the Astropy project to build a new core package only increases the 
> long term cost/overhead of maintaining this functionality. For example, 
> Section 3.5.2 describes `astropy.table` and notes that there's similarities 
> to the pandas package and numpy arrays. The functionality described in 
> `astropy.nddata` also sounds somewhat generic. Some discussion as to why 
> existing community tools (such as pandas) weren't used would be very welcome. 
> In addition, if the answer to this question is that these other tools don't 
> support all of the functionality the Astropy community needs (e.g. ability to
> handle Quantities with units in tables) are any efforts being made by the 
> Astropy community to contribute these changes to packages such as Pandas?

________________________

> Note from statistical editor.

> In sec 3.11.3, a sentence can be added warning users about difficulties in 
> interpreting the statistical significance of Lomb -Scargle periodogram peaks. 
> This is important because unreliable interpretation is common, and warnings 
> are not given elsewhere (e.g. NASA Exoplanet Archive Periodogram Service). 
> A good reference is Vanderplas 2017 (https://arxiv.org/abs/1703.09824) 
> soon to appear in the ApJ Suppl.

### 2018-02-15 main.tex
Change title to say core package instead of software
Update to AASTeX v6.2
Same title, minus inclusive due to need for further discussion
Response to referee: add discussion & citation regarding Lomb-Scargle interpretation

@@
-\documentclass[modern]{aastex61}
+\documentclass[modern]{aastex62}
 \usepackage{xspace}
@@
 \shorttitle{Astropy Project II}
-\shortauthors{Astropy Project et al.}
+\shortauthors{The Astropy Collaboration}
 
@@
 
-\title{The Astropy Project: Building an inclusive, open-science project and status of the v2.0 software}
+\title{The Astropy Project: Building an open-science project and status of the v2.0 core package}
 
@@
 
-\author{Astropy Project}
+\author{The Astropy Collaboration}
 \noaffiliation
@@
 in \astropypkg has been adapted from previously-published open-source code
-\citep{astroML, VanderPlas2015}.
+\citep{astroML, VanderPlas2015}. Users should be aware that correct
+interpretation of periodogram results involves some subtleties; for a thorough
+discussion of this issue, see \citet[][in press]{VanderPlas2018}.
 

### 2018-02-18 main.tex
switched to open-source

@@
 \python\footnote{\url{https://www.python.org/}} is an increasingly popular, general-purpose
-programming language that is available under a permissive open source software license and is free of
+programming language that is available under a permissive open-source software license and is free of
 charge for all major operating systems. The programming language has become especially popular
@@
 is a 501(c)(3) nonprofit that supports and promotes world-class, innovative,
-open source scientific computing.} organization. NumFOCUS has, to date, covered the direct costs incurred by the \astropy project.
+open-source scientific computing.} organization. NumFOCUS has, to date, covered the direct costs incurred by the \astropy project.
 

### 2018-02-18 main.tex
edits in intro

@@
 support or training.
-Other packages are developed by individual researchers or research groups and
-are then typically used by smaller groups for more domain-specific purposes.
+Other packages are developed by individual researchers or research groups,
+are then typically used by smaller groups for more domain-specific purposes, and 
+may have less extensive user support. 
 For both packages meant for wider distribution and for scripts specific to
 particular research projects, a library that addresses common astronomical tasks
-simplifies the software development process.
+simplifies the software development process by encouraging the reuse of common
+functions.  
 The users of such a library then also benefit from a community and ecosystem
@@
 The \astropy project has grown to become this community for \python astronomy
-software, and the \astropypkg core package is a feature-rich \python library.
+software, and the \astropypkg core package has becoming this shared foundation.
 
@@
 charge for all major operating systems. The programming language has become especially popular
-in the quantitative sciences, where researchers must simultaneously produce research, perform
+in the quantitative sciences, where researchers must simultaneously conduct research, perform
 data analysis, and develop software. A large part of this success owes itself to the vibrant
@@
 as Anaconda\footnote{\url{https://anaconda.org/}} has significantly streamlined
-the installation process for many libraries, lowering the barriers to entry.
+the installation process for many libraries, lowering the barriers to entry for new users.
 

### 2018-02-18 main.tex
fixes to section 2

@@
 While many \python projects adopt a ``Benevolent Dictator For Life'' (BDFL)
-model, \astropy has instead opted for a \emph{coordination committee}.  This
+model\footenote{https://en.wikipedia.org/wiki/Benevolent\_dictator\_for\_life}, \astropy has instead opted for a \emph{coordination committee}.  This
 is in part due to the nature of the project as a large-scale collaboration
@@
 
-Central to the success of \astropy is an open environment where anybody can
-contribute to the project.
-This model leads to an ``organic'' growth, where features are
-implemented by different people with different programming styles and
-interfaces.
-Thus, \astropy has a mechanism to more formally propose significant changes to
+The \astropy project has a formal mechanism to propose significant changes to
 the core package (e.g., re-writing the coordinates subpackage; \citealt{ape5}),
@@
 (e.g., \texttt{wcsaxes}).
-New functionality benefits from having a rapid development and release cycle that is not tied to that of the \astropypkg core (\sectionname~\ref{sect:releasecycle}).
+New functionality benefits from having a rapid development and release cycle 
+that is not tied to that of the \astropypkg core (\sectionname~\ref{sect:releasecycle}).  
+These projects may also have less stringent requirements for style, testing, or
+development as the core package.
 

### 2018-02-19 main.tex
add new panel to figure with num contributors per month. fixes #150

--- 2018-02-18 main.tex
@@
 \python\footnote{\url{https://www.python.org/}} is an increasingly popular, general-purpose
-programming language that is available under a permissive open-source software license and is free of
+programming language that is available under a permissive open source software license and is free of
 charge for all major operating systems. The programming language has become especially popular
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{ncommits.pdf}
+\includegraphics[width=\textwidth]{commits.pdf}
 \caption{%
     \emph{Left panel}: Distribution of number of commits per committer.
-    \emph{Right panel}: Cumulative number of commits to the \astropypkg core
+    \emph{Middle panel}: Cumulative number of commits to the \astropypkg core
     package over time.
+    \emph{Right panel}: Number of unique committers per month to the
+    \astropypkg core package.
     \label{fig:ncommits}
@@
 is a 501(c)(3) nonprofit that supports and promotes world-class, innovative,
-open-source scientific computing.} organization. NumFOCUS has, to date, covered the direct costs incurred by the \astropy project.
+open source scientific computing.} organization. NumFOCUS has, to date, covered the direct costs incurred by the \astropy project.
 

### 2018-02-19 figures/commits_figure.py

@@ -9,6 +9,7 @@ import pandas as pd
 import numpy as np
 from matplotlib import pyplot as plt
 
+
 def generate_commit_stats_file(filename='gitlogstats.csv', overwrite=False,
                                astropy_path=None):
     """
@@ -17,7 +18,7 @@ def generate_commit_stats_file(filename='gitlogstats.csv', overwrite=False,
     set `overwrite` to True to always re-generate the statistics.
     """
     if os.path.isfile(filename) and not overwrite:
-        return pd.read_csv(filename)
+        df = pd.read_csv(filename)
 
     else:
         import subprocess
@@ -30,11 +31,17 @@ def generate_commit_stats_file(filename='gitlogstats.csv', overwrite=False,
 
         with tempfile.NamedTemporaryFile(mode='w+') as f:
             f.write(output)
+            f.seek(0)
             df = pd.read_csv(f.name, names=['commit', 'date', 'author',
                                             'committer'])
 
+        print('writing df to file {0}'.format(filename))
         df.to_csv(filename)
-        return df
+
+    df['date'] = pd.to_datetime(df['date'])
+    df = df.set_index(df['date'])
+
+    return df
 
 
 def commits_plot(astropy_path, ax=None, **hist_kw):
@@ -74,8 +81,6 @@ def commits_vs_time(astropy_path, ax=None, **hist_kw):
 
     df = generate_commit_stats_file(astropy_path=astropy_path)
     # n_commits = df.groupby('date').size()
-    df['date'] = pd.to_datetime(df['date'])
-    df = df.set_index(df['date'])
 
     date_bins = df.groupby(pd.TimeGrouper('D'))
     commits_per_day = date_bins.size()
@@ -84,13 +89,28 @@ def commits_vs_time(astropy_path, ax=None, **hist_kw):
         fig, ax = plt.subplots(1, 1, figsize=(6,5))
 
     n_commits = np.cumsum(commits_per_day)
-    plt.fill_between(n_commits.index, 0, np.array(n_commits))
+    ax.fill_between(n_commits.index, 0, np.array(n_commits))
 
     ax.set_xlabel('year')
     ax.set_ylabel('number of commits')
 
     ax.set_xlim(datetime(2011,6,1), datetime(2018,1,1))
     ax.set_ylim(0, 21000)
+
+
[…]

### 2018-02-25 response.txt
Update response.txt
explain open development
Closes #140

@@
 comments.  We provide a response to specific comments from the referee
-and ths statistical editor below.
+and the statistical editor below.
 
@@
 
+This question is at the intersection of two communities. On the one
+side, there is the open source community, which by itself consists of
+many different projects with vastly different norms and
+processes. Many terms, "open develoment" being one of them, are used
+with slightly different meanings in different parts of this
+community. The model of astropy - the development happens openly on
+github and anyone with an internet connection can comment on issues or
+propose a pull request, but only a select set of maintainers can merge
+them - is by no means special. Many open source communities work in a
+very similar way, although they may use different terminology to
+describe it. On the other hand, there is the astrophysics community,
+and while there are several open source and open development (in the
+way astropy uses the term) projects in astronomy, astropy is probably
+the biggest one. Many astronmers are not involved in any open
+development (also many make use of open source projects they are not
+involved in e.g. GNU/Linux), and the concept is new to many of
+them. This article caters mostly to the astrophysics community, so we
+decided to add a definition, but we refrain from a comparative
+discussion with other open source projects.
+
 > A number of times I found myself wondering how the Astropy projects decides 
@@
 > soon to appear in the ApJ Suppl.
+
+A short note directing the reader to Vanderplas (2007) was included.

### 2018-02-25 main.tex
explain open development
Closes #140

@@
 support astronomical functionality in the \python programming language.
+``Open-development'' describes a process where anybody with an internet connection can suggest changes to the source code and contribute his or her opinion when new features, bug fixes, or other code changes are discussed (see Sect.~\ref{sect:devmod} and \ref{sect:ape} of how this is organized in practice).
 The \astropypkg core package is now a feature-rich library of sufficiently
@@
 \subsection{Astropy development model}
-
+\label{sect:devmod}
 Code is contributed to the \astropypkg core package or modified through ``pull
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{commits.pdf}
+\includegraphics[width=\textwidth]{ncommits.pdf}
 \caption{%
     \emph{Left panel}: Distribution of number of commits per committer.
-    \emph{Middle panel}: Cumulative number of commits to the \astropypkg core
+    \emph{Right panel}: Cumulative number of commits to the \astropypkg core
     package over time.
-    \emph{Right panel}: Number of unique committers per month to the
-    \astropypkg core package.
     \label{fig:ncommits}
@@
 \subsection{APEs - Astropy Proposals for Enhancement}
-
+\label{sect:ape}
 Central to the success of \astropy is an open environment where anybody can

### 2018-02-25 response.txt
Explain why we do *not* include code examples
fixes #139

--- 2018-02-14 response.txt
@@
 > either inline in the paper body or in the appendix.
+
+We did include code snippets in the first astropy paper from 2013, and
+it is not much work; we could use the same scripts to provide nicely
+formatted code examples with appropriate syntax highlighting here. However,
+we have made a conscious decision to avoid that this time as far as
+possible. We will explain our reasoning below, but if the referee
+insists, we can quickly add a few examples in a second revision.
+
+The main reasons why we chose NOT to include code samples are:
+
+- While we aim for stability, many of the newsest features are still
+  considered provisional, meaning that their API can still change. The
+  paper describes astropy 2.0, but at the time of writing this,
+  astropy 3.0 is already released. We hope that this paper is useful
+  for years to come. Code examples for a specific version are at risk
+  of being outdated much sooner than that.
+
+- Code examples belong in the documentation. In the documentation at
+  cods.astropy.org we provide extensive examples with enough comments
+  to actually understand what is going on. If readers are curious, we
+  want them to read the documentation.
+
+- It takes a lot of space to explain a code example well. Currently,
+  the text lists the names of the most important classes or
+  functions. To give a meaningful example that shows these classes in
+  action and is useful to people not familiar with astropy (or even
+  Python), we would have to detail several parameters and the format
+  of the results. We think that it is more useful to explain the
+  general concept in the paper and not the names and the specific
+  implementation of the functions and parameters.
+
+- Most new features would require some setup. For example, showing the
+  code for WCS axis plotting is not very useful without loading an
+  image with a WCS in it first. More complex features profit more from
+  code examples, but they also require much more setup to make such an
+  example self-consistent and useful. Again, the documentation is a better
+  place for that.
 

### 2018-02-25 main.tex
additional fixes to mid-sections

--- 2018-02-18 main.tex
@@
 advanced for LTS releases, ``y'' for non-LTS feature releases, and
-``z'' for bugfix releases.
+``z'' for bugfix releases.  This is similar to 
+Semantic Versioning\footnote{https://semver.org}.
 
@@
 is a 501(c)(3) nonprofit that supports and promotes world-class, innovative,
-open-source scientific computing.} organization. NumFOCUS has, to date, covered the direct costs incurred by the \astropy project.
+open-source scientific computing.} organization. NumFOCUS has, 
+to date, covered the direct costs incurred by the \astropy project.
 
@@
 (see \sectionname~\ref{sec:coordinates}) depends on them.
-For most other subpackages, quantities are at least accepted and often expected
-by default.
+Most \astropypkg subpackages have been made compatible with \texttt{Quantity} 
+objects, although they are not always required.
 
@@
 The package was described in detail in  \citet{astropy} and has
-stayed stable for the last several versions of \astropypkg.
+remained stable for the last several versions of \astropypkg.
 Thus, in what follows, we only highlight significant changes or new features

### 2018-02-25 response.txt
address small edits

--- 2018-02-14 response.txt
@@
 >  where appropriate.
+
+We have addressed all of the stylistic issues that were raised by the referee.
+Here are some responses to the more detailed comments:
+
+Comment on styles:
+As it was not related to the section, we removed the first paragraph 
+in the APE section that commented on different styles.  However, we
+did add a comment in the affiliated package section indicating that
+they may have different requirements and structure than the core package.
+
+Comment on NDData:
+At the time of initial development, the developers were not aware of 
+any open source packages that would have fit the requirements of NDData.  Since
+then, we have been working with different groups (LSST, sunypy) to coordinate
+development of the NDData interface as well as assessing other attempts at 
+something similar.  There is currently an APE about this under discussion.
 

### 2018-02-25 main.tex
address small edits

@@
     ecosystem.  Each red $x$ signifies a pixel that is set to \texttt{NaN} in the
-    original data (a).  If the data are convolved with a Gaussian kernel on a
+    original data (top left).  If the data are convolved with a Gaussian kernel on a
     $9\times 9$ grid using
-    \package{scipy}'s direct convolution (b), any pixel within range of the original \texttt{NaN}
-    pixels is also set to \texttt{NaN}.  Panel (c) shows what happens if the
+    \package{scipy}'s direct convolution (top right), any pixel within range of the original \texttt{NaN}
+    pixels is also set to \texttt{NaN}.  The bottom left panel shows what happens if the
     \texttt{NaN}s are set to zero first: the originally \texttt{NaN} regions are
-    depressed relative to their surroundings.  Finally, panel (d) shows
+    depressed relative to their surroundings.  Finally, the bottom right panel shows
     \astropypkg's convolution behavior, where the missing pixels are replaced
@@
 function to produce the RGB image from three SDSS filter images ($g$, $r$, $i$).
-The left and right panel images show two different parameter choices for the
-stretch and softening parameters (shown in the titles).
 \label{fig:ngc6977}}
@@
 
-The development of the \astropypkg package and cultivation of the \astropy
-ecosystem are still maintaining significant growth while improving in stability,
-breadth, and reliability.
+The \astropypkg package is improving in stability, breadth, and reliability
+while the the \astropy project is still significantly growing. 
 As the \astropypkg core package becomes more mature, several subpackages have
@@
 Foundation, the Sloan Foundation, and the Washington Research Foundation. SMC acknowledges the National Research
-Foundation of South Africa. TLA was supported by NASA contract NAS8-03060. Support for E.J.T. was provided by NASA
+Foundation of South Africa. TLA was supported by NASA contract NAS8-03060. Support for EJT. was provided by NASA
 through Hubble Fellowship grant No. 51316.01 awarded by the Space Telescope Science Institute, which is operated by
@@
 Giacconi Fellowship. MB was supported by the FONDECYT regular project 1170618 and the MINEDUC-UA projects codes
-ANT 1655 and ANT 1656. DH was supported through the SFB 881 ``The
-Milky Way System'' by the German Research Foundation
+ANT 1655 and ANT 1656. DH was supported through the SFB 881 ``The Milky Way System'' by the German Research Foundation
 (DFG). WEK was supported by an ESO Fellowship. C.M. is supported by NSF grant AST-1313484. SP was supported by

### 2018-02-27 main.tex
Add re-use section

--- 2018-02-25 main.tex
@@
 support astronomical functionality in the \python programming language.
-``Open-development'' describes a process where anybody with an internet connection can suggest changes to the source code and contribute his or her opinion when new features, bug fixes, or other code changes are discussed (see Sect.~\ref{sect:devmod} and \ref{sect:ape} of how this is organized in practice).
 The \astropypkg core package is now a feature-rich library of sufficiently
@@
 \subsection{Astropy development model}
-\label{sect:devmod}
+
 Code is contributed to the \astropypkg core package or modified through ``pull
@@
 \subsection{APEs - Astropy Proposals for Enhancement}
-\label{sect:ape}
+
 Central to the success of \astropy is an open environment where anybody can
@@
 
+\subsection{Reuse of the scientific Python ecosystem}
+
+The \astropy Project is built on a philosophy of building from the existing
+Python scientific ecosystem wherever possible. Many of the enabling technologies
+like \texttt{numpy}, \texttt{scipy}, \texttt{matplotlib}, or \texttt{cython},
+are necessary as the core underpinnings of \astropy packages.  Often this means
+simply means using these packages as ``building blocks'' (E.g., the ubiquitous
+use of \texttt{numpy} arrays throughout \astropypkg).  In other cases this means
+wrappers around more general algorithms that make them more convenient for
+astronomy use cases (E.g., the model-fitting in the \package{astropy.modeling}
+subpackage discussed in \sectionname~\ref{sec:modeling}).  Sometimes these
+simple wrappers evolve into more complex implementations that address
+astronomically-relevant use cases the general tool does not support (E.g.,
+\package{astropy.convolution}, see \sectionname~\ref{ssec:convolution}). As a
+broad rule, the Project explicitly encourages re-use of code where possible.
+
+However, the boundaries of when this re-use is called for often ambiguous.  Some
+of the examples above only evolved after significant debate in the community
+over whether these algorithms were sufficient.  Other times, even apparently
+general functionality did not exist in the wider ecosystem that met the \astropy
+community's needs, and hence the functionality had to be developed wholly from
+the developer resources available in the community (E.g.,
+\package{astropy.units}, or \package{astropy.table} when it began). While some
+of this functionality is ``given back'' to the wider community (E.g., myriad bug
+fixes for the enabling technologies listed above, and some of the testing and
+documentation architecture), in general, careful consideration is taken of
+whether the additional effort to make a piece of \astropy, and it is only
+``extracted'' when it seems plausible that the ongoing effort is worth the
+reward in the form of additional contributors or maintainers.
+
 \section{Astropy Core Package Version 2.0}
@@
 \subsection{Convolution}
+\label{ssec:convolution}
 

### 2018-02-28 main.tex
add context to new figure panel

@@
 \figurename~\ref{fig:ncommits}, left, shows the distribution of total number of
-commits per contributor as of November 2017.
+commits per contributor as of early 2018.
 The relative flatness of this distribution (as demonstrated by its log-log slope of
@@
 fix for a typographical error.
-\figurename~\ref{fig:ncommits}, right, shows the number of commits as a
+\figurename~\ref{fig:ncommits}, middle, shows the number of commits as a
 function of time since the genesis of the \astropypkg core package.
@@
 steady rate throughout its existence.
+\figurename~\ref{fig:ncommits}, right, shows that, $\approx$20--25 people
+contribute to the core package each month.
+While we would like for this number to grow, this demonstrates that the core
+package is still being developed and maintained by a substantial group of
+contributors.
 
@@
 
-\subsection{Reuse of the scientific Python ecosystem}
-
-The \astropy Project is built on a philosophy of building from the existing
-Python scientific ecosystem wherever possible. Many of the enabling technologies
-like \texttt{numpy}, \texttt{scipy}, \texttt{matplotlib}, or \texttt{cython},
-are necessary as the core underpinnings of \astropy packages.  Often this means
-simply means using these packages as ``building blocks'' (E.g., the ubiquitous
-use of \texttt{numpy} arrays throughout \astropypkg).  In other cases this means
-wrappers around more general algorithms that make them more convenient for
-astronomy use cases (E.g., the model-fitting in the \package{astropy.modeling}
-subpackage discussed in \sectionname~\ref{sec:modeling}).  Sometimes these
-simple wrappers evolve into more complex implementations that address
-astronomically-relevant use cases the general tool does not support (E.g.,
-\package{astropy.convolution}, see \sectionname~\ref{ssec:convolution}). As a
-broad rule, the Project explicitly encourages re-use of code where possible.
-
-However, the boundaries of when this re-use is called for often ambiguous.  Some
-of the examples above only evolved after significant debate in the community
-over whether these algorithms were sufficient.  Other times, even apparently
-general functionality did not exist in the wider ecosystem that met the \astropy
-community's needs, and hence the functionality had to be developed wholly from
-the developer resources available in the community (E.g.,
-\package{astropy.units}, or \package{astropy.table} when it began). While some
-of this functionality is ``given back'' to the wider community (E.g., myriad bug
-fixes for the enabling technologies listed above, and some of the testing and
-documentation architecture), in general, careful consideration is taken of
-whether the additional effort to make a piece of \astropy, and it is only
-``extracted'' when it seems plausible that the ongoing effort is worth the
-reward in the form of additional contributors or maintainers.
-
 \section{Astropy Core Package Version 2.0}
@@
 \subsection{Convolution}
-\label{ssec:convolution}
 

### 2018-02-28 main.tex
make class and function names links

@@
 \newcommand{\comment}[2]{\todo{#1: #2}\xspace}
+
+% Links to documentation: subpackages
+\newcommand{\astropysubpkg}[1]{\href{http://docs.astropy.org/en/stable/#1/index.html}{\texttt{astropy.#1}}\xspace}
+\newcommand{\astropyiosubpkg}[1]{\href{http://docs.astropy.org/en/stable/io/#1/index.html}{\texttt{astropy.io.#1}}\xspace}
+\newcommand{\astropywcsaxes}{\href{http://docs.astropy.org/en/stable/visualization/wcsaxes/index.html}{\texttt{astropy.visualization.wcsaxes}}\xspace}
+
+% Links to documentation: classes
+\newcommand{\astropyskycoord}{\href{http://docs.astropy.org/en/stable/api/astropy.coordinates.SkyCoord.html}{\texttt{SkyCoord}}\xspace}
+\newcommand{\astropyQuantity}{\href{http://docs.astropy.org/en/stable/api/astropy.units.Quantity.html}{\texttt{Quantity}}\xspace}
+\newcommand{\astropyTime}{\href{http://docs.astropy.org/en/stable/api/astropy.time.Time.html}{\texttt{Time}}\xspace}
+\newcommand{\astropyTable}{\href{http://docs.astropy.org/en/stable/api/astropy.table.Table.html}{\texttt{Table}}\xspace}
 
@@
 \figurename~\ref{fig:ncommits}, left, shows the distribution of total number of
-commits per contributor as of early 2018.
+commits per contributor as of November 2017.
 The relative flatness of this distribution (as demonstrated by its log-log slope of
@@
 fix for a typographical error.
-\figurename~\ref{fig:ncommits}, middle, shows the number of commits as a
+\figurename~\ref{fig:ncommits}, right, shows the number of commits as a
 function of time since the genesis of the \astropypkg core package.
@@
 steady rate throughout its existence.
-\figurename~\ref{fig:ncommits}, right, shows that, $\approx$20--25 people
-contribute to the core package each month.
-While we would like for this number to grow, this demonstrates that the core
-package is still being developed and maintained by a substantial group of
-contributors.
 
@@
 that will eventually be incorporated into the \astropypkg core package
-(e.g., \texttt{wcsaxes}).
+(e.g., \astropywcsaxes).
 New functionality benefits from having a rapid development and release cycle that is not tied to that of the \astropypkg core (\sectionname~\ref{sect:releasecycle}).
@@
 astronomical files, and units) or base classes for other
-packages to utilize for a common interface (e.g., \texttt{NDData}).
+packages to utilize for a common interface (e.g.,
+\href{http://docs.astropy.org/en/stable/nddata/index.html}{\texttt{NDData}}).
 In this section, we highlight new features introduced or substantially improved
@@
 
-The \texttt{astropy.units} subpackage adds support for representing units and
+The \astropysubpkg{units} subpackage adds support for representing units and
 numbers with associated units --- ``quantities'' --- in code.
@@
 numerical operations.
-In \texttt{astropy.units}, \texttt{Quantity} objects extend \texttt{numpy}
+In \astropysubpkg{units}, \astropyQuantity objects extend \texttt{numpy}
 array objects and have been designed with speed in mind.
@@
 Units are intimately entwined in the definition of astronomical coordinates;
-thus, nearly all functionality in the \texttt{astropy.coordinates} subpackage
+thus, nearly all functionality in the \astropysubpkg{coordinates} subpackage
 (see \sectionname~\ref{sec:coordinates}) depends on them.
@@
 
-\texttt{Quantity} objects extend
+\astropyQuantity objects extend
 \texttt{numpy.ndarray} objects and therefore
 work well with many of the functions in \texttt{numpy} that support
-array operations. For example, \texttt{Quantity} objects with angular
+array operations. For example, \astropyQuantity objects with angular
 units can be directly passed in to the trigonometric functions implemented in
@@
         By default, taking the logarithm of
-        a \texttt{Quantity} object with non-dimensionless units intentionally
+        a \astropyQuantity object with non-dimensionless units intentionally
         fails.
@@
         and decibels, which are more generic logarithmic ratios of quantities.
-        Logarithmic, relative units are now supported in \texttt{astropy.units}.
+        Logarithmic, relative units are now supported in \astropysubpkg{units}.
 
@@
         When writing code or
-        functions that expect \texttt{Quantity} objects, we often want to
+        functions that expect \astropyQuantity objects, we often want to
         enforce that the input units have the correct physical type.
-        For example, we may want to require only length-type \texttt{Quantity}
+        For example, we may want to require only length-type \astropyQuantity
         objects.
-        \texttt{astropy.units} provides a tool called \texttt{quantity\_input()}
+        \astropysubpkg{units} provides a tool called \href{http://docs.astropy.org/en/stable/api/astropy.units.quantity_input.html}{\texttt{quantity\_input()}}
         that can perform this verification automatically to avoid repetitive
@@
 
-The \texttt{astropy.constants} subpackage provides a selection of physical and
-astronomical constants as \texttt{Quantity} objects (see
+The \astropysubpkg{constants} subpackage provides a selection of physical and
+astronomical constants as \astropyQuantity objects (see
 \sectionname~\ref{sec:units}).
@@
 the values have to be imported directly; with version
-2.0, \texttt{astropy.units} uses the \texttt{astropyconst20} versions.
-
-Astronomers using \texttt{astropy.constants} should take particular note of the
+2.0, \astropysubpkg{units} uses the \texttt{astropyconst20} versions.
+
+Astronomers using \astropysubpkg{constants} should take particular note of the
 constants provided for Earth, Jupiter, and the Sun.
@@
 \label{sec:coordinates}
-The \package{astropy.coordinates} subpackage is designed to support representing
+The \astropysubpkg{coordinates} subpackage is designed to support representing
 and transforming celestial coordinates and, new in version 2.0, velocities.
-The framework heavily relies on the \package{astropy.units} subpackage, and most
-inputs to objects in this subpackage are expected to be \texttt{Quantity}
+The framework heavily relies on the \astropysubpkg{units} subpackage, and most
+inputs to objects in this subpackage are expected to be \astropyQuantity
 objects.
@@
 reference frame transformations as currently implemented in
-\texttt{astropy.coordinates}.
+\astropysubpkg{coordinates}.
 Custom user-implemented \texttt{Frame} classes that define transformations to
@@
     The full graph of possible reference frame transformations implemented in
-    \texttt{astropy.coordinates}.
+    \astropysubpkg{coordinates}.
     Arrows indicate transformations from one frame to another.
@@
 \texttt{Representation} classes directly.
-Instead, \texttt{astropy.coordinates} provides a high-level interface to
-representing astronomical coordinates through the \texttt{SkyCoord} class,
+Instead, \astropysubpkg{coordinates} provides a high-level interface to
+representing astronomical coordinates through the \astropyskycoord class,
 which was designed to provide a single class that
@@
 In what follows, we briefly highlight key new features in
-\texttt{astropy.coordinates}.
+\astropysubpkg{coordinates}.
 
@@
     Transformations between \texttt{AltAz} and any Barycentric coordinate frame
-    also requires specifying a time using the \texttt{Time} class from
+    also requires specifying a time using the \astropyTime class from
     \texttt{astropy.time}.
@@
     currently experimental.  As such, in version 2.0, only the \texttt{Frame}
-    classes (and not the \texttt{SkyCoord} class) support handling velocities.
+    classes (and not the \astropyskycoord class) support handling velocities.
 
@@
 In order to check the accuracy of the coordinate transformations in
-\package{astropy.coordinates}, we have created a set of benchmarks that we use
+\astropysubpkg{coordinates}, we have created a set of benchmarks that we use
 to compare transformations between a set of coordinate frames for a number of
@@
 
-The \package{astropy.time} subpackage focuses on supporting time scales (e.g.,
+The \astropysubpkg{time} subpackage focuses on supporting time scales (e.g.,
 UTC, TAI, UT1) and time formats (e.g., Julian date, modified Julian date) that
@@
 or sidereal times.
-\package{astropy.time} is currently built on the ERFA (\citealt{erfa}) C
+\astropysubpkg{time} is currently built on the ERFA (\citealt{erfa}) C
 library, which replicates the Standards of Fundamental Astronomy (SOFA;
@@
 standardized.
-With the location of a source on the sky (i.e., a \texttt{SkyCoord}
+With the location of a source on the sky (i.e., a \astropyskycoord
 object), the location of an observatory on Earth (i.e., an
-\texttt{EarthLocation} object), and time values as \texttt{Time}
+\href{http://docs.astropy.org/en/stable/api/astropy.coordinates.EarthLocation.html}{\texttt{EarthLocation}} object), and time values as \astropyTime
 objects, the time corrections to shift to the solar system barycenter or
-heliocenter can now be computed with \package{astropy.time} using the
-\texttt{light\_travel\_time} method of a \texttt{Time} object.
+heliocenter can now be computed with \astropysubpkg{time} using the
+\texttt{light\_travel\_time} method of a \astropyTime object.
 
@@
 
-The \package{astropy.nddata} subpackage provides three types of functionality: an
+The \astropysubpkg{nddata} subpackage provides three types of functionality: an
 abstract interface for representing generic arbitrary-dimensional datasets
@@
 
-The \package{astropy.nddata.utils} module provides utilities that can operate
+The \href{http://docs.astropy.org/en/stable/nddata/utils.html}
+{\package{astropy.nddata.utils}} module provides utilities that can operate
 on either plain \package{numpy} arrays or any of the classes in the
-\package{astropy.nddata} subpackage. It features a class for representing
+\astropysubpkg{nddata} subpackage. It features a class for representing
 two-dimensional image cutouts, allowing one to easily link pixels in the cutout
@@
 
-The \package{astropy.table} subpackage provides functionality for
+The \astropysubpkg{table} subpackage provides functionality for
 representing and manipulating heterogeneous data. In some respects,
@@
 \package{pandas} dataframes \citep{pandas} but with modifications for
-astronomical data. Most notably, tables from \package{astropy.table}
+astronomical data. Most notably, tables from \astropysubpkg{table}
 allow for table or column metadata and can handle
@@
 detail in \cite{astropy}.  Thus, in what follows, we only summarize
-key new features or updates to \package{astropy.table} since the
+key new features or updates to \astropysubpkg{table} since the
 previous \astropy paper. These are support for grouped table
@@
 the groups based on user-defined criteria. These kinds of grouping and
-aggregation operations are now fully supported by \texttt{Table} objects.
-
-\texttt{Table} objects can now be combined in several different ways. If two
+aggregation operations are now fully supported by \astropyTable objects.
+
+\astropyTable objects can now be combined in several different ways. If two
 tables have the same columns, we may want to stack them ``vertically'' to create a
@@
 
-The \texttt{Table} object now allows array-valued \texttt{Quantity}, celestial
-coordinate (\texttt{SkyCoord}), and date/time (\texttt{Time}) objects to
+The \astropyTable object now allows array-valued \astropyQuantity, celestial
+coordinate (\astropyskycoord), and date/time (\astropyTime) objects to
 be used as columns. It also provides a general way for other user-defined
@@
 represent catalogs of sources or time series in \astropy, while having both the
-benefits of the \texttt{Table} object (e.g., accessing specific rows/columns
+benefits of the \astropyTable object (e.g., accessing specific rows/columns
 or groups of them and combining tables) and of, for example,
-the \texttt{SkyCoord} or the \texttt{Time} classes (e.g., converting the
+the \astropyskycoord or the \astropyTime classes (e.g., converting the
 coordinates to a different frame or accessing the date/time in the desired time scale).
@@
 
-The \package{astropy.io} subpackage provides support for reading and writing
+The \package{astropy.io} subpackages provide support for reading and writing
 data to a variety of ASCII and binary file formats, such as a wide range of
@@
 It also provides a unified interface for reading and writing data with these
-different formats using the \package{astropy.table} subpackage.
+different formats using the \astropysubpkg{table} subpackage.
 For many common cases, this simplifies the process of file input and output (I/O) and
@@
 
-The \package{astropy.io.ascii} subpackage now includes a significantly faster
+The \astropyiosubpkg{ascii} subpackage now includes a significantly faster
 Cython/C engine for reading and writing ASCII files. This is available for most
@@
 
-The \package{astropy.io.ascii} subpackage now provides the capability
+The \astropyiosubpkg{ascii} subpackage now provides the capability
 to read a table within an HTML file or web URL into an \astropypkg
-\texttt{Table} object. A \texttt{Table} object can now also
+\astropyTable object. A \astropyTable object can now also
 be written out as an HTML table.
@@
 
-The \package{astropy.io.fits} subpackage started as a direct port of the
+The \astropyiosubpkg{fits} subpackage started as a direct port of the
 PyFITS project \citep{PyFITS}. Therefore, it is pretty stable, with mostly bug
@@
 Command-line scripts are now available for printing a summary of the HDUs in
-FITS file(s) (\texttt{fitsinfo}) and for printing the header information to
-the screen in a human-readable format (\texttt{fitsheader}).
+FITS file(s)
+(\href{http://docs.astropy.org/en/stable/io/fits/usage/scripts.html#module-astropy.io.fits.scripts.fitsinfo}{\texttt{fitsinfo}})
+and for printing the header information to the screen in a human-readable format
+(\href{http://docs.astropy.org/en/stable/io/fits/usage/scripts.html#module-astropy.io.fits.scripts.fitsheader}{\texttt{fitsheader}}).
 
@@
 memory until requested.  This approach should provide substantial speed-ups
-when using the convenience functions (e.g., \texttt{getheader()} or
-\texttt{getdata()}) to get an HDU that is near the beginning in a file with
+when using the convenience functions (e.g., \href{http://docs.astropy.org/en/stable/io/fits/api/files.html#getheader}{\texttt{getheader()}} or
+\href{http://docs.astropy.org/en/stable/io/fits/api/files.html#getdata}{\texttt{getdata()}}) to get an HDU that is near the beginning in a file with
 many HDUs.
@@
 
-The \package{astropy.modeling} subpackage provides a framework for representing
+The \astropysubpkg{modeling} subpackage provides a framework for representing
 analytical models and performing model evaluation and parameter fitting.
@@
 
-\package{astropy.modeling} provides an efficient way to set up the same type of model with many different sets of parameter values.
+\astropysubpkg{modeling} provides an efficient way to set up the same type of model with many different sets of parameter values.
 This creates a model set that can be efficiently evaluated.
@@
 
-\package{astropy.modeling} provides several fitters which are wrappers around some of the \texttt{numpy} and \texttt{scipy.optimize} functions and provide support for specifying parameter constraints.
+\astropysubpkg{modeling} provides several fitters which are wrappers around some of the \texttt{numpy} and \texttt{scipy.optimize} functions and provide support for specifying parameter constraints.
 The fitters take a model and data as input and return a copy of the model with the optimized parameter values set.
@@
 Sherpa \citep{sherpa},
-and \package{astropy.modeling}, to bring the Sherpa fitters into \astropypkg.
+and \astropysubpkg{modeling}, to bring the Sherpa fitters into \astropypkg.
 
@@
 If arithmetic combinations of existing models is not sufficient, new model
-classes can be defined in different ways. The \package{astropy.modeling}
+classes can be defined in different ways. The \astropysubpkg{modeling}
 package provides tools to turn a simple function into a full-featured model,
@@
 
-The \package{astropy.modeling} subpackage now supports the representation,
-evaluation, and fitting of models using \texttt{Quantity} objects, which attach
+The \astropysubpkg{modeling} subpackage now supports the representation,
+evaluation, and fitting of models using \astropyQuantity objects, which attach
 units to scalar values or arrays of values. In practice, this means that one
@@
 it using input values with different but equivalent units. For example, the
-blackbody model (\texttt{BlackBody1D}) can be used to fit observed flux
-densities in a variety of units and as a function of different units of
-spectral coordinates (e.g., wavelength or frequency).
+blackbody model
+(\href{http://docs.astropy.org/en/stable/api/astropy.modeling.blackbody.BlackBody1D.html}{\texttt{BlackBody1D}})
+can be used to fit observed flux densities in a variety of units and as a
+function of different units of spectral coordinates (e.g., wavelength or
+frequency).
 
@@
 
-The \package{astropy.convolution} subpackage implements
+The \astropysubpkg{convolution} subpackage implements
 \textit{normalized convolution} \citep[e.g.,][]{Knutsson1993}, an image
@@
 
-The \package{astropy.visualization} subpackage provides functionality that can
+The \astropysubpkg{visualization} subpackage provides functionality that can
 be helpful when visualizing data. This includes a framework (previously the
-standalone \package{wcsaxes} package) for plotting
+standalone \astropywcsaxes package) for plotting
 astronomical images with coordinates with \package{matplotlib}, functionality related to image
@@
 
-\package{astropy.visualization} provides a framework for transforming values in
+\astropysubpkg{visualization} provides a framework for transforming values in
 images (and more generally any arrays), typically for the purpose of
@@
 displaying data by passing in a normalization object.
-The \package{astropy.visualization} package also provides a normalization class
+The \astropysubpkg{visualization} package also provides a normalization class
 that wraps the interval and stretches objects into a normalization object that
@@
 (such as longitude/latitude) need not be lined up with the pixel axes of the
-image. The \package{astropy.visualization.wcsaxes} subpackage implements a
+image. The \astropywcsaxes subpackage implements a
 generalized way of making figures from an image array and a WCS object
@@
 focuses on providing a very high-level interface to plotting that requires very
-few lines of code to get a good result, whereas \package{wcsaxes} defines an
+few lines of code to get a good result, whereas \astropywcsaxes defines an
 interface that is much closer to that of \package{matplotlib} \citep{matplotlib}.
@@
 
-An example of a visualization made with \package{wcsaxes} is shown in
+An example of a visualization made with \astropywcsaxes is shown in
 \figurename~\ref{fig:wcsaxes}. This example illustrates the ability to
@@
 \caption{%
-An example of figure made using the \package{astropy.visualization.wcsaxes}
+An example of figure made using the \astropywcsaxes
 subpackage, using \textit{Spitzer}/IRAC 8.0~$\mu$m data from the Cygnus-X
@@
 
-\package{astropy.visualization} also provides a histogram function, which is a
+\astropysubpkg{visualization} also provides a histogram function, which is a
 generalization of \texttt{matplotlib}’s histogram function, to allow for a more
@@
 RGB composite images from three separate high-dynamic range
-arrays. The \package{astropy.visualization} subpackage provides a convenience
+arrays. The \astropysubpkg{visualization} subpackage provides a convenience
 function to create such a color image.  It also includes an associated set of
@@
 This image was generated from SDSS images using the
-\package{astropy.visualization} tools.
+\astropysubpkg{visualization} tools.
 
@@
 \caption{An RGB color image of the region near the Hickson 88 group
-constructed from SDSS images and the \package{astropy.visualization}
+constructed from SDSS images and the \astropysubpkg{visualization}
 tools.
-This example uses \package{astropy.visualization.wcsaxes} to display the
-sky coordinate grid, and the \texttt{astropy.visualization.make\_lupton\_rgb()}
+This example uses \astropywcsaxes to display the
+sky coordinate grid, and the
+\href{http://docs.astropy.org/en/stable/api/astropy.visualization.make_lupton_rgb.html}{\texttt{make\_lupton\_rgb()}}
 function to produce the RGB image from three SDSS filter images ($g$, $r$, $i$).
@@
 
-The \package{cosmology} subpackage contains classes for representing different
-cosmologies and functions for calculating commonly used quantities such as
-look-back time and distance.   The subpackage was described in detail in
+The \astropysubpkg{cosmology} subpackage contains classes for representing
+different cosmologies and functions for calculating commonly used quantities
+such as look-back time and distance.   The subpackage was described in detail in
 \cite{astropy}.  The default cosmology in \astropypkg version 2.0 is given by
@@
 
-The \package{astropy.stats} package provides statistical tools that
+The \astropysubpkg{stats} package provides statistical tools that
 are useful for astronomy and are either not found in or extend
@@
 as \package{scipy} \citep{scipy} or \package{statsmodels}
-\citep{seabold2010statsmodels}.  \package{astropy.stats} contains
+\citep{seabold2010statsmodels}.  \astropysubpkg{stats} contains
 a range of functionality used by many different disciplines
@@
 distributions that largely mitigate the effects of outliers.
-\package{astropy.stats} includes several robust statistical functions that are
+\astropysubpkg{stats} includes several robust statistical functions that are
 commonly used in astronomy, such as sigma clipping methods for rejecting
@@
 A set of circular statistical estimators based on \citet{JammalamadakaSengupta}
-are implemented in \package{astropy.stats}.  These functions provide
+are implemented in \astropysubpkg{stats}.  These functions provide
 measurements of the circular mean, variance, and moment.   All of these
 functions work with both \texttt{numpy.ndarrays} (assumed to be in radians) and
-\texttt{Quantity} objects.  In addition, the subpackage includes
+\astropyQuantity objects.  In addition, the subpackage includes
 tests for Rayleigh Test, \texttt{vtest}, and a function to compute the maximum
@@
 Periodic analysis of unevenly-spaced time series is common across many
-sub-fields of astronomy. The \package{astropy.stats} package now includes
+sub-fields of astronomy. The \astropysubpkg{stats} package now includes
 several efficient implementations of the Lomb-Scargle periodogram
@@
 \subsubsection{Bayesian Blocks and Histogram Binning}
-\package{astropy.stats} also includes an implementation of
+\astropysubpkg{stats} also includes an implementation of
 {\it Bayesian Blocks} \citep{Scargle2013}, an algorithm for analysis of
@@
 project in a number of different ways.  We would like to acknowledge
-Alex Conley and Neil Crighton for maintaining the  \package{cosmology}
+Alex Conley and Neil Crighton for maintaining the \astropysubpkg{cosmology}
 subpackage.

### 2018-02-28 main.tex
added table discussion

--- 2018-02-27 main.tex
@@
 this is similar to \package{numpy} record arrays \citep{numpy} or
-\package{pandas} dataframes \citep{pandas} but with modifications for
+\package{pandas} data frames \citep{pandas} but with modifications for
 astronomical data. Most notably, tables from \package{astropy.table}
 allow for table or column metadata and can handle
-vectors or arrays as table entries.
-The subpackage was described in
+vectors/arrays or arbitrary objects (with suitable column-like characteristics)
+as table entries. The subpackage was described in
 detail in \cite{astropy}.  Thus, in what follows, we only summarize
@@
 coordinates to a different frame or accessing the date/time in the desired time scale).
+
+Additionally, there is now interoperability between \texttt{Table}
+objects and \package{pandas} data frames using the \texttt{Table.to_pandas()}
+and \texttt{Table.from_pandas()} methods. \texttt{Table.to_pandas()} is,
+however, limited to a subset of possible \texttt{Table} objects, because several
+of the features outlined above cannot be represented as \package{pandas} data
+frames. While these features might be contributed to or combined with
+\package{pandas} at a later date, the architectural differences that
+enable these areas are significant, so no one has yet volunteered to do this
+major undertaking.
 

### 2018-02-28 main.tex
consistent capitalization of Astropy Project

@@
 \begin{abstract}
-The \astropy project supports and fosters the development of open-source and openly-developed
+The \astropy Project supports and fosters the development of open-source and openly-developed
 \python packages that provide commonly-needed functionality to the astronomical
 community.
-A key element of the \astropy project is the core package \astropypkg, which serves as the
+A key element of the \astropy Project is the core package \astropypkg, which serves as the
 foundation for more specialized projects and packages.
@@
 We conclude with a future outlook of planned new features and directions for the
-broader \astropy project.
+broader \astropy Project.
 \end{abstract}
@@
 built around a shared foundation.
-The \astropy project has grown to become this community for \python astronomy
+The \astropy Project has grown to become this community for \python astronomy
 software, and the \astropypkg core package is a feature-rich \python library.
@@
 
-The \astropy project aims to provide an open-source and open-development core
+The \astropy Project aims to provide an open-source and open-development core
 package (\astropypkg) and an ecosystem of \emph{affiliated packages} that
@@
 
-The \astropy project aims to develop and provide high-quality code and
+The \astropy Project aims to develop and provide high-quality code and
 documentation according to the best practices in software development.
@@
 
-We start by describing the way the \astropy project functions and is organized
+We start by describing the way the \astropy Project functions and is organized
 in \sectionname~\ref{sec:org}. We then describe the main software efforts
-developed by the \astropy project itself: a core package called \astropypkg
+developed by the \astropy Project itself: a core package called \astropypkg
 (\sectionname~\ref{sec:core}) and several separate packages that help maintain
@@
 
-A major part of the \astropy project is the concept of ``Affiliated Packages.''
+A major part of the \astropy Project is the concept of ``Affiliated Packages.''
 An affiliated package is an astronomy-related
 \python package that is not part of the \astropypkg core package, but
-has requested to be included as part of the \astropy project's
+has requested to be included as part of the \astropy Project's
 community. These packages support the goals and vision of \astropy of
@@
 This process of listing and promoting affiliated packages is one way in which
-the \astropy project tries to increase code re-use in the astronomical
+the \astropy Project tries to increase code re-use in the astronomical
 community.
@@
 
-The \astropy project, as of the version 2.0 release, does not receive any direct
+The \astropy Project, as of the version 2.0 release, does not receive any direct
 financial support for the development of \astropypkg.
 Development of the software, all supporting materials, and community support are
-provided by individuals who work on the \astropy project in their own personal
+provided by individuals who work on the \astropy Project in their own personal
 time, by individuals or groups contributing to \astropy as part of a research
@@
 for sustainability has not yet been established.
-The \astropy project has the ability to accept financial contributions
+The \astropy Project has the ability to accept financial contributions
 from institutions or individuals through the NumFOCUS\footnote{NumFOCUS
 is a 501(c)(3) nonprofit that supports and promotes world-class, innovative,
-open source scientific computing.} organization. NumFOCUS has, to date, covered the direct costs incurred by the \astropy project.
+open source scientific computing.} organization. NumFOCUS has, to date, covered the direct costs incurred by the \astropy Project.
 
@@
 \label{sec:core}
-The \astropy project aims to provide \python-based packages for all tasks that
+The \astropy Project aims to provide \python-based packages for all tasks that
 are commonly needed in a large subset of the astronomical community.
@@
 instead compare each tool to all other tools. The benchmarks are thus useful
-beyond the \astropy project since they allow all of the tools to be compared to
+beyond the \astropy Project since they allow all of the tools to be compared to
 all other tools. The tools included in the benchmark at the moment include the
@@
 originally developed for the \astropypkg core package and affiliated packages
-maintained by the \astropy project.
+maintained by the \astropy Project.
 The package template also provides a testing framework, template configurations
@@
 during the documentation build process.
-For the \astropy project, we have developed several \package{Sphinx} extensions
+For the \astropy Project, we have developed several \package{Sphinx} extensions
 that facilitate automatically generating API documentation for large projects,
@@
 
-Beyond the core code, the \astropy project is also further developing the
+Beyond the core code, the \astropy Project is also further developing the
 \astropy-managed affiliated packages.
@@
 simulation results, and writing publications.
-The strong emphasis that the \astropy project puts on reliability and high coding
+The strong emphasis that the \astropy Project puts on reliability and high coding
 standards helps users to trust the calculations performed with \astropypkg and
@@
 
-The \astropy project is also spreading awareness of best practices in
+The \astropy Project is also spreading awareness of best practices in
 community-driven software development.
@@
 encourages and welcomes new contributions from all.
-Thus, while the \astropy project provides and develops software and tools
+Thus, while the \astropy Project provides and develops software and tools
 essential to modern astronomical research, it also helps to prepare the current

### 2018-02-28 main.tex
addressed @bsipocz's suggestions

@@
 are necessary as the core underpinnings of \astropy packages.  Often this means
-simply means using these packages as ``building blocks'' (E.g., the ubiquitous
+using these packages as ``building blocks'' (E.g., the ubiquitous
 use of \texttt{numpy} arrays throughout \astropypkg).  In other cases this means
@@
 this is similar to \package{numpy} record arrays \citep{numpy} or
-\package{pandas} data frames \citep{pandas} but with modifications for
+\package{pandas} \texttt{DataFrame} objects \citep{pandas}, but with modifications for
 astronomical data. Most notably, tables from \package{astropy.table}
@@
 Additionally, there is now interoperability between \texttt{Table}
-objects and \package{pandas} data frames using the \texttt{Table.to_pandas()}
+and \package{pandas} \texttt{DataFrame} objects using the \texttt{Table.to_pandas()}
 and \texttt{Table.from_pandas()} methods. \texttt{Table.to_pandas()} is,

### 2018-02-28 main.tex
de-capitalize e.g.s

@@
 are necessary as the core underpinnings of \astropy packages.  Often this means
-using these packages as ``building blocks'' (E.g., the ubiquitous
+using these packages as ``building blocks'' (e.g., the ubiquitous
 use of \texttt{numpy} arrays throughout \astropypkg).  In other cases this means
 wrappers around more general algorithms that make them more convenient for
-astronomy use cases (E.g., the model-fitting in the \package{astropy.modeling}
+astronomy use cases (e.g., the model-fitting in the \package{astropy.modeling}
 subpackage discussed in \sectionname~\ref{sec:modeling}).  Sometimes these
 simple wrappers evolve into more complex implementations that address
-astronomically-relevant use cases the general tool does not support (E.g.,
+astronomically-relevant use cases the general tool does not support (e.g.,
 \package{astropy.convolution}, see \sectionname~\ref{ssec:convolution}). As a
@@
 community's needs, and hence the functionality had to be developed wholly from
-the developer resources available in the community (E.g.,
+the developer resources available in the community (e.g.,
 \package{astropy.units}, or \package{astropy.table} when it began). While some
-of this functionality is ``given back'' to the wider community (E.g., myriad bug
+of this functionality is ``given back'' to the wider community (e.g., myriad bug
 fixes for the enabling technologies listed above, and some of the testing and

### 2018-02-28 main.tex
Updated text based on @taldcroft's suggestion

@@
 \package{pandas} at a later date, the architectural differences that
-enable these areas are significant, so no one has yet volunteered to do this
-major undertaking.
+enable these areas are significant, so this would be a major undertaking that would 
+require substantial investment from the core maintainers and communities of both 
+packages.
 

### 2018-03-01 main.tex

--- 2018-02-28 main.tex
@@
 
+% Links to documentation: subpackages
+\newcommand{\astropysubpkg}[1]{\href{http://docs.astropy.org/en/stable/#1/index.html}{\texttt{astropy.#1}}\xspace}
+\newcommand{\astropyiosubpkg}[1]{\href{http://docs.astropy.org/en/stable/io/#1/index.html}{\texttt{astropy.io.#1}}\xspace}
+\newcommand{\astropywcsaxes}{\href{http://docs.astropy.org/en/stable/visualization/wcsaxes/index.html}{\texttt{astropy.visualization.wcsaxes}}\xspace}
+
+% Links to documentation: classes
+\newcommand{\astropyskycoord}{\href{http://docs.astropy.org/en/stable/api/astropy.coordinates.SkyCoord.html}{\texttt{SkyCoord}}\xspace}
+\newcommand{\astropyQuantity}{\href{http://docs.astropy.org/en/stable/api/astropy.units.Quantity.html}{\texttt{Quantity}}\xspace}
+\newcommand{\astropyTime}{\href{http://docs.astropy.org/en/stable/api/astropy.time.Time.html}{\texttt{Time}}\xspace}
+\newcommand{\astropyTable}{\href{http://docs.astropy.org/en/stable/api/astropy.table.Table.html}{\texttt{Table}}\xspace}
+
 \begin{document}
@@
 \begin{abstract}
-The \astropy Project supports and fosters the development of open-source and openly-developed
+The \astropy project supports and fosters the development of open-source and openly-developed
 \python packages that provide commonly-needed functionality to the astronomical
 community.
-A key element of the \astropy Project is the core package \astropypkg, which serves as the
+A key element of the \astropy project is the core package \astropypkg, which serves as the
 foundation for more specialized projects and packages.
@@
 We conclude with a future outlook of planned new features and directions for the
-broader \astropy Project.
+broader \astropy project.
 \end{abstract}
@@
 built around a shared foundation.
-The \astropy Project has grown to become this community for \python astronomy
+The \astropy project has grown to become this community for \python astronomy
 software, and the \astropypkg core package is a feature-rich \python library.
@@
 
-The \astropy Project aims to provide an open-source and open-development core
+The \astropy project aims to provide an open-source and open-development core
 package (\astropypkg) and an ecosystem of \emph{affiliated packages} that
@@
 
-The \astropy Project aims to develop and provide high-quality code and
+The \astropy project aims to develop and provide high-quality code and
 documentation according to the best practices in software development.
@@
 
-We start by describing the way the \astropy Project functions and is organized
+We start by describing the way the \astropy project functions and is organized
 in \sectionname~\ref{sec:org}. We then describe the main software efforts
-developed by the \astropy Project itself: a core package called \astropypkg
+developed by the \astropy project itself: a core package called \astropypkg
 (\sectionname~\ref{sec:core}) and several separate packages that help maintain
@@
 
-A major part of the \astropy Project is the concept of ``Affiliated Packages.''
+A major part of the \astropy project is the concept of ``Affiliated Packages.''
 An affiliated package is an astronomy-related
 \python package that is not part of the \astropypkg core package, but
-has requested to be included as part of the \astropy Project's
+has requested to be included as part of the \astropy project's
 community. These packages support the goals and vision of \astropy of
@@
 This process of listing and promoting affiliated packages is one way in which
-the \astropy Project tries to increase code re-use in the astronomical
+the \astropy project tries to increase code re-use in the astronomical
 community.
@@
 
-The \astropy Project, as of the version 2.0 release, does not receive any direct
+The \astropy project, as of the version 2.0 release, does not receive any direct
 financial support for the development of \astropypkg.
 Development of the software, all supporting materials, and community support are
-provided by individuals who work on the \astropy Project in their own personal
+provided by individuals who work on the \astropy project in their own personal
 time, by individuals or groups contributing to \astropy as part of a research
@@
 for sustainability has not yet been established.
-The \astropy Project has the ability to accept financial contributions
+The \astropy project has the ability to accept financial contributions
 from institutions or individuals through the NumFOCUS\footnote{NumFOCUS
 is a 501(c)(3) nonprofit that supports and promotes world-class, innovative,
-open source scientific computing.} organization. NumFOCUS has, to date, covered the direct costs incurred by the \astropy Project.
-
-\subsection{Reuse of the scientific Python ecosystem}
-
-The \astropy Project is built on a philosophy of building from the existing
-Python scientific ecosystem wherever possible. Many of the enabling technologies
-like \texttt{numpy}, \texttt{scipy}, \texttt{matplotlib}, or \texttt{cython},
-are necessary as the core underpinnings of \astropy packages.  Often this means
-using these packages as ``building blocks'' (e.g., the ubiquitous
-use of \texttt{numpy} arrays throughout \astropypkg).  In other cases this means
-wrappers around more general algorithms that make them more convenient for
-astronomy use cases (e.g., the model-fitting in the \package{astropy.modeling}
-subpackage discussed in \sectionname~\ref{sec:modeling}).  Sometimes these
-simple wrappers evolve into more complex implementations that address
-astronomically-relevant use cases the general tool does not support (e.g.,
-\package{astropy.convolution}, see \sectionname~\ref{ssec:convolution}). As a
-broad rule, the Project explicitly encourages re-use of code where possible.
-
-However, the boundaries of when this re-use is called for often ambiguous.  Some
-of the examples above only evolved after significant debate in the community
-over whether these algorithms were sufficient.  Other times, even apparently
-general functionality did not exist in the wider ecosystem that met the \astropy
-community's needs, and hence the functionality had to be developed wholly from
-the developer resources available in the community (e.g.,
-\package{astropy.units}, or \package{astropy.table} when it began). While some
-of this functionality is ``given back'' to the wider community (e.g., myriad bug
-fixes for the enabling technologies listed above, and some of the testing and
-documentation architecture), in general, careful consideration is taken of
-whether the additional effort to make a piece of \astropy, and it is only
-``extracted'' when it seems plausible that the ongoing effort is worth the
-reward in the form of additional contributors or maintainers.
+open source scientific computing.} organization. NumFOCUS has, to date, covered the direct costs incurred by the \astropy project.
 
@@
 \label{sec:core}
-The \astropy Project aims to provide \python-based packages for all tasks that
+The \astropy project aims to provide \python-based packages for all tasks that
 are commonly needed in a large subset of the astronomical community.
@@
 instead compare each tool to all other tools. The benchmarks are thus useful
-beyond the \astropy Project since they allow all of the tools to be compared to
+beyond the \astropy project since they allow all of the tools to be compared to
 all other tools. The tools included in the benchmark at the moment include the
@@
 
-The \package{astropy.table} subpackage provides functionality for
+The \astropysubpkg{table} subpackage provides functionality for
 representing and manipulating heterogeneous data. In some respects,
 this is similar to \package{numpy} record arrays \citep{numpy} or
-\package{pandas} \texttt{DataFrame} objects \citep{pandas}, but with modifications for
-astronomical data. Most notably, tables from \package{astropy.table}
+\package{pandas} dataframes \citep{pandas} but with modifications for
+astronomical data. Most notably, tables from \astropysubpkg{table}
 allow for table or column metadata and can handle
-vectors/arrays or arbitrary objects (with suitable column-like characteristics)
-as table entries. The subpackage was described in
+vectors or arrays as table entries.
+The subpackage was described in
 detail in \cite{astropy}.  Thus, in what follows, we only summarize
-key new features or updates to \package{astropy.table} since the
+key new features or updates to \astropysubpkg{table} since the
 previous \astropy paper. These are support for grouped table
@@
 represent catalogs of sources or time series in \astropy, while having both the
-benefits of the \texttt{Table} object (e.g., accessing specific rows/columns
+benefits of the \astropyTable object (e.g., accessing specific rows/columns
 or groups of them and combining tables) and of, for example,
-the \texttt{SkyCoord} or the \texttt{Time} classes (e.g., converting the
+the \astropyskycoord or the \astropyTime classes (e.g., converting the
 coordinates to a different frame or accessing the date/time in the desired time scale).
 
-Additionally, there is now interoperability between \texttt{Table}
-and \package{pandas} \texttt{DataFrame} objects using the \texttt{Table.to_pandas()}
-and \texttt{Table.from_pandas()} methods. \texttt{Table.to_pandas()} is,
-however, limited to a subset of possible \texttt{Table} objects, because several
-of the features outlined above cannot be represented as \package{pandas} data
-frames. While these features might be contributed to or combined with
-\package{pandas} at a later date, the architectural differences that
-enable these areas are significant, so no one has yet volunteered to do this
-major undertaking.
-
 \subsection{\package{io}}
 
-The \package{astropy.io} subpackage provides support for reading and writing
+The \package{astropy.io} subpackages provide support for reading and writing
 data to a variety of ASCII and binary file formats, such as a wide range of
@@
 memory until requested.  This approach should provide substantial speed-ups
-when using the convenience functions (e.g., \texttt{getheader()} or
-\texttt{getdata()}) to get an HDU that is near the beginning in a file with
+when using the convenience functions (e.g., \href{http://docs.astropy.org/en/stable/io/fits/api/files.html#getheader}{\texttt{getheader()}} or
+\href{http://docs.astropy.org/en/stable/io/fits/api/files.html#getdata}{\texttt{getdata()}}) to get an HDU that is near the beginning in a file with
 many HDUs.
+
+\subsubsection{HDF5}
+
+The \package{astropy.io.misc.hdf5} subpackage provides support for binary
+read and write access to files in the \emph{Hierarchical Data Format}
+(HDF5), if the \package{h5py} package is installed. Astropy table I/O
+is offered transparently through \texttt{Table.read()} and
+\texttt{Table.write()}, analogously to the other auto-detected
+formats. The keyword \texttt{path='group/subgroup/dataset'} specifies
+the path to the data inside the file's hierarchical structure.
 
@@
 it using input values with different but equivalent units. For example, the
-blackbody model (\texttt{BlackBody1D}) can be used to fit observed flux
-densities in a variety of units and as a function of different units of
-spectral coordinates (e.g., wavelength or frequency).
+blackbody model
+(\href{http://docs.astropy.org/en/stable/api/astropy.modeling.blackbody.BlackBody1D.html}{\texttt{BlackBody1D}})
+can be used to fit observed flux densities in a variety of units and as a
+function of different units of spectral coordinates (e.g., wavelength or
+frequency).
 
 \subsection{Convolution}
-\label{ssec:convolution}
-
-The \package{astropy.convolution} subpackage implements
+
+The \astropysubpkg{convolution} subpackage implements
 \textit{normalized convolution} \citep[e.g.,][]{Knutsson1993}, an image
@@
 originally developed for the \astropypkg core package and affiliated packages
-maintained by the \astropy Project.
+maintained by the \astropy project.
 The package template also provides a testing framework, template configurations
@@
 during the documentation build process.
-For the \astropy Project, we have developed several \package{Sphinx} extensions
+For the \astropy project, we have developed several \package{Sphinx} extensions
 that facilitate automatically generating API documentation for large projects,
@@
 
-Beyond the core code, the \astropy Project is also further developing the
+Beyond the core code, the \astropy project is also further developing the
 \astropy-managed affiliated packages.
@@
 simulation results, and writing publications.
-The strong emphasis that the \astropy Project puts on reliability and high coding
+The strong emphasis that the \astropy project puts on reliability and high coding
 standards helps users to trust the calculations performed with \astropypkg and
@@
 
-The \astropy Project is also spreading awareness of best practices in
+The \astropy project is also spreading awareness of best practices in
 community-driven software development.
@@
 encourages and welcomes new contributions from all.
-Thus, while the \astropy Project provides and develops software and tools
+Thus, while the \astropy project provides and develops software and tools
 essential to modern astronomical research, it also helps to prepare the current

### 2018-03-01 main.tex
address review comments

--- 2018-02-28 main.tex
@@
 
-The \astropy Project aims to provide an open-source and open-development core
+The \astropy project aims to provide an open-source and open development core
 package (\astropypkg) and an ecosystem of \emph{affiliated packages} that
 support astronomical functionality in the \python programming language.
+``Open development'' describes a process where anybody with an internet connection can suggest changes to the source code and contribute their opinion when new features, bug fixes, or other code changes, governance, or any other aspect of the development process is discussed (see Sect.~\ref{sect:devmod} and \ref{sect:ape} of how this is organized in practice).
 The \astropypkg core package is now a feature-rich library of sufficiently
@@
 this is similar to \package{numpy} record arrays \citep{numpy} or
-\package{pandas} \texttt{DataFrame} objects \citep{pandas}, but with modifications for
+\package{pandas} dataframes \citep{pandas} but with modifications for
 astronomical data. Most notably, tables from \package{astropy.table}
 allow for table or column metadata and can handle
-vectors/arrays or arbitrary objects (with suitable column-like characteristics)
-as table entries. The subpackage was described in
+vectors or arrays as table entries.
+The subpackage was described in
 detail in \cite{astropy}.  Thus, in what follows, we only summarize
@@
 coordinates to a different frame or accessing the date/time in the desired time scale).
-
-Additionally, there is now interoperability between \texttt{Table}
-and \package{pandas} \texttt{DataFrame} objects using the \texttt{Table.to_pandas()}
-and \texttt{Table.from_pandas()} methods. \texttt{Table.to_pandas()} is,
-however, limited to a subset of possible \texttt{Table} objects, because several
-of the features outlined above cannot be represented as \package{pandas} data
-frames. While these features might be contributed to or combined with
-\package{pandas} at a later date, the architectural differences that
-enable these areas are significant, so this would be a major undertaking that would 
-require substantial investment from the core maintainers and communities of both 
-packages.
 

### 2018-03-01 registry.tex
Using latest version of the package registry to generate the table

@@
 \href{http://github.com/astroML/astroML}{astroML} & Yes & \href{https://pypi.python.org/pypi/astroML}{astroML} & Jake Vanderplas &  \\
-\href{https://github.com/astropy/astroplan}{astroplan} & No & \href{https://pypi.python.org/pypi/astroplan}{astroplan} & Brett Morris & \citealt{astroplan_AAS} \\
+\href{https://github.com/astropy/astroplan}{astroplan} & No & \href{https://pypi.python.org/pypi/astroplan}{astroplan} & Brett Morris & \citealt{astroplan} \\
 \href{http://github.com/astropy/astroquery.git}{astroquery} & Yes & \href{https://pypi.python.org/pypi/astroquery}{astroquery} & Adam Ginsburg and Brigitta Sipocz & \citealt{astroquery} \\
@@
 \href{http://github.com/astropy/specutils.git}{specutils} & No & \href{https://pypi.python.org/pypi/specutils}{specutils} & Nicholas Earl, Adam Ginsburg, Steve Crawford, Erik Tollerud &  \\
+\href{https://github.com/spacetelescope/spherical_geometry.git}{spherical\_geometry} & No & \href{https://pypi.python.org/pypi/spherical-geometry}{spherical-geometry} & Bernie Simon and Michael Droettboom &  \\
 \href{https://github.com/StingraySoftware/stingray}{stingray} & No & \href{https://pypi.python.org/pypi/stingray}{stingray} & Daniela Huppenkothen, Matteo Bachetti, Abigail Stevens, Simone Migliari, and Paul Balm &  \\

### 2018-03-01 main.tex
Removing provisional packages section
Change wording as suggested by @crawfordsm

@@
 
-The \astropy project aims to provide an open-source and open development core
+The \astropy Project aims to provide an open-source and open-development core
 package (\astropypkg) and an ecosystem of \emph{affiliated packages} that
 support astronomical functionality in the \python programming language.
-``Open development'' describes a process where anybody with an internet connection can suggest changes to the source code and contribute their opinion when new features, bug fixes, or other code changes, governance, or any other aspect of the development process is discussed (see Sect.~\ref{sect:devmod} and \ref{sect:ape} of how this is organized in practice).
 The \astropypkg core package is now a feature-rich library of sufficiently
@@
 for sustainability has not yet been established.
-The \astropy project has the ability to accept financial contributions
+The \astropy Project has the ability to accept financial contributions
 from institutions or individuals through the NumFOCUS\footnote{NumFOCUS
 is a 501(c)(3) nonprofit that supports and promotes world-class, innovative,
-open source scientific computing.} organization. NumFOCUS has, to date, covered the direct costs incurred by the \astropy project.
+open source scientific computing.} organization. NumFOCUS has, to date, covered the direct costs incurred by the \astropy Project.
+
+\subsection{Reuse of the scientific Python ecosystem}
+
+The \astropy Project is built on a philosophy of building from the existing
+Python scientific ecosystem wherever possible. Many of the enabling technologies
+like \texttt{numpy}, \texttt{scipy}, \texttt{matplotlib}, or \texttt{cython},
+are necessary as the core underpinnings of \astropy packages.  Often this means
+using these packages as ``building blocks'' (e.g., the ubiquitous
+use of \texttt{numpy} arrays throughout \astropypkg).  In other cases this means
+wrappers around more general algorithms that make them more convenient for
+astronomy use cases (e.g., the model-fitting in the \package{astropy.modeling}
+subpackage discussed in \sectionname~\ref{sec:modeling}).  Sometimes these
+simple wrappers evolve into more complex implementations that address
+astronomically-relevant use cases the general tool does not support (e.g.,
+\package{astropy.convolution}, see \sectionname~\ref{ssec:convolution}). As a
+broad rule, the Project explicitly encourages re-use of code where possible.
+
+However, the boundaries of when this re-use is called for often ambiguous.  Some
+of the examples above only evolved after significant debate in the community
+over whether these algorithms were sufficient.  Other times, even apparently
+general functionality did not exist in the wider ecosystem that met the \astropy
+community's needs, and hence the functionality had to be developed wholly from
+the developer resources available in the community (e.g.,
+\package{astropy.units}, or \package{astropy.table} when it began). At the same 
+time, however, the \astropy Project has provided the wider community with myriad bug
+fixes to the enabling technologies listed above, as well as the testing and
+documentation architecture. Functionality is only ``extracted'' from \astropy to 
+other packages after careful consideration that includes considering the impact 
+on the maintenance and support of \astropy.
 
@@
 this is similar to \package{numpy} record arrays \citep{numpy} or
-\package{pandas} dataframes \citep{pandas} but with modifications for
+\package{pandas} \texttt{DataFrame} objects \citep{pandas}, but with modifications for
 astronomical data. Most notably, tables from \package{astropy.table}
 allow for table or column metadata and can handle
-vectors or arrays as table entries.
-The subpackage was described in
+vectors/arrays or arbitrary objects (with suitable column-like characteristics)
+as table entries. The subpackage was described in
 detail in \cite{astropy}.  Thus, in what follows, we only summarize
@@
 coordinates to a different frame or accessing the date/time in the desired time scale).
+
+Additionally, there is now interoperability between \texttt{Table}
+and \package{pandas} \texttt{DataFrame} objects using the \texttt{Table.to_pandas()}
+and \texttt{Table.from_pandas()} methods. \texttt{Table.to_pandas()} is,
+however, limited to a subset of possible \texttt{Table} objects, because several
+of the features outlined above cannot be represented as \package{pandas} data
+frames. While these features might be contributed to or combined with
+\package{pandas} at a later date, the architectural differences that
+enable these areas are significant, so this would be a major undertaking that would 
+require substantial investment from the core maintainers and communities of both 
+packages.
 

### 2018-03-02 response.txt
Update response according to comments

@@
 >  where appropriate.
-
-We have addressed all of the stylistic issues that were raised by the referee.
-Here are some responses to the more detailed comments:
-
-Comment on styles:
-As it was not related to the section, we removed the first paragraph 
-in the APE section that commented on different styles.  However, we
-did add a comment in the affiliated package section indicating that
-they may have different requirements and structure than the core package.
-
-Comment on NDData:
-At the time of initial development, the developers were not aware of 
-any open source packages that would have fit the requirements of NDData.  Since
-then, we have been working with different groups (LSST, sunypy) to coordinate
-development of the NDData interface as well as assessing other attempts at 
-something similar.  There is currently an APE about this under discussion.
 
@@
 
+This is an important point, but turns out to be very difficult to generalize how these decisions are made (ironically!).
+From a *dependency* point of view, Astropy deeply intertwines with the existing Python scientific ecosystem.
+Where possible we always try to use other tools instead of building our own.
+Some major astropy functionality is essentially an astro-relevant "wrapper" around existing code.
+For example, modeling makes it easier to use fitting functions from scipy with models that are primarily of interest in astronomy.
+Other bits of functionality are really astro-specific or the work to make it more "general" is difficult.
+The coordinates and nddata subpackages are good examples of this latter case - despite the general-sounding names, they are focused on the needs of the astronomy community.
+The `nddata` case the referee mentions is particularly notable because the actual underlying machinery is built completely on `numpy`, but essentially provides a standard "metadata" language for N-dimensional data *in astronomy*.
+That is, it has attributes like `wcs`, `flags`, etc, that have a particular meaning and shared "cultural" understanding in astronomy that is lost if it is made into a more "general" tool.
+
+Other pieces were originally more astro-specific or had no equivalent when they were started and have grown more generalizable as time goes on - e.g.
+units and table.
+In general, it's considered "best effort" to generalize these things because the first priority is basic tools for astronomy.
+Such changes come with non-trivial added cost because that means it now needs a maintainer to do releases, review pull requests, maintain the docs, etc.
+Using the astropy community helps this, of course, but it is still more work than simply leaving these things in the core.
+So how much anything is generalized dependes heavily on the time/interest of an individual to do the porting.
+So for example some of the documentation and testing machinery is now (after v2.0) getting moved from astropy into more generally-useful independent packages.
+Meanwhile, units/Quantity would require a much larger effort to disentangle from astropy and maintain independently - but no maintainer with enough time has thus far volunteered.
+
+We have added a new section 2.7 outlining some of the above discussion.
+
+Additionally, as the referee points out, `astropy.table` represents a particularly unusual case for this.
+It falls under the "historical" case in that it was started before Pandas.
+By the time Pandas became a standard tool in the pydata stack, tables had already developed a fairly large user base in astronomy, so it was not an option to completely eliminate it and say "use Pandas".
+It had also developed several features missing from Pandas but important for astronomy users (e.g., support for units, fully-fledged objects as columns, and support for the FITS table concept of "multidimensional columns").
+The `astropy.table` investigated this possibility, but it was clear that some of the features would require major incompatible changes *in Pandas* to do this, and it was clear by then that the Pandas user base was too large to accept this.
+This led to the current solution of `to_pandas` and `from_pandas`, which allows transformation back-and-forth for the use cases where this is supported.
+We have added a briefer summary of this discussion to the text in the tables subsection (3.5.2).
+
 ________________________

### 2018-03-02 main.tex
Typo fix from @crwafordsm's feedback

--- 2018-03-01 main.tex
@@
 for sustainability has not yet been established.
-The \astropy project has the ability to accept financial contributions
+The \astropy Project has the ability to accept financial contributions
 from institutions or individuals through the NumFOCUS\footnote{NumFOCUS
 is a 501(c)(3) nonprofit that supports and promotes world-class, innovative,
-open source scientific computing.} organization. NumFOCUS has, to date, covered the direct costs incurred by the \astropy project.
+open source scientific computing.} organization. NumFOCUS has, to date, covered the direct costs incurred by the \astropy Project.
+
+\subsection{Reuse of the scientific Python ecosystem}
+
+The \astropy Project is built on a philosophy of building from the existing
+Python scientific ecosystem wherever possible. Many of the enabling technologies
+like \texttt{numpy}, \texttt{scipy}, \texttt{matplotlib}, or \texttt{cython},
+are necessary as the core underpinnings of \astropy packages.  Often this means
+using these packages as ``building blocks'' (e.g., the ubiquitous
+use of \texttt{numpy} arrays throughout \astropypkg).  In other cases this means
+wrappers around more general algorithms that make them more convenient for
+astronomy use cases (e.g., the model-fitting in the \package{astropy.modeling}
+subpackage discussed in \sectionname~\ref{sec:modeling}).  Sometimes these
+simple wrappers evolve into more complex implementations that address
+astronomically-relevant use cases the general tool does not support (e.g.,
+\package{astropy.convolution}, see \sectionname~\ref{ssec:convolution}). As a
+broad rule, the Project explicitly encourages re-use of code where possible.
+
+However, the boundaries of when this re-use is called for is often ambiguous.  Some
+of the examples above only evolved after significant debate in the community
+over whether these algorithms were sufficient.  Other times, even apparently
+general functionality did not exist in the wider ecosystem that met the \astropy
+community's needs, and hence the functionality had to be developed wholly from
+the developer resources available in the community (e.g.,
+\package{astropy.units}, or \package{astropy.table} when it began). At the same 
+time, however, the \astropy Project has provided the wider community with myriad bug
+fixes to the enabling technologies listed above, as well as the testing and
+documentation architecture. Functionality is only ``extracted'' from \astropy to 
+other packages after careful consideration that includes considering the impact 
+on the maintenance and support of \astropy.
 
@@
 this is similar to \package{numpy} record arrays \citep{numpy} or
-\package{pandas} dataframes \citep{pandas} but with modifications for
+\package{pandas} \texttt{DataFrame} objects \citep{pandas}, but with modifications for
 astronomical data. Most notably, tables from \astropysubpkg{table}
 allow for table or column metadata and can handle
-vectors or arrays as table entries.
-The subpackage was described in
+vectors/arrays or arbitrary objects (with suitable column-like characteristics)
+as table entries. The subpackage was described in
 detail in \cite{astropy}.  Thus, in what follows, we only summarize

### 2018-03-02 main.tex
Update main.tex
Fix for broken build

@@
 Additionally, there is now interoperability between \texttt{Table}
-and \package{pandas} \texttt{DataFrame} objects using the \texttt{Table.to_pandas()}
-and \texttt{Table.from_pandas()} methods. \texttt{Table.to_pandas()} is,
+and \package{pandas} \texttt{DataFrame} objects using the \texttt{Table.to\_pandas()}
+and \texttt{Table.from\_pandas()} methods. \texttt{Table.to\_pandas()} is,
 however, limited to a subset of possible \texttt{Table} objects, because several

### 2018-03-12 main.tex

@@
 support or training.
-Other packages are developed by individual researchers or research groups and
-are then typically used by smaller groups for more domain-specific purposes.
+Other packages are developed by individual researchers or research groups,
+are then typically used by smaller groups for more domain-specific purposes, and 
+may have less extensive user support. 
 For both packages meant for wider distribution and for scripts specific to
 particular research projects, a library that addresses common astronomical tasks
-simplifies the software development process.
+simplifies the software development process by encouraging the reuse of common
+functions.  
 The users of such a library then also benefit from a community and ecosystem
 built around a shared foundation.
-The \astropy Project has grown to become this community for \python astronomy
-software, and the \astropypkg core package is a feature-rich \python library.
+The \astropy project has grown to become this community for \python astronomy
+software, and the \astropypkg core package has become this shared foundation.
 
@@
 \python\footnote{\url{https://www.python.org/}} is an increasingly popular, general-purpose
-programming language that is available under a permissive open source software license and is free of
+programming language that is available under a permissive open-source software license and is free of
 charge for all major operating systems. The programming language has become especially popular
-in the quantitative sciences, where researchers must simultaneously produce research, perform
+in the quantitative sciences, where researchers must simultaneously conduct research, perform
 data analysis, and develop software. A large part of this success owes itself to the vibrant
@@
 (e.g., \astropywcsaxes).
-New functionality benefits from having a rapid development and release cycle that is not tied to that of the \astropypkg core (\sectionname~\ref{sect:releasecycle}).
+New functionality benefits from having a rapid development and release cycle 
+that is not tied to that of the \astropypkg core (\sectionname~\ref{sect:releasecycle}).  
+These projects may also have less stringent requirements for style, testing, or
+development as the core package.
 
@@
 is a 501(c)(3) nonprofit that supports and promotes world-class, innovative,
-open source scientific computing.} organization. NumFOCUS has, to date, covered the direct costs incurred by the \astropy Project.
+open-source scientific computing.} organization. NumFOCUS has, 
+to date, covered the direct costs incurred by the \astropy Project.
 
@@
 on the maintenance and support of \astropy.
+
+>>>>>>> 0a5c93ffa551be5fd4bba22f4be705f8d79a39bd
 

### 2018-03-12 response.txt
update suggested edits

@@
 any open source packages that would have fit the requirements of NDData.  Since
-then, we have been working with different groups (LSST, sunypy) to coordinate
+then, we have been working with different groups (LSST, sunpy) to coordinate
 development of the NDData interface as well as assessing other attempts at 
-something similar.  There is currently an APE about this under discussion.
+something similar.  There is currently an APE about this under 
+discussion (https://github.com/astropy/astropy-APEs/pull/14)  .
 

### 2018-03-12 response.txt

@@
 > either inline in the paper body or in the appendix.
+
+We did include code snippets in the first astropy paper from 2013, and
+it is not much work; we could use the same scripts to provide nicely
+formatted code examples with appropriate syntax highlighting here. However,
+we have made a conscious decision to avoid that this time as far as
+possible. We will explain our reasoning below, but if the referee
+insists, we can quickly add a few examples in a second revision.
+
+The main reasons why we chose NOT to include code samples are:
+
+- While we aim for stability, many of the newsest features are still
+  considered provisional, meaning that their API can still change. The
+  paper describes astropy 2.0, but at the time of writing this,
+  astropy 3.0 is already released. We hope that this paper is useful
+  for years to come. Code examples for a specific version are at risk
+  of being outdated much sooner than that.
+
+- Code examples belong in the documentation. In the documentation at
+  cods.astropy.org we provide extensive examples with enough comments
+  to actually understand what is going on. If readers are curious, we
+  want them to read the documentation.
+
+- It takes a lot of space to explain a code example well. Currently,
+  the text lists the names of the most important classes or
+  functions. To give a meaningful example that shows these classes in
+  action and is useful to people not familiar with astropy (or even
+  Python), we would have to detail several parameters and the format
+  of the results. We think that it is more useful to explain the
+  general concept in the paper and not the names and the specific
+  implementation of the functions and parameters.
+
+- Most new features would require some setup. For example, showing the
+  code for WCS axis plotting is not very useful without loading an
+  image with a WCS in it first. More complex features profit more from
+  code examples, but they also require much more setup to make such an
+  example self-consistent and useful. Again, the documentation is a better
+  place for that.
+
+As a compromise, we have added links to the documentation in many places and
+there is a link in the introduction that points to the github repository where
+this article is written. That repository contains (and the text in the
+introduction says this) the scripts that we used to generate the figures.
 

### 2018-03-12 response.txt

@@
 
+This question is at the intersection of two communities. On the one
+side, there is the open source community, which by itself consists of
+many different projects with vastly different norms and
+processes. Many terms, "open develoment" being one of them, are used
+with slightly different meanings in different parts of this
+community. The model of astropy - the development happens openly on
+github and anyone with an internet connection can comment on issues or
+propose a pull request, but only a select set of maintainers can merge
+them - is by no means special. Many open source communities work in a
+very similar way, although they may use different terminology to
+describe it. On the other hand, there is the astrophysics community,
+and while there are several open source and open development (in the
+way astropy uses the term) projects in astronomy, astropy is probably
+the biggest one. Many astronmers are not involved in any open
+development (also many make use of open source projects they are not
+involved in e.g. GNU/Linux), and the concept is new to many of
+them. This article caters mostly to the astrophysics community, so we
+decided to add a definition, but we refrain from a comparative
+discussion with other open source projects.
+
 > A number of times I found myself wondering how the Astropy projects decides

### 2018-03-12 main.tex
update suggested edits
adding more edits

@@
 support astronomical functionality in the \python programming language.
+``Open development'' describes a process where anybody with an internet connection can suggest changes to the source code and contribute their opinion when new features, bug fixes, or other code changes, governance, or any other aspect of the development process is discussed (see Sect.~\ref{sect:devmod} and \ref{sect:ape} of how this is organized in practice).
 The \astropypkg core package is now a feature-rich library of sufficiently
@@
 \subsection{APEs - Astropy Proposals for Enhancement}
+\label{sect:ape}
 
@@
 When a community consensus emerges, the APEs are accepted and become
-the basis for future work.
-In cases where consensus cannot be reached, the
+the basis for future work.  In cases where consensus cannot be reached, the
 \astropy coordination committee may decide to close the discussion and
@@
 These projects may also have less stringent requirements for style, testing, or
-development as the core package.
+development as compared to the core package.
 
@@
 on the maintenance and support of \astropy.
-
->>>>>>> 0a5c93ffa551be5fd4bba22f4be705f8d79a39bd
 

### 2018-03-12 main.tex
Update main.tex
attempt to account for latex in link

@@
 While many \python projects adopt a ``Benevolent Dictator For Life'' (BDFL)
-model\footenote{https://en.wikipedia.org/wiki/Benevolent\_dictator\_for\_life}, \astropy has instead opted for a \emph{coordination committee}.  This
+model, \astropy has instead opted for a \emph{coordination committee}.  This
 is in part due to the nature of the project as a large-scale collaboration
@@
 
-\begin{deluxetable*}{cccp{3in}c}
-  \tablecaption{Registry of provisionally accepted affiliated packages.}
-  \label{tab:registry_prov}
-    \tablehead{
-        \colhead{Package Name} &
-        \colhead{Stable} &
-        \colhead{PyPI Name} &
-        \colhead{Maintainer} &
-        \colhead{Citation}
-      }
-    \startdata
-      \input{registry_prov.tex}
-    \enddata
-\end{deluxetable*}
-
 \end{document}

### 2018-03-12 response.txt
some edits on response.txt

@@
 
-We did include code snippets in the first astropy paper from 2013, and
-it is not much work; we could use the same scripts to provide nicely
-formatted code examples with appropriate syntax highlighting here. However,
-we have made a conscious decision to avoid that this time as far as
-possible. We will explain our reasoning below, but if the referee
-insists, we can quickly add a few examples in a second revision.
-
-The main reasons why we chose NOT to include code samples are:
+We did include code snippets in the first astropy paper from 2013. 
+However, we have made a conscious decision to avoid that this time 
+due to the following reasons:
 
@@
 > 'main.tex' file in the form `\inlinecomment{REVIEWER}{Comment}`
+
+We have updated Figure 6 to have the correct caption. Inline comments
+were also addressed throughout the text.
 

### 2018-03-12 author.tex
Update author.tex
fixed missing parentheses
Minor wording changes
added an additional author

@@
 \newcommand{\afpennstate}{Dept of Astronomy and Astrophysics, Pennsylvania State University, University Park, PA 16802}
-\newcommand{\afgemini}{Gemini Observatory, 670 N. Aohoku Pl, Hilo, HI 96720, USA}
+\newcommand{\afgeminin}{Gemini Observatory, 670 N. Aohoku Pl, Hilo, HI 96720, USA}
+\newcommand{\afgeminis}{Gemini Observatory, Casilla 603, La Serena, Chile}
 \newcommand{\aflco}{Las Cumbres Observatory, 6740 Cortona Drive, Suite 102, Goleta, CA 93117-5575, USA}
@@
 \affiliation{Department of Theoretical Physics \& Astrophysics, Masaryk University, Kotlarska 2, 61137 Brno, Czech Republic}
+
+\author[0000-0002-2618-1124]{Y. P. Bach}
+\affiliation{Department of Physics and Astronomy, Seoul National University, Gwanak-gu, Seoul 08826, South Korea}
 
@@
 \author{P. Hirst}
-\affiliation{\afgemini}
+\affiliation{\afgeminin}
 
@@
 \author{M. Mueller}
-\affil{Brown University/Department of Mathematics, 151 Thayer Street, Providence, RI 02912, USA}
+\affil{Department of Mathematics, Brown University, 151 Thayer Street, Providence, RI 02912, USA}
 
@@
 \author[0000-0002-5445-5401]{G. R. Tremblay}
-\affiliation{{\afcfa}
+\affiliation{{\afcfa}}
 
 \author{J. E. H. Turner}
-\affiliation{\afgemini}
+\affiliation{\afgeminis}
 

### 2018-03-12 main.tex
small update to figure caption
added an additional author

@@
 \href{http://docs.astropy.org/en/stable/api/astropy.visualization.make_lupton_rgb.html}{\texttt{make\_lupton\_rgb()}}
-function to produce the RGB image from three SDSS filter images ($g$, $r$, $i$).
+function to produce the RGB image from three SDSS filter images ($g$, $r$, $i$).  The image  on the left shows 
+the image with the default parameters, whereas the image on the right has paramets set to show a greater dynamical range. 
 \label{fig:ngc6977}}
@@
 is operated by the Association of Universities for Research in Astronomy, Inc., on behalf of the international
-Gemini partnership of Argentina, Brazil, Canada, Chile, and the United States of America.
+Gemini partnership of Argentina, Brazil, Canada, Chile, and the United States of America.  YPB was supported by 
+the Korea Astronomy and Space Science Institute under the R\&D program supervised by the Ministry of Science, 
+ICT and Future Planning.
 

### 2018-03-12 main.tex
added footnote about widespread use of ci-helpers

@@
 While the current development is mostly driven by the needs of the \astropy
-ecosystem, the actual usage of this package is extremely widespread. The current
+ecosystem, the actual usage of this package is extremely widespread\footnote{Approximately 30\%
+of the ci-helpers contributor are coming from outside the astropy community and 
+there are currently 292 repositories on github that has ci-helpers in their travis configuration file.}. The current
 tools support configuration for Travis CI\footnote{\url{https://travis-ci.org/}} and

### 2018-03-13 response.txt
adding additional referee responses
fix typo in link

@@
 Here are some responses to the more detailed comments:
+
+Comment on health of the project:
+
+We have added a plot of contributors per month along with our other metrics
+and some further comments about the health of the project.  A full analysis
+following the CHAOSS framework is beyond the scope of the current paper.
 
@@
 - Code examples belong in the documentation. In the documentation at
-  cods.astropy.org we provide extensive examples with enough comments
+  docs.astropy.org we provide extensive examples with enough comments
   to actually understand what is going on. If readers are curious, we

### 2018-03-14 registry.tex

@@
-\href{http://github.com/aplpy/aplpy.git}{APLpy} & Yes & \href{https://pypi.python.org/pypi/APLpy}{APLpy} & Thomas Robitaille and Eli Bressert &  \\
+\href{https://github.com/aplpy/aplpy}{APLpy} & Yes & \href{https://pypi.python.org/pypi/APLpy}{APLpy} & Thomas Robitaille and Eli Bressert & \citealt{aplpy} \\
 \href{https://github.com/astropy/astroscrappy}{Astro-SCRAPPY} & Yes & \href{https://pypi.python.org/pypi/astroscrappy}{astroscrappy} & Curtis McCully & \citealt{astroscrappy} \\
-\href{http://github.com/astroML/astroML}{astroML} & Yes & \href{https://pypi.python.org/pypi/astroML}{astroML} & Jake Vanderplas &  \\
+\href{https://github.com/astroML/astroML}{astroML} & Yes & \href{https://pypi.python.org/pypi/astroML}{astroML} & Jake Vanderplas & \citealt{astroML_conf, astroML_book} \\
 \href{https://github.com/astropy/astroplan}{astroplan} & No & \href{https://pypi.python.org/pypi/astroplan}{astroplan} & Brett Morris & \citealt{astroplan} \\
-\href{http://github.com/astropy/astroquery.git}{astroquery} & Yes & \href{https://pypi.python.org/pypi/astroquery}{astroquery} & Adam Ginsburg and Brigitta Sipocz & \citealt{astroquery} \\
-\href{http://github.com/astropy/ccdproc.git}{ccdproc} & Yes & \href{https://pypi.python.org/pypi/ccdproc}{ccdproc} & Steven Crawford, Matt Craig, and Michael Seifert & \citealt{ccdproc} \\
+\href{https://github.com/astropy/astroquery}{astroquery} & Yes & \href{https://pypi.python.org/pypi/astroquery}{astroquery} & Adam Ginsburg and Brigitta Sipocz & \citealt{astroquery} \\
+\href{https://github.com/astropy/ccdproc}{ccdproc} & Yes & \href{https://pypi.python.org/pypi/ccdproc}{ccdproc} & Steven Crawford, Matt Craig, and Michael Seifert & \citealt{ccdproc} \\
 \href{https://github.com/jesford/cluster-lensing}{cluster-lensing} & No & \href{https://pypi.python.org/pypi/cluster-lensing}{cluster-lensing} & Jes Ford & \citealt{clusterlensing} \\
@@
 \href{https://github.com/jobovy/galpy}{galpy} & Yes & \href{https://pypi.python.org/pypi/galpy}{galpy} & Jo Bovy & \citealt{galpy} \\
-\href{http://github.com/gammapy/gammapy.git}{gammapy} & No & \href{https://pypi.python.org/pypi/gammapy}{gammapy} & Christoph Deil & \citealt{gammapy} \\
-\href{http://github.com/ejeschke/ginga}{ginga} & Yes & \href{https://pypi.python.org/pypi/ginga}{ginga} & Eric Jeschke and Pey-Lian Lim & \citealt{ginga} \\
-\href{https://github.com/glue-viz/glue.git}{Glue} & Yes & \href{https://pypi.python.org/pypi/glueviz}{glueviz} & Chris Beaumont and Thomas Robitaille & \citealt{glue} \\
-\href{https://github.com/spacetelescope/gwcs.git}{gwcs} & No & \href{https://pypi.python.org/pypi/gwcs}{gwcs} & Nadia Dencheva & \citealt{gwcs} \\
+\href{https://github.com/gammapy/gammapy}{gammapy} & No & \href{https://pypi.python.org/pypi/gammapy}{gammapy} & Christoph Deil & \citealt{gammapy} \\
+\href{https://github.com/ejeschke/ginga}{ginga} & Yes & \href{https://pypi.python.org/pypi/ginga}{ginga} & Eric Jeschke and Pey-Lian Lim & \citealt{ginga} \\
+\href{https://github.com/glue-viz/glue}{Glue} & Yes & \href{https://pypi.python.org/pypi/glueviz}{glueviz} & Chris Beaumont and Thomas Robitaille & \citealt{glue} \\
+\href{https://github.com/spacetelescope/gwcs}{gwcs} & No & \href{https://pypi.python.org/pypi/gwcs}{gwcs} & Nadia Dencheva & \citealt{gwcs} \\
 \href{https://github.com/astropy/halotools}{Halotools} & Yes & \href{https://pypi.python.org/pypi/halotools}{halotools} & Andrew Hearin & \citealt{halotools} \\
-\href{https://github.com/StingraySoftware/HENDRICS}{HENDRICS} & Yes & \href{https://pypi.python.org/pypi/hendrics}{hendrics} & Matteo Bachetti &  \\
-\href{https://github.com/hipspy/hips}{hips} & No & \href{https://pypi.python.org/pypi/hips}{hips} & Christoph Deil and Thomas Boch &  \\
-\href{http://github.com/spacetelescope/imexam}{imexam} & No & \href{https://pypi.python.org/pypi/imexam}{imexam} & Megan Sosey & \citealt{imexam} \\
-\href{https://github.com/linetools/linetools}{linetools} & Yes & \href{https://pypi.python.org/pypi/linetools}{linetools} & J. Xavier Prochaska, Nicolas Tejos, and Neil Crighton &  \\
+\href{https://github.com/StingraySoftware/HENDRICS}{HENDRICS} & Yes & \href{https://pypi.python.org/pypi/hendrics}{hendrics} & Matteo Bachetti & \citealt{hendrics} \\
+\href{https://github.com/hipspy/hips}{hips} & No & \href{https://pypi.python.org/pypi/hips}{hips} & Christoph Deil and Thomas Boch & \citealt{hips} \\
+\href{https://github.com/spacetelescope/imexam}{imexam} & No & \href{https://pypi.python.org/pypi/imexam}{imexam} & Megan Sosey & \citealt{imexam} \\
+\href{https://github.com/linetools/linetools}{linetools} & Yes & \href{https://pypi.python.org/pypi/linetools}{linetools} & J.
+Xavier Prochaska, Nicolas Tejos, and Neil Crighton & \citealt{linetools} \\
 \href{https://github.com/Chandra-MARX/marxs}{marxs} & Yes & \href{https://pypi.python.org/pypi/marxs}{marxs} & Hans Moritz Günther & \citealt{marxs} \\
 \href{https://github.com/zblz/naima}{naima} & Yes & \href{https://pypi.python.org/pypi/naima}{naima} & Victor Zabalza & \citealt{naima} \\
-\href{https://github.com/RiceMunk/omnifit}{omnifit} & Yes & \href{https://pypi.python.org/pypi/omnifit}{omnifit} & Aleksi Suutarinen &  \\
-\href{http://github.com/astropy/photutils.git}{photutils} & No & \href{https://pypi.python.org/pypi/photutils}{photutils} & Larry Bradley and Brigitta Sipocz & \citealt{photutils} \\
+\href{https://github.com/RiceMunk/omnifit}{omnifit} & Yes & \href{https://pypi.python.org/pypi/omnifit}{omnifit} & Aleksi Suutarinen & \citealt{omnifit} \\
+\href{https://github.com/astropy/photutils}{photutils} & No & \href{https://pypi.python.org/pypi/photutils}{photutils} & Larry Bradley and Brigitta Sipocz & \citealt{photutils} \\
 \href{https://github.com/poliastro/poliastro}{poliastro} & No & \href{https://pypi.python.org/pypi/poliastro}{poliastro} & Juan Luis Cano Rodríguez & \citealt{poliastro} \\
-\href{http://github.com/weaverba137/pydl.git}{PyDL} & No & \href{https://pypi.python.org/pypi/pydl}{pydl} & Benjamin Alan Weaver & \citealt{pydl} \\
-\href{https://github.com/astropy/pyregion.git}{pyregion} & Yes & \href{https://pypi.python.org/pypi/pyregion}{pyregion} & Jae-Joon Lee and Christoph Deil &  \\
+\href{https://github.com/weaverba137/pydl}{PyDL} & No & \href{https://pypi.python.org/pypi/pydl}{pydl} & Benjamin Alan Weaver & \citealt{pydl} \\
+\href{https://github.com/astropy/pyregion}{pyregion} & Yes & \href{https://pypi.python.org/pypi/pyregion}{pyregion} & Jae-Joon Lee and Christoph Deil & \citealt{pyregions} \\
 \href{https://github.com/pyspeckit/pyspeckit}{pyspeckit} & Yes & \href{https://pypi.python.org/pypi/pyspeckit}{pyspeckit} & Adam Ginsburg & \citealt{pyspeckit} \\
 \href{https://github.com/olebole/python-cpl}{python-cpl} & No & \href{https://pypi.python.org/pypi/python-cpl}{python-cpl} & Ole Streicher & \citealt{pythoncpl} \\
-\href{https://github.com/pyvirtobs/pyvo.git}{PyVO} & No & \href{https://pypi.python.org/pypi/pyvo}{pyvo} & Stefan Becker &  \\
-\href{https://github.com/astropy/regions}{regions} & No & \href{https://pypi.python.org/pypi/regions}{regions} & Christoph Deil and Johannes King &  \\
-\href{https://github.com/astrofrog/reproject.git}{reproject} & Yes & \href{https://pypi.python.org/pypi/reproject}{reproject} & Thomas Robitaille &  \\
-\href{http://github.com/sncosmo/sncosmo}{sncosmo} & Yes & \href{https://pypi.python.org/pypi/sncosmo}{sncosmo} & Kyle Barbary & \citealt{sncosmo} \\
+\href{https://github.com/pyvirtobs/pyvo}{PyVO} & No & \href{https://pypi.python.org/pypi/pyvo}{pyvo} & Stefan Becker & \citealt{pyvo} \\
+\href{https://github.com/astropy/regions}{regions} & No & \href{https://pypi.python.org/pypi/regions}{regions} & Christoph Deil and Johannes King & \citealt{regions} \\
+\href{https://github.com/astrofrog/reproject}{reproject} & Yes & \href{https://pypi.python.org/pypi/reproject}{reproject} & Thomas Robitaille & \citealt{reproject} \\
+\href{https://github.com/sncosmo/sncosmo}{sncosmo} & Yes & \href{https://pypi.python.org/pypi/sncosmo}{sncosmo} & Kyle Barbary & \citealt{sncosmo} \\
 \href{https://github.com/radio-astro-tools/spectral-cube}{spectral-cube} & Yes & \href{https://pypi.python.org/pypi/spectral-cube}{spectral-cube} & Adam Ginsburg & \citealt{spectralcube} \\
-\href{http://github.com/astropy/specutils.git}{specutils} & No & \href{https://pypi.python.org/pypi/specutils}{specutils} & Nicholas Earl, Adam Ginsburg, Steve Crawford, Erik Tollerud &  \\
-\href{https://github.com/spacetelescope/spherical_geometry.git}{spherical\_geometry} & No & \href{https://pypi.python.org/pypi/spherical-geometry}{spherical-geometry} & Bernie Simon and Michael Droettboom &  \\
-\href{https://github.com/StingraySoftware/stingray}{stingray} & No & \href{https://pypi.python.org/pypi/stingray}{stingray} & Daniela Huppenkothen, Matteo Bachetti, Abigail Stevens, Simone Migliari, and Paul Balm &  \\
+\href{https://github.com/astropy/specutils}{specutils} & No & \href{https://pypi.python.org/pypi/specutils}{specutils} & Nicholas Earl, Adam Ginsburg, Steve Crawford, and Erik Tollerud & \citealt{specutils} \\
+\href{https://github.com/spacetelescope/spherical_geometry}{spherical\_geometry} & No & \href{https://pypi.python.org/pypi/spherical-geometry}{spherical-geometry} & Bernie Simon &  \\
+\href{https://github.com/StingraySoftware/stingray}{stingray} & No & \href{https://pypi.python.org/pypi/stingray}{stingray} & Daniela Huppenkothen, Matteo Bachetti, Abigail Stevens, Simone Migliari, and Paul Balm & \citealt{stingray} \\
+\href{https://github.com/spacetelescope/synphot_refactor}{synphot} & Yes & \href{https://pypi.python.org/pypi/synphot}{synphot} & Pey Lian Lim & \citealt{synphot} \\

### 2018-03-18 main.tex
Fixing minor bibtex issues
updated for v3.0 release

@@
     observation planning can now be completed with \astropypkg or the
-    \astropy-affiliated package \package{astroplan}\citep{astroplan_AAS}.
+    \astropy-affiliated package \package{astroplan}\citep{astroplan}.
 
@@
 Following the release of version 2.0, development on the next major version of
-the \astropypkg core package (version 3.0) has already begun.
+the \astropypkg core package (version 3.0) began.
 On top of planned changes and additions to the core package, we also plan to
@@
 simplify the code base, and reduce the testing overhead for the package.
-\astropypkg version 3.0 is currently scheduled for January 2018.
+\astropypkg version 3.0 ws released in February 2018.
 
@@
 Foundation, the Sloan Foundation, and the Washington Research Foundation. SMC acknowledges the National Research
-Foundation of South Africa. TLA was supported by NASA contract NAS8-03060. Support for EJT. was provided by NASA
+Foundation of South Africa. MVB was supported by NASA's Planetary Astronomy Program.
+TLA was supported by NASA contract NAS8-03060. Support for EJT. was provided by NASA
 through Hubble Fellowship grant No. 51316.01 awarded by the Space Telescope Science Institute, which is operated by

### 2018-04-03 main.tex
Update main.tex
Updated citation for this repository at the request of the journal editor

@@
 to produce the figures, is available in a \github
-repository\footnote{\url{https://github.com/astropy/astropy-v2.0-paper}}
+repository \citep[][]{adrian_price_whelan_2018_1211397}\footnote{Codebase: \url{https://github.com/astropy/astropy-v2.0-paper}}.
 
